### 2017-03-21 Grassmannian_cells.tex
Created tex file and added the basic structure.

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym}
\usepackage[margin=1in]{geometry}

\author{Dylan Rupel}
\author{Thorsten Weist}

\title{Cell Decomposition of Rank 2 Quiver Grassmannians}

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective and preinjective respesentations of a generalized Kronecker quiver admit a cell decomposition.  
  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
\end{abstract}
\maketitle

\section{Introduction}

\section{Quiver Representations}

\section{Compatible Pairs}

\end{document}

### 2017-03-24 Grassmannian_cells.tex
Added very rough outline for introduction.
Added note for acknowledgements.
added abstract
Trying to get a conflict.
making a conflict
Added outline of quiver Grassmannian goals

@@
 
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{definition}{Definition}[theorem]
+\newtheorem{lemma}{Lemma}[theorem]
+\newtheorem{question}{Question}[theorem]
+\newtheorem{proposition}{Proposition}[theorem]
+
+\newcommand{\bfe}{\mathbf{e}}
+\newcommand{\bff}{\mathbf{f}}
+\newcommand{\bfg}{\mathbf{g}}
+\newcommand{\tbfe}{{\tilde\bfe}}
+\newcommand{\tbff}{{\tilde\bff}}
+\newcommand{\tbfg}{{\tilde\bfg}}
+
+\renewcommand{\AA}{\mathbb{A}}
+\newcommand{\ZZ}{\mathbb{Z}}
+\newcommand{\Ext}{\operatorname{Ext}}
+\newcommand{\Hom}{\operatorname{Hom}}
+
+\title{Cell Decomposition of Rank 2 Quiver Grassmannians}
+
 \author{Dylan Rupel}
 \author{Thorsten Weist}
-
-\title{Cell Decomposition of Rank 2 Quiver Grassmannians}
 
@@
 \section{Introduction}
+-something about cluster algebras
+-something about categorification and quiver Grassmannians
+-something about compatible pairs and combinatorial construction of cluster variables
+-statement of our results
+-acknowledgements?
 
-\section{Quiver Representations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Torus Action on Quiver Grassmannians}
+\begin{definition}
+  universal cover $\tilde Q$
+\end{definition}
 
-\section{Compatible Pairs}
+\begin{lemma}
+  how to lift exceptional representations of $Q$ to $\tilde Q$
+\end{lemma}
+
+\begin{lemma}
+  $d:\tilde Q_0\to\ZZ$ defines a torus action on $Gr^Q_\bfe(X)$ if $d(q,w\rho)-d(q,w)=c_\rho$ for all $w\in W_{\tilde Q_1}$
+\end{lemma}
+
+\begin{lemma}
+  There exists $d:\tilde Q_0\to\ZZ$ such that $d(q,w)\ne d(q',w')$ for all $q,q',w,w'$ with $\dim X_{q,w}\ne0$ and $\dim X_{q',w'}\ne0$.
+\end{lemma}
+
+\begin{theorem}
+  $Gr^Q_\bfe(X)^T\cong\bigsqcup_{\tilde\bfe of type \bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$
+\end{theorem}
+
+\begin{corollary}
+  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
+  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
+\end{corollary}
+
+\begin{question}
+  What are the ranks of these bundles?  Poincar\'e polynomials?
+\end{question}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quiver Grassmannians of $\widetilde{K(n)}$}
+
+Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
+For $m\ge1$, let $P_m$ be the preprojective representation of $K(n)$ with dimension vector $(u_m,u_{m-1})$.
+
+Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$.
+\begin{lemma}
+  \label{le:preprojective lifts}
+  There exist lifts $\tilde P_{m-1,i}$ for $1\le i\le n$ of $P_{m-1}$ to $\widetilde{K(n)}$ so that:
+  \begin{enumerate}
+    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$;
+    \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
+      \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
+    \item The lifts $\tilde P_{m-1,i}$ are pairwise orthogonal. 
+    \item All nontrivial proper subrepresentations of $\tilde P_m^{(k)}$ are preprojective.
+  \end{enumerate}
+\end{lemma}
+
+We will always choose the subset $\{1,\ldots,k\}$ when using Lemma~\ref{le:preprojective lifts}.2 and thus we denote the cokernal simply by $\tilde P_m^{(k)}$.
+
+\begin{lemma}
+  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,i})$ has a cell decomposition, then $Gr^{\tilde Q}_\tbfe(\bigoplus\tilde P_{m-1,i_j})$ has a cell decomposition.
+\end{lemma}
+
+\begin{lemma}
+  \begin{enumerate}
+    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
+    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
+      \[\Ext(\bigoplus{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
+      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
+  \end{enumerate}
+\end{lemma}
+
+\begin{corollary}
+  observe when fibers are empty
+\end{corollary}
+
+\begin{proposition}
+  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}$.
+Then the following hold:
+  \begin{enumerate}
+    \item For $V\subsetneq \tilde P_m^{(k)}$ and $U\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$, we have $\psi^{-1}(U,V)=\AA^{\langle V,\bigoplus_{i=1}^k\tilde P_{m-1,i}/U\rangle}$.
+    \item If $V=\tilde P_m^{(k)}$ and the fiber is not empty, then $\psi^{-1}(U,V)$ is constant.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  (1) $V$ is preprojective but $\bigoplus_{i=1}^k\tilde P_{m-1,i}/U$ is not unless $U=0$
+
+  (2) \[0\longrightarrow[V,P/U]\longrightarrow[V,U]^1\longrightarrow[V,P]^1\longrightarrow[V,P/U]^1\longrightarrow0\]
+      and the middle map is surjective.
+\end{proof}
+
+\begin{theorem}
+  Every quiver Grassmannian of a preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
+\end{theorem}
+
+\begin{question}
+  cells of $Gr^{\tilde Q}_\tbfe(\tilde P_m)$ are in one-to-one correspondence with certain tuples of subgraphs for smaller $\tilde P_\ell^{i_1,\ldots,i_k}$
+\end{question}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
 

### 2017-03-24 Grassmannian_cells.tex
started writing

@@
 \newcommand{\tbfg}{{\tilde\bfg}}
+\newcommand{\C}{\mathbb{C}}
 
+\newcommand{\Rep}{\mathrm{Rep}}
+\newcommand{\Gr}{\mathrm{Gr}}
 \renewcommand{\AA}{\mathbb{A}}
@@
 \begin{abstract}
-  We prove that all quiver Grassmannians for preprojective and preinjective respesentations of a generalized Kronecker quiver admit a cell decomposition.  
+  We prove that all quiver Grassmannians for preprojective and preinjective representations of a generalized Kronecker quiver admit a cell decomposition.  
   We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
@@
 -statement of our results
+-something about torus actions and the universal cover
+-something about cell decompositions of quiver Grassmannians
 -acknowledgements?
@@
 \section{Torus Action on Quiver Grassmannians}
+\noindent Let $Q$ be an acylic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+Moreover, let $W_{Q}$ be the free (non-abelian) group generated by $Q_1$.
+We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
 \begin{definition}
-  universal cover $\tilde Q$
+The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
+
+We say that a representation $X\in \Rep(Q)$ can be lifted (to $\tilde Q$) if there exists a representation $\tilde X\in\Rep(\tilde Q)$ such that $F_Q\tilde X=X$ where $F_Q:\Rep(\tilde Q)\to\Rep(Q)$ is the natural functor.
 \end{definition}
-
 \begin{lemma}
-  how to lift exceptional representations of $Q$ to $\tilde Q$
+  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to a representation of $\tilde Q$.
 \end{lemma}
-
-\begin{lemma}
-  $d:\tilde Q_0\to\ZZ$ defines a torus action on $Gr^Q_\bfe(X)$ if $d(q,w\rho)-d(q,w)=c_\rho$ for all $w\in W_{\tilde Q_1}$
+\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
+Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the one of $Q$.
+Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,w)$ of $\tilde Q$.
+This leads the claim.
+The statement for preinjective representations follows in the same way.
+\end{proof}
+We choose a map $d:\tilde Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$.
+In any case, we can consider the decomposition $X_q=\bigoplus_{w\in W_Q} X_{(q,w)}$.
+We define a torus action on each $X_{(q,w)}$ via $t.x_{(q,w)}=t^{d(q,w)}x_{(q,w)}$ which can be extended linearly to each $X_q$.
+For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
+In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
+Actually, for this the action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$ and every $x\in X_i$.
+\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
+If $X\in\Rep(Q)$ can be lifted, $d:\tilde Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,w\alpha)-d(i,w)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
 \end{lemma}
+\begin{proof} Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$.
+Then the condition $X_{\alpha}(t.U_i)\in t.U_j$ translates into ...to be continued.
+\end{proof}
 
@@
 \section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
+\begin{thebibliography}{10}
+\bibitem{bgp}
+Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\end{thebibliography}
 

### 2017-03-31 Grassmannian_cells.tex
First pass on representation theory of (n)$: truncated projectives

--- 2017-03-24 Grassmannian_cells.tex
@@
 \usepackage[margin=1in]{geometry}
+
+\input xy
+\xyoption{all}
 
@@
 \renewcommand{\AA}{\mathbb{A}}
+\newcommand{\kk}{\Bbbk}
 \newcommand{\ZZ}{\mathbb{Z}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Representation Theory of $K(n)$}
+
+Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K(n)_0=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$.
+
+Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
+\begin{theorem}
+  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively.
+  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}P_{m+1}^{a_2}$ or $I_m^{a_1}I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
+\end{theorem}
+The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
+
+\begin{lemma}
+  For any $m\ge1$, we have $\dim\Hom(P_m,P_m)=1$, $\dim\Hom(P_m,P_{m+1})=n$, and $\dim\Hom(P_{m+1},P_m)=0$.  
+  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
+\end{lemma}
+Write $P_{m+1}^{\{f_1,\ldots,f_k\}}$ for the cokernel of the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$, i.e. we have a short exact sequence
+\begin{equation}
+\label{eq:truncated preprojectives}
+  0\longrightarrow P_m^k\stackrel{[f_1\ \cdots\ f_k]}{\longrightarrow} P_{m+1}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.
+\end{equation}
+\begin{lemma}
+  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the following hold:
+  \begin{enumerate}
+    \item $\Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})$ is naturally isomorphic to $\Hom(P_m,P_{m+1})/\kk f_1\oplus\cdots\oplus\kk f_k$;
+    \item $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ is naturally isomorphic to $\kk f_1\oplus\cdots\oplus\kk f_k$;
+    \item $\Hom(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)=0$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives the exact sequence
+  \[0\longrightarrow \Hom(P_m,P_m^k)\stackrel{[f_1\ \cdots\ f_k]\circ}{\longrightarrow} \Hom(P_m,P_{m+1})\longrightarrow \Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})\longrightarrow 0,\]
+  establishing (1).
+
+  To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
+  To get the isomorphism with $\kk f_1\oplus\cdots\oplus\kk f_k$, we work by induction on $k$.  
+  Indeed, $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
+  \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
+    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|{\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
+    0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
+     & 0 & 0 & & }\]
+  The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
+
+  Part (3) follows immediately from the observation that $\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=-k$.
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quiver Grassmannians of $\widetilde{K(n)}$}
-
-Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
-For $m\ge1$, let $P_m$ be the preprojective representation of $K(n)$ with dimension vector $(u_m,u_{m-1})$.
 

### 2017-04-01 Grassmannian_cells.tex
Explained right almost split sequences for truncated preprojectives.

@@
 \begin{lemma}
-  For any $m\ge1$, we have $\dim\Hom(P_m,P_m)=1$, $\dim\Hom(P_m,P_{m+1})=n$, and $\dim\Hom(P_{m+1},P_m)=0$.  
+  For any $m\ge1$, we have 
+  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0.\]  
   Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
@@
   To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
-  To get the isomorphism with $\kk f_1\oplus\cdots\oplus\kk f_k$, we work by induction on $k$.  
-  Indeed, $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
+  Observe that $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
   \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
@@
 
-  Part (3) follows immediately from the observation that $\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=-k$.
+  Part (3) follows immediately from (2) and the observation that 
+  \[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
+\end{proof}
+
+For any nonempty subset $I\subset[1,k]$, say with $|I|=\ell$, we get an exact sequence
+\[0\longrightarrow P_m^\ell\stackrel{[f_i]_{i\in I}}{\longrightarrow} P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.\]
+Each such sequence has the following almost-split property for subrepresentations of $P_{m+1}^{\{f_1,\ldots,f_k\}}$.
+\begin{lemma}
+  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, given any proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$, the upper pullback sequence
+  \[\xymatrix{0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r] & V^I\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V\ar[d]\ar[r] & 0 \\
+  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}} & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
+  splits for every $I\subset[1,k]$.
+\end{lemma}
+\begin{proof}
+  When $I=\emptyset$ there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
+
+  We proceed by induction on $k$.  For any nonzero $f\in\Hom(P_m,P_{m+1})$ the exact sequence
+  \[\xymatrix{0\ar[r] & P_m\ar[r]^f & P_{m+1}\ar[r] & P_{m+1}^{\{f\}}\ar[r] & 0}\]
+  is almost split, giving the claim in the case $k=1$.  For $k>1$ and a nontrivial subset $I\subset[1,k]$, we have the following commutative diagram
+  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
+  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_i\}_{i\in I}}\ar[d]\ar[r] & 0 \\
+  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
+  A proper subrepresentation $V\subset P_{m+1}^{\{f_1,\ldots,f_k\}}$ gives rise, via pullbacks, to the following commutative diagram
+  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
+  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\ar[d]\ar[r] & 0 \\
+  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & V^I\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
+  in which the middle vertical sequence and the middle horizontal sequence split by induction.  But then the lower horizontal sequence splits, establshing the claim for all $I\subset[1,k]$.
 \end{proof}

### 2017-04-01 Grassmannian_cells.tex
Lemma 2.1, Lemma 2.7, Proposition 2.1 changed
Added argument concerning irreducible morphism to Lemma 2.1
Added Lemma 2.7 which should describe the empty fibers (details have to
be checked)
Changed Proposition 2.1 (2) under consideration of 2.7

@@
 \usepackage[margin=1in]{geometry}
-
+\usepackage{extarrows}
 \input xy
@@
 \newcommand{\Hom}{\operatorname{Hom}}
+\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
 
@@
 \end{lemma}
+\begin{proof} Note that we have a Auslander-Reiten sequence
+\[0\longrightarrow P_{m-1}\longrightarrow P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0\]
+with irreducible homomorphisms $f_i$ which are also linear independent.
+Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}.
+If we pick $k<n$ linear independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective.
+Indeed otherwise, at least one of the homomorphisms were forced to factor through a representation $Z\neq P_{m}$.
+
  Write $P_{m+1}^{\{f_1,\ldots,f_k\}}$ for the cokernel of the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$, i.e. we have a short exact sequence
@@
 \end{equation}
+\end{proof}
 \begin{lemma}
@@
     \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
-      \[\Ext(\bigoplus{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
+      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
       where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
@@
 
-\begin{corollary}
-  observe when fibers are empty
-\end{corollary}
+\begin{lemma}\label{quotient}
+ Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
+If $U\subset P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
+\end{lemma}
+\begin{proof}
+First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$.
+As $U$ is preprojective with $U\subset \tilde P_m\subset \tilde P_{m+1}^{(k)}$, it follows that $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again).
+This yields $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$.
+Consider
+\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
+Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$.
+If $U=U_1\oplus\ldots\oplus U_r$ is a decomposition into indecomposable representations, we can write $\pi=(\pi_1,\ldots,\pi_r)$ and it suffices to show that $\pi_j\neq 0$ for at least one $j=1,\ldots,r$.
+Thus we can without loss of generality assume that $U$ is indecomposable (check again).
+This means that $U\cong \tilde P_{i}$ for some $i=1,\ldots,m$.
+Moreover, $\tilde P_{m+1}/U$ is indecomposable (details).
+
+If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$.
+Thus $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)\neq 0$ would imply that $\Ext(\tilde P_{m+1}^{(k-1)},U)=0$.
+But this contradicts the assumption and the claim follows.
+
+Thus assume that $\tilde P_{m+1}/U$ has self-extensions.
+Since $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})= 0$, from \cite[Lemma 4.1]{hr} we obtain that every homomorphism $\tilde P_{m+1}^{(k-1)}\to \tilde P_m/U$ is injective or surjective.
+By a dimension count it needs to be surjective (case $k=1$?).
+Such a homomorphism would yield $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})\twoheadrightarrow\Ext(\tilde P_m/U,\tilde P_m/U)\neq 0$ which contradicts the further observations.
+Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.
+
+\end{proof}
 
@@
     \item For $V\subsetneq \tilde P_m^{(k)}$ and $U\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$, we have $\psi^{-1}(U,V)=\AA^{\langle V,\bigoplus_{i=1}^k\tilde P_{m-1,i}/U\rangle}$.
-    \item If $V=\tilde P_m^{(k)}$ and the fiber is not empty, then $\psi^{-1}(U,V)$ is constant.
+    \item If $V=\tilde P_m^{(k)}$, the fibre $\psi^{-1}(U,V)$ is non-empty and of constant dimension if and only if $\Ext(\tilde P_m^{(k)},U)\neq 0$.
   \end{enumerate}
@@
 
-  (2) \[0\longrightarrow[V,P/U]\longrightarrow[V,U]^1\longrightarrow[V,P]^1\longrightarrow[V,P/U]^1\longrightarrow0\]
-      and the middle map is surjective.
+  (2) 
+If $\Ext(\tilde P_m^{(k)},U)= 0$, the fibre is empty because the sequence is non-split.
+If $\Ext(\tilde P_m^{(k)},U)\neq 0$, Lemma \ref{quotient} yields $\Ext(\tilde P_m^{(k)},\tilde P_{m-1}/U)=0$.
+In particular, the dimension is constant if it is not empty and
+$\Ext(\tilde P_{m+1}^{(k-1)},U)\xlongrightarrow{\pi}\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)$ is surjective. But this already means that the fibre is not empty.
 \end{proof}
@@
 \begin{thebibliography}{10}
+\bibitem{ass}
+Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
 \bibitem{bgp}
 Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
+
+\bibitem{sch} Schofield, A.: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
+
 \end{thebibliography}

### 2017-04-04 Grassmannian_cells.tex
Lemma 2.1, 2.7, Proposition 2.1
Added Lemma 3.4 which will provide the induction step for establishing cell decompositions, changed theorem numbering

@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{definition}{Definition}[theorem]
-\newtheorem{lemma}{Lemma}[theorem]
-\newtheorem{question}{Question}[theorem]
-\newtheorem{proposition}{Proposition}[theorem]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{question}[theorem]{Question}
+\newtheorem{proposition}[theorem]{Proposition}
 
@@
 \end{lemma}
-\begin{proof} Note that we have a Auslander-Reiten sequence
-\[0\longrightarrow P_{m-1}\longrightarrow P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0\]
-with irreducible homomorphisms $f_i$ which are also linear independent.
+\begin{proof} 
+  Note that we have an Auslander-Reiten sequence
+  \begin{equation}
+  \label{eq:AR sequence}
+    0\longrightarrow P_{m-1}\longrightarrow P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
+  \end{equation}
+  with irreducible homomorphisms $f_i$ which are also linearly independent. 
   Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
@@
   Indeed otherwise, at least one of the homomorphisms were forced to factor through a representation $Z\neq P_{m}$.
+\end{proof}
 
@@
 \end{equation}
-\end{proof}
+
 \begin{lemma}
@@
   \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
-    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|{\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
+    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|(.35){\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
     0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
@@
   \[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
+\end{proof}
+
+\begin{lemma}
+  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n^{th}$ factor.
+Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\cong P_m^{\{g\}}$.
+\end{lemma}
+\begin{proof}
+  We have the following commutative diagram
+  \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
+  0\ar[r]& P_m^{n-1}\ar[r]^{[f_1\ \cdots\ f_{n-1}]}& P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
+  Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
+  But this implies the kernels of the vertical morphisms coincide.  
+  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so the kernel is $P_{m-1}$.
+  It follows that there is a morphism $g:P_{m-1}\to P_m$ so that $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\cong P_m^{\{g\}}$.
 \end{proof}
@@
     \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
-    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
+    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
       \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
@@
 First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$.
-As $U$ is preprojective with $U\subset \tilde P_m\subset \tilde P_{m+1}^{(k)}$, it follows that $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again).
+Assume that $U$ is preprojective with $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again).
 This yields $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$.
@@
 Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.
+
+Case $\Hom(U,P)\neq 0$?
 

### 2017-04-06 Grassmannian_cells.tex
Added Lemma 2.7 and changed Lemma 2.8

@@
 \end{lemma}
-
+\begin{lemma}\label{AR}
+Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$
+There exists a short exact sequence 
+\[\ses{\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}}{\tilde P_m}{\tau\tilde P_{m+1}^{(k-1)}}\]
+where $\tau$ denotes the Auslander-Reiten translate.
+Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$.
+\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
+\end{lemma}
+\begin{proof}
+Idea: Check this for $m=1$ or $m=2$ and apply BGP-reflections.
+\end{proof}
 \begin{lemma}\label{quotient}
  Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
-If $U\subset P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
+If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
 \end{lemma}
 \begin{proof}
-First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$.
+Idea: Every $U\subset \tilde P_m$ gives rise to a diagram
+  \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
+  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
+
+	If $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$.
+Thus $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor.
+It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$ by Auslander-Reiten-theory and because
+$\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$.
+
+Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})=0$, it follows $\Ext(\tilde P_{m+1}^{(k-1)},(\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})/V)=0$.
+The first statement should be a consequence of Lemma \ref{AR}.
+This yields the claim.
+
+%First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$.
 Assume that $U$ is preprojective with $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again).
@@
 Consider
-\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
-Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$.
+%\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
+%Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$.
 If $U=U_1\oplus\ldots\oplus U_r$ is a decomposition into indecomposable representations, we can write $\pi=(\pi_1,\ldots,\pi_r)$ and it suffices to show that $\pi_j\neq 0$ for at least one $j=1,\ldots,r$.
@@
 Moreover, $\tilde P_{m+1}/U$ is indecomposable (details).
-
-If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$.
+%
+%If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$.
 Thus $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)\neq 0$ would imply that $\Ext(\tilde P_{m+1}^{(k-1)},U)=0$.
 But this contradicts the assumption and the claim follows.
-
-Thus assume that $\tilde P_{m+1}/U$ has self-extensions.
+%
+%Thus assume that $\tilde P_{m+1}/U$ has self-extensions.
 Since $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})= 0$, from \cite[Lemma 4.1]{hr} we obtain that every homomorphism $\tilde P_{m+1}^{(k-1)}\to \tilde P_m/U$ is injective or surjective.
@@
 Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.
-
-Case $\Hom(U,P)\neq 0$?
+%
+%Case $\Hom(U,P)\neq 0$?
 

### 2017-04-07 Grassmannian_cells.tex
Fixed (partially) the proof of Lemma 3.5

@@
 \begin{proof}
-  When $I=\emptyset$ there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
+  When $I=\emptyset$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
 
-  We proceed by induction on $k$.  For any nonzero $f\in\Hom(P_m,P_{m+1})$ the exact sequence
+  We proceed by simultaneous induction on $k$ and $\ell=|I|$.  For any nonzero $f\in\Hom(P_m,P_{m+1})$ the exact sequence
   \[\xymatrix{0\ar[r] & P_m\ar[r]^f & P_{m+1}\ar[r] & P_{m+1}^{\{f\}}\ar[r] & 0}\]
-  is almost split, giving the claim in the case $k=1$.  For $k>1$ and a nontrivial subset $I\subset[1,k]$, we have the following commutative diagram
+  is almost split, giving the claim in the case $k=\ell=1$.  For $k>1$ and a nontrivial proper subset $I\subsetneq[1,k]$, we have the following commutative diagram
   \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
@@
   0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & V^I\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  in which the middle vertical sequence and the middle horizontal sequence split by induction.  But then the lower horizontal sequence splits, establshing the claim for all $I\subset[1,k]$.
+  in which the middle vertical sequence and the middle horizontal sequence split by induction.  
+  But the images of $[f_i]_{i\in I}$ and $[f_j]_{j\in[1,k]\setminus I}$ intersect trivially inside $V^{[1,k]}$ and thus the lower horizontal sequence must split as well, establishing the claim for $I\subsetneq[1,k]$.
+
+  For $I=[1,k]$, we consider the commutative diagram
+  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_{m+1}\ar@{=}[r]\ar[d] & P_{m+1}\ar[d]\ar[r] & 0 \\
+  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & P_{m+1}\oplus P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_1\ \cdots\ f_{k-1}\}}\oplus P_{m+1}^{\{f_k\}}\ar[d]\ar[r] & 0 \\
+  0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d] & P_{m+1}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
+  A proper subrepresentation $V\subset P_{m+1}^{\{f_1,\ldots,f_k\}}$ then gives rise to the following commutative diagram
+  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & V^{[1,k]}\ar@{=}[r]\ar[d] & V^{[1,k]}\ar[d]\ar[r] & 0 \\
+  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & V^{[1,k]}\oplus V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\oplus V^I\ar[d]\ar[r] & 0 \\
+  0\ar[r]& P_m^k\ar[r]\ar[d] & V^{[1,k]}\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
+  in which the middle vertical sequence splits and the middle horizontal sequence is split by induction.  But then the lower horizontal sequence splits, establishing the claim for $I\subsetneq[1,k]$.
 \end{proof}
@@
   \begin{enumerate}
-    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$;
+    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
     \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
@@
     \item The lifts $\tilde P_{m-1,i}$ are pairwise orthogonal. 
-    \item All nontrivial proper subrepresentations of $\tilde P_m^{(k)}$ are preprojective.
+    \item All nontrivial proper subrepresentations of $\tilde P_m^{i_1,\ldots,i_k}$ are preprojective.
   \end{enumerate}
@@
 
-We will always choose the subset $\{1,\ldots,k\}$ when using Lemma~\ref{le:preprojective lifts}.2 and thus we denote the cokernal simply by $\tilde P_m^{(k)}$.
+We will always choose the subset $\{1,\ldots,k\}$ when using Lemma~\ref{le:preprojective lifts}.2 and thus we denote the cokernel simply by $\tilde P_m^{(k)}$.
 

### 2017-04-07 Grassmannian_cells.tex
Fixed the proof of Lemma 3.5

@@
   0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  A proper subrepresentation $V\subset P_{m+1}^{\{f_1,\ldots,f_k\}}$ gives rise, via pullbacks, to the following commutative diagram
+  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ gives rise, via pullbacks, to the following commutative diagram
   \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
@@
   0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d] & P_{m+1}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  A proper subrepresentation $V\subset P_{m+1}^{\{f_1,\ldots,f_k\}}$ then gives rise to the following commutative diagram
-  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & V^{[1,k]}\ar@{=}[r]\ar[d] & V^{[1,k]}\ar[d]\ar[r] & 0 \\
+  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ then gives rise to the following commutative diagram
+  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & V^{[1,k]}\ar@{=}[r]\ar[d]^{\Delta} & V^{[1,k]}\ar[d]\ar[r] & 0 \\
   0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & V^{[1,k]}\oplus V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\oplus V^I\ar[d]\ar[r] & 0 \\
   0\ar[r]& P_m^k\ar[r]\ar[d] & V^{[1,k]}\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  in which the middle vertical sequence splits and the middle horizontal sequence is split by induction.  But then the lower horizontal sequence splits, establishing the claim for $I\subsetneq[1,k]$.
+  in which the middle vertical sequence splits and the middle horizontal sequence is split by induction.  
+  But the image of $[f_1\ \cdots\ f_k]:P_m^{k-1}\oplus P_m\to V^{[1,k]}\oplus V^{[1,k]}$ and the diagonal $\Delta:V^{[1,k]}\to V^{[1,k]}\oplus V^{[1,k]}$ intersect trivially because $f_1,\ldots,f_k$ are linearly independent.
+  As above the lower horizontal sequence also splits, establishing the claim for $I=[1,k]$.
 \end{proof}

### 2017-04-16 Grassmannian_cells.tex
Thorsten's edits

@@
 Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K(n)_0=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$.
+By $S_1$ and $S_2$ we denote the BGP-reflection functor corresponding to the sink and source of $K(n)$ respectively \cite{bgp}.
+Note that the quiver $K(n)$ itself does not change when applying the reflection functors, but the vertices $1$ and $2$ are exchanged.
+Let $$\mathcal S:=\begin{cases}S_1\text{ if }1 \text{ is a source }\\S_2\text{ if }$2$ \text{ is a source }\end{cases}$$
 
@@
 \begin{theorem}
-  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively.
-  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}P_{m+1}^{a_2}$ or $I_m^{a_1}I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
+  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m=\mathcal S^{m-1} P_1$ and $I_m=\mathcal S^{-m+1} I_1$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively.
+Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
 \end{theorem}
@@
 \section{Quiver Grassmannians of $\widetilde{K(n)}$}
-
+\noindent 
 Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$.
+Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
+$w.(q,w')=(q,ww')$.
+Up to this action a lift $\tilde P_m$ of $P_m$ is unique.
 \begin{lemma}
@@
 \end{lemma}
+\begin{proof}
+Most of the things should directly follow from \cite{gab}, the fact that $F_Q$ is a covering functor and the considerations of the last section.
+\end{proof}
 
@@
 \begin{lemma}
-  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,i})$ has a cell decomposition, then $Gr^{\tilde Q}_\tbfe(\bigoplus\tilde P_{m-1,i_j})$ has a cell decomposition.
+  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,i})$ has a cell decomposition, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P_{m-1,i_j})$ has a cell decomposition.
 \end{lemma}
+\begin{proof}
+This follows by induction and by considering the Caldero-Chapoton map.
+Then we can use the fact that every subrepresentation $U$ of $\tilde P_{m-1}$ is preprojective whence every proper factor is preinjective $V$ which means that we have $\Ext(U,V)=0$.
+\end{proof}
 
@@
 \end{lemma}
+\begin{proof}
+The first statement follows by the last section.
+\end{proof}
 \begin{lemma}\label{AR}
-Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$
+Let $m\geq 3$. Consider the short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
 There exists a short exact sequence 
@@
 where $\tau$ denotes the Auslander-Reiten translate.
-Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$.
-\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
+Here the lifts of $P_{m-1}$ and $P_{m-2}$ have to be chosen appropriately.
+Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$.
+Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
+%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
 \end{lemma}
 \begin{proof}
-Idea: Check this for $m=1$ or $m=2$ and apply BGP-reflections.
+Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation).
+This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_1$.
+
+The last statement needs to be checked and should follow by construction.
+
 \end{proof}
@@
 \begin{proof}
-Idea: Every $U\subset \tilde P_m$ gives rise to a diagram
+Every $U\subset \tilde P_m$ gives rise to a commutative diagram
   \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
@@
 
-	If $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$.
-Thus $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor.
-It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$ by Auslander-Reiten-theory and because
-$\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$.
+We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext((\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=k$.
+Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.
+
+By Lemma \ref{AR}, if $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$. This means that $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k-1)}$. 
+It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$.
+Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k-1)}\to \tau\tilde P_{m+1}^{(k-1)}/W$ factors through the middle term $Z$ of the AR-sequence
+\[\ses{\tau\tilde P_{m+1}^{(k-1)}}{Z}{\tilde P_{m+1}^{(k-1)}}\]
+which means that the first map of the induced sequence
+\[\Hom(\tau\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W) \]
+is zero.
+As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$.
+Thus we obtain $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W)=0$
 
 Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})=0$, it follows $\Ext(\tilde P_{m+1}^{(k-1)},(\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})/V)=0$.
-The first statement should be a consequence of Lemma \ref{AR}.
 This yields the claim.
@@
 Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
 \bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
+\bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
 

### 2017-04-16 Grassmannian_cells.tex
Minor edits

@@
 Here the lifts of $P_{m-1}$ and $P_{m-2}$ have to be chosen appropriately.
-Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$.
+Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$.
 Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 
-We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext((\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=k$.
-Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.
+We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=\kk$.
+Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=\kk$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.
 
@@
 is zero.
-As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$.
+As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$.
 Thus we obtain $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W)=0$
@@
 \begin{proposition}
-  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}$.
+  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$.
 Then the following hold:

### 2017-04-25 Grassmannian_cells.tex
test
Proof of Lemma 4.1

@@
 \newcommand{\C}{\mathbb{C}}
+\newcommand{\ui}{\underline i}
+\newcommand{\uj}{\underline j}
+\newcommand\udim{{\underline{\dim}\, }}
 
@@
 \newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
+\newcommand{\Sc}[2]{\langle #1,#2\rangle}
 
@@
 Up to this action a lift $\tilde P_m$ of $P_m$ is unique.
+On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$.
+Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$.
+In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_k)$ with $j_i\leq n$ and $k\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k-1},u_{m-k})$.
+For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $k\leq n-1$, there exist exact sequences of the form
+\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]
+
+Using this notation, we obtain the following lemma:
 \begin{lemma}
   \label{le:preprojective lifts}
-  There exist lifts $\tilde P_{m-1,i}$ for $1\le i\le n$ of $P_{m-1}$ to $\widetilde{K(n)}$ so that:
   \begin{enumerate}
     \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
-    \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
-      \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item The lifts $\tilde P_{m-1,i}$ are pairwise orthogonal. 
-    \item All nontrivial proper subrepresentations of $\tilde P_m^{i_1,\ldots,i_k}$ are preprojective.
+   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
+   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
+    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal. 
+    \item All nontrivial proper subrepresentations of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
   \end{enumerate}
@@
 \begin{proof}
-Most of the things should directly follow from \cite{gab}, the fact that $F_Q$ is a covering functor and the considerations of the last section.
+The first statement should directly follow from \cite{gab} and the fact that $F_Q$ is a covering functor (precise reference).
+The second part follows for instance recursively by applying BGP-reflections.
+
+For the third part, we proceed by induction.
+Clearly $\tilde P_m$ has only preprojective subrepresentations.
+We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
+If $U\subsetneq P_m^{(i_1,\ldots,i_k)}$ were not preprojective, the embedding would not factor through $P_m^{(i_1,\ldots,i_{k-1})}$ by induction hypothesis.
+Thus we get a commutative diagram
+
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_k)}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
+because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k-1})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
+Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason.
+Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
+because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom does not split.
+But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
+
 \end{proof}
@@
 \begin{lemma}\label{quotient}
- Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
-If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
+ Consider the non-split short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
+If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ or the fiber $\Psi^{-1}(U,\tilde P_{m+1}^{(k-1)})$ is empty.
 \end{lemma}

### 2017-04-25 Grassmannian_cells.tex
Proof of Lemma 4.2

@@
 \end{proof}
-
-We will always choose the subset $\{1,\ldots,k\}$ when using Lemma~\ref{le:preprojective lifts}.2 and thus we denote the cokernel simply by $\tilde P_m^{(k)}$.
+If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$.
+The short exact sequence $\ses{\tilde P_{m-1,k}}{\tilde P_{m}^{(k-1)}}{\tilde P_{m}^{(k)}}$ induces a map between quiver Grassmannians
+$$\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m-1,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}),\,U\mapsto (U\cap \tilde P_{m-1,k},\pi(U))$$
+which is sometimes called Caldero-Chapoton map.
 
 \begin{lemma}
-  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,i})$ has a cell decomposition, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P_{m-1,i_j})$ has a cell decomposition.
+  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ has a cell decomposition into affine spaces, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j\geq 1$.
 \end{lemma}
-\begin{proof}
-This follows by induction and by considering the Caldero-Chapoton map.
-Then we can use the fact that every subrepresentation $U$ of $\tilde P_{m-1}$ is preprojective whence every proper factor is preinjective $V$ which means that we have $\Ext(U,V)=0$.
+\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}).$$
+
+Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
+But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
+Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
+In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
+Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
+By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this bundle down) and thus itself trivial as a vector bundle over an affine space.
 \end{proof}
@@
 Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\bibitem{cc}
+Caldero, P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
+Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
+
 \bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).

### 2017-04-25 Grassmannian_cells.tex
Proof of Lemma 4.4, started with improving 4.5

@@
 If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$.
-The short exact sequence $\ses{\tilde P_{m-1,k}}{\tilde P_{m}^{(k-1)}}{\tilde P_{m}^{(k)}}$ induces a map between quiver Grassmannians
-$$\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m-1,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}),\,U\mapsto (U\cap \tilde P_{m-1,k},\pi(U))$$
-which is sometimes called Caldero-Chapoton map.
 
@@
 \end{lemma}
-\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}).$$
+\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
+which is also sometimes called Caldero-Chapoton map.
 
@@
 
-\begin{lemma}
+\begin{lemma}\footnote{do we need this?}
   \begin{enumerate}
-    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
+    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
     \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
@@
 \begin{proof}
-The first statement follows by the last section.
+The first statement follows for instance by induction when applying BGP-reflections.
 \end{proof}
 \begin{lemma}\label{AR}
-Let $m\geq 3$. Consider the short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
-There exists a short exact sequence 
-\[\ses{\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}}{\tilde P_m}{\tau\tilde P_{m+1}^{(k-1)}}\]
-where $\tau$ denotes the Auslander-Reiten translate.
-Here the lifts of $P_{m-1}$ and $P_{m-2}$ have to be chosen appropriately.
-Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$.
-Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
-%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
+Let $m\geq 3$ and $n\geq k\geq 2$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
+\begin{enumerate}
+\item There exists a short exact sequence 
+\[\ses{\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}}{\tilde P_{m,k}}{\tau\tilde P_{m+1}^{(k)}}\]
+where $\tau$ denotes the Auslander-Reiten translate where
+$\tau\tilde P_{m+1}^{(k)}=\tilde P_{m-1}^{(k)}$. 
+\item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
+\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$\footnote{do we need this?}. 
+%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
+\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
 \end{lemma}
@@
 Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation).
-This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_1$.
+This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$.
+In this case, the first statement is straightforward (maybe a diagram?!).
 
-The last statement needs to be checked and should follow by construction.
+It is also straightforward to check that $\bigoplus_{j\neq k}\tilde P_{2,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{1,(k,k,j)}\in (\tilde P_{4}^{(k)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(k)},\tilde P_{3,k})=0$ which yields the second claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(k)},\underline{\quad})$.
 
 \end{proof}
+The short exact sequence $\ses{\tilde P_{m-1,k}}{\tilde P_{m}^{(k-1)}}{\tilde P_{m}^{(k)}}$ induces a map between quiver Grassmannians
+$$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m-1,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}).$$
+Let $P(m,k):=\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}$.
+
+By Lemma \ref{AR}, every $U\subset \tilde P_m$ gives rise to a commutative diagram
+
+ \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
+  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
+By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
+Using this notation, we obtain:
 \begin{lemma}\label{quotient}
- Consider the non-split short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
-If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ or the fiber $\Psi^{-1}(U,\tilde P_{m+1}^{(k-1)})$ is empty.
+ Consider the non-split short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. Let $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$. Then we have
+\begin{enumerate}
+\item The fibre $\Psi^{-1}(U,\tilde P_{m+1}^{(k-1)})$ is empty the case if and only if $U\in\Psi^{-1}_2(0,W)$ for some $W\neq 0$.
+\item If the fibre is not empty, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
+\end{enumerate} 
 \end{lemma}
 \begin{proof}
-Every $U\subset \tilde P_m$ gives rise to a commutative diagram
-  \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
-  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
 

### 2017-04-26 Grassmannian_cells.tex
Proof of Lemma 4.5, Proposition 4.6

@@
 \newcommand{\bfg}{\mathbf{g}}
+\newcommand{\bfh}{\mathbf{h}}
 \newcommand{\tbfe}{{\tilde\bfe}}
@@
 \newcommand{\tbfg}{{\tilde\bfg}}
+\newcommand{\tbfh}{{\tilde\bfh}}
 \newcommand{\C}{\mathbb{C}}
@@
 
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_k)}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & 0 \\
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
   0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
 where the vertical maps are injective. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
-because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k-1})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
+because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
 Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason.
@@
 
-\begin{lemma}
-  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ has a cell decomposition into affine spaces, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j\geq 1$.
+\begin{lemma}\label{directsums}
+  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ has a cell decomposition into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$.
 \end{lemma}
@@
 By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this bundle down) and thus itself trivial as a vector bundle over an affine space.
+
+In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
 \end{proof}
 
-\begin{lemma}\footnote{do we need this?}
+\begin{lemma}
   \begin{enumerate}
@@
       \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
-      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
+      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
   \end{enumerate}
@@
 \item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
-\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$\footnote{do we need this?}. 
+\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$.
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$.
-In this case, the first statement is straightforward (maybe a diagram?!).
+In this case, the first statement is straightforward as well as the third one (insert a diagram).
 
@@
 \end{proof}
-The short exact sequence $\ses{\tilde P_{m-1,k}}{\tilde P_{m}^{(k-1)}}{\tilde P_{m}^{(k)}}$ induces a map between quiver Grassmannians
-$$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m-1,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}).$$
+The short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$ induces a map between quiver Grassmannians
+$$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^{(k)}).$$
 Let $P(m,k):=\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}$.
 
-By Lemma \ref{AR}, every $U\subset \tilde P_m$ gives rise to a commutative diagram
+By Lemma \ref{AR}, every $U\subset \tilde P_{m,k}$ gives rise to a commutative diagram
 
- \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
+ \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_{m,k}\ar[r] & \tau\tilde P_{m+1}^{(k)}\ar[r] & 0 \\
   0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
@@
 \begin{lemma}\label{quotient}
- Consider the non-split short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. Let $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$. Then we have
+ Consider the non-split short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. Then we have:
 \begin{enumerate}
-\item The fibre $\Psi^{-1}(U,\tilde P_{m+1}^{(k-1)})$ is empty the case if and only if $U\in\Psi^{-1}_2(0,W)$ for some $W\neq 0$.
-\item If the fibre is not empty, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
+\item The fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is empty if and only if $U\in\Psi^{-1}_2(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,k)$.
+\item If the fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
 \end{enumerate} 
@@
 \begin{proof}
+If $W=0$, we get an exact sequence
+\[\ses{\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)}{\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)}{\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})}.\]
+Since $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we have $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
+This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ which means that the induced map
+\[\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\]
+is zero.
+This means that the induced exact sequence splits.
+On the other hand, every subrepresentation $U\subset \tilde P_{m,k}$ such that $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty comes with a commutative diagram
+ \[\xymatrix{0\ar[r] &\tilde P_{m,k}\ar[r] &  \tilde P_{m+1}^{(k-1)}\ar[r] & \tilde P_{m+1}^{(k)}\ar[r] & 0 \\
+  0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m+1}^{(k)}\ar[r]\ar[u]& 0}\]
+which means that the induced sequence in $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ does not split. This yields that the fibre is empty.
 
-We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=\kk$.
-Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=\kk$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.
+Thus assume that $U\in\Psi_2^{-1}(V,W)$ with $W\neq 0$.
+We first show that $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
+Clearly, $\tau\tilde P_{m+1}^{(k)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k)}$ if $W\neq 0$.
+It follows that we have $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$.
+Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k)}\to \tau\tilde P_{m+1}^{(k)}/W$ factors through the middle term $Z$ of the AR-sequence
+\[\ses{\tau\tilde P_{m+1}^{(k)}}{Z}{\tilde P_{m+1}^{(k)}}\]
+which means that the first map of the induced sequence
+\[\Hom(\tau\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)\to\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k)}/W) \]
+is zero.
+As $\tau\tilde P_{m+1}^{(k)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$ and $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$, i.e.
+Lemma \ref{AR}, yields $\Ext(Z,\tau\tilde P_{m+1}^{(k)})=0$ as the AR-sequence does not split.
+In conclusion, we obtain $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$.
 
-By Lemma \ref{AR}, if $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$. This means that $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k-1)}$. 
-It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$.
-Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k-1)}\to \tau\tilde P_{m+1}^{(k-1)}/W$ factors through the middle term $Z$ of the AR-sequence
-\[\ses{\tau\tilde P_{m+1}^{(k-1)}}{Z}{\tilde P_{m+1}^{(k-1)}}\]
-which means that the first map of the induced sequence
-\[\Hom(\tau\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W) \]
-is zero.
-As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$.
-Thus we obtain $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W)=0$
+By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$ and $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$.
+Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
+Together with $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$, this yields the claim.
 
-Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})=0$, it follows $\Ext(\tilde P_{m+1}^{(k-1)},(\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k})/V)=0$.
-This yields the claim.
+Thus it remains to show that $\Psi^{-1}_1(U,\tilde P_{m+1}^{(k)})$ is not empty if $W\neq 0$.
+Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_m/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
+\end{proof}
+Now we are able to state the following result concerning the fibers of $\Psi_1$:
+\begin{proposition}\label{fibers}\footnote{maybe formulate this in terms of $\Psi$ (see below)}
+ The following hold:
+  \begin{enumerate}
+    \item For $V\subsetneq \tilde P_{m+1}^{(k)}$ and $U\subseteq\tilde P_{m,k}$, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
+    \item If $V=\tilde P_{m+1}^{(k)}$, the fiber $\Psi_1^{-1}(U,V)$ is not empty if and only if $\Psi_2(U)\neq (U,0)$. In this case, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
+		\item Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
+But the representation $\tilde P_{m,k}/U$ is not as a quotient of a preprojective representation unless $U=0$.
+Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$.
+If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.
 
-%First observe that $\tilde P_m\in ~^\perp \tilde P_{m+1}^{(k-1)}$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$.
-Assume that $U$ is preprojective with $\Hom(U,\tilde P_{m+1}^{(k-1)})=0$ (check again).
-This yields $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$.
-Consider
-%\[0\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]\longrightarrow[\tilde P_{m+1}^{(k-1)},U]^1\xlongrightarrow{\pi}[\tilde P_{m+1}^{(k-1)},\tilde P_m]^1\longrightarrow[\tilde P_{m+1}^{(k-1)},\tilde P_m/U]^1\longrightarrow 0.\]
-%Since $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$, we have that $\pi$ is surjective if $\pi\neq 0$.
-If $U=U_1\oplus\ldots\oplus U_r$ is a decomposition into indecomposable representations, we can write $\pi=(\pi_1,\ldots,\pi_r)$ and it suffices to show that $\pi_j\neq 0$ for at least one $j=1,\ldots,r$.
-Thus we can without loss of generality assume that $U$ is indecomposable (check again).
-This means that $U\cong \tilde P_{i}$ for some $i=1,\ldots,m$.
-Moreover, $\tilde P_{m+1}/U$ is indecomposable (details).
-%
-%If $\tilde P_{m+1}/U$ is exceptional, $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})=0$ together with \cite[Theorem 4.1]{sch} yields that either $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$ or $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)=0$.
-Thus $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)\neq 0$ would imply that $\Ext(\tilde P_{m+1}^{(k-1)},U)=0$.
-But this contradicts the assumption and the claim follows.
-%
-%Thus assume that $\tilde P_{m+1}/U$ has self-extensions.
-Since $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})= 0$, from \cite[Lemma 4.1]{hr} we obtain that every homomorphism $\tilde P_{m+1}^{(k-1)}\to \tilde P_m/U$ is injective or surjective.
-By a dimension count it needs to be surjective (case $k=1$?).
-Such a homomorphism would yield $\Ext(\tilde P_m/U,\tilde P_{m+1}^{(k-1)})\twoheadrightarrow\Ext(\tilde P_m/U,\tilde P_m/U)\neq 0$ which contradicts the further observations.
-Thus $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, already yields $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ in this case.
-%
-%Case $\Hom(U,P)\neq 0$?
+The second statement follows directly from Lemma \ref{quotient}.
 
+For the third statement, we proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
+\[\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]
+
+By Lemma \ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition.
+The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
+In all other cases, the fiber dimension only depend on the dimension vector $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}.
+Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
+In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
 \end{proof}
 
-\begin{proposition}
-  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$.
-Then the following hold:
-  \begin{enumerate}
-    \item For $V\subsetneq \tilde P_m^{(k)}$ and $U\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$, we have $\psi^{-1}(U,V)=\AA^{\langle V,\bigoplus_{i=1}^k\tilde P_{m-1,i}/U\rangle}$.
-    \item If $V=\tilde P_m^{(k)}$, the fibre $\psi^{-1}(U,V)$ is non-empty and of constant dimension if and only if $\Ext(\tilde P_m^{(k)},U)\neq 0$.
-  \end{enumerate}
-\end{proposition}
-\begin{proof}
-  (1) $V$ is preprojective but $\bigoplus_{i=1}^k\tilde P_{m-1,i}/U$ is not unless $U=0$
-
-  (2) 
-If $\Ext(\tilde P_m^{(k)},U)= 0$, the fibre is empty because the sequence is non-split.
-If $\Ext(\tilde P_m^{(k)},U)\neq 0$, Lemma \ref{quotient} yields $\Ext(\tilde P_m^{(k)},\tilde P_{m-1}/U)=0$.
-In particular, the dimension is constant if it is not empty and
-$\Ext(\tilde P_{m+1}^{(k-1)},U)\xlongrightarrow{\pi}\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)$ is surjective. But this already means that the fibre is not empty.
-\end{proof}
+Note that we can also consider 
+$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
+But then one needs to adjust $\Psi_2$ as the factor $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
 
@@
 \end{theorem}
-
+\begin{proof}
+This follows by combining the results of Section 2 and Proposition \ref{fibers}.
+\end{proof}
 \begin{question}

### 2017-04-27 Grassmannian_cells.tex
Minor edits in Section 4

@@
 Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$.
-In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_k)$ with $j_i\leq n$ and $k\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k-1},u_{m-k})$.
-For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $k\leq n-1$, there exist exact sequences of the form
+In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
 \[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]
@@
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal. 
-    \item All nontrivial proper subrepresentations of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
+    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal;
+    \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
   \end{enumerate}
@@
   0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
 because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
@@
 \[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
-because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom does not split.
+because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom sequence does not split.
 But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
@@
 \end{proof}
-If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$.
+If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$ and $\tilde P_m^{(0)}=\tilde P_m$ respectively.
 
 \begin{lemma}\label{directsums}
-  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ has a cell decomposition into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$.
+  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
 \end{lemma}
-\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
+\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
 which is also sometimes called Caldero-Chapoton map.
@@
 Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
-By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this bundle down) and thus itself trivial as a vector bundle over an affine space.
+By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
 
@@
 \begin{lemma}\label{AR}
-Let $m\geq 3$ and $n\geq k\geq 2$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
+Let $m\geq 3$ and $n\geq k\geq 1$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
 \begin{enumerate}
@@
 \begin{proof}
-Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation).
+We have $\mathcal  S \tilde P_m=\tilde P_{m+1}$ (up to permutation).
 This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$.
@@
 \begin{lemma}\label{quotient}
- Consider the non-split short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. Then we have:
 \begin{enumerate}
@@
 \[\ses{\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)}{\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)}{\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})}.\]
-Since $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we have $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
-This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ which means that the induced map
+
+By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$, $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$.
+Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
+This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m,k})=\kk$ which means that the induced map
 \[\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\]
 is zero.
-This means that the induced exact sequence splits.
+Therefore, the induced exact sequence splits.
 On the other hand, every subrepresentation $U\subset \tilde P_{m,k}$ such that $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty comes with a commutative diagram
@@
 
-By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$ and $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$.
-Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
+Again we can apply Lemma \ref{AR} in order to see that $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$ as $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$. 
  Together with $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$, this yields the claim.
@@
 Thus it remains to show that $\Psi^{-1}_1(U,\tilde P_{m+1}^{(k)})$ is not empty if $W\neq 0$.
-Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_m/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
+Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
 \end{proof}
@@
     \item If $V=\tilde P_{m+1}^{(k)}$, the fiber $\Psi_1^{-1}(U,V)$ is not empty if and only if $\Psi_2(U)\neq (U,0)$. In this case, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
-		\item Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
+
   \end{enumerate}
@@
 \begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
-But the representation $\tilde P_{m,k}/U$ is not as a quotient of a preprojective representation unless $U=0$.
+But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
 Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$.
@@
 
-For the third statement, we proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
+\end{proof}
+\begin{theorem}\label{cellscover}
+Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
+\end{theorem}
+\begin{proof}
+We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
 \[\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]
@@
 The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vector $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}.
+In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}.
 Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
 In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
+
 \end{proof}
@@
 Note that we can also consider 
-$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
-But then one needs to adjust $\Psi_2$ as the factor $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
+$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
+But then one needs to adjust $\Psi_2$ because the factor of $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
 

### 2017-05-09 Grassmannian_cells.tex
Started compatible pairs section

@@
 \newcommand{\C}{\mathbb{C}}
+\newcommand{\cC}{\mathcal{C}}
 \newcommand{\ui}{\underline i}
@@
 \section{Introduction}
--something about cluster algebras
+A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion.
+Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
+
 -something about categorification and quiver Grassmannians
@@
 \section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
+For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
+More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
+It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.  
+Identify the edges of $D_m$ with the poset $E_m=\{1,\ldots,u_m+u_{m-1}\}$ where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
+Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the smallest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
+
+Let $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
+\begin{definition}
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called compatible if: 
+  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
+  \[e\ne v\qquad\text{and}\qquad |he\cap S_V|=n|he\cap S_H|\]
+  or
+  \[e\ne h\qquad\text{and}\qquad |ev\cap S_H|=n|ev\cap S_V|.\]
+  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
+\end{definition}
+
+The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{lee-li-zelevinsky} and the categorification of these variables using representations of $K(n)$ \cite{cc,caldero-keller}.
+\begin{theorem}\cite{lee-li-zelevinsky}
+  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
+\end{theorem}
+
+Our goal is to show that the compatible pairs provide a natural labelling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+
 \begin{thebibliography}{10}
@@
 Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+\bibitem{ck}
+  P. Caldero, B. Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
 \bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
@@
 \bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
+\bibitem{llz} K. Lee, L. Li, A. Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
 \bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).

### 2017-05-09 Grassmannian_cells.tex
Started editing Section 2
This is just to save my changes and to avoid conflicts...

--- 2017-04-27 Grassmannian_cells.tex
@@
 \end{lemma}
-\begin{proof} Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$.
-Then the condition $X_{\alpha}(t.U_i)\in t.U_j$ translates into ...to be continued.
+\begin{proof} Let $U\in \Gr_\bfe(X)$.
+Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$.
+Let $u_{(i,w)}\in U_{(i,w)}$ and $\alpha:i\to j\in Q_1$.
+Then we have $X_\alpha(u_{(i,w)})\in U_{(j,w\alpha)}$ because $X$ can be lifted to the universal cover.
+Then it follows
+\[X_\alpha(t.u_{(i,w)})=X_\alpha(t^{d(q,w)}u_{(i,w)})=t^{d(q,w)}X_\alpha(u_{(i,w)})=t^{d(q,w)}u_{(j,w\alpha)}=t^{-c_\alpha}t.u_{(j,w\alpha)}\]
+for some $u_{(j,w\alpha)}\in U_{(j,w\alpha)}$.
+Now we have \[\bigoplus_{w\in W_Q} t.U_{(j,w)}=\bigoplus_{w\in W_Q}t^{c(j,w)}t.U_{(j,w)}\]
+for every $t\in\C^\ast$ if $c(j,w)$ is constant. This yields  
+\[t.U_j=\bigoplus_{w\in W_Q} t.U_{(j,w)}=\bigoplus_{w\in W_Q}t^{-c_\alpha}t.U_{(j,w)}\]
+for every $t\in \C^\ast$.
 \end{proof}
 
-\begin{lemma}
-  There exists $d:\tilde Q_0\to\ZZ$ such that $d(q,w)\ne d(q',w')$ for all $q,q',w,w'$ with $\dim X_{q,w}\ne0$ and $\dim X_{q',w'}\ne0$.
+\begin{lemma} Let $X$ be an indecomposable representation of $\tilde Q$.
+There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,w)\ne d(j,w')$ if $i\neq j$ or $w\neq w'$ and such that $d(j,w')-d(i,w)=c_\alpha$ if and only if $w'=w\alpha$ and $(i,w),\,(j,w\alpha)\in \mathrm{supp}(X)$.
 \end{lemma}
+\begin{proof}
+Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
+In order to prove the statement, we assume that $d(q,1)=0$ and that $(q,1)\in \mathrm{supp}(X)$ and, moreover, fix the numbers $c_\alpha$ in such a way that the two conditions are satisfied.
+To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$.
+Let $|Q_1|=n$.
+Set $c_{\alpha_1}=1$ and inductively
+\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
+Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:W_Q\to A_Q$ is the group homomorphism induced by $f(\alpha)=\alpha$ and $f(\alpha^{-1})=-\alpha$ and $g:A_Q\to \ZZ$ the one defined by $g(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,w)=(g\circ f)(w)$ where $q$ is uniquely determined by $w$ on every connected component.
+In particular, we have
+\[d(q,w)=\sum_{i=1}^nd_ic_{\alpha_i}\]
+where $d_i$ counts the number of appearances of the arrow $\alpha_i$ in $w$ taking orientations into account. 
+First note that we obviously have $d(j,w\alpha)-d(i,w)=c_\alpha$. Now assume that $d(i,w)=d(j,w')$ which means that $\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}$
+which implies
+\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
+Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
+This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
+An analogous proof applies to show that $d(j,w')-d(i,w)\neq c_\alpha$ if $w'\neq w\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
 
+\end{proof}
 \begin{theorem}

### 2017-05-10 Grassmannian_cells.tex
Edited Section 2
Try to finish it next week, need to proofread it before

--- 2017-04-27 Grassmannian_cells.tex
@@
 \section{Torus Action on Quiver Grassmannians}
-\noindent Let $Q$ be an acylic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-Moreover, let $W_{Q}$ be the free (non-abelian) group generated by $Q_1$.
+\noindent Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
 We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
+Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
 \begin{definition}
+The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
+
 The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
 
-We say that a representation $X\in \Rep(Q)$ can be lifted (to $\tilde Q$) if there exists a representation $\tilde X\in\Rep(\tilde Q)$ such that $F_Q\tilde X=X$ where $F_Q:\Rep(\tilde Q)\to\Rep(Q)$ is the natural functor.
+We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
+$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
+$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
 \end{definition}
+Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+Moreover, note that for every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
+The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+Moreover, the group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp.
+dimension vectors) are equivalent in this case.
+The analogous observation can also be made for $\tilde Q$.
+
 \begin{lemma}
-  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to a representation of $\tilde Q$.
+  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
 \end{lemma}
 \begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
-Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the one of $Q$.
-Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,w)$ of $\tilde Q$.
+Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
+Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
+$(q,w)$ of $\tilde Q$).
 This leads the claim.
@@
 \end{proof}
-We choose a map $d:\tilde Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$.
-In any case, we can consider the decomposition $X_q=\bigoplus_{w\in W_Q} X_{(q,w)}$.
-We define a torus action on each $X_{(q,w)}$ via $t.x_{(q,w)}=t^{d(q,w)}x_{(q,w)}$ which can be extended linearly to each $X_q$.
+
+We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
+We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
+We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
 For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
@@
 \begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\Rep(Q)$ can be lifted, $d:\tilde Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,w\alpha)-d(i,w)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
+If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
 \end{lemma}
-\begin{proof} Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$.
-Then the condition $X_{\alpha}(t.U_i)\in t.U_j$ translates into ...to be continued.
+\begin{proof} Let $U\in \Gr_\bfe(X)$.
+Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
+Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
+Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
+Then it follows
+\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
+for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
+Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
+for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
+\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
+for every $t\in \C^\ast$.
 \end{proof}
 
-\begin{lemma}
-  There exists $d:\tilde Q_0\to\ZZ$ such that $d(q,w)\ne d(q',w')$ for all $q,q',w,w'$ with $\dim X_{q,w}\ne0$ and $\dim X_{q',w'}\ne0$.
+\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
+There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
 \end{lemma}
+\begin{proof}
+Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
+In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
+We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
+To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
+Set $c_{\alpha_1}=1$ and inductively
+\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
+Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
+In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
+\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
 
-\begin{theorem}
-  $Gr^Q_\bfe(X)^T\cong\bigsqcup_{\tilde\bfe of type \bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$
+First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
+Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
+which implies
+\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
+Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
+This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
+An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
+
+\end{proof}
+In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
+\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
+Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
+ a torus action on $Gr_\bfe^Q(X)$ such that
+  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
 \end{theorem}
-
+\begin{proof}
+\end{proof}
+The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
+to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
+Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
+Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
+Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
+If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
+We obtain:
+\begin{corollary}
+Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
+  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
+\end{corollary}
 \begin{corollary}
@@
 \bibitem{sch} Schofield, A.: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
-
+\bibitem{wei} Weist, T.: Localization in quiver moduli spaces.
 \end{thebibliography}

### 2017-06-05 Grassmannian_cells.tex
Added Theorem 2.1, Lemma 2.2 and proof of 2.7

@@
 \newcommand{\bfg}{\mathbf{g}}
+\newcommand{\bfi}{\mathbf{i}}
 \newcommand{\bfh}{\mathbf{h}}
@@
 \newcommand{\Sc}[2]{\langle #1,#2\rangle}
-
+\setcounter{MaxMatrixCols}{20}
 \title{Cell Decomposition of Rank 2 Quiver Grassmannians}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Torus Action on Quiver Grassmannians}
-\noindent Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+\section{Torus Actions on Quiver Grassmannians}
+\noindent The aim of this section is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
+More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
+For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
+\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
+
+Then we have the following statement, \cite[Section 4]{bb}:
+\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
+Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
+Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
+the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
+
+In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
+\end{theorem}
+
+Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
+We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
+Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
+Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
+there exist number $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
+\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
+Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
+Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
+This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
+We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
+there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
+where the unit vectors are in the columns $i_1,\ldots,i_d$.
+All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$ where $v_w\in X_j$, i.e.
+we have
+\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
+Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+\begin{lemma}\label{usualGrass}
+Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
+Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
+\end{lemma}
+\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
+\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
+where $j_0=0$.
+
+Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
+Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
+As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
+This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
+As the colums are linear independent, this already shows the claim.
+\end{proof}
+The next step is to generalize this to quiver Grassmannians.
+Now let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
 We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
@@
 In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
+
 \begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
@@
 \begin{proof}
+A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
+$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
+Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
+A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
+\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
+Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
 \end{proof}
@@
 \end{corollary}
-\begin{corollary}
-  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
-  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
-\end{corollary}
+%\begin{corollary}
+%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
+%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
+%\end{corollary}
 
 \begin{question}
-  What are the ranks of these bundles?  Poincar\'e polynomials?
+  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
 \end{question}
@@
 
-Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K(n)_0=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$.
+\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K(n)_0=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$.
 By $S_1$ and $S_2$ we denote the BGP-reflection functor corresponding to the sink and source of $K(n)$ respectively \cite{bgp}.
@@
 Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
+\bibitem{bb} Bialynicki-Birula, A.: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
 \bibitem{bgp}
@@
 Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+\bibitem{cr}
+Caldero, P., Reineke, M.: On the quiver Grassmannian in the acyclic case.
+Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
 \bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
@@
 \bibitem{sch} Schofield, A.: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
-\bibitem{wei} Weist, T.: Localization in quiver moduli spaces.
+	\bibitem{wei} Weist, T.: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
 \end{thebibliography}

### 2017-06-05 Grassmannian_cells.tex

@@
 Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+\bibitem{ck}
+  P. Caldero, B. Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
 \bibitem{cr}

### 2017-06-06 Grassmannian_cells.tex
Inserted section 2

--- 2017-06-05 Grassmannian_cells.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Torus Actions on Quiver Grassmannians}
-\noindent The aim of this section is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+\section{Terminology and Preliminary results}
+\subsection{Covering theory}
+Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
+Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
+\begin{definition}
+The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
+
+The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
+
+We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
+$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
+$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
+\end{definition}
+Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
+The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp.
+dimension vectors) are equivalent in this case.
+The analogous observation can also be made for $\tilde Q$.
+
+\begin{lemma}
+  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
+\end{lemma}
+\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
+Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
+Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
+$(q,w)$ of $\tilde Q$).
+This leads the claim.
+The statement for preinjective representations follows in the same way.
+\end{proof}
+
+\subsection{Bialynicki-Birula decomposition}
+The aim of this section is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
 If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
@@
 \end{theorem}
+
+\section{Torus Actions on Quiver Grassmannians}
+\noindent
 
@@
 The next step is to generalize this to quiver Grassmannians.
-Now let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
-Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
-\begin{definition}
-The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
 
-The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
-
-We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
-$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
-$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
-$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
-\end{definition}
-Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
-Moreover, note that for every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
-The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
-We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-Moreover, the group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp.
-dimension vectors) are equivalent in this case.
-The analogous observation can also be made for $\tilde Q$.
-
-\begin{lemma}
-  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
-\end{lemma}
-\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
-Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
-Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
-$(q,w)$ of $\tilde Q$).
-This leads the claim.
-The statement for preinjective representations follows in the same way.
-\end{proof}
-
+Let $Q$ be an acyclic quiver.
 We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
@@
 In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
-Actually, for this the action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$ and every $x\in X_i$.
+Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
 \begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
+If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
 \end{lemma}

### 2017-06-06 Grassmannian_cells.tex
minor changes

@@
 \section{Terminology and Preliminary results}
-\subsection{Covering theory}
+\subsection{Covering theory}\footnote{more and more precise definitions}
+For an introduction to covering theory we refer to \cite{gab}.
 Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
@@
 \end{definition}
+Note that in our definition every covering quiver has infinitely many connected components.
+But every connected component is a covering in the sense of \cite{gab}.
+As indecomposable representations live on one component this makes no difference.
 Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
@@
 The analogous observation can also be made for $\tilde Q$.
+If $M$ is a representation of $\hat Q$ (resp.
+$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
+$w\in W_Q$) by $M_\chi$ (resp.
+$M_w$).
 
@@
 \end{proof}
-
+As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
+\begin{theorem}\label{covering}
+The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
+\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
+The analogous statement is true when replacing $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
+\end{theorem}
 \subsection{Bialynicki-Birula decomposition}
@@
   For any $m\ge1$, we have 
-  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0.\]  
+  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
   Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
@@
      & 0 & 0 & & }\]
-  The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
+  The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which can be naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
 
-  Part (3) follows immediately from (2) and the observation that 
-  \[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
+  Part (3) follows immediately from $\Hom(P_{m+1},P_m)=0$.
+	%(2) and the observation that 
+  %\[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
 \end{proof}
@@
 \begin{proof}
-The first statement should directly follow from \cite{gab} and the fact that $F_Q$ is a covering functor (precise reference).
-The second part follows for instance recursively by applying BGP-reflections.
+The first statement follows from Theorem \ref{covering}. The second part follows for instance recursively by applying BGP-reflections.
 

### 2017-07-24 Grassmannian_cells.tex
Section 4 edits.

@@
 \documentclass{amsart}
-\usepackage{amsmath,amssymb,latexsym}
+\usepackage{amsmath,amssymb,latexsym,color}
+\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
 \usepackage[margin=1in]{geometry}
@@
 \newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{remark}[theorem]{Remark}
 
@@
 \newcommand{\Rep}{\mathrm{Rep}}
+\newcommand{\rep}{\operatorname{rep}}
 \newcommand{\Gr}{\mathrm{Gr}}
@@
 \section{Introduction}
-A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion.
+A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion \cite{fomin-zelevinsky}.
 Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
+These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}.
 
@@
 
-\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K(n)_0=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$.
-By $S_1$ and $S_2$ we denote the BGP-reflection functor corresponding to the sink and source of $K(n)$ respectively \cite{bgp}.
-Note that the quiver $K(n)$ itself does not change when applying the reflection functors, but the vertices $1$ and $2$ are exchanged.
-Let $$\mathcal S:=\begin{cases}S_1\text{ if }1 \text{ is a source }\\S_2\text{ if }$2$ \text{ is a source }\end{cases}$$
+\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
+Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.%, but the vertices $1$ and $2$ are exchanged.
+%Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$
 
@@
 \begin{theorem}
-  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m=\mathcal S^{m-1} P_1$ and $I_m=\mathcal S^{-m+1} I_1$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively.
+  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
   Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
+\begin{remark}
+  These representations satisfy the following recursions using the reflection functors:
+  \[P_1=S_1,\quad P_m=\Sigma_1 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
+  for $m\ge2$.
+\end{remark}
 
@@
      & 0 & 0 & & }\]
+  where $\hat f_k$ above indicates that the function $f_k$ has been omitted.
   The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which can be naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
@@
   \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
-  0\ar[r]& P_m^{n-1}\ar[r]^{[f_1\ \cdots\ f_{n-1}]}& P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
+  0\ar[r]& P_m^{n-1}\ \ \ \ar[r]^{[f_1\ \cdots\ f_{n-1}]}&\ \ \ P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
   Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
@@
   The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so the kernel is $P_{m-1}$.
-  It follows that there is a morphism $g:P_{m-1}\to P_m$ so that $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\cong P_m^{\{g\}}$.
+  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}\cong P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
 \end{proof}

### 2017-07-25 Grassmannian_cells.tex
Added definitions of piecewise compatibility to section 6

@@
 It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.
-Identify the edges of $D_m$ with the poset $E_m=\{1,\ldots,u_m+u_{m-1}\}$ where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
-Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the smallest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
 
-Let $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
+The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
+In what follows we assume $n\ge2$.
+\begin{theorem}
+  \cite[Corollary 2.4]{rupel}
+  \label{th:dyck path recursion}
+  For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
+  \begin{enumerate}
+    \item $D_1$ consists of a single horizontal edge;
+    \item $D_2$ consists of $n$ consecutive horizontal edges followed by a vertical edge;
+    \item $D_m$, $m\ge3$, consists of $n-1$ copies of $D_{m-1}$ followed by a copy of $D_{m-1}$ with its first $D_{m-2}$ removed.
+  \end{enumerate}
+\end{theorem}
+
+For $m\ge2$ and $1\le r\le n-1$, write $D_m^{(r)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $r$ copies of $D_{m-1}$.
+Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
+For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
+For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$  even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
+
+We identify the edges of $D_m$ with the ordered set $E_m=\{1,\ldots,u_m+u_{m-1}\}$, where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
+Let $E_m=H_m\sqcup V_m$, where $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
+Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{r=1}^n E_{m-1,r}$, where $E_{m-1,r}$ denotes the edges of $D_{m-1,r}$.
+The set $E_{m-1,r}$ is naturally partitioned into its subsets $H_{m-1,r}$ and $V_{m-1,r}$ of horizontal and vertical edges.
+
+Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
 \begin{definition}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called compatible if: 
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
   for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
-  \[e\ne v\qquad\text{and}\qquad |he\cap S_V|=n|he\cap S_H|\]
+  \begin{equation}
+    \label{eq:hgc}
+    e\ne v\qquad\text{and}\qquad |he\cap S_V|=n|he\cap S_H|
+  \end{equation}
   or
-  \[e\ne h\qquad\text{and}\qquad |ev\cap S_H|=n|ev\cap S_V|.\]
+  \begin{equation}
+    \label{eq:vgc}
+    e\ne h\qquad\text{and}\qquad |ev\cap S_H|=n|ev\cap S_V|.
+  \end{equation}
   Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
+\end{definition}
+\begin{remark}
+  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(r)}$, $1\le r\le n-1$.  Write $\cC_m^{(r)}$ for the set of all compatible pairs in $D_m^{(r)}$.
+\end{remark}
+
+The recursive structure of the maximal Dyck paths from Theorem~\ref{th:dyck path recursion} gives rise to a recursive characterization of compatible pairs.
+\begin{definition}
+  \cite[Definition 3.11]{rupel}
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in(S_H\cap H_{m-1,r})\times(S_V\cap V_{m-1,r})$ $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$ for some $1\le r\le n-1$.
 \end{definition}
@@
 
+\bibitem{rupel} Rupel, D.: Rank 2 Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
+
 \bibitem{sch} Schofield, A.: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).

### 2017-08-12 Grassmannian_cells.tex
Added results relating to piecewise compatibility.  Corollary 6.10 gives the combinatorial description of the 'empty fibers'.

@@
     \label{eq:AR sequence}
-    0\longrightarrow P_{m-1}\longrightarrow P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
+    0\longrightarrow P_{m-1}\stackrel{\iota}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
   \end{equation}
@@
   Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
-  If we pick $k<n$ linear independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
-  Indeed otherwise, at least one of the homomorphisms were forced to factor through a representation $Z\neq P_{m}$.
+  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
+  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
 \end{proof}
@@
      & 0 & 0 & & }\]
-  where $\hat f_k$ above indicates that the function $f_k$ has been omitted.
-  The bottom row of this diagram is the extension in $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which can be naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
+  where $\hat f_i$ above indicates that the function $f_i$ has been omitted.
+  The bottom row of this diagram is the extension from $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which is naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
 
@@
 \begin{lemma}
-  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n^{th}$ factor.
-Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\cong P_m^{\{g\}}$.
+  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion $\iota:P_{m-1}\hookrightarrow P_m^n$ from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n$-th factor.
+Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}=P_m^{\{g\}}$.
 \end{lemma}
@@
   But this implies the kernels of the vertical morphisms coincide.
-  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so the kernel is $P_{m-1}$.
-  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}\cong P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
+
+  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so its kernel is $P_{m-1}$.
+  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}=P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
 \end{proof}
@@
 \begin{proof}
-  When $I=\emptyset$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
+  When $I=\varnothing$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
 
@@
 
-For $m\ge2$ and $1\le r\le n-1$, write $D_m^{(r)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $r$ copies of $D_{m-1}$.
+We obtain the following as an immediate consequence.
+\begin{corollary}
+  \label{cor:short hooks}
+  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
+\end{corollary}
+\begin{proof}
+  We work by induction on $m\ge2$.
+  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
+  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
+\end{proof}
+
+For $m\ge2$ and $1\le k\le n-1$, write $D_m^{(k)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $k$ copies of $D_{m-1}$.
+Extending this notation we also set $D_m^{(0)}:=D_m$.
+\begin{remark}
   Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
+\end{remark}
 For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
 For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
+For $m\ge2$ and $1\le k\le n-1$, the maximal Dyck paths $D_{m-1,r}$, $k+1\le r\le n$, naturally identify with subpaths of $D_m^{(k)}$.
 
@@
 \begin{definition}
+  \label{def:compatibility}
   A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
@@
     \label{eq:hgc}
-    e\ne v\qquad\text{and}\qquad |he\cap S_V|=n|he\cap S_H|
+    e\ne v\qquad\text{and}\qquad |he\cap V_m|=n|he\cap S_H|
   \end{equation}
@@
     \label{eq:vgc}
-    e\ne h\qquad\text{and}\qquad |ev\cap S_H|=n|ev\cap S_V|.
+    e\ne h\qquad\text{and}\qquad |ev\cap H_m|=n|ev\cap S_V|.
   \end{equation}
@@
 \begin{remark}
-  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(r)}$, $1\le r\le n-1$.  Write $\cC_m^{(r)}$ for the set of all compatible pairs in $D_m^{(r)}$.
+  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.  Write $\cC_m^{(k)}$ for the set of all compatible pairs in $D_m^{(k)}$.
 \end{remark}
@@
   \cite[Definition 3.11]{rupel}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in(S_H\cap H_{m-1,r})\times(S_V\cap V_{m-1,r})$ $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$ for some $1\le r\le n-1$.
+  \label{def:piecewise compatibility}
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$.
 \end{definition}
+\begin{remark}
+  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.
+\end{remark}
+
+To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
+For a horizontal edge $h\in H_m$ and a subset $S_H\subset H_m$, write $D(h;S_H)=he$ for the shortest subpath of $D_m$ for which $|he\cap V_m|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_{m-1}}$.
+The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
+Similarly, for a vertical edge $v\in V_m$ and a subset $S_V\subset V_m$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_m$ for which $|ev\cap H_m|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
+\begin{definition}
+  \cite[Definition 3.17]{rupel}
+  A horizontal edge $h_i\in H_m$, $m\ge3$, is called \emph{blocking} for a subset $S_H\subset H_m$ if $D(h_i;S_H)=h_iv_{u_{m-1}}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal with this property.
+
+  Suppose $S_H\subset H_m$ admits a blocking edge $h_i\in H_m$.
+  Then $S_H$ is \emph{left-justified at $h_i$} if there exists $k\ge i$ so that $S_H=\{h_i,h_{i+1},\ldots,h_k\}$.
+  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_{m-1}}\cap V_m|=n|h_iv_{u_{m-1}}\cap S_H|$.
+
+  A subset $S_V\subset V_m$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_{m-1}}$ so that $S_V\cap h_iv_{u_{m-1}}=\{v_s,v_{s-1},\ldots,v_{u_{m-1}}\}$.
+  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_{m-1}};S_V)=h_iv_{u_{m-1}}$ with $|h_iv_{u_{m-1}}\cap H_m|=n|h_iv_{u_{m-1}}\cap S_V|$.
+\end{definition}
+
+\begin{theorem}
+  \cite[Theorem 3.20 and Corollary 3.22]{rupel}
+  \label{th:blocking edge conditions}
+  For $m\ge3$, suppose $S_H\subset H_m$ and $S_V\subset V_m$ are piecewise compatible. 
+  Then the following hold:
+  \begin{enumerate}
+    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_m$.
+    \item Suppose $S_H$ admits a blocking edge $h_i\in H_m$ and $(S_H,S_V)$ is not compatible.
+      Then $S_H$ is left-justified at $h_i$ and $S_V$ is strongly right-justified with respect to $h_i$.
+      In addition the following hold:
+      \begin{enumerate}
+        \item If $m=3$, then $S_H\cap h_iv_{u_{m-1}}=\{h_i\}$.
+        \item If $m\ge4$, then $S_H$ is strongly left-justified at $h_i$.
+        \item If $m\ge5$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_m$.
+      \end{enumerate}
+  \end{enumerate}
+\end{theorem}
+
+\begin{corollary}
+  For $m\ge4$ and $0\le k\le n-1$, consider $S_H\subset H_m^{(k)}$ and $S_V\subset V_m^{(k)}$ so that $(S_H,S_V)$ is piecewise compatible.
+  Assume $\big(S_H^{(k+1)},S_V^{(k+1)}\big)\in\cC_m^{(k+1)}$.
+  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $V_m^{(k+1)}\subset S_V$.
+\end{corollary}
+\begin{proof}
+  We begin with the reverse implication.
+  First note that there are $(n-k)u_{m-1}-u_{m-2}$ horizontal edges and $(n-k)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{(k)}$. 
+  It follows that $V_{m-2}^{(k+1)}\sqcup V_m^{(k+1)}$ contains $n(n-k)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{(k+1)}\sqcup H_m^{(k+1)}$ contains $n(n-k)u_{m-2}-nu_{m-3}$ horizontal edges.
+
+  Assuming $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $S_V^{(k+1)}=V_m^{(k+1)}$, we have $S_V\cap V_{m-2}^{(k+1)}=\varnothing$ and $S_H\cap H_m^{(k+1)}=\varnothing$ by piecewise compatibility.
+  Let $h\in H_m^{(k)}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{(k+1)}$.
+  Then, since there are $(n-k)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{(k+1)}$, the local shadow path $D(h;S_H)$ contains $n\big((n-k)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
+  Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
+  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_{m-1}}$ and so $(S_H,S_V)$ is not compatible.
+
+  For the forward implication, we work by induction on $m\ge4$.
+  Consider a pair $(S_H,S_V)$ for $D_4^{(k)}$ as above which is not compatible.
+  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{(k)}$ for the blocking edge of $S_H$.
+  Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
+  Since $(S_H^{(k+1)},S_V^{(k+1)})$ is compatible, we must have $h\in H_{3,k}$.
+  But observe that $|V_m^{(k)}|=(n-k)n-1$ and so the divisibility condition above implies $h\in H_{3,k}^{(n-1)}$.
+  But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
+  Identifying $H_{3,k}^{(n-1)}$ with $H_2^{(1)}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{(k+1)}\subset H_2^{(1)}$.
+  Then by piecewise compatibility, the vertical edge of $H_2^{(1)}$ cannot be an element of $S_V$ and we must have $V_4^{(k+1)}\subset S_V$.
+  By piecewise compatibility again, this implies $H_4^{(k+1)}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{(k+1)}\subset S_H$.
+
+  To continue, let $(S_H,S_V)$ be a pair for $D_m$, $m\ge5$, which is not compatible.
+  Write $\varphi:H_{m-1}\to V_m$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_{m-1}$.
+  For any subset $T\subset H_{m-1}$, set $\varphi^*(T)=V_m\setminus\varphi(T)$.
+  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_{m-1}$ and subsets of $V_m$.
+  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_{m-1}$ is given, we refer the reder to \emph{loc. cit} for notation.
+  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
+  Thus by induction, we must have $H_{m-3}^{(k+1)}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{(k+1)}\subset\Omega^{-1}S_H$.
+  It follows from piecewise compatibility that $H_{m-1}^{(k+1)}\cap(\varphi^*)^{-1}S_V=\varnothing$.
+  But then by the definition of $\varphi^*$ we have $V_{m-2}^{(k+1)}\cap S_V=\varnothing$ and $S_V^{(k+1)}=V_m^{(k+1)}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
+  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
+  But this can only occur if $H_{m-2}^{(k+1)}\subset S_H$ since $H_m^{(k+1)}\cap S_H=\varnothing$ by piecewise compatibility.
+\end{proof}
 
@@
 
-Our goal is to show that the compatible pairs provide a natural labelling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
 
@@
 
-\bibitem{rupel} Rupel, D.: Rank 2 Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
+\bibitem{rupel} Rupel, D.: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
 

### 2017-09-13 Grassmannian_cells.tex
Added section 7
When finished, it shall give a combinatorc descprition of non-empty
cells

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quiver Grassmannians of $\widetilde{K(n)}$}
+\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
 \noindent 
@@
 Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+\section{Combinatorial description of non-empty cells}
+
+\begin{definition}\begin{enumerate}
+\item A $2$-quiver is a triple $Q=(Q_0,Q_1,Q_2)$ consisting of a set of vertices $Q_0$, a set of (usual) arrows $Q_1$ and a set of $2$-arrows which are arrows between full subquivers of the quiver $(Q_0,Q_1)$.
+
+\item We call a subset $\beta\subset Q_0$ successor closed if for every arrow $v:p\to q$ we have: if $p\in \beta$, then $q\in\beta$.
+
+\item We call a subset $\beta\subset Q_0$ strong successor closed if it is successor closed and, moreover, for every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$, we have: if $\Gamma(1)_0\subset \beta$, then there exists a vertex $q\in\Gamma(2)_0$ such that $q\in\beta$.
+\end{enumerate}
+\end{definition}
+
+The aim is to associate a $2$-quiver with every preprojective representation $\tilde P_m$ and with their quotients $\tilde P_m^{(k)}$ defined in section \ref{QG}.
+These $2$-quivers are related to certain coefficient quivers of these representations.
+The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$.
+Hence the corresponding Euler characteristic can be computed when counting these subsets.
+A feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.
+
+\begin{remark} 
+Lemma \ref{AR} can be generalized to the cases $m\leq 2$.
+The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
+\end{remark}
+
+We call the following quivers with $n$ sinks, which are coefficient quivers of the indecomposable representations of dimension $(1,k)$ which can be lifted to the universal covering, basic and denote them by $\mathcal K_k$, i.e.
+the quivers of the form
+\[\xymatrix{&&\bullet\\\bullet\ar[rru]\ar[rrd] &&\vdots\\&&\bullet}\]
+The quiver $\mathcal K_{n-k}$ is also the $2$-quivers corresponding to the representations $\tilde P_2^{(k)}$.
+Now we can recursively define the $2$-quivers of the representations $\tilde P_3^{(n-1)}=\tilde P_2^{(1)},\ldots,\tilde P_3^{(0)}=\tilde P_3$ where $\udim \tilde P_2^{(1)}=(1,n-1)$ and $\udim\tilde P_3^{(k)}=(1,n-1)+(n-k-1)(1,n)$.
+This can be done by glueing the $2$-quiver of $\tilde P_3^{(k)}$ to the one of $\tilde P_2$ by a $2$-arrow.
+Note that one can find the image of the Auslander-Reiten translate of $\tilde P_3^{(k)}$ in $\tilde P_2$ as a full subquiver of dimension $(1,1)$.
+Thus the $2$-arrow goes from the whole $2$-quiver corresponding to $\tilde P_3^{(k)}$ to this subquiver.
+As we did not choose a colouring, the target $(1,1)$ can be chosen arbitrary (INSERT DIAGRAM).
+
+Now we can recursively define the $2$-quivers of the representations $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)},\ldots,\tilde P_m^{(0)}=\tilde P_m$ where $\udim\tilde P_m^{(k)}=\udim \tilde P_{m-1}^{(1)}+(n-k-1)\udim \tilde P_{m-1}$.
+To obtain the $2$-quiver of $\tilde P_{m}^{(k-1)}$ we glue the $2$-quiver of $\tilde P_m^{(k)}$ to the one of $\tilde P_{m-1}$ by a $2$-arrow.
+This $2$-arrow connects $\tilde P_m^{(k)}$ to its Auslander-Reiten-translate $\tau\tilde P_m^{(k)}=P_{m-2}^{(k)}$ (up to colouring) which can be found as full subquiver of {\it the} $\tilde P_{m-2}$ to which $\tilde P_{m-1}^{(1)}$ was glued in the last step (more precise).
+This construction is unique (in a sense sufficient for us).
+INSERT DIAGRAM.
 

### 2017-09-14 Grassmannian_cells.tex
Streamlining presentation of truncated preprojective representations

--- 2017-08-12 Grassmannian_cells.tex
@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{claim}[theorem]{Claim}
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \newcommand{\cC}{\mathcal{C}}
+\newcommand{\cP}{\mathcal{P}}
 \newcommand{\ui}{\underline i}
@@
 \renewcommand{\AA}{\mathbb{A}}
+\newcommand{\CC}{\mathbb{C}}
 \newcommand{\kk}{\Bbbk}
@@
 \newcommand{\Hom}{\operatorname{Hom}}
+\newcommand{\im}{\operatorname{im}}
+\newcommand{\codim}{\operatorname{codim}}
+\newcommand{\into}{\hookrightarrow}
+\newcommand{\onto}{\to\!\!\!\!\!\to}
 \newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
 \newcommand{\Sc}[2]{\langle #1,#2\rangle}
+\newcommand{\spn}{\operatorname{span}}
 \setcounter{MaxMatrixCols}{20}
@@
 Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.%, but the vertices $1$ and $2$ are exchanged.
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.
+%, but the vertices $1$ and $2$ are exchanged.
+With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
 %Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$
@@
   These representations satisfy the following recursions using the reflection functors:
-  \[P_1=S_1,\quad P_m=\Sigma_1 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
+  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
   for $m\ge2$.
@@
 
+Write $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.  
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
+\begin{equation}
+  \label{eq:AR sequence}
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+\end{equation}
+where the right-hand morphism is the natural evaluation map.
+
+Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
+Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
 \begin{lemma}
-  For any $m\ge1$, we have 
-  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
-  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
+  \label{le:injective evaluation maps}
+  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+\end{lemma}
+
+%%%%%%%%%%%%%%%%%%%
+% needs polishing %
+%%%%%%%%%%%%%%%%%%%
+%\begin{proof}
+%  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
+%  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
+%\end{proof}
+
+%\begin{lemma}
+%  For any $m\ge1$, we have 
+%  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
+%  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
+%\end{lemma}
+%\begin{proof} 
+%  Note that we have an Auslander-Reiten sequence
+%  \begin{equation}
+%    \label{eq:AR sequence}
+%    0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
+%  \end{equation}
+%  with irreducible homomorphisms $f_i$ which are also linearly independent. 
+%  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
+%  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
+%  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
+%\end{proof}
+%\begin{remark}
+%  Fix a basis $\{f_{m,1},\ldots,f_{m,n}\}$ for $\Hom(P_m,P_{m+1})$, $m\ge2$.
+%  Define a basis $\{f_{\ell,1},\ldots,f_{\ell,n}\}$ for each $\Hom(P_\ell,P_{\ell+1})$, $1\le\ell\le m-1$, by downward induction as follows.  
+%  Write $\iota_\ell:P_\ell\to P_{\ell+1}^n$ for the left-hand morphism from the sequence \eqref{eq:AR sequence} computed using $f_k=f_{\ell+1,k}$, $1\le k\le n$. 
+%  Then the basis element $f_{\ell,k}$ is given by composing $\iota_\ell$ with the coordinate projection $\pi_k:P_{\ell+1}^n\to P_{\ell+1}$ onto the $k$-th factor.
+%  Indeed, applying $\Hom(-,P_{\ell+1})$ to this sequence \eqref{eq:AR sequence} gives an isomorphism $\Hom(P_{\ell+1}^n,P_{\ell+1})\cong\Hom(P_\ell,P_{\ell+1})$ whereby the natural basis of coordinate projections on the left is taken to the basis $\{f_{\ell,k}\}$ on the right.
+%\end{remark}
+\begin{corollary}
+  \label{cor:preprojective homomorphism duality}
+  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
+\end{corollary}
+\begin{proof}
+  Define a map $\Theta:H_m^*\to H_{m-1}$ by $\Theta(\varphi)=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\Theta(\varphi)$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
+  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
+  Then $\Theta(\varphi)=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
+  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
+  Thus $\Theta:H_m^*\to H_{m-1}$ must be injective and hence an isomorphism.
+\end{proof}
+\begin{remark}
+  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
+  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
+  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
+\end{remark}
+
+\begin{definition}
+  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  \begin{equation}
+    \label{eq:truncated preprojectives}
+    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
+  \end{equation}
+\end{definition}
+\begin{remark}
+  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
+\end{remark}
+
+\begin{lemma}
+  \label{le:basic homological properties}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
 \end{lemma}
 \begin{proof}
-  Note that we have an Auslander-Reiten sequence
-  \begin{equation}
-    \label{eq:AR sequence}
-    0\longrightarrow P_{m-1}\stackrel{\iota}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
-  \end{equation}
-  with irreducible homomorphisms $f_i$ which are also linearly independent. 
-  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
-  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
-  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
+  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
+$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
+$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
+  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
 \end{proof}
 
-Write $P_{m+1}^{\{f_1,\ldots,f_k\}}$ for the cokernel of the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$, i.e. we have a short exact sequence
-\begin{equation}
-\label{eq:truncated preprojectives}
-  0\longrightarrow P_m^k\stackrel{[f_1\ \cdots\ f_k]}{\longrightarrow} P_{m+1}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.
-\end{equation}
+\begin{corollary}
+  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
+  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+\end{proof}
+
+The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
+\begin{lemma}
+  \label{le:unique morphisms}
+  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
+\end{lemma}
+\begin{proof}
+  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
+  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+\end{proof}
 
 \begin{lemma}
-  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the following hold:
+  \label{le:irreducible morphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, and $W\subsetneq V$ with $\codim_V W=1$, the unique morphism $P_{m+1}^W\to P_{m+1}^V$ is irreducible.
+\end{lemma}
+In particular, the poset $Gr(H_m)$, thought of as a directed graph, can be identified with a subset of the Auslander-Reiten quiver of $K(n)$.
+
+\begin{lemma}
+  \label{le:truncated homomorphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
+  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
+\end{proof}
+
+\begin{corollary}
+    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
+  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
+  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
+  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated extensions}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
+  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where $U\subset V$ satisfies $\dim(V/U)=1$.
+\end{lemma}
+\begin{proof}
+  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
+  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
+  This gives rise to the following commutative diagram:
+  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
+    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
+    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
+    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
+   & 0 & 0 & & }\]
+  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
+  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
+  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique truncated extension}
+  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  \begin{equation}
+    \label{eq:unique extension}
+    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
+  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
+    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
+    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
+    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
+\end{proof}
+\begin{corollary}
+  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
+  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:more truncated homomorphisms}
+  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
   \begin{enumerate}
-    \item $\Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})$ is naturally isomorphic to $\Hom(P_m,P_{m+1})/\kk f_1\oplus\cdots\oplus\kk f_k$;
-    \item $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ is naturally isomorphic to $\kk f_1\oplus\cdots\oplus\kk f_k$;
-    \item $\Hom(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)=0$.
+    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
+    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
   \end{enumerate}
@@
 \begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives the exact sequence
-  \[0\longrightarrow \Hom(P_m,P_m^k)\stackrel{[f_1\ \cdots\ f_k]\circ}{\longrightarrow} \Hom(P_m,P_{m+1})\longrightarrow \Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})\longrightarrow 0,\]
-  establishing (1).
+  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
+  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
+  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
 
-  To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
-  Observe that $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
-  \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
-    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|(.35){\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
-    0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
-     & 0 & 0 & & }\]
-  where $\hat f_i$ above indicates that the function $f_i$ has been omitted.
-  The bottom row of this diagram is the extension from $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which is naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
+\end{proof}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
+  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
+  The result immediately follows from this.
+\end{proof}
+\begin{remark}
+  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
+\end{remark}
 
-  Part (3) follows immediately from $\Hom(P_{m+1},P_m)=0$.
-	%(2) and the observation that 
-  %\[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
+Let $\tau:\rep K(n)\to\rep K(n)$ denote the Auslander-Reiten translation.
+\begin{lemma}
+  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
+More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
+\end{lemma}
+\begin{proof}
+  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
+  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
+  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
+  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
+  This proves the first claim.
+
+  It remains to show that $\tilde V=\bar{\bar{V}}$.
 \end{proof}
@@
 \begin{lemma}
-  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion $\iota:P_{m-1}\hookrightarrow P_m^n$ from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n$-th factor.
-Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}=P_m^{\{g\}}$.
+  \label{le:truncated exact sequences}
+  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
 \end{lemma}
 \begin{proof}
-  We have the following commutative diagram
-  \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
-  0\ar[r]& P_m^{n-1}\ \ \ \ar[r]^{[f_1\ \cdots\ f_{n-1}]}&\ \ \ P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
-  Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
-  But this implies the kernels of the vertical morphisms coincide.
+  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
+    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
+    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
+  It follows that the sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
+  is exact.
+  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
 
-  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so its kernel is $P_{m-1}$.
-  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}=P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
+  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
 \end{proof}
 
-For any nonempty subset $I\subset[1,k]$, say with $|I|=\ell$, we get an exact sequence
-\[0\longrightarrow P_m^\ell\stackrel{[f_i]_{i\in I}}{\longrightarrow} P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.\]
-Each such sequence has the following almost-split property for subrepresentations of $P_{m+1}^{\{f_1,\ldots,f_k\}}$.
+For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
+Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
 \begin{lemma}
-  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, given any proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$, the upper pullback sequence
-  \[\xymatrix{0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r] & V^I\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V\ar[d]\ar[r] & 0 \\
-  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}} & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
-  splits for every $I\subset[1,k]$.
+  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y\ar[r] \ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  splits for every proper subspace $W\subsetneq V$.
 \end{lemma}
 \begin{proof}
-  When $I=\varnothing$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.
+  We proceed by induction on $\codim_V W$.  
+  When $\codim_V W=1$, we have an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
+  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
 
-  We proceed by simultaneous induction on $k$ and $\ell=|I|$.  For any nonzero $f\in\Hom(P_m,P_{m+1})$ the exact sequence
-  \[\xymatrix{0\ar[r] & P_m\ar[r]^f & P_{m+1}\ar[r] & P_{m+1}^{\{f\}}\ar[r] & 0}\]
-  is almost split, giving the claim in the case $k=\ell=1$.  For $k>1$ and a nontrivial proper subset $I\subsetneq[1,k]$, we have the following commutative diagram
-  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
-  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_i\}_{i\in I}}\ar[d]\ar[r] & 0 \\
-  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ gives rise, via pullbacks, to the following commutative diagram
-  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
-  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\ar[d]\ar[r] & 0 \\
-  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & V^I\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  in which the middle vertical sequence and the middle horizontal sequence split by induction.  
-  But the images of $[f_i]_{i\in I}$ and $[f_j]_{j\in[1,k]\setminus I}$ intersect trivially inside $V^{[1,k]}$ and thus the lower horizontal sequence must split as well, establishing the claim for $I\subsetneq[1,k]$.
+  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
+  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
+  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y'\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
+  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
+  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
+  The result now follows since the outer square is also a pullback.
+\end{proof}
 
-  For $I=[1,k]$, we consider the commutative diagram
-  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_{m+1}\ar@{=}[r]\ar[d] & P_{m+1}\ar[d]\ar[r] & 0 \\
-  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & P_{m+1}\oplus P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_1\ \cdots\ f_{k-1}\}}\oplus P_{m+1}^{\{f_k\}}\ar[d]\ar[r] & 0 \\
-  0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d] & P_{m+1}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ then gives rise to the following commutative diagram
-  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & V^{[1,k]}\ar@{=}[r]\ar[d]^{\Delta} & V^{[1,k]}\ar[d]\ar[r] & 0 \\
-  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & V^{[1,k]}\oplus V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\oplus V^I\ar[d]\ar[r] & 0 \\
-  0\ar[r]& P_m^k\ar[r]\ar[d] & V^{[1,k]}\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
-  in which the middle vertical sequence splits and the middle horizontal sequence is split by induction.  
-  But the image of $[f_1\ \cdots\ f_k]:P_m^{k-1}\oplus P_m\to V^{[1,k]}\oplus V^{[1,k]}$ and the diagonal $\Delta:V^{[1,k]}\to V^{[1,k]}\oplus V^{[1,k]}$ intersect trivially because $f_1,\ldots,f_k$ are linearly independent.
-  As above the lower horizontal sequence also splits, establishing the claim for $I=[1,k]$.
-\end{proof}
+%\begin{lemma}
+%  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, a subrepresentation $V\subset P_m$ fits into a commutative diagram
+%  \[\xymatrix{0\ar[r] & V\ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & W\ar[d]\ar[r] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar@{=}[d]\ar[r] & 0 \\
+%  0\ar[r]& P_m\ar[r]^(.35){f_k} & P_{m+1}^{\{f_1,\ldots,f_{k-1}\}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
+%  if and only if the lower pushout sequence below splits: 
+%  \[\xymatrix{0\ar[r]& P_m\ar[r]^(.35){f_k}\ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^{\{f_1,\ldots,f_{k-1}\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar@{=}[d]\ar[r]& 0\\ 0\ar[r]& P_m/V\ar[r] & X\ar[r] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r] & 0}.\]
+%  This occurs (?) if and only if the composed morphism
+%  \[\xymatrix{V\ar[r] & P_m\ar[r] & P_m^{\{g_2,\ldots,g_n\}}\ar@{=}[r] & P_{m-1}^{\{g_1\}}\ar[r] & P_{m-1}^{\{g_1,\ldots,g_k\}}}\]
+%  is nonzero.
+%  
+%  there is a commutative diagram
+%\end{lemma}
+%\begin{proof}
+%  For a proper subrepresentation $V\subset P_m$ we have
+%  \[0\longrightarrow \Hom(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m/V)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},V)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m/V)\longrightarrow 0\]
+%  and
+%  \[0\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},V)\longrightarrow \Ext(P_{m+1},V)\longrightarrow \Ext(P_m^k,V)\longrightarrow 0.\]
+%\end{proof}
 

### 2017-09-26 Grassmannian_cells.tex
Section 7
inserted the notion and construction of 2-quivers
section needs to be revised

--- 2017-09-14 Grassmannian_cells.tex
@@
 \usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
+\usepackage{tikz}
+\usepackage{pgflibraryarrows}
+\usepackage{pgflibrarysnakes}
+\usetikzlibrary{fit}
 \usepackage[margin=1in]{geometry}
@@
 Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+\section{Combinatorial description of non-empty cells}
+
+\begin{definition}\begin{enumerate}
+\item A $2$-quiver is a triple $Q=(Q_0,Q_1,Q_2)$ consisting of a set of vertices $Q_0$, a set of (usual) arrows $Q_1$ and a set of $2$-arrows which are arrows between full subquivers of the quiver $(Q_0,Q_1)$.
+
+\item We call a subset $\beta\subset Q_0$ successor closed if for every arrow $v:p\to q$ we have: if $p\in \beta$, then $q\in\beta$.
+
+\item We call a subset $\beta\subset Q_0$ strong successor closed if it is successor closed and, moreover, for every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$, we have: if $\Gamma(1)_0\subset \beta$, then there exists a vertex $q\in\Gamma(2)_0$ such that $q\in\beta$.
+
+\item Notion of equivalence of $2$-quivers to justify the transformation of $2$-arrows into usual arrows.
+
+\end{enumerate}
+\end{definition}
+
+The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}.
+These $2$-quivers are related to certain coefficient quivers of these representations.
+The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$.
+Hence the corresponding Euler characteristic can be computed when counting these subsets.
+It will turn out that a feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.
+
+\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
+Lemma \ref{AR} can be generalized to the cases $m\leq 2$.
+The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
+
+\end{remark}
+
+We recall the notion of Section \ref{QG} where we denote the arrows of $K(n)$ by $v_1,\ldots,v_n$.
+Actually, all $2$-quivers can be build from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$ where $P_2^{(n-1)}$ depends on a choice as it is a truncated preprojective representation of dimension $(1,1)$.
+Indeed, it is the cokernel of a short exact sequence
+\[\ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}\]
+for which we have $n-1$ choices. Without loss of generality, we make the following choice when defining
+$$P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{v_1}i^{(n-1)}_2=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1$$
+by its coefficient quiver. Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
+$$\Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.$$
+
+This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
+\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
+by the coefficient quivers
+\[\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\]
+Note that we have a short exact sequence
+\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
+where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
+We define the $2$-quiver of $P_2^{(k)}$ by
+\\
+
+\begin{tikzpicture}
+\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
+\draw (0,0) node (A) {$j^{(k)}_{2,n-k}$} +(2.5,0) node (B) {$j^{(k)}_{2,n-k-1}$}+(2.5,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(5,0) node (B1) {$\dots$} +(7.5,0) node (C) {$j^{(k)}_{2,2}$} +(7.5,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(10,0) node (D) {$j^{(k)}_{2,1}$}  +(12.5,0) node (E) {$i^{(k)}_2$} +(10,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$};
+\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
+\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
+\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};
+
+\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
+\draw[<-] (D)--(E) node[pos=.5,above] {$v_1$};
+\draw[->,red] (Q1)--(C) node[pos=.5,above] {$v_2$};
+\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$v_3$};
+\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$v_{n-k-1}$};
+
+\draw[->,red] (Q3)--(A) node[pos=.5,above] {$v_{n-k}$};
+\end{tikzpicture}
+\\
+
+\noindent
+where the $2$-arrows are coloured red.
+As the number of strong successor closed subsets of this $2$-quiver coincides with the number of successor closed subsets of the coefficient quiver, for clearness reasons, we will mostly work with the coefficient quiver instead.
+
+The next step is to define the $2$-quivers of $P^{(k)}_3$ whence the remaining $2$-quivers can be obtained recursively. First we choose the basis of $\Ext(P_2^{(1)},P_2)$ given by the linear maps
+$$\{i_2^{(n-1)}\xlongrightarrow{v_n}j_{2,i}\mid i=n-1,\ldots,1\}.$$
+This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ where we drop the indices of the vertices in abuse of notation.
+\\
+
+\begin{tikzpicture}[scale=1.4]
+\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
+\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$v_1$};
+\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$v_2$};
+\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
+\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ;
+\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$v_1$};
+\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$v_2$};
+\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
+\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{(2)}$};
+
+\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ;
+\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$v_1$};
+\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$v_{n-2}$};
+\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
+\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$};
+\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$v_1$};
+\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$v_2$};
+\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
+\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ;
+\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $v_1$};
+\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $v_2$};
+\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $v_{n-1}$};
+%\tikzstyle{every node}=[circle,fill=white!10]
+\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
+%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
+\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$v_{n}$};
+\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
+\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$v_{n}$};
+\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
+\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$v_{n}$};
+\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
+
+\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$v_{n}$};
+\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$v_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$v_{n}$};
+
+\end{tikzpicture}
+\\
+
+We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$.
+If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, Lemma \ref{AR} gives a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
+Let us consider the case $m=3$.
+The coefficient quiver of $\tau P_3^{(k)}$ is given by
+\[\xymatrix@R10pt@C20pt{&&i_{1}\ar_{v_1}[lld]\\ j &&\vdots\\&&i_{k}\ar_{v_{k}}[llu]}.\]
+The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{v_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{v_l} i_l$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$.
+In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers.
+It can be seen that this is no restriction from the combinatorial point of view.
+
+Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure.
+For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
+Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
+\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]
+
+As before we get a one-to-one correspondence between basis elements when passing to the universal covering quiver.
+More precisely, we can take the BGP-reflected basis of the basis of $\Ext(P_2^{(1)},P_2)$ from above.
+
+Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{(k)}$. The $2$-quiver of $P^{(k-1)}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{(k)}$ to the one of $P_{m}$
+\\
+
+\begin{tikzpicture}
+\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{(1)}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{(n-2)}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{(1)}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{(k)}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{(n-2)}$} +(13.5,0) node (E1b) {$P^{(n-1)}_{m-2}$} ;
+\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
+\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
+\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
+\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
+\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
+\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
+\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
+\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
+\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
+\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
+\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {$$};
+\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {$$};
+\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {$$};
+\draw[->,red] (Q41)--(E1) node[pos=.5,above] {$$};
+\draw[->,red] (Q51)--(D1) node[pos=.5,above] {$$};
+\draw[->,red] (Q61)--(B11) node[pos=.5,above] {$$};
+\draw[->,red] (Q71)--(B1) node[pos=.5,above] {$$};
+\draw[->,red] (Q81)--(A1) node[pos=.5,above] {$$};
+
+\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{(k)}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{(n-2)}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{(n-1)}=P_{m}^{(1)}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{(n-1)}$};
+\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
+\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
+\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};
+
+\draw[<-,red] (D)--(E) node[pos=.5,above] {};
+\draw[->,red] (Q1)--(C) node[pos=.5,above] {$$};
+\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$$};
+\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$$};
+
+\node (PMK) [draw=black, thick,fit={(Q2b) (B)}]{};
+\draw[->,red,thick] (PMK)--(Q31);
+\end{tikzpicture}
+\\
+
+\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{(k)}$ to its Auslander-Reiten translate $\tau P_{m+1}^{(k)}= P_{m-1}^{(k)}$ in $P_m$.
+This subquiver can be found at the very right of the $2$-quiver of $P_m$.
+Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view.
+For $n=3$ the $2$-quiver of $P_3$ is given by:\\
+
+\begin{tikzpicture}[scale=1]
+\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
+\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
+\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
+%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\node (Q0)[draw=black,fit={(I3) (J31) }]{};
+\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
+\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};
+
+%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
+\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
+\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};
+\end{tikzpicture}
+\\
+
+The one of $P_4$ is given by:\\
+
+\begin{tikzpicture}[scale=1]
+\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
+\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
+\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
+%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\node (Q0)[draw=black,fit={(I3) (J31) }]{};
+\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
+\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};
+
+%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
+\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
+\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};
+
+\draw (0,-4) node (I1b) {$\bullet$} +(1,1) node (J11b) {$\bullet$} +(1,0) node (J12b) {$\bullet$} +(1,-1) node (J13b) {$\bullet$}; 
+\draw[->] (I1b)--(J11b) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I1b)--(J12b) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+
+\draw (2,-4) node (I2b) {$\bullet$} +(1,1) node (J21b) {$\bullet$} +(1,0) node (J22b) {$\bullet$} +(1,-1) node (J23b) {$\bullet$}; 
+\draw[->] (I2b)--(J21b) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I2b)--(J22b) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I2b)--(J23b) node[pos=.7,above,sloped]{\scriptsize$c$};
+
+\draw (6,-4) node (I3b) {$\bullet$} (5,-4) node (J31b) {$\bullet$} (4,-4) node (J33b) {$\bullet$}; 
+\draw[->] (I3b)--(J31b) node[pos=.5,above,sloped]{\scriptsize$a$};
+\node (Q0b)[draw=black,fit={(I3b) (J31b) }]{};
+\node (Q1b)[draw=black,fit={(Q0b) (J33b)}]{};
+\node (Q2b)[draw=black,fit={(Q1b) (I2b) (J21b) (J22b) (J23b)}]{};
+
+\draw[->,red] (Q0b)--(J33b) node[pos=.5,above] {\scriptsize $b$};
+\draw[->,red] (Q1b)--(J22b) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2b)--(J11b) node[pos=.5,above] {\scriptsize $c$};
+
+\draw (9,-4) node (I2c) {$\bullet$} +(1,1) node (J21c) {$\bullet$} +(1,0) node (J22c) {$\bullet$} +(1,-1) node (J23c) {$\bullet$}; 
+\draw[->] (I2c)--(J21c) node[pos=.7,above,sloped]{\scriptsize$a$};
+\draw[->] (I2c)--(J22c) node[pos=.7,above,sloped]{\scriptsize$b$};
+\draw[->] (I2c)--(J23c) node[pos=.7,above,sloped]{\scriptsize$c$};
+
+\draw (13,-4) node (I3c) {$\bullet$} (12,-4) node (J31c) {$\bullet$} (11,-4) node (J33c) {$\bullet$}; 
+\draw[->] (I3c)--(J31c) node[pos=.5,above,sloped]{\scriptsize$a$};
+\node (Q0c)[draw=black,fit={(I3c) (J31c) }]{};
+\node (Q1c)[draw=black,fit={(Q0c) (J33c)}]{};
+\node (Q2c)[draw=black,fit={(Q1c) (I2c) (J21c) (J22c) (J23c)}]{};
+\node (Q3c)[draw=black,fit={(Q2c) (Q2b) (I1b)}]{};
+\draw[->,red] (Q0c)--(J33c) node[pos=.5,above] {\scriptsize $b$};
+\draw[->,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {\scriptsize $b$};
+\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {\scriptsize $c$};
+
+\end{tikzpicture}
+
+\begin{theorem}
+The Euler characteristic $\chi(\Gr_e(P_m^{(k)}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{(k)}$.
+\end{theorem}
 

### 2017-09-26 Grassmannian_cells.tex
Theorem 7.3
(upgradeable) proof of 7.3

@@
 \newcommand\udim{{\underline{\dim}\, }}
-
+\newcommand{\pt}{\mathrm{pt}}
 \newcommand{\Rep}{\mathrm{Rep}}
@@
 \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
-The analogous statement is true when replacing $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
+The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
 \end{theorem}
+
+Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
+In general, considering the linear map  
+\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
+we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
+
 \subsection{Bialynicki-Birula decomposition}
-The aim of this section is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
 If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
@@
 
-\section{Torus Actions on Quiver Grassmannians}
+\section{Torus Actions on Quiver Grassmannians}\label{torusaction}
 \noindent 
-
 Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
@@
 We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
-there exist number $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
+there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
 \[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
@@
 All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$ where $v_w\in X_j$, i.e.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
 we have
@@
 by the coefficient quivers
-\[\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\]
+\begin{align}\label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\end{align}
 Note that we have a short exact sequence
@@
 \end{theorem}
+\begin{proof}
+We proceed by induction.
+The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{(n-1)}\}$.
+Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\emptyset,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
+As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.
+
+Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{(k)}$ (resp. $\tilde P_{m+1}^{(k)}$) and consider the short exact sequence
+\[\ses{\tilde P_m}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}.\]
+Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{(k)}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{(k)}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
+Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
+By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{(k)})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{(k)}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{(k)}})_0=\emptyset$.
+But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{(k)}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{(k)}}$ by a $2$-arrow.
+
+\end{proof}
 

### 2017-09-27 Grassmannian_cells.tex
Unknown edits

--- 2017-09-14 Grassmannian_cells.tex
@@
 With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
-%Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$
+Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
 
@@
 \begin{remark}
+  \label{rem:reflection recursion}
   These representations satisfy the following recursions using the reflection functors:
@@
   for $m\ge2$.
+  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
 \end{remark}
@@
 \begin{proof}
-  Define a map $\Theta:H_m^*\to H_{m-1}$ by $\Theta(\varphi)=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\Theta(\varphi)$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
+  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
   Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
-  Then $\Theta(\varphi)=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
+  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
   But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
-  Thus $\Theta:H_m^*\to H_{m-1}$ must be injective and hence an isomorphism.
+  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
 \end{proof}
@@
 \end{remark}
+Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
+Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
+The next observation is essential for the results to follow.
+\begin{proposition}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
+\end{proposition}
+\begin{proof}
+  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
+  Indeed, we have
+  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
+\end{proof}
 
@@
 \begin{corollary}
+  \label{cor:truncated preprojective isomorphism}
   Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
@@
 \end{proof}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
+\end{corollary}
 
@@
 \end{proof}
+\begin{remark}
+  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
+  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
+\end{remark}
 \begin{corollary}
@@
 
-Let $\tau:\rep K(n)\to\rep K(n)$ denote the Auslander-Reiten translation.
+\begin{lemma}
+  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
+\end{lemma}
+
 \begin{lemma}
@@
     & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
-    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
     0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
@@
   For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y\ar[r] \ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
     0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
@@
   Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
-  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y'\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
+  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
   P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
@@
 \end{proof}
-
-%\begin{lemma}
-%  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, a subrepresentation $V\subset P_m$ fits into a commutative diagram
-%  \[\xymatrix{0\ar[r] & V\ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & W\ar[d]\ar[r] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar@{=}[d]\ar[r] & 0 \\
-%  0\ar[r]& P_m\ar[r]^(.35){f_k} & P_{m+1}^{\{f_1,\ldots,f_{k-1}\}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
-%  if and only if the lower pushout sequence below splits: 
-%  \[\xymatrix{0\ar[r]& P_m\ar[r]^(.35){f_k}\ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^{\{f_1,\ldots,f_{k-1}\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar@{=}[d]\ar[r]& 0\\ 0\ar[r]& P_m/V\ar[r] & X\ar[r] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r] & 0}.\]
-%  This occurs (?) if and only if the composed morphism
-%  \[\xymatrix{V\ar[r] & P_m\ar[r] & P_m^{\{g_2,\ldots,g_n\}}\ar@{=}[r] & P_{m-1}^{\{g_1\}}\ar[r] & P_{m-1}^{\{g_1,\ldots,g_k\}}}\]
-%  is nonzero.
-%  
-%  there is a commutative diagram
-%\end{lemma}
-%\begin{proof}
-%  For a proper subrepresentation $V\subset P_m$ we have
-%  \[0\longrightarrow \Hom(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m/V)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},V)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m/V)\longrightarrow 0\]
-%  and
-%  \[0\longrightarrow \Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},V)\longrightarrow \Ext(P_{m+1},V)\longrightarrow \Ext(P_m^k,V)\longrightarrow 0.\]
-%\end{proof}
+\begin{corollary}
+  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+\end{corollary}
+
+\begin{lemma}
+  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  This occurs (?) if and only if the composed morphism
+  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
+  is nonzero.
+\end{lemma}
+\begin{proof}
+  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
+  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
+    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
+    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
+  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
+
+  and
+  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
+\end{proof}
 
@@
 Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\bibitem{brenner-butler} S. Benner, M.~C.~R. Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
 \bibitem{cc}

### 2017-11-16 Grassmannian_cells.tex
insert result of Reineke et al

@@
 \newcommand{\cC}{\mathcal{C}}
+\newcommand{\cG}{\mathcal{G}}
 \newcommand{\cP}{\mathcal{P}}
@@
 \end{theorem}
-
+Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
+\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
+which is also called Caldero-Chapoton map.
+By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
+Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
+$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
+The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
+\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+
+The following is proved in \cite[Section 3]{cefr}.
+\begin{theorem}\label{vb}
+If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
+In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+\end{theorem}
+\begin{proof}\footnote{sketch, double-check}
+
+As $X$ and $Y$ are projective, they are compact.
+As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
+This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
+
+\end{proof}
 \section{Torus Actions on Quiver Grassmannians}\label{torusaction}
@@
 The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}.
+In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma \ref{vb}?}.
 Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
@@
   P. Caldero, B. Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
+\bibitem{cefr} Cerulli Irelli, Esposito, Franzen, Reineke: Topology of Quiver Grassmannians. Preprint 2017.
 \bibitem{cr}
@@
 \bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
-
+%\bibitem{mats} Matsumura, H.: Commutative ring theory. 
 \bibitem{rupel} Rupel, D.: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.

### 2017-11-17 Grassmannian_cells.tex
Minors edits in K(n) section and reorganization

@@
 \setcounter{MaxMatrixCols}{20}
-\title{Cell Decomposition of Rank 2 Quiver Grassmannians}
+\title{Cell Decompositions for Rank Two Quiver Grassmannians}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Terminology and Preliminary results}
-\subsection{Covering theory}\footnote{more and more precise definitions}
-For an introduction to covering theory we refer to \cite{gab}.
-Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
-Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
-\begin{definition}
-The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
-
-The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
-
-We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
-$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
-$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
-$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
-\end{definition}
-Note that in our definition every covering quiver has infinitely many connected components.
-But every connected component is a covering in the sense of \cite{gab}.
-As indecomposable representations live on one component this makes no difference.
-Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
-Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
-The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
-We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp.
-dimension vectors) are equivalent in this case.
-The analogous observation can also be made for $\tilde Q$.
-If $M$ is a representation of $\hat Q$ (resp.
-$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
-$w\in W_Q$) by $M_\chi$ (resp.
-$M_w$).
-
-\begin{lemma}
-  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
-\end{lemma}
-\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
-Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
-Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
-$(q,w)$ of $\tilde Q$).
-This leads the claim.
-The statement for preinjective representations follows in the same way.
-\end{proof}
-As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
-\begin{theorem}\label{covering}
-The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
-\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
-The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
-\end{theorem}
-
-Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
-In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
-we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
-
-\subsection{Bialynicki-Birula decomposition}
-The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
-If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
-More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
-For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
-
-Then we have the following statement, \cite[Section 4]{bb}:
-\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
-Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
-Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
-the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
-
-In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
-\end{theorem}
-Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
-\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
-which is also called Caldero-Chapoton map.
-By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
-Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
-$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
-The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
-\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
-
-The following is proved in \cite[Section 3]{cefr}.
-\begin{theorem}\label{vb}
-If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
-In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
-\end{theorem}
-\begin{proof}\footnote{sketch, double-check}
-
-As $X$ and $Y$ are projective, they are compact.
-As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
-This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
-
-\end{proof}
-\section{Torus Actions on Quiver Grassmannians}\label{torusaction}
-\noindent 
-Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
-We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
-Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
-there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
-\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
-Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
-This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
-We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
-there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
-where the unit vectors are in the columns $i_1,\ldots,i_d$.
-All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
-we have
-\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
-Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
-\begin{lemma}\label{usualGrass}
-Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
-Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
-\end{lemma}
-\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
-\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
-where $j_0=0$.
-
-Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
-Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
-As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
-This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
-As the colums are linear independent, this already shows the claim.
-\end{proof}
-The next step is to generalize this to quiver Grassmannians.
-
-Let $Q$ be an acyclic quiver.
-We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
-We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
-We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
-For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
-In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
-Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
-\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
-\end{lemma}
-\begin{proof} Let $U\in \Gr_\bfe(X)$.
-Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
-Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
-Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
-Then it follows
-\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
-for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
-Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
-for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
-\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
-for every $t\in \C^\ast$.
-\end{proof}
-
-\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
-There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
-\end{lemma}
-\begin{proof}
-Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
-In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
-We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
-To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
-Set $c_{\alpha_1}=1$ and inductively
-\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
-Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
-In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
-\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
-
-First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
-Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
-which implies
-\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
-Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
-This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
-An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
-
-\end{proof}
-In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
-
-\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
-Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
- a torus action on $Gr_\bfe^Q(X)$ such that
-  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
-\end{theorem}
-\begin{proof}
-A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
-$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
-Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
-A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
-\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
-Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
-\end{proof}
-The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
-to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
-Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
-Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
-Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
-If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
-We obtain:
-\begin{corollary}
-Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
-\end{corollary}
-%\begin{corollary}
-%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
-%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
-%\end{corollary}
-
-\begin{question}
-  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
-\end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Representation Theory of $K(n)$}
@@
 \noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
+The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
+As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
+\begin{itemize}
+  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
+  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, in particular $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
+\end{itemize}
+Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
+More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
+\begin{lemma}
+  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta:g.M\to g.N$ for any $g\in GL_n(\CC)$.
+\end{lemma}
+\begin{proof}
+  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
+  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
+  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij} \theta_2\circ M_{a_j}=\sum\limits_{j=1}^n g_{ij} M_{a_j}\circ\theta_1=N'_{a_i}\circ\theta_1\]
+  for $1\le i\le n$ so that $\theta$ gives a morphism from $g.M$ to $g.N$. 
+\end{proof}
+
 Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.
 %, but the vertices $1$ and $2$ are exchanged.
-With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
+With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
+
+\begin{lemma}
+  The reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ are $GL_n(\CC)$-equivariant. 
+\end{lemma}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Terminology and Preliminary results}
+
+Incorporate these into other sections...
+
+\subsection{Covering theory}\footnote{more and more precise definitions}
+For an introduction to covering theory we refer to \cite{gab}.
+Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
+Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
+\begin{definition}
+The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
+
+The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
+
+We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
+$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
+$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
+\end{definition}
+Note that in our definition every covering quiver has infinitely many connected components.
+But every connected component is a covering in the sense of \cite{gab}.
+As indecomposable representations live on one component this makes no difference.
+Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
+The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp.
+dimension vectors) are equivalent in this case.
+The analogous observation can also be made for $\tilde Q$.
+If $M$ is a representation of $\hat Q$ (resp.
+$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
+$w\in W_Q$) by $M_\chi$ (resp.
+$M_w$).
+
+\begin{lemma}
+  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
+\end{lemma}
+\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
+Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
+Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
+$(q,w)$ of $\tilde Q$).
+This leads the claim.
+The statement for preinjective representations follows in the same way.
+\end{proof}
+As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
+\begin{theorem}\label{covering}
+The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
+\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
+The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
+\end{theorem}
+
+Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
+In general, considering the linear map  
+\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
+we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
+
+\section{Torus Actions on Quiver Grassmannians}\label{torusaction}
+
+Define quiver representations and quiver Grassmannians...
+
+\subsection{Bialynicki-Birula decomposition}
+The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
+More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
+For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
+\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
+
+Then we have the following statement, \cite[Section 4]{bb}:
+\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
+Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
+Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
+the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
+
+In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
+\end{theorem}
+
+Move this???
+
+Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
+\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
+which is also called Caldero-Chapoton map.
+By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
+Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
+$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
+The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
+\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+
+The following is proved in \cite[Section 3]{cefr}.
+\begin{theorem}\label{vb}
+If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
+In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+\end{theorem}
+\begin{proof}\footnote{sketch, double-check}
+
+As $X$ and $Y$ are projective, they are compact.
+As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
+This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
+
+\end{proof}
+
+%%%
+
+\noindent 
+Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
+We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
+Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
+Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
+there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
+\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
+Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
+Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
+This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
+We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
+there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
+where the unit vectors are in the columns $i_1,\ldots,i_d$.
+All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
+we have
+\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
+Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+\begin{lemma}\label{usualGrass}
+Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
+Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
+\end{lemma}
+\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
+\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
+where $j_0=0$.
+
+Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
+Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
+As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
+This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
+As the colums are linear independent, this already shows the claim.
+\end{proof}
+The next step is to generalize this to quiver Grassmannians.
+
+Let $Q$ be an acyclic quiver.
+We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
+We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
+We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
+For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
+In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
+Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
+\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
+If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
+\end{lemma}
+\begin{proof} Let $U\in \Gr_\bfe(X)$.
+Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
+Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
+Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
+Then it follows
+\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
+for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
+Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
+for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
+\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
+for every $t\in \C^\ast$.
+\end{proof}
+
+\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
+There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
+\end{lemma}
+\begin{proof}
+Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
+In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
+We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
+To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
+Set $c_{\alpha_1}=1$ and inductively
+\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
+Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
+In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
+\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
+
+First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
+Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
+which implies
+\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
+Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
+This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
+An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
+
+\end{proof}
+In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
+
+\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
+Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
+ a torus action on $Gr_\bfe^Q(X)$ such that
+  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
+\end{theorem}
+\begin{proof}
+A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
+$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
+Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
+A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
+\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
+Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
+\end{proof}
+The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
+to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
+Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
+Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
+Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
+If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
+We obtain:
+\begin{corollary}
+Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
+  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
+\end{corollary}
+%\begin{corollary}
+%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
+%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
+%\end{corollary}
+
+\begin{question}
+  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
+\end{question}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}

### 2017-11-17 Grassmannian_cells.tex
Reorganization

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Terminology and Preliminary results}
+
+Incorporate this into other sections...
+
+\begin{lemma}
+  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
+\end{lemma}
+\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
+Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
+Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
+$(q,w)$ of $\tilde Q$).
+This leads the claim.
+The statement for preinjective representations follows in the same way.
+\end{proof}
+As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
+\begin{theorem}\label{covering}
+The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
+\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
+The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
+\end{theorem}
+
+Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
+In general, considering the linear map  
+\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
+we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Torus Actions on Quiver Grassmannians}
+\label{torusaction}
+
+Move this somewhere...
+
+For an introduction to covering theory we refer to \cite{gab}.
+Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
+Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
+\begin{definition}
+The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
+
+The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
+
+We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
+$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
+$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
+\end{definition}
+Note that in our definition every covering quiver has infinitely many connected components.
+But every connected component is a covering in the sense of \cite{gab}.
+As indecomposable representations live on one component this makes no difference.
+Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
+The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp.
+dimension vectors) are equivalent in this case.
+The analogous observation can also be made for $\tilde Q$.
+If $M$ is a representation of $\hat Q$ (resp.
+$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
+$w\in W_Q$) by $M_\chi$ (resp.
+$M_w$).
+
+\subsection{Bialynicki-Birula decomposition}
+The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
+More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
+For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
+\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
+
+Then we have the following statement, \cite[Section 4]{bb}:
+\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
+Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
+Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
+the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
+
+In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
+\end{theorem}
+
+Move this???
+
+Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
+\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
+which is also called Caldero-Chapoton map.
+By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
+Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
+$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
+The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
+\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+
+The following is proved in \cite[Section 3]{cefr}.
+\begin{theorem}\label{vb}
+If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
+In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+\end{theorem}
+\begin{proof}\footnote{sketch, double-check}
+
+As $X$ and $Y$ are projective, they are compact.
+As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
+This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
+
+\end{proof}
+
+%%%
+
+\noindent 
+Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
+We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
+Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
+Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
+there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
+\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
+Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
+Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
+This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
+We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
+there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
+where the unit vectors are in the columns $i_1,\ldots,i_d$.
+All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
+we have
+\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
+Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+\begin{lemma}\label{usualGrass}
+Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
+Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
+\end{lemma}
+\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
+\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
+where $j_0=0$.
+
+Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
+Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
+As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
+This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
+As the colums are linear independent, this already shows the claim.
+\end{proof}
+The next step is to generalize this to quiver Grassmannians.
+
+Let $Q$ be an acyclic quiver.
+We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
+We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
+We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
+For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
+In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
+Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
+\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
+If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
+\end{lemma}
+\begin{proof} Let $U\in \Gr_\bfe(X)$.
+Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
+Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
+Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
+Then it follows
+\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
+for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
+Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
+for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
+\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
+for every $t\in \C^\ast$.
+\end{proof}
+
+\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
+There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
+\end{lemma}
+\begin{proof}
+Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
+In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
+We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
+To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
+Set $c_{\alpha_1}=1$ and inductively
+\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
+Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
+In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
+\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
+
+First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
+Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
+which implies
+\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
+Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
+This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
+An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
+
+\end{proof}
+In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
+
+\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
+Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
+ a torus action on $Gr_\bfe^Q(X)$ such that
+  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
+\end{theorem}
+\begin{proof}
+A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
+$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
+Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
+A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
+\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
+Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
+\end{proof}
+The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
+to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
+Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
+Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
+Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
+If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
+We obtain:
+\begin{corollary}
+Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
+  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
+\end{corollary}
+%\begin{corollary}
+%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
+%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
+%\end{corollary}
+
+\begin{question}
+  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
+\end{question}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Representation Theory of $K(n)$}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Terminology and Preliminary results}
-
-Incorporate these into other sections...
-
-\subsection{Covering theory}\footnote{more and more precise definitions}
-For an introduction to covering theory we refer to \cite{gab}.
-Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
-Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
-\begin{definition}
-The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
-
-The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
-
-We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
-$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
-$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
-$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
-\end{definition}
-Note that in our definition every covering quiver has infinitely many connected components.
-But every connected component is a covering in the sense of \cite{gab}.
-As indecomposable representations live on one component this makes no difference.
-Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
-Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
-The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
-We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp.
-dimension vectors) are equivalent in this case.
-The analogous observation can also be made for $\tilde Q$.
-If $M$ is a representation of $\hat Q$ (resp.
-$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
-$w\in W_Q$) by $M_\chi$ (resp.
-$M_w$).
-
-\begin{lemma}
-  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
-\end{lemma}
-\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
-Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
-Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
-$(q,w)$ of $\tilde Q$).
-This leads the claim.
-The statement for preinjective representations follows in the same way.
-\end{proof}
-As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
-\begin{theorem}\label{covering}
-The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
-\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
-The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
-\end{theorem}
-
-Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
-In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
-we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
-
-\section{Torus Actions on Quiver Grassmannians}\label{torusaction}
-
-Define quiver representations and quiver Grassmannians...
-
-\subsection{Bialynicki-Birula decomposition}
-The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
-If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
-More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
-For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
-
-Then we have the following statement, \cite[Section 4]{bb}:
-\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
-Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
-Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
-the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
-
-In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
-\end{theorem}
-
-Move this???
-
-Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
-\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
-which is also called Caldero-Chapoton map.
-By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
-Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
-$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
-The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
-\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
-
-The following is proved in \cite[Section 3]{cefr}.
-\begin{theorem}\label{vb}
-If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
-In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
-\end{theorem}
-\begin{proof}\footnote{sketch, double-check}
-
-As $X$ and $Y$ are projective, they are compact.
-As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
-This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
-
-\end{proof}
-
-%%%
-
-\noindent 
-Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
-We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
-Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
-there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
-\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
-Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
-This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
-We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
-there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
-where the unit vectors are in the columns $i_1,\ldots,i_d$.
-All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
-we have
-\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
-Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
-\begin{lemma}\label{usualGrass}
-Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
-Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
-\end{lemma}
-\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
-\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
-where $j_0=0$.
-
-Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
-Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
-As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
-This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
-As the colums are linear independent, this already shows the claim.
-\end{proof}
-The next step is to generalize this to quiver Grassmannians.
-
-Let $Q$ be an acyclic quiver.
-We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
-We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
-We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
-For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
-In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
-Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
-\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
-\end{lemma}
-\begin{proof} Let $U\in \Gr_\bfe(X)$.
-Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
-Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
-Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
-Then it follows
-\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
-for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
-Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
-for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
-\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
-for every $t\in \C^\ast$.
-\end{proof}
-
-\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
-There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
-\end{lemma}
-\begin{proof}
-Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
-In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
-We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
-To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
-Set $c_{\alpha_1}=1$ and inductively
-\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
-Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
-In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
-\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
-
-First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
-Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
-which implies
-\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
-Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
-This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
-An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
-
-\end{proof}
-In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
-
-\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
-Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
- a torus action on $Gr_\bfe^Q(X)$ such that
-  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
-\end{theorem}
-\begin{proof}
-A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
-$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
-Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
-A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
-\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
-Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
-\end{proof}
-The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
-to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
-Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
-Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
-Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
-If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
-We obtain:
-\begin{corollary}
-Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
-\end{corollary}
-%\begin{corollary}
-%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
-%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
-%\end{corollary}
-
-\begin{question}
-  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
-\end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
-For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
-More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
-It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.
-
-The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
-In what follows we assume $n\ge2$.
-\begin{theorem}
-  \cite[Corollary 2.4]{rupel}
-  \label{th:dyck path recursion}
-  For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
-  \begin{enumerate}
-    \item $D_1$ consists of a single horizontal edge;
-    \item $D_2$ consists of $n$ consecutive horizontal edges followed by a vertical edge;
-    \item $D_m$, $m\ge3$, consists of $n-1$ copies of $D_{m-1}$ followed by a copy of $D_{m-1}$ with its first $D_{m-2}$ removed.
-  \end{enumerate}
-\end{theorem}
-
-We obtain the following as an immediate consequence.
-\begin{corollary}
-  \label{cor:short hooks}
-  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
-\end{corollary}
-\begin{proof}
-  We work by induction on $m\ge2$.
-  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
-  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
-\end{proof}
-
-For $m\ge2$ and $1\le k\le n-1$, write $D_m^{(k)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $k$ copies of $D_{m-1}$.
-Extending this notation we also set $D_m^{(0)}:=D_m$.
-\begin{remark}
-  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
-\end{remark}
-For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
-For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
-For $m\ge2$ and $1\le k\le n-1$, the maximal Dyck paths $D_{m-1,r}$, $k+1\le r\le n$, naturally identify with subpaths of $D_m^{(k)}$.
-
-We identify the edges of $D_m$ with the ordered set $E_m=\{1,\ldots,u_m+u_{m-1}\}$, where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
-Let $E_m=H_m\sqcup V_m$, where $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
-Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{r=1}^n E_{m-1,r}$, where $E_{m-1,r}$ denotes the edges of $D_{m-1,r}$.
-The set $E_{m-1,r}$ is naturally partitioned into its subsets $H_{m-1,r}$ and $V_{m-1,r}$ of horizontal and vertical edges.
-
-Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
-\begin{definition}
-  \label{def:compatibility}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
-  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
-  \begin{equation}
-    \label{eq:hgc}
-    e\ne v\qquad\text{and}\qquad |he\cap V_m|=n|he\cap S_H|
-  \end{equation}
-  or
-  \begin{equation}
-    \label{eq:vgc}
-    e\ne h\qquad\text{and}\qquad |ev\cap H_m|=n|ev\cap S_V|.
-  \end{equation}
-  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
-\end{definition}
-\begin{remark}
-  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.  Write $\cC_m^{(k)}$ for the set of all compatible pairs in $D_m^{(k)}$.
-\end{remark}
-
-The recursive structure of the maximal Dyck paths from Theorem~\ref{th:dyck path recursion} gives rise to a recursive characterization of compatible pairs.
-\begin{definition}
-  \cite[Definition 3.11]{rupel}
-  \label{def:piecewise compatibility}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$.
-\end{definition}
-\begin{remark}
-  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.
-\end{remark}
-
-To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
-For a horizontal edge $h\in H_m$ and a subset $S_H\subset H_m$, write $D(h;S_H)=he$ for the shortest subpath of $D_m$ for which $|he\cap V_m|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_{m-1}}$.
-The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
-Similarly, for a vertical edge $v\in V_m$ and a subset $S_V\subset V_m$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_m$ for which $|ev\cap H_m|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
-\begin{definition}
-  \cite[Definition 3.17]{rupel}
-  A horizontal edge $h_i\in H_m$, $m\ge3$, is called \emph{blocking} for a subset $S_H\subset H_m$ if $D(h_i;S_H)=h_iv_{u_{m-1}}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal with this property.
-
-  Suppose $S_H\subset H_m$ admits a blocking edge $h_i\in H_m$.
-  Then $S_H$ is \emph{left-justified at $h_i$} if there exists $k\ge i$ so that $S_H=\{h_i,h_{i+1},\ldots,h_k\}$.
-  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_{m-1}}\cap V_m|=n|h_iv_{u_{m-1}}\cap S_H|$.
-
-  A subset $S_V\subset V_m$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_{m-1}}$ so that $S_V\cap h_iv_{u_{m-1}}=\{v_s,v_{s-1},\ldots,v_{u_{m-1}}\}$.
-  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_{m-1}};S_V)=h_iv_{u_{m-1}}$ with $|h_iv_{u_{m-1}}\cap H_m|=n|h_iv_{u_{m-1}}\cap S_V|$.
-\end{definition}
-
-\begin{theorem}
-  \cite[Theorem 3.20 and Corollary 3.22]{rupel}
-  \label{th:blocking edge conditions}
-  For $m\ge3$, suppose $S_H\subset H_m$ and $S_V\subset V_m$ are piecewise compatible. 
-  Then the following hold:
-  \begin{enumerate}
-    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_m$.
-    \item Suppose $S_H$ admits a blocking edge $h_i\in H_m$ and $(S_H,S_V)$ is not compatible.
-      Then $S_H$ is left-justified at $h_i$ and $S_V$ is strongly right-justified with respect to $h_i$.
-      In addition the following hold:
-      \begin{enumerate}
-        \item If $m=3$, then $S_H\cap h_iv_{u_{m-1}}=\{h_i\}$.
-        \item If $m\ge4$, then $S_H$ is strongly left-justified at $h_i$.
-        \item If $m\ge5$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_m$.
-      \end{enumerate}
-  \end{enumerate}
-\end{theorem}
-
-\begin{corollary}
-  For $m\ge4$ and $0\le k\le n-1$, consider $S_H\subset H_m^{(k)}$ and $S_V\subset V_m^{(k)}$ so that $(S_H,S_V)$ is piecewise compatible.
-  Assume $\big(S_H^{(k+1)},S_V^{(k+1)}\big)\in\cC_m^{(k+1)}$.
-  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $V_m^{(k+1)}\subset S_V$.
-\end{corollary}
-\begin{proof}
-  We begin with the reverse implication.
-  First note that there are $(n-k)u_{m-1}-u_{m-2}$ horizontal edges and $(n-k)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{(k)}$. 
-  It follows that $V_{m-2}^{(k+1)}\sqcup V_m^{(k+1)}$ contains $n(n-k)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{(k+1)}\sqcup H_m^{(k+1)}$ contains $n(n-k)u_{m-2}-nu_{m-3}$ horizontal edges.
-
-  Assuming $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $S_V^{(k+1)}=V_m^{(k+1)}$, we have $S_V\cap V_{m-2}^{(k+1)}=\varnothing$ and $S_H\cap H_m^{(k+1)}=\varnothing$ by piecewise compatibility.
-  Let $h\in H_m^{(k)}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{(k+1)}$.
-  Then, since there are $(n-k)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{(k+1)}$, the local shadow path $D(h;S_H)$ contains $n\big((n-k)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
-  Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
-  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_{m-1}}$ and so $(S_H,S_V)$ is not compatible.
-
-  For the forward implication, we work by induction on $m\ge4$.
-  Consider a pair $(S_H,S_V)$ for $D_4^{(k)}$ as above which is not compatible.
-  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{(k)}$ for the blocking edge of $S_H$.
-  Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
-  Since $(S_H^{(k+1)},S_V^{(k+1)})$ is compatible, we must have $h\in H_{3,k}$.
-  But observe that $|V_m^{(k)}|=(n-k)n-1$ and so the divisibility condition above implies $h\in H_{3,k}^{(n-1)}$.
-  But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
-  Identifying $H_{3,k}^{(n-1)}$ with $H_2^{(1)}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{(k+1)}\subset H_2^{(1)}$.
-  Then by piecewise compatibility, the vertical edge of $H_2^{(1)}$ cannot be an element of $S_V$ and we must have $V_4^{(k+1)}\subset S_V$.
-  By piecewise compatibility again, this implies $H_4^{(k+1)}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{(k+1)}\subset S_H$.
-
-  To continue, let $(S_H,S_V)$ be a pair for $D_m$, $m\ge5$, which is not compatible.
-  Write $\varphi:H_{m-1}\to V_m$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_{m-1}$.
-  For any subset $T\subset H_{m-1}$, set $\varphi^*(T)=V_m\setminus\varphi(T)$.
-  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_{m-1}$ and subsets of $V_m$.
-  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_{m-1}$ is given, we refer the reder to \emph{loc. cit} for notation.
-  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
-  Thus by induction, we must have $H_{m-3}^{(k+1)}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{(k+1)}\subset\Omega^{-1}S_H$.
-  It follows from piecewise compatibility that $H_{m-1}^{(k+1)}\cap(\varphi^*)^{-1}S_V=\varnothing$.
-  But then by the definition of $\varphi^*$ we have $V_{m-2}^{(k+1)}\cap S_V=\varnothing$ and $S_V^{(k+1)}=V_m^{(k+1)}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
-  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
-  But this can only occur if $H_{m-2}^{(k+1)}\subset S_H$ since $H_m^{(k+1)}\cap S_H=\varnothing$ by piecewise compatibility.
-\end{proof}
-
-The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{lee-li-zelevinsky} and the categorification of these variables using representations of $K(n)$ \cite{cc,caldero-keller}.
-\begin{theorem}\cite{lee-li-zelevinsky}
-  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
-\end{theorem}
-
-Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
 \section{Combinatorial description of non-empty cells}
@@
 
+\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
+For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
+More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
+It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.
+
+The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
+In what follows we assume $n\ge2$.
+\begin{theorem}
+  \cite[Corollary 2.4]{rupel}
+  \label{th:dyck path recursion}
+  For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
+  \begin{enumerate}
+    \item $D_1$ consists of a single horizontal edge;
+    \item $D_2$ consists of $n$ consecutive horizontal edges followed by a vertical edge;
+    \item $D_m$, $m\ge3$, consists of $n-1$ copies of $D_{m-1}$ followed by a copy of $D_{m-1}$ with its first $D_{m-2}$ removed.
+  \end{enumerate}
+\end{theorem}
+
+We obtain the following as an immediate consequence.
+\begin{corollary}
+  \label{cor:short hooks}
+  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
+\end{corollary}
+\begin{proof}
+  We work by induction on $m\ge2$.
+  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
+  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
+\end{proof}
+
+For $m\ge2$ and $1\le k\le n-1$, write $D_m^{(k)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $k$ copies of $D_{m-1}$.
+Extending this notation we also set $D_m^{(0)}:=D_m$.
+\begin{remark}
+  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
+\end{remark}
+For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
+For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
+For $m\ge2$ and $1\le k\le n-1$, the maximal Dyck paths $D_{m-1,r}$, $k+1\le r\le n$, naturally identify with subpaths of $D_m^{(k)}$.
+
+We identify the edges of $D_m$ with the ordered set $E_m=\{1,\ldots,u_m+u_{m-1}\}$, where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
+Let $E_m=H_m\sqcup V_m$, where $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
+Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{r=1}^n E_{m-1,r}$, where $E_{m-1,r}$ denotes the edges of $D_{m-1,r}$.
+The set $E_{m-1,r}$ is naturally partitioned into its subsets $H_{m-1,r}$ and $V_{m-1,r}$ of horizontal and vertical edges.
+
+Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
+\begin{definition}
+  \label{def:compatibility}
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
+  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
+  \begin{equation}
+    \label{eq:hgc}
+    e\ne v\qquad\text{and}\qquad |he\cap V_m|=n|he\cap S_H|
+  \end{equation}
+  or
+  \begin{equation}
+    \label{eq:vgc}
+    e\ne h\qquad\text{and}\qquad |ev\cap H_m|=n|ev\cap S_V|.
+  \end{equation}
+  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
+\end{definition}
+\begin{remark}
+  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.  Write $\cC_m^{(k)}$ for the set of all compatible pairs in $D_m^{(k)}$.
+\end{remark}
+
+The recursive structure of the maximal Dyck paths from Theorem~\ref{th:dyck path recursion} gives rise to a recursive characterization of compatible pairs.
+\begin{definition}
+  \cite[Definition 3.11]{rupel}
+  \label{def:piecewise compatibility}
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$.
+\end{definition}
+\begin{remark}
+  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.
+\end{remark}
+
+To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
+For a horizontal edge $h\in H_m$ and a subset $S_H\subset H_m$, write $D(h;S_H)=he$ for the shortest subpath of $D_m$ for which $|he\cap V_m|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_{m-1}}$.
+The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
+Similarly, for a vertical edge $v\in V_m$ and a subset $S_V\subset V_m$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_m$ for which $|ev\cap H_m|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
+\begin{definition}
+  \cite[Definition 3.17]{rupel}
+  A horizontal edge $h_i\in H_m$, $m\ge3$, is called \emph{blocking} for a subset $S_H\subset H_m$ if $D(h_i;S_H)=h_iv_{u_{m-1}}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal with this property.
+
+  Suppose $S_H\subset H_m$ admits a blocking edge $h_i\in H_m$.
+  Then $S_H$ is \emph{left-justified at $h_i$} if there exists $k\ge i$ so that $S_H=\{h_i,h_{i+1},\ldots,h_k\}$.
+  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_{m-1}}\cap V_m|=n|h_iv_{u_{m-1}}\cap S_H|$.
+
+  A subset $S_V\subset V_m$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_{m-1}}$ so that $S_V\cap h_iv_{u_{m-1}}=\{v_s,v_{s-1},\ldots,v_{u_{m-1}}\}$.
+  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_{m-1}};S_V)=h_iv_{u_{m-1}}$ with $|h_iv_{u_{m-1}}\cap H_m|=n|h_iv_{u_{m-1}}\cap S_V|$.
+\end{definition}
+
+\begin{theorem}
+  \cite[Theorem 3.20 and Corollary 3.22]{rupel}
+  \label{th:blocking edge conditions}
+  For $m\ge3$, suppose $S_H\subset H_m$ and $S_V\subset V_m$ are piecewise compatible. 
+  Then the following hold:
+  \begin{enumerate}
+    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_m$.
+    \item Suppose $S_H$ admits a blocking edge $h_i\in H_m$ and $(S_H,S_V)$ is not compatible.
+      Then $S_H$ is left-justified at $h_i$ and $S_V$ is strongly right-justified with respect to $h_i$.
+      In addition the following hold:
+      \begin{enumerate}
+        \item If $m=3$, then $S_H\cap h_iv_{u_{m-1}}=\{h_i\}$.
+        \item If $m\ge4$, then $S_H$ is strongly left-justified at $h_i$.
+        \item If $m\ge5$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_m$.
+      \end{enumerate}
+  \end{enumerate}
+\end{theorem}
+
+\begin{corollary}
+  For $m\ge4$ and $0\le k\le n-1$, consider $S_H\subset H_m^{(k)}$ and $S_V\subset V_m^{(k)}$ so that $(S_H,S_V)$ is piecewise compatible.
+  Assume $\big(S_H^{(k+1)},S_V^{(k+1)}\big)\in\cC_m^{(k+1)}$.
+  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $V_m^{(k+1)}\subset S_V$.
+\end{corollary}
+\begin{proof}
+  We begin with the reverse implication.
+  First note that there are $(n-k)u_{m-1}-u_{m-2}$ horizontal edges and $(n-k)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{(k)}$. 
+  It follows that $V_{m-2}^{(k+1)}\sqcup V_m^{(k+1)}$ contains $n(n-k)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{(k+1)}\sqcup H_m^{(k+1)}$ contains $n(n-k)u_{m-2}-nu_{m-3}$ horizontal edges.
+
+  Assuming $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $S_V^{(k+1)}=V_m^{(k+1)}$, we have $S_V\cap V_{m-2}^{(k+1)}=\varnothing$ and $S_H\cap H_m^{(k+1)}=\varnothing$ by piecewise compatibility.
+  Let $h\in H_m^{(k)}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{(k+1)}$.
+  Then, since there are $(n-k)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{(k+1)}$, the local shadow path $D(h;S_H)$ contains $n\big((n-k)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
+  Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
+  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_{m-1}}$ and so $(S_H,S_V)$ is not compatible.
+
+  For the forward implication, we work by induction on $m\ge4$.
+  Consider a pair $(S_H,S_V)$ for $D_4^{(k)}$ as above which is not compatible.
+  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{(k)}$ for the blocking edge of $S_H$.
+  Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
+  Since $(S_H^{(k+1)},S_V^{(k+1)})$ is compatible, we must have $h\in H_{3,k}$.
+  But observe that $|V_m^{(k)}|=(n-k)n-1$ and so the divisibility condition above implies $h\in H_{3,k}^{(n-1)}$.
+  But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
+  Identifying $H_{3,k}^{(n-1)}$ with $H_2^{(1)}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{(k+1)}\subset H_2^{(1)}$.
+  Then by piecewise compatibility, the vertical edge of $H_2^{(1)}$ cannot be an element of $S_V$ and we must have $V_4^{(k+1)}\subset S_V$.
+  By piecewise compatibility again, this implies $H_4^{(k+1)}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{(k+1)}\subset S_H$.
+
+  To continue, let $(S_H,S_V)$ be a pair for $D_m$, $m\ge5$, which is not compatible.
+  Write $\varphi:H_{m-1}\to V_m$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_{m-1}$.
+  For any subset $T\subset H_{m-1}$, set $\varphi^*(T)=V_m\setminus\varphi(T)$.
+  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_{m-1}$ and subsets of $V_m$.
+  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_{m-1}$ is given, we refer the reder to \emph{loc. cit} for notation.
+  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
+  Thus by induction, we must have $H_{m-3}^{(k+1)}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{(k+1)}\subset\Omega^{-1}S_H$.
+  It follows from piecewise compatibility that $H_{m-1}^{(k+1)}\cap(\varphi^*)^{-1}S_V=\varnothing$.
+  But then by the definition of $\varphi^*$ we have $V_{m-2}^{(k+1)}\cap S_V=\varnothing$ and $S_V^{(k+1)}=V_m^{(k+1)}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
+  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
+  But this can only occur if $H_{m-2}^{(k+1)}\subset S_H$ since $H_m^{(k+1)}\cap S_H=\varnothing$ by piecewise compatibility.
+\end{proof}
+
+The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{lee-li-zelevinsky} and the categorification of these variables using representations of $K(n)$ \cite{cc,caldero-keller}.
+\begin{theorem}\cite{lee-li-zelevinsky}
+  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
+\end{theorem}
+
+Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+
 \begin{thebibliography}{10}

### 2017-11-19 Grassmannian_cells.tex
GL_n actions

@@
 \setcounter{MaxMatrixCols}{20}
+
+\hyphenation{endo-functors}
+
 \title{Cell Decompositions for Rank Two Quiver Grassmannians}
@@
 Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
-These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}.
-
--something about categorification and quiver Grassmannians
+These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
+
+For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{lee-li-zelevinsky}.
+The confluence of these results gives rise to a combinatorial construction for the Euler characteristics of certain quiver Grassmannians.
+Our main result is a geometric explanation for this correspondence by constructing a decomposition of the quiver Grassmannians into affine cells which are labeled by compatible pairs.
+
 -something about compatible pairs and combinatorial construction of cluster variables
@@
   \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
-  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, in particular $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
+  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
 \end{itemize}
@@
 \begin{lemma}
-  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta:g.M\to g.N$ for any $g\in GL_n(\CC)$.
+  \label{le:hom equivariance}
+  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
+  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
 \end{lemma}
@@
   Then for $g=(g_{ij})\in GL_n(\CC)$, we have
-  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij} \theta_2\circ M_{a_j}=\sum\limits_{j=1}^n g_{ij} M_{a_j}\circ\theta_1=N'_{a_i}\circ\theta_1\]
-  for $1\le i\le n$ so that $\theta$ gives a morphism from $g.M$ to $g.N$. 
+  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
+  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
+\end{proof}
+\begin{corollary}
+  \label{cor:indecomposability}
+  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
+\end{corollary}
+\begin{proof}
+  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
+  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
 \end{proof}
@@
 Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.
-%, but the vertices $1$ and $2$ are exchanged.
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
 With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
@@
 \begin{lemma}
+  \footnote{Is this true?}
   The reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ are $GL_n(\CC)$-equivariant. 
@@
 Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
+The following is well-known.
 \begin{theorem}
+  \label{th:rigids}
   For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
@@
 \end{remark}
-
-Write $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.  
-For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
-\begin{equation}
-  \label{eq:AR sequence}
-  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
-\end{equation}
-where the right-hand morphism is the natural evaluation map.
+\begin{corollary}
+  \label{cor:preprojective stability}
+  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
+\end{corollary}
+\begin{proof}
+  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
+  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
+\end{proof}
+For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.
+
+Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$ and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
+Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
 
@@
 Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
+Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
+For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
+\begin{lemma}
+  \label{le:transitivity}
+  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $Gr_d(H_m)$.
+\end{lemma} 
+\begin{proof}
+
+\end{proof}
 \begin{lemma}
@@
 \end{lemma}
-
 %%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%
-%\begin{proof}
-%  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
-%  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
-%\end{proof}
+\begin{proof}
+  \footnote{This needs to be cleaned up, the proof seems false as written.}
+  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
+  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
+\end{proof}
+
+In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
+Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
+\begin{lemma}
+  \label{le:g equalities}
+  For any $g\in GL_n(\CC)$, the subrepresentation $g.(P_m\otimes V)\subset g.P_{m+1}$ is equal to $g.P_m\otimes V^g\subset g.P_{m+1}$ and the subrepresentation $\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)\subset P_{m+1}$ is equal to $P_m\otimes g.V\subset P_{m+1}$.
+\end{lemma}
+\begin{proof}
+  The first equality is immediate from the definitions.
+  The second equality also follows from the definitions by observing that $\phi_{m+1,g}(P_m\otimes g.V)=g.P_m\otimes V^g$.
+\end{proof}
+
+Following Lemma~\ref{le:injective evaluation maps} we define the following.
+\begin{definition}
+  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  \begin{equation}
+    \label{eq:truncated preprojectives}
+    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
+  \end{equation}
+\end{definition}
+\begin{remark}
+  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
+\end{remark}
+
+Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
+\begin{theorem}
+  The quiver Grassmannian $Gr_\bfe(P_{m+1}^V)$ is smooth for each dimension vector $\bfe$ and each $V\in Gr(H_m)$.
+  Moreover, for $V,W\in Gr_d(H_m)$, we have $Gr_\bfe(P_{m+1}^V)\cong Gr_\bfe(P_{m+1}^W)$ for all dimension vectors $\bfe$.
+\end{theorem}
+\begin{proof}
+  Both claims are proven via the same geometric construction.
+  For each dimension vector $\bfe$, there is a smooth variety
+  \[X_{\bfe,m}=\{(\tilde E,V):V\in Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
+  Under the natural projection $\pi:X_{\bfe,m}\to Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $Gr_\bfe(P_{m+1}^V)$.
+  In particular, this implies $Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in Gr_d(H_m)$.
+
+  The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.
+  Indeed, by Lemma~\ref{le:g equalities} we have 
+  \[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
+  Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $Gr_\bfe(P_{m+1}^V)$ and $Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in Gr_d(H_m)$.
+\end{proof}
 
@@
 %\end{remark}
+
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
+\begin{equation}
+  \label{eq:AR sequence}
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+\end{equation}
+where the right-hand morphism is the natural evaluation map.
 \begin{corollary}
@@
 \end{proof}
-
-\begin{definition}
-  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
-  \begin{equation}
-    \label{eq:truncated preprojectives}
-    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
-  \end{equation}
-\end{definition}
-\begin{remark}
-  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
-\end{remark}
 
@@
 \begin{lemma}\label{directsums}
+  \footnote{This can be proved on the quiver itself.}
   If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.

### 2017-11-20 Grassmannian_cells.tex
Consequences for F-polynomials and cell decompositions

@@
 \newcommand{\ZZ}{\mathbb{Z}}
+\newcommand{\NN}{\mathbb{N}}
+
 \newcommand{\Ext}{\operatorname{Ext}}
@@
  a torus action on $Gr_\bfe^Q(X)$ such that
-  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{[\hat\bfe]} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all equivalence classes of dimension vectors compatible with $\bfe$.
+  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
 \end{theorem}
@@
 Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{[\hat\bfe^{(k-1)}]} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{[\hat\bfe^{(k)}]} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{[\tilde\bfe]} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all equivalence classes of dimension vectors compatible with $\bfe$.
+  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
 \end{corollary}
@@
 %\end{corollary}
-
-\begin{question}
-  What are the ranks of the bundles over the fixed point set?  Poincar\'e polynomials?
-\end{question}
+Define the $F$-polynomial of a representation $X$ by 
+$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^e\in\ZZ[x_q\mid q\in Q_0].$$
+
+\begin{corollary}\label{fpoly}
+Let $X$ be a representation which can be lifted to the universal covering quiver.
+\begin{enumerate}
+\item 
+If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{\tilde \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(q,w)}\mid q\in Q_0,w\in W_Q]\to\ZZ[x_q\mid q\in Q_0]$ given by $S(x_{(q,w)})=x_q$ for all $q\in Q_0$ and $w\in W_Q$.
+\end{enumerate} 
+\end{corollary}
+An important special case for this is the case of exceptional representations.
+In this case the quiver Grassmannians $\Gr_\tbfe(X)$ are smooth by \cite[Corollary 4]{cr}.
+Moreover, every exceptional representation is a tree module by \cite{rin1} which means that it can be lifted to the universal covering.
 
@@
     \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
+
   \end{enumerate}
@@
 \end{proof}
+
+%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
+
 If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$ and $\tilde P_m^{(0)}=\tilde P_m$ respectively.
@@
 \end{proof}
+
 The short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$ induces a map between quiver Grassmannians
@@
 
-\begin{theorem}
+\begin{theorem}\label{celldec}
   Every quiver Grassmannian of a preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
@@
 \end{proof}
-\begin{question}
-  cells of $Gr^{\tilde Q}_\tbfe(\tilde P_m)$ are in one-to-one correspondence with certain tuples of subgraphs for smaller $\tilde P_\ell^{i_1,\ldots,i_k}$
-\end{question}
+
+As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{\udim P_m{(k)}}$.
+The description of the non-empty fibres in Proposition \ref{fibers} together with Corollary \ref{fpoly} and Theorem \ref{celldec} yield the following:
+\begin{corollary}
+For $m\geq 2$ and $0\leq k\leq n-2$, we have 
+$$F_{\udim P_m^{(k)}}=F_{\udim P_m^{(k+1)}}F_{\udim P_{m-1}}-x^{\udim P_{m}^{(k)}}F_{\udim P_{m-2}^{(k)}}.$$
+\end{corollary}
 
@@
 \bibitem{llz} K. Lee, L. Li, A. Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
+\bibitem{rin1} Claus Michael Ringel. Exceptional modules are tree modules. \textit{Linear algebra and its Applications}, 275/276:471-493, 1998.
 \bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).

### 2017-11-20 Grassmannian_cells.tex
Removed some statements about GL_n action

--- 2017-11-19 Grassmannian_cells.tex
@@
 
-\begin{lemma}
-  \footnote{Is this true?}
-  The reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ are $GL_n(\CC)$-equivariant. 
-\end{lemma}
+While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
+\begin{lemma}
+  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
+\end{lemma}
+\begin{proof}
+  We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
+  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{a_i})$, where $M'_2$ fits into the following exact sequence:
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
+  and $M'_{a_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
+  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,M''_{a_i})$ with 
+  \[M''_{a_i}=\sum\limits_{j=1}^n g_{ij}M'_{a_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
+  In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
+  i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
+\end{proof}
 
@@
 \end{remark}
-\begin{corollary}
-  \label{cor:preprojective stability}
-  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
-\end{corollary}
-\begin{proof}
-  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
-  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
-\end{proof}
-For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.
-
-Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$ and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
-Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
-
+%\begin{corollary}
+%  \label{cor:preprojective stability}
+%  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
+%\end{corollary}
+%\begin{proof}
+%  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
+%  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
+%\end{proof}
+%For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.
+
+Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
+%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
 Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
 Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
+%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
 For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
-\begin{lemma}
-  \label{le:transitivity}
-  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $Gr_d(H_m)$.
-\end{lemma} 
-\begin{proof}
-
-\end{proof}
+%\begin{lemma}
+%  \label{le:transitivity}
+%  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $Gr_d(H_m)$.
+%\end{lemma} 
+%\begin{proof}
+%  The map $\theta\mapsto g.\theta$ for $\theta\in H_m$ induces a group homomorphism $GL_n(\CC)\to GL(H_m)$ which we denote by $g\mapsto\tilde g_m$.
+%  We claim that this homomorphism is surjective which immediately implies the result.
+%
+%  We work by induction on $m$.
+%  Suppose $GL_n(\CC)\to GL(H_m)$ is surjective.
+%
+%\end{proof}
 \begin{lemma}
@@
 In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
-Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
-\begin{lemma}
-  \label{le:g equalities}
-  For any $g\in GL_n(\CC)$, the subrepresentation $g.(P_m\otimes V)\subset g.P_{m+1}$ is equal to $g.P_m\otimes V^g\subset g.P_{m+1}$ and the subrepresentation $\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)\subset P_{m+1}$ is equal to $P_m\otimes g.V\subset P_{m+1}$.
-\end{lemma}
-\begin{proof}
-  The first equality is immediate from the definitions.
-  The second equality also follows from the definitions by observing that $\phi_{m+1,g}(P_m\otimes g.V)=g.P_m\otimes V^g$.
-\end{proof}
-
+%Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
+%\begin{lemma}
+%  \label{le:g equalities}
+%  For any $g\in GL_n(\CC)$, the subrepresentation $g.(P_m\otimes V)\subset g.P_{m+1}$ is equal to $g.P_m\otimes V^g\subset g.P_{m+1}$ and the subrepresentation $\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)\subset P_{m+1}$ is equal to $P_m\otimes g.V\subset P_{m+1}$.
+%\end{lemma}
+%\begin{proof}
+%  The first equality is immediate from the definitions.
+%  The second equality also follows from the definitions by observing that $\phi_{m+1,g}(P_m\otimes g.V)=g.P_m\otimes V^g$.
+%\end{proof}
 Following Lemma~\ref{le:injective evaluation maps} we define the following.
@@
 
-Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
+%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
 \begin{theorem}
@@
 \begin{proof}
-  Both claims are proven via the same geometric construction.
-  For each dimension vector $\bfe$, there is a smooth variety
-  \[X_{\bfe,m}=\{(\tilde E,V):V\in Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
-  Under the natural projection $\pi:X_{\bfe,m}\to Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $Gr_\bfe(P_{m+1}^V)$.
-  In particular, this implies $Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in Gr_d(H_m)$.
-
-  The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.
-  Indeed, by Lemma~\ref{le:g equalities} we have 
-  \[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
-  Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $Gr_\bfe(P_{m+1}^V)$ and $Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in Gr_d(H_m)$.
+  \footnote{The proof using moduli spaces needs to be written}
+  %Both claims are proven via the same geometric construction.
+  %For each dimension vector $\bfe$, there is a smooth variety
+  %\[X_{\bfe,m}=\{(\tilde E,V):V\in Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
+  %Under the natural projection $\pi:X_{\bfe,m}\to Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $Gr_\bfe(P_{m+1}^V)$.
+  %In particular, this implies $Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in Gr_d(H_m)$.
+
+  %The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.
+  %Indeed, by Lemma~\ref{le:g equalities} we have 
+  %\[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
+  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $Gr_\bfe(P_{m+1}^V)$ and $Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in Gr_d(H_m)$.
 \end{proof}

### 2017-11-20 Grassmannian_cells.tex
Added to abstract

@@
 \begin{abstract}
-  We prove that all quiver Grassmannians for preprojective and preinjective representations of a generalized Kronecker quiver admit a cell decomposition.  
+  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
+  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
+  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established as well as for all indecomposable representations in their Auslander-Reiten components.
   We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 

### 2017-12-08 Grassmannian_cells.tex
no changes, just to sync
fixed latex error
Edited Section 5
Continue with Lemma 5.6 on the weekend...

--- 2017-11-20 Grassmannian_cells.tex
@@
 \usepackage{extarrows}
+\usepackage{verbatim}
 \input xy
@@
 \newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
+\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
 \newcommand{\Sc}[2]{\langle #1,#2\rangle}
@@
 \setcounter{MaxMatrixCols}{20}
-
+\newcommand{\vs}{\vspace{0.2cm}}
 \hyphenation{endo-functors}
@@
 \end{theorem}
-\begin{proof}\footnote{sketch, double-check}
-
-As $X$ and $Y$ are projective, they are compact.
+%\begin{proof}\footnote{sketch, double-check}
+
+%As $X$ and $Y$ are projective, they are compact.
 As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
@@
 
-\end{proof}
+%\end{proof}
 
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}
+\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
   \label{rem:reflection recursion}
@@
 \noindent 
-Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$.
-Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
-$w.(q,w')=(q,ww')$.
-Up to this action a lift $\tilde P_m$ of $P_m$ is unique.
-On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$.
-Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$.
-In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
-\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]
-
-Using this notation, we obtain the following lemma:
-\begin{lemma}
+We fix a natural number $n\geq 3$.
+We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
+For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_m)_{i,w}=0$ if $(i,w)\neq (1,1)$.
+Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
+Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
+we have
+\begin{align}\label{recursive}\tilde P_m=(\tilde\Sigma_1 \tilde P_{m-1})^T,\quad\tilde P_{m+1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\footnote{odd and even live on different components}\end{align}
+Recall that we obtain the Auslander-Reiten translate $\tau^{-1}\tilde P_m$ by applying the reflection functor to the sinks twice where the sinks become sources after each step. 
+\begin{remark}\begin{enumerate}
+\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
+$w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.
+Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
+\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,0)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
+\end{enumerate}
+\end{remark}
+The next step is to construct filtrations of $\tilde P_m$ by smaller preprojective $w.\tilde P_{l}$ for $l<m$ and certain $w\in W_Q$.
+To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
+
+Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. More precisely, we have 
+$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l+1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
+for all $l\geq 1$ and for $i=1,\ldots,n$.
+This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
+In the following, we sometimes identify the arrows with the numbers $1,\ldots,n$.
+
+We need some more notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
+With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+More detailed, we obtain a sequence of preprojective representations
+$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$
+
+Let
+$$I^n_l:=\{(i_1,\ldots,i_{l})\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.$$
+As we fixed the number of arrows, we drop the $n$ in what follows.
+For $\ui=(i_1,\ldots,i_{n-1})\in I_{n-1}$, let $i^c\in \{1,\ldots,n\}$ and $\ui^c=(i^c)$ where $i^c\neq i_j$ for $j=1,\ldots,n-1$.
+Clearly, $\ui^c$ is uniquely determined by $\ui$.
+
+Let $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ be a sequence with $\underline{i_1}\in I_{n-1}$, $\underline{i_2},\ldots,\underline{i_{r-1}}\in I_{n-2}$ and $\underline{i_r}\in I_s$ for $s\leq n-2$.
+Define $i_1^c$ as before and for $k\geq 2$ let $i_k^c\in\{1,\ldots,n\}$ be the unique number such that $i_k^c\neq i_{k,j}$ for $j=1,\ldots,n-2$ and $i_k^c\neq i_{k-1}^c$.
+We say that $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ is admissible if
+$$ i_{k,j}\neq i_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,j=1,\ldots,n-2\text{ and for }j=1,\ldots,s\text{ if }k=r.$$
+
+For $\ui\in I_{s}$ with $s\leq n-1$, there exist unique exact sequences of the form
+\[\ses{\bigoplus_{j=1}^s\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{\ui}},\quad\quad\ses{\tilde P_{m-1,i_s}}{\tilde P_{m}^{(i_1,\ldots,i_{s-1})}}{\tilde P_{m}^{\ui}}\]
+where the $\tilde P_m^{\ui}$ are truncated preprojectives (as defined in the last section).
+The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf i}=(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$.
+We define the admissible sequence $\delta {\bf i}$ (of length $r-1$) by
+\[\delta {\bf i}:=((i_1^c,\underline{i_2}),\ldots,\underline{i_r}).\]
+We recursively define $\delta^l{\bf i}$ for $l=1,\dots,r-1$.
+%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
+Note that we have $\delta\ui=(i^c)$ for $\ui\in I_{n-1}$.
+
+\begin{lemma}The following holds:
   \label{le:preprojective lifts}
   \begin{enumerate}
-    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
+    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{j=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$ is one-dimensional;
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal;
-    \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
-
+    \item The representations $\tilde P_{m,j}$ are pairwise orthogonal, i.e. for $j\neq i$ we have $$\Hom(\tilde P_{m-1,i},\tilde P_{m-1,j})=\Ext(\tilde P_{m-1,i},\tilde P_{m-1,j})=0;$$
+    \item If $\ui\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\ui}\cong \tilde P_{m-1,i^c}^{\ui^c}= P_{m-1,i^c}/P_{m-2,(i^c,i^c)}$.
+		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf i:=(\underline{i_1},\ldots,\underline{i_r})$ be an admissible sequence.
+Let ${\bf i}(l):=(\underline{i_1},\ldots,\underline{i_l})$ for $l=2,\ldots,r-1$.
+Then we recursively have
+		\[\tilde P_{m-l,(i_1^c,\ldots,i_l^c)}^{\delta^l{\bf i(l)}}=\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}\bf i(l)}\]
+		for $l=1,\ldots,r$.
+Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf i}_{m-r+1}:=\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}/\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{(i_{r-1}^c,i_{r,1},\ldots,i_{r,s})}$$ with each admissible sequence ${\bf i}$.
   \end{enumerate}
@@
 \begin{proof}
-The first statement follows from Theorem \ref{covering}. The second part follows for instance recursively by applying BGP-reflections.
-
-For the third part, we proceed by induction.
+The first statement follows from Theorem \ref{covering}. For $m=2$, the second part is obvious. For $m\geq 3$, it then follows by applying the identities (\ref{recursive}).
+
+To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
+\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-1}\tilde P_{m-1,i_j}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\ui}\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,i^c}\ar[u]\ar[r]& \tilde P_{m}^{\ui}\ar[r]\ar@{=}[u]& 0}\]
+
+%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
+For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,i^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(i^c,i^c)}$.
+Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,i^c}^{\ui^c}$.
+Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
+
+The forth statement is now obtained recursively when initially considering the diagram from above replacing $\ui$ by $\underline{i_1}$.
+
+We have $\delta^{l-1}{\bf i}(l)=(i_{l-1}^c,i_{l,1},\ldots,i_{l,n-1})$. We use the third statement in order to successively obtain commutative diagrams
+\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-2}\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})}\ar[r] &  \tilde P^{(i_{l-1}^c)}_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}\ar[r] & \tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}{\bf i}(l)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-(l+1),(i_1^c,\ldots,i_{l}^c,i_l^c)} \ar[r]\ar[u] & \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}\ar[u]\ar[r]& \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}^{(\underline{i_{l}^c)}}\ar[r]\ar@{=}[u]& 0}\]
+Now we have $\delta^l{\bf i}(l)=(i_l^c)$.	Finally, we consider the short exact sequence:
+
+\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{s}\tilde P_{m-r,(i_1^c,\ldots,i_{r-1}^c,i_{r,j})}\ar[r] &  \tilde P^{(i_{r-1}^c)}_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{{\bf i}}\ar[r] & 0 }.\]
+As $\Hom(\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})},\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)})=k$ for all $l=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf i}$ is uniquely determined.
+	\end{proof}
+We denote the quotient morphism by $\pi_m^{\bf i}:\tilde P_m\to \tilde P_{m-r+1}^{\bf i}$.
+It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{(1,\ldots,l)}$ where $l\leq n-1$ and $j_k\neq i_1^c$ for $k=1,\ldots, l$.
+We also denote the quotient morphism from $\tilde P_m^{(j_1,\ldots,j_l)}$ to $\tilde P_{m-r+1}^{\bf i}$ by $\pi_m^{\bf i}$.
+
+For convenience, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$, denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+But we point out that the next statements also hold for general sequences $(j_1,\ldots,j_l)$ with the same proof.
+We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
+\begin{lemma}\label{le:subrep}
+   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(1,\ldots,l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}
+
+\end{lemma}
+\begin{proof}
+
+We proceed by induction.
 Clearly $\tilde P_m$ has only preprojective subrepresentations.
 We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
-If $U\subsetneq P_m^{(i_1,\ldots,i_k)}$ were not preprojective, the embedding would not factor through $P_m^{(i_1,\ldots,i_{k-1})}$ by induction hypothesis.
+Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
+Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
 Thus we get a commutative diagram
 
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
-because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
-Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason.
-Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
-\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
-because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom sequence does not split.
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
+because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
+We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
+
+As the sequence does not split, this shows that $U'$ is an indecomposable  (reference) preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$.
+Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
+Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
 But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
@@
 
-If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$ and $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-
+DO NOT NEED THIS-------FROM HERE----
 \begin{lemma}\label{directsums}
@@
 \end{proof}
-\begin{lemma}\label{AR}
-Let $m\geq 3$ and $n\geq k\geq 1$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
+----TO HERE----DO NOT NEED THIS----
+
+\begin{lemma}\label{AR}\footnote{special case $m=3$}
+Let $m\geq 4$ and $n-1\geq l\geq 1$. Consider the short exact sequence $$\sesm{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}{\pi^{(1,\ldots,l)}_m}$$. The following holds:
 \begin{enumerate}
-\item There exists a short exact sequence 
-\[\ses{\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}}{\tilde P_{m,k}}{\tau\tilde P_{m+1}^{(k)}}\]
-where $\tau$ denotes the Auslander-Reiten translate where
-$\tau\tilde P_{m+1}^{(k)}=\tilde P_{m-1}^{(k)}$. 
-\item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
-\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$.
+\item We have $\tau\tilde P_{m}^{(l)}=\tilde P_{m-2}^{(l)}$.
+\item For $m\geq 4$, $l\leq n-1$, there exists a short exact sequences 
+\[\sesm{\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{m-3,(l,l,j)}}{\tilde P_{m-1,l}}{\tau\tilde P_{m}^{(l)}}{\pi^{\bf i_l}_{m-1,l}}\]
+where ${\bf i}_l=((1,\ldots,l-1,\hat l,l+1,\ldots,n),(1,\ldots,l-1)).$
+
+\item Moreover, we have $\Ext(\tilde P_{m}^{(l)},\tilde P_{m-1,l})\cong \Ext(\tilde P_{m-1}^{(l)},\tau\tilde P_{m}^{(l)})=\kk$, $\Hom(\tilde P_{m}^{(l)},\tau\tilde P_{m}^{(l)})=0$. 
+\item We have $\tau\tilde P_{m}^{(l)}\in ~^\perp(\tilde P_{m}^{(l)})$.
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 \begin{proof}
-We have $\mathcal  S \tilde P_m=\tilde P_{m+1}$ (up to permutation).
-This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$.
-In this case, the first statement is straightforward as well as the third one (insert a diagram).
-
-It is also straightforward to check that $\bigoplus_{j\neq k}\tilde P_{2,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{1,(k,k,j)}\in (\tilde P_{4}^{(k)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(k)},\tilde P_{3,k})=0$ which yields the second claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(k)},\underline{\quad})$.
-
-\end{proof}
-
-The short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$ induces a map between quiver Grassmannians
-$$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^{(k)}).$$
-Let $P(m,k):=\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}$.
+Using the identities (\ref{recursive}), it suffices to prove the first statement for $m=4$ and arbitrary $1\leq l\leq n-1$.
+The representation $\tilde P_2$ is given determined by the following quiver and dimension vector:
+
+\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
+The quiver of $P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+Using this notation the support of $\tilde P_4$ is given by
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the numbers correspond to the dimensions of the respective vertices.
+Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
+The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
+Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar^{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar^{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar^{a_n}[lllu]	&&&&}\]
+
+%\begin{tikzpicture}[scale=1]
+%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\end{tikzpicture}
+
+Note that, starting with these cases, we only reflect at sinks and no representation appearing is isomorphic to the simple injective representation $S_2$.
+
+In this case, the first two statements and the last one are straightforward\footnote{make this explicit, insert diagrams}.
+
+It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(l)},\tilde P_{3,l})=0$ which yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(l)},\underline{\quad})$.
+
+\end{proof}
+
+The short exact sequence $\ses{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}$ induces a map between quiver Grassmannians
+$$\Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(l-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{(l)}).$$
+Let $P(m,l):=\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-1,(l,j)}\oplus \bigoplus_{j=1}^l\tilde P_{m-2,(l,l,j)}$.
 
@@
   0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
-By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
+%By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
 Using this notation, we obtain:
@@
 \end{proposition}
-\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
+\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
 But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
@@
 \begin{theorem}\label{cellscover}
-Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
+Let $\ui=(i_1,\ldots,i_k)$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ admits a cell decomposition into affine spaces.
 \end{theorem}
 \begin{proof}
+
+In order to prove the claim, we prove the more general statement:
+\vs
+
+\noindent {\bf Claim.} Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})$ has a cell decomposition which is compatible with a fixed quotient map $\pi_m^{\bf j}$ in the following way:
+ Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ such that $\pi_m^{\bf j}(U)\neq 0.$
+Then we have $\pi_m^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
+\vs
+
+We proceed by induction on $m$ and $k$. If $m=1$ or $m=2$, the statement is straightforward as all quiver Grassmannians are points. Now let $m\geq 3$.
+The short exact sequence $$\sesm{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{\ui}}{\pi_m^{\ui}}$$ induces a map between quiver Grassmannians
+$$\Psi_1:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\ui}).$$
+Let $P(m,\ui)=\bigoplus_{\substack{1\leq j\leq n\\j\neq i_k}}\tilde P_{m-2,(i_k,j)}\oplus \bigoplus_{j=1}^{k-1}\tilde P_{m-3,(i_k,i_k,i_j)}$. Then we obtain a short exact sequence
+$$\sesm{P(m,\ui)}{\tilde P_{m-1,i_k}}{\tau\tilde P_{m}^{\ui}}{\pi^{\bf j}_m}$$
+with
+$${\bf j}=((1,\ldots,i_k-1,\hat i_k,i_k+1,\ldots,n),(i_1,\ldots,i_{k-1}))$$
+and $\tau\tilde P_{m}^{\ui} =\tilde P^{\ui}_{m-2}=\tilde P_{m-2}^{\bf j}$\footnote{notation}.
+
+By induction hypothesis the quiver Grassmannians corresponding to the representation on the left hand side have cell decompositions which are compatible with $\pi^{\bf j}_m$.
+The second part of Proposition \ref{fibers} says that the fibres are empty if and only if $\pi^{\bf j}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
+In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(\ui)})$ whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf j}(U)\neq 0$.
+By Theorem \ref{vb}, the claim follows.
+Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})$ which is compatible with a fixed $\pi_m^{\bf j'}$,
+Idee:
+
+\begin{comment}
 We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
@@
 In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
-
+\end{comment}
 \end{proof}
@@
 \bibitem{brenner-butler} S. Benner, M.~C.~R. Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
-\bibitem{cc}
-Caldero, P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
+\bibitem{cc} P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
 Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).

### 2017-12-11 Grassmannian_cells.tex
Continued editing Section 5

@@
 
-For convenience, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$, denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-But we point out that the next statements also hold for general sequences $(j_1,\ldots,j_l)$ with the same proof.
  We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
 \begin{lemma}\label{le:subrep}
-   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(1,\ldots,l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}
-
-\end{lemma}
-\begin{proof}
-
+   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}
+
+\end{lemma}
+\begin{proof}
+Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
 We proceed by induction.
@@
 \begin{lemma}\label{AR}\footnote{special case $m=3$}
-Let $m\geq 4$ and $n-1\geq l\geq 1$. Consider the short exact sequence $$\sesm{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}{\pi^{(1,\ldots,l)}_m}$$. The following holds:
+ Let $m\geq 4$ and $n-1\geq l\geq 1$ and let $(j_1,\ldots,j_l)$ be an admissible sequence.
+Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{(j_1,\ldots,j_l)}}{\pi^{(j_1,\ldots,j_l)}_m}$$.
+The following holds:
 \begin{enumerate}
-\item We have $\tau\tilde P_{m}^{(l)}=\tilde P_{m-2}^{(l)}$.
-\item For $m\geq 4$, $l\leq n-1$, there exists a short exact sequences 
-\[\sesm{\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{m-3,(l,l,j)}}{\tilde P_{m-1,l}}{\tau\tilde P_{m}^{(l)}}{\pi^{\bf i_l}_{m-1,l}}\]
-where ${\bf i}_l=((1,\ldots,l-1,\hat l,l+1,\ldots,n),(1,\ldots,l-1)).$
-
-\item Moreover, we have $\Ext(\tilde P_{m}^{(l)},\tilde P_{m-1,l})\cong \Ext(\tilde P_{m-1}^{(l)},\tau\tilde P_{m}^{(l)})=\kk$, $\Hom(\tilde P_{m}^{(l)},\tau\tilde P_{m}^{(l)})=0$. 
-\item We have $\tau\tilde P_{m}^{(l)}\in ~^\perp(\tilde P_{m}^{(l)})$.
+\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
+%\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
+What do we need?
+We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
+
+\item There exists a short exact sequences 
+\[\sesm{\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{(l)}}{\pi^{\bf j_l}_{m-1,j_l}}\]
+where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
+\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, $\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\cong\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ and $\Hom(\tilde P_{m}^{\uj},\tilde P_{m,j_l})=0$ and thus $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+\item We have $\Ext(\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{(j_1,\ldots,j_l)},\tau\tilde P_{m}^{(j_1,\ldots,j_{l})})=\kk$, $\Hom(\tilde P_{m}^{((j_1,\ldots,j_l)},\tau\tilde P_{m}^{(j_1,\ldots,j_l)})=0$.
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 \begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove the first statement for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
+Note that, starting with these cases, we only reflect at sinks and no representation appearing is isomorphic to the simple injective representation $S_2$.
+
 The representation $\tilde P_2$ is given determined by the following quiver and dimension vector:
@@
 \begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
-The quiver of $P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+The quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(1,\ldots, l)}$ is obtained by erasing the arrows $a_{a_1},\ldots, a_l$.
+
  Using this notation the support of $\tilde P_4$ is given by
@@
 
+Finally, the quiver corresponding to $\tilde P_4^{(1,\ldots,l)}$ is given by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+
 %\begin{tikzpicture}[scale=1]
@@
 %\end{tikzpicture}
-
-Note that, starting with these cases, we only reflect at sinks and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-In this case, the first two statements and the last one are straightforward\footnote{make this explicit, insert diagrams}.
-
-It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(l)},\tilde P_{3,l})=0$ which yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(l)},\underline{\quad})$.
-
-\end{proof}
-
-The short exact sequence $\ses{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}$ induces a map between quiver Grassmannians
-$$\Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(l-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{(l)}).$$
-Let $P(m,l):=\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-1,(l,j)}\oplus \bigoplus_{j=1}^l\tilde P_{m-2,(l,l,j)}$.
-
-By Lemma \ref{AR}, every $U\subset \tilde P_{m,k}$ gives rise to a commutative diagram
-
- \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_{m,k}\ar[r] & \tau\tilde P_{m+1}^{(k)}\ar[r] & 0 \\
+Now it is straightforward that the representation $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, which is given by reflecting at all the sinks twice, is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
+\footnote{say something concerning $W_Q$-translation?} This shows the first statement.
+
+Considering the quiver $\tilde P_{3,l}$ from above, it is clear that $\tilde P_2^{(1,\ldots,l)}$ is a quotient. Moreover, the representation
+$$\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}$$
+is the kernel of the corresponding map.
+Actually, the first summand corresponds to the quiver $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row which lying on the left.
+This shows the second/third statement.
+
+It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
+This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
+
+\end{proof}
+
+Let $\uj=(j_1,\ldots,j_l)$ be an admissible sequence and $m\geq 3$.
+The short exact sequence $\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{(j_1,\ldots,j_l)}}$ induces a map between quiver Grassmannians
+$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
+Define 
+$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
+
+Using Lemma \ref{AR}, for $m\geq 4$, every subrepresentation $U\subset \tilde P_{m,j_l}$ gives rise to a commutative diagram
+
+ \[\xymatrix{0\ar[r] &P(m,\uj)\ar[r] &  \tilde P_{m-1,j_l}\ar[r] & \tau\tilde P_{m}^{\uj}\ar[r] & 0 \\
   0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
-%By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
-Using this notation, we obtain:
-\begin{lemma}\label{quotient}
+If $m=3$, we consider the sequence
+ \[\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \bullet\xrightarrow{a_{j_l}}\bullet\ar[r] & 0}\]	
+	where the kernel is clearly just a direct sum of simple representations. In this case, the Auslander-Reiten translate of $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
+In particular, the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.
+In all cases, we denote the corresponding map between quiver Grassmannians by $\Phi_{m,\uj}$. Using this notation, we obtain:
+\begin{lemma}\label{quotient}Let $m\geq 3$ and $\uj=(j_1,\ldots,j_l)\in I_l^n$. The following holds:
 \begin{enumerate}
-\item The fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is empty if and only if $U\in\Psi^{-1}_2(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,k)$.
-\item If the fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
+\item The fibre $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is empty if and only if $U\in\Phi_{m,\uj}^{-1}(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,\uj)$.
+\item If the fibre $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty, we have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l}/U)= 0$.
 \end{enumerate} 
@@
 \begin{proof}
-If $W=0$, we get an exact sequence
-\[\ses{\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)}{\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)}{\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})}.\]
-
-By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$, $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$.
-Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$.
-This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m,k})=\kk$ which means that the induced map
-\[\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\]
+In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ by  $\bullet\xrightarrow{a_{j_l}}\bullet$ in which case all arguments hold in the same way.
+
+If $W=0$, from Lemma \ref{AR}, i.e. $\Hom(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=0$, we obtain a commutative diagram
+
+ \[\xymatrix{&0&0&0&\\0\ar[r] &\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\ar[r]\ar[u] & \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\ar[r]\ar[u] & 0 \\
+0\ar[r] &\Ext(\tilde P_{m}^{\uj},P(m,\uj))\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\ar[r]\ar[u] & \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\ar[r]\ar@{=}[u] & 0\\  0\ar[r] &\Ext(\tilde P_{m}^{\uj},V)\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},U)\ar[r]\ar[u] &0\ar[r]\ar[u] & 0}\]
+
+Moreover, the lemma implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
+This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ which means that the induced map
+\[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
 is zero.
 Therefore, the induced exact sequence splits.
-On the other hand, every subrepresentation $U\subset \tilde P_{m,k}$ such that $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty comes with a commutative diagram
- \[\xymatrix{0\ar[r] &\tilde P_{m,k}\ar[r] &  \tilde P_{m+1}^{(k-1)}\ar[r] & \tilde P_{m+1}^{(k)}\ar[r] & 0 \\
-  0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m+1}^{(k)}\ar[r]\ar[u]& 0}\]
-which means that the induced sequence in $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ does not split. This yields that the fibre is empty.
-
-Thus assume that $U\in\Psi_2^{-1}(V,W)$ with $W\neq 0$.
-We first show that $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
-Clearly, $\tau\tilde P_{m+1}^{(k)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k)}$ if $W\neq 0$.
-It follows that we have $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$.
-Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k)}\to \tau\tilde P_{m+1}^{(k)}/W$ factors through the middle term $Z$ of the AR-sequence
-\[\ses{\tau\tilde P_{m+1}^{(k)}}{Z}{\tilde P_{m+1}^{(k)}}\]
+On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
+ \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{(j_1,\ldots,j_{l-1})}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar[u]& 0}\]
+which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split.
+Indeed, we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{(j_1,\ldots,j_{l-1})})=0$ by Lemma \ref{AR}.
+This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.
+
+Thus assume that $U\in\Phi_{m,\uj}^{-1}(V,W)$ with $W\neq 0$.
+We first show that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$.
+Clearly, $\tau\tilde P_{m}^{\uj}/W$ is a proper factor of $\tau \tilde P_{m}^{\uj}$ if $W\neq 0$.
+It follows that we have $\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$.
+Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m}^{\uj}\to \tau\tilde P_{m}^{\uj}/W$ factors through the middle term $Z$ of the AR-sequence
+\[\ses{\tau\tilde P_{m}^{\uj}}{Z}{\tilde P_{m}^{\uj}}\]
 which means that the first map of the induced sequence
-\[\Hom(\tau\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)\to\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k)}/W) \]
-is zero.
-As $\tau\tilde P_{m+1}^{(k)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$ and $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$, i.e.
+\[\Hom(\tau\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(Z,\tau\tilde P_{m}^{\uj}/W) \]
+is zero. As $\tilde P_m^{\uj}$ is exceptional on the universal covering by the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}, it follows that 
+$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$ Since the map $\kk=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective and thus bijective, together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.
+
+%As $\tau\tilde P_{m+1}^{(k)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$ and $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$, i.e.
 Lemma \ref{AR}, yields $\Ext(Z,\tau\tilde P_{m+1}^{(k)})=0$ as the AR-sequence does not split.
@@
 
-Again we can apply Lemma \ref{AR} in order to see that $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$ as $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$. 
- Together with $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$, this yields the claim.
-
-Thus it remains to show that $\Psi^{-1}_1(U,\tilde P_{m+1}^{(k)})$ is not empty if $W\neq 0$.
-Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
-\end{proof}
-Now we are able to state the following result concerning the fibers of $\Psi_1$:
-\begin{proposition}\label{fibers}\footnote{maybe formulate this in terms of $\Psi$ (see below)}
+Again we can apply Lemma \ref{AR} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
+ Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.
+
+Thus it remains to show that $\Psi_{m,\uj}(U,\tilde P_{m}^{\uj})$ is not empty if $W\neq 0$.
+Since $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l})$ is surjective which already means that there exists a commutative diagram as above which, in turn, shows that the fiber is not empty.
+\end{proof}
+Now we are able to state the following result concerning the fibers of $\Psi_{m,\uj}$:
+\begin{proposition}\label{fibers}
  The following hold:
   \begin{enumerate}
-    \item For $V\subsetneq \tilde P_{m+1}^{(k)}$ and $U\subseteq\tilde P_{m,k}$, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
-    \item If $V=\tilde P_{m+1}^{(k)}$, the fiber $\Psi_1^{-1}(U,V)$ is not empty if and only if $\Psi_2(U)\neq (U,0)$. In this case, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
+    \item For $V\subsetneq \tilde P_{m}^{\uj}$ and $U\subseteq\tilde P_{m-1,j_l}$, we have $\Psi_{m,\uj}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m-1,j_l}/U\rangle}$.
+    \item If $V=\tilde P_{m,\uj}$, the fiber $\Psi_{m,\uj}^{-1}(U,V)$ is not empty if and only if $\Phi_{m,\uj}(U)\neq (U,0)$.
+In this case, we have $\Psi_{m,\uj}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m-1,l_j}/U\rangle}$.
 
@@
 \end{proposition}
-\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
-But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
-Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$.
-If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.
+\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m}^{\uj}$ is preprojective.
+But the representation $\tilde P_{m-1,l_j}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
+Thus we have $\Ext(V,\tilde P_{m-1,l_j}/U)=0$.
+If $U=0$, we have $\Ext(V,\tilde P_{m-1,l_j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
 
@@
 \begin{theorem}\label{cellscover}
-Let $\ui=(i_1,\ldots,i_k)$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ admits a cell decomposition into affine spaces.
+Let $\uj=(i_1,\ldots,i_l)$ be an admissible sequence. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
 \end{theorem}
@@
 
-\noindent {\bf Claim.} Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})$ has a cell decomposition which is compatible with a fixed quotient map $\pi_m^{\bf j}$ in the following way:
- Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ such that $\pi_m^{\bf j}(U)\neq 0.$
+\noindent {\bf Claim.} Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition which is compatible with a fixed quotient map $\pi_m^{\bf j}$ with ${\bf j}_1=\uj$ in the following way:
+ Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
 Then we have $\pi_m^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
@@
 
-We proceed by induction on $m$ and $k$. If $m=1$ or $m=2$, the statement is straightforward as all quiver Grassmannians are points. Now let $m\geq 3$.
-The short exact sequence $$\sesm{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{\ui}}{\pi_m^{\ui}}$$ induces a map between quiver Grassmannians
-$$\Psi_1:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\ui}).$$
-Let $P(m,\ui)=\bigoplus_{\substack{1\leq j\leq n\\j\neq i_k}}\tilde P_{m-2,(i_k,j)}\oplus \bigoplus_{j=1}^{k-1}\tilde P_{m-3,(i_k,i_k,i_j)}$. Then we obtain a short exact sequence
-$$\sesm{P(m,\ui)}{\tilde P_{m-1,i_k}}{\tau\tilde P_{m}^{\ui}}{\pi^{\bf j}_m}$$
+We proceed by induction on $m$ and reverse induction on $l$. If $m=1$ or $m=2$, the statement is straightforward as all quiver Grassmannians are points.
+The short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}{\pi_m^{\uj}}$$ induces a map between quiver Grassmannians
+$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
+We consider the short exact sequence
+$$\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j}_m}$$
 with
-$${\bf j}=((1,\ldots,i_k-1,\hat i_k,i_k+1,\ldots,n),(i_1,\ldots,i_{k-1}))$$
-and $\tau\tilde P_{m}^{\ui} =\tilde P^{\ui}_{m-2}=\tilde P_{m-2}^{\bf j}$\footnote{notation}.
+$${\bf j}=((1,\ldots,j_l-1,\widehat{j_l},j_l+1,\ldots,n),(j_1,\ldots,j_{l-1}))$$
+and $\tau\tilde P_{m}^{\uj} =\tilde P^{\uj}_{m-2}=\tilde P_{m-2}^{\bf j}$.
 
@@
 By Theorem \ref{vb}, the claim follows.
-Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})$ which is compatible with a fixed $\pi_m^{\bf j'}$,
-Idee:
+Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})$ which is compatible with a fixed $\pi_m^{\bf j'}$,
 
@@
 
-Note that we can also consider 
-$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
+%Note that we can also consider 
+%$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
 But then one needs to adjust $\Psi_2$ because the factor of $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.

### 2017-12-12 Grassmannian_cells.tex
nearly finished section 5
last bit of main theorem and proof-reading are missing

@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
 
@@
 We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_m)_{i,w}=0$ if $(i,w)\neq (1,1)$.
+For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
 Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
 Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+Moreover, sinks become sources and vice versa.
 For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
 we have
-\begin{align}\label{recursive}\tilde P_m=(\tilde\Sigma_1 \tilde P_{m-1})^T,\quad\tilde P_{m+1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\footnote{odd and even live on different components}\end{align}
-Recall that we obtain the Auslander-Reiten translate $\tau^{-1}\tilde P_m$ by applying the reflection functor to the sinks twice where the sinks become sources after each step. 
+\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\end{align}
+It is rather important that $\tilde P_{2m}$ and $\tilde P_{2m-1}$ live on two different components of the universal covering quiver.
+
 \begin{remark}\begin{enumerate}
@@
 Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,0)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
+\item Then we have 
+$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
+for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
+
+\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,1)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
 \end{enumerate}
 \end{remark}
-The next step is to construct filtrations of $\tilde P_m$ by smaller preprojective $w.\tilde P_{l}$ for $l<m$ and certain $w\in W_Q$.
-To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
-
-Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. More precisely, we have 
-$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l+1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
-for all $l\geq 1$ and for $i=1,\ldots,n$.
-This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
-In the following, we sometimes identify the arrows with the numbers $1,\ldots,n$.
-
-We need some more notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
+
+%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
+
+Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.
+
+\begin{example}\label{smallm}[The cases $m=2,3,4$]
+\end{example}
+
+The representation $\tilde P_2$ is given by the following coefficient quiver:
+
+\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
+The coefficient quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
+
+Using this notation, we obtain that $\tilde P_3$ can be written as
+	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
+	and, moreover, $\tilde P_3^{\uj}$ is obtained when erasing the subquiver $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of the sink by one.
+The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
+In particular, the image of the unique homomorphism $\tilde P_{2,j_l}=a_{j_l}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.
+
+The support of $\tilde P_4$ is given by
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the numbers correspond to the dimensions of the respective vertices.
+Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
+The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
+Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
+
+Finally, the quiver corresponding to $\tilde P_4^{(1,\ldots,l)}$ is given by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau^{-1}$ is given by reflecting at all the sinks first and at all sources afterwards.
+Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
+
+%\begin{tikzpicture}[scale=1]
+%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\end{tikzpicture}
+
+\begin{remark}
+Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
+We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
+Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
+\end{remark}
+
+The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
 With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
@@
 Let
-$$I^n_l:=\{(i_1,\ldots,i_{l})\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.$$
+$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
 As we fixed the number of arrows, we drop the $n$ in what follows.
-For $\ui=(i_1,\ldots,i_{n-1})\in I_{n-1}$, let $i^c\in \{1,\ldots,n\}$ and $\ui^c=(i^c)$ where $i^c\neq i_j$ for $j=1,\ldots,n-1$.
-Clearly, $\ui^c$ is uniquely determined by $\ui$.
-
-Let $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ be a sequence with $\underline{i_1}\in I_{n-1}$, $\underline{i_2},\ldots,\underline{i_{r-1}}\in I_{n-2}$ and $\underline{i_r}\in I_s$ for $s\leq n-2$.
-Define $i_1^c$ as before and for $k\geq 2$ let $i_k^c\in\{1,\ldots,n\}$ be the unique number such that $i_k^c\neq i_{k,j}$ for $j=1,\ldots,n-2$ and $i_k^c\neq i_{k-1}^c$.
-We say that $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ is admissible if
-$$ i_{k,j}\neq i_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,j=1,\ldots,n-2\text{ and for }j=1,\ldots,s\text{ if }k=r.$$
-
-For $\ui\in I_{s}$ with $s\leq n-1$, there exist unique exact sequences of the form
-\[\ses{\bigoplus_{j=1}^s\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{\ui}},\quad\quad\ses{\tilde P_{m-1,i_s}}{\tilde P_{m}^{(i_1,\ldots,i_{s-1})}}{\tilde P_{m}^{\ui}}\]
-where the $\tilde P_m^{\ui}$ are truncated preprojectives (as defined in the last section).
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf i}=(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$.
-We define the admissible sequence $\delta {\bf i}$ (of length $r-1$) by
-\[\delta {\bf i}:=((i_1^c,\underline{i_2}),\ldots,\underline{i_r}).\]
-We recursively define $\delta^l{\bf i}$ for $l=1,\dots,r-1$.
+For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ and $\uj^c=(j^c)$ where $j^c\neq j_i$ for $i=1,\ldots,n-1$.
+Clearly, $\uj^c$ is uniquely determined by $\uj$.
+
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
+Define $j_1^c$ as before.
+ We say that ${\bf j}$ is admissible if 
+$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
+where $j_k^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique number satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
+\end{definition}
+
+For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
+\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}\]
+where the $\tilde P_m^{\uj}$ are lifts of truncated preprojectives (as defined in the last section).
+The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
+We define the admissible sequence $\delta {\bf j}$ (of length $r-1$) by
+\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\ldots,\underline{j_r}).\]
+We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r-1$.
 %In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\ui=(i^c)$ for $\ui\in I_{n-1}$.
+Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
 
@@
   \begin{enumerate}
-    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{j=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$ is one-dimensional;
+    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item The representations $\tilde P_{m,j}$ are pairwise orthogonal, i.e. for $j\neq i$ we have $$\Hom(\tilde P_{m-1,i},\tilde P_{m-1,j})=\Ext(\tilde P_{m-1,i},\tilde P_{m-1,j})=0;$$
-    \item If $\ui\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\ui}\cong \tilde P_{m-1,i^c}^{\ui^c}= P_{m-1,i^c}/P_{m-2,(i^c,i^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf i:=(\underline{i_1},\ldots,\underline{i_r})$ be an admissible sequence.
-Let ${\bf i}(l):=(\underline{i_1},\ldots,\underline{i_l})$ for $l=2,\ldots,r-1$.
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
+    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
+		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence.
+Let ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$.
 Then we recursively have
-		\[\tilde P_{m-l,(i_1^c,\ldots,i_l^c)}^{\delta^l{\bf i(l)}}=\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}\bf i(l)}\]
-		for $l=1,\ldots,r$.
-Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf i}_{m-r+1}:=\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}/\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{(i_{r-1}^c,i_{r,1},\ldots,i_{r,s})}$$ with each admissible sequence ${\bf i}$.
+		\[\tilde P_{m-l,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-l+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
+		for $k=1,\ldots,r$.
+Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$%/\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}$$
+		with each admissible sequence ${\bf j}$.
   \end{enumerate}
@@
 \begin{proof}
-The first statement follows from Theorem \ref{covering}. For $m=2$, the second part is obvious. For $m\geq 3$, it then follows by applying the identities (\ref{recursive}).
+The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
 
 To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-1}\tilde P_{m-1,i_j}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\ui}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,i^c}\ar[u]\ar[r]& \tilde P_{m}^{\ui}\ar[r]\ar@{=}[u]& 0}\]
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
 
 %Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,i^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(i^c,i^c)}$.
-Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,i^c}^{\ui^c}$.
+For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,j^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
+Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,j^c}^{\uj^c}$.
 Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
 
-The forth statement is now obtained recursively when initially considering the diagram from above replacing $\ui$ by $\underline{i_1}$.
-
-We have $\delta^{l-1}{\bf i}(l)=(i_{l-1}^c,i_{l,1},\ldots,i_{l,n-1})$. We use the third statement in order to successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-2}\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})}\ar[r] &  \tilde P^{(i_{l-1}^c)}_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}\ar[r] & \tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}{\bf i}(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(l+1),(i_1^c,\ldots,i_{l}^c,i_l^c)} \ar[r]\ar[u] & \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}\ar[u]\ar[r]& \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}^{(\underline{i_{l}^c)}}\ar[r]\ar@{=}[u]& 0}\]
-Now we have $\delta^l{\bf i}(l)=(i_l^c)$.	Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{s}\tilde P_{m-r,(i_1^c,\ldots,i_{r-1}^c,i_{r,j})}\ar[r] &  \tilde P^{(i_{r-1}^c)}_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{{\bf i}}\ar[r] & 0 }.\]
-As $\Hom(\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})},\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)})=k$ for all $l=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf i}$ is uniquely determined.
-	\end{proof}
-We denote the quotient morphism by $\pi_m^{\bf i}:\tilde P_m\to \tilde P_{m-r+1}^{\bf i}$.
-It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{(1,\ldots,l)}$ where $l\leq n-1$ and $j_k\neq i_1^c$ for $k=1,\ldots, l$.
-We also denote the quotient morphism from $\tilde P_m^{(j_1,\ldots,j_l)}$ to $\tilde P_{m-r+1}^{\bf i}$ by $\pi_m^{\bf i}$.
+The forth statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
+We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$.
+We use the third statement in order to successively obtain commutative diagrams
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
+Now we have $\delta^{k-1}{\bf j}(k)=(j_k^c)$.	Finally, we consider the short exact sequence:
+
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
+As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
+	\end{proof}
+We denote the quotient morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$.
+Let $\ui=(i_{1},\ldots,i_{l})$.
+It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{\ui}$ where $l\leq n-1$ and $i_k\neq j_1^c$ for $k=1,\ldots, l$.
+We denote the quotient morphism from $\tilde P_m^{\ui}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\ui}^{\bf j}$.
+
+Our construction immediately yields the following lemma.
+\begin{lemma}\label{projections}
+Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
+Then we have
+\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}\]
+and, for any sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
+\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
+for $k=1,\ldots,r-1$ where $\pi_{m,j_{-1}^c}^{\underline{j_1}}:=\pi_m^{\underline{j_1}}$ and the analogous statement for $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ and $(l_1,\ldots,l_{s-1})\in I_{s-1}$ holds.
+\end{lemma}
+We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
+Therefore, we need to apply a translated version of this morphism.
+In abuse of notation, we also denote this morphism $\pi_m^{\bf j}$.
 
@@
 
+\begin{comment} 
 DO NOT NEED THIS-------FROM HERE----
@@
 ----TO HERE----DO NOT NEED THIS----
-
+\end{comment}
 \begin{lemma}\label{AR}\footnote{special case $m=3$}
- Let $m\geq 4$ and $n-1\geq l\geq 1$ and let $(j_1,\ldots,j_l)$ be an admissible sequence.
-Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{(j_1,\ldots,j_l)}}{\pi^{(j_1,\ldots,j_l)}_m}$$.
+ Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
+Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
+$$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
+
  The following holds:
@@
 \item There exists a short exact sequences 
-\[\sesm{\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{(l)}}{\pi^{\bf j_l}_{m-1,j_l}}\]
+\[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
 where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, $\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\cong\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ and $\Hom(\tilde P_{m}^{\uj},\tilde P_{m,j_l})=0$ and thus $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
-\item We have $\Ext(\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{(j_1,\ldots,j_l)},\tau\tilde P_{m}^{(j_1,\ldots,j_{l})})=\kk$, $\Hom(\tilde P_{m}^{((j_1,\ldots,j_l)},\tau\tilde P_{m}^{(j_1,\ldots,j_l)})=0$.
+
+\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
+\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
+\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$ 
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
-Note that, starting with these cases, we only reflect at sinks and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-The representation $\tilde P_2$ is given determined by the following quiver and dimension vector:
-
-\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
-The quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(1,\ldots, l)}$ is obtained by erasing the arrows $a_{a_1},\ldots, a_l$.
-
- Using this notation the support of $\tilde P_4$ is given by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the numbers correspond to the dimensions of the respective vertices.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar^{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar^{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar^{a_n}[lllu]	&&&&}\]
-
-Finally, the quiver corresponding to $\tilde P_4^{(1,\ldots,l)}$ is given by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-Now it is straightforward that the representation $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, which is given by reflecting at all the sinks twice, is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
-\footnote{say something concerning $W_Q$-translation?} This shows the first statement.
-
-Considering the quiver $\tilde P_{3,l}$ from above, it is clear that $\tilde P_2^{(1,\ldots,l)}$ is a quotient. Moreover, the representation
-$$\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}$$
-is the kernel of the corresponding map.
-Actually, the first summand corresponds to the quiver $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row which lying on the left.
-This shows the second/third statement.
-
-It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
+Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
+
+In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
+In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
+Therefore, we may consider the short exact sequence
+\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
+and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
+As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
+
+Considering the quiver $\tilde P_{3,l}$ from above, it is clear that we obtain an exact sequence
+$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
+Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
+This shows the second statement.
+
+As $\tilde P_m^{\uj}$ is exceptional on the universal covering by the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}, it follows that 
+$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
+As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
+This yields the remaining results at once.
+
+%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
 This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
@@
  \[\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \bullet\xrightarrow{a_{j_l}}\bullet\ar[r] & 0}\]	
-	where the kernel is clearly just a direct sum of simple representations. In this case, the Auslander-Reiten translate of $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	where the kernel is clearly just a direct sum of simple representations. Recall that the Auslander-Reiten translate of $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
 	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
@@
 \begin{theorem}\label{cellscover}
-Let $\uj=(i_1,\ldots,i_l)$ be an admissible sequence. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
+Let $m\geq 2$ and let $\uj=(j_1,\ldots,j_l)\in I_l$ with $l\leq n-1$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
 \end{theorem}
@@
 
-\noindent {\bf Claim.} Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition which is compatible with a fixed quotient map $\pi_m^{\bf j}$ with ${\bf j}_1=\uj$ in the following way:
+\noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$.
+The quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition into affine spaces which is compatible with $\pi_{m,\uj}^{\bf j}$  in the following way:
  Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
-Then we have $\pi_m^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
+Then we have $\pi_{m,\uj}^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
 \vs
 
-We proceed by induction on $m$ and reverse induction on $l$. If $m=1$ or $m=2$, the statement is straightforward as all quiver Grassmannians are points.
-The short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}{\pi_m^{\uj}}$$ induces a map between quiver Grassmannians
-$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
-We consider the short exact sequence
-$$\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j}_m}$$
-with
-$${\bf j}=((1,\ldots,j_l-1,\widehat{j_l},j_l+1,\ldots,n),(j_1,\ldots,j_{l-1}))$$
-and $\tau\tilde P_{m}^{\uj} =\tilde P^{\uj}_{m-2}=\tilde P_{m-2}^{\bf j}$.
-
-By induction hypothesis the quiver Grassmannians corresponding to the representation on the left hand side have cell decompositions which are compatible with $\pi^{\bf j}_m$.
-The second part of Proposition \ref{fibers} says that the fibres are empty if and only if $\pi^{\bf j}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(\ui)})$ whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf j}(U)\neq 0$.
+We proceed by induction on $m$ and reverse induction on $l$.
+Let $\uj'=(j_1,\ldots,j_{l-1})$.
+If $m=1$ or $m=2$, the statement is straightforward for arbitrary $l$ as all quiver Grassmannians are points.
+For general $m$, we consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ induces a map between quiver Grassmannians
+$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
+It is important that we can choose $j_l$ arbitrarily with respect to the condition $j_l\neq j_1,\ldots, j_{l-1}$. Moreover, we consider the short exact sequence
+$$\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf i}_m}$$
+where
+$${\bf i}=((1,\ldots,j_l-1,\widehat{j_l},j_l+1,\ldots,n),(j_1,\ldots,j_{l-1}))$$
+and $\tau\tilde P_{m}^{\uj} =\tilde P^{\uj}_{m-2}=\tilde P_{m-2}^{\bf i}$ together with the induced map on quiver Grassmannians $\Phi_{m,\uj}$.
+
+By induction hypothesis the quiver Grassmannians $\Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})$ have cell decompositions which are compatible with $\pi^{\bf i}_m$ and, moreover, the quiver Grassmannians $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ have a cell decompositions which are compatible with $\pi^{\bf j}_{m,\uj}$.
+The second part of Proposition \ref{fibers} says that the fibres are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
+This yields a collection of cells over which the fibres are empty.
+Note that $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is just a point in this case.
+
+If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ which satisfy $\pi_m^{\bf i}(U)\neq 0$, but also over those whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)= 0$.
 By Theorem \ref{vb}, the claim follows.
-Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})$ which is compatible with a fixed $\pi_m^{\bf j'}$,
+
+Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ which is compatible with a fixed $\pi_{m,\uj'}^{\bf j'}$ where ${\bf j'}=(\underline{j'_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
+Recall that we have $\pi_{m,\uj'}^{\bf j'}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{projections}.
+
+Thus let $\pi_{m,\uj'}^{\bf j'}(U)= 0$ with $U\subset \tilde P_{m}^{\uj'}$.
+Then we either have $\pi_{m,\uj'}^{j_l}(U)=0$ which means that $U$ comes from a subrepresentation of $\tilde P_{m,j_l}$ and $\tbfg=0$.
+In this case, all representations in the cell of $U$ come from a subrepresentation of $\tilde P_{m,j_l}$.
+Thus assume that $\pi_{m,\uj'}^{j_l}(U)\neq 0$.
+We have $\pi_{m,\uj'}^{j_l}(U)\neq \tilde P_{m}^{\uj}$ because otherwise we had $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$.
+Apply induction hypothesis now.
 

### 2017-12-12 Grassmannian_cells.tex
Random edits

--- 2017-12-08 Grassmannian_cells.tex
@@
 \usepackage{extarrows}
-\usepackage{verbatim}
 \input xy
@@
 \newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
-\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
 \newcommand{\Sc}[2]{\langle #1,#2\rangle}
@@
 \setcounter{MaxMatrixCols}{20}
-\newcommand{\vs}{\vspace{0.2cm}}
+
 \hyphenation{endo-functors}
@@
 
--something about compatible pairs and combinatorial construction of cluster variables
--statement of our results
--something about torus actions and the universal cover
--something about cell decompositions of quiver Grassmannians
--acknowledgements?
+-something about compatible pairs and combinatorial construction of cluster variables\\
+-statement of our results\\
+-something about torus actions and the universal cover\\
+-something about cell decompositions of quiver Grassmannians\\
+-acknowledgements?\\
 
@@
 \begin{lemma}
-  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
-\end{lemma}
-\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$.
-Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$.
-Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp.
-$(q,w)$ of $\tilde Q$).
-This leads the claim.
-The statement for preinjective representations follows in the same way.
+  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
+\end{lemma}
+\begin{proof}
+  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
+  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
+  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
+  This gives the claim.
 \end{proof}
 As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
-\begin{theorem}\label{covering}
-The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
+\begin{theorem}
+  \label{covering}
+  The functors $F_Q$ and $G_Q$ preserve indecomposability.
+  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
   \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
-The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
+  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
 \end{theorem}
 
-Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$.
+Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$.
 In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
+\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
@@
 \end{theorem}
-%\begin{proof}\footnote{sketch, double-check}
-
-%As $X$ and $Y$ are projective, they are compact.
+\begin{proof}\footnote{sketch, double-check}
+
+As $X$ and $Y$ are projective, they are compact.
 As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
@@
 
-%\end{proof}
+\end{proof}
 
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
+\begin{remark}
   \label{rem:reflection recursion}
@@
 \noindent 
-We fix a natural number $n\geq 3$.
-We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_m)_{i,w}=0$ if $(i,w)\neq (1,1)$.
-Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
-Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
-For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
-we have
-\begin{align}\label{recursive}\tilde P_m=(\tilde\Sigma_1 \tilde P_{m-1})^T,\quad\tilde P_{m+1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\footnote{odd and even live on different components}\end{align}
-Recall that we obtain the Auslander-Reiten translate $\tau^{-1}\tilde P_m$ by applying the reflection functor to the sinks twice where the sinks become sources after each step. 
-\begin{remark}\begin{enumerate}
-\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
-$w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.
-Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,0)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
-\end{enumerate}
-\end{remark}
-The next step is to construct filtrations of $\tilde P_m$ by smaller preprojective $w.\tilde P_{l}$ for $l<m$ and certain $w\in W_Q$.
-To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
-
-Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. More precisely, we have 
-$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l+1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
-for all $l\geq 1$ and for $i=1,\ldots,n$.
-This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
-In the following, we sometimes identify the arrows with the numbers $1,\ldots,n$.
-
-We need some more notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
-With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-More detailed, we obtain a sequence of preprojective representations
-$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$
-
-Let
-$$I^n_l:=\{(i_1,\ldots,i_{l})\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.$$
-As we fixed the number of arrows, we drop the $n$ in what follows.
-For $\ui=(i_1,\ldots,i_{n-1})\in I_{n-1}$, let $i^c\in \{1,\ldots,n\}$ and $\ui^c=(i^c)$ where $i^c\neq i_j$ for $j=1,\ldots,n-1$.
-Clearly, $\ui^c$ is uniquely determined by $\ui$.
-
-Let $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ be a sequence with $\underline{i_1}\in I_{n-1}$, $\underline{i_2},\ldots,\underline{i_{r-1}}\in I_{n-2}$ and $\underline{i_r}\in I_s$ for $s\leq n-2$.
-Define $i_1^c$ as before and for $k\geq 2$ let $i_k^c\in\{1,\ldots,n\}$ be the unique number such that $i_k^c\neq i_{k,j}$ for $j=1,\ldots,n-2$ and $i_k^c\neq i_{k-1}^c$.
-We say that $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ is admissible if
-$$ i_{k,j}\neq i_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,j=1,\ldots,n-2\text{ and for }j=1,\ldots,s\text{ if }k=r.$$
-
-For $\ui\in I_{s}$ with $s\leq n-1$, there exist unique exact sequences of the form
-\[\ses{\bigoplus_{j=1}^s\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{\ui}},\quad\quad\ses{\tilde P_{m-1,i_s}}{\tilde P_{m}^{(i_1,\ldots,i_{s-1})}}{\tilde P_{m}^{\ui}}\]
-where the $\tilde P_m^{\ui}$ are truncated preprojectives (as defined in the last section).
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf i}=(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$.
-We define the admissible sequence $\delta {\bf i}$ (of length $r-1$) by
-\[\delta {\bf i}:=((i_1^c,\underline{i_2}),\ldots,\underline{i_r}).\]
-We recursively define $\delta^l{\bf i}$ for $l=1,\dots,r-1$.
-%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\ui=(i^c)$ for $\ui\in I_{n-1}$.
-
-\begin{lemma}The following holds:
+Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$.
+Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
+$w.(q,w')=(q,ww')$.
+Up to this action a lift $\tilde P_m$ of $P_m$ is unique.
+On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$.
+Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$.
+In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
+\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]
+
+Using this notation, we obtain the following lemma:
+\begin{lemma}
   \label{le:preprojective lifts}
   \begin{enumerate}
-    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{j=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$ is one-dimensional;
+    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item The representations $\tilde P_{m,j}$ are pairwise orthogonal, i.e. for $j\neq i$ we have $$\Hom(\tilde P_{m-1,i},\tilde P_{m-1,j})=\Ext(\tilde P_{m-1,i},\tilde P_{m-1,j})=0;$$
-    \item If $\ui\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\ui}\cong \tilde P_{m-1,i^c}^{\ui^c}= P_{m-1,i^c}/P_{m-2,(i^c,i^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf i:=(\underline{i_1},\ldots,\underline{i_r})$ be an admissible sequence.
-Let ${\bf i}(l):=(\underline{i_1},\ldots,\underline{i_l})$ for $l=2,\ldots,r-1$.
-Then we recursively have
-		\[\tilde P_{m-l,(i_1^c,\ldots,i_l^c)}^{\delta^l{\bf i(l)}}=\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}\bf i(l)}\]
-		for $l=1,\ldots,r$.
-Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf i}_{m-r+1}:=\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}/\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{(i_{r-1}^c,i_{r,1},\ldots,i_{r,s})}$$ with each admissible sequence ${\bf i}$.
+    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal;
+    \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
+
   \end{enumerate}
@@
 \begin{proof}
-The first statement follows from Theorem \ref{covering}. For $m=2$, the second part is obvious. For $m\geq 3$, it then follows by applying the identities (\ref{recursive}).
-
-To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-1}\tilde P_{m-1,i_j}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\ui}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,i^c}\ar[u]\ar[r]& \tilde P_{m}^{\ui}\ar[r]\ar@{=}[u]& 0}\]
-
-%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,i^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(i^c,i^c)}$.
-Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,i^c}^{\ui^c}$.
-Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
-
-The forth statement is now obtained recursively when initially considering the diagram from above replacing $\ui$ by $\underline{i_1}$.
-
-We have $\delta^{l-1}{\bf i}(l)=(i_{l-1}^c,i_{l,1},\ldots,i_{l,n-1})$. We use the third statement in order to successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-2}\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})}\ar[r] &  \tilde P^{(i_{l-1}^c)}_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}\ar[r] & \tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}{\bf i}(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(l+1),(i_1^c,\ldots,i_{l}^c,i_l^c)} \ar[r]\ar[u] & \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}\ar[u]\ar[r]& \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}^{(\underline{i_{l}^c)}}\ar[r]\ar@{=}[u]& 0}\]
-Now we have $\delta^l{\bf i}(l)=(i_l^c)$.	Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{s}\tilde P_{m-r,(i_1^c,\ldots,i_{r-1}^c,i_{r,j})}\ar[r] &  \tilde P^{(i_{r-1}^c)}_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{{\bf i}}\ar[r] & 0 }.\]
-As $\Hom(\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})},\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)})=k$ for all $l=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf i}$ is uniquely determined.
-	\end{proof}
-We denote the quotient morphism by $\pi_m^{\bf i}:\tilde P_m\to \tilde P_{m-r+1}^{\bf i}$.
-It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{(1,\ldots,l)}$ where $l\leq n-1$ and $j_k\neq i_1^c$ for $k=1,\ldots, l$.
-We also denote the quotient morphism from $\tilde P_m^{(j_1,\ldots,j_l)}$ to $\tilde P_{m-r+1}^{\bf i}$ by $\pi_m^{\bf i}$.
-
-For convenience, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$, denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-But we point out that the next statements also hold for general sequences $(j_1,\ldots,j_l)$ with the same proof.
-We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
-\begin{lemma}\label{le:subrep}
-   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(1,\ldots,l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}
-
-\end{lemma}
-\begin{proof}
-
-We proceed by induction.
+The first statement follows from Theorem \ref{covering}. The second part follows for instance recursively by applying BGP-reflections.
+
+For the third part, we proceed by induction.
 Clearly $\tilde P_m$ has only preprojective subrepresentations.
 We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
-Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
-Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
+If $U\subsetneq P_m^{(i_1,\ldots,i_k)}$ were not preprojective, the embedding would not factor through $P_m^{(i_1,\ldots,i_{k-1})}$ by induction hypothesis.
 Thus we get a commutative diagram
 
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
-We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-
-As the sequence does not split, this shows that $U'$ is an indecomposable  (reference) preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$.
-Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
-Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
-\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
+because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not.
+Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason.
+Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
+because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom sequence does not split.
 But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
@@
 
-DO NOT NEED THIS-------FROM HERE----
+If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$ and $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+
 \begin{lemma}\label{directsums}
@@
 \end{proof}
-----TO HERE----DO NOT NEED THIS----
-
-\begin{lemma}\label{AR}\footnote{special case $m=3$}
-Let $m\geq 4$ and $n-1\geq l\geq 1$. Consider the short exact sequence $$\sesm{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}{\pi^{(1,\ldots,l)}_m}$$. The following holds:
+\begin{lemma}\label{AR}
+Let $m\geq 3$ and $n\geq k\geq 1$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
 \begin{enumerate}
-\item We have $\tau\tilde P_{m}^{(l)}=\tilde P_{m-2}^{(l)}$.
-\item For $m\geq 4$, $l\leq n-1$, there exists a short exact sequences 
-\[\sesm{\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{m-3,(l,l,j)}}{\tilde P_{m-1,l}}{\tau\tilde P_{m}^{(l)}}{\pi^{\bf i_l}_{m-1,l}}\]
-where ${\bf i}_l=((1,\ldots,l-1,\hat l,l+1,\ldots,n),(1,\ldots,l-1)).$
-
-\item Moreover, we have $\Ext(\tilde P_{m}^{(l)},\tilde P_{m-1,l})\cong \Ext(\tilde P_{m-1}^{(l)},\tau\tilde P_{m}^{(l)})=\kk$, $\Hom(\tilde P_{m}^{(l)},\tau\tilde P_{m}^{(l)})=0$. 
-\item We have $\tau\tilde P_{m}^{(l)}\in ~^\perp(\tilde P_{m}^{(l)})$.
+\item There exists a short exact sequence 
+\[\ses{\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}}{\tilde P_{m,k}}{\tau\tilde P_{m+1}^{(k)}}\]
+where $\tau$ denotes the Auslander-Reiten translate where
+$\tau\tilde P_{m+1}^{(k)}=\tilde P_{m-1}^{(k)}$. 
+\item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
+\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$.
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 \begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove the first statement for $m=4$ and arbitrary $1\leq l\leq n-1$.
-The representation $\tilde P_2$ is given determined by the following quiver and dimension vector:
-
-\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
-The quiver of $P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
-Using this notation the support of $\tilde P_4$ is given by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the numbers correspond to the dimensions of the respective vertices.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar^{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar^{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar^{a_n}[lllu]	&&&&}\]
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-
-Note that, starting with these cases, we only reflect at sinks and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-In this case, the first two statements and the last one are straightforward\footnote{make this explicit, insert diagrams}.
-
-It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(l)},\tilde P_{3,l})=0$ which yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(l)},\underline{\quad})$.
-
-\end{proof}
-
-The short exact sequence $\ses{\tilde P_{m-1,l}}{\tilde P_{m}^{(l-1)}}{\tilde P_{m}^{(l)}}$ induces a map between quiver Grassmannians
-$$\Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(l-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{(l)}).$$
-Let $P(m,l):=\bigoplus_{\substack{1\leq j\leq n\\j\neq l}}\tilde P_{m-1,(l,j)}\oplus \bigoplus_{j=1}^l\tilde P_{m-2,(l,l,j)}$.
+We have $\mathcal  S \tilde P_m=\tilde P_{m+1}$ (up to permutation).
+This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$.
+In this case, the first statement is straightforward as well as the third one (insert a diagram).
+
+It is also straightforward to check that $\bigoplus_{j\neq k}\tilde P_{2,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{1,(k,k,j)}\in (\tilde P_{4}^{(k)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(k)},\tilde P_{3,k})=0$ which yields the second claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(k)},\underline{\quad})$.
+
+\end{proof}
+
+The short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$ induces a map between quiver Grassmannians
+$$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^{(k)}).$$
+Let $P(m,k):=\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}$.
 
@@
   0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
-%By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
+By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
 Using this notation, we obtain:
@@
 \end{proposition}
-\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
+\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective.
 But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
@@
 \begin{theorem}\label{cellscover}
-Let $\ui=(i_1,\ldots,i_k)$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ admits a cell decomposition into affine spaces.
+Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
 \end{theorem}
 \begin{proof}
-
-In order to prove the claim, we prove the more general statement:
-\vs
-
-\noindent {\bf Claim.} Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})$ has a cell decomposition which is compatible with a fixed quotient map $\pi_m^{\bf j}$ in the following way:
- Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\ui})$ such that $\pi_m^{\bf j}(U)\neq 0.$
-Then we have $\pi_m^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
-\vs
-
-We proceed by induction on $m$ and $k$. If $m=1$ or $m=2$, the statement is straightforward as all quiver Grassmannians are points. Now let $m\geq 3$.
-The short exact sequence $$\sesm{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{\ui}}{\pi_m^{\ui}}$$ induces a map between quiver Grassmannians
-$$\Psi_1:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\ui}).$$
-Let $P(m,\ui)=\bigoplus_{\substack{1\leq j\leq n\\j\neq i_k}}\tilde P_{m-2,(i_k,j)}\oplus \bigoplus_{j=1}^{k-1}\tilde P_{m-3,(i_k,i_k,i_j)}$. Then we obtain a short exact sequence
-$$\sesm{P(m,\ui)}{\tilde P_{m-1,i_k}}{\tau\tilde P_{m}^{\ui}}{\pi^{\bf j}_m}$$
-with
-$${\bf j}=((1,\ldots,i_k-1,\hat i_k,i_k+1,\ldots,n),(i_1,\ldots,i_{k-1}))$$
-and $\tau\tilde P_{m}^{\ui} =\tilde P^{\ui}_{m-2}=\tilde P_{m-2}^{\bf j}$\footnote{notation}.
-
-By induction hypothesis the quiver Grassmannians corresponding to the representation on the left hand side have cell decompositions which are compatible with $\pi^{\bf j}_m$.
-The second part of Proposition \ref{fibers} says that the fibres are empty if and only if $\pi^{\bf j}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,i_k})\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(\ui)})$ whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf j}(U)\neq 0$.
-By Theorem \ref{vb}, the claim follows.
-Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(i_1,\ldots,i_{k-1})})$ which is compatible with a fixed $\pi_m^{\bf j'}$,
-Idee:
-
-\begin{comment}
 We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
@@
 In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
-\end{comment}
+
 \end{proof}
@@
 \bibitem{brenner-butler} S. Benner, M.~C.~R. Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
-\bibitem{cc} P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
+\bibitem{cc}
+Caldero, P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
 Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).

### 2017-12-15 Grassmannian_cells.tex
Finshed section 5 and inserted 4.9-4.11

--- 2017-12-12 Grassmannian_cells.tex
@@
 \newcommand{\Gr}{\mathrm{Gr}}
+\newcommand{\Gl}{\mathrm{Gl}}
+\newcommand{\Ind}{\mathrm{Ind}}
 \renewcommand{\AA}{\mathbb{A}}
@@
 \newcommand{\NN}{\mathbb{N}}
-
+\newcommand{\rk}{\mathrm{rk}}
 \newcommand{\Ext}{\operatorname{Ext}}
@@
 While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
-\begin{lemma}
+\begin{lemma}\label{compatibleGSigma}
   For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
+\begin{proposition}\label{indecomposables}Let $m\geq 1$.
+Let $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
+Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
+The following holds:
+\begin{enumerate}
+\item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
+\item The set indecomposable representations of dimension $\alpha(m,r)$ ist given by a non-empty open subset of $R_\alpha(K(n))$. 
+\item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+
+As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
+Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
+This means that $M\in R_\alpha(K(n))$ is given by a matrix $M\in\CC^{d\times n}$ where the $i^{\mathrm{th}}$ column stands for $M_{a_i}$.
+Now $M$ is indecomposable if and only if $\rk{M}=d$.
+Indeed, it is clear that $S_1^{m}$ splits up if and only if $\rk{M}=d-m$.
+
+This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$  are in one-to-one correspondence with matrices of maximal rank.
+Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M$.
+Now it straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
+This shows the first statement.
+
+It can be checked straightforwardly that $\alpha(1,d)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
+Thus the roots $\alpha(m,d)$ are also Schur roots.
+It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{\alpha(m,r)}(K(n))$, see for example \cite{sch}.
+This shows the second statement.
+
+For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
+As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
+\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
+\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
+As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
+\end{proof}
+\begin{remark}There is a more elegant way to prove Proposition \ref{indecomposables} using the notion of stability and moduli spaces.
+Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
+We inserted this proof because the notion of stability were only used at this point and we wanted to keep this part as simple as possible.
+\end{remark}
+
 \begin{theorem}
@@
 \begin{proof}
-  \footnote{The proof using moduli spaces needs to be written}
+Let $g\in\Gl_n(\CC)$.
+We first show that $\Gr_\bfe(g.P_{m+1}^V)=\Gr_\bfe(P_{m+1}^V)$.
+Assume that $P_{m+1}^V$ is given by the linear maps $M_{a_i}$.
+Then $g.P_{m+1}^V$ is given by the matrices $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+Let $(U_1,U_2)\in\Gr_\bfe(g.P_{m+1}^V)$.
+Then we have
+\[M_{a_i}(U_2)\subset U_1 \text{ for all } i=1,\ldots,n\Leftrightarrow \left(\sum\limits_{j=1}^n g_{ij}M_{a_j}\right)(U_2)\subset U_1 \text{ for all } i=1,\ldots,n.\]
+Note that we have $g^{-1}.(g.P_{m+1}^V)=P_{m+1}^V$ which shows the non-obvious direction.
+
+Together with Proposition \ref{indecomposables} this shows that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
+With other words we use that all indecomposables are truncated preprojectives.
+
+As the indecomposables form a dense open subset of all representations, we found a dense subset whose quiver Grassmannians for a fixed $\bfe$ are isomorphic.
+But now the same proof as for exceptional roots applies in order to show that these quiver Grassmannians need to be smooth, see \cite[Corollary 4]{cr}.
+ % \footnote{The proof using moduli spaces needs to be written}
   %Both claims are proven via the same geometric construction.
@@
 
-Thus let $\pi_{m,\uj'}^{\bf j'}(U)= 0$ with $U\subset \tilde P_{m}^{\uj'}$.
+Fix $\tbff$ and $\tbfg$ together with cell decompositions 
+\[\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})=\coprod_{i\in I} B_i,\quad \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})=\coprod_{k\in K} C_k\]
+such that the cell decomposition of $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is compatible with $\pi^{\bf j}_{m,\uj}$.
+To finish the prove, it suffices to show that the cell decomposition of for $\Gr_{\tbff+\tbfg}(\tilde P_m^{\uj'})$ is compatible with $\pi^{\bf j'}_{m,\uj'}$ because every projection onto a truncated preprojective is of this shape and we did not put (?) any restrictions on ${\bf j'}$.
+
+We distinguish the following cases
+\begin{itemize}
+\item $\tbfg =\udim \tilde P_{m}^{\uj}$.
+\item $\tbfg \neq \udim \tilde P_{m}^{\uj}$ with cells $B_i$ and $C_k$ such that $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$.
+ \item $\tbfg \neq \udim \tilde P_{m}^{\uj}$ with cells $B_i$ and $C_k$ such that $\pi^{\bf j}_{m,\uj}(V)\neq 0$ for all $V\in C_k$.
+
+\end{itemize}
+In the first case, we have $\Gr_\tbfg(\tilde P_{m}^{\uj})=\{\pt\}$ and thus there exists a single cell $C_0=\mathbb{A}^0$.
+Fix a cell $B_i\subset\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$.
+As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fibre over $B_i\times C_0$ is empty or that the fibre is of constant dimension building a new cell $CB_i$.
+For all representations $U\in CB_i$ we have $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$ because $\pi_{m,\uj}^{\bf j}$ is surjective and $\pi_{m,\uj'}^{j_l}(U)=\tilde P_{m}^{\uj}$.
+
+In the second case, the fibre over $B_i\times C_k$ is non empty and of constant dimension building a new cell $CB_{i,k}$.
+As we have $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$, it follows that $\pi^{\bf j'}_{m,\uj'}(U)=0$ for all representations $U\in (CB)_{i,k}$.
+
+In the third case, an analogous argument shows that $\pi^{\bf j'}_{m,\uj'}(U)\neq 0$ for all $U\in (CB)_{i,k}$.
+
+%Thus let $\pi_{m,\uj'}^{\bf j'}(U)= 0$ with $U\subset \tilde P_{m}^{\uj'}$.
 Then we either have $\pi_{m,\uj'}^{j_l}(U)=0$ which means that $U$ comes from a subrepresentation of $\tilde P_{m,j_l}$ and $\tbfg=0$.

### 2017-12-19 Grassmannian_cells.tex
2-quivers

@@
 
+%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{lee-li-zelevinsky}.
-The confluence of these results gives rise to a combinatorial construction for the Euler characteristics of certain quiver Grassmannians.
-Our main result is a geometric explanation for this correspondence by constructing a decomposition of the quiver Grassmannians into affine cells which are labeled by compatible pairs.
+The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
+Our main result is a geometric explanation for this correspondence by constructing a decomposition of these quiver Grassmannians into affine cells which are labeled by compatible pairs.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Terminology and Preliminary results}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Representation Theory of $K(n)$}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
+\section{Quiver Grassmannians of $\widetilde{K(n)}$}
+\label{QG}
 \noindent 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Combinatorial description of non-empty cells}
-
-\begin{definition}\begin{enumerate}
-\item A $2$-quiver is a triple $Q=(Q_0,Q_1,Q_2)$ consisting of a set of vertices $Q_0$, a set of (usual) arrows $Q_1$ and a set of $2$-arrows which are arrows between full subquivers of the quiver $(Q_0,Q_1)$.
-
-\item We call a subset $\beta\subset Q_0$ successor closed if for every arrow $v:p\to q$ we have: if $p\in \beta$, then $q\in\beta$.
-
-\item We call a subset $\beta\subset Q_0$ strong successor closed if it is successor closed and, moreover, for every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$, we have: if $\Gamma(1)_0\subset \beta$, then there exists a vertex $q\in\Gamma(2)_0$ such that $q\in\beta$.
-
-\item Notion of equivalence of $2$-quivers to justify the transformation of $2$-arrows into usual arrows.
-
-\end{enumerate}
+In this section we provide a direct quiver theoretic description of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
+The key concept is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
+\begin{definition}
+  Let $Q=(Q_0,Q_1)$ be a quiver.
+  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $v:p\to q$ in $Q_1$ implies $q\in\beta$.
+
+  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
+  A \emph{2-quiver} is a pair $\tilde Q=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
+  Given a 2-quiver $\tilde Q$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed} if it is successor closed and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
+  \footnote{Include a notion of equivalence of $2$-quivers to justify the transformation of $2$-arrows into usual arrows.}
 \end{definition}
 
-The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}.
-These $2$-quivers are related to certain coefficient quivers of these representations.
-The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$.
-Hence the corresponding Euler characteristic can be computed when counting these subsets.
-It will turn out that a feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.
+%The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}.
+%These $2$-quivers are related to certain coefficient quivers of these representations.
+%The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$.
+%Hence the corresponding Euler characteristic can be computed when counting these subsets.
+%It will turn out that a feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.
 
@@
   The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
-
 \end{remark}
@@
 We recall the notion of Section \ref{QG} where we denote the arrows of $K(n)$ by $v_1,\ldots,v_n$.
-Actually, all $2$-quivers can be build from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$ where $P_2^{(n-1)}$ depends on a choice as it is a truncated preprojective representation of dimension $(1,1)$.
+Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where $P_2^{(n-1)}$ depends on a choice as it is a truncated preprojective representation of dimension $(1,1)$.
 Indeed, it is the cokernel of a short exact sequence
-\[\ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}\]
-for which we have $n-1$ choices. Without loss of generality, we make the following choice when defining
-$$P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{v_1}i^{(n-1)}_2=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1$$
-by its coefficient quiver. Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
-$$\Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.$$
+\[
+  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}
+\]
+for which we have $n$ choices.
+Without loss of generality, we make the following choice when defining
+\[
+  P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{v_1}i^{(n-1)}_2=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+\]
+by its coefficient quiver.
+Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
+\[
+  \Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.
+\]
 
@@
 \draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
-\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {$$};
-\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {$$};
-\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {$$};
-\draw[->,red] (Q41)--(E1) node[pos=.5,above] {$$};
-\draw[->,red] (Q51)--(D1) node[pos=.5,above] {$$};
-\draw[->,red] (Q61)--(B11) node[pos=.5,above] {$$};
-\draw[->,red] (Q71)--(B1) node[pos=.5,above] {$$};
-\draw[->,red] (Q81)--(A1) node[pos=.5,above] {$$};
+\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
+\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
+\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
+\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
+\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
+\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
+\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
+\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};
 
@@
 \draw[<-,red] (D)--(E) node[pos=.5,above] {};
-\draw[->,red] (Q1)--(C) node[pos=.5,above] {$$};
-\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$$};
-\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$$};
+\draw[->,red] (Q1)--(C) node[pos=.5,above] {};
+\draw[->,red] (Q2)--(B1) node[pos=.5,above] {};
+\draw[->,red] (Q2b)--(B) node[pos=.5,above] {};
 
@@
   Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{(k)}$ (resp. $\tilde P_{m+1}^{(k)}$) and consider the short exact sequence
-\[\ses{\tilde P_m}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}.\]
+  \[
+    \ses{\tilde P_m}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}.
+  \]
   Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{(k)}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{(k)}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
@@
   But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{(k)}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{(k)}}$ by a $2$-arrow.
-
-\end{proof}
-
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{thebibliography}{10}

### 2017-12-19 Grassmannian_cells.tex
reorganized section 5

@@
 Moreover, sinks become sources and vice versa.
-For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
+For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
 we have
-\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\end{align}
-It is rather important that $\tilde P_{2m}$ and $\tilde P_{2m-1}$ live on two different components of the universal covering quiver.
+\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.\end{align}
+It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
 
 \begin{remark}\begin{enumerate}
-\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e.
-$w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.
-Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-\item Then we have 
+\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.
+
+%Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
+\item We have 
 $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
@@
 
-\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,1)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
+Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.
+
+\item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
 \end{enumerate}
 \end{remark}
-
+Let
+$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
+As we fixed the number of arrows, we drop the $n$ in what follows.
+
+With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+More detailed, we obtain a sequence of preprojective representations
+$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
+
+\begin{lemma}\label{le:properties}The following holds:
+\begin{enumerate}
+ \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
+   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
+   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
+		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
+		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
+		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+
+		\end{enumerate}
+\end{lemma} 
+\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
+
+The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
+
+As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
+
+For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
+Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
+Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
+
+\end{proof} 
 %To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
 
-Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.
+In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
+Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
+These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
 
@@
 \end{example}
-
-The representation $\tilde P_2$ is given by the following coefficient quiver:
-
-\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
-The coefficient quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
+We use this fact and do not state the particular maps defining the lifts.
+In this example, we just state the support of the representation including those dimensions which are not one.
+We call it the quiver of the representations.
+
+The representation $\tilde P_2$ is defined by the following quiver:
+
+\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
+The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
 In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
 
-Using this notation, we obtain that $\tilde P_3$ can be written as
+The representation $\tilde P_3$ is given by the quiver
 	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
-	and, moreover, $\tilde P_3^{\uj}$ is obtained when erasing the subquiver $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of the sink by one.
+	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
+Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
 The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
-	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_l}=a_{j_l}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.
-
-The support of $\tilde P_4$ is given by
+	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
+In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
+
+The representation $\tilde P_4$ is defined by
 \[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
 \mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the numbers correspond to the dimensions of the respective vertices.
+where the middle vertex is $(2,1)$.
 Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
@@
 &&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
-
-Finally, the quiver corresponding to $\tilde P_4^{(1,\ldots,l)}$ is given by
+where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
 
@@
 &\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau^{-1}$ is given by reflecting at all the sinks first and at all sources afterwards.
+where the upper vertex is again $(2,1)$.
+Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
 Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
@@
 
-The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
-With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-More detailed, we obtain a sequence of preprojective representations
-$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$
-
-Let
-$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-As we fixed the number of arrows, we drop the $n$ in what follows.
-For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ and $\uj^c=(j^c)$ where $j^c\neq j_i$ for $i=1,\ldots,n-1$.
-Clearly, $\uj^c$ is uniquely determined by $\uj$.
-
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
-Define $j_1^c$ as before.
- We say that ${\bf j}$ is admissible if 
-$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
-where $j_k^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique number satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
-\end{definition}
-
-For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
-\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}\]
-where the $\tilde P_m^{\uj}$ are lifts of truncated preprojectives (as defined in the last section).
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
-We define the admissible sequence $\delta {\bf j}$ (of length $r-1$) by
-\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\ldots,\underline{j_r}).\]
-We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r-1$.
-%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
-
-\begin{lemma}The following holds:
-  \label{le:preprojective lifts}
-  \begin{enumerate}
-    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
-   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
-   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
-    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence.
-Let ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$.
-Then we recursively have
-		\[\tilde P_{m-l,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-l+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
-		for $k=1,\ldots,r$.
-Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$%/\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}$$
-		with each admissible sequence ${\bf j}$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
-
-To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
-
-%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,j^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
-Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,j^c}^{\uj^c}$.
-Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
-
-The forth statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
-We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$.
-We use the third statement in order to successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
-Now we have $\delta^{k-1}{\bf j}(k)=(j_k^c)$.	Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
-	\end{proof}
-We denote the quotient morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$.
-Let $\ui=(i_{1},\ldots,i_{l})$.
-It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{\ui}$ where $l\leq n-1$ and $i_k\neq j_1^c$ for $k=1,\ldots, l$.
-We denote the quotient morphism from $\tilde P_m^{\ui}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\ui}^{\bf j}$.
-
-Our construction immediately yields the following lemma.
-\begin{lemma}\label{projections}
-Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
-Then we have
-\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}\]
-and, for any sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
-\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
-for $k=1,\ldots,r-1$ where $\pi_{m,j_{-1}^c}^{\underline{j_1}}:=\pi_m^{\underline{j_1}}$ and the analogous statement for $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ and $(l_1,\ldots,l_{s-1})\in I_{s-1}$ holds.
-\end{lemma}
-We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
-Therefore, we need to apply a translated version of this morphism.
-In abuse of notation, we also denote this morphism $\pi_m^{\bf j}$.
-
  We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
 \begin{lemma}\label{le:subrep}
-   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}
-
-\end{lemma}
-\begin{proof}
-Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
+
+\end{lemma}
+\begin{proof}
+Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
+
 We proceed by induction.
@@
 \[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
 where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
@@
 
-As the sequence does not split, this shows that $U'$ is an indecomposable  (reference) preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$.
+As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
 Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
@@
 \end{comment}
+
 \begin{lemma}\label{AR}\footnote{special case $m=3$}
@@
 \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
-\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$ 
+\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
 %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
-Therefore, we may consider the short exact sequence
+Therefore, we consider the short exact sequence
 \[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
@@
 
-Considering the quiver $\tilde P_{3,l}$ from above, it is clear that we obtain an exact sequence
+Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
 $$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
@@
 
-As $\tilde P_m^{\uj}$ is exceptional on the universal covering by the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}, it follows that 
+As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
 $$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
@@
 Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
-This yields the remaining results at once.
+This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
 
@@
 \end{proof}
+
+The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
+
+For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
+
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
+Define $j_1^c$ as before.
+ We say that ${\bf j}$ is admissible if 
+$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
+where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
+\end{definition}
+
+For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
+\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
+The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
+We define the admissible sequence $\delta {\bf j}$ by
+\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
+We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
+%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
+Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
+
+\begin{lemma}The following holds:
+  \label{le:preprojective lifts}
+  \begin{enumerate}
+    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
+		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
+		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
+	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
+Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
+		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
+		for $k=1,\ldots,r$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+
+To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
+
+%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
+For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
+Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
+Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
+
+The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
+We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
+We use the third statement in order to successively obtain commutative diagrams
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
+
+Finally, we consider the short exact sequence:
+
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
+Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
+%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
+	\end{proof}
+The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
+Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
+It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
+We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
+We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
+Therefore, we need to apply a translated version of this morphism.
+In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
+
+Our construction immediately yields the following lemma.
+\begin{lemma}\label{projections}
+Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
+Then we have
+\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
+Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
+\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
+for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
+\end{lemma}
 
@@
 If $m=3$, we consider the sequence
- \[\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \bullet\xrightarrow{a_{j_l}}\bullet\ar[r] & 0}\]	
-	where the kernel is clearly just a direct sum of simple representations. Recall that the Auslander-Reiten translate of $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
-	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.
-In all cases, we denote the corresponding map between quiver Grassmannians by $\Phi_{m,\uj}$. Using this notation, we obtain:
-\begin{lemma}\label{quotient}Let $m\geq 3$ and $\uj=(j_1,\ldots,j_l)\in I_l^n$. The following holds:
+ \[\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & (2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\ar[r] & 0}\]	
+instead.
+Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=(2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})$, see also Example \ref{smallm}.
+
+	%The Auslander-Reiten translate of $\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	%\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
+%
+
+For $m\geq 4$, we obtain another map between quiver Grassmannians 
+$$\Phi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,j_l})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(P(m,\uj))\times \Gr^{\tilde Q}_\tbfg(\tau \tilde P_{m}^{\uj}).$$
+For $m=3$, we obtain also a map $\Phi_{3,\uj}$ when replacing $\tau\tilde P_{m}^{\uj}$ by $\tau' \tilde P_3^{\uj}$. 
+\begin{proposition}\label{quotient}Let $m\geq 3$ and $\uj=\in I_l$. The following holds:
 \begin{enumerate}
@@
 \end{enumerate} 
-\end{lemma}
-\begin{proof}
-In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ by  $\bullet\xrightarrow{a_{j_l}}\bullet$ in which case all arguments hold in the same way.
-
-If $W=0$, from Lemma \ref{AR}, i.e. $\Hom(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=0$, we obtain a commutative diagram
+\end{proposition}
+\begin{proof}
+In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ by  $\tau'\tilde P_{3}^{(j_1,\ldots,j_l)}$ in which case all arguments hold in the same way.\footnote{das anders}
+
+If $W=0$,  we consider the following commutative diagram
 
@@
 
-Moreover, the lemma implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
-This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ which means that the induced map
+Lemma \ref{AR}.(5) implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
+This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$.
+Using Lemma \ref{AR}.(5), this means that the induced map
 \[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
-is zero.
-Therefore, the induced exact sequence splits.
+is zero. Therefore, the induced exact sequence splits.
+
 On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
  \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{(j_1,\ldots,j_{l-1})}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar[u]& 0}\]
+  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
 which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split.
-Indeed, we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{(j_1,\ldots,j_{l-1})})=0$ by Lemma \ref{AR}.
+This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{(j_1,\ldots,j_{l-1})})=0$ by Lemma ???.
 This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.
@@
 \[\Hom(\tau\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(Z,\tau\tilde P_{m}^{\uj}/W) \]
-is zero. As $\tilde P_m^{\uj}$ is exceptional on the universal covering by the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}, it follows that 
+is zero. As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} yield  
 $$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$ Since the map $\kk=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective and thus bijective, together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.
@@
 Thus it remains to show that $\Psi_{m,\uj}(U,\tilde P_{m}^{\uj})$ is not empty if $W\neq 0$.
-Since $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l})$ is surjective which already means that there exists a commutative diagram as above which, in turn, shows that the fiber is not empty.
+Since $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l})$ is surjective which already means that there exists a commutative diagram as above.
+This shows that the fiber is not empty.
 \end{proof}
@@
 \end{proposition}
-\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m}^{\uj}$ is preprojective.
+\begin{proof}By Lemma \ref{le:subrep}, any subrepresentation $V\subsetneq \tilde P_{m}^{\uj}$ is preprojective.
 But the representation $\tilde P_{m-1,l_j}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
 Thus we have $\Ext(V,\tilde P_{m-1,l_j}/U)=0$.
-If $U=0$, we have $\Ext(V,\tilde P_{m-1,l_j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
-
-The second statement follows directly from Lemma \ref{quotient}.
+If $U=0$, we have $\Ext(V,\tilde P_{m-1,l_j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
+
+The second statement follows directly from Proposition \ref{quotient}.
 
@@
 
-In order to prove the claim, we prove the more general statement:
+In order to prove the claim, we prove the following more general statement:
 \vs
@@
 
-We proceed by induction on $m$ and reverse induction on $l$.
+We proceed by induction on $m$ and reverse (?) induction on $l$.
 Let $\uj'=(j_1,\ldots,j_{l-1})$.
 If $m=1$ or $m=2$, the statement is straightforward for arbitrary $l$ as all quiver Grassmannians are points.
-For general $m$, we consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ induces a map between quiver Grassmannians
+For general $m$, we consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ which induces a map between quiver Grassmannians
 $$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
@@
 
-If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ which satisfy $\pi_m^{\bf i}(U)\neq 0$, but also over those whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)= 0$.
-By Theorem \ref{vb}, the claim follows.
-
-Thus it remains to show that there exists a cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ which is compatible with a fixed $\pi_{m,\uj'}^{\bf j'}$ where ${\bf j'}=(\underline{j'_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
-Recall that we have $\pi_{m,\uj'}^{\bf j'}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{projections}.
+If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, by Proposition \ref{fibers}, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$.
+In particular, they are constant over cells whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)\neq 0$, but also over those whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)= 0$.
+By Theorem \ref{vb}, it follows that $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ has a cell decomposition.
+
+Thus it remains to show that this cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ is compatible with $\pi_{m,\uj'}^{\bf j}$ where ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
+Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{projections}.
 
@@
 such that the cell decomposition of $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is compatible with $\pi^{\bf j}_{m,\uj}$.
-To finish the prove, it suffices to show that the cell decomposition of for $\Gr_{\tbff+\tbfg}(\tilde P_m^{\uj'})$ is compatible with $\pi^{\bf j'}_{m,\uj'}$ because every projection onto a truncated preprojective is of this shape and we did not put (?) any restrictions on ${\bf j'}$.
+To finish the prove, it suffices to show that the cell decomposition of for $\Gr_{\tbff+\tbfg}(\tilde P_m^{\uj'})$ is compatible with $\pi^{\bf j}_{m,\uj'}$ because every projection onto a truncated preprojective is of this shape and we did not impose any restrictions on ${\bf j}$.
 
@@
 	\bibitem{wei} Weist, T.: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
+	\bibitem{wei2} Weist, T.: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
+%\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).
 \end{thebibliography}

### 2017-12-20 Grassmannian_cells.tex
Section 4 reorganization
Major reorganization - part 1

@@
 \end{abstract}
+
+\setcounter{tocdepth}{2}
+
 \maketitle
 
+\tableofcontents
 %%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Terminology and Preliminary results}
-
-Incorporate this into other sections...
+\section{Quiver Covering Theory}
+
+For an introduction to covering theory we refer to \cite{gab}.
+Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
+We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
+
+Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$.
+In general, considering the linear map  
+\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
+we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
+
+Let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
+\begin{definition}
+  The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$, where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
+
+  The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$, where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
+
+  We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
+$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \tilde X=X$), where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
+$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
+\end{definition}
+
+Note that in our definition every covering quiver has infinitely many connected components.
+But every connected component is a covering in the sense of \cite{gab}.
+As indecomposable representations live on one component this makes no difference.
+Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
 
@@
 \end{proof}
+
+The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp. dimension vectors) are equivalent in this case.
+The analogous observation can also be made for $\tilde Q$.
+If $M$ is a representation of $\hat Q$ (resp. $\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp. $w\in W_Q$) by $M_\chi$ (resp. $M_w$).
+
 As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
@@
 
-Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$.
-In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
-we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{torusaction}
-
-Move this somewhere...
-
-For an introduction to covering theory we refer to \cite{gab}.
-Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
-Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.
-\begin{definition}
-The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
-
-The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
-
-We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
-$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
-$G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
-$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
-\end{definition}
-Note that in our definition every covering quiver has infinitely many connected components.
-But every connected component is a covering in the sense of \cite{gab}.
-As indecomposable representations live on one component this makes no difference.
-Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
-Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
-The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
-We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp.
-dimension vectors) are equivalent in this case.
-The analogous observation can also be made for $\tilde Q$.
-If $M$ is a representation of $\hat Q$ (resp.
-$\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp.
-$w\in W_Q$) by $M_\chi$ (resp.
-$M_w$).
 
@@
 \end{theorem}
-
-Move this???
-
-Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
-\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
-which is also called Caldero-Chapoton map.
-By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
-Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
-$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
-The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
-\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
-
-The following is proved in \cite[Section 3]{cefr}.
-\begin{theorem}\label{vb}
-If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
-In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
-\end{theorem}
-%\begin{proof}\footnote{sketch, double-check}
-
-%As $X$ and $Y$ are projective, they are compact.
-As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
-This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
-
-%\end{proof}
-
-%%%
 
@@
 \end{itemize}
-Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
-More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
-Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
-\begin{lemma}
-  \label{le:hom equivariance}
-  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
-  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
-\end{lemma}
-\begin{proof}
-  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
-  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
-  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
-  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
-\end{proof}
-\begin{corollary}
-  \label{cor:indecomposability}
-  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
-\end{corollary}
-\begin{proof}
-  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
-  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
-\end{proof}
 
@@
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
-
-While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
-\begin{lemma}\label{compatibleGSigma}
-  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
-\end{lemma}
-\begin{proof}
-  We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
-  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{a_i})$, where $M'_2$ fits into the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
-  and $M'_{a_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
-  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,M''_{a_i})$ with 
-  \[M''_{a_i}=\sum\limits_{j=1}^n g_{ij}M'_{a_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
-  In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
-  i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
-\end{proof}
 
@@
 \end{remark}
+
+Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
+%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
+Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
+Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
+%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
+For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
+
+\begin{lemma}
+  \label{le:injective evaluation maps}
+  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+\end{lemma}
+%%%%%%%%%%%%%%%%%%%
+% needs polishing %
+%%%%%%%%%%%%%%%%%%%
+\begin{proof}
+  \footnote{This needs to be cleaned up, the proof seems false as written.}
+  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
+  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
+\end{proof}
+
+In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
+Following Lemma~\ref{le:injective evaluation maps} we define the following.
+\begin{definition}
+  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  \begin{equation}
+    \label{eq:truncated preprojectives}
+    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
+  \end{equation}
+\end{definition}
+\begin{remark}
+  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
+\end{remark}
+
+\begin{lemma}
+  \label{le:basic homological properties}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+\end{lemma}
+\begin{proof}
+  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
+$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
+$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
+  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+\end{proof}
+
+\begin{corollary}
+  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
+  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+\end{proof}
+
+\subsection{Understanding Truncated Preprojectives}
+
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
+\begin{equation}
+  \label{eq:AR sequence}
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+\end{equation}
+where the right-hand morphism is the natural evaluation map.
+\begin{corollary}
+  \label{cor:preprojective homomorphism duality}
+  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
+\end{corollary}
+\begin{proof}
+  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
+  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
+  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
+  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
+  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
+\end{proof}
+\begin{remark}
+  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
+  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
+  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
+\end{remark}
+Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
+Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
+The next observation is essential for the results to follow.
+\begin{proposition}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
+\end{proposition}
+\begin{proof}
+  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
+  Indeed, we have
+  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
+\end{proof}
+
+The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
+\begin{lemma}
+  \label{le:unique morphisms}
+  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
+\end{lemma}
+\begin{proof}
+  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
+  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated homomorphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
+  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
+\end{proof}
+
+\begin{corollary}
+    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
+  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
+  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
+  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated extensions}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
+  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where $U\subset V$ satisfies $\dim(V/U)=1$.
+\end{lemma}
+\begin{proof}
+  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
+  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
+  This gives rise to the following commutative diagram:
+  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
+    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
+    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
+    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
+   & 0 & 0 & & }\]
+  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
+  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
+  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique truncated extension}
+  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  \begin{equation}
+    \label{eq:unique extension}
+    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
+  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
+    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
+    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
+    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
+\end{proof}
+\begin{corollary}
+  \label{cor:truncated preprojective isomorphism}
+  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
+  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{proof}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
+\end{corollary}
+
+\begin{lemma}
+  \label{le:more truncated homomorphisms}
+  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
+  \begin{enumerate}
+    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
+    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
+  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
+  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
+
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
+\end{proof}
+\begin{remark}
+  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
+  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
+\end{remark}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
+  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
+  The result immediately follows from this.
+\end{proof}
+\begin{remark}
+  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
+\end{remark}
+
+\begin{lemma}
+  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
+\end{lemma}
+
+\begin{lemma}
+  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
+More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
+\end{lemma}
+\begin{proof}
+  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
+  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
+  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
+  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
+  This proves the first claim.
+
+  It remains to show that $\tilde V=\bar{\bar{V}}$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated exact sequences}
+  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
+\end{lemma}
+\begin{proof}
+  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
+    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
+    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
+  It follows that the sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
+  is exact.
+  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
+
+  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
+\end{proof}
+
+For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
+Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
+\begin{lemma}
+  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  splits for every proper subspace $W\subsetneq V$.
+\end{lemma}
+\begin{proof}
+  We proceed by induction on $\codim_V W$.  
+  When $\codim_V W=1$, we have an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
+  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
+
+  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
+  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
+  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
+  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
+  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
+  The result now follows since the outer square is also a pullback.
+\end{proof}
+\begin{corollary}
+  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+\end{corollary}
+
+\begin{lemma}
+  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  This occurs (?) if and only if the composed morphism
+  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
+  is nonzero.
+\end{lemma}
+\begin{proof}
+  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
+  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
+    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
+    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
+  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
+
+  and
+  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
+\end{proof}
+
+\subsection{Results on the universal cover $\widetilde{K(n)}$}
+
+We fix a natural number $n\geq 3$.
+We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
+For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
+Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
+Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+Moreover, sinks become sources and vice versa.
+For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
+we have
+\begin{align}
+  \label{recursive}
+  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
+\end{align}
+It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+
+\begin{remark}
+  \begin{enumerate}
+    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. 
+      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
+    \item We have 
+      $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
+      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
+
+      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
+    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
+\end{enumerate}
+\end{remark}
+Let
+$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
+As we fixed the number of arrows, we drop the $n$ in what follows.
+
+With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+More detailed, we obtain a sequence of preprojective representations
+$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
+
+\begin{lemma}\label{le:properties}The following holds:
+\begin{enumerate}
+ \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
+   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
+   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
+		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
+		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
+		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+
+		\end{enumerate}
+\end{lemma} 
+\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
+
+The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
+
+As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
+
+For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
+Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
+Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
+
+\end{proof} 
+%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
+
+In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
+Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
+These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
+
+\begin{example}\label{smallm}[The cases $m=2,3,4$]
+\end{example}
+
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
+We use this fact and do not state the particular maps defining the lifts.
+In this example, we just state the support of the representation including those dimensions which are not one.
+We call it the quiver of the representations.
+
+The representation $\tilde P_2$ is defined by the following quiver:
+
+\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
+The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
+
+The representation $\tilde P_3$ is given by the quiver
+	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
+	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
+Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
+The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
+In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
+
+The representation $\tilde P_4$ is defined by
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the middle vertex is $(2,1)$.
+Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
+The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
+Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
+where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the upper vertex is again $(2,1)$.
+Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
+Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
+
+%\begin{tikzpicture}[scale=1]
+%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\end{tikzpicture}
+
+\begin{remark}
+Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
+We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
+Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
+\end{remark}
+
+ We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
+\begin{lemma}\label{le:subrep}
+  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
+
+\end{lemma}
+\begin{proof}
+Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
+
+We proceed by induction.
+Clearly $\tilde P_m$ has only preprojective subrepresentations.
+We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
+Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
+Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
+Thus we get a commutative diagram
+
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
+because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
+We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
+
+As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
+Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
+Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
+But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
+
+\end{proof}
+
+%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
+
+\begin{comment} 
+DO NOT NEED THIS-------FROM HERE----
+\begin{lemma}\label{directsums}
+  \footnote{This can be proved on the quiver itself.}
+  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
+\end{lemma}
+\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
+which is also sometimes called Caldero-Chapoton map.
+
+Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
+But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
+Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
+In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
+Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
+By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
+
+In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
+\end{proof}
+
+\begin{lemma}
+  \begin{enumerate}
+    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
+    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
+      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
+      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+The first statement follows for instance by induction when applying BGP-reflections.
+\end{proof}
+----TO HERE----DO NOT NEED THIS----
+\end{comment}
+
+\begin{lemma}\label{AR}\footnote{special case $m=3$}
+ Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
+Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
+$$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
+
+ The following holds:
+\begin{enumerate}
+\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
+%\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
+What do we need?
+We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
+
+\item There exists a short exact sequences 
+\[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
+where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
+
+\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
+\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
+\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
+\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
+\end{lemma}
+\begin{proof}
+Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
+Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
+
+In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
+In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
+Therefore, we consider the short exact sequence
+\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
+and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
+As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
+
+Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
+$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
+Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
+This shows the second statement.
+
+As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
+$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
+As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
+This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
+
+%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
+This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
+
+\end{proof}
+
+The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
+
+For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
+
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
+Define $j_1^c$ as before.
+ We say that ${\bf j}$ is admissible if 
+$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
+where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
+\end{definition}
+
+For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
+\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
+The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
+We define the admissible sequence $\delta {\bf j}$ by
+\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
+We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
+%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
+Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
+
+\begin{lemma}The following holds:
+  \label{le:preprojective lifts}
+  \begin{enumerate}
+    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
+		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
+		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
+	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
+Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
+		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
+		for $k=1,\ldots,r$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+
+To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
+
+%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
+For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
+Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
+Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
+
+The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
+We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
+We use the third statement in order to successively obtain commutative diagrams
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
+
+Finally, we consider the short exact sequence:
+
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
+Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
+%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
+	\end{proof}
+The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
+Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
+It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
+We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
+We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
+Therefore, we need to apply a translated version of this morphism.
+In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
+
+Our construction immediately yields the following lemma.
+\begin{lemma}\label{projections}
+Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
+Then we have
+\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
+Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
+\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
+for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
+\end{lemma}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quiver Grassmannians}
+\label{QG}
+
+\subsection{Action on arrows}
+Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
+More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
+\begin{lemma}
+  \label{le:hom equivariance}
+  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
+  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
+\end{lemma}
+\begin{proof}
+  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
+  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
+  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
+  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
+\end{proof}
+\begin{corollary}
+  \label{cor:indecomposability}
+  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
+\end{corollary}
+\begin{proof}
+  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
+  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
+\end{proof}
+
+%Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
+%Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
+%With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+%Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
+
+While the reflection functors are not $GL_n(\CC)$-equivariant, they do admit the following twisted equivariance.
+\begin{lemma}\label{compatibleGSigma}
+  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
+\end{lemma}
+\begin{proof}
+  We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
+  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{a_i})$, where $M'_2$ fits into the following exact sequence:
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
+  and $M'_{a_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
+  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,M''_{a_i})$ with 
+  \[M''_{a_i}=\sum\limits_{j=1}^n g_{ij}M'_{a_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
+  In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
+  i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
+\end{proof}
+
 %\begin{corollary}
@@
 
-Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
-%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
-Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
-Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
-For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
 %\begin{lemma}
@@
 %\end{proof}
-\begin{lemma}
-  \label{le:injective evaluation maps}
-  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
-\end{lemma}
-%%%%%%%%%%%%%%%%%%%
-% needs polishing %
-%%%%%%%%%%%%%%%%%%%
-\begin{proof}
-  \footnote{This needs to be cleaned up, the proof seems false as written.}
-  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
-  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
-\end{proof}
-
-In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
+
 %Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
@@
 %\end{proof}
-Following Lemma~\ref{le:injective evaluation maps} we define the following.
-\begin{definition}
-  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
-  \begin{equation}
-    \label{eq:truncated preprojectives}
-    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
-  \end{equation}
-\end{definition}
-\begin{remark}
-  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
-\end{remark}
 
@@
 
-For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
-\begin{equation}
-  \label{eq:AR sequence}
-  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
-\end{equation}
-where the right-hand morphism is the natural evaluation map.
-\begin{corollary}
-  \label{cor:preprojective homomorphism duality}
-  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
-\end{corollary}
-\begin{proof}
-  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
-  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
-  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
-  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
-  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
-\end{proof}
-\begin{remark}
-  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
-  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
-  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
-\end{remark}
-Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
-Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
-The next observation is essential for the results to follow.
-\begin{proposition}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
-\end{proposition}
-\begin{proof}
-  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
-  Indeed, we have
-  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
-\end{proof}
-
-\begin{lemma}
-  \label{le:basic homological properties}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
-  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{lemma}
-\begin{proof}
-  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
-$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
-  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{proof}
-
-\begin{corollary}
-  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
-  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-\end{proof}
-
-The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
-\begin{lemma}
-  \label{le:unique morphisms}
-  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
-  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-\end{lemma}
-\begin{proof}
-  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
-  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
-  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:irreducible morphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, and $W\subsetneq V$ with $\codim_V W=1$, the unique morphism $P_{m+1}^W\to P_{m+1}^V$ is irreducible.
-\end{lemma}
-In particular, the poset $Gr(H_m)$, thought of as a directed graph, can be identified with a subset of the Auslander-Reiten quiver of $K(n)$.
-
-\begin{lemma}
-  \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
-  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
-\end{proof}
-
-\begin{corollary}
-    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
-  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
-  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
-  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated extensions}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
-  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where $U\subset V$ satisfies $\dim(V/U)=1$.
-\end{lemma}
-\begin{proof}
-  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
-  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
-  This gives rise to the following commutative diagram:
-  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
-    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
-    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
-    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
-   & 0 & 0 & & }\]
-  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
-  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
-  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
-\end{proof}
-
-\begin{lemma}
-  \label{le:unique truncated extension}
-  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
-  \begin{equation}
-    \label{eq:unique extension}
-    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
-  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
-    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
-    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
-    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
-\end{proof}
-\begin{corollary}
-  \label{cor:truncated preprojective isomorphism}
-  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
-  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{proof}
-\begin{corollary}
-  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
-\end{corollary}
-
-\begin{lemma}
-  \label{le:more truncated homomorphisms}
-  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
-  \begin{enumerate}
-    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
-    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
-  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
-  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
-
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
-\end{proof}
-\begin{remark}
-  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
-  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
-\end{remark}
-\begin{corollary}
-  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
-  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
-  The result immediately follows from this.
-\end{proof}
-\begin{remark}
-  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
-\end{remark}
-
-\begin{lemma}
-  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
-\end{lemma}
-
-\begin{lemma}
-  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
-More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
-\end{lemma}
-\begin{proof}
-  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
-  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
-  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
-  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
-  This proves the first claim.
-
-  It remains to show that $\tilde V=\bar{\bar{V}}$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated exact sequences}
-  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
-\end{lemma}
-\begin{proof}
-  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
-    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
-    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
-  It follows that the sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
-  is exact.
-  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
-
-  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
-\end{proof}
-
-For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
-\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
-Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
-\begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  splits for every proper subspace $W\subsetneq V$.
-\end{lemma}
-\begin{proof}
-  We proceed by induction on $\codim_V W$.  
-  When $\codim_V W=1$, we have an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
-  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
-
-  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
-  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
-  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
-  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
-  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
-  The result now follows since the outer square is also a pullback.
-\end{proof}
-\begin{corollary}
-  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
-  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-\end{corollary}
-
-\begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  This occurs (?) if and only if the composed morphism
-  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
-  is nonzero.
-\end{lemma}
-\begin{proof}
-  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
-  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
-    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
-    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
-  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
-
-  and
-  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quiver Grassmannians of $\widetilde{K(n)}$}
-\label{QG}
-\noindent 
-We fix a natural number $n\geq 3$.
-We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
-Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
-Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
-Moreover, sinks become sources and vice versa.
-For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
-we have
-\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.\end{align}
-It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
-
-\begin{remark}\begin{enumerate}
-\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.
-
-%Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-\item We have 
-$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
-for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
-
-Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.
-
-\item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
-\end{enumerate}
-\end{remark}
-Let
-$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-As we fixed the number of arrows, we drop the $n$ in what follows.
-
-With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-More detailed, we obtain a sequence of preprojective representations
-$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
-
-\begin{lemma}\label{le:properties}The following holds:
-\begin{enumerate}
- \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
-   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
-   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
-		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
-		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
-		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
-
-		\end{enumerate}
-\end{lemma} 
-\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
-
-The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
-
-As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
-
-For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
-Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
-Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
-
-\end{proof} 
-%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
-
-In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
-Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
-These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
-
-\begin{example}\label{smallm}[The cases $m=2,3,4$]
-\end{example}
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
-We use this fact and do not state the particular maps defining the lifts.
-In this example, we just state the support of the representation including those dimensions which are not one.
-We call it the quiver of the representations.
-
-The representation $\tilde P_2$ is defined by the following quiver:
-
-\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
-The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
-
-The representation $\tilde P_3$ is given by the quiver
-	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
-	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
-Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
-The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
-	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
-
-The representation $\tilde P_4$ is defined by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the middle vertex is $(2,1)$.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
-where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the upper vertex is again $(2,1)$.
-Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
-Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-
-\begin{remark}
-Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
-We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
-Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
-\end{remark}
-
- We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
-\begin{lemma}\label{le:subrep}
-  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
-
-\end{lemma}
-\begin{proof}
-Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
-
-We proceed by induction.
-Clearly $\tilde P_m$ has only preprojective subrepresentations.
-We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
-Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
-Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
-Thus we get a commutative diagram
-
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
-We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-
-As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
-Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
-Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
-\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
-But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
-
-\end{proof}
-
-%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
-
-\begin{comment} 
-DO NOT NEED THIS-------FROM HERE----
-\begin{lemma}\label{directsums}
-  \footnote{This can be proved on the quiver itself.}
-  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
-\end{lemma}
-\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
-which is also sometimes called Caldero-Chapoton map.
-
-Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
-But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
-Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
-In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
-Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
-By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
-
-In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
-\end{proof}
-
-\begin{lemma}
-  \begin{enumerate}
-    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
-    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
-      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
-      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-The first statement follows for instance by induction when applying BGP-reflections.
-\end{proof}
-----TO HERE----DO NOT NEED THIS----
-\end{comment}
-
-\begin{lemma}\label{AR}\footnote{special case $m=3$}
- Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
-Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
-$$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
-
- The following holds:
-\begin{enumerate}
-\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
-%\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
-What do we need?
-We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
-
-\item There exists a short exact sequences 
-\[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
-where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-
-\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
-\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
-\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
-%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
-\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
-\end{lemma}
-\begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
-Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
-Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
-In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
-Therefore, we consider the short exact sequence
-\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
-and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
-As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
-
-Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
-$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
-Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
-This shows the second statement.
-
-As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
-$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
-As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
-Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
-This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
-
-%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
-This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
-
-\end{proof}
-
-The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
-
-For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
-
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
-Define $j_1^c$ as before.
- We say that ${\bf j}$ is admissible if 
-$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
-where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
-\end{definition}
-
-For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
-\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
-We define the admissible sequence $\delta {\bf j}$ by
-\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
-We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
-%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
-
-\begin{lemma}The following holds:
-  \label{le:preprojective lifts}
-  \begin{enumerate}
-    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
-		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
-	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
-Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
-		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
-		for $k=1,\ldots,r$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-
-To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
-
-%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
-Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
-Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
-
-The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
-We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
-We use the third statement in order to successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
-
-Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
-%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
-	\end{proof}
-The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
-Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
-It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
-We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
-We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
-Therefore, we need to apply a translated version of this morphism.
-In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
-
-Our construction immediately yields the following lemma.
-\begin{lemma}\label{projections}
-Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
-Then we have
-\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
-Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
-\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
-for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
-\end{lemma}
+\subsection{Fibrations of Quiver Grassmannians}
+
+Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
+\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
+which is also called Caldero-Chapoton map.
+By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
+Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
+$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
+The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
+\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+
+The following is proved in \cite[Section 3]{cefr}.
+\begin{theorem}\label{vb}
+If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
+In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+\end{theorem}
+%\begin{proof}\footnote{sketch, double-check}
+
+%As $X$ and $Y$ are projective, they are compact.
+As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
+This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
+
+%\end{proof}
+
+%%%
 

### 2017-12-21 Grassmannian_cells.tex
Major reorganization - part 2

@@
 \documentclass{amsart}
+
+% Commands for marginal notes
+\usepackage[draft]{say}
+\newcommand{\sayD}[1]{\say[D]{#1}}
+\newcommand{\sayT}[1]{\say[T]{#1}}
+
 \usepackage{amsmath,amssymb,latexsym,color}
@@
 \usetikzlibrary{fit}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1in,marginparwidth=0.8in, marginparsep=0.1in]{geometry}
 \usepackage{extarrows}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Torus Actions on Quiver Grassmannians}
-\label{torusaction}
+\section{Representation Theory of $K(n)$}
+
+Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
+The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
+As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
+\begin{itemize}
+  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
+  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
+\end{itemize}
+
+Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
+With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
+
+Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
+The following is well-known.
+\begin{theorem}
+  \label{th:rigids}
+  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
+  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
+\end{theorem}
+The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
+\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
+  \label{rem:reflection recursion}
+  These representations satisfy the following recursions using the reflection functors:
+  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
+  for $m\ge2$.
+  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
+\end{remark}
+
+Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
+%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
+Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
+Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
+%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
+For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
+
+\begin{lemma}
+  \label{le:injective evaluation maps}
+  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+\end{lemma}
+%%%%%%%%%%%%%%%%%%%
+% needs polishing %
+%%%%%%%%%%%%%%%%%%%
+\begin{proof}
+  \footnote{This needs to be cleaned up, the proof seems false as written.}
+  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
+  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
+\end{proof}
+In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
+
+\subsection{Truncated Preprojectives}
+\label{sec:truncated preprojectives}
+Following Lemma~\ref{le:injective evaluation maps} we define the following.
+\begin{definition}
+  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  \begin{equation}
+    \label{eq:truncated preprojectives}
+    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
+  \end{equation}
+\end{definition}
+\begin{remark}
+  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
+\end{remark}
+
+\begin{lemma}
+  \label{le:basic homological properties}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+\end{lemma}
+\begin{proof}
+  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
+$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
+$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
+  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+\end{proof}
+
+\begin{corollary}
+  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
+  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+\end{proof}
+
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
+\begin{equation}
+  \label{eq:AR sequence}
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+\end{equation}
+where the right-hand morphism is the natural evaluation map.
+\begin{corollary}
+  \label{cor:preprojective homomorphism duality}
+  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
+\end{corollary}
+\begin{proof}
+  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
+  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
+  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
+  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
+  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
+\end{proof}
+\begin{remark}
+  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
+  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
+  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
+\end{remark}
+Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
+Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
+The next observation is essential for the results to follow.
+\begin{proposition}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
+\end{proposition}
+\begin{proof}
+  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
+  Indeed, we have
+  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
+\end{proof}
+
+The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
+\begin{lemma}
+  \label{le:unique morphisms}
+  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
+\end{lemma}
+\begin{proof}
+  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
+  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated homomorphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
+  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
+\end{proof}
+
+\begin{corollary}
+    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
+  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
+  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
+  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated extensions}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
+  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where $U\subset V$ satisfies $\dim(V/U)=1$.
+\end{lemma}
+\begin{proof}
+  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
+  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
+  This gives rise to the following commutative diagram:
+  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
+    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
+    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
+    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
+   & 0 & 0 & & }\]
+  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
+  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
+  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique truncated extension}
+  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  \begin{equation}
+    \label{eq:unique extension}
+    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
+  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
+    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
+    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
+    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
+\end{proof}
+\begin{corollary}
+  \label{cor:truncated preprojective isomorphism}
+  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
+  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{proof}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
+\end{corollary}
+
+\begin{lemma}
+  \label{le:more truncated homomorphisms}
+  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
+  \begin{enumerate}
+    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
+    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
+  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
+  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
+
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
+\end{proof}
+\begin{remark}
+  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
+  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
+\end{remark}
+\begin{corollary}
+  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
+  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
+  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
+  The result immediately follows from this.
+\end{proof}
+\begin{remark}
+  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
+\end{remark}
+
+\begin{lemma}
+  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
+\end{lemma}
+
+\begin{lemma}
+  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
+More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
+\end{lemma}
+\begin{proof}
+  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
+  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
+  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
+  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
+  This proves the first claim.
+
+  It remains to show that $\tilde V=\bar{\bar{V}}$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:truncated exact sequences}
+  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
+\end{lemma}
+\begin{proof}
+  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
+    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
+    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
+  It follows that the sequence
+  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
+  is exact.
+  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
+
+  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
+\end{proof}
+
+For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
+Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
+\begin{lemma}
+  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  splits for every proper subspace $W\subsetneq V$.
+\end{lemma}
+\begin{proof}
+  We proceed by induction on $\codim_V W$.  
+  When $\codim_V W=1$, we have an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
+  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
+
+  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
+  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
+  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
+  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
+  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
+  The result now follows since the outer square is also a pullback.
+\end{proof}
+\begin{corollary}
+  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+\end{corollary}
+
+\begin{lemma}
+  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  This occurs (?) if and only if the composed morphism
+  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
+  is nonzero.
+\end{lemma}
+\begin{proof}
+  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
+  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
+    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
+    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
+  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
+  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  if and only if the lower pushout sequence below splits: 
+  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
+  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
+  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
+
+  and
+  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
+\end{proof}
+
+\subsection{Lifting to $\widetilde{K(n)}$}
+
+We fix a natural number $n\geq 3$.
+We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
+For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
+Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
+Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+Moreover, sinks become sources and vice versa.
+For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
+we have
+\begin{align}
+  \label{recursive}
+  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
+\end{align}
+It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+
+\begin{remark}
+  \begin{enumerate}
+    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. 
+      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
+    \item We have 
+      $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
+      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
+
+      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
+    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
+\end{enumerate}
+\end{remark}
+Let
+$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
+As we fixed the number of arrows, we drop the $n$ in what follows.
+
+With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
+More detailed, we obtain a sequence of preprojective representations
+$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
+
+\begin{lemma}\label{le:properties}The following holds:
+\begin{enumerate}
+ \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
+   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
+   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
+		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
+		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
+		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+
+		\end{enumerate}
+\end{lemma} 
+\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
+
+The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
+
+As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
+
+For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
+Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
+Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
+
+\end{proof} 
+%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
+
+In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
+Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
+These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
+
+\begin{example}\label{smallm}[The cases $m=2,3,4$]
+\end{example}
+
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
+We use this fact and do not state the particular maps defining the lifts.
+In this example, we just state the support of the representation including those dimensions which are not one.
+We call it the quiver of the representations.
+
+The representation $\tilde P_2$ is defined by the following quiver:
+
+\begin{align*}
+  \xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}
+\end{align*}
+The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
+
+The representation $\tilde P_3$ is given by the quiver
+	\begin{align*}
+          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}
+        \end{align*}
+	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
+Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
+The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+	\begin{align*}
+          \xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}
+        \end{align*}
+In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
+
+The representation $\tilde P_4$ is defined by
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the middle vertex is $(2,1)$.
+Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
+The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
+Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
+where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+where the upper vertex is again $(2,1)$.
+Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
+Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
+
+%\begin{tikzpicture}[scale=1]
+%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\end{tikzpicture}
+
+\begin{remark}
+Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
+We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
+Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
+\end{remark}
+
+ We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
+\begin{lemma}\label{le:subrep}
+  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
+
+\end{lemma}
+\begin{proof}
+Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
+
+We proceed by induction.
+Clearly $\tilde P_m$ has only preprojective subrepresentations.
+We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
+Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
+Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
+Thus we get a commutative diagram
+
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
+because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
+We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
+
+As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
+Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
+Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
+But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
+
+\end{proof}
+
+%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
+
+\begin{comment} 
+DO NOT NEED THIS-------FROM HERE----
+\begin{lemma}\label{directsums}
+  \footnote{This can be proved on the quiver itself.}
+  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
+\end{lemma}
+\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
+which is also sometimes called Caldero-Chapoton map.
+
+Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
+But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
+Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
+In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
+Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
+By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
+
+In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
+\end{proof}
+
+\begin{lemma}
+  \begin{enumerate}
+    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
+    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
+      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
+      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+The first statement follows for instance by induction when applying BGP-reflections.
+\end{proof}
+----TO HERE----DO NOT NEED THIS----
+\end{comment}
+
+\begin{lemma}\label{AR}\footnote{special case $m=3$}
+ Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
+Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
+$$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
+
+ The following holds:
+\begin{enumerate}
+\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
+%\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
+What do we need?
+We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
+
+\item There exists a short exact sequences 
+\[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
+where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
+
+\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
+\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
+\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
+\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
+\end{lemma}
+\begin{proof}
+Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
+Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
+
+In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
+In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
+Therefore, we consider the short exact sequence
+\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
+and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
+As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
+
+Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
+$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
+Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
+This shows the second statement.
+
+As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
+$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
+As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
+This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
+
+%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
+This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
+
+\end{proof}
+
+The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
+
+For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
+
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
+Define $j_1^c$ as before.
+ We say that ${\bf j}$ is admissible if 
+$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
+where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
+\end{definition}
+
+For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
+\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
+The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
+We define the admissible sequence $\delta {\bf j}$ by
+\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
+We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
+%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
+Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
+
+\begin{lemma}The following holds:
+  \label{le:preprojective lifts}
+  \begin{enumerate}
+    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
+		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
+		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
+	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
+Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
+		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
+		for $k=1,\ldots,r$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+
+To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
+
+%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
+For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
+Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
+Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
+
+The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
+We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
+We use the third statement in order to successively obtain commutative diagrams
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
+
+Finally, we consider the short exact sequence:
+
+\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
+Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
+%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
+	\end{proof}
+The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
+Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
+It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
+We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
+We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
+Therefore, we need to apply a translated version of this morphism.
+In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
+
+Our construction immediately yields the following lemma.
+\begin{lemma}\label{projections}
+Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
+Then we have
+\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
+Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
+\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
+for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
+\end{lemma}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Quiver Grassmannians}
+\label{QG}
 
@@
 If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
-More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action.
-For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
-
-Then we have the following statement, \cite[Section 4]{bb}:
-\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
-Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
-Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
-the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
-
-In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
+More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
+For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
+\[
+  \mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}
+\]
+
+The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
+\begin{theorem}
+  \cite[Section 4]{bb}
+  Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
+  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$, where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
+  Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
+
+  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
 \end{theorem}
 
-\noindent 
+\subsection{Torus Actions}
+\label{torusaction}
+
 Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Representation Theory of $K(n)$}
-
-\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
-The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
-As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
-\begin{itemize}
-  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
-  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
-\end{itemize}
-
-Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
-With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
-Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
-
-Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
-The following is well-known.
-\begin{theorem}
-  \label{th:rigids}
-  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
-  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
-\end{theorem}
-The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
-  \label{rem:reflection recursion}
-  These representations satisfy the following recursions using the reflection functors:
-  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
-  for $m\ge2$.
-  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
-\end{remark}
-
-Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
-%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
-Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
-Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
-For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
-
-\begin{lemma}
-  \label{le:injective evaluation maps}
-  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
-\end{lemma}
-%%%%%%%%%%%%%%%%%%%
-% needs polishing %
-%%%%%%%%%%%%%%%%%%%
-\begin{proof}
-  \footnote{This needs to be cleaned up, the proof seems false as written.}
-  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
-  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
-\end{proof}
-
-In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
-Following Lemma~\ref{le:injective evaluation maps} we define the following.
-\begin{definition}
-  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
-  \begin{equation}
-    \label{eq:truncated preprojectives}
-    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
-  \end{equation}
-\end{definition}
-\begin{remark}
-  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
-\end{remark}
-
-\begin{lemma}
-  \label{le:basic homological properties}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
-  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{lemma}
-\begin{proof}
-  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
-$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
-  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{proof}
-
-\begin{corollary}
-  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
-  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-\end{proof}
-
-\subsection{Understanding Truncated Preprojectives}
-
-For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
-\begin{equation}
-  \label{eq:AR sequence}
-  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
-\end{equation}
-where the right-hand morphism is the natural evaluation map.
-\begin{corollary}
-  \label{cor:preprojective homomorphism duality}
-  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
-\end{corollary}
-\begin{proof}
-  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
-  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
-  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
-  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
-  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
-\end{proof}
-\begin{remark}
-  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
-  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
-  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
-\end{remark}
-Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
-Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
-The next observation is essential for the results to follow.
-\begin{proposition}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
-\end{proposition}
-\begin{proof}
-  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
-  Indeed, we have
-  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
-\end{proof}
-
-The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
-\begin{lemma}
-  \label{le:unique morphisms}
-  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
-  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-\end{lemma}
-\begin{proof}
-  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
-  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
-  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
-  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
-\end{proof}
-
-\begin{corollary}
-    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
-  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
-  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
-  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated extensions}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
-  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where $U\subset V$ satisfies $\dim(V/U)=1$.
-\end{lemma}
-\begin{proof}
-  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
-  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
-  This gives rise to the following commutative diagram:
-  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
-    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
-    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
-    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
-   & 0 & 0 & & }\]
-  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
-  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
-  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
-\end{proof}
-
-\begin{lemma}
-  \label{le:unique truncated extension}
-  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
-  \begin{equation}
-    \label{eq:unique extension}
-    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
-  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
-    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
-    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
-    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
-\end{proof}
-\begin{corollary}
-  \label{cor:truncated preprojective isomorphism}
-  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
-  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{proof}
-\begin{corollary}
-  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
-\end{corollary}
-
-\begin{lemma}
-  \label{le:more truncated homomorphisms}
-  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
-  \begin{enumerate}
-    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
-    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
-  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
-  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
-
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
-\end{proof}
-\begin{remark}
-  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
-  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
-\end{remark}
-\begin{corollary}
-  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
-  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
-  The result immediately follows from this.
-\end{proof}
-\begin{remark}
-  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
-\end{remark}
-
-\begin{lemma}
-  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
-\end{lemma}
-
-\begin{lemma}
-  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
-More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
-\end{lemma}
-\begin{proof}
-  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
-  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
-  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
-  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
-  This proves the first claim.
-
-  It remains to show that $\tilde V=\bar{\bar{V}}$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated exact sequences}
-  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
-\end{lemma}
-\begin{proof}
-  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
-    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
-    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
-  It follows that the sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
-  is exact.
-  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
-
-  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
-\end{proof}
-
-For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
-\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
-Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
-\begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  splits for every proper subspace $W\subsetneq V$.
-\end{lemma}
-\begin{proof}
-  We proceed by induction on $\codim_V W$.  
-  When $\codim_V W=1$, we have an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
-  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
-
-  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
-  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
-  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
-  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
-  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
-  The result now follows since the outer square is also a pullback.
-\end{proof}
-\begin{corollary}
-  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
-  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-\end{corollary}
-
-\begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  This occurs (?) if and only if the composed morphism
-  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
-  is nonzero.
-\end{lemma}
-\begin{proof}
-  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
-  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
-    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
-    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
-  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
-
-  and
-  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
-\end{proof}
-
-\subsection{Results on the universal cover $\widetilde{K(n)}$}
-
-We fix a natural number $n\geq 3$.
-We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
-Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
-Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
-Moreover, sinks become sources and vice versa.
-For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
-we have
-\begin{align}
-  \label{recursive}
-  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
-\end{align}
-It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
-
-\begin{remark}
-  \begin{enumerate}
-    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. 
-      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-    \item We have 
-      $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
-      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
-
-      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
-    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
-\end{enumerate}
-\end{remark}
-Let
-$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-As we fixed the number of arrows, we drop the $n$ in what follows.
-
-With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-More detailed, we obtain a sequence of preprojective representations
-$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
-
-\begin{lemma}\label{le:properties}The following holds:
-\begin{enumerate}
- \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
-   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
-   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
-		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
-		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
-		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
-
-		\end{enumerate}
-\end{lemma} 
-\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
-
-The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
-
-As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
-
-For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
-Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
-Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
-
-\end{proof} 
-%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
-
-In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
-Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
-These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
-
-\begin{example}\label{smallm}[The cases $m=2,3,4$]
-\end{example}
-
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
-We use this fact and do not state the particular maps defining the lifts.
-In this example, we just state the support of the representation including those dimensions which are not one.
-We call it the quiver of the representations.
-
-The representation $\tilde P_2$ is defined by the following quiver:
-
-\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
-The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
-
-The representation $\tilde P_3$ is given by the quiver
-	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
-	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
-Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
-The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
-	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
-
-The representation $\tilde P_4$ is defined by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the middle vertex is $(2,1)$.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
-where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
-where the upper vertex is again $(2,1)$.
-Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
-Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-
-\begin{remark}
-Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
-We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
-Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
-\end{remark}
-
- We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
-\begin{lemma}\label{le:subrep}
-  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
-
-\end{lemma}
-\begin{proof}
-Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
-
-We proceed by induction.
-Clearly $\tilde P_m$ has only preprojective subrepresentations.
-We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
-Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
-Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
-Thus we get a commutative diagram
-
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
-We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-
-As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
-Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
-Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
-\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
-But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
-
-\end{proof}
-
-%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
-
-\begin{comment} 
-DO NOT NEED THIS-------FROM HERE----
-\begin{lemma}\label{directsums}
-  \footnote{This can be proved on the quiver itself.}
-  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
-\end{lemma}
-\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
-which is also sometimes called Caldero-Chapoton map.
-
-Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
-But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
-Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
-In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
-Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
-By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
-
-In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
-\end{proof}
-
-\begin{lemma}
-  \begin{enumerate}
-    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
-    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
-      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
-      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-The first statement follows for instance by induction when applying BGP-reflections.
-\end{proof}
-----TO HERE----DO NOT NEED THIS----
-\end{comment}
-
-\begin{lemma}\label{AR}\footnote{special case $m=3$}
- Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
-Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
-$$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
-
- The following holds:
-\begin{enumerate}
-\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
-%\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
-What do we need?
-We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
-
-\item There exists a short exact sequences 
-\[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
-where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-
-\item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
-\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
-\item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
-%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
-\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
-\end{lemma}
-\begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
-Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
-Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
-In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
-Therefore, we consider the short exact sequence
-\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
-and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
-As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
-
-Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
-$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
-Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
-This shows the second statement.
-
-As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
-$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
-As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
-Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
-This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
-
-%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
-This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
-
-\end{proof}
-
-The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
-
-For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
-
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
-Define $j_1^c$ as before.
- We say that ${\bf j}$ is admissible if 
-$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
-where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
-\end{definition}
-
-For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
-\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
-We define the admissible sequence $\delta {\bf j}$ by
-\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
-We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
-%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
-
-\begin{lemma}The following holds:
-  \label{le:preprojective lifts}
-  \begin{enumerate}
-    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
-		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
-	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
-Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
-		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
-		for $k=1,\ldots,r$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-
-To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
-
-%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
-Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
-Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
-
-The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
-We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
-We use the third statement in order to successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
-
-Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
-%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
-	\end{proof}
-The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
-Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
-It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
-We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
-We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
-Therefore, we need to apply a translated version of this morphism.
-In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
-
-Our construction immediately yields the following lemma.
-\begin{lemma}\label{projections}
-Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
-Then we have
-\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
-Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
-\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
-for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
-\end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quiver Grassmannians}
-\label{QG}
-
-\subsection{Action on arrows}
+\subsection{$GL_n$ Action on Arrows of $K(n)$}
 Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
-\begin{proposition}\label{indecomposables}Let $m\geq 1$.
+\begin{proposition}
+  \label{indecomposables}
+  Let $m\geq 1$.
   Let $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
   Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
-The following holds:
+  The following hold:
+  \sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
   \begin{enumerate}
     \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
-\item The set indecomposable representations of dimension $\alpha(m,r)$ ist given by a non-empty open subset of $R_\alpha(K(n))$. 
+    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
     \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
@@
 \section{Combinatorial description of non-empty cells}
-In this section we provide a direct quiver theoretic description of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
-The key concept is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
+In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
+The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition.
+The second is the notion of compatible pairs in a maximal Dyck path.
+We give a bijection between these which provides a partial answer to a question of the first author.
+
+\subsection{$2$-Quivers}
+
+The key concept for describing the cell decompositions is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
 \begin{definition}
@@
 by the coefficient quivers
-\begin{align}\label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\end{align}
+\begin{align}
+  \label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.
+\end{align}
 Note that we have a short exact sequence
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
+\subsection{Compatible Pairs}
 For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  

### 2017-12-21 Grassmannian_cells.tex
startetd new proof of Lemma 3.3

@@
 
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite[Section V]{ars}
+\begin{equation}
+  \label{eq:AR sequence}
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+\end{equation}
+where the right-hand morphism is the natural evaluation map.
+
 \begin{lemma}
@@
 \begin{proof}
-  \footnote{This needs to be cleaned up, the proof seems false as written.}
-  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
-  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
+As $\Ext(P_m\otimes V,P_{m-1})=0$, we obtain a commutative diagram
+\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & 0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]
+
+% \footnote{This needs to be cleaned up, the proof seems false as written.}
+ % A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
+ % But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
 \end{proof}
@@
 
-For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
-\begin{equation}
-  \label{eq:AR sequence}
-  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
-\end{equation}
-where the right-hand morphism is the natural evaluation map.
 \begin{corollary}
@@
 Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
+\bibitem{ars} Auslander, M., Reiten, I., Smalo S.O.: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
 \bibitem{bb} Bialynicki-Birula, A.: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).

### 2017-12-22 Grassmannian_cells.tex
Reorganization and says

@@
 \xyoption{all}
+
+%\usepackage[marginal]{showlabels}
 
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
+\begin{remark}
+  \footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
+  \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}
   \label{rem:reflection recursion}
@@
 
+\begin{lemma}
+  \label{le:unique morphisms}
+  There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
+\end{lemma}
+\begin{proof}
+  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
+  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+\end{proof}
+
 \begin{corollary}
@@
 \begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
-  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+\end{proof}
+
+\begin{remark}
+  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
+  By Lemma~\ref{le:unique morphisms}, the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+\end{remark}
+
+\begin{lemma}
+  \label{le:truncated homomorphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
+  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
 \end{proof}
@@
 \begin{corollary}
-  \label{cor:preprojective homomorphism duality}
+    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
+\end{corollary}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
+  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
+  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
+  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique truncated extension}
+  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  \begin{equation}
+    \label{eq:unique extension}
+    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
+  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
+  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
+    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
+    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
+    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
+    & & 0 & 0 & }\]
+  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
+\end{proof}
+
+\begin{lemma}
+  \label{le:preprojective homomorphism duality}
   The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
-\end{corollary}
+\end{lemma}
 \begin{proof}
@@
 \begin{remark}
-  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
+  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
   We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
@@
 \end{remark}
+
+\begin{corollary}
+  \label{cor:truncated preprojective isomorphism}
+  Suppose $V\in Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
+  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
+  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
+  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
+\end{proof}
+
 Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
-Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
+Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
 The next observation is essential for the results to follow.
@@
 \begin{proof}
+  \sayD{Proof needed}
   We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
@@
   \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
-\end{proof}
-
-The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
-\begin{lemma}
-  \label{le:unique morphisms}
-  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
-  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-\end{lemma}
-\begin{proof}
-  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
-  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
-  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
-  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
-\end{proof}
-
-\begin{corollary}
-    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
-  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
-  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
-  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
 \end{proof}
@@
 
-\begin{lemma}
-  \label{le:unique truncated extension}
-  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
-  \begin{equation}
-    \label{eq:unique extension}
-    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
-  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
-    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
-    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
-    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
-\end{proof}
-\begin{corollary}
-  \label{cor:truncated preprojective isomorphism}
-  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
-  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{proof}
 \begin{corollary}
@@
 \begin{proof}
-  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
+  By Lemma~\ref{le:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
   Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
@@
 \begin{remark}
-  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
+  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
   Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
@@
 Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
+\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
 \begin{lemma}
@@
 \subsection{Lifting to $\widetilde{K(n)}$}
+
+In this section, we fix compatible bases for each $H_m=\Hom(P_{m-1},P_m)$ and use these to lift the (truncated) preprojectives to the universal cover of $K(n)$.
+This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.
 
@@
 
-\begin{lemma}\label{le:properties}The following holds:
+\begin{lemma}
+  \label{le:properties}
+  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
+  The following holds:
   \begin{enumerate}
@@
       On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
-
   \end{enumerate}
 \end{lemma} 
-\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
+\begin{proof}
+  The first statement follows from Theorem \ref{covering}.
+  For $m=1$, the second part is obvious.
+  For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
 
@@
 Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
-
 \end{proof} 
@@
  We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
-\begin{lemma}\label{le:subrep}
-  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.
-
+\begin{lemma}
+  \label{le:subrep}
+  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}
+  Let $\uj\in I_l$.
+  All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.	
 \end{lemma}
@@
 
-\begin{lemma}\label{AR}\footnote{special case $m=3$}
+\newpage
+
+\begin{lemma}
+  \label{AR}
+  \footnote{special case $m=3$}
+  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.
+Do parts (2), (3), (4) have analogues for $K(n)$?
+The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.
+The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}
   Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
@@
 We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
-
     \item There exists a short exact sequences 
@@
       where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-
     \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 

### 2017-12-31 Grassmannian_cells.tex
Edited sections 3 and 4

@@
 Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
-With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
-Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
+Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we can view these as endofunctors acting on the category $\rep K(n)$.
+
+The endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
 
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}
-  \footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
-  \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}
+\begin{remark} \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}	\sayT{Changed it a bit}
   \label{rem:reflection recursion}
-  These representations satisfy the following recursions using the reflection functors:
+   \begin{enumerate}
+	\item   These representations satisfy the following recursions using the reflection functors:
   \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
@@
   In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
+	\item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$ and $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
+Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
+This is because $\Sigma_2 S_2=0$.
+	\end{enumerate}
+
+\end{remark}
+ We will see that the indecomposable representations of dimension $\alpha(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
+\begin{proposition}
+  \label{pro:indecomposables}
+  Let $m\geq 1$. Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
+  The following hold:
+  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
+  \begin{enumerate}
+    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
+    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
+   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+
+As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
+Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
+This means that $M\in R_\alpha(K(n))$ is given by a matrix $M\in\CC^{d\times n}$ where the $i^{\mathrm{th}}$ column stands for $M_{a_i}$.
+Now $M$ is indecomposable if and only if $\rk{M}=d$.
+Indeed, it is clear that $S_1^{m}$ splits up if and only if $\rk{M}=d-m$.
+
+This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$  are in one-to-one correspondence with matrices of maximal rank.
+Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M$.
+Now it straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
+This shows the first statement.
+
+It can be checked straightforwardly that $\alpha(1,d)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
+Thus the roots $\alpha(m,d)$ are also Schur roots.
+It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{\alpha(m,r)}(K(n))$, see for example \cite{sch}.
+This shows the second statement.
+
+%For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
+As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
+%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
+%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
+%As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
+\end{proof}
+\begin{remark}There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
+Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
+We inserted this proof because the notion of stability were only used at this point and we wanted to keep this part as simple as possible.
 \end{remark}
@@
   \label{le:injective evaluation maps}
-  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+Let $m\geq 1$.  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
 \end{lemma}
@@
 %%%%%%%%%%%%%%%%%%%
-\begin{proof}
-As $\Ext(P_m\otimes V,P_{m-1})=0$, we obtain a commutative diagram
-\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & 0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]
+\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
+
+As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$ respectively, we obtain a commutative diagram 
+\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]
+where $P_0=0$ and $I_{l}=0$ for $l\leq 0$.
+The snake lemma shows that $ev_V$ is injective if $m=1$ because $\mathrm{id}_{P_1}\otimes \iota_V$ is injective.
+In view of Remark \ref{rem:reflection recursion}, it is enough to show that the cokernel of $ev_V$ does not have a preinjective direct summand if $m=1$.
+Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
+
+Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps where the vertical maps are surjective
+\[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0}\]
+We need to show that $K$ has no preinjective direct summand.
+As $\Hom(P_2,P_1)=0$, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
+But this already shows that $K$ is indecomposable as $\udim K=(\dim H_1/V,1)$.
+Since $V$ is a proper subspace of $H_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
 
@@
 $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
-  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{this is maybe not clear as we do not know that $P_{m+1}^V$ is indecomposable?!
+Therefore, I added a sentence.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
 \end{proof}
@@
 \begin{corollary}
-  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable. Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
 \end{corollary}
@@
   By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
 \end{proof}
@@
 This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.
+A big advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering.
 
@@
 
+\begin{lemma}\label{le:homdecomposition}\sayT{I split up some lemmas. Check references}
+Let $m\geq 2$. The following holds:
+\begin{enumerate}
+\item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
+\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
+      \begin{align}\label{ses1}\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\end{align}
+  \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$
+
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+The first part is a consequence of Theorem \ref{covering}.
+Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part.
+The last part is also a consequence of Theorem \ref{covering} as, for $1\leq i\neq k\leq n$, we have
+$$\kk= \Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong \Hom_Q(P_{m},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})$$
+which implies $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$. Now $\Ext(\tilde P_{m,i},\tilde P_{m,k})=0$ follows in the same manner using that $P_m$ is exceptional.
+
+\end{proof}
+In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
+Note that, we can quotient out the lifted preproctives successively, i.e.
+we have short exact sequences
+\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
 \begin{lemma}
@@
   \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
-  The following holds:
+  Let $m\geq 2$ and let $\uj\in I_l$. The following holds:
   \begin{enumerate}
-    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
+    \item 
     % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
     %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
-    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
-      \[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
-      On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+
+     We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  for $k\neq j_i$ for $i=1,\ldots,l$. 
+		\item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
+		\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+
   \end{enumerate}
@@
 \begin{proof}
-  The first statement follows from Theorem \ref{covering}.
-  For $m=1$, the second part is obvious.
-  For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).
-
-  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.
-
-  As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.
+
+  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.
+
+The second identities are an immediate consequence of Lemma \ref{le:basic homological properties}, but can also be obtained when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
+%  As $\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the identities in the second statement follow when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
 
   For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
-Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
-Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
+Thus applying $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\underline{\quad})$ to (\ref{ses1}) yields $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
+In view of the second identity, we obtain the third identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$ to (\ref{ses1}).
 \end{proof} 
@@
   \label{le:subrep}
-  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}
+  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
+This is because $U\notin\tilde P_{m-1,l}^\perp$}
   Let $\uj\in I_l$.
@@
 
-\newpage
-
 \begin{lemma}
@@
 The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.
-The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}
+The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}\sayT{The sequence (6) should have an analogue on $K(n)$.
+I would be happy with a direct proof of (1) and (2).
+I did not check the details so far.
+	(4) and the first half of (3) hold only on the universal cover. We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
   Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
@@
     \item There exists a short exact sequences 
-      \[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
+      \begin{align}\label{ses3}\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\end{align}
       where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
@@
     \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
-    \item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+
     %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 $$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
-As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+
+We have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ by Lemma \ref{le:basic homological properties}.
+As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+This yields the third and forth identity.
+
+%As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
 Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
-This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}
+This yields the remaining results at once.
 
@@
 This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
+
+\end{proof}
+Define 
+$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
+
+If $m=3$, we replace the short exact sequence (\ref{ses3}) by
+ \begin{align}\label{ses4}\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.\end{align}
+ Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.
+
+\begin{corollary}\label{cor: perpendicular}
+For $m\geq 3$ and $\uj\in I_l$, we have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+\end{corollary}
+\begin{proof}
+If $m\geq 4$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence (\ref{ses3}).
+Using the identities of Lemma \ref{AR}, the result follows.
+
+If $m=3$, we have $\Hom(\tilde P_{3}^{\uj},P(3,\uj))=0$ because $P(3,\uj)$ is a direct sum of simple projective representations. Moreover, it is straightforward that 
+$\Ext(\tilde P_{3}^{\uj},\tilde P_{1,(j_l,i)})=0$ for $i\neq j_l$.
+This is because $\tilde P_{1,(j_l,i)}$ is supported at a  vertex which is not a neighbour of the support of $\tilde P_{3}^{\uj}$, see also Example  \ref{smallm}.
 
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
-\begin{proposition}
-  \label{indecomposables}
-  Let $m\geq 1$.
-  Let $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
-  Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
-  The following hold:
+\begin{proposition} \label{indecomposables}
   \sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
-  \begin{enumerate}
-    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
-    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
-    \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
-  \end{enumerate}
+  \sayT{moved}  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+
 \end{proposition}
 \begin{proof}
-
-As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
-Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
-This means that $M\in R_\alpha(K(n))$ is given by a matrix $M\in\CC^{d\times n}$ where the $i^{\mathrm{th}}$ column stands for $M_{a_i}$.
-Now $M$ is indecomposable if and only if $\rk{M}=d$.
-Indeed, it is clear that $S_1^{m}$ splits up if and only if $\rk{M}=d-m$.
-
-This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$  are in one-to-one correspondence with matrices of maximal rank.
-Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M$.
-Now it straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
-This shows the first statement.
-
-It can be checked straightforwardly that $\alpha(1,d)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
-Thus the roots $\alpha(m,d)$ are also Schur roots.
-It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{\alpha(m,r)}(K(n))$, see for example \cite{sch}.
-This shows the second statement.
 
@@
 \end{proof}
-\begin{remark}There is a more elegant way to prove Proposition \ref{indecomposables} using the notion of stability and moduli spaces.
-Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
-We inserted this proof because the notion of stability were only used at this point and we wanted to keep this part as simple as possible.
-\end{remark}
 
@@
 
-Together with Proposition \ref{indecomposables} this shows that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
+Proposition \ref{pro:indecomposables} and \ref{indecomposables} imply that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
 With other words we use that all indecomposables are truncated preprojectives.
@@
 $$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
-Define 
-$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
-
-Using Lemma \ref{AR}, for $m\geq 4$, every subrepresentation $U\subset \tilde P_{m,j_l}$ gives rise to a commutative diagram
-
- \[\xymatrix{0\ar[r] &P(m,\uj)\ar[r] &  \tilde P_{m-1,j_l}\ar[r] & \tau\tilde P_{m}^{\uj}\ar[r] & 0 \\
-  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
-If $m=3$, we consider the sequence
- \[\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & (2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\ar[r] & 0}\]	
-instead.
-Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=(2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})$, see also Example \ref{smallm}.
 
@@
 \begin{proof}
-In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ by  $\tau'\tilde P_{3}^{(j_1,\ldots,j_l)}$ in which case all arguments hold in the same way.\footnote{das anders}
+In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{\uj}$ by  $\tau'\tilde P_{3}^{\uj}$ in which case all arguments hold in the same way.
+In particular, we make use of $\Ext(\tau' P_3^{\uj},\tau' P_3^{\uj})=0$.
 
@@
 
-Lemma \ref{AR}.(5) implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
-This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$.
-Using Lemma \ref{AR}.(5), this means that the induced map
+Corollary \ref{cor: perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
+This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ and thus $$\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\cong  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U).$$ This means that the induced map
 \[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
 is zero. Therefore, the induced exact sequence splits. 
-
+Let $\uj'=(j_1,\ldots,j_{l-1})$.
 On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
- \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{(j_1,\ldots,j_{l-1})}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
+ \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{\uj'}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
   e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
 which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split.
-This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{(j_1,\ldots,j_{l-1})})=0$ by Lemma ???.
+This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj'})=0$ by Lemma \ref{le:unique morphisms}.
 This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.
@@
 \[\Hom(\tau\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(Z,\tau\tilde P_{m}^{\uj}/W) \]
-is zero. As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} yield  
-$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$ Since the map $\kk=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective and thus bijective, together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.
+is zero. By Lemmas \ref{le:properties} and \ref{AR}, we have 
+$$\Ext(\tau\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=0,\quad \Ext(\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=\kk$$
+for $m\geq 4$.
+The same identities hold for $m=3$ when replacing $\tau$ by $\tau'$.
+The second identity follows for instance when using $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})=\kk$, which is straightforward by Example \ref{smallm}, together with the isomorphism $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})\cong\Ext(\tilde P_{3}^{\uj},\tau'\tilde P_{3}^{\uj})$ obtained above.
+
+Thus the injective map $\kk=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective is bijective.
+Together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.
 
@@
 
-Again we can apply Lemma \ref{AR} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
+Again we can apply Corollary \ref{cor: perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
  Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.

### 2018-01-03 Grassmannian_cells.tex
Small say

@@
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
+\sayD{These edits make the statements false.
+By viewing the reflection functors as endofunctors, we have to interchange the vertex labels so that the inverse of $\Sigma_1$ is $\Sigma_2$.
+Maybe we want to explicitly introduce the functor identifying $\rep K(n)$ with $\rep K(n)^{op}$, is there a standard notation for this?}
 
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark} \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}	\sayT{Changed it a bit}
+\begin{remark}
   \label{rem:reflection recursion}
@@
   \end{enumerate}
-
 \end{remark}

### 2018-01-05 Grassmannian_cells.tex
Section 2 edits

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quiver Covering Theory}
@@
 For an introduction to covering theory we refer to \cite{gab}.
-Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
-We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
-
-Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$.
+Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
+A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
+Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
+Write $\Rep(Q)$ for the abelian category of $\C$-representations of $Q$.
+
+Recall that, given $\CC$-representations $X$ and $Y$ of $Q$, any tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term given by the vector spaces $Z_i=X_i\oplus Y_i$ for $i\in Q_0$ and the linear maps $Z_\alpha=\begin{pmatrix} X_\alpha & 0 \\ g_\alpha & Y_\alpha \end{pmatrix}$ for $\alpha\in Q_1$.
 In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
+\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
 
-Let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
+Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
+Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
 \begin{definition}
-  The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$, where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.
-
-  The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$, where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.
-
-  We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp.
-$\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp.
-$G_Q \tilde X=X$), where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp.
-$G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
+  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
+  Write $F_Q:\Rep(\hat Q)\to\Rep(Q)$ for the natural functor.
+
+  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
+  Write $G_Q:\Rep(\widetilde Q)\to\Rep(Q)$ for the natural functor.
+
+  We say that a representation $X\in\Rep(Q)$ can be \emph{lifted} to $\hat Q$ (resp.
+$\widetilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
+$\widetilde X\in\Rep(\widetilde Q)$) such that $F_Q\hat X=X$ (resp.
+$G_Q \widetilde X=X$).
 \end{definition}
 
-Note that in our definition every covering quiver has infinitely many connected components.
-But every connected component is a covering in the sense of \cite{gab}.
-As indecomposable representations live on one component this makes no difference.
-Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
+Note that in our definition every covering quiver has infinitely many connected components, but each of its connected components is a covering in the sense of \cite{gab}.
+As indecomposable representations live on one of these components this distinction will be irrelevant.
+Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\Rep(\widetilde Q)\to\Rep(\hat Q)$.
 In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
@@
 \begin{lemma}
-  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
+  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
 \end{lemma}
@@
   Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
-  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
+  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\widetilde Q$).
   This gives the claim.
@@
 The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
-We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp. dimension vectors) are equivalent in this case.
-The analogous observation can also be made for $\tilde Q$.
-If $M$ is a representation of $\hat Q$ (resp. $\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp. $w\in W_Q$) by $M_\chi$ (resp. $M_w$).
-
-As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
+We say that a dimension vector $\hat \bfe$ of $\hat Q$ is \emph{compatible} with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
+The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
+The analogous observation can also be made for $\widetilde Q$.
+If $M$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $M_\chi$ (resp. $M_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).
+
+As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
+\sayD{Citation needed?}
 \begin{theorem}
@@
   Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
-  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
-  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
+  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
+  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\widetilde Q)$.
 \end{theorem}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Representation Theory of $K(n)$}
@@
   \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
-  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
+  \item $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_k\alpha_ie_\ell=\delta_{k1}\delta_{\ell2}\alpha_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
 \end{itemize}
@@
   \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
-      \begin{align}\label{ses1}\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\end{align}
+      \begin{align}
+        \label{ses1}
+        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
+      \end{align}
   \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$
-
 \end{enumerate}
@@
     \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
-
   \end{enumerate}
@@
     \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
-      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
+      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)}),\]
       where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
@@
     \item There exists a short exact sequences 
-      \begin{align}\label{ses3}\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\end{align}
+      \begin{align}
+        \label{ses3}
+        \sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}
+      \end{align}
       where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
@@
 If $m=3$, we replace the short exact sequence (\ref{ses3}) by
- \begin{align}\label{ses4}\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.\end{align}
+ \begin{align}
+   \label{ses4}
+   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.
+ \end{align}
  Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.
@@
 Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
-\begin{lemma}\label{usualGrass}
+\begin{lemma}
+  \label{usualGrass}
   Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
@@
 \end{lemma}
-\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
+\begin{proof}
+  If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
 \[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
@@
 \end{lemma}
-\begin{proof} Let $U\in \Gr_\bfe(X)$.
+\begin{proof} 
+  Let $U\in \Gr_\bfe(X)$.
 Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
@@
 
-\begin{lemma}\label{degreecondition} Let $X$ be an indecomposable representation of $\hat Q$.
+\begin{lemma}
+  \label{degreecondition} 
+  Let $X$ be an indecomposable representation of $\hat Q$.
 There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
@@
 \begin{proposition} \label{indecomposables}
-  \sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
-  \sayT{moved}  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
-
+  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
 \end{proposition}

### 2018-01-06 Grassmannian_cells.tex
Some section 3 edits

@@
 Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we can view these as endofunctors acting on the category $\rep K(n)$.
-
-The endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
+Then the endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
-\sayD{These edits make the statements false.
-By viewing the reflection functors as endofunctors, we have to interchange the vertex labels so that the inverse of $\Sigma_1$ is $\Sigma_2$.
-Maybe we want to explicitly introduce the functor identifying $\rep K(n)$ with $\rep K(n)^{op}$, is there a standard notation for this?}
 
@@
   \label{rem:reflection recursion}
+  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
+  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
+  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
   \begin{enumerate}
-    \item These representations satisfy the following recursions using the reflection functors:
-      \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
+    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
+      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
       for $m\ge2$.
       In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
-    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$ and $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
-      Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
-      This is because $\Sigma_2 S_2=0$.
+    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
+      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
+      %This is because $\Sigma_2 S_2=0$.
   \end{enumerate}
@@
 We will see that the indecomposable representations of dimension $\alpha(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
+For a dimension vector $\alpha$, write $R_\alpha(K(n))$ for the affine space of representations of dimension $\alpha$.
 \begin{proposition}
   \label{pro:indecomposables}
-  Let $m\geq 1$. Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
+  Let $m\geq 1$ and $0\le r\le n-1$.
   The following hold:
@@
     \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
-    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
+    \item The set of indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_{\alpha(m,r)}(K(n))$. 
    % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
@@
 \begin{proof}
-
   As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
   Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
-This means that $M\in R_\alpha(K(n))$ is given by a matrix $M\in\CC^{d\times n}$ where the $i^{\mathrm{th}}$ column stands for $M_{a_i}$.
-Now $M$ is indecomposable if and only if $\rk{M}=d$.
-Indeed, it is clear that $S_1^{m}$ splits up if and only if $\rk{M}=d-m$.
-
-This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$  are in one-to-one correspondence with matrices of maximal rank.
-Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M$.
-Now it straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
+  This means that $X\in R_\alpha(K(n))$ is given by a matrix $M_X\in\CC^{d\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
+  Now $X$ is indecomposable if and only if $\rk(M_X)=d$.
+  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)=d-m$.
+
+  This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$ are in one-to-one correspondence with $d\times n$ matrices of maximal rank.
+  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M_X$.
+  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
   This shows the first statement.
@@
 \end{proof}
-\begin{remark}There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
+\begin{remark}
+  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
   Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
-We inserted this proof because the notion of stability were only used at this point and we wanted to keep this part as simple as possible.
+  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
 \end{remark}

### 2018-01-08 Grassmannian_cells.tex
Random edits

@@
 This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.
-A big advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering.
-
-We fix a natural number $n\geq 3$.
-We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
-Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$.
-Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+The main advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering.
+
+Fix a natural number $n\geq 3$ and consider the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
+For $m=1$, we assume that $\dim(\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
+Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=\alpha_1,\ldots,\alpha_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
+Recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
 Moreover, sinks become sources and vice versa.
-For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e.
-we have
+For $m\geq 2$, we build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates, i.e. we have
 \begin{align}
@@
 \begin{remark}
+  \mbox{}
   \begin{enumerate}
-    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. 
+    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\Rep(\widetilde{K(n)})$. 
       %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
     \item We have 
-      $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
+      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
       for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
@@
 
-\begin{lemma}\label{le:homdecomposition}\sayT{I split up some lemmas. Check references}
+\begin{lemma}
+  \label{le:homdecomposition}
+  \sayT{I split up some lemmas. Check references}
   Let $m\geq 2$. The following holds:
@@
       \end{align}
-  \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
+      $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).$$
   \end{enumerate}
@@
 \begin{proof}
-The first part is a consequence of Theorem \ref{covering}.
+  The first part is immediate from Theorem \ref{covering}.
   Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part.
-The last part is also a consequence of Theorem \ref{covering} as, for $1\leq i\neq k\leq n$, we have
-$$\kk= \Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong \Hom_Q(P_{m},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})$$
-which implies $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$. Now $\Ext(\tilde P_{m,i},\tilde P_{m,k})=0$ follows in the same manner using that $P_m$ is exceptional.
-
+  The last part is also a consequence of Theorem \ref{covering}.
+  Indeed, for $1\leq k\leq n$, we have 
+  $$\CC=\Hom_Q(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k}).$$
+  But $\Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong\CC$ and so we must have $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$.
+  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
 \end{proof}
 In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
-Note that, we can quotient out the lifted preproctives successively, i.e.
-we have short exact sequences
+Note that, we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
 \[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
@@
   \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
-  Let $m\geq 2$ and let $\uj\in I_l$. The following holds:
+  For $m\geq 2$ and $\uj\in I_l$, the following hold:
   \begin{enumerate}
-    \item 
-    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
-    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
-
-      We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  for $k\neq j_i$ for $i=1,\ldots,l$. 
-    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
+    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
+    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
     \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
@@
 \begin{proof}
-
-  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.
+  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.
 
@@
 
-  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$.
+  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\CC$.
 Thus applying $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\underline{\quad})$ to (\ref{ses1}) yields $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
@@
 Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
-These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.
+These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\CC$.
 
@@
 
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector.
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by its dimension vector.
 We use this fact and do not state the particular maps defining the lifts.
@@
 \begin{align*}
-  \xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}
+  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
 \end{align*}
-The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.
+The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$.
 
@@
 	\begin{align*}
-          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}
+          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}
         \end{align*}
@@
 	\begin{align*}
-          \xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}
+          \xymatrix@R10pt@C20pt{&&(2,\alpha_{j_1}^{-1})\ar_{\alpha_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{j_l}^{-1})\ar_{\alpha_{j_l}}[llu]}
         \end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.
+In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=\alpha^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,\alpha_{j_i}^{-1})\xrightarrow{\alpha_{j_i}}(1,1)$ for $i=1,\ldots,l$.
 
 The representation $\tilde P_4$ is defined by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{\alpha_1}[llllld]\ar^{\alpha_2}[ld]\ar^{\alpha_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_n\ar^{\alpha_n}[lu]&\mathcal A_1\ar^{\alpha_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{\alpha_3}&\hdots&\mathcal A_n\ar^{\alpha_n}[llu]	&\hdots&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
 where the middle vertex is $(2,1)$.
@@
 Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
-where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{\alpha_1}[llllld]\ar^{\alpha_{l-1}}[ld]\ar^{\alpha_l}[d]\ar^{\alpha_{l+1}}[rd]\ar^{\alpha_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{\alpha_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{\alpha_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{\alpha_n}[lllu]	&&&&}\]
+where the middle vertex is $(1,\alpha_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{\alpha_1}[llllld]\ar^{\alpha_{l}}[llld]\ar^{\alpha_{l+1}}[lld]\ar^{\alpha_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{\alpha_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{\alpha_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{\alpha_n}[lllu]&&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
 where the upper vertex is again $(2,1)$.
 Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
-Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.
+Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $\alpha_{l+1},\ldots,\alpha_n$.
 

### 2018-01-09 Grassmannian_cells.tex
Minor edits in Section 2 and Prop. 3.3

@@
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
-Write $\Rep(Q)$ for the abelian category of $\C$-representations of $Q$.
+Write $\rep Q$ for the abelian category of $\C$-representations of $Q$.
 
@@
   The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
-  Write $F_Q:\Rep(\hat Q)\to\Rep(Q)$ for the natural functor.
+  Write $F_Q:\rep \hat Q\to\rep Q$ for the natural functor.
 
   The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
-  Write $G_Q:\Rep(\widetilde Q)\to\Rep(Q)$ for the natural functor.
-
-  We say that a representation $X\in\Rep(Q)$ can be \emph{lifted} to $\hat Q$ (resp.
-$\widetilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp.
-$\widetilde X\in\Rep(\widetilde Q)$) such that $F_Q\hat X=X$ (resp.
+  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.
+
+  We say that a representation $X\in\rep Q$ can be \emph{lifted} to $\hat Q$ (resp.
+$\widetilde Q$) if there exists a representation $\hat X\in\rep \hat Q$ (resp.
+$\widetilde X\in\rep \widetilde Q$) such that $F_Q\hat X=X$ (resp.
 $G_Q \widetilde X=X$).
@@
 As indecomposable representations live on one of these components this distinction will be irrelevant.
-Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\Rep(\widetilde Q)\to\Rep(\hat Q)$.
+Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\rep \widetilde Q\to\rep \hat Q$.
 In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.
@@
   Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
-  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\widetilde Q$).
+  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$ where $\chi$ runs through all $\chi\in A_Q$ (resp.
+to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
   This gives the claim.
@@
 We say that a dimension vector $\hat \bfe$ of $\hat Q$ is \emph{compatible} with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
-The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
+The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\rep\hat Q$ and on $\ZZ^{\hat Q_1}$.
 We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
 The analogous observation can also be made for $\widetilde Q$.
-If $M$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $M_\chi$ (resp. $M_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).
+If $X$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $X_\chi$ (resp. $X_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).
 
@@
   The functors $F_Q$ and $G_Q$ preserve indecomposability.
-  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
+  Moreover, for all representations $\hat X,\hat Y \in\rep(\hat Q)$, we have 
   \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
-  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\widetilde Q)$.
+  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ and/or $\rep \hat Q$ by $\rep\widetilde Q$.
 \end{theorem}
@@
 \end{remark}
-We will see that the indecomposable representations of dimension $\alpha(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
-For a dimension vector $\alpha$, write $R_\alpha(K(n))$ for the affine space of representations of dimension $\alpha$.
+We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
+For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $\alpha$.
 \begin{proposition}
@@
     \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
-    \item The set of indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_{\alpha(m,r)}(K(n))$. 
+    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
    % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
@@
 \begin{proof}
-  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
-  Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
-  This means that $X\in R_\alpha(K(n))$ is given by a matrix $M_X\in\CC^{d\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
-  Now $X$ is indecomposable if and only if $\rk(M_X)=d$.
-  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)=d-m$.
-
-  This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$ are in one-to-one correspondence with $d\times n$ matrices of maximal rank.
-  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M_X$.
-  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
+  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(d(m,r))=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
+  Then we have $d(m,r)=(1,l)$ for $l:=n-r$.
+  This means that $X\in R_{d(m,r)}(K(n))$ is given by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
+  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
+  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)\leq l-m$.
+
+  This shows that the indecomposable representations in $R_{(1,l)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
+  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $l$ spanned by the column vectors of $M_X$.
+  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_l(\CC)$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\Gl_l(\CC)$ on the set of subspaces.
   This shows the first statement.
 
-  It can be checked straightforwardly that $\alpha(1,d)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
-  Thus the roots $\alpha(m,d)$ are also Schur roots.
-  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{\alpha(m,r)}(K(n))$, see for example \cite{sch}.
+  It can be checked straightforwardly that $(1,l)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
+  Thus the roots $d(m,r)$ are also Schur roots.
+  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
   This shows the second statement.
@@
   There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
-  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
+  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
   We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
@@
 $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{this is maybe not clear as we do not know that $P_{m+1}^V$ is indecomposable?!
-Therefore, I added a sentence.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$.
+} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
 \end{proof}
@@
   \begin{enumerate}
-    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\Rep(\widetilde{K(n)})$. 
+    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\rep\widetilde{K(n)}$. 
       %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
@@
 Let $Q$ be an acyclic quiver.
-We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$.
+We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
 We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
@@
 \begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
+If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
 \end{lemma}

### 2018-01-11 Grassmannian_cells.tex
added some says, minor changes

@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}
-  \label{rem:reflection recursion}
+\begin{remark}\label{rem:reflection recursion}
   We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
@@
 $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$.
-} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
 \end{proof}
@@
 
-\begin{corollary}
+\begin{corollary}\sayT{exchange $W$ and $V$?}
     For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
@@
   Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
-  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
+  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.\sayT{why does this imply that $\iota_{m-1}=0$?
+This should contradict the fact that \eqref{eq:AR sequence} is an AR-sequence.}
   Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
@@
   We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
-  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
+  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.\sayT{more details?}
 \end{remark}
@@
 \begin{proof}
-  \sayD{Proof needed}
+  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
   We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
@@
 
-\begin{corollary}
+\begin{corollary}\sayT{proof?}
   For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
@@
 
-\begin{lemma}
+\begin{lemma}\sayT{proof? Special case of 3.23?}
   For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
@@
       %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-    \item We have 
+    \item  Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 	
+		We have 
       $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
@@
 
-      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
     \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
@@
 \end{align*}
-The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$.
+The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink.
+In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.
 

### 2018-01-11 Grassmannian_cells.tex
improved proof of Lemma 4.4, minor changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Representation Theory of $K(n)$}
+\section{Representation Theory of $K(n)$}\label{sec:RepK(n)}
 
@@
   \label{recursive}
-  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
+  \tilde P_m=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
 \end{align}
+
 It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
@@
 Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
-Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
+Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l}}< 0$, we obtain
 \[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
@@
 \end{comment}
+Define 
+$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
 
@@
   \label{AR}
-  \footnote{special case $m=3$}
   \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.
@@
   Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
-  Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
-  $$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$
-
-  The following holds:
+  Consider the short exact sequence $$\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}.$$ The following holds:
   \begin{enumerate}
@@
         \label{ses3}
-        \sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}
+        \ses{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}%{\pi^{\bf j_l}_{m-1}}
       \end{align}
@@
 \begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Using the identities (\ref{recursive}), it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
 Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
-We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
+We should point out that it is very important for this proof that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
 Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
 
-In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$.
-In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$.
-Therefore, we consider the short exact sequence
+In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$. For $m=5$,  we consider the short exact sequence
 \[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
-and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$.
-As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.
+and apply the reflection functor $\tilde\Sigma_1\tilde\Sigma_2$ which is the same as applying $\tau^{-1}$.
+As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^{(1,\ldots,l)}=\tilde P_5^{(1,\ldots,l)}$ which is statement for $m=5$.
+The general statement follows from the identities (\ref{recursive}).
+Note that this also shows that
+\[(\tilde \Sigma_2\tilde P_{m}^{(1,\ldots,l)})^\sigma=\tau^{-1}\tilde P^{(1,\ldots,l)}_{m-1}.\]
 
 Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
-$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
-Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
-This shows the second statement.
+$$\ses{P(4,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
+Actually, the first summand of $P(4,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
+Together with the first statement and the identities (\ref{recursive}), this shows the second statement.
 
@@
 \end{proof}
-Define 
-$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
 
@@
    \label{ses4}
-   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.
+   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)\ar[r] & 0}.
  \end{align}
- Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.
+ Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)$, see also Example \ref{smallm}.
 
@@
 
-For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
-\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
+%For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
+%\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
 The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
@@
 %In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.
+Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$. We obtain the following analogue of Lemma \ref{cor:truncated preprojective isomorphism}.
 
@@
 		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
-	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$.
+	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$.
 Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
@@
 We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
-We use the third statement in order to successively obtain commutative diagrams
+We successively obtain commutative diagrams
 \[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
@@
 \[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
+Using Lemma \ref{le:properties}.(2), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
 %As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
@@
 The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
-Let $\uj=(j_{1},\ldots,j_{l})\in I_l$.
+Let $\underline{j_1}=(j_{1,1},\ldots,j_{1,n-1})$ and $\uj=(j_{1,1},\ldots,j_{1,l})\in I_l$.
 It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
@@
 \begin{lemma}\label{projections}
-Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$.
-Then we have
-\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
+Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
+\[\pi_m^{\bf j}=\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}\circ\ldots\circ\pi^{(j_{2}^c,\underline{j_2})}_{m-1,(j_1^c)}\circ\pi_m^{\underline{j_1}}.\]
 Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
-\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
-for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
+\[\pi_{m-k+1,(j_{k-1}^c)}^{(j_{k-1}^c,\underline{j_k})}=\prod_{i=1}^{n-2} \pi^{(j_{k-1}^c,j_{k,l_1},\ldots, j_{k,l_{i}})}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
+for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
 \end{lemma}
@@
 
-Fix a vector space $X$ of dimension $n$ and let $d\leq n$.
+Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
 We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
@@
 Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$.
-This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$.
-We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
-there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
-where the unit vectors are in the columns $i_1,\ldots,i_d$.
-All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$.
+Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ linearly to $X$.
+This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
+We can write every $U\in\Gr_k(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
+there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ and a unique matrix representation of $U$ of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k)\]
+where the unit vectors are in the columns $i_1,\ldots,i_k$.
+All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_k)$.
 The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
 we have
-\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
-Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
+for $w=1,\ldots,k$. Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
 \begin{lemma}
@@
   If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
-\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
+\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_{i-1}+1)}(U\cap X_i)=U\]
 where $j_0=0$.
@@
 Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
-Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{i_w}\in X_s$.
+Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{w}\in X_s$.
 As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
@@
 The next step is to generalize this to quiver Grassmannians.
-
 Let $Q$ be an acyclic quiver.
@@
 For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
-In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
+In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
 Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
@@
 Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
-Then it follows
+It follows
 \[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
@@
   \label{degreecondition} 
-  Let $X$ be an indecomposable representation of $\hat Q$.
-There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that $d(i,\chi)\ne d(j,\chi')$ if $i\neq j$ or $\chi\neq \chi'$ and such that $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$ and $(i,\chi),\,(j,\chi+e_\alpha)\in \mathrm{supp}(X)$.
-\end{lemma}
-\begin{proof}
-Since $X$ is finite-dimensional, $\mathrm{supp}( X)$ is a connected finite tree.
-In order to prove the statement, we may assume that $d(q,0)=0$ and that $(q,0)\in \mathrm{supp}(X)$.
-We now fix numbers $c_\alpha$ and show that the two conditions are satisfied.
-To do so, let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ and assume that $|Q_1|=n$.
-Set $c_{\alpha_1}=1$ and inductively
-\[c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}.\]
-Note that if $A_Q$ is the free abelian group in the generators $\alpha_1,\ldots,\alpha_n$ and $f:A_Q\to \ZZ$ the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$,  we have $d(q,\chi)=f(\chi)$.
-In particular, there exist $d_i$ with $|d_i|\leq K$ such that we have
-\[d(q,\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
-
-First note that we obviously have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
-Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$
-which implies
+  Let $X$ be an indecomposable representation of $\hat Q$. There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
+	\begin{enumerate}
+	\item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$ with $(i,\chi)\neq (j,\chi')$ we have $d(i,\chi)\ne d(j,\chi')$;
+	\item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}Assume that $|Q_1|=n$.
+Since $X$ is finite-dimensional and indecomposable, $\mathrm{supp}( X)$ is a connected and finite subquiver of $\hat Q$.
+In order to prove the statement, we may assume that $(q,0)\in \mathrm{supp}(X)$ for some $q\in Q_0$.
+We fix $c_\alpha\in\NN$ and show that we can choose a degree such that the two conditions are satisfied for this choice.
+Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(q,0)$ such that the underlying graph of the path has no cycles.
+This implies that, for $(q',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have $|d_i|\leq K$.
+
+Set $c_{\alpha_1}=1$ and choose $c_{\alpha_j}$ recursively in such way that 
+\[c_{\alpha_j}\geq 2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}\]
+for $j=2,\ldots,n$.
+
+Let $f:A_Q\to \ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(q',\chi):=f(\chi)$ for $(q',\chi)\in\mathrm{supp}(X)$.
+In particular, for $(q',\chi)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have
+\[d(q',\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
+
+First note that we have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
+Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^{n}d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^{n}e_ic_{\alpha_i}$.
+This implies
 \[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
-Since we have $|d_i-e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|\leq K\sum_{i=1}^{n-1}c_{\alpha_i}<c_{\alpha_n}$$
+Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}$$
 This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
-An analogous proof applies to show that $d(j,\chi')-d(i,\chi)\neq c_\alpha$ if $\chi'\neq \chi+e_\alpha$ using that, actually, $c_{\alpha_n}> (K+1)\sum_{i=1}^{n-1}c_{\alpha_i}$.
+
+Finally, assume that $d(j,\chi')-d(i,\chi)=c_\alpha$.
+Then we have $d(j,\chi')=d(j,\chi+e_\alpha)$.
+An analogous proof as the one above shows that $\chi'=\chi+e_\alpha$.
+Note that it is a priori possible that $(j,\chi+e_\alpha)\notin\mathrm{supp}(X)$.
+Thus we chose $c_{\alpha_j}$ in such a way that it is greater than $2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}$.
 
@@
 \item 
-If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{\tilde \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{ \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
 \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(q,w)}\mid q\in Q_0,w\in W_Q]\to\ZZ[x_q\mid q\in Q_0]$ given by $S(x_{(q,w)})=x_q$ for all $q\in Q_0$ and $w\in W_Q$.

### 2018-01-12 Grassmannian_cells.tex
Random edits, section 3 edits

@@
 \newcommand{\Gr}{\mathrm{Gr}}
-\newcommand{\Gl}{\mathrm{Gl}}
+\newcommand{\GL}{\mathrm{GL}}
 \newcommand{\Ind}{\mathrm{Ind}}
@@
 
-For an introduction to covering theory we refer to \cite{gab}.
+We refer to \cite{gab} for an introduction to covering theory.
 Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
@@
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
-Write $\rep Q$ for the abelian category of $\C$-representations of $Q$.
+Write $\rep Q$ for the hereditary abelian category of $\C$-representations of $Q$.
 
@@
 In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
+\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},\]
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
@@
   Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
-  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$ where $\chi$ runs through all $\chi\in A_Q$ (resp.
+  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp.
 to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
@@
 As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
-\sayD{Citation needed?}
+\sayD{Specific reference needed?}
 \begin{theorem}
@@
       In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
-    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
+    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
       %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
@@
 We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
-For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $\alpha$.
+For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
 \begin{proposition}
@@
   \begin{enumerate}
-    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
+    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
     \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
-   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+   % \item The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
   \end{enumerate}
@@
 \begin{proof}
-  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(d(m,r))=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
-  Then we have $d(m,r)=(1,l)$ for $l:=n-r$.
-  This means that $X\in R_{d(m,r)}(K(n))$ is given by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
+  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
+  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
+  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
   Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
-  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)\leq l-m$.
-
-  This shows that the indecomposable representations in $R_{(1,l)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
-  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $l$ spanned by the column vectors of $M_X$.
-  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_l(\CC)$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\Gl_l(\CC)$ on the set of subspaces.
+  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.
+
+  This shows that the indecomposable representations in $R_{(l,1)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
+  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$l$ spanned by the row vectors of the corresponding matrix $M_X$.
+  Now it is straightforward to check that the $\GL_{d(m,r)}=\GL_l(\CC)\times\CC^\ast$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\GL_l(\CC)$ on the set of these subspaces.
   This shows the first statement.
 
-  It can be checked straightforwardly that $(1,l)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
+  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
   Thus the roots $d(m,r)$ are also Schur roots.
@@
 
-%For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
-As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
+%For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
+As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
 %\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
 %\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
-%As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
+%As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
 \end{proof}
@@
 %Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
-For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
+For $1\le r\le n-1$, let $Gr_r(H_m)\subset Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.
 
@@
 \begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
-
-As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$ respectively, we obtain a commutative diagram 
-\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]
-where $P_0=0$ and $I_{l}=0$ for $l\leq 0$.
-The snake lemma shows that $ev_V$ is injective if $m=1$ because $\mathrm{id}_{P_1}\otimes \iota_V$ is injective.
-In view of Remark \ref{rem:reflection recursion}, it is enough to show that the cokernel of $ev_V$ does not have a preinjective direct summand if $m=1$.
+  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
+  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
+  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
+  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.
+
+  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
   Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
-
-Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps where the vertical maps are surjective
-\[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0}\]
+  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
+  \[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0.}\]
+
   We need to show that $K$ has no preinjective direct summand.
@@
   Since $V$ is a proper subspace of $H_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
-
-% \footnote{This needs to be cleaned up, the proof seems false as written.}
- % A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
- % But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
-\end{proof}
+\end{proof}
+
 In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
@@
 \label{sec:truncated preprojectives}
-Following Lemma~\ref{le:injective evaluation maps} we define the following.
+Following Lemma~\ref{le:injective evaluation maps}, we define the following.
 \begin{definition}
@@
     \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
-    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
+    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\CC$.
 
@@
 We have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ by Lemma \ref{le:basic homological properties}.
-As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
+As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\CC$ by a straightforward check, applying (\ref{recursive}), it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\CC$.
 This yields the third and forth identity.
@@
 \[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-Using Lemma \ref{le:properties}.(2), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
+Using Lemma \ref{le:properties}.(2), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\CC$.
 %As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
@@
 \begin{proposition} \label{indecomposables}
-  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
 \end{proposition}
@@
 
-For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
-As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
+For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
+As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
 \[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
 \Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
-As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
+As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
 \end{proof}
@@
 \begin{proof}
-Let $g\in\Gl_n(\CC)$.
+Let $g\in\GL_n(\CC)$.
 We first show that $\Gr_\bfe(g.P_{m+1}^V)=\Gr_\bfe(P_{m+1}^V)$.
@@
 is zero. By Lemmas \ref{le:properties} and \ref{AR}, we have 
-$$\Ext(\tau\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=0,\quad \Ext(\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=\kk$$
+$$\Ext(\tau\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=0,\quad \Ext(\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=\CC$$
 for $m\geq 4$.
 The same identities hold for $m=3$ when replacing $\tau$ by $\tau'$.
-The second identity follows for instance when using $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})=\kk$, which is straightforward by Example \ref{smallm}, together with the isomorphism $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})\cong\Ext(\tilde P_{3}^{\uj},\tau'\tilde P_{3}^{\uj})$ obtained above.
-
-Thus the injective map $\kk=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective is bijective.
+The second identity follows for instance when using $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})=\CC$, which is straightforward by Example \ref{smallm}, together with the isomorphism $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})\cong\Ext(\tilde P_{3}^{\uj},\tau'\tilde P_{3}^{\uj})$ obtained above.
+
+Thus the injective map $\CC=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective is bijective.
 Together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.

### 2018-01-12 Grassmannian_cells.tex
Reorganization in Section 3.1, more needed

@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
-\begin{remark}\label{rem:reflection recursion}
+\begin{remark}
+  \label{rem:reflection recursion}
   We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
@@
   Thus the roots $d(m,r)$ are also Schur roots.
+  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
   It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
@@
 \begin{lemma}
+  \label{le:truncated homomorphisms}
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V=0$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
+  and a surjective map
+  \[\Ext(P_m,P_{m+1})\onto\Ext(P_m,P_{m+1}^V).\]
+  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
+  The final claim follows from Remark~\ref{rem:reflection recursion}.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique preprojective morphism}
+  For $V\in Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
+\end{lemma}
+\begin{proof}
+  Applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism 
+  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
+  and a surjective map
+  \[\Ext(P_{m+1},P_{m+1})\onto\Ext(P_{m+1},P_{m+1}^V).\]
+  The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
+  The rigidity of $P_{m+1}$ gives the final claim.
+\end{proof}
+
+\begin{lemma}
+  \label{le:unique morphisms}
+  Consider $V,W\in Gr(H_m)$, $m\ge1$.
+  \begin{enumerate}
+    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
+    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
+  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+  In this case, there is an isomorphism 
+  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
+  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+\end{proof}
+
+\begin{corollary}
+  \label{cor:indecomposable truncated} 
+  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
+\end{proof}
+
+\begin{lemma}
   \label{le:basic homological properties}
   For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
-  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{lemma}
-\begin{proof}
-  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp.
+\end{lemma}
+\begin{proof}
+  Recall that $\Hom(X,P_\ell)\ne0$ (resp.
 $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$.
-The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:unique morphisms}
-  There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-\end{lemma}
-\begin{proof}
-  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
-  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
-  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-\end{proof}
-
-\begin{corollary}
-  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable. Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
+$1\le r\le\ell-2$).
+  whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$.
+The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.}
+  Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
 \end{proof}
@@
 \end{remark}
-
-\begin{lemma}
-  \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
-\end{lemma}
-\begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
-  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
-\end{proof}
-
-\begin{corollary}\sayT{exchange $W$ and $V$?}
-    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
-  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
-  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
-  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
-\end{proof}
 
@@
   \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
+  By Lemma~\ref{le:unique preprojective morphism}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
 \end{proof}

### 2018-01-12 Grassmannian_cells.tex
Towards Lemma 3.28

@@
   \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V=0$.
+  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
 \end{lemma}
@@
 
+\begin{remark}
+  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion.
+  This structure gives rise to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
+  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+\end{remark}
+
 \begin{corollary}
@@
 $1\le r\le\ell-2$).
-  whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$.
-The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.}
-  Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
-\end{proof}
-
-\begin{remark}
-  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
-  By Lemma~\ref{le:unique morphisms}, the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
-\end{remark}
+  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
+\end{proof}
 
@@
   Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
-  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.\sayT{why does this imply that $\iota_{m-1}=0$?
-This should contradict the fact that \eqref{eq:AR sequence} is an AR-sequence.}
+  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.\sayT{why does this imply that $\iota_{m-1}=0$?
+This should contradict the fact that \eqref{eq:AR sequence} is an AR-sequence.}\sayD{is this better?}
   Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
@@
 \begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
+  For $V\in Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+  Moreover, the upper pullback sequence
   \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
@@
 \begin{proof}
+  We proceed by simultaneous induction on $m$ and $\codim_{H_m} V$.
+
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$ which gives both claims in this case.
+
+  By Corollary~\ref{cor:truncated preprojective isomorphism}, the first claim for $m\ge2$ and $\codim_{H_m} V = 1$ follows from the first claim for $m-1$.
+
+  Now we show that the first claim implies the second.
+  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
+  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and so the upper pullback sequence above will split giving the second claim.
+
   We proceed by induction on $\codim_V W$.  

### 2018-01-12 Grassmannian_cells.tex
Removed says

@@
   Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
-  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.\sayT{why does this imply that $\iota_{m-1}=0$?
-This should contradict the fact that \eqref{eq:AR sequence} is an AR-sequence.}\sayD{is this better?}
+  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
   Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.

### 2018-01-12 Grassmannian_cells.tex
Lemma 4.8

@@
 Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
-More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{a_i})$ with $(g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
 Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
@@
   Then for $g=(g_{ij})\in GL_n(\CC)$, we have
-  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
+  \[\theta_2\circ (g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(N_{a_j}\circ\theta_1)=(g.N)_{a_i}\circ\theta_1\]
   for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 

### 2018-01-12 Grassmannian_cells.tex
Gr's

@@
 %Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
-Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
-Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
-For $1\le r\le n-1$, let $Gr_r(H_m)\subset Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.
+Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
+Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
+%Lemma~\ref{le:hom equivariance} gives an identification of $\Gr(H_m)$ with $\Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
+For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.
 
@@
   \label{le:injective evaluation maps}
-Let $m\geq 1$.  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
 \end{lemma}
@@
 \begin{definition}
-  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  For $V\in \Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
   \begin{equation}
@@
   \label{le:truncated homomorphisms}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
+  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
 \end{lemma}
@@
   \label{le:unique preprojective morphism}
-  For $V\in Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  For $V\in \Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
   Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
@@
   \label{le:unique morphisms}
-  Consider $V,W\in Gr(H_m)$, $m\ge1$.
+  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
   \begin{enumerate}
@@
 \begin{remark}
-  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion.
-  This structure gives rise to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
-  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
+  The total Grassmannian $\Gr(H_m)$ is naturally a poset under inclusion.
+  This structure gives rise to a $\CC$-linear category $\CC \Gr(H_m)$ with objects the elements of $\Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
+  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(H_m)$.
+  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(H_m)\cong\cP_{m+1}$.
 \end{remark}
@@
   \label{cor:indecomposable truncated} 
-  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+  For $V\in \Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
   Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
@@
   \label{le:basic homological properties}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
 \end{lemma}
@@
   \label{le:unique truncated extension}
-  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  For $V\in \Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
   \begin{equation}
@@
 \begin{remark}
-  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
+  The set $\Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(H_m)^{op}\cong \Gr(H_m^*)$ with $\Gr(H_{m-1})$.
   We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
@@
   \label{cor:truncated preprojective isomorphism}
-  Suppose $V\in Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+  Suppose $V\in \Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
 \end{corollary}
@@
 \begin{proposition}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
+  For $V\in \Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
 \end{proposition}
@@
   \label{le:truncated extensions}
-  For $V\in Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
+  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
   More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
@@
 \begin{corollary}\sayT{proof?}
-  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
+  For $V,W\in \Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
 \end{corollary}
@@
   \label{le:more truncated homomorphisms}
-  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
+  For $W\in \Gr(H_m)$, $m\ge2$, the following hold:
   \begin{enumerate}
@@
 \begin{remark}
-  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
+  For $W\in \Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
   Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
@@
 \begin{corollary}
-  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
+  For $V,W\in \Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
   \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
@@
 \begin{lemma}\sayT{proof? Special case of 3.23?}
-  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
-\end{lemma}
-
-\begin{lemma}
-  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
+  For $V,W\in \Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
+\end{lemma}
+
+\begin{lemma}
+  For $m\ge2$ and $V\in \Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
 More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
@@
   \label{le:truncated exact sequences}
-  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
+  For $V\in \Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
   \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
@@
 
-For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
 \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
@@
 \begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
   Moreover, the upper pullback sequence
@@
 \begin{corollary}
-  Consider $V,W\in Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
   Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
@@
 \begin{lemma}
-  For $V\in Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
+  For $V\in \Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
   \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
@@
   \footnote{This can be proved on the quiver itself.}
-  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
-\end{lemma}
-\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
+  If the quiver Grassmannians $\Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $\Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
+\end{lemma}
+\begin{proof}The claim follows by induction when considering the map $$\Psi:\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times \Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
 which is also sometimes called Caldero-Chapoton map.
@@
 But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
-Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
+Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in \Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times \Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
 In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
@@
 
-In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
+In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
 \end{proof}
@@
 Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
- a torus action on $Gr_\bfe^Q(X)$ such that
-  $$Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
+ a torus action on $\Gr_\bfe^Q(X)$ such that
+  $$\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
 \end{theorem}
@@
 Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
-Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
-If we denote the iterated torus fixed points by $Gr^Q_\bfe(X)^{T^{(k)}}$.
+Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
+If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$.
 We obtain:
@@
 Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
+  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
 \end{corollary}
 %\begin{corollary}
-%  affine bundles over $Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $Gr^Q_\bfe(X)$ is smooth
-%  \[\{U\in Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
+%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
+%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
 %\end{corollary}
@@
 %  \label{le:transitivity}
-%  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $Gr_d(H_m)$.
+%  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $\Gr_d(H_m)$.
 %\end{lemma} 
@@
 
-%Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
+%Similarly, for $V^g\in \Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
 %\begin{lemma}
@@
 \begin{theorem}
-  The quiver Grassmannian $Gr_\bfe(P_{m+1}^V)$ is smooth for each dimension vector $\bfe$ and each $V\in Gr(H_m)$.
-  Moreover, for $V,W\in Gr_d(H_m)$, we have $Gr_\bfe(P_{m+1}^V)\cong Gr_\bfe(P_{m+1}^W)$ for all dimension vectors $\bfe$.
+  The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each dimension vector $\bfe$ and each $V\in \Gr(H_m)$.
+  Moreover, for $V,W\in \Gr_d(H_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$ for all dimension vectors $\bfe$.
 \end{theorem}
@@
   %For each dimension vector $\bfe$, there is a smooth variety
-  %\[X_{\bfe,m}=\{(\tilde E,V):V\in Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
-  %Under the natural projection $\pi:X_{\bfe,m}\to Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $Gr_\bfe(P_{m+1}^V)$.
-  %In particular, this implies $Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in Gr_d(H_m)$.
+  %\[X_{\bfe,m}=\{(\tilde E,V):V\in \Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
+  %Under the natural projection $\pi:X_{\bfe,m}\to \Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $\Gr_\bfe(P_{m+1}^V)$.
+  %In particular, this implies $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr_d(H_m)$.
 
@@
   %\[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
-  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $Gr_\bfe(P_{m+1}^V)$ and $Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in Gr_d(H_m)$.
+  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ and $\Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in \Gr_d(H_m)$.
 \end{proof}
@@
 Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
-\[\Psi_\tbfe:Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr_\tbff(M)\times Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
+\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
 which is also called Caldero-Chapoton map.
@@
 We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
-\[\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]
+\[\Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} \Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]
 
@@
 The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma \ref{vb}?}.
+In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma \ref{vb}?}.
 Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
-In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
+In total, this yields a cell decomposition of the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
 \end{comment}
@@
 %Note that we can also consider 
-%$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
+%$\Psi_1:\Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times \Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
 But then one needs to adjust $\Psi_2$ because the factor of $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
@@
 \begin{theorem}\cite{lee-li-zelevinsky}
-  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
+  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
 \end{theorem}
 
-Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
 

### 2018-01-14 Grassmannian_cells.tex
Section 3.2 edits

@@
 \section{Quiver Covering Theory}
+\label{sec:covering}
 
@@
 
-In this section, we fix compatible bases for each $H_m=\Hom(P_{m-1},P_m)$ and use these to lift the (truncated) preprojectives to the universal cover of $K(n)$.
-This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.
-The main advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering.
-
-Fix a natural number $n\geq 3$ and consider the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
-For $m=1$, we assume that $\dim(\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
-Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=\alpha_1,\ldots,\alpha_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
-Recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
-Moreover, sinks become sources and vice versa.
-For $m\geq 2$, we build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates, i.e. we have
+Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
+In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojectives to the universal cover $\widetilde{K(n)}$ of the quiver $K(n)$.
+This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
+The main advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
+
+We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
+First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+Moreover, under this operation all sinks become sources and vice versa.
+The preprojective lifts we use are defined recursively as follows.
+\begin{itemize}
+  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
+  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
+  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
+    More precisely, we set
     \begin{align}
-  \label{recursive}
-  \tilde P_m=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
+      \label{eq:recursive covers}
+      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
     \end{align}
-
-It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
-
+\end{itemize}
+
+It will be rather important that the lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
+Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
+To simplify the notation, we abbreviate $P_{2l-1,i}:=P_{2l-1,\alpha_i}$ and $P_{2l,i}:=P_{2l,\alpha_i^{-1}}$.
+\begin{lemma}
+  For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
+  These are the representations $P_{m-1,i}$ corresponding the $n$ different arrows of $K(n)$. 
+\end{lemma}
+\begin{proof}
+  This is clear for $m=2$ and follows in general by applying the identities \eqref{eq:recursive covers}.
+\end{proof}
 \begin{remark}
-  \mbox{}
-  \begin{enumerate}
-    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\rep\widetilde{K(n)}$. 
-      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
-    \item  Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 	
-		We have 
-      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
-      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).
-
-    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
-\end{enumerate}
+  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
+  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
 \end{remark}
@@
 \begin{remark}
-Actually, these examples already show how the (truncated) preprojectives are built, also using the identities (\ref{recursive}).
+Actually, these examples already show how the (truncated) preprojectives are built, also using the identities \eqref{eq:recursive covers}.
 We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
@@
 \begin{proof}
-Using the identities (\ref{recursive}), it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+Using the identities \ref{eq:recursive covers}, it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
 Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
@@
 As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^{(1,\ldots,l)}=\tilde P_5^{(1,\ldots,l)}$ which is statement for $m=5$.
-The general statement follows from the identities (\ref{recursive}).
+The general statement follows from the identities \ref{eq:recursive covers}.
 Note that this also shows that
@@
 Actually, the first summand of $P(4,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
-Together with the first statement and the identities (\ref{recursive}), this shows the second statement.
+Together with the first statement and the identities \eqref{eq:recursive covers}, this shows the second statement.
 
@@
 We have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ by Lemma \ref{le:basic homological properties}.
-As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\CC$ by a straightforward check, applying (\ref{recursive}), it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\CC$.
+As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\CC$ by a straightforward check, applying \ref{eq:recursive covers}, it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\CC$.
 This yields the third and forth identity.
@@
 Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
-Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.
+Applying the identities \eqref{eq:recursive covers} the claim follows for $m\geq 3$.
 

### 2018-01-14 Grassmannian_cells.tex
Random edits, more alpha's

@@
 
-As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}.
+As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
 Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
@@
 \subsection{$GL_n$ Action on Arrows of $K(n)$}
-Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
-More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{a_i})$ with $(g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+Observe that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
+More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
 Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
@@
 \begin{proof}
-  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
-  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
-  \[\theta_2\circ (g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(N_{a_j}\circ\theta_1)=(g.N)_{a_i}\circ\theta_1\]
-  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
+  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{\alpha_j}=N_{\alpha_j}\circ\theta_1$ for $1\le j\le n$.
+  Then for $g=(g_{ij})\in GL_n(\CC)$ and $1\le i\le n$, we have
+  \[\theta_2\circ (g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{\alpha_j})=\sum\limits_{j=1}^n g_{ij}(N_{\alpha_j}\circ\theta_1)=(g.N)_{\alpha_i}\circ\theta_1\]
+  so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
 \end{proof}
@@
   We present all the details for $\Sigma_2$, the proof for $\Sigma_1$ is similar.
-  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{a_i})$, where $M'_2$ fits into the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
-  and $M'_{a_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
-  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,M''_{a_i})$ with 
-  \[M''_{a_i}=\sum\limits_{j=1}^n g_{ij}M'_{a_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
+  For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{\alpha_i})$, where $M'_2$ fits into the following exact sequence:
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
+  and $M'_{\alpha_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
+  Then for $g=(g_{ij})\in GL_n(\CC)$, we have $g.\Sigma_2(M)=(M_1,M'_2,(g.M')_{\alpha_i})$ with 
+  \[(g.M')_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M'_{\alpha_j}=\sum\limits_{j=1}^n g_{ij}(\pi\circ\iota_j)=\pi\circ\sum\limits_{j=1}^n g_{ij}\iota_j=\pi\circ g^T\circ\iota_i.\]
   In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{a_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
+  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
   i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
@@
 \begin{proposition} \label{indecomposables}
-  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
+  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),d(m,r))$.
 \end{proposition}
 \begin{proof}
-
-For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
+  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_{d(1,r)}(K(n))$.
   As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
-\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
-\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
+  \[\xymatrix{\Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),d(m+1,r))\ar[d]^g\\
+    \Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),d(m+1,r))}.\]
   As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
@@
 \begin{theorem}
-  The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each dimension vector $\bfe$ and each $V\in \Gr(H_m)$.
-  Moreover, for $V,W\in \Gr_d(H_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$ for all dimension vectors $\bfe$.
+  Fix a dimension vector $\bfe$.
+  The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr(H_m)$.
+  Moreover, for $V,W\in \Gr_d(H_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$.
 \end{theorem}
@@
   We first show that $\Gr_\bfe(g.P_{m+1}^V)=\Gr_\bfe(P_{m+1}^V)$.
-Assume that $P_{m+1}^V$ is given by the linear maps $M_{a_i}$.
-Then $g.P_{m+1}^V$ is given by the matrices $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
+  Assume that $P_{m+1}^V$ is given by the linear maps $M_{\alpha_i}$.
+  Then $g.P_{m+1}^V$ is given by the matrices $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
   Let $(U_1,U_2)\in\Gr_\bfe(g.P_{m+1}^V)$.
   Then we have  
-\[M_{a_i}(U_2)\subset U_1 \text{ for all } i=1,\ldots,n\Leftrightarrow \left(\sum\limits_{j=1}^n g_{ij}M_{a_j}\right)(U_2)\subset U_1 \text{ for all } i=1,\ldots,n.\]
+  \[M_{\alpha_i}(U_2)\subset U_1 \text{ for all } i=1,\ldots,n\Leftrightarrow \left(\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}\right)(U_2)\subset U_1 \text{ for all } i=1,\ldots,n.\]
   Note that we have $g^{-1}.(g.P_{m+1}^V)=P_{m+1}^V$ which shows the non-obvious direction.
@@
   %In particular, this implies $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr_d(H_m)$.
-
   %The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.

### 2018-01-16 Grassmannian_cells.tex
Notion of equivalence of 2-quivers

@@
 
-  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
+  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
   A \emph{2-quiver} is a pair $\tilde Q=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
   Given a 2-quiver $\tilde Q$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed} if it is successor closed and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
-  \footnote{Include a notion of equivalence of $2$-quivers to justify the transformation of $2$-arrows into usual arrows.}
+
 \end{definition}
+We introduce a notion of equivalence of $2$-quivers.
+\begin{definition}\label{def:2equivalence}
+Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $q$ and $\Gamma(2)$ has precisely one sink $q'$.
+Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:q\to q'$.
+This defines a relation on the set of $2$-quivers denoted by $\tilde Q_V\to \tilde Q$.
+Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation.
+\end{definition}
+Observe that the set of vertices of two equivalent $2$-quivers coincide.
+\begin{lemma}
+Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
+The number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
+\end{lemma}
+\begin{proof}
+We may assume that $\tilde Q'=\tilde Q_V$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$.
+As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $q$, the unique sink of $\Gamma(2)$ by $q'$ and the new arrow by $\alpha_V:q\to q'$.
+
+Let $\beta\subset Q_0$ be a strong successor closed subset.
+Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a two arrow.
+Then it is also a $2$-arrow of $\tilde Q$.
+This means that  we have $\Gamma(2)_0\cap \beta\neq\varnothing$ if $\Gamma(1)_0\subset \beta$.
+
+Let $\alpha:i\to j\in (Q_V)_1$.
+If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $Q_0$.
+Thus assume that $\alpha=\alpha_V$.
+If $q\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $q$ is the unique source of $\Gamma(1)$ which means that for every vertex $p\in\Gamma(1)_0$ different from $q$, there exists an arrow $\alpha:q\to p$.
+As $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
+But then we have $q'\in\beta$ as there exists an arrow $\alpha:p'\to q'$.
+Thus $\beta$ is strong successor closed as a subset of $(Q_V)_0$.
+
+Thus assume that $\beta\subset (Q_V)_0$ is strong successor closed.
+The cases of arrows $\alpha\in Q_1$ and $2$-arrows $W\neq V$ can be treated as before.
+Thus consider the $2$-arrow $V$ and the arrow $\alpha_V$.
+Assume that $\Gamma(1)_0\subset\beta$.
+Then we have $q\in\beta$.
+But then we have $q'\in\beta$ as $\alpha_V:q\to q'$ and $\beta$ is successor closed as a subset of $(Q_V)_0$.
+It follows that $\Gamma(2)_0\cap\beta\neq\varnothing$.
+\end{proof}
 
@@
 
-\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
-  Lemma \ref{AR} can be generalized to the cases $m\leq 2$.
-  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
-\end{remark}
+%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
+%  Lemma \ref{AR} can be generalized to the cases $m\leq 2$.
+%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
+%\end{remark}
 

### 2018-01-17 Grassmannian_cells.tex
started improving section 5

@@
 
-\subsection{Lifting to $\widetilde{K(n)}$}
+\subsection{Lifting to $\widetilde{K(n)}$}\label{Lifting}
 
@@
 The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
-\begin{theorem}
+\begin{theorem}\label{thm:bb}
   \cite[Section 4]{bb}
@@
 
-\subsection{Torus Actions}
-\label{torusaction}
+\subsection{Torus Actions}\label{torusaction}
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:truncpp}
   Fix a dimension vector $\bfe$.
@@
 
-\begin{theorem}\label{celldec}
-  Every quiver Grassmannian of a preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
+\begin{theorem}\label{celldec}The following holds:
+\begin{enumerate}
+\item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
+\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq m-1$.
+Then every quiver Grassmannian $\Gr_{\tbfe}(X)$ has a cell decomposition into affine spaces.
+\end{enumerate}
 \end{theorem}
 \begin{proof}
-This follows by combining the results of Section 2 and Proposition \ref{fibers}.
+The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover}.
+The dual version for preinjective representations follows as $\Gr_{\tbfe}(P_m)\cong\Gr_{\udim P_m-\tbfe}(I_m)$.
+
+The second part follows in the same way, additionally, taking Theorem \ref{thm:truncpp} into account.
 \end{proof}
@@
 
-We recall the notion of Section \ref{QG} where we denote the arrows of $K(n)$ by $v_1,\ldots,v_n$.
-Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where $P_2^{(n-1)}$ depends on a choice as it is a truncated preprojective representation of dimension $(1,1)$.
-Indeed, it is the cokernel of a short exact sequence
+The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
+Therefore, we use the recursive construction described in Section \ref{Lifting}.
+In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
+Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and on $\udim P_m^V$.
+
+Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where $P_2^{(n-1)}$ is chosen to be the cokernel of the short exact sequence
 \[
-  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}
+  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}.}
 \]
-for which we have $n$ choices.
 Without loss of generality, we make the following choice when defining
 \[
-  P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{v_1}i^{(n-1)}_2=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+  P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{\alpha_1}i^{(n-1)}_2%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
 \]

### 2018-01-17 Grassmannian_cells.tex
Small notation changes

--- 2018-01-14 Grassmannian_cells.tex
@@
 Define the $F$-polynomial of a representation $X$ by 
-$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^e\in\ZZ[x_q\mid q\in Q_0].$$
+$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$
 
@@
 If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{ \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
-\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(q,w)}\mid q\in Q_0,w\in W_Q]\to\ZZ[x_q\mid q\in Q_0]$ given by $S(x_{(q,w)})=x_q$ for all $q\in Q_0$ and $w\in W_Q$.
+\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[x_i\mid i\in Q_0]$ given by $S(x_{(i,w)})=x_i$ for all $i\in Q_0$ and $w\in W_Q$.
 \end{enumerate} 

### 2018-01-19 Grassmannian_cells.tex
continued improving section 5

--- 2018-01-17 Grassmannian_cells.tex
@@
 Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
-The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
+We assume that $(j_1,\ldots,j_l)=(1,\ldots,l)$ which is no restriction as the general case can be obtained by relabelling.
+The Auslander-Reiten translate $\tau\tilde P_{3}^{(1,\ldots,l)}$ is given by
 	\begin{align*}
-          \xymatrix@R10pt@C20pt{&&(2,\alpha_{j_1}^{-1})\ar_{\alpha_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{j_l}^{-1})\ar_{\alpha_{j_l}}[llu]}
+          \xymatrix@R10pt@C20pt{&&(2,\alpha_{l+1}^{-1})\ar_{\alpha_{l+1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{n}^{-1})\ar_{\alpha_{n}}[llu]}
         \end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=\alpha^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,\alpha_{j_i}^{-1})\xrightarrow{\alpha_{j_i}}(1,1)$ for $i=1,\ldots,l$.
+In particular, the image of the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_{3}^{(1,\ldots,l)}$ has image $(2,\alpha_{i}^{-1})\xrightarrow{\alpha_{i}}(1,1)$ for $i=l+1,\ldots,n$.
 
@@
 In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
-Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and on $\udim P_m^V$.
-
-Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where $P_2^{(n-1)}$ is chosen to be the cokernel of the short exact sequence
+Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
+
+Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where we define $P_2^{(n-1)}$ by the lift (using the conventions of Example \ref{smallm}):
 \[
-  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}.}
+  \tilde P_2^{(n-1)}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
 \]
-Without loss of generality, we make the following choice when defining
+
+%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
+%\[
+%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
+%\]
+Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
 \[
-  P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{\alpha_1}i^{(n-1)}_2%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+  \Ext(P_2^{(n-1)},P_1)\cong\langle (2,1)\xrightarrow{\alpha_l}(1,\alpha_l)\mid l=2,\ldots,n\rangle.
 \]
-by its coefficient quiver.
-Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
-\[
-  \Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.
-\]
-
-This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
-\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
-by the coefficient quivers
+
+This defines recursively the truncated preprojective representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ by the lifts 
 \begin{align}
-  \label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.
+  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
 \end{align}
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$j^{(k)}_{2,n-k}$} +(2.5,0) node (B) {$j^{(k)}_{2,n-k-1}$}+(2.5,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(5,0) node (B1) {$\dots$} +(7.5,0) node (C) {$j^{(k)}_{2,2}$} +(7.5,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(10,0) node (D) {$j^{(k)}_{2,1}$}  +(12.5,0) node (E) {$i^{(k)}_2$} +(10,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 \node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
-\draw[<-] (D)--(E) node[pos=.5,above] {$v_1$};
-\draw[->,red] (Q1)--(C) node[pos=.5,above] {$v_2$};
-\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$v_3$};
-\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$v_{n-k-1}$};
-
-\draw[->,red] (Q3)--(A) node[pos=.5,above] {$v_{n-k}$};
+\draw[<-] (D)--(E) node[pos=.5,above] {\footnotesize$\alpha_1$};
+\draw[->,red] (Q1)--(C) node[pos=.5,above] {\footnotesize$\alpha_2$};
+\draw[->,red] (Q2)--(B1) node[pos=.5,above] {\footnotesize$\alpha_3$};
+\draw[->,red] (Q2b)--(B) node[pos=.5,above] {\footnotesize$\alpha_{n-k-1}$};
+
+\draw[->,red] (Q3)--(A) node[pos=.5,above] {\footnotesize$\alpha_{n-k}$};
 \end{tikzpicture}
@@
 \noindent
-where the $2$-arrows are coloured red.
-As the number of strong successor closed subsets of this $2$-quiver coincides with the number of successor closed subsets of the coefficient quiver, for clearness reasons, we will mostly work with the coefficient quiver instead.
-
-The next step is to define the $2$-quivers of $P^{(k)}_3$ whence the remaining $2$-quivers can be obtained recursively. First we choose the basis of $\Ext(P_2^{(1)},P_2)$ given by the linear maps
-$$\{i_2^{(n-1)}\xlongrightarrow{v_n}j_{2,i}\mid i=n-1,\ldots,1\}.$$
-This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ where we drop the indices of the vertices in abuse of notation.
-\\
+where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver instead.
+
+The next step is to define the $2$-quivers of certain truncated preprojectives $P^{(k)}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{(k)}$ can be obtained recursively.
+In view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any truncated preprojective of this dimension.
+
+As in Section \ref{Lifting}, let $\tilde P_2$ be supported at $(2,1)$. Then we have 
+$$\Ext(P_2^{(1)},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_2^{(1)},\alpha_i^{-1}\alpha_n\tilde P_2).$$
+This decomposition induces a basis of $\Ext(P_2^{(1)},P_2)$, each basis element given by the linear map $$(2,1)\xlongrightarrow{\alpha_n}(1,\alpha_n)\in\Hom_{\CC}((\tilde P_2^{(1)})_{(2,1)}),(\alpha_i^{-1}\alpha_n\tilde P_2)_{(1,\alpha_n)})$$
+for $i=1,\ldots,n-1$.
+
+Now define $\tilde P_3^{(n-1)}:=\tilde P_2^{(1)}$
+
+This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
+Note that the middle vertex of $P_3^{(n-1)}$ is $(2,1)$ and that all $2$-arrows end in a vertex corresponding to the vertex $(1,\alpha_n)$ of $\widetilde{K(n)}$.\\
 
@@
 \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
-\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$v_1$};
-\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$v_2$};
-\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
-\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
 \draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ;
-\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$v_1$};
-\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$v_2$};
-\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
-\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
@@
 \draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ;
-\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$v_1$};
-\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$v_{n-2}$};
-\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
-\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
+\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
 \draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$};
-\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$v_1$};
-\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$v_2$};
-\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
-\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
 \draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ;
-\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $v_1$};
-\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $v_2$};
-\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $v_{n-1}$};
+\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
+\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
+\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
 %\tikzstyle{every node}=[circle,fill=white!10]
@@
 %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
-\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$v_{n}$};
+\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$\alpha_{n}$};
 \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
-\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$v_{n}$};
+\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$\alpha_{n}$};
 \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
-\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$v_{n}$};
+\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$\alpha_{n}$};
 \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
@@
 \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$v_{n}$};
-\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$v_{n}$};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$v_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$\alpha_{n}$};
+\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$\alpha_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$\alpha_{n}$};
 
@@
 
-We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$.
-If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, Lemma \ref{AR} gives a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
-Let us consider the case $m=3$.
-The coefficient quiver of $\tau P_3^{(k)}$ is given by
-\[\xymatrix@R10pt@C20pt{&&i_{1}\ar_{v_1}[lld]\\ j &&\vdots\\&&i_{k}\ar_{v_{k}}[llu]}.\]
-The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{v_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{v_l} i_l$.
+We have $\dim \Hom(P_{m-1},\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_{m-1})=n-k$.
+If a basis of $\Ext(P_m^{(k)},P_{m-1})$ is compatible with a lift to the universal covering,  there is a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
+For $m=3$, the lift of $\tau P_3^{(k)}$ is given by
+\[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_k^{-1})\ar_{\alpha_{k}}[llu]}.\]
+The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{\alpha_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{\alpha_l} i_l$.
 Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$.
@@
 
+We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$.
+If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, it is straightforward to get a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
 Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure.
@@
 \draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
@@
 \draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
@@
 %\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \node (Q0)[draw=black,fit={(I3) (J31) }]{};
@@
 \draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 

### 2018-01-19 Grassmannian_cells.tex
continued improving section 5

@@
 
-\subsection{Fibrations of Quiver Grassmannians}
+\subsection{Fibrations of Quiver Grassmannians}\label{sec:fibrations}
 
@@
 Observe that the set of vertices of two equivalent $2$-quivers coincide.
-\begin{lemma}
+\begin{lemma}\label{lem:2equivalence}
 Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
@@
 
-The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
+The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $ P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
 Therefore, we use the recursive construction described in Section \ref{Lifting}.
@@
 Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
-
-Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where we define $P_2^{(n-1)}$ by the lift (using the conventions of Example \ref{smallm}):
+In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.\sayT{Introduce notation for $2$-quivers associated with $P_m^V$?}.
+
+For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
+It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}=\tilde P_2^{(1,\ldots,n-1)}$ as defined in Section \ref{Lifting}, i.e.
+we have:
 \[
-  \tilde P_2^{(n-1)}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
 \]
-
+We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
 %In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
@@
 Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
-\[
-  \Ext(P_2^{(n-1)},P_1)\cong\langle (2,1)\xrightarrow{\alpha_l}(1,\alpha_l)\mid l=2,\ldots,n\rangle.
-\]
-
-This defines recursively the truncated preprojective representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ by the lifts 
+\begin{align}\label{eq:case2}
+  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\alpha_i\tilde P_{1})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
+\end{align}
+
+This defines recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
 \begin{align}
@@
 \end{align}
-Note that we have a short exact sequence
-\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
-where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
-We define the $2$-quiver of $P_2^{(k)}$ by
+Note that, for general $m\geq 2$, we have a short exact sequence
+\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
+Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
+We define the $2$-quiver of $P_m^{[k]}$ by
 \\
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-The next step is to define the $2$-quivers of certain truncated preprojectives $P^{(k)}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{(k)}$ can be obtained recursively.
-In view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any truncated preprojective of this dimension.
-
-As in Section \ref{Lifting}, let $\tilde P_2$ be supported at $(2,1)$. Then we have 
-$$\Ext(P_2^{(1)},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_2^{(1)},\alpha_i^{-1}\alpha_n\tilde P_2).$$
-This decomposition induces a basis of $\Ext(P_2^{(1)},P_2)$, each basis element given by the linear map $$(2,1)\xlongrightarrow{\alpha_n}(1,\alpha_n)\in\Hom_{\CC}((\tilde P_2^{(1)})_{(2,1)}),(\alpha_i^{-1}\alpha_n\tilde P_2)_{(1,\alpha_n)})$$
+The next step is to define the $2$-quivers of certain truncated preprojectives $\tilde P^{[k]}_3$ and $P^{[k]}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{[k]}$ can be obtained recursively.
+
+Define $\tilde P_3^{[n-1]}:=\tilde P_3^{(1,\ldots,n-1)}=\alpha_n^{-1}\tilde P_2^{[1]}$. We have 
+$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
+This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
 for $i=1,\ldots,n-1$.
 
-Now define $\tilde P_3^{(n-1)}:=\tilde P_2^{(1)}$
-
-This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $P_3^{(n-1)}$ is $(2,1)$ and that all $2$-arrows end in a vertex corresponding to the vertex $(1,\alpha_n)$ of $\widetilde{K(n)}$.\\
+ This basis recursively gives rise to the following $2$-quiver of $\tilde P_3^{[k]}=\tilde P_3^{(1,\ldots,k)}$ (resp.
+for $P_3^{[k]}$) for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
+Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(1,1)$ and that all $2$-arrows end in this vertex of $\widetilde{K(n)}$.\\
 
@@
 
-\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ;
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{[1]}$} ;
 \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{(2)}$};
-
-\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ;
+\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{[2]}$};
+
+\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{[n-3]}$} ;
 \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$};
+\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{[n-2]}$};
 \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ;
+\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{[n-1]}$}   ;
 \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
@@
 %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
-\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$\alpha_{n}$};
+\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{\scriptsize$\alpha_{n}$};
 \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
-\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$\alpha_{n}$};
+\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
 \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
-\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$\alpha_{n}$};
+\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {\scriptsize$\alpha_{n}$};
 \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
@@
 \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$\alpha_{n}$};
-\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$\alpha_{n}$};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$\alpha_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
 
@@
 
-We have $\dim \Hom(P_{m-1},\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_{m-1})=n-k$.
-If a basis of $\Ext(P_m^{(k)},P_{m-1})$ is compatible with a lift to the universal covering,  there is a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
-For $m=3$, the lift of $\tau P_3^{(k)}$ is given by
-\[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_k^{-1})\ar_{\alpha_{k}}[llu]}.\]
-The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{\alpha_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{\alpha_l} i_l$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$.
-In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers.
-It can be seen that this is no restriction from the combinatorial point of view.
-
-We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$.
-If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, it is straightforward to get a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
-Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure.
-For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
-Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
-\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]
-
-As before we get a one-to-one correspondence between basis elements when passing to the universal covering quiver.
-More precisely, we can take the BGP-reflected basis of the basis of $\Ext(P_2^{(1)},P_2)$ from above.
-
-Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{(k)}$. The $2$-quiver of $P^{(k-1)}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{(k)}$ to the one of $P_{m}$
+For odd $m$, we have
+
+$$ \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{-1}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_i^{-1}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1})$$.
+
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with a lift to the universal covering which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+The representation $\tau\tilde P_3^{[k]}$ is given by
+\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
+Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
+It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
+
+\begin{align}\label{eq:case2}
+ \Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
+\end{align}
+
+Now we can recursively the $2$-quivers of $P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure.
+For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
+%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$. 
+As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[1]})$ and $\Ext(P_m^{[1]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
+Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{[k]}$.
+The $2$-quiver of $P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{[k]}$ to the one of $P_{m}$
 \\
@@
 \begin{tikzpicture}
-\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{(1)}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{(n-2)}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{(1)}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{(k)}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{(n-2)}$} +(13.5,0) node (E1b) {$P^{(n-1)}_{m-2}$} ;
+\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$P^{]n-1]}_{m-2}$} ;
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 
-\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{(k)}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{(n-2)}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{(n-1)}=P_{m}^{(1)}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{(n-1)}$};
+\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{[n-1]}=P_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{(k)}$ to its Auslander-Reiten translate $\tau P_{m+1}^{(k)}= P_{m-1}^{(k)}$ in $P_m$.
+\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau P_{m+1}^{[k]}= P_{m-1}^{[k]}$ in $P_m$.
 This subquiver can be found at the very right of the $2$-quiver of $P_m$.
@@
 \begin{theorem}
-  The Euler characteristic $\chi(\Gr_e(P_m^{(k)}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{(k)}$.
+  The Euler characteristic $\chi(\Gr_e(P_m^{[k]}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{[k]}$.
 \end{theorem}
@@
   We proceed by induction.
-  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{(n-1)}\}$.
+  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
   Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\emptyset,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
@@
 
-  Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{(k)}$ (resp. $\tilde P_{m+1}^{(k)}$) and consider the short exact sequence
+  Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{[k]}$ (resp. $\tilde P_{m+1}^{[k]}$) and consider the short exact sequence
   \[
-    \ses{\tilde P_m}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}.
+    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
   \]
-  Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{(k)}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{(k)}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
+  Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{[k]}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{[k]}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
   Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{(k)})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{(k)}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{(k)}})_0=\emptyset$.
-  But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{(k)}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{(k)}}$ by a $2$-arrow.
+  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\emptyset$.
+  But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{[k]}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{[k]}}$ by a $2$-arrow.
 \end{proof}

### 2018-01-20 Grassmannian_cells.tex
Random edits

--- 2018-01-17 Grassmannian_cells.tex
@@
 
-  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
+  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$\sayD{Should we write $\alpha w$ here so that arrows act of the left and compose as functions?} for $\alpha\in Q_1$ and $w\in W_Q$.
   Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.
@@
 \begin{lemma}
-  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
+  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
 \end{lemma}
@@
 We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
-Then the endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep_{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep_{\langle i\rangle} K(n)\to\rep_{\langle i\rangle} K(n)^{op}$.
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
@@
   \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
-  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
+  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
   This shows the second statement.
@@
 
-For each $m\ge2$, there is an Auslander-Reiten sequence \cite[Section V]{ars}
+For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
 \begin{equation}
@@
   \label{le:injective evaluation maps}
-Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
 \end{lemma}
@@
   As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
-  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
+  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
   in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
@@
   Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
-  \[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0.}\]
+  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
 
@@
   But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-  In this case, there is an isomorphism 
+  In this case, there are isomorphisms
   \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
@@
   \label{le:basic homological properties}
-  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
 \end{lemma}
@@
   %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
+\end{proof}
+
+\begin{lemma}
+  For $V\in\Gr(H_m)$, $m\ge1$, the representation $\Sigma_2(P_{m+1}^V)^\sigma$ is also truncated preprojective.
+\end{lemma}
+\begin{proof}
+  Apply the functor $\Sigma_2(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives}.
 \end{proof}
@@
    & 0 & 0 & & }\]
-  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
+  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
   \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
@@
 \begin{proof}
-  We proceed by simultaneous induction on $m$ and $\codim_{H_m} V$.
-
+  For the first claim, we proceed by induction on $m$.
   When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$ which gives both claims in this case.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$.
 
@@
 
-It will be rather important that the lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
 Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
-To simplify the notation, we abbreviate $P_{2l-1,i}:=P_{2l-1,\alpha_i}$ and $P_{2l,i}:=P_{2l,\alpha_i^{-1}}$.
+To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
 \begin{lemma}
   For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
-  These are the representations $P_{m-1,i}$ corresponding the $n$ different arrows of $K(n)$. 
+  These are the representations $\tilde P_{m-1,i}$ corresponding to the $n$ different arrows of $K(n)$. 
 \end{lemma}
@@
 \end{remark}
-Let
-$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-As we fixed the number of arrows, we drop the $n$ in what follows.
-
+
+Recall that $n\ge3$ is fixed.
+Set
+\[I_l:=\{(j_1,\ldots,j_l)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.\]
 With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
@@
   \begin{enumerate}
-    \item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
+    \item We have $\Hom_{K(n)}(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional.
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
+      \[\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).\]
     \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
@@
       \end{align}
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
-      $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).$$
   \end{enumerate}
@@
 \begin{proof}
-  The first part is immediate from Theorem \ref{covering}.
-  Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part.
-  The last part is also a consequence of Theorem \ref{covering}.
+  The first part is immediate from Theorem~\ref{covering}.
+  The second part is also a consequence of Theorem~\ref{covering}.
   Indeed, for $1\leq k\leq n$, we have 
@@
   The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
+  Now the observations of Section~\ref{sec:truncated preprojectives} immediately yield the final claim.
 \end{proof}
 In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
-Note that, we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
+Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
 \[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
@@
 
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by its dimension vector.
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
 We use this fact and do not state the particular maps defining the lifts.
@@
 The representation $\tilde P_2$ is defined by the following quiver:
-
 \begin{align*}

### 2018-01-20 Grassmannian_cells.tex
test

--- 2018-01-19 Grassmannian_cells.tex
@@
 %\usepackage[marginal]{showlabels}
-
+%
 \newtheorem{theorem}{Theorem}[section]

### 2018-01-20 Grassmannian_cells.tex
Section 3 edits

@@
 \begin{lemma}
-  For $V\in\Gr(H_m)$, $m\ge1$, the representation $\Sigma_2(P_{m+1}^V)^\sigma$ is also truncated preprojective.
-\end{lemma}
-\begin{proof}
-  Apply the functor $\Sigma_2(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives}.
-\end{proof}
+  \label{le:reflected truncated preprojectives}
+  For $V\in\Gr(H_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
+\end{lemma}
+\begin{proof}
+  By Corollary~\ref{cor:indecomposable truncated} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
+  In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
+  Thus, following Remark~\ref{rem:reflection recursion}, we may apply the functor $\Sigma_1(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives} to get the exact sequence
+  \[0\longrightarrow P_{m-1}\otimes V\xrightarrow{\Sigma_1(ev_V)^\sigma} P_m\longrightarrow \Sigma_1(P_{m+1}^V)^\sigma\longrightarrow 0\]
+  which gives the claim.
+\end{proof}
+
+For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
+Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
+\begin{lemma}
+  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+  Moreover, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  splits for every proper subspace $W\subsetneq V$.
+\end{lemma}
+\begin{proof}
+  For the first claim, we proceed by induction on $m$.
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$.
+
+  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which is not isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion}.
+
+  Now we show that the first claim implies the second.
+  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
+  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence above must split.
+\end{proof}
+\begin{corollary}
+  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+\end{corollary}
 
@@
 
-For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
-\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
-Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
-\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
-\begin{lemma}
-  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
-  Moreover, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  splits for every proper subspace $W\subsetneq V$.
-\end{lemma}
-\begin{proof}
-  For the first claim, we proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$.
-
-  By Corollary~\ref{cor:truncated preprojective isomorphism}, the first claim for $m\ge2$ and $\codim_{H_m} V = 1$ follows from the first claim for $m-1$.
-
-  Now we show that the first claim implies the second.
-  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
-  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and so the upper pullback sequence above will split giving the second claim.
-
-  We proceed by induction on $\codim_V W$.  
-  When $\codim_V W=1$, we have an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
-  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
-
-  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
-  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
-  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
-  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
-  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
-  The result now follows since the outer square is also a pullback.
-\end{proof}
-\begin{corollary}
-  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
-  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-\end{corollary}
-
+\sayD{The next result needs some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
 \begin{lemma}
@@
 
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$.
 Define $j_1^c$ as before.

### 2018-01-20 Grassmannian_cells.tex
Refactoring statements in Section 3

@@
   For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
-  Moreover, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  splits for every proper subspace $W\subsetneq V$.
-\end{lemma}
-\begin{proof}
-  For the first claim, we proceed by induction on $m$.
+\end{lemma}
+\begin{proof}
+  We proceed by induction on $m$.
   When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$.
-
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which is not isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion}.
-
-  Now we show that the first claim implies the second.
-  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
-  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence above must split.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.
+
+  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
 \end{proof}
@@
 \end{corollary}
+\begin{proof}
+  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  must split.
+  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
+\end{proof}
 

### 2018-01-21 Grassmannian_cells.tex
New proof of Lemma 3.38, random edits

@@
 \begin{lemma}
+  \label{le:lifts of transjectives}
   Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
+  \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
 \end{lemma}
@@
 \begin{lemma}
+  \label{le:projective subrepresentations}
   For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
@@
   \label{le:subrep}
-  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
+  %\sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
 This is because $U\notin\tilde P_{m-1,l}^\perp$}
@@
 \begin{proof}
-Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
-
-We proceed by induction.
+  We begin by observing that the projected representation $G_{K(n)}(\tilde P_m^{\uj})$ is a truncated preprojective of $K(n)$.
+  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G_{K(n)}(\tilde P_m^{\uj})$ are direct sums of preprojective representations of $K(n)$.
+  But any subrepresentation of $\tilde P_m^{\uj}$ also projects to a subrepresentation of $G_{K(n)}(\tilde P_m^{\uj})$.
+  Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
+  %Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
+  %We proceed by induction.
 Clearly $\tilde P_m$ has only preprojective subrepresentations.
@@
 Thus we get a commutative diagram
-
-\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
+  %\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
+  %  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+  %where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
+  %because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
 We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-
-As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
+  %As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
 Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
 Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l}}< 0$, we obtain
-\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
-But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
-
+  %\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
+  %But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
 \end{proof}
@@
   \cite[Section 4]{bb}
-  Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
-  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$, where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
+  Let $X^{\C^\ast}=\coprod_{i=1}^r C_i$ be the decomposition of the fixed point set of $X$ into connected components.
+  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ containing $C_i$ as a subvariety.
   Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle. 
-
   In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
@@
 \subsection{Torus Actions}\label{torusaction}
-
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
 We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
-Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
-there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
-\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
+Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.
+
+Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $1\leq r_1\leq r_2\ldots\leq r_l\leq n$ such that
+\[v_1,\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_l+1},\ldots,v_n\in X_l.\]
 Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ linearly to $X$.
+Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
 This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
-We can write every $U\in\Gr_k(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
-there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ and a unique matrix representation of $U$ of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k)\]
-where the unit vectors are in the columns $i_1,\ldots,i_k$.
-All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_k)$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
-we have
+We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ so that $M(U)$ is of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k),\]
+where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
+The set of all subspaces of $X$ represented by matrices of this fixed form define the \emph{Schubert cell} $X_\bfi$.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.\ we have
 \[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
-for $w=1,\ldots,k$. Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+for $w=1,\ldots,n$.
+Every Schubert cell is invariant under the torus action, i.e.\ $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
 \begin{lemma}
   \label{usualGrass}
-  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
+  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
   Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.

### 2018-01-21 Grassmannian_cells.tex
Random edits and notation changes

@@
 \newtheorem{example}[theorem]{Example}
+
+\numberwithin{equation}{section}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Representation Theory of $K(n)$}\label{sec:RepK(n)}
+\section{Representation Theory of $K(n)$}
+\label{sec:RepK(n)}
 
@@
 
-\subsection{Torus Actions}\label{torusaction}
+\subsection{Torus Actions}
+\label{torusaction}
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
@@
 Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $1\leq r_1\leq r_2\ldots\leq r_l\leq n$ such that
-\[v_1,\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_l+1},\ldots,v_n\in X_l.\]
-Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{l-1}<r_l=n$ such that
+\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{l-1}+1},\ldots,v_{r_l}\in X_l.\]
+Moreover, we choose a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_j$ for some $j$.
 Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
 This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
-We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ so that $M(U)$ is of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k),\]
+We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
+\[M(U):=
+  \begin{pmatrix}
+    \ast&\cdots &\ast &1&0 &\cdots& 0 & 0 & 0 &\cdots&0&0&0&\cdots&0\\
+    \ast&\cdots &\ast&0&\ast&\cdots &\ast&1&0&\cdots&0&0&0&\cdots&0\\
+    \ast &\cdots&\ast&0&\ast &\cdots&\ast&0&\ast&\cdots&0&0&0&\cdots&0\\[-0.4em]
+    \vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots&\ddots&\vdots\\
+    \ast&\cdots &\ast&0&\ast&\cdots &\ast&0&\ast&\cdots&0&0&0&\cdots&0\\
+    \ast&\cdots &\ast&0&\ast&\cdots &\ast&0&\ast&\cdots&\ast&1&0&\cdots&0
+  \end{pmatrix}\in M_{k,n}(k),\]
 where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
@@
   \label{usualGrass}
-  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
-  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
-\end{lemma}
-\begin{proof}
-  If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
-\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_{i-1}+1)}(U\cap X_i)=U\]
-where $j_0=0$.
-
+  Consider $d:\{1,\ldots,n\}\to\ZZ$ for which $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
+  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{j=1}^l U\cap X_j$.
+\end{lemma}
+\begin{proof}
+  If $U=\bigoplus_{j=1}^l U\cap X_j$, we have 
+  \[t.U=\bigoplus_{j=1}^l t.(U\cap X_j)=\bigoplus_{j=1}^l t^{d(r_j)}(U\cap X_j)=U.\]
   Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
-Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{w}\in X_s$.
-As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero.
-This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
-As the colums are linear independent, this already shows the claim.
+  Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_w\in X_j$. 
+  As the matrix representation $M(U)$ is uniquely determined, the assumptions on $d$ imply that all matrix coefficients corresponding to a basis element $v_i$ with $v_i\notin X_j$ are zero.
+  This means that $\widehat{M(U)}_w\in X_j$, where~$\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
+  As the colums are linearly independent, this already shows the claim.
 \end{proof}
@@
 We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
-We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$.
-We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$.
-For a fixed a subspace $U_q$, we can define the subspace $t.U_q$.
-In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$.
-Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$.
-\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
-\end{lemma}
-\begin{proof} 
-  Let $U\in \Gr_\bfe(X)$.
+We can consider the decomposition $X_i=\bigoplus_{(i,\chi)\in A_Q} X_{(i,\chi)}$.
+We define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_q$.
+For a fixed a subspace $U_i$, we can define the subspace $t.U_i$.
+In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_\bfe(X)$ as $t.U=(t.U_i)_{i\in Q_0}$ is no subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
+Actually, such an action has to satisfy $X_\alpha(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
+\begin{lemma}
+  Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
+  If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_Q$.
+\end{lemma}
+\begin{proof} 
+  Let $U\in\Gr_\bfe(X)$.
 Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
@@
 \end{lemma}
-\begin{proof}Assume that $|Q_1|=n$.
-Since $X$ is finite-dimensional and indecomposable, $\mathrm{supp}( X)$ is a connected and finite subquiver of $\hat Q$.
-In order to prove the statement, we may assume that $(q,0)\in \mathrm{supp}(X)$ for some $q\in Q_0$.
+\begin{proof}
+  Assume that $|Q_1|=n$.
+  Since $X$ is finite-dimensional and indecomposable, the support quiver $\mathrm{supp}(X)$ is a connected and finite subquiver of $\hat Q$.
+  In order to prove the statement, we may assume that $(i,0)\in\mathrm{supp}(X)$ for some $i\in Q_0$.
   We fix $c_\alpha\in\NN$ and show that we can choose a degree such that the two conditions are satisfied for this choice.
-Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(q,0)$ such that the underlying graph of the path has no cycles.
-This implies that, for $(q',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have $|d_i|\leq K$.
+  Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(i,0)$ such that the underlying graph of the path has no cycles.
+  This implies that, for $(i',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have $|d_j|\leq K$.
 
   Set $c_{\alpha_1}=1$ and choose $c_{\alpha_j}$ recursively in such way that 
-\[c_{\alpha_j}\geq 2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}\]
-for $j=2,\ldots,n$.
-
-Let $f:A_Q\to \ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(q',\chi):=f(\chi)$ for $(q',\chi)\in\mathrm{supp}(X)$.
-In particular, for $(q',\chi)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have
-\[d(q',\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]
+  \[c_{\alpha_k}\geq 2(K+1)\sum_{j=1}^{k-1} c_{\alpha_j}\]
+  for $k=2,\ldots,n$.
+
+  Let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i',\chi):=f(\chi)$ for $(i',\chi)\in\mathrm{supp}(X)$.
+  In particular, for $(i',\chi)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have
+  \[d(i',\chi)=\sum_{j=1}^n d_jc_{\alpha_j}.\]
 
   First note that we have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
-Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^{n}d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^{n}e_ic_{\alpha_i}$.
+  Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^n d_ic_{\alpha_i}=\sum_{i=1}^n e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^n d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^n e_ic_{\alpha_i}$.
   This implies
   \[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
-Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}$$
-This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.
+  Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain 
+  \[|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}.\]
+  This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_i}$.
 
@@
   Thus we chose $c_{\alpha_j}$ in such a way that it is greater than $2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}$. 
-
-\end{proof}
-In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.
-
-\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
-Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
- a torus action on $\Gr_\bfe^Q(X)$ such that
-  $$\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
+\end{proof}
+
+In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{degreecondition}.
+\begin{theorem}
+  Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
+  Then the torus action of $T$ on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  \[\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
+  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
 \end{theorem}
 \begin{proof}
-A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.
-$t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$.
-Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$.
+  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$, $t\in\C^\ast$.
+  Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_i}(X_i)$ induced by the decompositions $X_i=\bigoplus_{\chi\in A_Q} X_{i,\chi}$.
   A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
-\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
-Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
+  \[X_i\cap U_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}\cap U_{(i,\chi)}=\bigoplus_{\chi\in A_Q} U_{(i,\chi)}.\]
+  Thus we can apply Lemma~\ref{usualGrass} to obtain the claim.
 \end{proof}
@@
 \subsection{$GL_n$ Action on Arrows of $K(n)$}
-Observe that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
+We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
 More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.

### 2018-01-22 Grassmannian_cells.tex
Section 3.2 edits

@@
 \xyoption{all}
+
+\usepackage[inline]{showlabels}
 
@@
 \newcommand{\cP}{\mathcal{P}}
-\newcommand{\ui}{\underline i}
-\newcommand{\uj}{\underline j}
+\newcommand{\ui}{{\underline i}}
+\newcommand{\uj}{{\underline j}}
 \newcommand\udim{{\underline{\dim}\, }}
@@
 Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
-In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojectives to the universal cover $\widetilde{K(n)}$ of the quiver $K(n)$.
+In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
 This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
-The main advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
+Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
+One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
 
@@
 First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
-Moreover, under this operation all sinks become sources and vice versa.
-The preprojective lifts we use are defined recursively as follows.
+Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
+The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
 \begin{itemize}
@@
 It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
-Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
+Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
@@
 \begin{lemma}
-  For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
-  These are the representations $\tilde P_{m-1,i}$ corresponding to the $n$ different arrows of $K(n)$. 
-\end{lemma}
-\begin{proof}
-  This is clear for $m=2$ and follows in general by applying the identities \eqref{eq:recursive covers}.
+  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
+  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
+\end{lemma}
+\begin{proof}
+  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
 \end{proof}
@@
 
-Recall that $n\ge3$ is fixed.
+Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
 Set
-\[I_l:=\{(j_1,\ldots,j_l)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.\]
-With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
-More detailed, we obtain a sequence of preprojective representations
-$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$
-
+\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.\]
+Depending on context (more specifically the parity of $m+1$ below), we will sometimes identify the word $(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
+In this way, we associate to each $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$, $1\leq k\leq m$, a preprojective subrepresentation $\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+More precisely, we obtain a sequence of preprojective representations 
+\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
 \begin{lemma}
   \label{le:homdecomposition}
-  \sayT{I split up some lemmas. Check references}
-  Let $m\geq 2$. The following holds:
+  For $m\geq 1$, the following hold.
   \begin{enumerate}
-    \item We have $\Hom_{K(n)}(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional.
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
-      \[\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).\]
-    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
+    \item We have $\Hom_{K(n)}(P_m,P_{m+1})\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
+    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
+      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
+    \item For every $\ui\in A_1^{(l)}$, there exists a truncated preprojective representation $\tilde P_{m+1}^\ui$ which is the cokernel of
       \begin{align}
         \label{ses1}
-        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
+        \ses{\bigoplus_{j=1}^l \tilde P_{m,i_j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\ui}}.
       \end{align}
@@
   Indeed, for $1\leq k\leq n$, we have 
-  $$\CC=\Hom_Q(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k}).$$
-  But $\Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong\CC$ and so we must have $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$.
-  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
-  Now the observations of Section~\ref{sec:truncated preprojectives} immediately yield the final claim.
+  $$\CC=\Hom_{K(n)}(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j}).$$
+  But $\Hom_{\widetilde{K(n)}}(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
+  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.
+
+  For the final claim, observe that under the isomorphism from part (1) the sequence $\ui\in A_1^{(l)}$ corresponds to an $l$-dimensional subspace $V\in H_m$.
+  The map $\bigoplus_{j=1}^l \tilde P_{m,i_j}\to \tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
+  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^\ui$.
 \end{proof}
@@
 
-\begin{corollary}\label{cor: perpendicular}
+\begin{corollary}\label{cor:perpendicular}
 For $m\geq 3$ and $\uj\in I_l$, we have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
@@
 
-Corollary \ref{cor: perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
+Corollary \ref{cor:perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
 This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ and thus $$\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\cong  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U).$$ This means that the induced map
@@
 
-Again we can apply Corollary \ref{cor: perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
+Again we can apply Corollary \ref{cor:perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
  Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.

### 2018-01-22 Grassmannian_cells.tex
some edits

--- 2018-01-21 Grassmannian_cells.tex
@@
 
-  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$\sayD{Should we write $\alpha w$ here so that arrows act of the left and compose as functions?} for $\alpha\in Q_1$ and $w\in W_Q$.
+  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
   Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.
@@
 \begin{lemma}
-  \label{le:lifts of transjectives}
-  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
-  \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
+  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
 \end{lemma}
@@
 We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
-Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep_{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
-In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep_{\langle i\rangle} K(n)\to\rep_{\langle i\rangle} K(n)^{op}$.
+Then the endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
@@
   \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
-  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
+  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
   This shows the second statement.
@@
 
-For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
+For each $m\ge2$, there is an Auslander-Reiten sequence \cite[Section V]{ars}
 \begin{equation}
@@
   \label{le:injective evaluation maps}
-  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
 \end{lemma}
@@
   As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
-  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
+  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
   in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
@@
   Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
-  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
+  \[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0.}\]
 
@@
   But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
-  In this case, there are isomorphisms
+  In this case, there is an isomorphism 
   \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
@@
   \label{le:basic homological properties}
-  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
 \end{lemma}
@@
   %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:reflected truncated preprojectives}
-  For $V\in\Gr(H_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
-\end{lemma}
-\begin{proof}
-  By Corollary~\ref{cor:indecomposable truncated} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
-  In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
-  Thus, following Remark~\ref{rem:reflection recursion}, we may apply the functor $\Sigma_1(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives} to get the exact sequence
-  \[0\longrightarrow P_{m-1}\otimes V\xrightarrow{\Sigma_1(ev_V)^\sigma} P_m\longrightarrow \Sigma_1(P_{m+1}^V)^\sigma\longrightarrow 0\]
-  which gives the claim.
-\end{proof}
-
-For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
-\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
-Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
-\begin{lemma}
-  \label{le:projective subrepresentations}
-  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
-\end{lemma}
-\begin{proof}
-  We proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.
-
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-\end{proof}
-\begin{corollary}
-  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
-  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-\end{corollary}
-\begin{proof}
-  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence
-  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  must split.
-  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
 \end{proof}
@@
    & 0 & 0 & & }\]
-  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
+  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
   \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
@@
 
-\sayD{The next result needs some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
+For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
+where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
+Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
+\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
+\begin{lemma}
+  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+  Moreover, the upper pullback sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+  splits for every proper subspace $W\subsetneq V$.
+\end{lemma}
+\begin{proof}
+  We proceed by simultaneous induction on $m$ and $\codim_{H_m} V$.
+
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$ which gives both claims in this case.
+
+  By Corollary~\ref{cor:truncated preprojective isomorphism}, the first claim for $m\ge2$ and $\codim_{H_m} V = 1$ follows from the first claim for $m-1$.
+
+  Now we show that the first claim implies the second.
+  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
+  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and so the upper pullback sequence above will split giving the second claim.
+
+  We proceed by induction on $\codim_V W$.  
+  When $\codim_V W=1$, we have an exact sequence
+  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
+  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
+
+  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
+  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
+  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
+  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
+  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
+  The result now follows since the outer square is also a pullback.
+\end{proof}
+\begin{corollary}
+  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
+  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
+\end{corollary}
+
 \begin{lemma}
@@
 
-It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+It will be rather important that the lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
 Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
-To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
+To simplify the notation, we abbreviate $P_{2l-1,i}:=P_{2l-1,\alpha_i}$ and $P_{2l,i}:=P_{2l,\alpha_i^{-1}}$.
 \begin{lemma}
   For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
-  These are the representations $\tilde P_{m-1,i}$ corresponding to the $n$ different arrows of $K(n)$. 
+  These are the representations $P_{m-1,i}$ corresponding the $n$ different arrows of $K(n)$. 
 \end{lemma}
@@
 \end{remark}
-
-Recall that $n\ge3$ is fixed.
-Set
-\[I_l:=\{(j_1,\ldots,j_l)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.\]
+Let
+$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
+As we fixed the number of arrows, we drop the $n$ in what follows.
+
 With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$.
@@
   \begin{enumerate}
-    \item We have $\Hom_{K(n)}(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional.
-    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
-      \[\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).\]
+    \item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
     \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
@@
       \end{align}
+    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
+      $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).$$
   \end{enumerate}
@@
 \begin{proof}
-  The first part is immediate from Theorem~\ref{covering}.
-  The second part is also a consequence of Theorem~\ref{covering}.
+  The first part is immediate from Theorem \ref{covering}.
+  Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part.
+  The last part is also a consequence of Theorem \ref{covering}.
   Indeed, for $1\leq k\leq n$, we have 
@@
   The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
-  Now the observations of Section~\ref{sec:truncated preprojectives} immediately yield the final claim.
 \end{proof}
 In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
-Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
+Note that, we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
 \[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
@@
 
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
+As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by its dimension vector.
 We use this fact and do not state the particular maps defining the lifts.
@@
 The representation $\tilde P_2$ is defined by the following quiver:
+
 \begin{align*}
@@
   \label{le:subrep}
-  %\sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
+  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
 This is because $U\notin\tilde P_{m-1,l}^\perp$}
@@
 \begin{proof}
-  We begin by observing that the projected representation $G_{K(n)}(\tilde P_m^{\uj})$ is a truncated preprojective of $K(n)$.
-  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G_{K(n)}(\tilde P_m^{\uj})$ are direct sums of preprojective representations of $K(n)$.
-  But any subrepresentation of $\tilde P_m^{\uj}$ also projects to a subrepresentation of $G_{K(n)}(\tilde P_m^{\uj})$.
-  Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
-  %Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
-  %We proceed by induction.
+Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
+
+We proceed by induction.
 Clearly $\tilde P_m$ has only preprojective subrepresentations.
@@
 Thus we get a commutative diagram
-  %\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  %  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-  %where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-  %because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
+
+\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
+  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
+where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
+because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
 We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-  %As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
+
+As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
 Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
 Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l}}< 0$, we obtain
-  %\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
-  %But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
+\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
+But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
+
 \end{proof}
@@
 
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$.
+\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$.
 Define $j_1^c$ as before.
@@
   \cite[Section 4]{bb}
-  Let $X^{\C^\ast}=\coprod_{i=1}^r C_i$ be the decomposition of the fixed point set of $X$ into connected components.
-  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ containing $C_i$ as a subvariety.
+  Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
+  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$, where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
   Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.
+
   In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
@@
 \subsection{Torus Actions}\label{torusaction}
+
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
 We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.
-
-Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $1\leq r_1\leq r_2\ldots\leq r_l\leq n$ such that
-\[v_1,\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_l+1},\ldots,v_n\in X_l.\]
+Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner.
+Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
+We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e.
+there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
+\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
 Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
+Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ linearly to $X$.
 This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
-We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ so that $M(U)$ is of the form
-\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k),\]
-where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
-The set of all subspaces of $X$ represented by matrices of this fixed form define the \emph{Schubert cell} $X_\bfi$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.\ we have
+We can write every $U\in\Gr_k(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e.
+there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ and a unique matrix representation of $U$ of the form
+\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k)\]
+where the unit vectors are in the columns $i_1,\ldots,i_k$.
+All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_k)$.
+The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.
+we have
 \[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
-for $w=1,\ldots,n$.
-Every Schubert cell is invariant under the torus action, i.e.\ $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+for $w=1,\ldots,k$. Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
 \begin{lemma}
   \label{usualGrass}
-  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
+  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
   Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
@@
 Define the $F$-polynomial of a representation $X$ by 
-$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$
+$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^e\in\ZZ[x_q\mid q\in Q_0].$$
 
@@
 If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{ \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
-\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[x_i\mid i\in Q_0]$ given by $S(x_{(i,w)})=x_i$ for all $i\in Q_0$ and $w\in W_Q$.
+\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(q,w)}\mid q\in Q_0,w\in W_Q]\to\ZZ[x_q\mid q\in Q_0]$ given by $S(x_{(q,w)})=x_q$ for all $q\in Q_0$ and $w\in W_Q$.
 \end{enumerate} 
@@
 \begin{definition}\label{def:2equivalence}
-Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $q$ and $\Gamma(2)$ has precisely one sink $q'$.
-Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:q\to q'$.
+Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $p$ and $\Gamma(2)$ has precisely one sink $q$.
+Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:p\to q$.
 This defines a relation on the set of $2$-quivers denoted by $\tilde Q_V\to \tilde Q$.
@@
 \begin{lemma}\label{lem:2equivalence}
-Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
-The number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
+Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. A subset $\beta\subset Q_0$ is strong successor closed if and only of $\beta\subset Q_0'$ is strong successor closed.
+In particular, the number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
 \end{lemma}

### 2018-01-23 Grassmannian_cells.tex
test
Section 3.2 edits and notation changes up to Lemma 3.36

--- 2018-01-22 Grassmannian_cells.tex
@@
     \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
-      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
-      %This is because $\Sigma_2 S_2=0$.
   \end{enumerate}
@@
   The following hold:
-  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
   \begin{enumerate}
@@
     \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
-   % \item The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
   \end{enumerate}
@@
   This shows the second statement.
-
-%For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$.
-As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
-%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
-%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
-%As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
 \end{proof}
@@
 
-Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
-%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
+Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
 Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
 Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-%Lemma~\ref{le:hom equivariance} gives an identification of $\Gr(H_m)$ with $\Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
 For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.
@@
 where the right-hand morphism is the natural evaluation map.
-
 \begin{lemma}
@@
 \end{lemma}
-%%%%%%%%%%%%%%%%%%%
-% needs polishing %
-%%%%%%%%%%%%%%%%%%%
-\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
+\begin{proof}
   As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
@@
 
-\subsection{Lifting to $\widetilde{K(n)}$}\label{Lifting}
+\subsection{Lifting to $\widetilde{K(n)}$}
+\label{Lifting}
 
@@
 Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
-Set
-\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.\]
-Depending on context (more specifically the parity of $m+1$ below), we will sometimes identify the word $(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
-In this way, we associate to each $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$, $1\leq k\leq m$, a preprojective subrepresentation $\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
-More precisely, we obtain a sequence of preprojective representations 
+For $l\ge1$, set
+\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_{j+1}\text{ for } 1\le j<l\}.\]
+Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
+In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$ we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
 \[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
@@
   \begin{enumerate}
-    \item We have $\Hom_{K(n)}(P_m,P_{m+1})\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
+    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
     \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
       \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
-    \item For every $\ui\in A_1^{(l)}$, there exists a truncated preprojective representation $\tilde P_{m+1}^\ui$ which is the cokernel of
-      \begin{align}
+    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
+      \begin{equation}
         \label{ses1}
-        \ses{\bigoplus_{j=1}^l \tilde P_{m,i_j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\ui}}.
-      \end{align}
+        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
+      \end{equation}
   \end{enumerate}
 \end{lemma}
+\begin{remark}
+  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
+\end{remark}
 \begin{proof}
@@
   The second part is also a consequence of Theorem~\ref{covering}.
-  Indeed, for $1\leq k\leq n$, we have 
-  $$\CC=\Hom_{K(n)}(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j}).$$
-  But $\Hom_{\widetilde{K(n)}}(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
+  Indeed, for $1\leq j\leq n$, we have 
+  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
+  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
   The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.
 
-  For the final claim, observe that under the isomorphism from part (1) the sequence $\ui\in A_1^{(l)}$ corresponds to an $l$-dimensional subspace $V\in H_m$.
-  The map $\bigoplus_{j=1}^l \tilde P_{m,i_j}\to \tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
-  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^\ui$.
-\end{proof}
-In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
-Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
-\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
+  For the final claim, observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to a subspace $V\in H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
+  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
+  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$.
+\end{proof}
+In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
 \begin{lemma}
   \label{le:properties}
-  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
-  For $m\geq 2$ and $\uj\in I_l$, the following hold:
+  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
   \begin{enumerate}
-    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
-    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
-    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
+    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
+      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
+    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
+    \item We have $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
   \end{enumerate}
@@
 \begin{proof}
-  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.
-
-  The second identities are an immediate consequence of Lemma \ref{le:basic homological properties}, but can also be obtained when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
-%  As $\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the identities in the second statement follow when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
-
-  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\CC$.
-Thus applying $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\underline{\quad})$ to (\ref{ses1}) yields $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional.
-In view of the second identity, we obtain the third identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$ to (\ref{ses1}).
-\end{proof} 
-%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
+  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
+  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
+  where the final zero follows from Lemma~\ref{le:homdecomposition}(2).
+  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).
+
+  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
+  Part (3) then follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1}.
+\end{proof}
+
+Note that by Lemma~\ref{le:properties}(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
+\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
 
@@
   The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
-  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\emptyset,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
+  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
   As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.
@@
   Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\emptyset$.
+  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\varnothing$.
   But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{[k]}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{[k]}}$ by a $2$-arrow.

### 2018-01-23 Grassmannian_cells.tex
Section 3.2

@@
 For $l\ge1$, set
-\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_{j+1}\text{ for } 1\le j<l\}.\]
+\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\}.\]
 Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
@@
 
+Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
 In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
@@
 In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
-The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition.
+The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section \ref{sec:fibrations}.
 The second is the notion of compatible pairs in a maximal Dyck path.
@@
   Let $Q=(Q_0,Q_1)$ be a quiver.
-  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $v:p\to q$ in $Q_1$ implies $q\in\beta$.
+  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $\alpha:p\to q$ in $Q_1$ implies $q\in\beta$.
 
@@
 We may assume that $\tilde Q'=\tilde Q_V$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$.
-As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $q$, the unique sink of $\Gamma(2)$ by $q'$ and the new arrow by $\alpha_V:q\to q'$.
-
-Let $\beta\subset Q_0$ be a strong successor closed subset.
-Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a two arrow.
+As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $p$, the unique sink of $\Gamma(2)$ by $q$ and the new arrow by $\alpha_V:p\to q$.
+
+Let $\beta\subset Q_0$ be a strong successor closed subset (of the $2$-quiver $Q$).
+Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a  $2$-arrow.
 Then it is also a $2$-arrow of $\tilde Q$.
-This means that  we have $\Gamma(2)_0\cap \beta\neq\varnothing$ if $\Gamma(1)_0\subset \beta$.
+This means that  we have $\Gamma'(2)_0\cap \beta\neq\varnothing$ if $\Gamma'(1)_0\subset \beta$.
 
@@
 Thus assume that $\alpha=\alpha_V$.
-If $q\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $q$ is the unique source of $\Gamma(1)$ which means that for every vertex $p\in\Gamma(1)_0$ different from $q$, there exists an arrow $\alpha:q\to p$.
+If $p\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that for every vertex $q'\in\Gamma(1)_0$ different from $p$, there exists an arrow $\alpha:p\to q'$.
 As $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
-But then we have $q'\in\beta$ as there exists an arrow $\alpha:p'\to q'$.
+But then we have $q\in\beta$ as there exists an arrow $\alpha:p'\to q$ if $p'\neq q$.
 Thus $\beta$ is strong successor closed as a subset of $(Q_V)_0$.
@@
 Thus assume that $\beta\subset (Q_V)_0$ is strong successor closed.
-The cases of arrows $\alpha\in Q_1$ and $2$-arrows $W\neq V$ can be treated as before.
+The cases of arrows $\alpha\in Q_1$ and $2$-arrows $V'\neq V$ can be treated as before.
 Thus consider the $2$-arrow $V$ and the arrow $\alpha_V$.
 Assume that $\Gamma(1)_0\subset\beta$.
-Then we have $q\in\beta$.
-But then we have $q'\in\beta$ as $\alpha_V:q\to q'$ and $\beta$ is successor closed as a subset of $(Q_V)_0$.
+Then we have $p\in\beta$.
+But then we have $q\in\beta$ as $\alpha_V:p\to q$ and $\beta$ is successor closed as a subset of $(Q_V)_0$.
 It follows that $\Gamma(2)_0\cap\beta\neq\varnothing$.

### 2018-01-23 Grassmannian_cells.tex
Notation change before Example 3.37

@@
 
-Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$.
-Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$.
-These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\CC$.
+%Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
+In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
+That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
+These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
 

### 2018-01-23 Grassmannian_cells.tex
Section 5 (not finished)

--- 2018-01-23 Grassmannian_cells.tex
@@
 In general, considering the linear map  
-\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},\]
+\begin{align}\label{eq:homext}d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},\end{align}
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
@@
 
-The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $ P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
-Therefore, we use the recursive construction described in Section \ref{Lifting}.
+The next step is to associate a $2$-quiver with certain lifts of (truncated) preprojective representation $\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
+Recall that the cells of the quiver Grassmannians attached to $P_m^{\uj}:= F_{K(n)}\tilde P_m^{\uj}$ coincide with those attached to the lift $\tilde P_m^{\uj}$.
+
+For building these $2$-quivers, we use the recursive construction described in Section \ref{Lifting}.
 In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
 Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
-In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.\sayT{Introduce notation for $2$-quivers associated with $P_m^V$?}.
-
-For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}=\tilde P_2^{(1,\ldots,n-1)}$ as defined in Section \ref{Lifting}, i.e.
-we have:
+In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.
+
+%For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
+It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}:=\tilde P_2^{(1,\ldots,n-1)}$.
+Using the conventions of Section \ref{Lifting} the representation $\tilde P_2^{[n-1]}$ is defined by
 \[
@@
 \]
-We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
+We now recursively consider the lifted truncated preprojectives $\tilde P_m^{[k]}:=\tilde P_m^{(1,\ldots,k)}$ for $m\geq 2$ and $0\leq k\leq n-1$. We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
 %In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
@@
 %\]
-Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
+Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:homext}), we have 
 \begin{align}\label{eq:case2}
-  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\alpha_i\tilde P_{1})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
+  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\tilde P_{1,i})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
 \end{align}
 
-This defines recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
+This yields recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
 \begin{align}
@@
 \end{align}
-Note that, for general $m\geq 2$, we have a short exact sequence
+For general $m\geq 2$, there exists a short exact sequence
 \[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
 Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
-We define the $2$-quiver of $P_m^{[k]}$ by
+We define the $2$-quiver of $P_2^{[k]}$ by
 \\
@@
 \noindent
-where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver instead.
-
-The next step is to define the $2$-quivers of certain truncated preprojectives $\tilde P^{[k]}_3$ and $P^{[k]}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{[k]}$ can be obtained recursively.
+where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver (\ref{coeff}) instead.
+
+The next step is to define the $2$-quivers of certain truncated preprojective lifts $\tilde P^{[k]}_3$ (resp.
+of $P^{[k]}_3$) whence the remaining $2$-quivers attached to the truncated preprojectives $P_m^{[k]}$ can be obtained recursively.
 
@@
 for $P_3^{[k]}$) for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(1,1)$ and that all $2$-arrows end in this vertex of $\widetilde{K(n)}$.\\
+Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex $(1,1)$ of $\widetilde{K(n)}$.\\
 

### 2018-01-25 Grassmannian_cells.tex
Section 3.2 edits and notation changes (not completed)

--- 2018-01-23 Grassmannian_cells.tex
@@
 \newcommand{\C}{\mathbb{C}}
+\newcommand{\cA}{\mathcal{A}}
+\newcommand{\cB}{\mathcal{B}}
 \newcommand{\cC}{\mathcal{C}}
@@
 \begin{definition}
+  \label{def:covering quivers}
   The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
@@
 We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
-First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
+In the notation of Definition~\ref{def:covering quivers}, this means $G(\tilde P_m)=P_m$, where $G$ is the covering functor 
+\[G:=G_{K(n)}:\rep\widetilde{K(n)}\to\rep K(n).\]
+
+To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
 Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
@@
       \label{eq:recursive covers}
-      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
+      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
     \end{align}
+    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
 \end{itemize}
 
-It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
+It will be rather important that our chosen lifts of $\tilde P_{2l}$ and $\tilde P_{2l-1}$, $l\ge1$, live on two different components of the universal covering quiver.
 Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
-Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
+Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
 To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
@@
 \begin{remark}
-  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
+  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
   In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
@@
 
-Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
-For $l\ge1$, set
-\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\}.\]
-Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
-In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$ we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
-More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
-\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
+The next result establishes some basic homological properties of these translated preprojective representations.
 \begin{lemma}
@@
       \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
+    \item For $j\in\{1,\ldots,n\}$, we have
+      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
     \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
@@
       \end{equation}
+      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
   \end{enumerate}
@@
 \begin{proof}
-  The first part is immediate from Theorem~\ref{covering}.
-  The second part is also a consequence of Theorem~\ref{covering}.
+  Part (1) is immediate from Theorem~\ref{covering}.
+  Part (2) is also a consequence of Theorem~\ref{covering}.
   Indeed, for $1\leq j\leq n$, we have 
@@
 
-  For the final claim, observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to a subspace $V\in H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
+  Part (3) is clear for $m=1$ and follows for $m\ge2$ by applying the reflection recursion \eqref{eq:recursive covers}.
+
+  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
   The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
-  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$.
+  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
 \end{proof}
@@
     \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
-    \item We have $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
+    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
+      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
+      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\tilde P_{m,j},\tilde P_{m,j})=\CC.\] 
+    \item We have $\Hom(P_{m+1}^I,P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
+      In particular, $P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
+    %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
   \end{enumerate}
@@
   \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
-  where the final zero follows from Lemma~\ref{le:homdecomposition}(2).
+  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
   Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).
@@
   Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
-  Part (3) then follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1}.
-\end{proof}
-
-Note that by Lemma~\ref{le:properties}(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
-\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
-
-%Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
-In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
-These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-
-\begin{example}\label{smallm}[The cases $m=2,3,4$]
-\end{example}
-
-As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
-We use this fact and do not state the particular maps defining the lifts.
-In this example, we just state the support of the representation including those dimensions which are not one.
-We call it the quiver of the representations.
-
-The representation $\tilde P_2$ is defined by the following quiver:
-\begin{align*}
-  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
-\end{align*}
-The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink.
-In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.
-
-The representation $\tilde P_3$ is given by the quiver
-	\begin{align*}
-          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}
-        \end{align*}
-	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.
-Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.
-We assume that $(j_1,\ldots,j_l)=(1,\ldots,l)$ which is no restriction as the general case can be obtained by relabelling.
-The Auslander-Reiten translate $\tau\tilde P_{3}^{(1,\ldots,l)}$ is given by
-	\begin{align*}
-          \xymatrix@R10pt@C20pt{&&(2,\alpha_{l+1}^{-1})\ar_{\alpha_{l+1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{n}^{-1})\ar_{\alpha_{n}}[llu]}
-        \end{align*}
-In particular, the image of the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_{3}^{(1,\ldots,l)}$ has image $(2,\alpha_{i}^{-1})\xrightarrow{\alpha_{i}}(1,1)$ for $i=l+1,\ldots,n$.
-
-The representation $\tilde P_4$ is defined by
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{\alpha_1}[llllld]\ar^{\alpha_2}[ld]\ar^{\alpha_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_n\ar^{\alpha_n}[lu]&\mathcal A_1\ar^{\alpha_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{\alpha_3}&\hdots&\mathcal A_n\ar^{\alpha_n}[llu]	&\hdots&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
-where the middle vertex is $(2,1)$.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{\alpha_1}[llllld]\ar^{\alpha_{l-1}}[ld]\ar^{\alpha_l}[d]\ar^{\alpha_{l+1}}[rd]\ar^{\alpha_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{\alpha_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{\alpha_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{\alpha_n}[lllu]	&&&&}\]
-where the middle vertex is $(1,\alpha_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{\alpha_1}[llllld]\ar^{\alpha_{l}}[llld]\ar^{\alpha_{l+1}}[lld]\ar^{\alpha_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{\alpha_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{\alpha_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{\alpha_n}[lllu]&&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
-where the upper vertex is again $(2,1)$.
-Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
-Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $\alpha_{l+1},\ldots,\alpha_n$.
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-
-\begin{remark}
-Actually, these examples already show how the (truncated) preprojectives are built, also using the identities \eqref{eq:recursive covers}.
-We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j_l}\to\tau\tilde P_3^{\uj}$ is not surjective.
-Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
-\end{remark}
+  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
+  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
+  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
+  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
+  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
+  %The Auslender-Reiten formulas \cite[Theorem IV.2.13]{ass} then give part (4).
+
+  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
+  %Then the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
+  %\[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0\]
+  %and
+  %\[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1\]
+  %which proves part (6).
+\end{proof}
+
+Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
+Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
+For $l\ge1$, set
+\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
+Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
+In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
+\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
+
+Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
+For $m\ge3$, define the representation 
+\begin{lemma}
+  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
+  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\CC$.
+  Moreover, the kernel of the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
+  \[\tilde P_m(I,j):=
+    \begin{cases}
+      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,i} & \text{ if $m\geq 3$;}\\
+      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
+    \end{cases}\]
+\end{lemma}
+\begin{proof}
+  The first claim follows from Lemma~\ref{le:properties}.(3) by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}.
+  Indeed, this gives the isomorphism
+  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=\CC.\]
+
+  We establish the final claim directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
+\end{proof}
+%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
+%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
+
+%In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
+%That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
+%These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
 
@@
 This is because $U\notin\tilde P_{m-1,l}^\perp$}
-  Let $\uj\in I_l$.
-  All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.	
-\end{lemma}
-\begin{proof}
-  We begin by observing that the projected representation $G_{K(n)}(\tilde P_m^{\uj})$ is a truncated preprojective of $K(n)$.
-  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G_{K(n)}(\tilde P_m^{\uj})$ are direct sums of preprojective representations of $K(n)$.
-  But any subrepresentation of $\tilde P_m^{\uj}$ also projects to a subrepresentation of $G_{K(n)}(\tilde P_m^{\uj})$.
+  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations $U$ of $\tilde P_{m+1}^I$ are preprojective.	
+\end{lemma}
+\begin{proof}
+  By Lemma~\ref{le:homdecomposition}, the projected representation $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$.
+  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G(\tilde P_{m+1}^I)$ are direct sums of preprojective representations of $K(n)$.
+  But any subrepresentation of $\tilde P_{m+1}^I$ also projects to a subrepresentation of $G(\tilde P_{m+1}^I)$.
   Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
@@
 
-%Fix $\ui=(i_1,\ldots,i_k)$ and $\uj=(j_1,\ldots,j_l)$ with $i$
-
 \begin{comment} 
@@
 \end{comment}
-Define 
-$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$
+
+The following indicates how the preprojective lifts $\tilde P_m$ are built for $m=2,3,4$.
+\begin{example}\label{smallm}[The cases $m=2,3,4$]
+  By construction, the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$ and thus they are uniquely determined by their dimension vectors.
+  We use this fact and do not state the particular maps defining the lifts.
+  In this example, we just state the support of the representation including those dimensions which are not one.
+  We call it the \emph{support quiver} of the representations.
+
+  The representation $\tilde P_2$ is defined by the following quiver:
+  \[\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}\]
+  For $i\in\{1,\ldots,n\}$, the support of $\tilde P_2^{\{i\}}$ can be obtained from the quiver of $\tilde P_m$ by erasing the arrow $\alpha_i$ and the corresponding sink. 
+  We denote this support quiver of $\tilde P_2^{\{i\}}$ by $\mathcal A_i$.
+  In turn, for $I\subset\{1,\ldots,n\}$, the quiver of $\tilde P_2^I$ is obtained by erasing the arrows $\alpha_i$ and the corresponding sinks $(1,\alpha_i)$ for $i\in I$.
+
+  The representation $\tilde P_3$ is given by the quiver
+  \[\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}\]
+  where the vertex of dimension $n-1$ is the middle vertex $(1,1)$.
+  Moreover, for $I\subset\{1,\ldots,n\}$, the representation $\tilde P_3^I$ is obtained by erasing the subquivers $\mathcal A_i$ for $i\in I$ and decreasing the dimension of the space at vertex $(1,1)$ by $|I|$.
+
+  To continue, we assume for convenience that $I=\{1,\ldots,l\}$.
+  This is not actually a restriction of generality as the general case can be obtained by relabelling the arrows. 
+  The Auslander-Reiten translate $\tau\tilde P_3^I$ is given by
+  \[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_l^{-1})\ar_{\alpha_l}[llu]}\]
+  In particular, for $i\in I$ the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_3^I$ has image $(2,\alpha_i^{-1})\xrightarrow{\alpha_i}(1,1)$.
+
+The representation $\tilde P_4$ is defined by
+  \[\xymatrix@R10pt@C20pt{&&\mathcal B_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal B_n\ar_{\alpha_n}[llu]}\]
+  where the vertex of dimension $n-1$ is the middle vertex $(2,1)$ and $\cB_i$ is the quiver
+\[\xymatrix@R40pt@C10pt{&&&2n-3&&&\\
+\cA_1\ar^{\alpha_1}[rrru]&\hdots&\cA_{i-1}\ar_{\alpha_{i-1}}[ru]&\widehat{\cA_i}&\cA_{i+1}\ar_{\alpha_{i+1}}[lu]&\hdots&\cA_n\ar_{\alpha_n}[lllu]}\]
+
+\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{\alpha_1}[llllld]\ar^{\alpha_2}[ld]\ar^{\alpha_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
+\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_n\ar^{\alpha_n}[lu]&\mathcal A_1\ar^{\alpha_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{\alpha_3}&\hdots&\mathcal A_n\ar^{\alpha_n}[llu]	&\hdots&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
+where the middle vertex is $(2,1)$.
+Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
+The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
+Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
+\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{\alpha_1}[llllld]\ar^{\alpha_{l-1}}[ld]\ar^{\alpha_l}[d]\ar^{\alpha_{l+1}}[rd]\ar^{\alpha_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
+&&&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{\alpha_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{\alpha_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{\alpha_n}[lllu]	&&&&}\]
+where the middle vertex is $(1,\alpha_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
+
+\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{\alpha_1}[llllld]\ar^{\alpha_{l}}[llld]\ar^{\alpha_{l+1}}[lld]\ar^{\alpha_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
+&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{\alpha_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{\alpha_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{\alpha_n}[lllu]&&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
+where the upper vertex is again $(2,1)$.
+Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
+Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $\alpha_{l+1},\ldots,\alpha_n$.
+
+%\begin{tikzpicture}[scale=1]
+%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
+%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
+%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
+%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
+%\end{tikzpicture}
+\end{example}
+
+\begin{remark}
+  Actually, these examples already show how the (truncated) preprojectives are built, also using the identities \eqref{eq:recursive covers}.
+  We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is not surjective.
+  Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
+\end{remark}
 
@@
   \label{AR}
-  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.
-Do parts (2), (3), (4) have analogues for $K(n)$?
-The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.
-The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}\sayT{The sequence (6) should have an analogue on $K(n)$.
+  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Does part (2) have an analogue for $K(n)$?}
+  \sayT{The sequence \eqref{ses3} should have an analogue on $K(n)$.
 I would be happy with a direct proof of (1) and (2).
 I did not check the details so far.
-	(4) and the first half of (3) hold only on the universal cover. We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
-  Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
-  Consider the short exact sequence $$\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}.$$ The following holds:
+We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
+  For $m\geq 3$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
+  %Consider the short exact sequence $$\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}.$$ The following holds:
   \begin{enumerate}
-    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
+    \item We have $\tau\tilde P_{m+1}^I=\tilde P_{m-1}^I$.
     %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
@@
 We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
-    \item There exists a short exact sequences 
+    \item For each $j\in I$, there is a short exact sequence
       \begin{align}
         \label{ses3}
-        \ses{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}%{\pi^{\bf j_l}_{m-1}}
+        \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.
       \end{align}
-      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
-    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\CC$.
-
+      %where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
     %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
@@
 \begin{proof}
-Using the identities \ref{eq:recursive covers}, it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
-Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively.
+  Using the identities \eqref{eq:recursive covers}, it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
+  Without loss of generality, we choose $I=\{1,\ldots,l\}$.
   We should point out that it is very important for this proof that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
@@
 
-In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$. For $m=5$,  we consider the short exact sequence
-\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
+  In Example~\ref{smallm} it was shown that $\tau\tilde P_4^I=\tilde P_2^I$.
+  For $m=5$, we consider the short exact sequence
+  \[\ses{\bigoplus_{i\in I}\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^I}\]
   and apply the reflection functor $\tilde\Sigma_1\tilde\Sigma_2$ which is the same as applying $\tau^{-1}$.
-As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^{(1,\ldots,l)}=\tilde P_5^{(1,\ldots,l)}$ which is statement for $m=5$.
-The general statement follows from the identities \ref{eq:recursive covers}.
-Note that this also shows that
-\[(\tilde \Sigma_2\tilde P_{m}^{(1,\ldots,l)})^\sigma=\tau^{-1}\tilde P^{(1,\ldots,l)}_{m-1}.\]
-
-Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
-$$\ses{P(4,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
-Actually, the first summand of $P(4,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left.
+  As we have $\tau^{-1}(\tilde P_{2,i})=\tilde P_{4,i}$ and $\tau^{-1}(\tilde P_3)=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^I=\tilde P_5^I$ which is statement for $m=5$.
+  The general statement follows from the identities \eqref{eq:recursive covers}.
+  Note that this also shows for $m\ge2$ that
+  \[\tilde\Sigma_2(\tilde P_{m+1}^I)^\sigma=\tau^{-1}(\tilde P_m^I).\]
+
+  Considering the support quiver $\tilde P_{3,j}$ from Example~\ref{smallm}, it is clear that we obtain an exact sequence
+  \[\ses{\tilde P_3(I,j)}{P_{3,j}}{\tilde P_2^I}.\]
+  Actually, the first summand of $\tilde P_3(I,j)$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $|I|-1$ sources in the second row lying on the left.
   Together with the first statement and the identities \eqref{eq:recursive covers}, this shows the second statement.
-
-As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
-$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
-
-We have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ by Lemma \ref{le:basic homological properties}.
-As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\CC$ by a straightforward check, applying \ref{eq:recursive covers}, it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\CC$.
-This yields the third and forth identity.
-
-%As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$.
-Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement.
-This yields the remaining results at once.
-
-%It is also straightforward to check that $\bigoplus_{j\neq l}\tilde P_{2,(l,j)}\oplus \bigoplus_{j=1}^{l-1}\tilde P_{1,(l,l,j)}\in (\tilde P_{4}^{(1,\ldots,l)})^\perp$ and, moreover, that $\Hom(\tilde P_{4}^{(1,\ldots,l)},\tilde P_{3,l})=0$.
-This yields the third claim when considering the long exact sequence obtained when applying $\Hom(\tilde P_{4}^{(1,\ldots,l)},\underline{\quad})$ to the short exact sequence considered in the second statement.
-
-\end{proof}
-
-If $m=3$, we replace the short exact sequence (\ref{ses3}) by
+\end{proof}
+
+If $m=3$, we replace the short exact sequence \eqref{ses3} by
 \begin{align}
   \label{ses4}
-   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)\ar[r] & 0}.
+  \xymatrix{0\ar[r] &\tilde P_3(I,j)\ar[r] & \tilde P_{2,j}\ar[r] & \left((2,1)\xrightarrow{\alpha_j}(1,\alpha_j)\right)\ar[r] & 0}.
 \end{align}
- Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)$, see also Example \ref{smallm}.
-
-\begin{corollary}\label{cor:perpendicular}
-For $m\geq 3$ and $\uj\in I_l$, we have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
+Recall that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is just $\left((2,1)\xrightarrow{\alpha_j}(1,\alpha_j)\right)$, see also Example \ref{smallm}.
+
+\begin{corollary}
+  \label{cor:perpendicular}
+  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
+  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
 \end{corollary}
 \begin{proof}
-If $m\geq 4$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence (\ref{ses3}).
-Using the identities of Lemma \ref{AR}, the result follows.
-
-If $m=3$, we have $\Hom(\tilde P_{3}^{\uj},P(3,\uj))=0$ because $P(3,\uj)$ is a direct sum of simple projective representations. Moreover, it is straightforward that 
-$\Ext(\tilde P_{3}^{\uj},\tilde P_{1,(j_l,i)})=0$ for $i\neq j_l$.
-This is because $\tilde P_{1,(j_l,i)}$ is supported at a  vertex which is not a neighbour of the support of $\tilde P_{3}^{\uj}$, see also Example  \ref{smallm}.
-
-\end{proof}
+  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence \eqref{ses3}.
+  The result then follows immediately from the identities of Lemma~\ref{AR}.
+
+  If $m=2$, we have $\Hom(\tilde P_3^I,\tilde P_2(I,j))=0$ because $\tilde P_2(I,j)$ is a direct sum of simple projective representations.
+  Moreover, it is straightforward that $\Ext(\tilde P_3^I,\tilde P_{1,(j,i)})=0$ for $i\neq j$.
+  This is because $\tilde P_{1,(j,i)}$ is supported at a vertex which is not a neighbour of the support of $\tilde P_3^I$, see also Example~\ref{smallm}.
+\end{proof}
+
+\newpage
+\sayD{Notation changes still needed after this point.}
 

### 2018-01-25 Grassmannian_cells.tex
Section 5 (still not finished...)

--- 2018-01-23 Grassmannian_cells.tex
@@
 \begin{definition}\label{def:2equivalence}
-Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $p$ and $\Gamma(2)$ has precisely one sink $q$.
-Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:p\to q$.
-This defines a relation on the set of $2$-quivers denoted by $\tilde Q_V\to \tilde Q$.
+Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that one of the following conditions is satisfied:
+\begin{enumerate}
+\item $\Gamma(1)$ has precisely one source $p$; 
+\item $\Gamma(2)$ has precisely one sink $q$;
+\item $\Gamma(1)$ has precisely one source $p$ and $\Gamma(2)$ has precisely one sink $q$.
+\end{enumerate}
+Depending on the condition which is satisfied, we define
+\begin{enumerate}
+\item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a $2$-arrow $V_p:p\to\Gamma(2)$;
+\item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a $2$-arrow $V_q:\Gamma(1)\to q$;
+\item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:p\to q$. 
+\end{enumerate}
+
+This defines a relation on the set of $2$-quivers denoted by $\tilde Q\to \tilde Q_p$, $\tilde Q\to \tilde Q_q$ and $\tilde Q\to \tilde Q_V$ respectively.
 Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation.
 \end{definition}
+
+Note that in a finite connected quiver, which is a tree and which has precisely one source $p$, all arrows are pointing away from $p$ or equivalently there exists a path from $p$ to every vertex of the quiver.
+The analogous statement is satisfied if a quiver has precisely one sink.
+
 Observe that the set of vertices of two equivalent $2$-quivers coincide.
+
 \begin{lemma}\label{lem:2equivalence}
@@
 \begin{proof}
-We may assume that $\tilde Q'=\tilde Q_V$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$.
+We may assume that $\tilde Q'=\tilde Q_V$, $\tilde Q'=\tilde Q_p$ or $\tilde Q'=\tilde Q_q$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$ and one of the conditions of Definition \ref{def:2equivalence} is satisfied.
+We only consider the case $\tilde Q'=\tilde Q_V$, the other two cases follow by the same arguments.
 As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $p$, the unique sink of $\Gamma(2)$ by $q$ and the new arrow by $\alpha_V:p\to q$.
 
-Let $\beta\subset Q_0$ be a strong successor closed subset (of the $2$-quiver $Q$).
-Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a  $2$-arrow.
-Then it is also a $2$-arrow of $\tilde Q$.
-This means that  we have $\Gamma'(2)_0\cap \beta\neq\varnothing$ if $\Gamma'(1)_0\subset \beta$.
+Let $\beta\subset Q_0$ be a strong successor closed subset (of the $2$-quiver $\tilde Q$). We need to show that it defines a strong successor closed subset of $(\tilde Q_V)_0$.
+Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a  $2$-arrow. Then it is also a $2$-arrow of $\tilde Q$. This means that  we have $\Gamma'(2)_0\cap \beta\neq\varnothing$ if $\Gamma'(1)_0\subset \beta$.
 
 Let $\alpha:i\to j\in (Q_V)_1$.
-If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $Q_0$.
+If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $\tilde Q_0$.
 Thus assume that $\alpha=\alpha_V$.
-If $p\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that for every vertex $q'\in\Gamma(1)_0$ different from $p$, there exists an arrow $\alpha:p\to q'$.
+We need to show that $q\in\beta$ if $p\in\beta$.
+Thus assume that $p\in\beta$.
+Then we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that for every vertex $q'\in\Gamma(1)_0$, there exists a path from $p$ to $q'$.
+In particular, we have $q'\in\beta$ as $\beta\subset \tilde Q_0$ is successor closed.
 As $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
-But then we have $q\in\beta$ as there exists an arrow $\alpha:p'\to q$ if $p'\neq q$.
+But then we have $q\in\beta$ as, by the same argument, there exists a path from $p'$ to $q$ if $p'\neq q$.
 Thus $\beta$ is strong successor closed as a subset of $(Q_V)_0$.
@@
 %\end{remark}
-
-The next step is to associate a $2$-quiver with certain lifts of (truncated) preprojective representation $\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians.
-Recall that the cells of the quiver Grassmannians attached to $P_m^{\uj}:= F_{K(n)}\tilde P_m^{\uj}$ coincide with those attached to the lift $\tilde P_m^{\uj}$.
-
-For building these $2$-quivers, we use the recursive construction described in Section \ref{Lifting}.
+In the following, we frequently use the notation and conventions of Section \ref{Lifting}.
+The next step is to associate a $2$-quiver with certain lifts of (truncated) preprojective representation $\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians.
+Recall that the cells of the quiver Grassmannians attached to $P_m^{\uj}:= F_{K(n)}\tilde P_m^{\uj}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{\uj}$.
+Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
+In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.
+
+Thus it suffices to consider the lifted truncated preprojectives $\tilde P_m^{[k]}:=\tilde P_m^{(1,\ldots,k)}$ for $m\geq 2$ and $0\leq k\leq n-1$. We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
+
+For building the mentioned $2$-quivers, we use the recursive construction described in Section \ref{Lifting}.
 In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
-Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
-In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.
-
 %For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}:=\tilde P_2^{(1,\ldots,n-1)}$.
-Using the conventions of Section \ref{Lifting} the representation $\tilde P_2^{[n-1]}$ is defined by
+
+It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by
 \[
@@
 \]
-We now recursively consider the lifted truncated preprojectives $\tilde P_m^{[k]}:=\tilde P_m^{(1,\ldots,k)}$ for $m\geq 2$ and $0\leq k\leq n-1$. We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
+
 %In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
@@
 Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
-We define the $2$-quiver of $P_2^{[k]}$ by
+We define the $2$-quiver of $\tilde P_2^{[k]}$ by
 \\
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{[n-1]}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \tilde P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \tilde P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$\tilde P_2^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-The next step is to define the $2$-quivers of certain truncated preprojective lifts $\tilde P^{[k]}_3$ (resp.
-of $P^{[k]}_3$) whence the remaining $2$-quivers attached to the truncated preprojectives $P_m^{[k]}$ can be obtained recursively.
-
-Define $\tilde P_3^{[n-1]}:=\tilde P_3^{(1,\ldots,n-1)}=\alpha_n^{-1}\tilde P_2^{[1]}$. We have 
+For $m\geq 3$, we have
+
+$$ \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1})$$.
+
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+
+The next step is to define the $2$-quivers of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
+
+Observe that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, we have 
 $$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
@@
 
- This basis recursively gives rise to the following $2$-quiver of $\tilde P_3^{[k]}=\tilde P_3^{(1,\ldots,k)}$ (resp.
-for $P_3^{[k]}$) for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex $(1,1)$ of $\widetilde{K(n)}$.\\
+ This basis recursively gives rise to the following $2$-quiver of $P_3^{[k]}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
+Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+
+The representation $\tau\tilde P_3^{[k]}$ is given by 
+\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
+Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
+\\
 
@@
 
-\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{[1]}$} ;
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$\tilde P_3^{[1]}$} ;
 \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{[2]}$};
-
-\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{[n-3]}$} ;
+\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$\tilde P_3^{[2]}$};
+
+\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\tilde P_3^{[n-3]}$} ;
 \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{[n-2]}$};
+\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\tilde P_3^{[n-2]}$};
 \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{[n-1]}$}   ;
+\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\tilde P_3^{[n-1]}$}   ;
 \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
@@
 
-For odd $m$, we have
-
-$$ \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{-1}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_i^{-1}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1})$$.
-
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with a lift to the universal covering which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-The representation $\tau\tilde P_3^{[k]}$ is given by
-\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
-Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
-It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
-
-\begin{align}\label{eq:case2}
- \Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
-\end{align}
-
-Now we can recursively the $2$-quivers of $P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure.
+%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
+
+%\begin{align}\label{eq:case2}
+ %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
+%\end{align}
+
+Now we can recursively the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure.
 For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
@@
 As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[1]})$ and $\Ext(P_m^{[1]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
-Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{[k]}$.
-The $2$-quiver of $P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{[k]}$ to the one of $P_{m}$
+Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
+The $2$-quiver of $P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $ P_{m+1}^{[k]}$ to the one of $ P_{m}$
 \\
@@
 \begin{tikzpicture}
-\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$P^{]n-1]}_{m-2}$} ;
+\draw (0,4) node (A1) {$\tilde P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$\tilde P_{m}$} +(1.5,0) node (B1) {$\tilde P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$\tilde P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$\tilde P_{m-1}$}  +(6,0) node (E1) {$\tilde P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$\tilde P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$\tilde P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$\tilde P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$\tilde P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$\tilde P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$\tilde P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$\tilde P^{[n-1]}_{m-2}$} ;
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 
-\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{[n-1]}=P_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{[n-1]}$};
+\draw (0,0) node (B) {$\tilde P_{m}$}+(0,-.8) node (P1) {\footnotesize$\tilde P_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\tilde P_{m}$} +(5,-.7) node (P3) {\footnotesize$\tilde P_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$\tilde P_{m}$}  +(10,0) node (E) {$\tilde P_{m+1}^{[n-1]}=\tilde P_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\tilde P_{m+1}^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau P_{m+1}^{[k]}= P_{m-1}^{[k]}$ in $P_m$.
-This subquiver can be found at the very right of the $2$-quiver of $P_m$.
+\noindent where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$.
+This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$.
 Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view.
-For $n=3$ the $2$-quiver of $P_3$ is given by:\\
+As an example consider the case $n=3$ and $m=3$.
+The $2$-quiver of $\tilde P_3$ is given by:\\
 
@@
 
-The one of $P_4$ is given by:\\
+The one of $\tilde P_4$ is given by:\\
 
@@
 
-\end{tikzpicture}
-
-\begin{theorem}
-  The Euler characteristic $\chi(\Gr_e(P_m^{[k]}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{[k]}$.
+\end{tikzpicture}\\
+
+Write $\mathcal Q(m,k)$ for the $2$-quiver of $\tilde P_m^{[k]}$.
+Clearly, every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$.
+Note that two different vertices of $\mathcal Q(m,k)_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset\mathcal Q(m,k)_0$ are defined by
+$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$
+
+\begin{theorem}\begin{enumerate}
+\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
+	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
+\end{enumerate}
 \end{theorem}
 \begin{proof}
-  We proceed by induction.
-  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
+The results of Section \ref{QG} imply that the second statement follows from the first one.
+
+We proceed by induction on $m$ and $k$.
+The strong successor closed subsets of the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
   Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.

### 2018-01-27 Grassmannian_cells.tex
Section 3.2 edits, Corollary 3.43 is next

--- 2018-01-25 Grassmannian_cells.tex
@@
 In general, considering the linear map  
-\begin{align}\label{eq:homext}d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},\end{align}
+\begin{align}
+  \label{eq:homext}
+  d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),
+  \quad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},
+\end{align}
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
@@
 
-Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
+Fix a natural number $n\geq 3$.
+Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
 In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
@@
 \begin{itemize}
-  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
-  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
+  \item We consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,e)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
+  \item We consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,e)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
   \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
@@
       \label{eq:recursive covers}
-      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
+      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
     \end{align}
@@
 
-It will be rather important that our chosen lifts of $\tilde P_{2l}$ and $\tilde P_{2l-1}$, $l\ge1$, live on two different components of the universal covering quiver.
+It will be rather important that our chosen lifts of $P_{2l}$ for $l\ge1$ and our chosen lifts of $P_{2l-1}$ for $l\ge1$ live on two different components of the universal covering quiver.
 Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
@@
 \begin{lemma}
+  \label{le:shifted subreps}
   For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
@@
   Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
-  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
+  In particular, they all have the same central vertex $(1,e)$ if $m$ is odd and central vertex $(2,e)$ if $m$ is even.
 \end{remark}
 
-The next result establishes some basic homological properties of these translated preprojective representations.
+\begin{example}
+  \label{ex:lifted preprojectives}
+  Here we explicitly describe the preprojective lifts $\tilde P_m$ for $m=2,3,4$ as well as their shifted preprojective subrepresentations as in Lemma~\ref{le:shifted subreps}.
+  By Lemma~\ref{le:lifts of transjectives}, the lifts of all preprojectives are exceptional as representations of $\widetilde{K(n)}$ and thus they are uniquely determined by their dimension vectors.
+  We make use of this fact below, stating only the support of the representation (also specifying those dimensions which are not one) and do not state the particular maps present in the lifts.
+  We call this the \emph{support quiver} of the representation and let $W_n$ act on these quivers by translating all vertices.
+
+  The representation $\tilde P_2$ is defined by the following quiver:
+  \begin{equation}
+    \label{dia:P2 quiver}
+    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n)}
+  \end{equation}
+  Then $\tilde P_{1,i}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_i)$.
+  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink.
+
+  The representation $\tilde P_3$ is given by the quiver
+  \begin{equation}
+    \label{dia:P3 quiver}
+    \xymatrix@R40pt@C10pt{&n-1&\\ \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[ru]&\cdots&\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lu]}
+  \end{equation}
+  where the top vertex of dimension $n-1$ is $(1,e)$ and the arrow from $\alpha_i^{-1}.\cA_i$ emanates from its unique source~$(2,\alpha_i^{-1})$.
+  Then $\tilde P_{2,i}\subset\tilde P_3$ has one-dimensional spaces at each vertex of the quiver
+  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_i^{-1})\ar_{\alpha_i}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_i^{-1}\alpha_1)&\cdots&(1,\alpha_i^{-1}\alpha_{i-1})&&(1,\alpha_i^{-1}\alpha_{i+1})&\cdots&(1,\alpha_i^{-1}\alpha_n)}\]
+
+  The representation $\tilde P_4$ has support quiver
+  \begin{equation}
+    \label{dia:P4 quiver}
+    \xymatrix@R40pt@C10pt{&n-1\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1&\cdots&\alpha_n.\cB_n}
+  \end{equation}
+  where the top vertex of dimension $n-1$ is $(2,e)$ and $\cB_i$ is the following analogue of the support quiver for $\tilde P_3$:
+  \[\xymatrix@R40pt@C10pt{&&&2n-3&&&\\
+    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
+  with top vertex $(1,e)$ having dimension $2n-3$.
+  Now $\tilde P_{3,i}$ can be found as the representation corresponding to the subquiver
+  \[\xymatrix@R40pt@C10pt{
+    &&&1\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^{\alpha_i}[d]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\
+    1&\hdots&1&n-1&1&\hdots&1\\
+    \alpha_i\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_i\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&&\alpha_i\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_i\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
+  where the top vertex is $(2,e)$ and the central vertex is $(1,\alpha_i)$.
+\end{example}
+
+The next result establishes some basic homological properties of the translated preprojective representations.
 \begin{lemma}
@@
   Indeed, for $1\leq j\leq n$, we have 
-  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
+  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
   But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
@@
 \end{proof}
-In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
+
+In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
 \begin{lemma}
@@
     \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
-      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
-    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
+      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\] 
+    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
     \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
       Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
-      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\tilde P_{m,j},\tilde P_{m,j})=\CC.\] 
-    \item We have $\Hom(P_{m+1}^I,P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
-      In particular, $P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
+      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
+    \item We have $\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
+      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
     %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
@@
 
+\begin{example}
+  \label{ex:truncated lifts}
+  Fix $I\subsetneq\{1,\ldots,n\}$.
+  Building on Example~\ref{ex:lifted preprojectives}, we describe here the truncated preprojectives $\tilde P_m^I$ for $m=2,3,4$.
+  Following Lemma~\ref{le:properties}.(4), we can do this by simply specifying their dimension vectors as we did above.
+
+  The support quiver of $\tilde P_2^I$ is obtained from the quiver \eqref{dia:P2 quiver} of $\tilde P_2$ by removing the sinks $(1,\alpha_i)$ for $i\in I$.
+  The support quiver of $\tilde P_3^I$ is obtained from the quiver \eqref{dia:P3 quiver} of $\tilde P_3$ by removing the subquivers $\alpha_i^{-1}.\cA_i$ for $i\in I$ and decreasing the dimension of the space at vertex $(1,e)$ by $|I|$.
+
+  The support quiver of $\tilde P_4^I$ is given by the following analogue of the quiver \eqref{dia:P4 quiver} of $\tilde P_4$:
+  \[\xymatrix@R40pt@C10pt{&n-1-|I|\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1^I&\cdots&\alpha_n.\cB_n^I}\]
+  where the top vertex of dimension $n-1-|I|$ is again $(2,e)$ and $\cB_i^I$ is simply a space of dimension~$n-1-|I|$ if $i\in I$ and otherwise is the quiver
+  \[\xymatrix@R40pt@C10pt{&&&2n-3-|I|&&&\\
+    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
+\end{example}
+
+\begin{lemma}
+  \label{le:truncated tau}
+  For $m\ge3$ and $I\subsetneq\{1,\ldots,n\}$, we have $\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma=\tilde P_m^I$ and $\tau\tilde P_{m+1}^I=\tilde P_{m-1}^I$.
+\end{lemma}
+\begin{proof}
+  By Lemma~\ref{le:homdecomposition}, we get the short exact sequence \eqref{ses1} defining the truncated preprojective $\tilde P_{m-1}^I$:
+  \[\ses{\bigoplus_{i\in I} \tilde P_{m-2,i}}{\tilde P_{m-1}}{\tilde P_{m-1}^I}.\]
+  Applying the functor $\tilde\Sigma_2(-)^\sigma$ to this sequence and recalling the reflection recursion \eqref{eq:recursive covers}, we obtain a short exact sequence
+  \[\ses{\bigoplus_{i\in I} \tilde P_{m-1,i}}{\tilde P_m}{\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma}.\]
+  The equality $\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma=\tilde P_m^I$ immediately follows.
+  The equality $\tilde P_{m+1}^I=\tau^{-1}\tilde P_{m-1}^I$ is obtained in the same way using the functor $\tilde\Sigma_1\tilde\Sigma_2=\tau^{-1}$.
+\end{proof}
+
 Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
@@
 For $l\ge1$, set
-\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
+\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le l$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
 Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
@@
 
+\begin{lemma}
+  \label{le:special subrepresentations}
   Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
-For $m\ge3$, define the representation 
-\begin{lemma}
-  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
-  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\CC$.
-  Moreover, the kernel of the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
+  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
+  Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
   \[\tilde P_m(I,j):=
@@
 \begin{proof}
-  The first claim follows from Lemma~\ref{le:properties}.(3) by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}.
-  Indeed, this gives the isomorphism
-  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=\CC.\]
+  The first claim is immediate by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
+  Indeed, this gives
+  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]
 
@@
 \end{proof}
+
+\begin{remark}
+  We should point out that the case $m=3$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
+  Indeed, the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
+  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\] 
+  If we factor out the image of this morphism from $\tau\tilde P_3^I$, the remaining representation is a direct sum of the simple injective representations corresponding to the vertices $(2,\alpha_i^{-1})$ for $i\in I$, $i\ne j$.
+  Note that these disappear after reflecting at all sources.
+\end{remark}
+
 %Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
@@
   \label{le:subrep}
-  %\sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions.
-This is because $U\notin\tilde P_{m-1,l}^\perp$}
   For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations $U$ of $\tilde P_{m+1}^I$ are preprojective.	
@@
   Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
-  %Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.
-  %We proceed by induction.
-Clearly $\tilde P_m$ has only preprojective subrepresentations.
-We can assume without loss of generality that the subrepresentation $U$ is indecomposable.
-Assume that $U\subsetneq P_m^{(l)}$ is not preprojective.
-Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.
-Thus we get a commutative diagram
-  %\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
-  %  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
-  %where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
-  %because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not.
-We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.
-  %As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.7]{wei2}.
-Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$.
-Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l}}< 0$, we obtain
-  %\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
-  %But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
-\end{proof}
-
-\begin{comment} 
-DO NOT NEED THIS-------FROM HERE----
-\begin{lemma}\label{directsums}
-  \footnote{This can be proved on the quiver itself.}
-  If the quiver Grassmannians $\Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $\Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
-\end{lemma}
-\begin{proof}The claim follows by induction when considering the map $$\Psi:\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times \Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
-which is also sometimes called Caldero-Chapoton map.
-
-Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$.
-But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$.
-Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in \Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times \Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$.
-In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side.
-Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$.
-By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.
-
-In the same manner, we can proceed by inductively adding the summands $\tilde P_{m-1,i}$ in order to see that $\Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition.
-\end{proof}
-
-\begin{lemma}
-  \begin{enumerate}
-    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
-    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
-      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)}),\]
-      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-The first statement follows for instance by induction when applying BGP-reflections.
-\end{proof}
-----TO HERE----DO NOT NEED THIS----
-\end{comment}
-
-The following indicates how the preprojective lifts $\tilde P_m$ are built for $m=2,3,4$.
-\begin{example}\label{smallm}[The cases $m=2,3,4$]
-  By construction, the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$ and thus they are uniquely determined by their dimension vectors.
-  We use this fact and do not state the particular maps defining the lifts.
-  In this example, we just state the support of the representation including those dimensions which are not one.
-  We call it the \emph{support quiver} of the representations.
-
-  The representation $\tilde P_2$ is defined by the following quiver:
-  \[\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}\]
-  For $i\in\{1,\ldots,n\}$, the support of $\tilde P_2^{\{i\}}$ can be obtained from the quiver of $\tilde P_m$ by erasing the arrow $\alpha_i$ and the corresponding sink. 
-  We denote this support quiver of $\tilde P_2^{\{i\}}$ by $\mathcal A_i$.
-  In turn, for $I\subset\{1,\ldots,n\}$, the quiver of $\tilde P_2^I$ is obtained by erasing the arrows $\alpha_i$ and the corresponding sinks $(1,\alpha_i)$ for $i\in I$.
-
-  The representation $\tilde P_3$ is given by the quiver
-  \[\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}\]
-  where the vertex of dimension $n-1$ is the middle vertex $(1,1)$.
-  Moreover, for $I\subset\{1,\ldots,n\}$, the representation $\tilde P_3^I$ is obtained by erasing the subquivers $\mathcal A_i$ for $i\in I$ and decreasing the dimension of the space at vertex $(1,1)$ by $|I|$.
-
-  To continue, we assume for convenience that $I=\{1,\ldots,l\}$.
-  This is not actually a restriction of generality as the general case can be obtained by relabelling the arrows. 
-  The Auslander-Reiten translate $\tau\tilde P_3^I$ is given by
-  \[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_l^{-1})\ar_{\alpha_l}[llu]}\]
-  In particular, for $i\in I$ the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_3^I$ has image $(2,\alpha_i^{-1})\xrightarrow{\alpha_i}(1,1)$.
-
-The representation $\tilde P_4$ is defined by
-  \[\xymatrix@R10pt@C20pt{&&\mathcal B_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal B_n\ar_{\alpha_n}[llu]}\]
-  where the vertex of dimension $n-1$ is the middle vertex $(2,1)$ and $\cB_i$ is the quiver
-\[\xymatrix@R40pt@C10pt{&&&2n-3&&&\\
-\cA_1\ar^{\alpha_1}[rrru]&\hdots&\cA_{i-1}\ar_{\alpha_{i-1}}[ru]&\widehat{\cA_i}&\cA_{i+1}\ar_{\alpha_{i+1}}[lu]&\hdots&\cA_n\ar_{\alpha_n}[lllu]}\]
-
-\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{\alpha_1}[llllld]\ar^{\alpha_2}[ld]\ar^{\alpha_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
-\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_n\ar^{\alpha_n}[lu]&\mathcal A_1\ar^{\alpha_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{\alpha_3}&\hdots&\mathcal A_n\ar^{\alpha_n}[llu]	&\hdots&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
-where the middle vertex is $(2,1)$.
-Moreover, all dimensions on the subquivers $\mathcal A_i$ are one.
-The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$.
-Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
-\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{\alpha_1}[llllld]\ar^{\alpha_{l-1}}[ld]\ar^{\alpha_l}[d]\ar^{\alpha_{l+1}}[rd]\ar^{\alpha_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
-&&&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{\alpha_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{\alpha_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{\alpha_n}[lllu]	&&&&}\]
-where the middle vertex is $(1,\alpha_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by
-
-\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{\alpha_1}[llllld]\ar^{\alpha_{l}}[llld]\ar^{\alpha_{l+1}}[lld]\ar^{\alpha_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
-&\mathcal A_1\ar^{\alpha_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{\alpha_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{\alpha_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{\alpha_n}[lllu]&&\mathcal A_2\ar^{\alpha_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{\alpha_{n-1}}[lu]}\]
-where the upper vertex is again $(2,1)$.
-Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards.
-Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $\alpha_{l+1},\ldots,\alpha_n$.
-
-%\begin{tikzpicture}[scale=1]
-%\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
-%\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
-%\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
-%\end{tikzpicture}
-\end{example}
-
-\begin{remark}
-  Actually, these examples already show how the (truncated) preprojectives are built, also using the identities \eqref{eq:recursive covers}.
-  We should point out that the case $m=3$ is rather special because it is the only case for which the unique morphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is not surjective.
-  Note that if we factor out the image of this morphism, the remaining representation is a direct sum of simple injective representations which disappear after reflecting at the source.
-\end{remark}
-
-\begin{lemma}
-  \label{AR}
-  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Does part (2) have an analogue for $K(n)$?}
-  \sayT{The sequence \eqref{ses3} should have an analogue on $K(n)$.
-I would be happy with a direct proof of (1) and (2).
-I did not check the details so far.
-We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
-  For $m\geq 3$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
-  %Consider the short exact sequence $$\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}.$$ The following holds:
-  \begin{enumerate}
-    \item We have $\tau\tilde P_{m+1}^I=\tilde P_{m-1}^I$.
-    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$.
-What do we need?
-We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
-    \item For each $j\in I$, there is a short exact sequence
-      \begin{align}
-        \label{ses3}
-        \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.
-      \end{align}
-      %where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
-    %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
-  \end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
-\end{lemma}
-\begin{proof}
-  Using the identities \eqref{eq:recursive covers}, it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$.
-  Without loss of generality, we choose $I=\{1,\ldots,l\}$.
-  We should point out that it is very important for this proof that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section.
-  Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.
-
-  In Example~\ref{smallm} it was shown that $\tau\tilde P_4^I=\tilde P_2^I$.
-  For $m=5$, we consider the short exact sequence
-  \[\ses{\bigoplus_{i\in I}\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^I}\]
-  and apply the reflection functor $\tilde\Sigma_1\tilde\Sigma_2$ which is the same as applying $\tau^{-1}$.
-  As we have $\tau^{-1}(\tilde P_{2,i})=\tilde P_{4,i}$ and $\tau^{-1}(\tilde P_3)=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^I=\tilde P_5^I$ which is statement for $m=5$.
-  The general statement follows from the identities \eqref{eq:recursive covers}.
-  Note that this also shows for $m\ge2$ that
-  \[\tilde\Sigma_2(\tilde P_{m+1}^I)^\sigma=\tau^{-1}(\tilde P_m^I).\]
-
-  Considering the support quiver $\tilde P_{3,j}$ from Example~\ref{smallm}, it is clear that we obtain an exact sequence
-  \[\ses{\tilde P_3(I,j)}{P_{3,j}}{\tilde P_2^I}.\]
-  Actually, the first summand of $\tilde P_3(I,j)$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $|I|-1$ sources in the second row lying on the left.
-  Together with the first statement and the identities \eqref{eq:recursive covers}, this shows the second statement.
-\end{proof}
-
-If $m=3$, we replace the short exact sequence \eqref{ses3} by
-\begin{align}
-  \label{ses4}
-  \xymatrix{0\ar[r] &\tilde P_3(I,j)\ar[r] & \tilde P_{2,j}\ar[r] & \left((2,1)\xrightarrow{\alpha_j}(1,\alpha_j)\right)\ar[r] & 0}.
-\end{align}
-Recall that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is just $\left((2,1)\xrightarrow{\alpha_j}(1,\alpha_j)\right)$, see also Example \ref{smallm}.
+\end{proof}
 

### 2018-01-27 Grassmannian_cells.tex
Section 5
I need to clean up the notation and to say something concerning
compatibility in the main proof.

--- 2018-01-25 Grassmannian_cells.tex
@@
 In the following, we frequently use the notation and conventions of Section \ref{Lifting}.
-The next step is to associate a $2$-quiver with certain lifts of (truncated) preprojective representation $\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians.
-Recall that the cells of the quiver Grassmannians attached to $P_m^{\uj}:= F_{K(n)}\tilde P_m^{\uj}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{\uj}$.
-Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
-In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.
-
-Thus it suffices to consider the lifted truncated preprojectives $\tilde P_m^{[k]}:=\tilde P_m^{(1,\ldots,k)}$ for $m\geq 2$ and $0\leq k\leq n-1$. We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
+The next step is to associate a $2$-quiver $\mathcal Q(m,k)$ with the lifted truncated preprojective representations $\tilde P_m^{[k]}:=\tilde P_m^{\{1,\ldots,k\}}$ for $m\geq 2$, $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians.
+Recall that the cells of the quiver Grassmannians attached to $P_m^{[k]}:= F_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
+Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
+In particular, in view of Theorem \ref{thm:truncpp}, the $2$-quivers $\mathcal Q(m,k)$ can be seen as being attached to any (truncated) preprojective representation of this dimension.
 
@@
 
-$$ \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1})$$.
+\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
 
@@
 for $i=1,\ldots,n-1$.
-
- This basis recursively gives rise to the following $2$-quiver of $P_3^{[k]}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
 
@@
 In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
+
+ The chosen basis of $\Ext(P_3^{[n-1]},P_2)$ recursively gives rise to the following $2$-quiver of $P_3^{[k]}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
+Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
 \\
@@
 
-Now we can recursively the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure.
+Now we can recursively the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure and considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}).
+As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
+
 For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$. 
-As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[1]})$ and $\Ext(P_m^{[1]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
  Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
-The $2$-quiver of $P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $ P_{m+1}^{[k]}$ to the one of $ P_{m}$
+The $2$-quiver of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to the one of $\tilde P_{m}$ where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$.
+This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$.
 \\
@@
 
-\noindent where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$.
-This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$.
-Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view.
+\noindent In order to keep the diagrams as simple as possible we did not insert the labels of the vertices and arrows.
+As  every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q(m,k)$.
 As an example consider the case $n=3$ and $m=3$.
@@
 
-Write $\mathcal Q(m,k)$ for the $2$-quiver of $\tilde P_m^{[k]}$.
-Clearly, every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$.
  Note that two different vertices of $\mathcal Q(m,k)_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
@@
 The results of Section \ref{QG} imply that the second statement follows from the first one.
-
 We proceed by induction on $m$ and $k$.
-The strong successor closed subsets of the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
-  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
-  As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.
-
-  Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{[k]}$ (resp. $\tilde P_{m+1}^{[k]}$) and consider the short exact sequence
+The case of the representation $\tilde P_1$ is trivial.
+The strong successor closed subsets of the $2$-quivers  $\mathcal Q(2,k)$ of $\tilde P_2^{[k]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}).
+As $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, the  subrepresentations are in one-to-one correspondence with the successor closed subsets of (\ref{coeff}).
+Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $e\subset \mathcal Q(2,k)$ is successor closed.
+
+  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
   \[
@@
   \]
-  Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{[k]}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{[k]}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
-  Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\varnothing$.
-  But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{[k]}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{[k]}}$ by a $2$-arrow.
+  We have $\mathcal Q(m+1,k-1)_0=\mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$.
+	Let $\beta_1\coprod\beta_2\subset \mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
+ % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
+  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=\mathcal Q(m+1,k)_0$ and $\beta_1\cap\mathcal T(m-1,k)_0=\varnothing$ where $\mathcal T(m-1,k)$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q(m,0)$.
+  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q(m+1,k)$ is connected to $\mathcal T(m-1,k)$ by a $2$-arrow.\sayT{compatibility?
+Classify the cells which satisfy the condition that the quotient on the AR-translate is zero...}
 \end{proof}

### 2018-01-27 Grassmannian_cells.tex
Section 3.2 edits (also not finished)

--- 2018-01-27 Grassmannian_cells.tex
@@
   with top vertex $(1,e)$ having dimension $2n-3$.
-  Now $\tilde P_{3,i}$ can be found as the representation corresponding to the subquiver
+  Now $\tilde P_{3,i}$ can be found as the subrepresentation corresponding to the subquiver
   \[\xymatrix@R40pt@C10pt{
-    &&&1\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^{\alpha_i}[d]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\
-    1&\hdots&1&n-1&1&\hdots&1\\
+    &&&\cA_i\ar^{\alpha_i}[d]&&&\\
+    &&&n-1&&&\\
     \alpha_i\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_i\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&&\alpha_i\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_i\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
-  where the top vertex is $(2,e)$ and the central vertex is $(1,\alpha_i)$.
+  where the central vertex is $(1,\alpha_i)$.
+  Note that taking the subquiver $\cA_i$ together with the image of the map $\alpha_i$ gives a subrepresentation of $\tilde P_{3,i}$ isomorphic to $\tilde P_2$ while taking the subquiver $\alpha_i\alpha_j^{-1}.\cA_j$ together with the image of the map $\alpha_j$ gives a subrepresentation of $\tilde P_{3,i}$ isomorphic to $\tilde P_{2,\alpha_i\alpha_j^{-1}}$.
 \end{example}
@@
 
+It will be important to understand the possible subrepresentations of the truncated preprojective representations $\tilde P_{m+1}^I$.
+To describe these, we introduce notation for locating lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
+Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
+For $k\ge1$, set
+\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
+Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
+In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
+\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
+Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.
+
+To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
+Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
+Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
+\begin{lemma}
+  \label{le:subrep}
+  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations of $\tilde P_{m+1}^I$ are direct sums of shifted preprojective representations $\tilde P_{m+1-k,\ui}$ for $1\le k\le m$ and $\ui\in A_1^{(k)}$.
+\end{lemma}
+\begin{proof}
+  \sayD{The proof needs to be improved for the new stronger statement.}
+  By Lemma~\ref{le:homdecomposition}, the projected representation $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$.
+  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G(\tilde P_{m+1}^I)$ are direct sums of preprojective representations of $K(n)$.
+  But any subrepresentation of $\tilde P_{m+1}^I$ also projects to a subrepresentation of $G(\tilde P_{m+1}^I)$.
+  Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
+\end{proof}
+
 In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
@@
 
-Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
-Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
-For $l\ge1$, set
-\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le l$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
-Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
-In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
-More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
-\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
-
 \begin{lemma}
@@
 %These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-
-We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
-\begin{lemma}
-  \label{le:subrep}
-  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations $U$ of $\tilde P_{m+1}^I$ are preprojective.	
-\end{lemma}
-\begin{proof}
-  By Lemma~\ref{le:homdecomposition}, the projected representation $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$.
-  Then Lemma~\ref{le:projective subrepresentations} shows that all subrepresentations of $G(\tilde P_{m+1}^I)$ are direct sums of preprojective representations of $K(n)$.
-  But any subrepresentation of $\tilde P_{m+1}^I$ also projects to a subrepresentation of $G(\tilde P_{m+1}^I)$.
-  Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
-\end{proof}
 

### 2018-01-28 Grassmannian_cells.tex
Section 3.2 edits, finished up to Corollary 3.43, sequences of subsets will be next

@@
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
-To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
+To simplify the notation, we abbreviate $\tilde P_{2l-1,j}:=\tilde P_{2l-1,\alpha_j}$ and $\tilde P_{2l,j}:=\tilde P_{2l,\alpha_j^{-1}}$.
 \begin{lemma}
@@
   For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
-  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
+  These are the representations $\tilde P_{m,j}$ corresponding to the $n$ different arrows of $K(n)$. 
 \end{lemma}
@@
   \end{equation}
-  Then $\tilde P_{1,i}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_i)$.
+  Then $\tilde P_{1,j}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_j)$.
   Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink.
@@
   \end{equation}
-  where the top vertex of dimension $n-1$ is $(1,e)$ and the arrow from $\alpha_i^{-1}.\cA_i$ emanates from its unique source~$(2,\alpha_i^{-1})$.
-  Then $\tilde P_{2,i}\subset\tilde P_3$ has one-dimensional spaces at each vertex of the quiver
-  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_i^{-1})\ar_{\alpha_i}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_i^{-1}\alpha_1)&\cdots&(1,\alpha_i^{-1}\alpha_{i-1})&&(1,\alpha_i^{-1}\alpha_{i+1})&\cdots&(1,\alpha_i^{-1}\alpha_n)}\]
+  where the top vertex of dimension $n-1$ is $(1,e)$ and the arrow from each $\alpha_j^{-1}.\cA_j$ emanates from its unique source~$(2,\alpha_j^{-1})$.
+  Then $\tilde P_{2,j}\subset\tilde P_3$ has one-dimensional spaces at each vertex of the quiver
+  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_j^{-1})\ar_{\alpha_j}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{j-1}}[ld]\ar^(.65){\alpha_{j+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_j^{-1}\alpha_1)&\cdots&(1,\alpha_j^{-1}\alpha_{j-1})&&(1,\alpha_j^{-1}\alpha_{j+1})&\cdots&(1,\alpha_j^{-1}\alpha_n)}\]
 
@@
   with top vertex $(1,e)$ having dimension $2n-3$.
-  Now $\tilde P_{3,i}$ can be found as the subrepresentation corresponding to the subquiver
+  Now $\tilde P_{3,j}$ can be found as the subrepresentation corresponding to the subquiver
   \[\xymatrix@R40pt@C10pt{
-    &&&\cA_i\ar^{\alpha_i}[d]&&&\\
+    &&&\cA_j\ar^{\alpha_j}[d]&&&\\
     &&&n-1&&&\\
-    \alpha_i\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_i\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&&\alpha_i\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_i\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
-  where the central vertex is $(1,\alpha_i)$.
-  Note that taking the subquiver $\cA_i$ together with the image of the map $\alpha_i$ gives a subrepresentation of $\tilde P_{3,i}$ isomorphic to $\tilde P_2$ while taking the subquiver $\alpha_i\alpha_j^{-1}.\cA_j$ together with the image of the map $\alpha_j$ gives a subrepresentation of $\tilde P_{3,i}$ isomorphic to $\tilde P_{2,\alpha_i\alpha_j^{-1}}$.
+    \alpha_j\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_j\alpha_{j-1}^{-1}.\cA_{j-1}\ar^(.35){\alpha_{j-1}}[ru]&&\alpha_j\alpha_{j+1}^{-1}.\cA_{j+1}\ar_(.35){\alpha_{j+1}}[lu]&\cdots&\alpha_j\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
+  where the central vertex is $(1,\alpha_j)$.
+  Note that taking the subquiver $\cA_j$ together with the image of the map $\alpha_j$ gives a subrepresentation of $\tilde P_{3,j}$ isomorphic to $\tilde P_2$ while taking the subquiver $\alpha_j\alpha_i^{-1}.\cA_i$ together with the image of the map $\alpha_i$ gives a subrepresentation of $\tilde P_{3,j}$ isomorphic to $\tilde P_{2,\alpha_j\alpha_i^{-1}}$.
 \end{example}
@@
       In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
-    %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
   \end{enumerate}
@@
   Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
-  %The Auslender-Reiten formulas \cite[Theorem IV.2.13]{ass} then give part (4).
 
   Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
-  %Then the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
-  %\[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0\]
-  %and
-  %\[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1\]
-  %which proves part (6).
 \end{proof}
@@
 
+For the notation of the following result, we refer the reader to the discussion before Lemma~\ref{le:subrep}.
 \begin{lemma}
@@
   Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
-  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
+  \begin{enumerate}
+    \item For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
       Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
@@
         \begin{cases}
-      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,i} & \text{ if $m\geq 3$;}\\
+          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
           \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
         \end{cases}\]
-\end{lemma}
-\begin{proof}
-  The first claim is immediate by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
+    \item For $m\ge3$, any nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is surjective.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
   Indeed, this gives
   \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]
-
-  We establish the final claim directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
+  We establish the final claim of part (1) directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
+  Using the description in Example~\ref{ex:truncated lifts}, it is not hard to see that $\tau\tilde P_3^I$ is indecomposable with one-dimensional spaces at only the vertices $(1,e)$ and $(2,\alpha_i^{-1})$ for $i\in I$.
+  But then for~$j\in I$, the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
+  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\]
+  From the support quiver of $\tilde P_{2,j}$ given in Example~\ref{ex:lifted preprojectives}, we see that the kernel of this map is precisely $\tilde P_2(I,j)$.
+
+  For the $m=3$ case, we note that $\tau\tilde P_4^I=\tilde P_2^I$ by Lemma~\ref{le:truncated tau}.
+  Then the claimed structure $\tilde P_3(I,j)$ of the kernel and the surjectivity of the map $\tilde P_{3,j}\to\tau\tilde P_4^I$ are immediate from the explicit descriptions of $\tilde P_{3,j}$ and $\tilde P_2^I$ in Example~\ref{ex:lifted preprojectives} and Example~\ref{ex:truncated lifts} respectively.
+  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers}.
 \end{proof}
@@
 \begin{remark}
-  We should point out that the case $m=3$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
-  Indeed, the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
+  We should point out that the case $m=2$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
+  Indeed, recall from the proof of Lemma~\ref{le:special subrepresentations} that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
   \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\] 
@@
 
-%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
-%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
-
-%In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-%That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
-%These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-
+The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
 \begin{corollary}
@@
 \begin{proof}
-  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence \eqref{ses3}.
-  The result then follows immediately from the identities of Lemma~\ref{AR}.
-
-  If $m=2$, we have $\Hom(\tilde P_3^I,\tilde P_2(I,j))=0$ because $\tilde P_2(I,j)$ is a direct sum of simple projective representations.
-  Moreover, it is straightforward that $\Ext(\tilde P_3^I,\tilde P_{1,(j,i)})=0$ for $i\neq j$.
-  This is because $\tilde P_{1,(j,i)}$ is supported at a vertex which is not a neighbour of the support of $\tilde P_3^I$, see also Example~\ref{smallm}.
-\end{proof}
+  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
+  \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
+  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$.
+  From Lemma~\ref{le:properties}.(3) again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
+  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.(4), we get
+  \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
+  It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
+  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.(4) again imply 
+  \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
+  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
+
+  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of simple projective representations.
+  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,i)}$ for $i\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$ and this implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,i)}\big)=0$ for $i\neq j$.
+\end{proof}
+
+%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
+%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
+
+%In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
+%That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
+%These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
 

### 2018-01-29 Grassmannian_cells.tex
Still working...

@@
 \newcommand{\bfi}{\mathbf{i}}
+\newcommand{\bfI}{\mathbf{I}}
 \newcommand{\bfh}{\mathbf{h}}
@@
   \begin{enumerate}
-    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
+    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
       \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\] 
-    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
+    \item For any $I'\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\ne0$ if and only if $I'\subset I$, in which case
+      \[\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)=0.\]
     \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
@@
   where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
-  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).
-
-  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
-  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
-  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
-  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
+  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.(3).
+  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).
+
+  The first claim of part (2) is an immediate consequence of Lemma~\ref{le:unique morphisms}.(1) together with Theorem~\ref{covering}.
+  For the second claim of part (2), we apply $\Hom(-,\tilde P_{m+1}^I)$ to the sequence \eqref{ses1} for $I'$.
+
+  Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering}
+
+  The first part of (4) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
+  For the second part of (4), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
+  Then taking into account Lemma~\ref{le:homdecomposition} part (4), we get the isomorphism
   \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
-  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
-
-  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
+  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (4).
+
+  Part (5) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
 \end{proof}
@@
 
-%In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-%That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
-%These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-
 \newpage
@@
 
-\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$.
+\begin{definition}
+  Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$.
 Define $j_1^c$ as before.
@@
 \end{lemma}
-\begin{proof}
-
-To prove the first part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
+
+\begin{definition}
+  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
+  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge1$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
+  \begin{enumerate}
+    \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
+    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_l:=(I'_{l-1})^c\cup I_l$ for $1\le l\le k$ satisfy $(I'_{l-1})^c\cap I_l=\varnothing$ for $1\le l\le k$.
+      In particular, we have $|I'_l|=n-1$ for $0\le l\le k-1$.
+  \end{enumerate}
+  Any sequence consisting of a single nonempty subset $\bfI=(I_1)$ will also be considered admissible.
+  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_1)=(I_1^c)$.
+\end{definition}
+
+In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
+That is, taking $\varepsilon=(-1)^{m+1}$ we have an exact sequence
+\[\ses{\bigoplus_{i\in I} \tilde P_{m,w\alpha_i^\varepsilon}}{\tilde P_{m+1,w}}{\tilde P_{m+1,w}^I}.\]
+These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
+We adopt similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
+\begin{lemma}
+  \label{le:truncated quotients}
+  For $m\ge3$, the following hold:
+  \begin{enumerate}
+    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
+      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
+    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}$ for $0\le l\le k-1$.
+      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a sequence of surjections
+      \[\tilde P_{m+1}\onto\tilde P_{m+1}^{I'_0}\onto\tilde P_{m,i_0}^{I'_1}\onto\tilde P_{m-1,(i_0,i_1)}^{I'_2}\onto\cdots\onto P_{m+1-k,\ui}^{I'_k}.\]
+      the truncated preprojective representation
+      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_{k+1}}\]
+      is a quotient of $\tilde P_{m+1}$ with $\Hom(\tilde P_{m+1},\tilde P_{m+1-k}^\bfI)\cong\CC$.
+      These quotients  
+  \item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
+    \[\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}\]
+    is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$.
+    Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
+    \[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
+    for $k=1,\ldots,r$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+
+For part (1), we consider the following commutative diagram, where the square on the left hand side is the corresponding Auslander-Reiten sequence:
+\[\xymatrix{0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0 \\
+  0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[u] & \tilde P_{m,j}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
 
@@
 
-\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
+\begin{align}
+  \label{eq:homext} 
+  \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
+\end{align}
 

### 2018-01-30 Grassmannian_cells.tex
section 5 close to being finished...

--- 2018-01-28 Grassmannian_cells.tex
@@
 \begin{align}
-  \label{eq:homext}
+  \label{eq:maphomext}
   d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),
@@
 \item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a $2$-arrow $V_q:\Gamma(1)\to q$;
-\item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:p\to q$. 
+\item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by an usual arrow $\alpha_V:p\to q$. 
 \end{enumerate}
@@
 \end{definition}
-
-Note that in a finite connected quiver, which is a tree and which has precisely one source $p$, all arrows are pointing away from $p$ or equivalently there exists a path from $p$ to every vertex of the quiver.
-The analogous statement is satisfied if a quiver has precisely one sink.
-
 Observe that the set of vertices of two equivalent $2$-quivers coincide.
@@
 \begin{lemma}\label{lem:2equivalence}
-Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
-The number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
-\end{lemma}
-\begin{proof}
-We may assume that $\tilde Q'=\tilde Q_V$, $\tilde Q'=\tilde Q_p$ or $\tilde Q'=\tilde Q_q$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$ and one of the conditions of Definition \ref{def:2equivalence} is satisfied.
-We only consider the case $\tilde Q'=\tilde Q_V$, the other two cases follow by the same arguments.
-As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $p$, the unique sink of $\Gamma(2)$ by $q$ and the new arrow by $\alpha_V:p\to q$.
-
-Let $\beta\subset Q_0$ be a strong successor closed subset (of the $2$-quiver $\tilde Q$). We need to show that it defines a strong successor closed subset of $(\tilde Q_V)_0$.
+Let $\tilde Q=(Q,Q_2)$ and $\tilde Q'=(Q',Q_2')$ be two equivalent $2$-quivers.
+If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
+In particular, the number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
+\end{lemma}
+\begin{proof}
+For the proof of this Lemma the following straightforward observation is essential: in a finite connected quiver, which is a tree and which has precisely one source $p$, all arrows are pointing away from $p$ or equivalently there exists a path from $p$ to every vertex of the quiver.
+The analogous statement holds if a quiver has precisely one sink.
+
+We may assume that $\tilde Q'\in\{\tilde Q_p,\tilde Q_q,\tilde Q_V\}$ and one of the conditions of Definition \ref{def:2equivalence} is satisfied.
+We again denote the unique source of $\Gamma(1)$ by $p$, the unique sink of $\Gamma(2)$ by $q$ and the new arrow by $\alpha_V:p\to q$.
+We only consider the case $\tilde Q'=\tilde Q_V=(Q_V,(Q_V)_2)$, the other two cases follow by the same arguments.
+
+Let $\beta\subset Q_0$ be a strong successor closed subset. We need to show that it defines a strong successor closed subset of $(Q_V)_0$.
 Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a  $2$-arrow. Then it is also a $2$-arrow of $\tilde Q$. This means that  we have $\Gamma'(2)_0\cap \beta\neq\varnothing$ if $\Gamma'(1)_0\subset \beta$.
@@
 Let $\alpha:i\to j\in (Q_V)_1$.
-If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $\tilde Q_0$.
+If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $ Q_0$.
 Thus assume that $\alpha=\alpha_V$.
 We need to show that $q\in\beta$ if $p\in\beta$.
-Thus assume that $p\in\beta$.
-Then we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that for every vertex $q'\in\Gamma(1)_0$, there exists a path from $p$ to $q'$.
-In particular, we have $q'\in\beta$ as $\beta\subset \tilde Q_0$ is successor closed.
-As $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
+If $p\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that, for every vertex $q'\in\Gamma(1)_0$, there exists a path from $p$ to $q'$.
+In particular, we have $q'\in\beta$ for all $q'\in\Gamma(1)_0$ because $\beta\subset Q_0$ is successor closed.
+It follows that, as $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
 But then we have $q\in\beta$ as, by the same argument, there exists a path from $p'$ to $q$ if $p'\neq q$.
@@
 In the following, we frequently use the notation and conventions of Section \ref{Lifting}.
-The next step is to associate a $2$-quiver $\mathcal Q(m,k)$ with the lifted truncated preprojective representations $\tilde P_m^{[k]}:=\tilde P_m^{\{1,\ldots,k\}}$ for $m\geq 2$, $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians.
+The next step is to associate a $2$-quiver $\mathcal Q_m^{[k]}$ with the lifted truncated preprojective representations $\tilde P_m^{[k]}:=\tilde P_m^{\{1,\ldots,k\}}$ for $m\geq 2$ and $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_m^{[k]}$.
 Recall that the cells of the quiver Grassmannians attached to $P_m^{[k]}:= F_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
-Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.
-In particular, in view of Theorem \ref{thm:truncpp}, the $2$-quivers $\mathcal Q(m,k)$ can be seen as being attached to any (truncated) preprojective representation of this dimension.
+Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of arbitrary truncated preprojective representations $P_m^V$ only depend on $\tbfe$ and $\udim P_m^V$.
+In short, in view of Theorem \ref{thm:truncpp}, the $2$-quivers $\mathcal Q_m^{[k]}$ can be seen as being attached to any (truncated) preprojective representation of the respective dimension.
 
@@
 %For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-
-It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by
+\begin{remark}It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$.
+  For general $m$, every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
+If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
+In these cases, we label the $2$-arrows by the corresponding arrow.
+
+\end{remark}
+
+It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$.
+Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
 \[
@@
 %\]
-Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:homext}), we have 
+Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:maphomext}), we have 
 \begin{align}\label{eq:case2}
@@
 
-This yields recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
+We can recursively build the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ defined by the support quivers
 \begin{align}
@@
 Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
-We define the $2$-quiver of $\tilde P_2^{[k]}$ by
+We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
 \\
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \tilde P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \tilde P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$\tilde P_2^{[n-1]}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 \noindent
-where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver (\ref{coeff}) instead.
-
+where the $2$-arrows are coloured red.
+This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}).
+In abuse of notation, we also denote it by $\mathcal Q_{2}^{[k]}$.
+In order to keep the illustrations and combinatorics simple, we will work with the quiver (\ref{coeff}) instead.
 For $m\geq 3$, we have
 
-\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
+\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
 
@@
 
-Observe that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, we have 
+Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
 $$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
@@
 \[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
-Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
-
- The chosen basis of $\Ext(P_3^{[n-1]},P_2)$ recursively gives rise to the following $2$-quiver of $P_3^{[k]}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+Note that the image of the homomorphism corresponding to the basis element spanning $\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2)$ corresponds to the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
+In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivates the following definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$ which can be found as subquivers.
 \\
@@
 
-\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$\tilde P_3^{[1]}$} ;
+\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$\mathcal Q_3^{[1]}$} ;
 \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$\tilde P_3^{[2]}$};
-
-\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\tilde P_3^{[n-3]}$} ;
+\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$\mathcal Q_3^{[2]}$};
+
+\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\mathcal Q_3^{[n-3]}$} ;
 \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\tilde P_3^{[n-2]}$};
+\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\mathcal Q_3^{[n-2]}$};
 \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\tilde P_3^{[n-1]}$}   ;
+\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\mathcal Q_3^{[n-1]}$}   ;
 \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
@@
 %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
-\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
 \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
-\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {};
 \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
-\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {};
 \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
@@
 \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {\scriptsize$\alpha_{n}$};
-\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
-\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {};
+\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {};
+\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
 
@@
 
+\noindent In abuse of notation, we dropped the labels of the vertices in the illustration.
+Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
 %It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
@@
 %\end{align}
-
-Now we can recursively the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure and considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}).
-As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
-
-For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
+Now we can recursively build the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure and considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}).
+%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
+
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$. 
- Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
-The $2$-quiver of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to the one of $\tilde P_{m}$ where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$.
-This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$.
+ \sayT{improve this paragraph, introduce translated versions of $\mathcal Q_m^{[k]}$?} Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
+For $m\geq 4$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
+Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_m$ by a $2$-arrow.
+Thereby,  $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to the one of Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_{m,k}$.
+This subquiver can be found at the very right of the $2$-quiver $\mathcal Q_m$.
+This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
 \\
@@
 \begin{tikzpicture}
-\draw (0,4) node (A1) {$\tilde P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$\tilde P_{m}$} +(1.5,0) node (B1) {$\tilde P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$\tilde P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$\tilde P_{m-1}$}  +(6,0) node (E1) {$\tilde P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$\tilde P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$\tilde P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$\tilde P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$\tilde P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$\tilde P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$\tilde P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$\tilde P^{[n-1]}_{m-2}$} ;
+\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.5,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.5,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3,0) node (B11) {\footnotesize$\dots$} +(4.5,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.5,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(7.5,0) node (A1b) {\footnotesize$\dots$} +(9,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(10.5,0) node (B11b) {\footnotesize$\dots$} +(12,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 
-\draw (0,0) node (B) {$\tilde P_{m}$}+(0,-.8) node (P1) {\footnotesize$\tilde P_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\tilde P_{m}$} +(5,-.7) node (P3) {\footnotesize$\tilde P_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$\tilde P_{m}$}  +(10,0) node (E) {$\tilde P_{m+1}^{[n-1]}=\tilde P_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\tilde P_{m+1}^{[n-1]}$};
+\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-1}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}=\mathcal Q_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-\noindent In order to keep the diagrams as simple as possible we did not insert the labels of the vertices and arrows.
-As  every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q(m,k)$.
-As an example consider the case $n=3$ and $m=3$.
-The $2$-quiver of $\tilde P_3$ is given by:\\
+\noindent 
+%In order to keep the diagrams as simple as possible we did not insert the labels of the vertices.
+As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$.
+ Note that two different vertices of $(\mathcal Q_m^{[k]})_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
+$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$
+
+\begin{theorem}\begin{enumerate}
+\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.\sayT{use notation of Section 3.1, use translated versions of $2$-quivers}
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+The results of Section \ref{QG} imply that the second statement follows from the first one.
+We proceed by induction on $m$ and $k$.
+The case of the representation $\tilde P_1$ is trivial.
+We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
+Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $e\subset \mathcal Q_2^{[k]}$ is successor closed.
+
+  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
+  \[
+    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
+  \]
+  We have $(\mathcal Q_{m+1}^{[k-1]})_0=(\mathcal Q_{m+1}^{[k]})_0\coprod{}(\mathcal Q_m)_0$.
+	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[k-1]})_0\coprod{}(\mathcal Q_m)_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
+ % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
+  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k-1]})_0$ and $\beta_1\cap(cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $(\mathcal Q_{m-1}^{[k]}$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q_m$.
+  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.
+\end{proof}
+
+As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\\
 
@@
 \draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2)--(J11) node[pos=.5,above] {´};
 \end{tikzpicture}
@@
 \draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2)--(J11) node[pos=.5,above] {};
 
@@
 \draw[->,red] (Q1b)--(J22b) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2b)--(J11b) node[pos=.5,above] {\scriptsize $c$};
+\draw[->,red] (Q2b)--(J11b) node[pos=.5,above] {};
 
@@
 \draw[->,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {\scriptsize $c$};
+\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {};
+\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {};
 
 \end{tikzpicture}\\
-
- Note that two different vertices of $\mathcal Q(m,k)_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset\mathcal Q(m,k)_0$ are defined by
-$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$
-
-\begin{theorem}\begin{enumerate}
-\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
-	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
-\end{enumerate}
-\end{theorem}
-\begin{proof}
-The results of Section \ref{QG} imply that the second statement follows from the first one.
-We proceed by induction on $m$ and $k$.
-The case of the representation $\tilde P_1$ is trivial.
-The strong successor closed subsets of the $2$-quivers  $\mathcal Q(2,k)$ of $\tilde P_2^{[k]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}).
-As $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, the  subrepresentations are in one-to-one correspondence with the successor closed subsets of (\ref{coeff}).
-Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $e\subset \mathcal Q(2,k)$ is successor closed.
-
-  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
-  \[
-    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
-  \]
-  We have $\mathcal Q(m+1,k-1)_0=\mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$.
-	Let $\beta_1\coprod\beta_2\subset \mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
- % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=\mathcal Q(m+1,k)_0$ and $\beta_1\cap\mathcal T(m-1,k)_0=\varnothing$ where $\mathcal T(m-1,k)$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q(m,0)$.
-  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q(m+1,k)$ is connected to $\mathcal T(m-1,k)$ by a $2$-arrow.\sayT{compatibility?
-Classify the cells which satisfy the condition that the quotient on the AR-translate is zero...}
-\end{proof}
 

### 2018-01-31 Grassmannian_cells.tex
again section 5

@@
 \newcommand{\rk}{\mathrm{rk}}
+\newcommand{\cQ}{\mathcal{Q}}
 \newcommand{\Ext}{\operatorname{Ext}}
@@
 \begin{remark}It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$.
-  For general $m$, every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
-If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
-In these cases, we label the $2$-arrows by the corresponding arrow.
-
+Also every usual arrow of $\mathcal Q_m^{[k]}$ does.
+In particular, the quiver obtained from $\mathcal Q_m^{[k]}$ when forgetting the $2$-arrows gives rise to a (non-disjoint) union of subquivers of $\widetilde{K(n)}$.
+
+For general $m$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
+If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and precisely one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
+In these cases, we label the $2$-arrow by the corresponding arrow.
+
+Recall that, for $m\geq 3$, we have
+\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
+These isomorphisms are also present in the structure of the $2$-quivers we define.
 \end{remark}
 
-It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$.
+%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
+The $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is given by the vertex $(1,e)$.
+Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
 Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
 \[
-  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
 \]
@@
 \begin{align}
-  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
+  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,e)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
 \end{align}
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,e)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 where the $2$-arrows are coloured red.
-This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}).
-In abuse of notation, we also denote it by $\mathcal Q_{2}^{[k]}$.
-In order to keep the illustrations and combinatorics simple, we will work with the quiver (\ref{coeff}) instead.
-For $m\geq 3$, we have
-
-\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
-
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-
-The next step is to define the $2$-quivers of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
-
-Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
-$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
-This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
-for $i=1,\ldots,n-1$.
-
-The representation $\tau\tilde P_3^{[k]}$ is given by 
-\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
-Note that the image of the homomorphism corresponding to the basis element spanning $\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2)$ corresponds to the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
-In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivates the following definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$ which can be found as subquivers.
-\\
+Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
+The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the quiver (\ref{coeff}).
+In abuse of notation, we also denote the quiver (\ref{coeff}) by $\mathcal Q_{2}^{[k]}$.
+In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
+We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices by $\alpha_i^{-1}$.
+
+The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
+First, we define
+$$\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},$$
+i.e.
+we translate all vertices by $\alpha_n^{-1}$.
+Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
 
@@
 Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$.
+
+\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
+$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
+This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
+for $i=1,\ldots,n-1$.
+
+The representation $\tau\tilde P_3^{[k]}$ is given by 
+\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
+Note that the image of the homomorphism corresponding to the basis element spanning $\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2)$ corresponds to the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
+In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
+\end{remark}
 %It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
-
 %\begin{align}\label{eq:case2}
@@
 %\end{align}
-Now we can recursively build the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure and considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}).
+Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$ when repeating the procedure. 
+%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
 %As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
@@
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
- \sayT{improve this paragraph, introduce translated versions of $\mathcal Q_m^{[k]}$?} Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
+
+Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k+1$.
+As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
+
 For $m\geq 4$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
-Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_m$ by a $2$-arrow.
-Thereby,  $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to the one of Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_{m,k}$.
-This subquiver can be found at the very right of the $2$-quiver $\mathcal Q_m$.
+This can also be seen on the level of $2$-quivers, i.e.
+we find $\cQ_{m-1}^{[k]}$ as a subquiver of $\cQ_{m,k}$.
+More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.
+
+Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow.
+Thereby, the $2$-arrow connects $\mathcal Q_{m+1}^{[k]}$ to the subquiver $\cQ_{m-1}^{[k]}$ in $\cQ_{m,k}$.
 This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
@@
 \begin{tikzpicture}
-\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.5,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.5,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3,0) node (B11) {\footnotesize$\dots$} +(4.5,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.5,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(7.5,0) node (A1b) {\footnotesize$\dots$} +(9,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(10.5,0) node (B11b) {\footnotesize$\dots$} +(12,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
+\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 
-\node (PMK) [draw=black, thick,fit={(Q2b) (B)}]{};
+\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
 \draw[->,red,thick] (PMK)--(Q31);
@@
 As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$.
- Note that two different vertices of $(\mathcal Q_m^{[k]})_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
+ Note that two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
 Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
-$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$
+$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta)$$
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta$.
 
@@
 \item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
-	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.\sayT{use notation of Section 3.1, use translated versions of $2$-quivers}
+	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
 \end{enumerate}
@@
 We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
-Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $e\subset \mathcal Q_2^{[k]}$ is successor closed.
+Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.
 
@@
   \]
-  We have $(\mathcal Q_{m+1}^{[k-1]})_0=(\mathcal Q_{m+1}^{[k]})_0\coprod{}(\mathcal Q_m)_0$.
-	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[k-1]})_0\coprod{}(\mathcal Q_m)_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
+  We have $(\mathcal Q_{m+1}^{[k-1]})_0=(\mathcal Q_{m+1}^{[k]})_0\coprod{}(\mathcal Q_{m,k})_0$.
+	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[k-1]})_0\coprod{}(\mathcal Q_{m,k})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
  % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k-1]})_0$ and $\beta_1\cap(cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $(\mathcal Q_{m-1}^{[k]}$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q_m$.
+  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k-1]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.

### 2018-01-31 Grassmannian_cells.tex
Section 3.2 edits (almost done...)

--- 2018-01-29 Grassmannian_cells.tex
@@
 \newcommand{\onto}{\to\!\!\!\!\!\to}
-\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
-\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
+\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
+\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
+\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
+%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
 \newcommand{\Sc}[2]{\langle #1,#2\rangle}
@@
         \label{ses1}
-        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
+        \sesm{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}{\pi_{m+1}^I}.
       \end{equation}
@@
 In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
+
 \begin{lemma}
@@
       \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
-    \item For any $I'\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\ne0$ if and only if $I'\subset I$, in which case
-      \[\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)=0.\]
+    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
     \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
@@
       \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
-    \item We have $\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
+    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subset I$, in which case
+      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
       In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
@@
 
-  The first claim of part (2) is an immediate consequence of Lemma~\ref{le:unique morphisms}.(1) together with Theorem~\ref{covering}.
-  For the second claim of part (2), we apply $\Hom(-,\tilde P_{m+1}^I)$ to the sequence \eqref{ses1} for $I'$.
-
-  Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering}
-
-  The first part of (4) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
-  For the second part of (4), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
-  Then taking into account Lemma~\ref{le:homdecomposition} part (4), we get the isomorphism
+  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
+  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
+  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
+  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
   \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
-  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (4).
-
-  Part (5) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
+  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
+
+  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).
 \end{proof}
@@
 \begin{remark}
+  \label{rem:special case}
   We should point out that the case $m=2$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
   Indeed, recall from the proof of Lemma~\ref{le:special subrepresentations} that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
-  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\] 
+  \begin{equation}
+    \label{eq:special case}
+    (2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).
+  \end{equation}
   If we factor out the image of this morphism from $\tau\tilde P_3^I$, the remaining representation is a direct sum of the simple injective representations corresponding to the vertices $(2,\alpha_i^{-1})$ for $i\in I$, $i\ne j$.
@@
 
-%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
-%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]
-
-\newpage
-\sayD{Notation changes still needed after this point.}
-
-The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
-
-For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.
-
-\begin{definition}
-  Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$.
-Define $j_1^c$ as before.
- We say that ${\bf j}$ is admissible if 
-$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
-where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
-\end{definition}
-
-%For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
-%\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
-The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$.
-We define the admissible sequence $\delta {\bf j}$ by
-\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
-We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
-%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
-Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$. We obtain the following analogue of Lemma \ref{cor:truncated preprojective isomorphism}.
-
-\begin{lemma}The following holds:
-  \label{le:preprojective lifts}
-  \begin{enumerate}
-    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
-		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
-		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
-	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$.
-Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
-		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
-		for $k=1,\ldots,r$.
-  \end{enumerate}
-\end{lemma}
-
+The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
 \begin{definition}
@@
     \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
-    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_l:=(I'_{l-1})^c\cup I_l$ for $1\le l\le k$ satisfy $(I'_{l-1})^c\cap I_l=\varnothing$ for $1\le l\le k$.
-      In particular, we have $|I'_l|=n-1$ for $0\le l\le k-1$.
+    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=(I'_l)^c\cup I_{l+1}$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
   \end{enumerate}
-  Any sequence consisting of a single nonempty subset $\bfI=(I_1)$ will also be considered admissible.
-  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_1)=(I_1^c)$.
+  Here we take $I_{k+1}=\varnothing$.
+
+  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_0)=(I'_1)$.
 \end{definition}
@@
 We adopt similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
+
+By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
+\[\sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.\]
+For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
+For $w\in W_n$, we write $\pi_{m+1,w}^{I,J}:\tilde P_{m+1,w}^I\to\tilde P_{m+1,w}^J$ for the translated morphism with similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
 \begin{lemma}
@@
       \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
-    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}$ for $0\le l\le k-1$.
-      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a sequence of surjections
-      \[\tilde P_{m+1}\onto\tilde P_{m+1}^{I'_0}\onto\tilde P_{m,i_0}^{I'_1}\onto\tilde P_{m-1,(i_0,i_1)}^{I'_2}\onto\cdots\onto P_{m+1-k,\ui}^{I'_k}.\]
-      the truncated preprojective representation
-      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_{k+1}}\]
-      is a quotient of $\tilde P_{m+1}$ with $\Hom(\tilde P_{m+1},\tilde P_{m+1-k}^\bfI)\cong\CC$.
-      These quotients  
-  \item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
-    \[\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}\]
-    is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$.
-    Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
-    \[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
-    for $k=1,\ldots,r$.
+    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
+      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
+      \begin{equation}
+        \label{dia:truncated coherence}
+        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
+        \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
+      \end{equation}
+      where the composed map $\pi_{m+1}^\bfI:\tilde P_{m+1}\to\tilde P_{m+1-k,\ui}^{I'_k}$ is unique up to scaling and therefore we write
+      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_k}.\]
+      These truncated preprojective representations satisfy 
+      \[\tilde P_{m+1}^\bfI=\tilde P_{m,i_0}^{\delta\bfI}=\cdots=\tilde P_{m+1-k,\ui}^{\delta^k\bfI}.\]
   \end{enumerate}
@@
 For part (1), we consider the following commutative diagram, where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0 \\
-  0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[u] & \tilde P_{m,j}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
+\[\xymatrix{0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[d] & \tilde P_{m,j}\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
+  0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
 
@@
 	\end{proof}
+
 The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
@@
 
-\subsection{Fibrations of Quiver Grassmannians}\label{sec:fibrations}
-
-Let $\ses{M}{B}{N}$ be a short exact sequence of representations. This induces a map between quiver Grassmannians
-\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M)\]
-which is also called Caldero-Chapoton map.
-By the results of \cite[Section 3]{cc} it follows that $\Psi^{-1}_\tbfe(A,V)=\mathbb{A}^{\dim\Hom(A,M/V)}$ for all pairs of subrepresentations $(A,V)$ for which the fibre is not empty.
+\subsection{Fibrations of Quiver Grassmannians}
+\label{sec:fibrations}
+
+Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
+This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
+\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M).\]
+Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(V,W)=\mathbb{A}^{\dim\Hom(W,M/V)}$.
+
 Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
@@
 \[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
-
 The following is proved in \cite[Section 3]{cefr}.
-\begin{theorem}\label{vb}
-If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image.
+\begin{theorem}
+  \label{vb}
+  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it is an affine bundle over the image.
   In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
@@
 %\begin{proof}\footnote{sketch, double-check}
-
 %As $X$ and $Y$ are projective, they are compact.
-As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
+As the fibers are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
 This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
-
 %\end{proof}
 
-%%%
-
-Let $\uj=(j_1,\ldots,j_l)$ be an admissible sequence and $m\geq 3$.
-The short exact sequence $\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{(j_1,\ldots,j_l)}}$ induces a map between quiver Grassmannians
-$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(j_1,\ldots,j_{l-1})})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
-
-	%The Auslander-Reiten translate of $\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
-	%\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
-%
-
-For $m\geq 4$, we obtain another map between quiver Grassmannians 
-$$\Phi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,j_l})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(P(m,\uj))\times \Gr^{\tilde Q}_\tbfg(\tau \tilde P_{m}^{\uj}).$$
-For $m=3$, we obtain also a map $\Phi_{3,\uj}$ when replacing $\tau\tilde P_{m}^{\uj}$ by $\tau' \tilde P_3^{\uj}$. 
-\begin{proposition}\label{quotient}Let $m\geq 3$ and $\uj=\in I_l$. The following holds:
+We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
+Fix $m\ge1$.
+For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
+\[\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}\]
+which induces a map between quiver Grassmannians as above:
+\[\Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).\]
+To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
+Here we consider the short exact sequence 
+\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
+where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
+Then in the same way as above we obtain the map
+\[\Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).\]
+\begin{proposition}
+  \label{quotient}
+  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
+  The following hold for any $j\in I$:
   \begin{enumerate}
-\item The fibre $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is empty if and only if $U\in\Phi_{m,\uj}^{-1}(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,\uj)$.
-\item If the fibre $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty, we have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l}/U)= 0$.
+    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
+    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $U\in\Phi_{m,I,j}^{-1}(V,0)$ for some $V\subset\tilde P_m(I,j)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
   \end{enumerate} 
@@
 \begin{proof}
-In order to prove the case $m=3$, we replace $\tau\tilde P_{3}^{\uj}$ by  $\tau'\tilde P_{3}^{\uj}$ in which case all arguments hold in the same way.
-In particular, we make use of $\Ext(\tau' P_3^{\uj},\tau' P_3^{\uj})=0$.
-
-If $W=0$,  we consider the following commutative diagram
-
- \[\xymatrix{&0&0&0&\\0\ar[r] &\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\ar[r]\ar[u] & \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\ar[r]\ar[u] & 0 \\
-0\ar[r] &\Ext(\tilde P_{m}^{\uj},P(m,\uj))\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\ar[r]\ar[u] & \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\ar[r]\ar@{=}[u] & 0\\  0\ar[r] &\Ext(\tilde P_{m}^{\uj},V)\ar[r]\ar[u] &  \Ext(\tilde P_{m}^{\uj},U)\ar[r]\ar[u] &0\ar[r]\ar[u] & 0}\]
-
-Corollary \ref{cor:perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.
-This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ and thus $$\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\cong  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U).$$ This means that the induced map
-\[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
-is zero. Therefore, the induced exact sequence splits. 
-Let $\uj'=(j_1,\ldots,j_{l-1})$.
-On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
- \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{\uj'}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
-  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
-which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split.
-This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj'})=0$ by Lemma \ref{le:unique morphisms}.
-This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.
-
-Thus assume that $U\in\Phi_{m,\uj}^{-1}(V,W)$ with $W\neq 0$.
-We first show that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$.
-Clearly, $\tau\tilde P_{m}^{\uj}/W$ is a proper factor of $\tau \tilde P_{m}^{\uj}$ if $W\neq 0$.
-It follows that we have $\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$.
-Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m}^{\uj}\to \tau\tilde P_{m}^{\uj}/W$ factors through the middle term $Z$ of the AR-sequence
-\[\ses{\tau\tilde P_{m}^{\uj}}{Z}{\tilde P_{m}^{\uj}}\]
-which means that the first map of the induced sequence
-\[\Hom(\tau\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj}/W)\to\Ext(Z,\tau\tilde P_{m}^{\uj}/W) \]
-is zero. By Lemmas \ref{le:properties} and \ref{AR}, we have 
-$$\Ext(\tau\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=0,\quad \Ext(\tilde P_m^{\uj},\tau\tilde P_m^{\uj})=\CC$$
-for $m\geq 4$.
-The same identities hold for $m=3$ when replacing $\tau$ by $\tau'$.
-The second identity follows for instance when using $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})=\CC$, which is straightforward by Example \ref{smallm}, together with the isomorphism $\Ext(\tilde P_{3}^{\uj},\tilde P_{2,j_l})\cong\Ext(\tilde P_{3}^{\uj},\tau'\tilde P_{3}^{\uj})$ obtained above.
-
-Thus the injective map $\CC=\Hom(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})\to\Ext(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})$ induced by the Auslander-Reiten sequence is injective is bijective.
-Together with $\Ext(\tau \tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=0$, this shows $\Ext(Z,\tau\tilde P_{m}^{\uj})=0$ and thus $\Ext(Z,\tau\tilde P_{m}^{\uj}/W)=0$.
-
-%As $\tau\tilde P_{m+1}^{(k)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$ and $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$, i.e.
-Lemma \ref{AR}, yields $\Ext(Z,\tau\tilde P_{m+1}^{(k)})=0$ as the AR-sequence does not split.
-In conclusion, we obtain $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$.
-
-Again we can apply Corollary \ref{cor:perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
- Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.
-
-Thus it remains to show that $\Psi_{m,\uj}(U,\tilde P_{m}^{\uj})$ is not empty if $W\neq 0$.
-Since $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m,j_l})$ is surjective which already means that there exists a commutative diagram as above.
-This shows that the fiber is not empty.
-\end{proof}
-Now we are able to state the following result concerning the fibers of $\Psi_{m,\uj}$:
-\begin{proposition}\label{fibers}
+  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
+  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
+  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
+  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
+    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
+  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
+  This implies that the map 
+  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
+  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
+  This argument can be reversed and thus (1) holds.
+
+  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
+  This gives rise to the following commutative diagram:  
+  \[\xymatrix{
+    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
+    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
+    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
+    &0&0&0&}\]
+  By Corollary~\ref{cor:perpendicular}, we have $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)=0$ as well.
+  This yields the isomorphisms
+  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]
+
+  If $W=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)=\varnothing$.
+
+  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
+  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
+  \begin{equation}
+    \label{eq:ar2}
+    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
+  \end{equation}
+  This in particular says the first map of the induced sequence
+  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
+  is zero.
+  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
+  \[\Ext(\tilde K_m,\tilde K_m)=0,\quad \Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
+  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
+  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yeilds $\Ext(Z,\tilde K_m)=0$.
+  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
+  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
+\end{proof}
+
+Now we are able to state the following result concerning the fibers of $\Psi_{m+1,I,j}$:
+\begin{proposition}
+  \label{fibers}
   The following hold:
   \begin{enumerate}
-    \item For $V\subsetneq \tilde P_{m}^{\uj}$ and $U\subseteq\tilde P_{m-1,j_l}$, we have $\Psi_{m,\uj}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m-1,j_l}/U\rangle}$.
-    \item If $V=\tilde P_{m,\uj}$, the fiber $\Psi_{m,\uj}^{-1}(U,V)$ is not empty if and only if $\Phi_{m,\uj}(U)\neq (U,0)$.
-In this case, we have $\Psi_{m,\uj}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m-1,l_j}/U\rangle}$.
-
+    \item For $V\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
+    \item If $V=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,V)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
+      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
   \end{enumerate}
 \end{proposition}
-\begin{proof}By Lemma \ref{le:subrep}, any subrepresentation $V\subsetneq \tilde P_{m}^{\uj}$ is preprojective.
-But the representation $\tilde P_{m-1,l_j}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$.
-Thus we have $\Ext(V,\tilde P_{m-1,l_j}/U)=0$.
-If $U=0$, we have $\Ext(V,\tilde P_{m-1,l_j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
+\begin{proof}
+  By Lemma~\ref{le:subrep}, any subrepresentation $V\subsetneq\tilde P_{m+1}^I$ is preprojective.
+  But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
+  Thus we have $\Ext(V,\tilde P_{m,j}/U)=0$. 
+  If $U=0$, we have $\Ext(V,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
 
   The second statement follows directly from Proposition \ref{quotient}.
-
-\end{proof}
-\begin{theorem}\label{cellscover}
-Let $m\geq 2$ and let $\uj=(j_1,\ldots,j_l)\in I_l$ with $l\leq n-1$. Every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ admits a cell decomposition into affine spaces.
+\end{proof}
+
+\begin{theorem}
+  \label{cellscover}
+  For $m\geq 1$ and $I\subset\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
 \end{theorem}
@@
 
-In order to prove the claim, we prove the following more general statement:
-\vs
+In order to prove the claim, we prove the following more general statement:\\
 
@@
 By induction hypothesis the quiver Grassmannians $\Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})$ have cell decompositions which are compatible with $\pi^{\bf i}_m$ and, moreover, the quiver Grassmannians $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ have a cell decompositions which are compatible with $\pi^{\bf j}_{m,\uj}$.
-The second part of Proposition \ref{fibers} says that the fibres are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
-This yields a collection of cells over which the fibres are empty.
+The second part of Proposition \ref{fibers} says that the fibers are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
+This yields a collection of cells over which the fibers are empty.
 Note that $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is just a point in this case.
@@
 Fix a cell $B_i\subset\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$.
-As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fibre over $B_i\times C_0$ is empty or that the fibre is of constant dimension building a new cell $CB_i$.
+As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fiber over $B_i\times C_0$ is empty or that the fiber is of constant dimension building a new cell $CB_i$.
 For all representations $U\in CB_i$ we have $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$ because $\pi_{m,\uj}^{\bf j}$ is surjective and $\pi_{m,\uj'}^{j_l}(U)=\tilde P_{m}^{\uj}$.
 
-In the second case, the fibre over $B_i\times C_k$ is non empty and of constant dimension building a new cell $CB_{i,k}$.
+In the second case, the fiber over $B_i\times C_k$ is non empty and of constant dimension building a new cell $CB_{i,k}$.
 As we have $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$, it follows that $\pi^{\bf j'}_{m,\uj'}(U)=0$ for all representations $U\in (CB)_{i,k}$.
@@
 By Lemma \ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition.
-The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
+The second part of the Proposition says that the fibers are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
 In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma \ref{vb}?}.
@@
 As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{\udim P_m{(k)}}$.
-The description of the non-empty fibres in Proposition \ref{fibers} together with Corollary \ref{fpoly} and Theorem \ref{celldec} yield the following:
+The description of the non-empty fibers in Proposition \ref{fibers} together with Corollary \ref{fpoly} and Theorem \ref{celldec} yield the following:
 \begin{corollary}
@@
  % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=\mathcal Q(m+1,k)_0$ and $\beta_1\cap\mathcal T(m-1,k)_0=\varnothing$ where $\mathcal T(m-1,k)$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q(m,0)$.
+  By Proposition \ref{quotient}, the fiber over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=\mathcal Q(m+1,k)_0$ and $\beta_1\cap\mathcal T(m-1,k)_0=\varnothing$ where $\mathcal T(m-1,k)$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q(m,0)$.
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q(m+1,k)$ is connected to $\mathcal T(m-1,k)$ by a $2$-arrow.\sayT{compatibility?

### 2018-01-31 Grassmannian_cells.tex

@@
 %For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-
-It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by
+\begin{remark}It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$.
+Also every usual arrow of $\mathcal Q_m^{[k]}$ does.
+In particular, the quiver obtained from $\mathcal Q_m^{[k]}$ when forgetting the $2$-arrows gives rise to a (non-disjoint) union of subquivers of $\widetilde{K(n)}$.
+
+For general $m$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
+If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and precisely one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
+In these cases, we label the $2$-arrow by the corresponding arrow.
+
+Recall that, for $m\geq 3$, we have
+\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
+These isomorphisms are also present in the structure of the $2$-quivers we define.
+\end{remark}
+
+%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
+The $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is given by the vertex $(1,e)$.
+Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
+Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
 \[
-  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
+  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
 \]
@@
 
-This yields recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
+We can recursively build the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ defined by the support quivers
 \begin{align}
-  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
+  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,e)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
 \end{align}
@@
 \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \tilde P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \tilde P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$\tilde P_2^{[n-1]}$};
+\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,e)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 \noindent
-where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver (\ref{coeff}) instead.
-
-For $m\geq 3$, we have
-
-\begin{align}
-  \label{eq:homext} 
-  \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
-\end{align}
-
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-
-The next step is to define the $2$-quivers of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
-
-Observe that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, we have 
-$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
-This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
-for $i=1,\ldots,n-1$.
-
-The representation $\tau\tilde P_3^{[k]}$ is given by 
-\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
-Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers.
-
- The chosen basis of $\Ext(P_3^{[n-1]},P_2)$ recursively gives rise to the following $2$-quiver of $P_3^{[k]}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation.
-Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(2,\alpha_n^{-1})$ and that all $2$-arrows end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
-\\
+where the $2$-arrows are coloured red.
+Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
+The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the quiver (\ref{coeff}).
+In abuse of notation, we also denote the quiver (\ref{coeff}) by $\mathcal Q_{2}^{[k]}$.
+In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
+We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices by $\alpha_i^{-1}$.
+
+The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
+First, we define
+$$\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},$$
+i.e.
+we translate all vertices by $\alpha_n^{-1}$.
+Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
 
@@
 
+\noindent In abuse of notation, we dropped the labels of the vertices in the illustration.
+Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$.
+
+\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
+$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
+This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
+for $i=1,\ldots,n-1$.
+
+The representation $\tau\tilde P_3^{[k]}$ is given by 
+\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
+Note that the image of the homomorphism corresponding to the basis element spanning $\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2)$ corresponds to the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
+Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
+In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
+\end{remark}
 %It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
-
 %\begin{align}\label{eq:case2}
@@
 %\end{align}
-
-Now we can recursively the $2$-quivers of $ \tilde P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure and considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}).
-As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
-
-For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
+Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$ when repeating the procedure. 
+%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
+%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
+
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
- Let us assume that we already constructed the $2$-quiver of $ P_{m+1}^{[k]}$.
-The $2$-quiver of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to the one of $\tilde P_{m}$ where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$.
-This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$.
+
+Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k+1$.
+As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
+
+For $m\geq 4$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
+This can also be seen on the level of $2$-quivers, i.e.
+we find $\cQ_{m-1}^{[k]}$ as a subquiver of $\cQ_{m,k}$.
+More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.
+
+Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow.
+Thereby, the $2$-arrow connects $\mathcal Q_{m+1}^{[k]}$ to the subquiver $\cQ_{m-1}^{[k]}$ in $\cQ_{m,k}$.
+This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
 \\
@@
 \begin{tikzpicture}
-\draw (0,4) node (A1) {$\tilde P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$\tilde P_{m}$} +(1.5,0) node (B1) {$\tilde P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$\tilde P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$\tilde P_{m-1}$}  +(6,0) node (E1) {$\tilde P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$\tilde P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$\tilde P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$\tilde P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$\tilde P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$\tilde P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$\tilde P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$\tilde P^{[n-1]}_{m-2}$} ;
+\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 
-\noindent In order to keep the diagrams as simple as possible we did not insert the labels of the vertices and arrows.
-As  every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q(m,k)$.
-As an example consider the case $n=3$ and $m=3$.
-The $2$-quiver of $\tilde P_3$ is given by:\\
+\noindent 
+%In order to keep the diagrams as simple as possible we did not insert the labels of the vertices.
+As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$.
+ Note that two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
+$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta)$$
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta$.
+
+\begin{theorem}\begin{enumerate}
+\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+The results of Section \ref{QG} imply that the second statement follows from the first one.
+We proceed by induction on $m$ and $k$.
+The case of the representation $\tilde P_1$ is trivial.
+We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
+Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.
+
+  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
+  \[
+    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
+  \]
+  We have $(\mathcal Q_{m+1}^{[k-1]})_0=(\mathcal Q_{m+1}^{[k]})_0\coprod{}(\mathcal Q_{m,k})_0$.
+	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[k-1]})_0\coprod{}(\mathcal Q_{m,k})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
+ % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
+  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k-1]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
+  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.
+\end{proof}
+
+As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\\
 
@@
 \draw[->,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {\scriptsize $c$};
+\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {};
+\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {};
 
 \end{tikzpicture}\\
-
- Note that two different vertices of $\mathcal Q(m,k)_0$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset\mathcal Q(m,k)_0$ are defined by
-$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$
-
-\begin{theorem}\begin{enumerate}
-\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
-	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
-\end{enumerate}
-\end{theorem}
-\begin{proof}
-The results of Section \ref{QG} imply that the second statement follows from the first one.
-We proceed by induction on $m$ and $k$.
-The case of the representation $\tilde P_1$ is trivial.
-The strong successor closed subsets of the $2$-quivers  $\mathcal Q(2,k)$ of $\tilde P_2^{[k]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}).
-As $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, the  subrepresentations are in one-to-one correspondence with the successor closed subsets of (\ref{coeff}).
-Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $e\subset \mathcal Q(2,k)$ is successor closed.
-
-  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
-  \[
-    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
-  \]
-  We have $\mathcal Q(m+1,k-1)_0=\mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$.
-	Let $\beta_1\coprod\beta_2\subset \mathcal Q(m+1,k)_0\coprod{}\mathcal Q(m,0)_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
- % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fiber over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=\mathcal Q(m+1,k)_0$ and $\beta_1\cap\mathcal T(m-1,k)_0=\varnothing$ where $\mathcal T(m-1,k)$ is the $2$-quiver of $\tilde\tau P_{m+1}^{[k]}=\tilde P_{m-1}^{[k]}$ sitting inside $\mathcal Q(m,0)$.
-  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q(m+1,k)$ is connected to $\mathcal T(m-1,k)$ by a $2$-arrow.\sayT{compatibility?
-Classify the cells which satisfy the condition that the quotient on the AR-translate is zero...}
-\end{proof}
 

### 2018-02-01 Grassmannian_cells.tex
Small edits

@@
   \label{le:subrep}
-  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations of $\tilde P_{m+1}^I$ are direct sums of shifted preprojective representations $\tilde P_{m+1-k,\ui}$ for $1\le k\le m$ and $\ui\in A_1^{(k)}$.
-\end{lemma}
-\begin{proof}
-  \sayD{The proof needs to be improved for the new stronger statement.}
+  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, all non-trivial proper subrepresentations of $\tilde P_{m+1}^I$ are direct sums of preprojective representations.	
+\end{lemma}
+\begin{proof}
   By Lemma~\ref{le:homdecomposition}, the projected representation $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$.
@@
 Recall that, for $m\geq 3$, we have
-\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
+\begin{align}
+  \label{eq:homext} 
+  \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
+\end{align}
 This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.

### 2018-02-02 Grassmannian_cells.tex
Section 5 again nearly finished

--- 2018-01-31 Grassmannian_cells.tex
@@
 The next step is to associate a $2$-quiver $\mathcal Q_m^{[k]}$ with the lifted truncated preprojective representations $\tilde P_m^{[k]}:=\tilde P_m^{\{1,\ldots,k\}}$ for $m\geq 2$ and $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_m^{[k]}$.
-Recall that the cells of the quiver Grassmannians attached to $P_m^{[k]}:= F_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
-Moreover, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of arbitrary truncated preprojective representations $P_m^V$ only depend on $\tbfe$ and $\udim P_m^V$.
-In short, in view of Theorem \ref{thm:truncpp}, the $2$-quivers $\mathcal Q_m^{[k]}$ can be seen as being attached to any (truncated) preprojective representation of the respective dimension.
+Recall that, by Theorem \ref{celldec}, the cells of the quiver Grassmannians attached to $P_m^{[k]}:= G_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
+Moreover, by Theorem \ref{thm:truncpp}, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of arbitrary truncated preprojective representations $P_m^V$ only depend on $\tbfe$ and $\udim P_m^V$.
+In short, the $2$-quivers $\mathcal Q_m^{[k]}$ can be seen as being attached to any (truncated) preprojective representation of the respective dimension.
 
 For building the mentioned $2$-quivers, we use the recursive construction described in Section \ref{Lifting}. 
-In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
+%In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
 %For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-\begin{remark}It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$.
+\begin{remark}\begin{enumerate}\item It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
 Also every usual arrow of $\mathcal Q_m^{[k]}$ does.
@@
 
-For general $m$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
+For general $m\geq 1$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
 If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and precisely one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
 In these cases, we label the $2$-arrow by the corresponding arrow.
-
-Recall that, for $m\geq 3$, we have
-\begin{align}\label{eq:homext} \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).\end{align}
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
-These isomorphisms are also present in the structure of the $2$-quivers we define.
-\end{remark}
-
-%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
-The $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is given by the vertex $(1,e)$.
-Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
-Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
+\item The following two remarks are meant to understand the structure of the $2$-quivers. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
 \[
@@
 
-We can recursively build the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ defined by the support quivers
-\begin{align}
-  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,e)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
-\end{align}
-For general $m\geq 2$, there exists a short exact sequence
+\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
+\begin{align}\label{eq:homext} \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.
+\tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).\end{align}
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
+These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
 \[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
 Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
+\end{enumerate}
+\end{remark}
+
+%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
+Initially, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined by the vertex $(1,e)$.
+Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
+Using (\ref{eq:case2}), we can recursively construct the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ which are defined by the support quivers
+\begin{align}
+  \label{coeff}
+    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-k}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-k})}
+\end{align}
+
 We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
@@
 Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
-The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the quiver (\ref{coeff}).
-In abuse of notation, we also denote the quiver (\ref{coeff}) by $\mathcal Q_{2}^{[k]}$.
+The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}).
+In abuse of notation, we also denote the support quiver by $\mathcal Q_{2}^{[k]}$.
 In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
-We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices by $\alpha_i^{-1}$.
+We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
 
@@
 i.e.
-we translate all vertices by $\alpha_n^{-1}$.
+we translate all vertices - understood as vertices of $\widetilde{K(n)}$ - by $\alpha_n^{-1}$.
 Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
@@
 
-\noindent In abuse of notation, we dropped the labels of the vertices in the illustration.
-Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in the vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
-We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$.
+\noindent In abuse of notation, we did not label the vertices in the illustration.
+Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in a vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.
 
@@
 $$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
-This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
-for $i=1,\ldots,n-1$.
-
-The representation $\tau\tilde P_3^{[k]}$ is given by 
-\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
-Note that the image of the homomorphism corresponding to the basis element spanning $\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2)$ corresponds to the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$.
-Thus in this case the $2$-arrow connects the $2$-quiver of $\tilde P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
+for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
+\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
+Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
+This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
 In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
-In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
+%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
 \end{remark}
@@
 %\end{align}
-Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$ when repeating the procedure. 
+Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
 %This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
 %As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
-
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
-
-Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k+1$.
+Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$.
 As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
-
-For $m\geq 4$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
+Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\alpha_{n}^{(-1)^{m+1}}.\cQ_{m}^{[1]}.$$\sayT{check: is it always $\alpha_n$?}
+
+For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
 This can also be seen on the level of $2$-quivers, i.e.
@@
 More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.
-
 Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow.
@@
 
-\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-1}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}=\mathcal Q_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-1]}$};
+\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(11,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}=\alpha_{n}^{(-1)^{m+1}}.\cQ_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$.
- Note that two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
+ As already mentioned two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
 Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by

### 2018-02-03 Grassmannian_cells.tex
Section 3.2 edits (done?)

--- 2018-02-01 Grassmannian_cells.tex
@@
 
+\begin{corollary}
+  \label{cor:AR lift}
+  For $m\ge2$, the Auslander-Reiten sequence~\eqref{eq:AR sequence} on $K(n)$ lifts to the Auslander-Reiten sequence
+  \begin{equation}
+    \label{eq:lifted AR sequence}
+    \xymatrix{0 \ar[r] & \tilde P_{m-1} \ar^(.4){\tilde\iota_{m-1}}[r] & \bigoplus_{j=1}^n \tilde P_{m,j} \ar[r] & \tilde P_{m+1} \ar[r] & 0}.
+  \end{equation}
+\end{corollary}
+
 \begin{example}
@@
   \end{enumerate}
-  Here we take $I_{k+1}=\varnothing$.
+  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $I_k$.
 
@@
 \begin{proof}
-
-For part (1), we consider the following commutative diagram, where the square on the left hand side is the corresponding Auslander-Reiten sequence:
-\[\xymatrix{0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[d] & \tilde P_{m,j}\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
-  0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
-
-%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
-For $m=3$, it is straightforward that the injection of the lower row factors over $\tilde P_{1,(j^c,j^c)}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$.
-Thus we have $\tilde P_{3}^{\uj}\cong \tilde P_{2,j^c}^{\uj^c}/\tilde P_{1,(j^c,j^c)}=\tilde P_{2,j^c}^{(j^c)}$.
-Applying the identities \eqref{eq:recursive covers} the claim follows for $m\geq 3$.
-
-The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$.
-We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$.
-We successively obtain commutative diagrams
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
-  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
-
-Finally, we consider the short exact sequence:
-
-\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
-Using Lemma \ref{le:properties}.(2), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\CC$.
-%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
-	\end{proof}
-
-The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars.
-Let $\underline{j_1}=(j_{1,1},\ldots,j_{1,n-1})$ and $\uj=(j_{1,1},\ldots,j_{1,l})\in I_l$.
-It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$.
-We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$.
-We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$.
-Therefore, we need to apply a translated version of this morphism.
-In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.
-
-Our construction immediately yields the following lemma.
-\begin{lemma}\label{projections}
-Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
-\[\pi_m^{\bf j}=\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}\circ\ldots\circ\pi^{(j_{2}^c,\underline{j_2})}_{m-1,(j_1^c)}\circ\pi_m^{\underline{j_1}}.\]
-Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
-\[\pi_{m-k+1,(j_{k-1}^c)}^{(j_{k-1}^c,\underline{j_k})}=\prod_{i=1}^{n-2} \pi^{(j_{k-1}^c,j_{k,l_1},\ldots, j_{k,l_{i}})}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
-for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
-\end{lemma}
+  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
+  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
+    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
+    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
+    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
+  & & 0& 0&}\]
+  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.
+
+  The first claim of part (2) is then immediate by repeatedly applying part (1) while the final claim of part (2) is a consequence of the definition of $\delta$.
+\end{proof}
 
@@
 Thus it remains to show that this cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ is compatible with $\pi_{m,\uj'}^{\bf j}$ where ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
-Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{projections}.
+Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{le:truncated quotients}.(2).
 

### 2018-02-03 Grassmannian_cells.tex

--- 2018-02-02 Grassmannian_cells.tex
@@
 
-For general $m\geq 1$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$.
-If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and precisely one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does.
-In these cases, we label the $2$-arrow by the corresponding arrow.
 \item The following two remarks are meant to understand the structure of the $2$-quivers. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
@@
 \item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
-\begin{align}\label{eq:homext} \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}.
-\tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).\end{align}
+\begin{align}
+  \label{eq:homext} 
+  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
+\end{align}
 This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.

### 2018-02-05 Grassmannian_cells.tex
Section 5 (finished ?)

@@
 \section{Combinatorial description of non-empty cells}
-In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
+\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
 The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section \ref{sec:fibrations}.
@@
 In the following, we frequently use the notation and conventions of Section \ref{Lifting}.
-The next step is to associate a $2$-quiver $\mathcal Q_m^{[k]}$ with the lifted truncated preprojective representations $\tilde P_m^{[k]}:=\tilde P_m^{\{1,\ldots,k\}}$ for $m\geq 2$ and $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_m^{[k]}$.
+The next step is to associate a $2$-quiver $\mathcal Q_m^{[k]}$ with the lifted truncated preprojective representations 
+$$\tilde P_m^{[k]}:=\begin{cases}\tilde P_m^{\{n,\ldots,n-k+1\}}\text{ if } m\text{ is even}\\\tilde P_m^{\{1,\ldots,k\}}\text{ if }m\text{ is odd}\end{cases}$$ 
+for $m\geq 2$ and $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_m^{[k]}$.
 Recall that, by Theorem \ref{celldec}, the cells of the quiver Grassmannians attached to $P_m^{[k]}:= G_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
@@
 
-For building the mentioned $2$-quivers, we use the recursive construction described in Section \ref{Lifting}. 
+For building the mentioned $2$-quivers, we use the recursive construction described in Section \ref{Lifting}. The following remarks are meant to understand the structure of the $2$-quivers. 
 %In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
@@
 \begin{remark}\begin{enumerate}\item It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Also every usual arrow of $\mathcal Q_m^{[k]}$ does.
+Also every usual arrow of $\mathcal Q_m^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
 In particular, the quiver obtained from $\mathcal Q_m^{[k]}$ when forgetting the $2$-arrows gives rise to a (non-disjoint) union of subquivers of $\widetilde{K(n)}$.
 
-\item The following two remarks are meant to understand the structure of the $2$-quivers. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
+\item Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
 \[
@@
 
-The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the truncated preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the truncated preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
+The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the (truncated) preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the (truncated) preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
 First, we define
@@
 i.e.
-we translate all vertices - understood as vertices of $\widetilde{K(n)}$ - by $\alpha_n^{-1}$.
+we translate all vertices - understood as vertices of $\widetilde{K(n)}$ - and $(2)$-arrows by $\alpha_n^{-1}$.
 Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
@@
 \noindent In abuse of notation, we did not label the vertices in the illustration.
-Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in a vertex corresponding to $(1,1)$ of $\widetilde{K(n)}$.
+Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in a vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
 We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.
 
-\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
+\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
 $$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
@@
 As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
-Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\alpha_{n}^{(-1)^{m+1}}.\cQ_{m}^{[1]}.$$\sayT{check: is it always $\alpha_n$?}
+Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$
 
@@
 
-\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(11,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}=\alpha_{n}^{(-1)^{m+1}}.\cQ_{m}^{[1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
+\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
-$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta)$$
-where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta$.
+$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G_{K(n)}\tbfe (\beta)\in\NN^{K(n)_0}$$
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[k]})_0$.
 
@@
 The case of the representation $\tilde P_1$ is trivial.
-We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
+We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
 Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.
@@
  % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k-1]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
+  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.

### 2018-02-06 Grassmannian_cells.tex
Section 4 edits

--- 2018-02-03 Grassmannian_cells.tex
@@
 It will be important to understand the possible subrepresentations of the truncated preprojective representations $\tilde P_{m+1}^I$.
-To describe these, we introduce notation for locating lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
-Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
-For $k\ge1$, set
-\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
-Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
-In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
-More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
-\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
-Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.
-
-To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
-Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
-Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
+
 \begin{lemma}
@@
 
-For the notation of the following result, we refer the reader to the discussion before Lemma~\ref{le:subrep}.
+We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
+Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
+For $k\ge1$, set
+\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
+Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
+In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
+\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
+Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.
+
+To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
+Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
+Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
 \begin{lemma}
@@
   \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
-  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$.
+  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
   From Lemma~\ref{le:properties}.(3) again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
@@
 For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[
-  \mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}
-\]
-
+\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
 The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
@@
 We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
-We can consider the decomposition $X_i=\bigoplus_{(i,\chi)\in A_Q} X_{(i,\chi)}$.
-We define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_q$.
-For a fixed a subspace $U_i$, we can define the subspace $t.U_i$.
-In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_\bfe(X)$ as $t.U=(t.U_i)_{i\in Q_0}$ is no subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
-Actually, such an action has to satisfy $X_\alpha(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
-\begin{lemma}
-  Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
-  If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_Q$.
-\end{lemma}
-\begin{proof} 
-  Let $U\in\Gr_\bfe(X)$.
-Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$.
-Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$.
-Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover.
-It follows
-\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
-for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
-Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
-for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
-\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
-for every $t\in \C^\ast$.
+We can consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_i$.
+Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
+In general, this does not induce a torus action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
+Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$. 
+\begin{lemma}
+  Let $X$ be a representation of $Q$ which can be lifted to $\hat Q$.
+  Fix an integer $c_\alpha\in\ZZ$ for each~$\alpha\in Q_1$.
+  Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
+  Then the torus action on $X$ determined by $d$ induces a torus action on $\Gr_\bfe(X)$.
+\end{lemma}
+\begin{proof} 
+  Since $X$ can be lifted, for any arrow $\alpha\in Q_1$ we can write $X_\alpha:X_i\to X_j$ as a block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$ for $\chi\in A_Q$.
+  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
+  Then we can write $u_i=\sum_{\chi\in A_Q} u_{(i,\chi)}$ for some vectors $u_{(i,\chi)}\in U_i\cap X_{(i,\chi)}$.
+  But observe that for an arrow $\alpha:i\to j$ of $Q$, we have $X_\alpha(u_{(i,\chi)})=X_{(\alpha,\chi)}(u_{(i,\chi)})\in U_j\cap X_{(j,\chi+e_\alpha)}$, say $X_{(\alpha,\chi)}(u_{(i,\chi)})=u_{(j,\chi+e_\alpha)}$.
+  It follows that
+  \begin{align*}
+    X_\alpha(t.u_i)=\sum\limits_{\chi\in A_Q}X_{(\alpha,\chi)}(t.u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}X_{(\alpha,\chi)}(u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}\sum\limits_{\chi\in A_Q} t.u_{(j,\chi+e_\alpha)}
+  \end{align*}
+  and thus $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$.
 \end{proof}
@@
   \label{degreecondition} 
-  Let $X$ be an indecomposable representation of $\hat Q$. There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
+  Let $X$ be an indecomposable representation of $\hat Q$.
+  There exists $d:\mathrm{supp}(X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
   \begin{enumerate}
-    \item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$ with $(i,\chi)\neq (j,\chi')$ we have $d(i,\chi)\ne d(j,\chi')$;
+    \item for $(i,\chi),\,(i,\chi')\in\mathrm{supp}(X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
     \item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
@@
 \begin{proof}
-  Assume that $|Q_1|=n$.
+  For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_\}$.
   Since $X$ is finite-dimensional and indecomposable, the support quiver $\mathrm{supp}(X)$ is a connected and finite subquiver of $\hat Q$.
   In order to prove the statement, we may assume that $(i,0)\in\mathrm{supp}(X)$ for some $i\in Q_0$.
-  We fix $c_\alpha\in\NN$ and show that we can choose a degree such that the two conditions are satisfied for this choice.
   Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(i,0)$ such that the underlying graph of the path has no cycles.
-  This implies that, for $(i',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have $|d_j|\leq K$.
-
-  Set $c_{\alpha_1}=1$ and choose $c_{\alpha_j}$ recursively in such way that 
-  \[c_{\alpha_k}\geq 2(K+1)\sum_{j=1}^{k-1} c_{\alpha_j}\]
-  for $k=2,\ldots,n$.
-
-  Let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i',\chi):=f(\chi)$ for $(i',\chi)\in\mathrm{supp}(X)$.
-  In particular, for $(i',\chi)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have
-  \[d(i',\chi)=\sum_{j=1}^n d_jc_{\alpha_j}.\]
-
-  First note that we have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
-  Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^n d_ic_{\alpha_i}=\sum_{i=1}^n e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^n d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^n e_ic_{\alpha_i}$.
+  This implies that, for $(i',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.
+
+  Set $c_{\alpha_1}=1$ and choose $c_{\alpha_l}$ recursively in such way that 
+  \[c_{\alpha_l}\geq 2(K+1)\sum_{k=1}^{l-1} c_{\alpha_k}\]
+  for $l=2,\ldots,n$.
+
+  Let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i',\chi):=f(\chi)$ for $(i',\chi)\in\mathrm{supp}(X)$.
+  In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
+  \[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]
+
+  Now assume that $d(i',\chi)=d(i',\chi')$ for $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$ and $\chi'=\sum_{l=1}^n \kappa'_l e_{\alpha_l}$.
   This implies
-  \[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
-  Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain 
-  \[|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}.\]
-  This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_i}$.
-
-  Finally, assume that $d(j,\chi')-d(i,\chi)=c_\alpha$.
+  \[\sum_{l=1}^{n-1}(\kappa_l-\kappa'_l)c_{\alpha_l}=(\kappa'_n-\kappa_n)c_{\alpha_n}.\]
+  But we have $|\kappa_l-\kappa'_l|\leq |\kappa_l|+|\kappa'_l|\le 2K$ and thus we obtain 
+  \[|\sum_{l=1}^{n-1}(\kappa_l-\kappa'_l)c_{\alpha_l}|\le 2K\sum_{l=1}^{n-1}c_{\alpha_l} < c_{\alpha_n}.\]
+  This inductively yields $\kappa_l=\kappa'_l$ for $l=n,\ldots,1$ by the choice of the $c_{\alpha_l}$.
+
+  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$.
+  Assume that $d(j,\chi')-d(i,\chi)=c_\alpha$.
   Then we have $d(j,\chi')=d(j,\chi+e_\alpha)$.
@@
   Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
-  Then the torus action of $T$ on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
-  \[\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
+  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
   where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
@@
   A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$, $t\in\C^\ast$.
-  Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_i}(X_i)$ induced by the decompositions $X_i=\bigoplus_{\chi\in A_Q} X_{i,\chi}$.
-  A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
-  \[X_i\cap U_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}\cap U_{(i,\chi)}=\bigoplus_{\chi\in A_Q} U_{(i,\chi)}.\]
-  Thus we can apply Lemma~\ref{usualGrass} to obtain the claim.
+  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$ induced by the decompositions $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$.
+  By Lemma~\ref{usualGrass}, this holds precisely when we have a decomposition 
+  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
+  which is equivalent to $U$ being liftable to the universal abelian covering.
 \end{proof}

### 2018-02-06 Grassmannian_cells.tex
Section 4 edits

@@
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
-We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
+We first consider a natural torus action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
 Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.
 
-Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
-We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{l-1}<r_l=n$ such that
-\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{l-1}+1},\ldots,v_{r_l}\in X_l.\]
-Moreover, we choose a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_j$ for some $j$.
-Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
-This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
-We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
+Given a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ and a map $d:\{1,\ldots,n\}\to\ZZ$, we get a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_r:=t^{d(r)}v_r$ for $r=1,\ldots,n$ to all of $X$.
+This naturally induces an action of $\C^\ast$ on the Grassmannian $\Gr_k(X)$.
+Our goal is to understand the fixed points of this action.
+
+For this recall that we can represent each subspace~$U\in\Gr_k(X)$ uniquely by a $k\times n$ matrix $M(U)$ whose rows provide a basis for $U$ when expanded as coefficient vectors in the basis $\mathcal B$.
+The uniqueness of $M(U)$ comes from requiring that it be in row-echelon form, i.e.\ there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
 \[M(U):=
@@
     \ast&\cdots &\ast&0&\ast&\cdots &\ast&0&\ast&\cdots&\ast&1&0&\cdots&0
-  \end{pmatrix}\in M_{k,n}(k),\]
+  \end{pmatrix}\in M_{k,n}(\CC),\]
 where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
-The set of all subspaces of $X$ represented by matrices of this fixed form define the \emph{Schubert cell} $X_\bfi$.
-The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.\ we have
-\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
-for $w=1,\ldots,n$.
-Every Schubert cell is invariant under the torus action, i.e.\ $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
+The set of all $U\in\Gr_k(X)$ represented by matrices of this fixed form gives the \emph{Schubert cell} $X_\bfi$.
+
+The $\C^\ast$-action on $U\in\Gr_k(X)$ can then be described in terms of the matrix representation $M(U)$, that is for $U\in X_\bfi$ we have
+\[M(t.U)_{qr}=t^{d(r)-d(i_q)} M(U)_{qr}\]
+for $q=1,\ldots,k$ and $r=1,\ldots,n$.
+Observe that each Schubert cell $X_\bfi$ is invariant under this torus action.
+
+Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
+\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
 \begin{lemma}
   \label{usualGrass}
-  Consider $d:\{1,\ldots,n\}\to\ZZ$ for which $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
-  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{j=1}^l U\cap X_j$.
-\end{lemma}
-\begin{proof}
-  If $U=\bigoplus_{j=1}^l U\cap X_j$, we have 
-  \[t.U=\bigoplus_{j=1}^l t.(U\cap X_j)=\bigoplus_{j=1}^l t^{d(r_j)}(U\cap X_j)=U.\]
-  Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
-  Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_w\in X_j$. 
-  As the matrix representation $M(U)$ is uniquely determined, the assumptions on $d$ imply that all matrix coefficients corresponding to a basis element $v_i$ with $v_i\notin X_j$ are zero.
-  This means that $\widehat{M(U)}_w\in X_j$, where~$\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
-  As the colums are linearly independent, this already shows the claim.
+  Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
+  Then under the $\CC^*$-action determined by $d$, we have $U\in\Gr_k(X)^{\C^\ast}$ if and only if $U=\bigoplus_{l=1}^m U\cap X_l$.
+\end{lemma}
+\begin{proof}
+  Assume $U=\bigoplus_{l=1}^m U\cap X_l$.
+  Then any $u\in U$ can be written uniquely as $u=\sum_{l=1}^m u_l$ for some $u_l\in U\cap X_l$.
+  It follows that $t.u=\sum_{l=1}^m t.u_l=\sum_{l=1}^m t^{d(r_l)}u_l\in\bigoplus_{l=1}^m U\cap X_l=U$ and thus $t.U=U$.
+
+  For the reverse direction, assume $U\in X_{\bfi}$ is a torus fixed point represented by the matrix $M(U)$.
+  Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
+  That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
 \end{proof}
@@
 \begin{proof}
-  For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_\}$.
+  For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_n\}$.
   Since $X$ is finite-dimensional and indecomposable, the support quiver $\mathrm{supp}(X)$ is a connected and finite subquiver of $\hat Q$.

### 2018-02-08 Grassmannian_cells.tex
Section 4 edits

@@
 \newcommand{\spn}{\operatorname{span}}
+\newcommand{\supp}{\operatorname{supp}}
 \setcounter{MaxMatrixCols}{20}
@@
 This naturally induces an action of $\C^\ast$ on the Grassmannian $\Gr_k(X)$.
-Our goal is to understand the fixed points of this action.
+Our goal is to understand the fixed points of such an action.
 
@@
 \begin{lemma}
-  \label{usualGrass}
+  \label{le:usualGrass}
   Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
@@
 In general, this does not induce a torus action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
-Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$. 
+Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
 \begin{lemma}
@@
 \begin{proof} 
-  Since $X$ can be lifted, for any arrow $\alpha\in Q_1$ we can write $X_\alpha:X_i\to X_j$ as a block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$ for $\chi\in A_Q$.
   Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
-  Then we can write $u_i=\sum_{\chi\in A_Q} u_{(i,\chi)}$ for some vectors $u_{(i,\chi)}\in U_i\cap X_{(i,\chi)}$.
-  But observe that for an arrow $\alpha:i\to j$ of $Q$, we have $X_\alpha(u_{(i,\chi)})=X_{(\alpha,\chi)}(u_{(i,\chi)})\in U_j\cap X_{(j,\chi+e_\alpha)}$, say $X_{(\alpha,\chi)}(u_{(i,\chi)})=u_{(j,\chi+e_\alpha)}$.
-  It follows that
+  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.
+
+  As $X$ can be lifted to $\hat Q$, for any arrow $\alpha\in Q_1$ we can write $X_\alpha:X_i\to X_j$ as a block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$ for $\chi\in A_Q$.
+  Then writing $u_i=\sum_{\chi\in A_Q} u_{(i,\chi)}$ for some vectors $u_{(i,\chi)}\in X_{(i,\chi)}$, we have $X_\alpha(u_{(i,\chi)})=X_{(\alpha,\chi)}(u_{(i,\chi)})\in X_{(j,\chi+e_\alpha)}$, say $X_{(\alpha,\chi)}(u_{(i,\chi)})=u_{(j,\chi+e_\alpha)}$.
+  It follows that $u_j=\sum_{\chi\in A_Q} u_{(j,\chi+e_\alpha)}$ and so
   \begin{align*}
-    X_\alpha(t.u_i)=\sum\limits_{\chi\in A_Q}X_{(\alpha,\chi)}(t.u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}X_{(\alpha,\chi)}(u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}\sum\limits_{\chi\in A_Q} t.u_{(j,\chi+e_\alpha)}
+    X_\alpha(t.u_i)
+    &=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}X_{(\alpha,\chi)}(u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}\sum\limits_{\chi\in A_Q} t.u_{(j,\chi+e_\alpha)}=t^{-c_\alpha} t.u_j.
   \end{align*}
-  and thus $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$.
-\end{proof}
-
-\begin{lemma}
-  \label{degreecondition} 
-  Let $X$ be an indecomposable representation of $\hat Q$.
-  There exists $d:\mathrm{supp}(X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
+  Therefore $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and we obtain a $\CC^*$-action on $\Gr_\bfe(X)$.
+\end{proof}
+
+The next result provides conditions required of the map $d:\hat Q_0\to\ZZ$ needed to get an analogue of Lemma~\ref{le:usualGrass}
+\begin{lemma}
+  \label{le:degree condition} 
+  Let $\hat X$ be an indecomposable representation of $\hat Q$.
+  There exists $d:\supp(X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
   \begin{enumerate}
-    \item for $(i,\chi),\,(i,\chi')\in\mathrm{supp}(X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
-    \item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
+    \item for $(i,\chi),\,(i,\chi')\in\supp(X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
+    \item for $(i,\chi),\,(j,\chi')\in\supp(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
   \end{enumerate}
@@
   For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_n\}$.
-  Since $X$ is finite-dimensional and indecomposable, the support quiver $\mathrm{supp}(X)$ is a connected and finite subquiver of $\hat Q$.
-  In order to prove the statement, we may assume that $(i,0)\in\mathrm{supp}(X)$ for some $i\in Q_0$.
-  Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(i,0)$ such that the underlying graph of the path has no cycles.
-  This implies that, for $(i',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.
+  Since $X$ is finite-dimensional and indecomposable, the support quiver $\supp(X)$ is a connected and finite subquiver of $\hat Q$.
+  In order to prove the statement, we may assume that $(i',0)\in\supp(X)$ for some $i'\in Q_0$.
+  Let $K$ be the maximal length of a path in $\supp(X)$ starting or ending in $(i',0)$ such that the underlying graph of the path has no cycles.
+  This implies that, for $(i,\chi)\in\supp(X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.
 
@@
   for $l=2,\ldots,n$.  
-
-  Let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i',\chi):=f(\chi)$ for $(i',\chi)\in\mathrm{supp}(X)$.
-  In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
-  \[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]
-
-  Now assume that $d(i',\chi)=d(i',\chi')$ for $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$ and $\chi'=\sum_{l=1}^n \kappa'_l e_{\alpha_l}$.
+  Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(X)$.
+  %In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
+  %\[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]
+
+  To check property (1), assume that $d(i,\chi)=d(i,\chi')$ for $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$ and $\chi'=\sum_{l=1}^n \kappa'_l e_{\alpha_l}$.
   This implies
@@
   But we have $|\kappa_l-\kappa'_l|\leq |\kappa_l|+|\kappa'_l|\le 2K$ and thus we obtain 
-  \[|\sum_{l=1}^{n-1}(\kappa_l-\kappa'_l)c_{\alpha_l}|\le 2K\sum_{l=1}^{n-1}c_{\alpha_l} < c_{\alpha_n}.\]
-  This inductively yields $\kappa_l=\kappa'_l$ for $l=n,\ldots,1$ by the choice of the $c_{\alpha_l}$.
-
-  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$.
-  Assume that $d(j,\chi')-d(i,\chi)=c_\alpha$.
-  Then we have $d(j,\chi')=d(j,\chi+e_\alpha)$.
-  An analogous proof as the one above shows that $\chi'=\chi+e_\alpha$.
-  Note that it is a priori possible that $(j,\chi+e_\alpha)\notin\mathrm{supp}(X)$.
-  Thus we chose $c_{\alpha_j}$ in such a way that it is greater than $2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}$. 
-\end{proof}
-
-In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{degreecondition}.
+  \[|\kappa'_n-\kappa_n|c_{\alpha_n}=\left|\sum_{l=1}^{n-1}(\kappa_l-\kappa'_l)c_{\alpha_l}\right|\le 2K\sum_{l=1}^{n-1}c_{\alpha_l} < c_{\alpha_n}.\]
+  This inductively yields $\kappa_l=\kappa'_l$ for $l=n,\ldots,1$ by the choice of the $c_{\alpha_l}$ and thus $\chi=\chi'$.
+
+  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ when $(j,\chi+e_\alpha)\in\supp(X)$.
+  Now assuming $d(j,\chi')-d(i,\chi)=c_\alpha$, an analogous argument to the one above shows that $\chi'=\chi+e_\alpha$.
+\end{proof}
+
+In the following, we say that $d:\supp(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
 \begin{theorem}
-  Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
+  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
   Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
@@
 \begin{proof}
-  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$, $t\in\C^\ast$.
-  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$ induced by the decompositions $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$.
-  By Lemma~\ref{usualGrass}, this holds precisely when we have a decomposition 
+  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
+  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
+  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
   \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
@@
 \end{proof}
-The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.
-to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
-Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
-Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree.
-Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
-If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$.
-We obtain:
+The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
+Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
+Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
+Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
+If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
 \begin{corollary}

### 2018-02-08 Grassmannian_cells.tex
minor changes in 3.1
In 3.13 we need that X is indecomposable

@@
 \label{sec:covering}
-
+\noindent
 We refer to \cite{gab} for an introduction to covering theory.
@@
   Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
-  \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
+Any lift of a preprojective (or preinjective) representation is preprojective (preinjective).
+ % \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
 \end{lemma}
@@
 to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
-  This gives the claim.
+  This gives both claims.
 \end{proof}
@@
 
-Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
+\noindent Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
 The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
@@
 We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
-For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
+For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
 \begin{proposition}
@@
   We need to show that $K$ has no preinjective direct summand.
-  As $\Hom(P_2,P_1)=0$, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
+  As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
   But this already shows that $K$ is indecomposable as $\udim K=(\dim H_1/V,1)$.
@@
 \label{sec:truncated preprojectives}
-Following Lemma~\ref{le:injective evaluation maps}, we define the following.
+Motivated by Lemma~\ref{le:injective evaluation maps}, we define the following.
 \begin{definition}
@@
   But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
-  The final claim follows from Remark~\ref{rem:reflection recursion}.
+  The final claim follows from Theorem ~\ref{th:rigids} which implies $\Ext(P_m,P_{m+1})=0$.
 \end{proof}
@@
   \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
   But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
@@
   Recall that $\Hom(X,P_\ell)\ne0$ (resp.
-$\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp.
+$\Ext(P_\ell,X)\ne0$) for some indecomposable representation $X$ and some $\ell\ge1$ implies that $X$ is preprojective of the form $P_r$ with $1\le r\le\ell$ (resp.
 $1\le r\le\ell-2$).
-  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+  However, $P_{m+1}^V$ is indecomposable by Corollary \ref{cor:indecomposable truncated} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
   %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.

### 2018-02-15 Grassmannian_cells.tex
added a comment
Minor edits

@@
 \newcommand{\cQ}{\mathcal{Q}}
+\newcommand{\Att}{\operatorname{Att}}
 \newcommand{\Ext}{\operatorname{Ext}}
@@
 
-\subsection{Bialynicki-Birula decomposition}
+\subsection{Torus Actions and the Bialynicki-Birula Decomposition}
 The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
@@
 For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]
+\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
 The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
-\begin{theorem}\label{thm:bb}
+\begin{theorem}
+  \label{thm:bb}
   \cite[Section 4]{bb}
-  Let $X^{\C^\ast}=\coprod_{i=1}^r C_i$ be the decomposition of the fixed point set of $X$ into connected components.
-  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ containing $C_i$ as a subvariety.
-  Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle. 
+  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is a vector bundle.
+  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
   In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
@@
 
-\subsection{Torus Actions}
+If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
+Indeed, we can trivialize each vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
+
+\subsection{Torus Actions on Quiver Grassmannians}
 \label{torusaction}
@@
 \subsection{$GL_n$ Action on Arrows of $K(n)$}
+The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
 We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
@@
   For $M\in\rep K(n)$, we have $\Sigma_2(M)=(M_1,M'_2,M'_{\alpha_i})$, where $M'_2$ fits into the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
+  \[\xymatrix@C30pt{0 \ar[r] & M_2 \ar[r]^(.4){\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^\pi & M'_2 \ar[r] & 0}\]
   and $M'_{\alpha_i}=\pi\circ\iota_i$ for $\iota_i:M_1\to\bigoplus_{i=1}^n M_1$ the inclusion of the $i$-th factor.
@@
   In particular, we may construct $g.\Sigma_2(M)$ using the following exact sequence:
-  \[\xymatrix{0 \ar[r] & M_2 \ar[r]^{g^{-T}\circ\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
+  \[\xymatrix@C50pt{0 \ar[r] & M_2 \ar[r]^(.45){g^{-T}\circ\bigoplus\limits_{i=1}^n M_{\alpha_i}} & \bigoplus\limits_{i=1}^n M_1 \ar[r]^{\pi\circ g^T} & M'_2 \ar[r] & 0},\]
   i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
@@
 \label{sec:fibrations}
-
 Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
@@
     \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
-    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $U\in\Phi_{m,I,j}^{-1}(V,0)$ for some $V\subset\tilde P_m(I,j)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
+    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
   \end{enumerate} 
@@
   For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
-  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yeilds $\Ext(Z,\tilde K_m)=0$.
+  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
   But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.

### 2018-02-17 Grassmannian_cells.tex
Hopefully addressed the comment.
Theorem 4.16 edits (mostly done)

@@
 \newcommand{\bfg}{\mathbf{g}}
+\newcommand{\bfh}{\mathbf{h}}
 \newcommand{\bfi}{\mathbf{i}}
 \newcommand{\bfI}{\mathbf{I}}
-\newcommand{\bfh}{\mathbf{h}}
+\newcommand{\bfJ}{\mathbf{J}}
 \newcommand{\tbfe}{{\tilde\bfe}}
@@
   For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
-  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge1$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
+  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge0$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
   \begin{enumerate}
-    \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
-    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=(I'_l)^c\cup I_{l+1}$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
+    \item if $k\ge1$, then $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
+    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=I_{l+1}\cup (I'_l)^c$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
   \end{enumerate}
-  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $I_k$.
-
-  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_0)=(I'_1)$.
+  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $(I'_k)^c$.
+  Given an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k\ge1$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$.
 \end{definition}
@@
       \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
-    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
+    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $0<k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
       For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
@@
         \label{dia:truncated coherence}
-        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
+        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I'_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
         \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
@@
 This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
-\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M).\]
-Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(V,W)=\mathbb{A}^{\dim\Hom(W,M/V)}$.
+\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto (V\cap M,(V+M)/M).\]
+Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.
 
@@
 For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
-\[\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}\]
+\begin{equation}
+  \label{eq:truncated ses}
+  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
+\end{equation}
 which induces a map between quiver Grassmannians as above:
-\[\Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).\]
+\begin{equation}
+  \label{eq:truncated CC}
+  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
+\end{equation}
 To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
@@
 Then in the same way as above we obtain the map
-\[\Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).\]
+\begin{equation}
+  \label{eq:truncated CC2}
+  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
+\end{equation}
 \begin{proposition}
@@
   \begin{enumerate}
-    \item For $V\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
-    \item If $V=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,V)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
-      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
+    \item For $W\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
+    \item If $W=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,W)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
+      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
   \end{enumerate}
@@
   But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
-  Thus we have $\Ext(V,\tilde P_{m,j}/U)=0$. 
-  If $U=0$, we have $\Ext(V,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
+  Thus we have $\Ext(W,\tilde P_{m,j}/U)=0$. 
+  If $U=0$, we have $\Ext(W,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
 
@@
   \label{cellscover}
-  For $m\geq 1$ and $I\subset\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
+  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
 \end{theorem}
 \begin{proof}
-
-In order to prove the claim, we prove the following more general statement:\\
-
+  We work by induction on $m$.
+  When $m=1$, the claim is trivial since all quiver Grassmannians are points in this case.
+  We establish the result for $m\ge2$ by proving the following more general statement:\\
+
+  \noindent{\bf Claim.}
+  For any proper subset $J\subsetneq\{1,\ldots,n\}$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces with the following property:
+  \begin{itemize}
+    \item[($\dagger$)] For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$ consider the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients}.
+      For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
+  \end{itemize}
+  \vs
+
+  In what follows, we will freely use the notation from Lemma~\ref{le:truncated quotients}.
+  We proceed by simultaneous induction on $m$ and reverse induction on $|J|$.
+  Fix an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$.
+
+  To begin, we assume $|J|=n-1$ and thus $J=I_0$.
+  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,i_0}^{J_0}$ and so by induction on $m$ the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)=\Gr^{\tilde Q}_\tbfe(\tilde P_{m,i_0}^{J_0})$ admits a decomposition into affine spaces so that the compatibility condition ($\dagger$) holds for the unique map $\pi_{m,i_0}^{J_0,\delta\bfI}:\tilde P_{m,i_0}^{J_0}\to\tilde P_{m,i_0}^{\delta\bfI}$.
+  But $\tilde P_{m,i_0}^{\delta\bfI}=\tilde P_{m+1}^\bfI$ so that $\pi_{m,i_0}^{J_0,\delta\bfI}$ coincides with the map $\pi_{m+1}^{J,\bfI}$ and thus the condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+
+  Now suppose $|J|<n-1$.
+  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
+  Thus we may assume $J\subsetneq I_0$.
+
+  Choose any subset $I\subsetneq\{1,\ldots,n\}$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
+  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
+  There are two cases to consider.
+
+  First suppose $I\subset I_0$.
+  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
+  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{k=1}^r C_k.\]
+
+  When $m=2$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ is just a point.
+  For $m\ge3$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ admits a decomposition into affine spaces which is compatible with the map $\pi_{m,j}^\bfJ:\tilde P_{m,j}\to\tilde P_{m-1,(j,j)}^I$, where $\bfJ=(\{1,\ldots,\widehat j,\ldots,n\},I)$, say
+  \[\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=\coprod_{\ell=1}^s B_\ell.\] 
+  For $m=2$, we write $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=B_1$.
+
+  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi_{m+1,I,j}$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
+  \begin{itemize}
+    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
+    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
+  \end{itemize}
+  Otherwise, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
+  But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+
+  It remains to consider the case $j\notin I_0$.
+
+\begin{comment}
 \noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$.
@@
 
-\begin{comment}
 We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
@@
 \item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq m-1$.
-Then every quiver Grassmannian $\Gr_{\tbfe}(X)$ has a cell decomposition into affine spaces.
+Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
 \end{enumerate}

### 2018-02-17 Grassmannian_cells.tex
Fixed Theorem 4.16

@@
   \noindent{\bf Claim.}
-  For any proper subset $J\subsetneq\{1,\ldots,n\}$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces with the following property:
+  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces which are compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
-    \item[($\dagger$)] For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$ consider the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients}.
-      For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
+    \item[($\dagger$)] For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
   \end{itemize}
@@
 
-  Choose any subset $I\subsetneq\{1,\ldots,n\}$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
+  Choose any subset $I\subset I_0$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
   This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
-  There are two cases to consider.
-
-  First suppose $I\subset I_0$.
   Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
@@
   \end{itemize}
-  Otherwise, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  When the fibers of $\Psi_{m+1,I,j}$ are not empty, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
   For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
   But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
-
-  It remains to consider the case $j\notin I_0$.
-
 \begin{comment}

### 2018-02-18 Grassmannian_cells.tex
Minor edit

@@
 \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
-\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq m-1$.
+\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
 Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.

### 2018-02-18 Grassmannian_cells.tex
Some clean-up and reorganization in 3.1, more polishing needed

@@
 Any lift of a preprojective (or preinjective) representation is preprojective (preinjective).
- % \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
 \end{lemma}
@@
 As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
-\sayD{Specific reference needed?}
 \begin{theorem}
@@
 \end{remark}
-We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
-For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
-\begin{proposition}
-  \label{pro:indecomposables}
-  Let $m\geq 1$ and $0\le r\le n-1$.
-  The following hold:
-  \begin{enumerate}
-    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
-    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
-  \end{enumerate}
-\end{proposition}
-\begin{proof}
-  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
-  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
-  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
-  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
-  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.
-
-  This shows that the indecomposable representations in $R_{(l,1)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
-  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$l$ spanned by the row vectors of the corresponding matrix $M_X$.
-  Now it is straightforward to check that the $\GL_{d(m,r)}=\GL_l(\CC)\times\CC^\ast$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\GL_l(\CC)$ on the set of these subspaces.
-  This shows the first statement.
-
-  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
-  Thus the roots $d(m,r)$ are also Schur roots.
-  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
-  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
-  This shows the second statement.
-\end{proof}
-\begin{remark}
-  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
-  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
-  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
-\end{remark}
 
@@
 
+We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
+For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
+\begin{proposition}
+  \label{pro:indecomposables}
+  Let $m\geq 1$ and $0\le r\le n-1$.
+  The following hold:
+  \begin{enumerate}
+    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
+    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
+  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
+  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
+  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
+  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.
+
+  This shows that the indecomposable representations in $R_{(l,1)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
+  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$l$ spanned by the row vectors of the corresponding matrix $M_X$.
+  Now it is straightforward to check that the $\GL_{d(m,r)}=\GL_l(\CC)\times\CC^\ast$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\GL_l(\CC)$ on the set of these subspaces.
+  This shows the first statement.
+
+  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
+  Thus the roots $d(m,r)$ are also Schur roots.
+  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
+  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
+  This shows the second statement.
+\end{proof}
+\begin{remark}
+  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
+  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
+  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
+\end{remark}
+
 \begin{lemma}
@@
   Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{proof}
-
-Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
-Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
-The next observation is essential for the results to follow.
-\begin{proposition}
-  For $V\in \Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
-\end{proposition}
-\begin{proof}
-  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
-  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
-  Indeed, we have
-  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated extensions}
-  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
-  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
-where $U\subset V$ satisfies $\dim(V/U)=1$.
-\end{lemma}
-\begin{proof}
-  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
-  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
-  This gives rise to the following commutative diagram:
-  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
-    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
-    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
-    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
-   & 0 & 0 & & }\]
-  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
-  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
-  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
-\end{proof}
-
-\begin{corollary}\sayT{proof?}
-  For $V,W\in \Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
-\end{corollary}
-
-\begin{lemma}
-  \label{le:more truncated homomorphisms}
-  For $W\in \Gr(H_m)$, $m\ge2$, the following hold:
-  \begin{enumerate}
-    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
-    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  By Lemma~\ref{le:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
-  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
-  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]
-
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:unique preprojective morphism}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
-\end{proof}
-\begin{remark}
-  For $W\in \Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
-  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
-\end{remark}
-\begin{corollary}
-  For $V,W\in \Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
-  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
-\end{corollary}
-\begin{proof}
-  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
-  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
-  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
-  The result immediately follows from this.
-\end{proof}
-\begin{remark}
-  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
-\end{remark}
-
-\begin{lemma}\sayT{proof? Special case of 3.23?}
-  For $V,W\in \Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
-\end{lemma}
-
-\begin{lemma}
-  For $m\ge2$ and $V\in \Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.
-More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
-\end{lemma}
-\begin{proof}
-  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
-  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
-  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
-  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
-  This proves the first claim.
-
-  It remains to show that $\tilde V=\bar{\bar{V}}$.
-\end{proof}
-
-\begin{lemma}
-  \label{le:truncated exact sequences}
-  For $V\in \Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
-\end{lemma}
-\begin{proof}
-  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
-  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
-    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
-    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
-    & & 0 & 0 & }\]
-  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
-  It follows that the sequence
-  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
-  is exact.
-  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.
-
-  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
-\end{proof}
-
-\sayD{The next result needs some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
-\begin{lemma}
-  For $V\in \Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  This occurs (?) if and only if the composed morphism
-  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
-  is nonzero.
-\end{lemma}
-\begin{proof}
-  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
-  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
-    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
-    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
-  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
-  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
-    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
-  if and only if the lower pushout sequence below splits: 
-  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
-  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
-  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.
-
-  and
-  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
 \end{proof}

### 2018-02-21 Grassmannian_cells.tex
Intro

@@
 
+A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrize subrepresentations of a fixed dimension.
+Throughout the last years, quiver Grassmannians became of growing interest.
+On the one hand, this is due to the fact that the generating functions of the Euler characteristics of quiver Grassmannians of exceptional representations can be found as cluster variables.
+On the other hand, they are clearly interesting on their own as they reveal many properties of the representation and its geometry.
+Even if it turned out that every projective variety can be realized as a quiver Grassmannian - which is maybe not surprising as the classification problem of indecomposable quiver representations is wild - it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
+For instance quiver Grassmannians attached to exceptional representations  are smooth.
+For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces.
+It is also conjectured that this is true for exceptional representations, i.e.
+particularly for preprojective and preinjective representations.
+
+There are basically two possible ways to find cell decompositions of quiver Grassmannians if they exist.
+One is to find a non-trivial torus action on the quiver Grassmannian under consideration.
+If it is additionally smooth, one can apply a result of Bialynicki-Birula which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
+In particular, this shows that the quiver Grassmannian has a cell decomposition if the fixed point components do have it.
+Another method is to consider short exact sequences of quiver representations which induce a map between the quiver Grassmannians of the middle term and products of quiver Grassmannians of the outer terms.
+This map is also known as Caldero-Chapoton map.
+If this sequence has certain properties - e.g.
+(almost) split and generalizations - cell decompositions of quiver Grassmannians attached to the outer terms transfer to a decomposition of quiver Grassmannians of the middle term.
+
+In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition into affine spaces.
+The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
+It turns out that these are precisely those representations which can be obtained from indecomposable representations of dimension $(d,1)$ when applying reflection functors.
+Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the dimension vector of the subrepresentations.
+
+As a first step, we show that a torus action with a proper fixed point set can be defined on every quiver Grassmannian attached to representations of any quiver with multiple arrows or non-oriented cycles which can be lifted to the universal (abelian) covering quiver.
+These are precisely those cases where the universal covering quiver differs from the original quiver.
+This lifting property holds particularly for so-called tree modules which include all exceptional representations.
+The fixed point set consists precisely of those subrepresentations which can also be lifted to the universal (abelian) covering quiver.
+Actually, it turns out that each fixed point component is itself a quiver Grassmannians attached to the lifted representation.
+
+The next step is to investigate under which conditions the fixed point components admit a cell decomposition.
+Here the Caldero-Chapoton map comes into play.
+In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
+These filtration can be successively described by short exact sequences.
+The main advantage when passing to the universal covering is that the preprojective subrepresentations of the same dimension become orthogonal which rigidifies the situation in a sense.
+In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
+As all the quiver Grassmannians of the (non-lifted) representation are smooth this gives rise to a cell decomposition of these quiver Grassmannians.
+
+As a benefit (?) of this construction, we obtain a graph theoretical description of the non-empty cells.
+More precisely, with every (truncated) preprojective representation we can associate a so-called $2$-quiver.
+Basically, such a quiver is obtained from a usual quiver when adding so-called $2$-arrows which connect fixed subquivers.
+Now with every subset of the vertices we can associate a dimension vector.
+If this subset is also strong successor closed, which is in fact a condition to be checked easily, it corresponds to a cell and vice versa.
+The upshot is that we get a one-to-one correspondence between these subsets and compatible pairs of the respective Dyck path which leads to a geometric explanation for the Dyck path combinatorics appearing in the theory of quiver Grassmannians.
+
+\sayT{references need to be included}
+
 -something about compatible pairs and combinatorial construction of cluster variables\\

### 2018-02-21 Grassmannian_cells.tex
Intro edits

--- 2018-02-18 Grassmannian_cells.tex
@@
 \section{Introduction}
-A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion \cite{fomin-zelevinsky}.
-Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
-These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
-
+
+A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension.
+In recent years, interest in quiver Grassmannians has grown considerably.
+On the one hand, this is due to the fact that generating functions for the Euler characteristics of quiver Grassmannians of exceptional representations can be found as cluster variables.
+On the other hand, they are clearly interesting on their own as they reveal many properties of the representation and its geometry.
+Although it has been shown that every projective variety can be realized as a quiver Grassmannian -- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
+For instance quiver Grassmannians attached to exceptional representations are smooth.
+For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces.
+It is conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
+
+There are basically two possible ways to find cell decompositions of quiver Grassmannians if they exist.
+One is to find a non-trivial torus action on the quiver Grassmannian under consideration.
+If the quiver Grassmannian is smooth, one can apply a result of Bialynicki-Birula which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
+In particular, this shows that the quiver Grassmannian has a cell decomposition if the fixed point components have such a decomposition.
+
+Another method uses short exact sequences of quiver representations to induce maps between quiver Grassmannians.
+More precisely, the quiver Grassmannian of the middle term maps to the product of quiver Grassmannians of the outer terms via the ``Caldero-Chapoton map''. 
+If the short exact sequence has certain properties -- e.g.
+(almost) split sequences and certain generalizations -- then cell decompositions of quiver Grassmannians attached to the outer terms transfer to a decomposition of the quiver Grassmannians of the middle term.
+
+In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition into affine spaces.
+The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
+It turns out that these are precisely those representations which can be obtained from indecomposable representations of dimension $(d,1)$ when applying reflection functors.
+Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the dimension vector of the subrepresentations.
+
+As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to liftable representations of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
+These are precisely those cases where the universal covering quiver differs from the original quiver.
+This lifting property holds in particular for so-called tree modules, a class of representations which includes all exceptional representations.
+The fixed point set of this torus action consists precisely of those subrepresentations which can also be lifted to the universal (abelian) covering quiver.
+Actually, it turns out that each fixed point component is itself a quiver Grassmannian attached to the lifted representation.
+
+The next step is to investigate conditions under which the fixed point components admit a cell decomposition.
+Here the Caldero-Chapoton map comes into play.
+In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
+These filtration can be successively described by short exact sequences.
+The main advantage when passing to the universal covering is that the preprojective subrepresentations of the same dimension become orthogonal, a property which rigidifies the situation in a sense.
+In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
+As all the quiver Grassmannians of the (non-lifted) representation are smooth this gives rise to a cell decomposition of these quiver Grassmannians.
+
+As a benefit of this construction, we obtain a graph theoretic description of the non-empty cells.
+More precisely, with every (truncated) preprojective representation we can associate a so-called $2$-quiver.
+Essentially, such a quiver is obtained from a usual quiver by adding a collection of ``$2$-arrows'' between pairs of subquivers.
+Now with every subset of the vertices we can associate a dimension vector.
+If this subset is also strong successor closed, a condition which is easily verified in paractice, it corresponds to a cell and vice versa.
+
+As mentioned above, the Laurent polynomial expressions for cluster variables have been described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
 For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{lee-li-zelevinsky}.
 The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
-Our main result is a geometric explanation for this correspondence by constructing a decomposition of these quiver Grassmannians into affine cells which are labeled by compatible pairs.
+A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.
+
+\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
+
+\sayT{references need to be included}
 

### 2018-02-22 Grassmannian_cells.tex
Abstract

@@
 \begin{abstract}
-  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
+  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
   In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
-  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established as well as for all indecomposable representations in their Auslander-Reiten components.
-  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
+  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established. 
+  We also provide two natural combinatorial labelings for these cells.
+On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
+On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a preprojective representation.
+As there is a natural bijection between these two labelings this gives also a geometric explanation for the Dyck path combinatorics appearing in the theory of quiver Grassmannians.
 \end{abstract}
@@
 \section{Introduction}
-
-A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension.
+\noindent A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension.
 In recent years, interest in quiver Grassmannians has grown considerably.
@@
 Now with every subset of the vertices we can associate a dimension vector.
-If this subset is also strong successor closed, a condition which is easily verified in paractice, it corresponds to a cell and vice versa.
+If this subset is also strong successor closed, a condition which is easily verified in practice, it corresponds to a cell and vice versa.
 
@@
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
-Write $\rep Q$ for the hereditary abelian category of $\C$-representations of $Q$.
+We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$ and we assume in the following that all representations are finite-dimensional.\sayT{Inserted finite-dimensional as we do not need infite-dimensional one (I am also not sure if we need to be careful at some points otherwise)}
 

### 2018-02-22 Grassmannian_cells.tex
added some references in the introduction

@@
 In recent years, interest in quiver Grassmannians has grown considerably.
-On the one hand, this is due to the fact that generating functions for the Euler characteristics of quiver Grassmannians of exceptional representations can be found as cluster variables.
+On the one hand, this is due to the fact that generating functions for the Euler characteristics of quiver Grassmannians of exceptional representations can be found as cluster variables \cite{ck}.
 On the other hand, they are clearly interesting on their own as they reveal many properties of the representation and its geometry.
-Although it has been shown that every projective variety can be realized as a quiver Grassmannian -- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
-For instance quiver Grassmannians attached to exceptional representations are smooth.
-For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces.
+Although it has been shown by various authors that every projective variety can be realized as a quiver Grassmannian -- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
+For instance quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
+For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
 It is conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
@@
 One is to find a non-trivial torus action on the quiver Grassmannian under consideration.
-If the quiver Grassmannian is smooth, one can apply a result of Bialynicki-Birula which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
+If the quiver Grassmannian is smooth, one can apply a result of Bialynicki-Birula \cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
 In particular, this shows that the quiver Grassmannian has a cell decomposition if the fixed point components have such a decomposition.
@@
 Another method uses short exact sequences of quiver representations to induce maps between quiver Grassmannians.
-More precisely, the quiver Grassmannian of the middle term maps to the product of quiver Grassmannians of the outer terms via the ``Caldero-Chapoton map''. 
+More precisely, the quiver Grassmannian of the middle term maps to the product of quiver Grassmannians of the outer terms via the ``Caldero-Chapoton map'' which first appeared in \cite{cc}. 
 If the short exact sequence has certain properties -- e.g.
@@
 
+\sayT{references to be unified}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   P. Caldero, B. Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
-\bibitem{cefr} Cerulli Irelli, Esposito, Franzen, Reineke: Topology of Quiver Grassmannians. Preprint 2017.
+\bibitem{ce} Cerulli Irelli, G., Esposito, F.: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory, 5(6), 777-801.
+\bibitem{cefr} Cerulli Irelli, G., Esposito, F., Franzen, H., Reineke, M.: Topology of Quiver Grassmannians. Preprint 2017.
 \bibitem{cr}
@@
 Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
-\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
-
+%\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
 \bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
@@
 \bibitem{llz} K. Lee, L. Li, A. Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
+\bibitem{lw} Lorscheid, O., Weist, T.: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
 \bibitem{rin1} Claus Michael Ringel. Exceptional modules are tree modules. \textit{Linear algebra and its Applications}, 275/276:471-493, 1998.

### 2018-02-22 Grassmannian_cells.tex
eliminated some warnings and overfull hboxes

@@
 \usepackage{tikz}
-\usepackage{pgflibraryarrows}
-\usepackage{pgflibrarysnakes}
+%\usepackage{pgflibraryarrows}
+%\usepackage{pgflibrarysnakes}
 \usetikzlibrary{fit}
@@
 \newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
-\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
+\newcommand{\ses}[3]{\xymatrix@C15pt{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
 \newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
@@
 
-As mentioned above, the Laurent polynomial expressions for cluster variables have been described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
-For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{lee-li-zelevinsky}.
+As mentioned above, the Laurent polynomial expressions for cluster variables have been described using the representation theory of quivers \cite{cc,ck}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
+For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{llz}.
 The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
 A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.
-
 \sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
-
-\sayT{references need to be included}
-
 -something about compatible pairs and combinatorial construction of cluster variables\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Representation Theory of $K(n)$}
+\section{Representation Theory of Generalized Kronecker Quivers}
 \label{sec:RepK(n)}
@@
 
-\subsection{Lifting to $\widetilde{K(n)}$}
+\subsection{Lifting to \texorpdfstring{$\mathbf{\widetilde{K(n)}}$}{K(n)}}
 \label{Lifting}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$GL_n$ Action on Arrows of $K(n)$}
+\subsection{\texorpdfstring{$\mathbf{GL_n}$}{Gln}-Action on Arrows of \texorpdfstring{$\mathbf{K(n)}$}{K(n)}}
 The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
@@
 
-\subsection{$2$-Quivers}
+\subsection{2-Quivers}
 
@@
 \end{align}
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
+This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
 In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
@@
 
-\begin{tikzpicture}[scale=1.4]
+\begin{tikzpicture}[scale=1.35]
 \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
@@
 \\
-
-\begin{tikzpicture}
+\begin{flushleft}
+\begin{tikzpicture}[scale=0.97]
 \draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
@@
 \\
-
+\end{flushleft}
 \noindent 
@@
 
-The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{lee-li-zelevinsky} and the categorification of these variables using representations of $K(n)$ \cite{cc,caldero-keller}.
-\begin{theorem}\cite{lee-li-zelevinsky}
+The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{llz} and the categorification of these variables using representations of $K(n)$ \cite{cc,ck}.
+\begin{theorem}\cite{llz}
   For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
@@
 
-Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
+Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~ ?%\ref{???}.
 

### 2018-02-24 Grassmannian_cells.tex
Minor intro edits, standardizing names in bibliography

@@
   On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a preprojective representation.
-As there is a natural bijection between these two labelings this gives also a geometric explanation for the Dyck path combinatorics appearing in the theory of quiver Grassmannians.
+  As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
 \end{abstract}
@@
 On the other hand, they are clearly interesting on their own as they reveal many properties of the representation and its geometry.
+
 Although it has been shown by various authors that every projective variety can be realized as a quiver Grassmannian -- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
-For instance quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
+For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
 For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
-It is conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
+It has been conjectured\sayD{reference?} that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
 
@@
 One is to find a non-trivial torus action on the quiver Grassmannian under consideration.
-If the quiver Grassmannian is smooth, one can apply a result of Bialynicki-Birula \cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
+If the quiver Grassmannian is smooth, one can apply a result of Bia\l{}ynicki-Birula \cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
 In particular, this shows that the quiver Grassmannian has a cell decomposition if the fixed point components have such a decomposition.
@@
 Another method uses short exact sequences of quiver representations to induce maps between quiver Grassmannians.
-More precisely, the quiver Grassmannian of the middle term maps to the product of quiver Grassmannians of the outer terms via the ``Caldero-Chapoton map'' which first appeared in \cite{cc}. 
+More precisely, the quiver Grassmannian of the middle term maps to the product of the quiver Grassmannians for the two outer terms via the ``Caldero-Chapoton map'' which first appeared in \cite{cc}. 
 If the short exact sequence has certain properties -- e.g.
@@
 It turns out that these are precisely those representations which can be obtained from indecomposable representations of dimension $(d,1)$ when applying reflection functors.
-Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the dimension vector of the subrepresentations.
+Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
 
@@
 In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
-As all the quiver Grassmannians of the (non-lifted) representation are smooth this gives rise to a cell decomposition of these quiver Grassmannians.
+As all the quiver Grassmannians of the (non-lifted) representation are smooth, this combines with the torus action to give a cell decomposition of these quiver Grassmannians.
 
@@
 \sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
+
 -something about compatible pairs and combinatorial construction of cluster variables\\
@@
 
-\subsection{Torus Actions and the Bialynicki-Birula Decomposition}
+\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}
 The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
-If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
+If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
 More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
@@
 \[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
-The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
+The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
 \begin{theorem}
@@
 The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section \ref{sec:fibrations}.
-The second is the notion of compatible pairs in a maximal Dyck path.
-We give a bijection between these which provides a partial answer to a question of the first author.
+The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
+We give a bijection between these which provides a partial answer to a question of the first author \cite{rupel}.
 
@@
 \begin{thebibliography}{10}
+
 \bibitem{ass} 
-Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
-\bibitem{ars} Auslander, M., Reiten, I., Smalo S.O.: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
-\bibitem{bb} Bialynicki-Birula, A.: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
+  I.~Assem, D.~Simson, A.~Skowronski: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
+\bibitem{ars} 
+  M.~Auslander, I.~Reiten, S.~O.~Smalo: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
+\bibitem{bb} 
+  A.~Bia\l{}ynicki-Birula: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
 \bibitem{bgp} 
-Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
-\bibitem{brenner-butler} S. Benner, M.~C.~R. Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
-\bibitem{cc} P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
-Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+  I.~N.~Bernstein, I.~M.~Gelfand, V.~A.~Ponomarev: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+\bibitem{brenner-butler} 
+  S.~Benner, M.~C.~R.~Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
+\bibitem{cc} 
+  P.~Caldero, F.~Chapoton: Cluster algebras as {H}all algebras of quiver representations. Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
 \bibitem{ck} 
-  P. Caldero, B. Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
-\bibitem{ce} Cerulli Irelli, G., Esposito, F.: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory, 5(6), 777-801.
-\bibitem{cefr} Cerulli Irelli, G., Esposito, F., Franzen, H., Reineke, M.: Topology of Quiver Grassmannians. Preprint 2017.
+  P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
+\bibitem{ce} 
+  G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory, 5(6), 777-801.
+\bibitem{cefr} 
+  G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2017.
 \bibitem{cr} 
-Caldero, P., Reineke, M.: On the quiver Grassmannian in the acyclic case.
-Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
+  P.~Caldero, M.~Reineke: On the quiver Grassmannian in the acyclic case. Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
 %\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
-\bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
-\bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
-\bibitem{llz} K. Lee, L. Li, A. Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
-\bibitem{lw} Lorscheid, O., Weist, T.: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
-\bibitem{rin1} Claus Michael Ringel. Exceptional modules are tree modules. \textit{Linear algebra and its Applications}, 275/276:471-493, 1998.
-\bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
+\bibitem{gab} 
+  P.~Gabriel: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
+\bibitem{hr} 
+  D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
+\bibitem{llz} 
+  K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
+\bibitem{lw} 
+  O.~Lorscheid, T.~Weist: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
+\bibitem{rin1} 
+  C.~M.~Ringel. Exceptional modules are tree modules. \textit{Linear algebra and its Applications}, 275/276:471-493, 1998.
+\bibitem{rin} 
+  C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
 %\bibitem{mats} Matsumura, H.: Commutative ring theory. 
-\bibitem{rupel} Rupel, D.: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
-
-\bibitem{sch} Schofield, A.: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
-	\bibitem{wei} Weist, T.: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
-	\bibitem{wei2} Weist, T.: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
+\bibitem{rupel} 
+  D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
+\bibitem{sch} 
+  A.~Schofield: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
+\bibitem{wei} 
+  T.~Weist: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
+\bibitem{wei2} 
+  T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
 %\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).

### 2018-02-24 Grassmannian_cells.tex
Minor edit

@@
 This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
+In view of Lemma \ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
 %In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.

### 2018-02-24 Grassmannian_cells.tex
changes in 3.1

--- 2018-02-24 Grassmannian_cells.tex
@@
 we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.
+In the following, we write $\Hom$ (resp.
+$\Ext$) instead of $\Hom_Q$ (resp.
+$\Ext_Q$).
+As usual, we call a representation $X$ \emph{rigid} if $\Ext(X,X)=0$ and \emph{exceptional} if it is also indecomposable.
 
@@
   \label{th:rigids}
-  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
+  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp.
+$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0 $(resp.
+$\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
   Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
+
 \end{theorem}
@@
 \begin{proof}
-  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
+  As $P_m$ is exceptional, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
   \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
-  and a surjective map
-  \[\Ext(P_m,P_{m+1})\onto\Ext(P_m,P_{m+1}^V).\]
+  and an isomorphism
+  \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
   But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
@@
 \begin{proof}
-  Applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism 
+ As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain isomorphisms 
   \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
-  and a surjective map
-  \[\Ext(P_{m+1},P_{m+1})\onto\Ext(P_{m+1},P_{m+1}^V).\]
+  and 
+  \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
   The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
@@
 \end{remark}
-
-\begin{corollary}
-  \label{cor:indecomposable truncated} 
-  For $V\in \Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
-  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
-\end{proof}
-
-We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
+For the truncated preprojective representations $P_{m+1}^V$, we have  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
+They will play an important role when describing quiver Grassmannians of preprojective representations recursively.
 For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
@@
 
-  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
-  Thus the roots $d(m,r)$ are also Schur roots.
-  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
-  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
+By Lemma \ref{le:unique morphisms} the roots $d(m,r)$ are Schur roots as there exist representations with trivial endomorphism ring.
+%  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
+  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
   This shows the second statement.
@@
   There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
-  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
+  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
   We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
 \end{remark}
+
+\begin{corollary}
+  \label{cor:indecomposable truncated} 
+  For $V\in \Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
+  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
+\end{corollary}
+\begin{proof}
+  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
+\end{proof}
 
@@
 
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
   Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
@@
 \begin{proof}
-  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence
+  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives $P_r$ with $1\leq r\leq m$, the upper pullback sequence
   \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
@@
   We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
-  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.\sayT{more details?}
+  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
 \end{remark}

### 2018-02-25 Grassmannian_cells.tex
Section 5 edits

@@
   Let $Q=(Q_0,Q_1)$ be a quiver.
-  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $\alpha:p\to q$ in $Q_1$ implies $q\in\beta$.
+  A subset $\beta\subset Q_0$ is \emph{successor closed in $Q$} if for each $p\in\beta$, the existence of an arrow $\alpha:p\to q$ in $Q_1$ implies $q\in\beta$.
 
@@
   A \emph{2-quiver} is a pair $\tilde Q=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
-  Given a 2-quiver $\tilde Q$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed} if it is successor closed and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
-
+  Given a 2-quiver $\tilde Q$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\tilde Q$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
 \end{definition}
+
 We introduce a notion of equivalence of $2$-quivers.
-\begin{definition}\label{def:2equivalence}
-Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that one of the following conditions is satisfied:
+\begin{definition}
+  \label{def:2equivalence}
+  Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
   \begin{enumerate}
@@
     \item $\Gamma(2)$ has precisely one sink $q$;
-\item $\Gamma(1)$ has precisely one source $p$ and $\Gamma(2)$ has precisely one sink $q$.
+    \item $\Gamma(1)=\{p\}$ and $\Gamma(2)=\{q\}$.
   \end{enumerate}
@@
   \begin{enumerate}
-\item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a $2$-arrow $V_p:p\to\Gamma(2)$;
-\item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a $2$-arrow $V_q:\Gamma(1)\to q$;
-\item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by an usual arrow $\alpha_V:p\to q$. 
+    \item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
+    \item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
+    \item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
   \end{enumerate}
-
   This defines a relation on the set of $2$-quivers denoted by $\tilde Q\to \tilde Q_p$, $\tilde Q\to \tilde Q_q$ and $\tilde Q\to \tilde Q_V$ respectively.
@@
 \end{definition}
-Observe that the set of vertices of two equivalent $2$-quivers coincide.
-
-\begin{lemma}\label{lem:2equivalence}
-Let $\tilde Q=(Q,Q_2)$ and $\tilde Q'=(Q',Q_2')$ be two equivalent $2$-quivers.
-If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
-In particular, the number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
-\end{lemma}
-\begin{proof}
-For the proof of this Lemma the following straightforward observation is essential: in a finite connected quiver, which is a tree and which has precisely one source $p$, all arrows are pointing away from $p$ or equivalently there exists a path from $p$ to every vertex of the quiver.
-The analogous statement holds if a quiver has precisely one sink.
-
-We may assume that $\tilde Q'\in\{\tilde Q_p,\tilde Q_q,\tilde Q_V\}$ and one of the conditions of Definition \ref{def:2equivalence} is satisfied.
-We again denote the unique source of $\Gamma(1)$ by $p$, the unique sink of $\Gamma(2)$ by $q$ and the new arrow by $\alpha_V:p\to q$.
-We only consider the case $\tilde Q'=\tilde Q_V=(Q_V,(Q_V)_2)$, the other two cases follow by the same arguments.
-
-Let $\beta\subset Q_0$ be a strong successor closed subset. We need to show that it defines a strong successor closed subset of $(Q_V)_0$.
-Let $V':\Gamma'(1)\to\Gamma'(2)\in (Q_V)_2$ be a  $2$-arrow. Then it is also a $2$-arrow of $\tilde Q$. This means that  we have $\Gamma'(2)_0\cap \beta\neq\varnothing$ if $\Gamma'(1)_0\subset \beta$.
-
-Let $\alpha:i\to j\in (Q_V)_1$.
-If $\alpha\neq\alpha_V$, we have $j\in \beta$ if $i\in\beta$ as $\beta$ is successor closed as a subset of $ Q_0$.
-Thus assume that $\alpha=\alpha_V$.
-We need to show that $q\in\beta$ if $p\in\beta$.
-If $p\in\beta$, we have $\beta\subset\Gamma(1)_0$ because $\beta$ is successor closed and $p$ is the unique source of $\Gamma(1)$ which means that, for every vertex $q'\in\Gamma(1)_0$, there exists a path from $p$ to $q'$.
-In particular, we have $q'\in\beta$ for all $q'\in\Gamma(1)_0$ because $\beta\subset Q_0$ is successor closed.
-It follows that, as $\beta$ is strong successor closed, there exists a vertex $p'\in\Gamma(2)_0\cap\beta$.
-But then we have $q\in\beta$ as, by the same argument, there exists a path from $p'$ to $q$ if $p'\neq q$.
-Thus $\beta$ is strong successor closed as a subset of $(Q_V)_0$.
-
-Thus assume that $\beta\subset (Q_V)_0$ is strong successor closed.
-The cases of arrows $\alpha\in Q_1$ and $2$-arrows $V'\neq V$ can be treated as before.
-Thus consider the $2$-arrow $V$ and the arrow $\alpha_V$.
-Assume that $\Gamma(1)_0\subset\beta$.
-Then we have $p\in\beta$.
-But then we have $q\in\beta$ as $\alpha_V:p\to q$ and $\beta$ is successor closed as a subset of $(Q_V)_0$.
-It follows that $\Gamma(2)_0\cap\beta\neq\varnothing$.
+
+Observe that the vertex sets of equivalent $2$-quivers coincide.
+\begin{lemma}
+  \label{lem:2equivalence}
+  Let $\tilde Q=(Q,Q_2)$ and $\tilde Q'=(Q',Q_2')$ be equivalent $2$-quivers.
+  If $\beta\subset Q_0$ is strong successor closed in $\tilde Q$, it also defines a strong successor closed set of vertices in $\tilde Q$.
+  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\tilde Q$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\tilde Q'$.
+\end{lemma}
+
+For the proof of this Lemma the following straightforward observation is essential: in a finite connected quiver which has precisely one source $p$, there exists a path from $p$ to every other vertex of the quiver.
+An analogous statement holds if a quiver has precisely one sink.
+
+\begin{proof}
+  By induction, we only need to consider the cases $\tilde Q'\in\{\tilde Q_p,\tilde Q_q,\tilde Q_V\}$ where one of the conditions of Definition~\ref{def:2equivalence} is satisfied.
+
+  Assume first that $\tilde Q'\in\{\tilde Q_p,\tilde Q_q\}$.
+  Then we have $Q=Q'$ from which we immediately see that $\beta\subset Q_0$ is successor closed in $Q$ if and only if $\beta$ is successor closed in $Q'$.
+  We only consider the case $\tilde Q'=\tilde Q_p$ below, the argument for $\tilde Q'=\tilde Q_q$ is dual.
+
+  Let $\beta\subset Q_0$ be strong successor closed in $\tilde Q$.
+  To see that $\beta$ is strong successor closed in $\tilde Q_p$ it suffices to consider the 2-arrow $V_p:\{p\}\to\Gamma(2)$.
+  Suppose $\{p\}\subset\beta$.
+  As $\beta$ is successor closed in $Q$ and $p$ is a source in the connected quiver $\Gamma(1)$, we have $\Gamma(1)_0\subset\beta$ and thus $\Gamma(2)_0\cap\beta\ne\varnothing$, i.e.\ $\beta$ is strong successor closed in $\tilde Q_p$.
+  The reverse implication is immediate since $\{p\}\subset\Gamma(1)_0$.
+
+  Now assume $\tilde Q'=\tilde Q_V=\big(Q_V,(Q_V)_2\big)$. 
+  Let $\beta\subset Q_0$ be strong successor closed in $\tilde Q$.
+  Since $(Q_V)_2\subset Q_2$, to see that $\beta$ is strong successor closed in $\tilde Q_V$ we only need to show that $\beta$ is successor closed in $Q_V$.  
+  For this it suffices to consider the arrow $\alpha_V:p\to q$ for which that claim is obvious since $p\in\beta$ is equivalent to $\{p\}\subset\beta$ and similarly for $q$.
+
+  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\tilde Q_V$.
+  Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
+  To see that $\beta$ is strong successor closed in $\tilde Q$, it suffices to consider the 2-arrow $V:\{p\}\to\{q\}$ for which the claim is obvious as above.
 \end{proof}
@@
 %Hence the corresponding Euler characteristic can be computed when counting these subsets.
-%It will turn out that a feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.
+%It will turn out that a feature of this description is that it does not take care of the coloring of the different arrows induced by the arrows of $K(n)$.
 
@@
 \noindent
-where the $2$-arrows are coloured red.
+where the $2$-arrows are colored red.
 Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
@@
 \noindent In abuse of notation, we did not label the vertices in the illustration.
-Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again coloured red, end in a vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
+Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again colored red, end in a vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
 We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.

### 2018-02-26 Grassmannian_cells.tex
Remark on equivalences

@@
 
+\renewcommand{\AA}{\mathbb{A}}
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\CC}{\mathbb{C}}
+\newcommand{\kk}{\Bbbk}
+\newcommand{\NN}{\mathbb{N}}
+\newcommand{\ZZ}{\mathbb{Z}}
+
 \newcommand{\bfe}{\mathbf{e}}
@@
 \newcommand{\bfJ}{\mathbf{J}}
+
 \newcommand{\tbfe}{{\tilde\bfe}}
@@
 \newcommand{\tbfh}{{\tilde\bfh}}
-\newcommand{\C}{\mathbb{C}}
+
 \newcommand{\cA}{\mathcal{A}}
@@
 \newcommand{\cP}{\mathcal{P}}
+\newcommand{\cQ}{\mathcal{Q}}
+
 \newcommand{\ui}{{\underline i}}
@@
 \newcommand\udim{{\underline{\dim}\, }}
+
+\newcommand{\into}{\hookrightarrow}
+\newcommand{\onto}{\to\!\!\!\!\!\to}
+\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
+
+\newcommand{\Att}{\operatorname{Att}}
+\newcommand{\codim}{\operatorname{codim}}
+\newcommand{\Ext}{\operatorname{Ext}}
+\newcommand{\Gr}{\mathrm{Gr}}
+\newcommand{\GL}{\mathrm{GL}}
+\newcommand{\Hom}{\operatorname{Hom}}
+\newcommand{\im}{\operatorname{im}}
+\newcommand{\Ind}{\mathrm{Ind}}
 \newcommand{\pt}{\mathrm{pt}}
@@
 \newcommand{\rep}{\operatorname{rep}}
-\newcommand{\Gr}{\mathrm{Gr}}
-\newcommand{\GL}{\mathrm{GL}}
-\newcommand{\Ind}{\mathrm{Ind}}
-\renewcommand{\AA}{\mathbb{A}}
-\newcommand{\CC}{\mathbb{C}}
-\newcommand{\kk}{\Bbbk}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\NN}{\mathbb{N}}
 \newcommand{\rk}{\mathrm{rk}}
-\newcommand{\cQ}{\mathcal{Q}}
-\newcommand{\Att}{\operatorname{Att}}
-\newcommand{\Ext}{\operatorname{Ext}}
-\newcommand{\Hom}{\operatorname{Hom}}
-\newcommand{\im}{\operatorname{im}}
-\newcommand{\codim}{\operatorname{codim}}
-\newcommand{\into}{\hookrightarrow}
-\newcommand{\onto}{\to\!\!\!\!\!\to}
-\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
+\newcommand{\Sc}[2]{\langle #1,#2\rangle}
 \newcommand{\ses}[3]{\xymatrix@C15pt{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
 \newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
-%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
-\newcommand{\Sc}[2]{\langle #1,#2\rangle}
 \newcommand{\spn}{\operatorname{span}}
 \newcommand{\supp}{\operatorname{supp}}
+\newcommand{\vs}{\vspace{0.2cm}}
+
+\hyphenation{endo-functors}
 \setcounter{MaxMatrixCols}{20}
-\newcommand{\vs}{\vspace{0.2cm}}
-\hyphenation{endo-functors}
 
@@
 \author{Dylan Rupel}
+\address[Dylan Rupel]{University of Notre Dame, Department of Mathematics, Notre Dame, IN 46556, USA}
+\email{drupel@nd.edu}
 \author{Thorsten Weist}
+\address[Thorsten Weist]{}
+\email{weist@uni-wuppertal.de}
 
@@
   \begin{enumerate}
-    \item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
-    \item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
-    \item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing the 2-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
+    \item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
+    \item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
+    \item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
   \end{enumerate}
@@
 
+\begin{remark}
+  We will usually apply Lemma~\ref{lem:2equivalence} below after performing each of the equivalences from Definition~\ref{def:2equivalence}.
+  That is, given a 2-arrow $V:\Gamma(1)\to\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
+\end{remark}
+
 %The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}.
@@
 %\end{remark}
-In the following, we frequently use the notation and conventions of Section \ref{Lifting}.
-The next step is to associate a $2$-quiver $\mathcal Q_m^{[k]}$ with the lifted truncated preprojective representations 
-$$\tilde P_m^{[k]}:=\begin{cases}\tilde P_m^{\{n,\ldots,n-k+1\}}\text{ if } m\text{ is even}\\\tilde P_m^{\{1,\ldots,k\}}\text{ if }m\text{ is odd}\end{cases}$$ 
-for $m\geq 2$ and $0\leq k\leq n-1$  whose strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_m^{[k]}$.
-Recall that, by Theorem \ref{celldec}, the cells of the quiver Grassmannians attached to $P_m^{[k]}:= G_{K(n)}\tilde P_m^{[k]}$ are in one-to-one correspondence with those attached to the lift $\tilde P_m^{[k]}$.
-Moreover, by Theorem \ref{thm:truncpp}, the quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ of arbitrary truncated preprojective representations $P_m^V$ only depend on $\tbfe$ and $\udim P_m^V$.
-In short, the $2$-quivers $\mathcal Q_m^{[k]}$ can be seen as being attached to any (truncated) preprojective representation of the respective dimension.
-
-For building the mentioned $2$-quivers, we use the recursive construction described in Section \ref{Lifting}. The following remarks are meant to understand the structure of the $2$-quivers. 
-%In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering.
-%For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
-\begin{remark}\begin{enumerate}\item It will turn out that every vertex of the quiver $\mathcal Q_m^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
+In the following, we frequently use the notation and conventions of Section~\ref{Lifting}.
+The next step is to associate a $2$-quiver $\mathcal Q_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
+\[\tilde P_{m+1}^{[k]}:=
+  \begin{cases}
+    \tilde P_{m+1}^{\{n,n-1,\ldots,n-k+1\}} & \text{ if $m$ is odd;}\\
+    \tilde P_{m+1}^{\{1,2,\ldots,k\}} & \text{ if $m$ is even;}
+  \end{cases}\] 
+for $m\geq 1$ and $0\leq k\leq n-1$.
+When $k=0$ above, we take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$.
+We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_{m+1}^{[k]}$.
+
+Recall that, by Theorem~\ref{celldec}, the cells of the quiver Grassmannians attached to $P_{m+1}^{[k]}:=G(\tilde P_{m+1}^{[k]})$ are in one-to-one correspondence with those attached to the lift $\tilde P_{m+1}^{[k]}$.
+Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_{\tbfe}(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\tbfe$ and $\udim P_{m+1}^V$.
+In short, the $2$-quivers $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.
+
+For building the mentioned $2$-quivers, we use the recursive construction described in Section~\ref{Lifting}.
+The following remarks are meant to understand the structure of these $2$-quivers. 
+\begin{remark}\mbox{}
+  \begin{enumerate}
+    \item It will turn out that every vertex of the quiver $\mathcal Q_{m+1}^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_{m+1}^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
       Also every usual arrow of $\mathcal Q_m^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
@@
 Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
-The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}).
+The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}) thought of as a 2-quiver with no 2-arrows.
 In abuse of notation, we also denote the support quiver by $\mathcal Q_{2}^{[k]}$.

### 2018-02-26 Grassmannian_cells.tex
Added 4.18, included 3.12 in 3.10, minor edits

@@
 
-Although it has been shown by various authors that every projective variety can be realized as a quiver Grassmannian -- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
+Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
+%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
+it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
 For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
@@
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
-We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$ and we assume in the following that all representations are finite-dimensional.\sayT{Inserted finite-dimensional as we do not need infite-dimensional one (I am also not sure if we need to be careful at some points otherwise)}
+We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$ and we assume in the following that all representations are finite-dimensional.
 
@@
   For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp.
-$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0 $(resp.
+$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0 $ (resp.
 $\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
@@
   \begin{enumerate}
+
     \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
+  \item The indecomposable representations of dimension $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$. 
 	\item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$.
+
   \end{enumerate}
@@
 
-By Lemma \ref{le:unique morphisms} the roots $d(m,r)$ are Schur roots as there exist representations with trivial endomorphism ring.
+	  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
+As both, the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$, are parametrized by the same Grassmannian, this gives the second claim.
+
+As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
 %  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
   It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
-  This shows the second statement.
+  This shows the last claim.
 	\end{proof}
 \begin{remark}
-  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
+  There is a more elegant way to prove the first part of Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
   Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
@@
 
-\begin{corollary}
-  \label{cor:indecomposable truncated} 
-  For $V\in \Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
-  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
-\end{corollary}
-\begin{proof}
-  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
-\end{proof}
-
 \begin{lemma}
@@
 $1\le r\le\ell-2$).
-  However, $P_{m+1}^V$ is indecomposable by Corollary \ref{cor:indecomposable truncated} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+  However, $P_{m+1}^V$ is indecomposable by Proposition \ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
   %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
@@
 \begin{proof}
-  By Corollary~\ref{cor:indecomposable truncated} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
+  By Proposition~\ref{pro:indecomposables} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
   In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
@@
   Then the claimed structure $\tilde P_3(I,j)$ of the kernel and the surjectivity of the map $\tilde P_{3,j}\to\tau\tilde P_4^I$ are immediate from the explicit descriptions of $\tilde P_{3,j}$ and $\tilde P_2^I$ in Example~\ref{ex:lifted preprojectives} and Example~\ref{ex:truncated lifts} respectively.
-  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers}.
+  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark \ref{rem:reflection recursion}.(2).
 \end{proof}
@@
 Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
+  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
 \end{corollary}
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
+Write $\Ind(K(n),d)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ of dimension $d$ for $d\in\NN^{K(n)_0}$.
+As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind(K(n),d)$.
 \begin{proposition} \label{indecomposables}
@@
 \begin{proof}
-  By Lemma~\ref{le:subrep}, any subrepresentation $V\subsetneq\tilde P_{m+1}^I$ is preprojective.
+  By Lemma~\ref{le:subrep}, any subrepresentation $W\subsetneq\tilde P_{m+1}^I$ is preprojective.
   But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
   Thus we have $\Ext(W,\tilde P_{m,j}/U)=0$. 
-  If $U=0$, we have $\Ext(W,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.
+  If $U=0$, we have $\Ext(W,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $W$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_m)=0$ for $l\leq m+1$.
 
@@
   \noindent{\bf Claim.}
-  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces which are compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
@@
   Now suppose $|J|<n-1$.
-  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
+  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.\sayT{if $J=I_0$ we have $|J|=n-1$?}
   Thus we may assume $J\subsetneq I_0$.
@@
 \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
-\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
+\item Let $X\in\rep K(n)$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
 Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
@@
 \begin{proof}
-The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover}.
-The dual version for preinjective representations follows as $\Gr_{\tbfe}(P_m)\cong\Gr_{\udim P_m-\tbfe}(I_m)$.
+The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover} taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation which can be proven using the same argument as in the proof of Lemma \ref{le:lifts of transjectives}.
+The dual version for preinjective representations follows as $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$ respectively.
 
 The second part follows in the same way, additionally, taking Theorem \ref{thm:truncpp} into account.
+\end{proof}
+
+\begin{corollary}
+Let $X\in\rep K(n)$ be a direct sum of exceptional representations.
+Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
+In particular, this is true for all rigid representations of $K(n)$.
+\end{corollary}
+\begin{proof}
+As every exceptional representation of $K(n)$ is either preprojective or preinjective, we have
+$$X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i}$$
+where we assume that $j_i\leq j_{i+1}$ and write
+$$P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}$$ 
+for $r'\leq r$ and $s'\leq s$.
+
+By Theorem \ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$. Consider the short exact sequence
+\[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
+By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition into affine spaces. Consider the Caldero-Chapoton map
+\[\Psi_\bfe:\Gr_\bfe(P(r'+1))\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r')).\]
+The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,V)=\AA^{\dim\Hom(V,P_{j_{r'+1}}/U)}$  for all $(U,V)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$, in particular the fibre is never empty.
+Now every subrepresentation $V$ of $P(r')$ is isomorphic to direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
+Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
+Together this yields $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
+$$\dim\Hom(V,P_{j_{r'+1}}/U)=\langle V, P_{j_{r'+1}}/U\rangle$$
+for all $(U,V)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
+By Theorem \ref{vb}, this already shows that $\Gr_{\bfe}(P(r'))$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
+By duality, the same is true for $\Gr_{\bfe}(I(s))$.
+
+Finally consider the short exact sequence
+$$\ses{I(s)}{X}{P(r)}.$$
+As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition into affine spaces
 \end{proof}

### 2018-02-27 Grassmannian_cells.tex
Notation change in section 5

--- 2018-02-26 Grassmannian_cells.tex
@@
 
-The key concept for describing the cell decompositions is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
+The key concept for describing the cell decompositions is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations.
+It will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
 \begin{definition}
@@
   A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
-  A \emph{2-quiver} is a pair $\tilde Q=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
-  Given a 2-quiver $\tilde Q$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\tilde Q$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
+  A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
+  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
 \end{definition}
@@
   \label{def:2equivalence}
-  Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
+  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
   \begin{enumerate}
@@
   \begin{enumerate}
-    \item $\tilde Q_p$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
-    \item $\tilde Q_q$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
-    \item $\tilde Q_V$ as the $2$-quiver obtained from $\tilde Q$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
+    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
+    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
+    \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
   \end{enumerate}
-  This defines a relation on the set of $2$-quivers denoted by $\tilde Q\to \tilde Q_p$, $\tilde Q\to \tilde Q_q$ and $\tilde Q\to \tilde Q_V$ respectively.
+  This defines a relation on the set of $2$-quivers denoted by $\cQ\to\cQ_p$, $\cQ\to\cQ_q$ and $\cQ\to\cQ_V$ respectively.
   Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
@@
   \label{lem:2equivalence}
-  Let $\tilde Q=(Q,Q_2)$ and $\tilde Q'=(Q',Q_2')$ be equivalent $2$-quivers.
-  If $\beta\subset Q_0$ is strong successor closed in $\tilde Q$, it also defines a strong successor closed set of vertices in $\tilde Q$.
-  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\tilde Q$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\tilde Q'$.
+  Let $\cQ=(Q,Q_2)$ and $\cQ'=(Q',Q_2')$ be equivalent $2$-quivers.
+  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ$.
+  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\cQ$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\cQ'$.
 \end{lemma}
@@
 \begin{proof}
-  By induction, we only need to consider the cases $\tilde Q'\in\{\tilde Q_p,\tilde Q_q,\tilde Q_V\}$ where one of the conditions of Definition~\ref{def:2equivalence} is satisfied.
-
-  Assume first that $\tilde Q'\in\{\tilde Q_p,\tilde Q_q\}$.
+  By induction, we only need to consider the cases $\cQ'\in\{\cQ_p,\cQ_q,\cQ_V\}$ where one of the conditions of Definition~\ref{def:2equivalence} is satisfied.
+
+  Assume first that $\cQ'\in\{\cQ_p,\cQ_q\}$.
   Then we have $Q=Q'$ from which we immediately see that $\beta\subset Q_0$ is successor closed in $Q$ if and only if $\beta$ is successor closed in $Q'$.
-  We only consider the case $\tilde Q'=\tilde Q_p$ below, the argument for $\tilde Q'=\tilde Q_q$ is dual.
-
-  Let $\beta\subset Q_0$ be strong successor closed in $\tilde Q$.
-  To see that $\beta$ is strong successor closed in $\tilde Q_p$ it suffices to consider the 2-arrow $V_p:\{p\}\to\Gamma(2)$.
+  We only consider the case $\cQ'=\cQ_p$ below, the argument for $\cQ'=\cQ_q$ is dual.
+
+  Let $\beta\subset Q_0$ be strong successor closed in $\cQ$.
+  To see that $\beta$ is strong successor closed in $\cQ_p$ it suffices to consider the 2-arrow $V_p:\{p\}\to\Gamma(2)$.
   Suppose $\{p\}\subset\beta$.
-  As $\beta$ is successor closed in $Q$ and $p$ is a source in the connected quiver $\Gamma(1)$, we have $\Gamma(1)_0\subset\beta$ and thus $\Gamma(2)_0\cap\beta\ne\varnothing$, i.e.\ $\beta$ is strong successor closed in $\tilde Q_p$.
+  As $\beta$ is successor closed in $Q$ and $p$ is a source in the connected quiver $\Gamma(1)$, we have $\Gamma(1)_0\subset\beta$ and thus $\Gamma(2)_0\cap\beta\ne\varnothing$, i.e.\ $\beta$ is strong successor closed in $\cQ_p$.
   The reverse implication is immediate since $\{p\}\subset\Gamma(1)_0$.
 
-  Now assume $\tilde Q'=\tilde Q_V=\big(Q_V,(Q_V)_2\big)$. 
-  Let $\beta\subset Q_0$ be strong successor closed in $\tilde Q$.
-  Since $(Q_V)_2\subset Q_2$, to see that $\beta$ is strong successor closed in $\tilde Q_V$ we only need to show that $\beta$ is successor closed in $Q_V$.  
+  Now assume $\cQ'=\cQ_V=\big(Q_V,(Q_V)_2\big)$. 
+  Let $\beta\subset Q_0$ be strong successor closed in $\cQ$.
+  Since $(Q_V)_2\subset Q_2$, to see that $\beta$ is strong successor closed in $\cQ_V$ we only need to show that $\beta$ is successor closed in $Q_V$.  
   For this it suffices to consider the arrow $\alpha_V:p\to q$ for which that claim is obvious since $p\in\beta$ is equivalent to $\{p\}\subset\beta$ and similarly for $q$.
 
-  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\tilde Q_V$.
+  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\cQ_V$.
   Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
-  To see that $\beta$ is strong successor closed in $\tilde Q$, it suffices to consider the 2-arrow $V:\{p\}\to\{q\}$ for which the claim is obvious as above.
+  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\to\{q\}$ for which the claim is obvious as above.
 \end{proof}
@@
 In the following, we frequently use the notation and conventions of Section~\ref{Lifting}.
-The next step is to associate a $2$-quiver $\mathcal Q_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
+The next step is to associate a $2$-quiver $\cQ_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
 \[\tilde P_{m+1}^{[k]}:=

### 2018-02-27 Grassmannian_cells.tex
TeX cleanup

@@
   For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp.
-$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0 $ (resp.
+$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0$ (resp.
 $\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
@@
   By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-As both, the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$, are parametrized by the same Grassmannian, this gives the second claim.
+  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.
 
   As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
-%  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
   It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
@@
 \begin{proof}
-  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
+  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
   Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
@@
 %\end{align}
-Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
+Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $\tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
 %This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
@@
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
-Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$.
+Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$.
 As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
@@
 \begin{theorem}\begin{enumerate}
-\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
-	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
 \end{enumerate}

### 2018-02-27 Grassmannian_cells.tex
Prevent line breaks in references

@@
 \begin{remark}
-  There is a more elegant way to prove the first part of Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
+  There is a more elegant way to prove the first part of Proposition~\ref{pro:indecomposables} using the notion of stability and moduli spaces.
   Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
@@
 $1\le r\le\ell-2$).
-  However, $P_{m+1}^V$ is indecomposable by Proposition \ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+  However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
   %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
@@
   Then the claimed structure $\tilde P_3(I,j)$ of the kernel and the surjectivity of the map $\tilde P_{3,j}\to\tau\tilde P_4^I$ are immediate from the explicit descriptions of $\tilde P_{3,j}$ and $\tilde P_2^I$ in Example~\ref{ex:lifted preprojectives} and Example~\ref{ex:truncated lifts} respectively.
-  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark \ref{rem:reflection recursion}.(2).
+  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark~\ref{rem:reflection recursion}.(2).
 \end{proof}
@@
 \subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}
-The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
 If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
@@
   For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_{d(1,r)}(K(n))$.
-  As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
+  As the reflection functors preserve indecomposability and isomorphism classes, by Lemma~\ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
   \[\xymatrix{\Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),d(m+1,r))\ar[d]^g\\
@@
 
-  Proposition \ref{pro:indecomposables} and \ref{indecomposables} imply that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
+  Proposition~\ref{pro:indecomposables} and~\ref{indecomposables} imply that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
   With other words we use that all indecomposables are truncated preprojectives.
@@
 
-  The second statement follows directly from Proposition \ref{quotient}.
+  The second statement follows directly from Proposition~\ref{quotient}.
 \end{proof}
@@
 By induction hypothesis the quiver Grassmannians $\Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})$ have cell decompositions which are compatible with $\pi^{\bf i}_m$ and, moreover, the quiver Grassmannians $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ have a cell decompositions which are compatible with $\pi^{\bf j}_{m,\uj}$.
-The second part of Proposition \ref{fibers} says that the fibers are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
+The second part of Proposition~\ref{fibers} says that the fibers are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
 This yields a collection of cells over which the fibers are empty.
@@
 
-If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, by Proposition \ref{fibers}, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$.
+If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, by Proposition~\ref{fibers}, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$.
 In particular, they are constant over cells whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)\neq 0$, but also over those whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)= 0$.
-By Theorem \ref{vb}, it follows that $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ has a cell decomposition.
+By Theorem~\ref{vb}, it follows that $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ has a cell decomposition.
 
 Thus it remains to show that this cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ is compatible with $\pi_{m,\uj'}^{\bf j}$ where ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
-Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma \ref{le:truncated quotients}.(2).
+Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma~\ref{le:truncated quotients}.(2).
 
@@
 
-By Lemma \ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition.
+By Lemma~\ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition.
 The second part of the Proposition says that the fibers are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma \ref{vb}?}.
-Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
+In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma~\ref{vb}?}.
+Analogously to Lemma~\ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
 In total, this yields a cell decomposition of the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
@@
 \begin{proof}
-The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover} taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation which can be proven using the same argument as in the proof of Lemma \ref{le:lifts of transjectives}.
+The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover} taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation which can be proven using the same argument as in the proof of Lemma~\ref{le:lifts of transjectives}.
 The dual version for preinjective representations follows as $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$ respectively.
 
-The second part follows in the same way, additionally, taking Theorem \ref{thm:truncpp} into account.
+The second part follows in the same way, additionally, taking Theorem~\ref{thm:truncpp} into account.
 \end{proof}
@@
 
-By Theorem \ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$. Consider the short exact sequence
+By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$. Consider the short exact sequence
 \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
@@
 for all $(U,V)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
-By Theorem \ref{vb}, this already shows that $\Gr_{\bfe}(P(r'))$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
+By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}(P(r'))$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
 By duality, the same is true for $\Gr_{\bfe}(I(s))$.
@@
 As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{\udim P_m{(k)}}$.
-The description of the non-empty fibers in Proposition \ref{fibers} together with Corollary \ref{fpoly} and Theorem \ref{celldec} yield the following:
+The description of the non-empty fibers in Proposition~\ref{fibers} together with Corollary~\ref{fpoly} and Theorem~\ref{celldec} yield the following:
 \begin{corollary}
@@
 \noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
-The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section \ref{sec:fibrations}.
+The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
 The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
@@
 
-%The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}.
+%The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section~\ref{QG}.
 %These $2$-quivers are related to certain coefficient quivers of these representations.
@@
 %\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
-%  Lemma \ref{AR} can be generalized to the cases $m\leq 2$.
+%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
 %  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
@@
 This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
+In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
 These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
@@
 This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma \ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
+In view of Lemma~\ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
 %In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
 \end{remark}
-%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
+%It remains to consider the case when $m$ is even. Lemma~\ref{AR} yields
 %\begin{align}\label{eq:case2}
@@
 \begin{proof}
-The results of Section \ref{QG} imply that the second statement follows from the first one.
+The results of Section~\ref{QG} imply that the second statement follows from the first one.
 We proceed by induction on $m$ and $k$.
@@
  % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition \ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
+  By Proposition~\ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.

### 2018-03-01 Grassmannian_cells.tex
Section 5 edits (not yet finished)

@@
 \end{definition}
+Observe that any quiver can be considered as a 2-quiver with no 2-arrows.
 
@@
     \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
+      \sayD{It doesn't seem to be part of the definition that there must exist such an arrow in $Q$.}
   \end{enumerate}
@@
   Let $\cQ=(Q,Q_2)$ and $\cQ'=(Q',Q_2')$ be equivalent $2$-quivers.
-  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ$.
+  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ'$.
   In particular, the number of subsets of $Q_0$ which are strong successor closed in $\cQ$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\cQ'$.
@@
 When $k=0$ above, we take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$.
-We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_{m+1}^{[k]}$.
+We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$\tilde P_{m+1}^{[k]}$.
 
 Recall that, by Theorem~\ref{celldec}, the cells of the quiver Grassmannians attached to $P_{m+1}^{[k]}:=G(\tilde P_{m+1}^{[k]})$ are in one-to-one correspondence with those attached to the lift $\tilde P_{m+1}^{[k]}$.
-Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_{\tbfe}(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\tbfe$ and $\udim P_{m+1}^V$.
-In short, the $2$-quivers $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.
+Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
+In short, the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.
 
@@
     \item It will turn out that every vertex of the quiver $\mathcal Q_{m+1}^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_{m+1}^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-      Also every usual arrow of $\mathcal Q_m^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
-In particular, the quiver obtained from $\mathcal Q_m^{[k]}$ when forgetting the $2$-arrows gives rise to a (non-disjoint) union of subquivers of $\widetilde{K(n)}$.
+      Also every usual arrow of $\mathcal Q_{m+1}^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
+      In particular, the quiver obtained from $\mathcal Q_{m+1}^{[k]}$ when forgetting the $2$-arrows gives rise to a (possibly non-disjoint) union of subquivers of $\widetilde{K(n)}$.
 
   \item Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
-\[
-  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
-\]
-
-%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
-%\[
-%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
-%\]
+    \[\tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).\]
+
     Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:maphomext}), we have 
-\begin{align}\label{eq:case2}
-  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\tilde P_{1,i})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
+    \begin{align}
+      \label{eq:case2}
+      \Ext\big(P_2^{[n-1]},P_1\big)
+      \cong\bigoplus_{i=2}^{n}\Ext\big(\tilde P_2^{[n-1]},\tilde P_{1,i}\big)
+      \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\big\rangle.
     \end{align}
 
-\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
+  \item  For $m\geq 2$, recall that we have $\dim\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)=\dim\Ext\big(P_{m+1}^{[k]},P_m\big)$ by the Auslander-Reiten formula.
+    This induces isomorphisms
     \begin{align}
       \label{eq:homext} 
-  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
+      \bigoplus_{i=k+1}^n \Hom\big(\alpha_{i}^{(-1)^{m+1}}.\tilde P_m,\tau\tilde P_{m+1}^{[k]}\big)
+      \cong\bigoplus_{i=k+1}^n \Ext\big(\tilde P_{m+1}^{[k]},\alpha_{i}^{(-1)^{m+1}}.\tilde P_m\big)
+      \cong\Ext\big(P_{m+1}^{[k]},P_m\big).
     \end{align}
-This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$.
-In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
-These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
-\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
-Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
+    This means that we can choose a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ and $\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)$.
+    In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism 
+    \[\Ext\big(\tilde P_{m+1}^{[k]},\tilde P_{m,k}\big)\cong\Ext\big(\tilde P_{m+1}^{[k]},\tau\tilde P_{m+1}^{[k]}\big).\]
+    These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_{m+1}^{[k]}$.
+    Finally note that there exists a short exact sequence
+    \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[k]},P_m\big)}{\Ext\big(P_{m+1}^{[k+1]},P_m\big)}.\]
+    Thus a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
   \end{enumerate}
@@
 
-%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
-Initially, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined by the vertex $(1,e)$.
+The $2$-quivers $\cQ_{m+1}^{[k]}$ will be built inductively.
+To begin, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined simply as the quiver consisting of a single vertex $(1,e)$.
 Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
-Using (\ref{eq:case2}), we can recursively construct the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ which are defined by the support quivers
+Using (\ref{eq:case2}), we recursively construct the (truncated) preprojective representations $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ using their support quivers
 \begin{align}
@@
 We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
-\\
-
+\[
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\\
-
-\noindent
+\]
 where the $2$-arrows are colored red.
@@
 In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
-We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
+We also define the translated two quivers $\cQ_{2,i}$ as those obtained from $\cQ_2$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
 
@@
 First, we define
-$$\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},$$
-i.e.
-we translate all vertices - understood as vertices of $\widetilde{K(n)}$ - and $(2)$-arrows by $\alpha_n^{-1}$.
-Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
-
+\[\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},\]
+i.e. we translate all vertices -- understood as vertices of $\widetilde{K(n)}$ -- and (2-)arrows by $\alpha_n^{-1}$.
+Then $\cQ_3^{[k]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
+\[
 \begin{tikzpicture}[scale=1.35]
@@
 \end{tikzpicture}
-\\
-
-\noindent In abuse of notation, we did not label the vertices in the illustration.
-Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again colored red, end in a vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
+\] 
+To avoid cluttering the diagram, we did not label the vertices in the illustration.
+Observe that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that the target of the $2$-arrow, again colored red, into $\cQ_{2,n-1}$ is the vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
+In general, the 2-arrow from $\cQ_3^{[i]}$ into $\cQ_{2,i}$ has target the vertex corresponding to $(1,e)$ in $\widetilde{K(n)}$.
 We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.
@@
 \[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
-Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
+Note that the image of the homomorphism corresponding to the basis element spanning 
+\[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
+corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
 This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
@@
 %Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
-Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$.
+Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$, $j=0,\ldots, n-1$ and $l=m+1$, $j=n-1,\ldots,k$.
 As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
-Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$
+Moreover, we define 
+\[\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{-1}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.\]
 

### 2018-03-01 Grassmannian_cells.tex
Remark on Caldero-Chapoton maps for K(n)

@@
 \begin{corollary}
+  \label{cor:base fibers}
   Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
@@
 \end{proposition}
+\begin{remark}
+  Part (1) of Proposition~\ref{fibers} holds equally well when considering the analogues of the Caldero-Chapoton maps $\Psi_{m+1,I,j}$ for $K(n)$.
+  This follows from Corollary~\ref{cor:base fibers} and Lemma~\ref{le:projective subrepresentations}.
+  However, there does not seem to be a reasonable analogue of part (2) when considering Calcero-Chapoton maps for $K(n)$.
+\end{remark}
 \begin{proof}

### 2018-03-02 Grassmannian_cells.tex
no edits

@@
 For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
-It has been conjectured\sayD{reference?} that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
+It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
 

### 2018-03-05 Grassmannian_cells.tex
Theorem 5.7, Introduction (main results and organization), minor edits

@@
 \newtheorem{example}[theorem]{Example}
-
+\newtheorem{thm}{Theorem}
 \numberwithin{equation}{section}
@@
 -acknowledgements?\\
-
+The paper is organized as follows.
+In Section \ref{sec:covering}, we collect several results concerning quiver covering theory.
+In Section \ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which is needed to investigate the quiver Grassmannians attached to preprojective representations later.
+We first focus on preprojective and preinjective representations, written as $P_m$ and $I_m$, which enables us to investigate a special class of indecomposable representations in Section \ref{sec:truncated preprojectives} - we call them truncated preprojective representations.
+We proof that every preprojective representation admits a filtration by preprojectives of smaller dimensions such that all quotients appearing are actually truncated preprojective representations.
+In Section \ref{Lifting}, we use this together with the fact that every preprojective representation can be lifted to the universal covering in order to construct lifted filtrations.
+Throughout this section, we collect many results which will turn out to completely reveal the structure of quiver Grassmannians attached to (truncated) preprojective representations.
+
+The aim of Section \ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
+This is obtained by combining a torus action on quiver Grassmannians which is introduced in Section \ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations in Section \ref{sec:fibrations}.
+Our first main result is Theorem \ref{thm:torusfixedpoints} which may be formulated as follows.
+\begin{thm}
+  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q$.
+Then there exists a map $d:\supp(\hat X)\to\ZZ$ - with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ - which induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
+  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
+\end{thm}
+This torus action can be iterated in such a way that the remaining torus fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
+As far as generalized Kronecker quivers are concerned, we can show in Theorem \ref{thm:truncpp} that all quiver Grassmannians attached to truncated representations are smooth - actually, they only depend on dimension vectors.
+In view of results of Bia\l{}ynicki-Birula \cite{bb} - which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety - we can use this result to lift the investigation of the quiver Grassmannians to the universal covering quiver.
+This is insofar important as results as Corollary \ref{cor:perpendicular} are available which do not hold on the original quiver.
+Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems \ref{cellscover} and \ref{celldec}.
+ \begin{thm} For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
+\end{thm}
+Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.
+
+In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
+Theorem \ref{thm:2quivercells} can be formulated as follows.\begin{thm}
+With every truncated preprojective representation $P_{m+1}^V$ we can associated a $2$-quiver $\mathcal Q_{m+1}^{[\dim V]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[\dim V]})_0$.
+In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
+\end{thm}
+\sayT{Insert something about Dyck path combinatorics and the correspondence here}
+\sayT{maybe we can erase some parts which show up twice in the introduction?}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}
+\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
 The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
@@
   Let $\hat X$ be an indecomposable representation of $\hat Q$.
-  There exists $d:\supp(X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
+  There exists $d:\supp(\hat X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
   \begin{enumerate}
@@
 
-In the following, we say that $d:\supp(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
-\begin{theorem}
+In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
+\begin{theorem}\label{thm:torusfixedpoints}
   Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Combinatorial description of non-empty cells}
+\section{Combinatorial description of non-empty cells}\label{sec:combinatorics}
 \noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
@@
 
-\subsection{2-Quivers}
+\subsection{2-Quivers}\label{sec:2quivers}
 
@@
 
-\begin{theorem}\begin{enumerate}
-\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
-	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe$ of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+\begin{theorem}\label{thm:2quivercells}
+\begin{enumerate}
+\item The cells of the cell decomposition of $\Gr_\tbfe(\tilde P_m^{[k]})$ (resp.
+$Gr_\bfe( P_m^{[k]})$) induced by Theorem \ref{cellscover}  can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[k]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
+$\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
+
+\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
+$\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ (resp.
+$\chi(\Gr_{\bfe }(P_m^{[k]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$  (resp.
+$\bfe$) of the $2$-quiver of $\mathcal Q_m^{[k]}$.
+
 \end{enumerate}
@@
 \begin{proof}
-The results of Section~\ref{QG} imply that the second statement follows from the first one.
+The results of Sections~\ref{sec:bb} and \ref{torusaction} imply that the statements in parentheses follow from the respective results for the lifted representations.
+Moreover, the second result follows from the first one.
+
 We proceed by induction on $m$ and $k$.
@@
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.
+This shows the first claim.
 \end{proof}

### 2018-03-05 Grassmannian_cells.tex
Section 5.1 edits

--- 2018-03-01 Grassmannian_cells.tex
@@
 \usepackage{tikz}
+\usetikzlibrary{arrows}
 %\usepackage{pgflibraryarrows}
@@
   \begin{enumerate}
-
     \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
-  \item The indecomposable representations of dimension $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$. 
+    \item The indecomposable representations of dimension $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$ with $\dim V=r$. 
     \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
-
   \end{enumerate}
@@
 By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
-\[\sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.\]
+\begin{equation}
+  \label{eq:truncted sequence}
+  \sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.
+\end{equation}
 For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
@@
   This follows from Corollary~\ref{cor:base fibers} and Lemma~\ref{le:projective subrepresentations}.
-  However, there does not seem to be a reasonable analogue of part (2) when considering Calcero-Chapoton maps for $K(n)$.
+  However, there does not seem to be a reasonable analogue of part (2) when considering Caldero-Chapoton maps for $K(n)$.
 \end{remark}
@@
   Now suppose $|J|<n-1$.
-  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.\sayT{if $J=I_0$ we have $|J|=n-1$?}
+  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
   Thus we may assume $J\subsetneq I_0$.
@@
 The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
-We give a bijection between these which provides a partial answer to a question of the first author \cite{rupel}.
+We give a bijection between these which provides a partial geometric explanation for the combinatorial construction of counting polynomials for rank two quiver Grassmannians given in \cite{rupel}.
 
@@
 The key concept for describing the cell decompositions is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations.
+This construction makes use of the support quivers from Examples~\ref{ex:lifted preprojectives} and~\ref{ex:truncated lifts}.
 It will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
@@
 \end{definition}
+
+The following notion of equivalence for $2$-quivers will be useful in the construction of 2-quivers whose strong successor closed subsets label cells in quiver Grassmannians.
 Observe that any quiver can be considered as a 2-quiver with no 2-arrows.
-
-We introduce a notion of equivalence of $2$-quivers.
 \begin{definition}
@@
     \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
-      \sayD{It doesn't seem to be part of the definition that there must exist such an arrow in $Q$.}
   \end{enumerate}
@@
 
-Observe that the vertex sets of equivalent $2$-quivers coincide.
+An important consequence of this definition is that the vertex sets of equivalent $2$-quivers coincide, in particular we can formulate the following result.
 \begin{lemma}
@@
   Let $\cQ=(Q,Q_2)$ and $\cQ'=(Q',Q_2')$ be equivalent $2$-quivers.
-  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ'$.
-  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\cQ$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\cQ'$.
+  A subset $\beta\subset Q_0$ is strong successor closed in $\cQ$ if and only if it is strong successor closed in $\cQ'$.
 \end{lemma}
@@
 An analogous statement holds if a quiver has precisely one sink. 
-
 \begin{proof}
@@
 \begin{remark}
-  We will usually apply Lemma~\ref{lem:2equivalence} below after performing each of the equivalences from Definition~\ref{def:2equivalence}.
+  Below we will usually apply Lemma~\ref{lem:2equivalence} after performing each of the equivalences from Definition~\ref{def:2equivalence}.
   That is, given a 2-arrow $V:\Gamma(1)\to\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
@@
 %\end{remark}
-In the following, we frequently use the notation and conventions of Section~\ref{Lifting}.
-The next step is to associate a $2$-quiver $\cQ_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
-\[\tilde P_{m+1}^{[k]}:=
+In the following, we freely use the notation and conventions of Section~\ref{sec:RepK(n)}.
+For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(H_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
+In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.
+
+By Theorem~\ref{celldec}, the cells of the quiver Grassmannians of $P_{m+1}^V$ are in one-to-one correspondence with those attached to any lift $\tilde P_{m+1}^{[r]}$ to $\widetilde{K(n)}$.
+Since the choice of $V\in\Gr(H_m)$ with $\dim V=r$ is immaterial for understanding the geometry of $\Gr_\bfe(P_{m+1}^V)$, we may fix a particular choice of $V$ and a particular lift to the universal cover.
+Indeed, set
+\[\tilde P_{m+1}^{[r]}:=
   \begin{cases}
-    \tilde P_{m+1}^{\{n,n-1,\ldots,n-k+1\}} & \text{ if $m$ is odd;}\\
-    \tilde P_{m+1}^{\{1,2,\ldots,k\}} & \text{ if $m$ is even;}
+    \tilde P_{m+1}^{\{n,n-1,\ldots,n-r+1\}} & \text{ if $m$ is odd;}\\
+    \tilde P_{m+1}^{\{1,2,\ldots,r\}} & \text{ if $m$ is even;}
   \end{cases}\] 
-for $m\geq 1$ and $0\leq k\leq n-1$.
-When $k=0$ above, we take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$.
-We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$\tilde P_{m+1}^{[k]}$.
-
-Recall that, by Theorem~\ref{celldec}, the cells of the quiver Grassmannians attached to $P_{m+1}^{[k]}:=G(\tilde P_{m+1}^{[k]})$ are in one-to-one correspondence with those attached to the lift $\tilde P_{m+1}^{[k]}$.
-Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
-In short, the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.
-
-For building the mentioned $2$-quivers, we use the recursive construction described in Section~\ref{Lifting}.
-The following remarks are meant to understand the structure of these $2$-quivers. 
-\begin{remark}\mbox{}
-  \begin{enumerate}
-    \item It will turn out that every vertex of the quiver $\mathcal Q_{m+1}^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_{m+1}^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-      Also every usual arrow of $\mathcal Q_{m+1}^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
-      In particular, the quiver obtained from $\mathcal Q_{m+1}^{[k]}$ when forgetting the $2$-arrows gives rise to a (possibly non-disjoint) union of subquivers of $\widetilde{K(n)}$.
-
-  \item Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
-    \[\tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).\]
-
-    Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:maphomext}), we have 
+and write $P_{m+1}^{[r]}=G(\tilde P_{m+1}^{[r]})$.
+Note that we may allow $r=0$ above and take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$, then we write $\cQ_{m+1}$ in place of $\cQ_{m+1}^{[0]}$.
+Fixing a choice of lift will allows us to give a concrete description of the 2-quiver~$\cQ_{m+1}^{[r]}$, it will be clear from the construction that making another choice of lift and following an analogous procedure will give a construction of an isomorphic 2-quiver.
+In this way, the 2-quiver $\cQ_{m+1}$ should be viewed as a combinatorial shadow of the sequences \eqref{ses1} defining the truncated preprojective representations of $\widetilde{K(n)}$.
+In fact, the related sequences \eqref{eq:truncted sequence} will be used together with Lemma~\ref{le:truncated quotients} to recursively construct the 2-quivers $\cQ_{m+1}^{[r]}$.
+
+Each 2-quiver $\cQ_{m+1}^{[r]}$ should be thought of as a combinatorially enhanced version of the coefficient quiver of $\tilde P_{m+1}^{[r]}$ in which certain arrows are upgraded to 2-arrows.
+In particular, the vertices and arrows of the quiver $Q_{m+1}^{[r]}$ underlying the 2-quiver $\cQ_{m+1}^{[r]}$ can naturally be associated with vertices and arrows of $\widetilde{K(n)}$.
+
+To begin, we take the $2$-quiver $\cQ_1=\cQ_1^{[0]}$ associated to $\tilde P_1$ to be the quiver $Q_1$ consisting of a single vertex which we associate to the vertex $(1,e)$ of $\widetilde{K(n)}$.
+By analogy with the notation of Section~\ref{Lifting}, we define a 2-quiver $\cQ_{1,i}$ for $1\le i\le n$ whose underlying quiver $Q_{1,i}$ has a single vertex which is associated to the vertex $(1,\alpha_i)$ of $\widetilde{K(n)}$.
+
+The 2-quiver $\cQ_2^{[r]}$ associated to the (truncated) preprojective $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
+\[\begin{tikzpicture}
+  \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
+  \draw (0,0) node (Vr) {$(1,\alpha_{n-r})$} +(.8,-.9) node {\footnotesize$ \mathcal Q_2^{[r]}$} +(3,0) node (Vr1) {$(1,\alpha_{n-r+1})$}+(3.8,-.9) node (Lr1) {\footnotesize$ \mathcal Q_2^{[r+1]}$} +(6,0) node (Vx) {$\dots$} +(9,.15) node (V2) {$(1,\alpha_{2})$} +(9.8,-.75) node (L2) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,.45) node (V1) {$(1,\alpha_1)$}  +(14,.45) node (V0) {$(2,e)$} +(12.8,-.35) node (L1) {\footnotesize$\mathcal Q_2^{[n-1]}$};
+
+  \node (Q0) [draw=black,fit={(V0)}]{};
+  \node (P1) [draw=black,fit={(V1)}]{};
+  \node (Q1) [draw=black,fit={(P1) (Q0) (L1)}]{};
+  \node (P2) [draw=black,fit={(V2)}]{};
+  \node (Q2) [draw=black,fit={(Q1) (P2) (L2)}]{};
+  \node (Q2b) [draw=black,fit={(Q2) (Vx) }]{};
+  \node (Pr1) [draw=black,fit={(Vr1)}]{};
+  \node (Q3) [draw=black,fit={(Q2b) (Pr1) (Lr1)}]{};
+  \node (Pr) [draw=black,fit={(Vr)}]{};
+
+  \draw[implies-,double equal sign distance,red] (P1)--(Q0) node[pos=.5,above] {\footnotesize$\alpha_1$};
+  \draw[-implies,double equal sign distance,red] (Q1)--(P2) node[pos=.5,above] {\footnotesize$\alpha_2$};
+  \draw[-implies,double equal sign distance,red] (Q2)--(Vx) node[pos=.5,above] {\footnotesize$\alpha_3$};
+  \draw[-implies,double equal sign distance,red] (Q2b)--(Pr1) node[pos=.5,above] {\footnotesize$\alpha_{n-r-1}$};
+  \draw[-implies,double equal sign distance,red] (Q3)--(Pr) node[pos=.5,above] {\footnotesize$\alpha_{n-r}$};
+\end{tikzpicture}\]
+The source and target quivers for each 2-arrow above have been drawn inside a box.
+Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$ and that $\cQ_2^{[t]}$ is a sub-2-quiver of $\cQ_2^{[r]}$ for $t\ge r$.
+
+\begin{remark}
+  \label{rem:2-arrows Q2}
+  The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
+  \begin{equation*}
+    \label{eq:case2}
+    \Ext(P_2,P_1)
+    \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
+    \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
+  \end{equation*}
+  and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
+  In particular, the isomorphism \eqref{eq:case2} can be used with these surjections to obtain compatible bases for each $\Ext(P_2^{[r]},P_1)$.
+\end{remark}
+The $2$-quiver $\mathcal Q_2^{[r]}$ given above is clearly equivalent to the support quiver \eqref{coeff} thought of as a 2-quiver with no 2-arrows:
 \begin{align}
-      \label{eq:case2}
-      \Ext\big(P_2^{[n-1]},P_1\big)
-      \cong\bigoplus_{i=2}^{n}\Ext\big(\tilde P_2^{[n-1]},\tilde P_{1,i}\big)
-      \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\big\rangle.
+  \label{coeff}
+    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r})}
 \end{align}
-
-  \item  For $m\geq 2$, recall that we have $\dim\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)=\dim\Ext\big(P_{m+1}^{[k]},P_m\big)$ by the Auslander-Reiten formula.
-    This induces isomorphisms
+In this way we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
+In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
+In this way we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
+
+The 2-quiver $\cQ_3^{[r]}$ associated to $\tilde P_3^{[r]}$ has underlying quiver $Q_3^{[r]}:=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{2,i}$.
+Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$.
+For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
+By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
+By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
+Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
+\[
+\begin{tikzpicture}[scale=1.35]
+  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
+  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
+
+  \draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$\mathcal Q_3^{[1]}$} ;
+  \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+  \draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+  \draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+  \draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
+
+  \draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$\mathcal Q_3^{[2]}$};
+
+  \draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.6) node (D31) { $\vdots$} +(1,0) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\mathcal Q_3^{[n-3]}$} ;
+  \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+  \draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
+  \draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+  \draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
+
+  \draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0.1) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\mathcal Q_3^{[n-2]}$};
+  \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
+  \draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
+  \draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
+  \draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
+
+  \draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0.1) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\mathcal Q_3^{[n-1]}$}   ;
+  \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
+  \draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
+  \draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
+  %\tikzstyle{every node}=[circle,fill=white!10]
+  \node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
+  %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
+  \draw[-implies,double equal sign distance,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
+  \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
+  \draw[-implies,double equal sign distance,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {};
+  \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
+  \draw[-implies,double equal sign distance,red] (Q4)--(DOTS)  node[pos=.5,above] {};
+  \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
+
+  \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
+  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
+
+\end{tikzpicture}
+\]  
+To avoid cluttering the diagram, we did not label the vertices in the illustration.
+
+\begin{remark} 
+  Here we justify the definition of the 2-arrows in $\cQ_3^{[r]}$, this discussion will also serve to motivate the choice of 2-arrows for general $\cQ_{m+1}^{[r]}$ and thus we work in that generality.
+
+  For $m\ge2$, we may apply Theorem~\ref{covering} together with Lemma~\ref{le:properties} and the Auslander-Reiten formula to get an isomorphism 
   \begin{align}
     \label{eq:homext} 
-      \bigoplus_{i=k+1}^n \Hom\big(\alpha_{i}^{(-1)^{m+1}}.\tilde P_m,\tau\tilde P_{m+1}^{[k]}\big)
-      \cong\bigoplus_{i=k+1}^n \Ext\big(\tilde P_{m+1}^{[k]},\alpha_{i}^{(-1)^{m+1}}.\tilde P_m\big)
-      \cong\Ext\big(P_{m+1}^{[k]},P_m\big).
+    \Ext\big(P_{m+1}^{[r]},P_m\big)
+    \cong\bigoplus_{i=r+1}^n \Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)
+    \cong\bigoplus_{i=r+1}^n \Hom\big(\tilde P_{m,i},\tau\tilde P_{m+1}^{[r]}\big).
   \end{align}
-    This means that we can choose a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ and $\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)$.
+\end{remark}
+
+\begin{remark}
+  Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$.
+  Moreover, (\ref{eq:homext}) for $m=3$ yields 
+  \[\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).\]
+  This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map 
+  \[(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})\]
+  for $i=1,\ldots,n-1$.
+  Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
+  \[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
+  Note that the image of the homomorphism corresponding to the basis element spanning 
+  \[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
+  corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
+  This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
+
+  This gives a justification for the original definition of the 2-arrows in $\cQ_3^{[r]}$.
+
     In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism 
@@
     Thus a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
-  \end{enumerate}
 \end{remark}
-
-The $2$-quivers $\cQ_{m+1}^{[k]}$ will be built inductively.
-To begin, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined simply as the quiver consisting of a single vertex $(1,e)$.
-Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
-Using (\ref{eq:case2}), we recursively construct the (truncated) preprojective representations $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ using their support quivers
-\begin{align}
-  \label{coeff}
-    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-k}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-k})}
-\end{align}
-
-We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
-\[
-\begin{tikzpicture}
-\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
-\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,e)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$};
-\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
-\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
-\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};
-
-\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
-\draw[<-] (D)--(E) node[pos=.5,above] {\footnotesize$\alpha_1$};
-\draw[->,red] (Q1)--(C) node[pos=.5,above] {\footnotesize$\alpha_2$};
-\draw[->,red] (Q2)--(B1) node[pos=.5,above] {\footnotesize$\alpha_3$};
-\draw[->,red] (Q2b)--(B) node[pos=.5,above] {\footnotesize$\alpha_{n-k-1}$};
-
-\draw[->,red] (Q3)--(A) node[pos=.5,above] {\footnotesize$\alpha_{n-k}$};
-\end{tikzpicture}
-\]
-where the $2$-arrows are colored red.
-Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
-The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}) thought of as a 2-quiver with no 2-arrows.
-In abuse of notation, we also denote the support quiver by $\mathcal Q_{2}^{[k]}$.
-In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
-We also define the translated two quivers $\cQ_{2,i}$ as those obtained from $\cQ_2$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
 
@@
 
-  \draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\mathcal Q_3^{[n-3]}$} ;
+  \draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.6) node (D31) { $\vdots$} +(1,0) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\mathcal Q_3^{[n-3]}$} ;
   \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-  \draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\mathcal Q_3^{[n-2]}$};
+  \draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0.1) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\mathcal Q_3^{[n-2]}$};
   \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 
-  \draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\mathcal Q_3^{[n-1]}$}   ;
+  \draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0.1) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\mathcal Q_3^{[n-1]}$}   ;
   \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
@@
   %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
-  \draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
+  \draw[-implies,double equal sign distance,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
   \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
-  \draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {};
   \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
-  \draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {};
+  \draw[-implies,double equal sign distance,red] (Q4)--(DOTS)  node[pos=.5,above] {};
   \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
@@
   \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
-  \draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {};
-  \draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {};
-  \draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {};
+  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
 

### 2018-03-06 Grassmannian_cells.tex
Section 5.1 edits

@@
 Here we consider the short exact sequence 
-\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
-where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
+\begin{equation}
+  \label{eq:tau sequence}
+  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
+\end{equation}
+where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
 Then in the same way as above we obtain the map
@@
 For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(H_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
-In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.
+In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.
 
@@
 
-The 2-quiver $\cQ_2^{[r]}$ associated to the (truncated) preprojective $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
+The 2-quiver $\cQ_2^{[r]}$ associated to $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
 \[\begin{tikzpicture}
@@
   The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
-  \begin{equation*}
+  \begin{equation}
     \label{eq:case2}
@@
     \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
-    \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
-  \end{equation*}
+    \cong\big\langle (2,e)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
+  \end{equation}
   and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
@@
   \end{align}
+  The image of a nonzero map $\tilde P_{m,i}\to\tau\tilde P_{m+1}^{[r]}$ is the representation $\tilde K_m$ from the appropriate sequence \eqref{eq:tau sequence}.
+  Such a map is surjective if $m\ge3$ and for $m=2$ has image with support quiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,e)$.
+  In view of Corollary~\ref{cor:perpendicular}, the sequence \eqref{eq:tau sequence} gives rise to an isomorphism 
+  \[\Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)\cong\Ext\big(\tilde P_{m+1}^{[r]},\tilde K_m\big).\]
+
+  Finally note for $0\le r\le n-2$ that there exists a short exact sequence
+  \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[r]},P_m\big)}{\Ext\big(P_{m+1}^{[r+1]},P_m\big)}.\]
+  Thus a basis of $\Ext\big(P_{m+1}^{[r]},P_m\big)$ can be obtained by taking the last $r$ elements of a basis for $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
+  The choice of 2-arrows in $\cQ_{m+1}^{[r]}$ should be viewed as a combinatorial shadow of the isomorphisms above.
 \end{remark}
 
+We are now ready to define the 2-quivers $\cQ_{m+1}^{[r]}$ for $m\ge3$.
+This will be by induction, so assume we have already constructed the 2-quivers $\cQ_m^{[s]}$ for $0\le s\le n-1$ and define the 2-quivers $\cQ_{m,i}^{[s]}:=\alpha_i^{(-1)^{m+1}}.\cQ_m^{[s]}$ for $1\le i\le n$.
+Then we may take the underlying quiver of $\cQ_{m+1}^{[r]}$ to be
+\[Q_{m+1}^{[r]}:=
+  \begin{cases}
+    Q_{m,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{m,i} & \text{if $m$ is even;}\\
+    Q_{m,1}^{[1]}\sqcup\coprod\limits_{i=2}^{n-r} Q_{m,i} & \text{if $m$ is odd.}
+  \end{cases}\]
+For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
 \begin{remark}
-  Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$.
-  Moreover, (\ref{eq:homext}) for $m=3$ yields 
-  \[\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).\]
-  This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map 
-  \[(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})\]
-  for $i=1,\ldots,n-1$.
-  Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
-  \[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
-  Note that the image of the homomorphism corresponding to the basis element spanning 
-  \[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
-  corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
-  This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-
-  This gives a justification for the original definition of the 2-arrows in $\cQ_3^{[r]}$.
-
-    In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism 
-    \[\Ext\big(\tilde P_{m+1}^{[k]},\tilde P_{m,k}\big)\cong\Ext\big(\tilde P_{m+1}^{[k]},\tau\tilde P_{m+1}^{[k]}\big).\]
-    These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_{m+1}^{[k]}$.
-    Finally note that there exists a short exact sequence
-    \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[k]},P_m\big)}{\Ext\big(P_{m+1}^{[k+1]},P_m\big)}.\]
-    Thus a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
+  For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[s]}\cong\tilde P_{m-1}^{[s]}$ can uniquely be found as a quotient of $\tilde P_{m,s}$.
+  This is reflected in the structure of the $2$-quivers as we can find $\cQ_{m-1}^{[s]}$ as a subquiver of $\cQ_{m,s}$.
+  In the diagrams for 2-quivers given here, this sub-2-quiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,s}$.
 \end{remark}
 
-The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the (truncated) preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the (truncated) preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
-First, we define
-\[\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},\]
-i.e. we translate all vertices -- understood as vertices of $\widetilde{K(n)}$ -- and (2-)arrows by $\alpha_n^{-1}$.
-Then $\cQ_3^{[k]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
-\[
-\begin{tikzpicture}[scale=1.35]
-  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
-  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
-  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
-  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
-  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
-
-  \draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$\mathcal Q_3^{[1]}$} ;
-  \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
-  \draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
-  \draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
-  \draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
-
-  \draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$\mathcal Q_3^{[2]}$};
-
-  \draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.6) node (D31) { $\vdots$} +(1,0) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$\mathcal Q_3^{[n-3]}$} ;
-  \draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
-  \draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
-  \draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
-  \draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
-
-  \draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0.1) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$\mathcal Q_3^{[n-2]}$};
-  \draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
-  \draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
-  \draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
-  \draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
-
-  \draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0.1) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$\mathcal Q_3^{[n-1]}$}   ;
-  \draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
-  \draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
-  \draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
-  %\tikzstyle{every node}=[circle,fill=white!10]
-  \node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
-  %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
-  \draw[-implies,double equal sign distance,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
-  \node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
-  \draw[-implies,double equal sign distance,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {};
-  \node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
-  \draw[-implies,double equal sign distance,red] (Q4)--(DOTS)  node[pos=.5,above] {};
-  \node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};
-
-  \node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
-  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {};
-  \draw[-implies,double equal sign distance,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {};
-  \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
-
-\end{tikzpicture}
-\] 
-To avoid cluttering the diagram, we did not label the vertices in the illustration.
-Observe that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that the target of the $2$-arrow, again colored red, into $\cQ_{2,n-1}$ is the vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
-In general, the 2-arrow from $\cQ_3^{[i]}$ into $\cQ_{2,i}$ has target the vertex corresponding to $(1,e)$ in $\widetilde{K(n)}$.
-We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.
-
-\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
-$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
-This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
-for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
-\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
-Note that the image of the homomorphism corresponding to the basis element spanning 
-\[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
-corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
-This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.
-In view of Lemma~\ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$.
-%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
-\end{remark}
-%It remains to consider the case when $m$ is even. Lemma~\ref{AR} yields
-%\begin{align}\label{eq:case2}
- %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
-%\end{align}
-Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $\tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
-%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
-%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
-%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
-Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$, $j=0,\ldots, n-1$ and $l=m+1$, $j=n-1,\ldots,k$.
-As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
-Moreover, we define 
-\[\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{-1}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.\]
-
-For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$.
-This can also be seen on the level of $2$-quivers, i.e.
-we find $\cQ_{m-1}^{[k]}$ as a subquiver of $\cQ_{m,k}$.
-More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.
-Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow.
-Thereby, the $2$-arrow connects $\mathcal Q_{m+1}^{[k]}$ to the subquiver $\cQ_{m-1}^{[k]}$ in $\cQ_{m,k}$.
-This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
-\\
 \begin{flushleft}
 \begin{tikzpicture}[scale=0.97]
-\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ;
+\draw (0,4) node (A1) {\footnotesize$Q_{m-1,1}$}
+  +(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,r}$}
+  +(1.65,0) node (B1) {\footnotesize$Q_{m-1,2}$}
+  +(1.65,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$}
+  +(3,0) node (B11) {\footnotesize$\dots$}
+  +(4.55,0) node (D1) {\footnotesize$Q_{m-1,n-1}$}
+  +(4.55,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}
+  +(6.4,0) node (E1) {\footnotesize$Q_{m-2,2}$}
+  +(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}
+  +(7.75,0) node (A1b) {\footnotesize$\dots$}
+  +(9.6,0) node (B1b) {\footnotesize$Q_{m-2,r+1}$}
+  +(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[r]}$}
+  +(11.2,0) node (B11b) {\footnotesize$\dots$}
+  +(12.8,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
+  +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
+  +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$};
 \node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
@@
 \node (Q91)[draw=black,fit={(Q81) (A1)}]{};
-\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
-\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
-\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
-\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
-\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
-\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
-\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
-\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
-\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};
-
-\draw (0,0) node (B) {$\mathcal Q_{m,k+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[k]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
+\draw[implies-,double equal sign distance,red] (D1b)--(E1b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q11)--(B11b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q21)--(B1b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q31)--(A1b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q41)--(E1) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q51)--(D1) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q61)--(B11) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q71)--(B1) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q81)--(A1) node[pos=.5,above] {};
+
+\draw (4.45,0) node (B) {$\mathcal Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 
-\draw[<-,red] (D)--(E) node[pos=.5,above] {};
-\draw[->,red] (Q1)--(C) node[pos=.5,above] {};
-\draw[->,red] (Q2)--(B1) node[pos=.5,above] {};
-\draw[->,red] (Q2b)--(B) node[pos=.5,above] {};
+\draw[implies-,double equal sign distance,red] (D)--(E) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q1)--(C) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q2)--(B1) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q2b)--(B) node[pos=.5,above] {};
 
 \node (PMK) [draw=black,fit={(Q2b) (B)}]{};
-\draw[->,red,thick] (PMK)--(Q31);
+\draw[-implies,double equal sign distance,red,thick] (PMK)--(P11b);
 \end{tikzpicture}
@@
 \noindent 
-%In order to keep the diagrams as simple as possible we did not insert the labels of the vertices.
-As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$.
- As already mentioned two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
-$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G_{K(n)}\tbfe (\beta)\in\NN^{K(n)_0}$$
-where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[k]})_0$.
-
-\begin{theorem}\label{thm:2quivercells}
+As already mentioned two different vertices of $\mathcal Q_m^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[r]})_0$ are defined by
+\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[r]})_0$.
+
+\begin{theorem}\mbox{}
+  \label{thm:2quivercells}
   \begin{enumerate}
-\item The cells of the cell decomposition of $\Gr_\tbfe(\tilde P_m^{[k]})$ (resp.
-$Gr_\bfe( P_m^{[k]})$) induced by Theorem \ref{cellscover}  can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[k]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
+    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_m^{[r]}\big)$ (resp.
+$Gr_\bfe\big(P_m^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
 $\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
-
     \item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
-$\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ (resp.
-$\chi(\Gr_{\bfe }(P_m^{[k]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$  (resp.
-$\bfe$) of the $2$-quiver of $\mathcal Q_m^{[k]}$.
-
+$\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[r]}))$ (resp.
+$\chi(\Gr_{\bfe }(P_m^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$  (resp.
+$\bfe$) of the $2$-quiver of $\mathcal Q_m^{[r]}$.
   \end{enumerate}
@@
 
-We proceed by induction on $m$ and $k$.
+We proceed by induction on $m$ and $r$.
 The case of the representation $\tilde P_1$ is trivial.
-We have $(\tilde P_2^{[k]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[k]}$ .
-Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[k]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[k]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[k]}$ is strong successor closed.
-
-  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[k]}$ and consider the short exact sequence
+We have $(\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[r]}$ .
+Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[r]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[r]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[r]}$ is strong successor closed.
+
+  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[r]}$ and consider the short exact sequence
   \[
-    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
+    \ses{\tilde P_m}{\tilde P_{m+1}^{[r-1]}}{\tilde P_{m+1}^{[r]}}.
   \]
-  We have $(\mathcal Q_{m+1}^{[k-1]})_0=(\mathcal Q_{m+1}^{[k]})_0\coprod{}(\mathcal Q_{m,k})_0$.
-	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[k-1]})_0\coprod{}(\mathcal Q_{m,k})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
+  We have $(\mathcal Q_{m+1}^{[r-1]})_0=(\mathcal Q_{m+1}^{[r]})_0\coprod{}(\mathcal Q_{m,r})_0$.
+	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[r-1]})_0\coprod{}(\mathcal Q_{m,r})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
  % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition~\ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[k]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[k]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[k]}$ is considered as a $2$-quiver of $\mathcal Q_{m,k}$.
-  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[k]}$ is connected to $\mathcal Q_{m-1}^{[k]}$ by a $2$-arrow.
+  By Proposition~\ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[r]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[r]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[r]}$ is considered as a $2$-quiver of $\mathcal Q_{m,r}$.
+  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[r]}$ is connected to $\mathcal Q_{m-1}^{[r]}$ by a $2$-arrow.
 This shows the first claim.

### 2018-03-06 Grassmannian_cells.tex
Sketch of bijection proof, more details needed

@@
 
-For $m\ge2$ and $1\le k\le n-1$, write $D_m^{(k)}$ for the maximal Dyck path obtained from $D_m$ by removing the first $k$ copies of $D_{m-1}$.
-Extending this notation we also set $D_m^{(0)}:=D_m$.
+For $m\ge2$ and $1\le r\le n-1$, write $D_m^{[r]}$ for the maximal Dyck path obtained from $D_m$ by removing the first $r$ copies of $D_{m-1}$.
+Extending this notation we also set $D_m^{[0]}:=D_m$.
 \begin{remark}
-  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{(n-1)}$, $m\ge3$, with $D_{m-1}^{(1)}$.
+  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{[n-1]}$, $m\ge3$, with $D_{m-1}^{[1]}$.
 \end{remark}
-For fixed $m\ge2$ and $1\le r\le n-1$, we write $D_{m-1,r}$ for the $r$-th copy of $D_{m-1}$ inside $D_m$.
-For notational convenience we also set $D_{m-1,n}:=D_m^{(n-1)}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
-For $m\ge2$ and $1\le k\le n-1$, the maximal Dyck paths $D_{m-1,r}$, $k+1\le r\le n$, naturally identify with subpaths of $D_m^{(k)}$.
+For fixed $m\ge2$ and $1\le i\le n-1$, we write $D_{m-1,i}$ for the $i$-th copy of $D_{m-1}$ inside $D_m$.
+For notational convenience we also set $D_{m-1,n}:=D_m^{[n-1]}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
+For $m\ge2$ and $1\le r\le n-1$, the maximal Dyck paths $D_{m-1,i}$, $r+1\le i\le n$, naturally identify with subpaths of $D_m^{[r]}$.
 
@@
 Let $E_m=H_m\sqcup V_m$, where $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
-Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{r=1}^n E_{m-1,r}$, where $E_{m-1,r}$ denotes the edges of $D_{m-1,r}$.
-The set $E_{m-1,r}$ is naturally partitioned into its subsets $H_{m-1,r}$ and $V_{m-1,r}$ of horizontal and vertical edges.
+Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{i=1}^n E_{m-1,i}$, where $E_{m-1,i}$ denotes the edges of $D_{m-1,i}$.
+The set $E_{m-1,i}$ is naturally partitioned into its subsets $H_{m-1,i}$ and $V_{m-1,i}$ of horizontal and vertical edges.
 
@@
 \begin{remark}
-  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.  Write $\cC_m^{(k)}$ for the set of all compatible pairs in $D_m^{(k)}$.
+  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{[r]}$, $1\le r\le n-1$.  Write $\cC_m^{[r]}$ for the set of all compatible pairs in $D_m^{[r]}$.
 \end{remark}
@@
   \label{def:piecewise compatibility}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,r}$ and $v\in V_{m-1,r}$.
+  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,i}$ and $v\in V_{m-1,i}$.
 \end{definition}
 \begin{remark}
-  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{(k)}$, $1\le k\le n-1$.
+  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{[r]}$, $1\le r\le n-1$.
 \end{remark}
@@
 \begin{corollary}
-  For $m\ge4$ and $0\le k\le n-1$, consider $S_H\subset H_m^{(k)}$ and $S_V\subset V_m^{(k)}$ so that $(S_H,S_V)$ is piecewise compatible.
-  Assume $\big(S_H^{(k+1)},S_V^{(k+1)}\big)\in\cC_m^{(k+1)}$.
-  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $V_m^{(k+1)}\subset S_V$.
+  \label{cor:piecewise not compatible}
+  For $m\ge4$ and $0\le r\le n-1$, consider $S_H\subset H_m^{[r]}$ and $S_V\subset V_m^{[r]}$ so that $(S_H,S_V)$ is piecewise compatible.
+  Assume $\big(S_H^{[r+1]},S_V^{[r+1]}\big)\in\cC_m^{[r+1]}$.
+  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{[r+1]}\subset S_{H,r+1}$ and $V_m^{[r+1]}\subset S_V$.
 \end{corollary}
@@
   We begin with the reverse implication.
-  First note that there are $(n-k)u_{m-1}-u_{m-2}$ horizontal edges and $(n-k)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{(k)}$. 
-  It follows that $V_{m-2}^{(k+1)}\sqcup V_m^{(k+1)}$ contains $n(n-k)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{(k+1)}\sqcup H_m^{(k+1)}$ contains $n(n-k)u_{m-2}-nu_{m-3}$ horizontal edges.
-
-  Assuming $H_{m-2}^{(k+1)}\subset S_{H,k+1}$ and $S_V^{(k+1)}=V_m^{(k+1)}$, we have $S_V\cap V_{m-2}^{(k+1)}=\varnothing$ and $S_H\cap H_m^{(k+1)}=\varnothing$ by piecewise compatibility.
-  Let $h\in H_m^{(k)}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{(k+1)}$.
-  Then, since there are $(n-k)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{(k+1)}$, the local shadow path $D(h;S_H)$ contains $n\big((n-k)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
+  First note that there are $(n-r)u_{m-1}-u_{m-2}$ horizontal edges and $(n-r)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{[r]}$. 
+  It follows that $V_{m-2}^{[r+1]}\sqcup V_m^{[r+1]}$ contains $n(n-r)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{[r+1]}\sqcup H_m^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ horizontal edges.
+
+  Assuming $H_{m-2}^{[r+1]}\subset S_{H,r+1}$ and $S_V^{[r+1]}=V_m^{[r+1]}$, we have $S_V\cap V_{m-2}^{[r+1]}=\varnothing$ and $S_H\cap H_m^{[r+1]}=\varnothing$ by piecewise compatibility.
+  Let $h\in H_m^{[r]}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{[r+1]}$.
+  Then, since there are $(n-r)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{[r+1]}$, the local shadow path $D(h;S_H)$ contains $n\big((n-r)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
   Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
@@
   For the forward implication, we work by induction on $m\ge4$.
-  Consider a pair $(S_H,S_V)$ for $D_4^{(k)}$ as above which is not compatible.
-  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{(k)}$ for the blocking edge of $S_H$.
+  Consider a pair $(S_H,S_V)$ for $D_4^{[r]}$ as above which is not compatible.
+  Following Theorem~\ref{th:blocking edge conditions}, write $h\in H_4^{[r]}$ for the blocking edge of $S_H$.
   Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
-  Since $(S_H^{(k+1)},S_V^{(k+1)})$ is compatible, we must have $h\in H_{3,k}$.
-  But observe that $|V_m^{(k)}|=(n-k)n-1$ and so the divisibility condition above implies $h\in H_{3,k}^{(n-1)}$.
+  Since $\big(S_H^{[r+1]},S_V^{[r+1]}\big)$ is compatible, we must have $h\in H_{3,r}$.
+  But observe that $|V_m^{[r]}|=(n-r)n-1$ and so the divisibility condition above implies $h\in H_{3,r}^{[n-1]}$.
   But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
-  Identifying $H_{3,k}^{(n-1)}$ with $H_2^{(1)}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{(k+1)}\subset H_2^{(1)}$.
-  Then by piecewise compatibility, the vertical edge of $H_2^{(1)}$ cannot be an element of $S_V$ and we must have $V_4^{(k+1)}\subset S_V$.
-  By piecewise compatibility again, this implies $H_4^{(k+1)}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{(k+1)}\subset S_H$.
+  Identifying $H_{3,r}^{[n-1]}$ with $H_2^{[1]}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{[r+1]}\subset H_2^{[1]}$.
+  Then by piecewise compatibility, the vertical edge of $H_2^{[1]}$ cannot be an element of $S_V$ and we must have $V_4^{[r+1]}\subset S_V$.
+  By piecewise compatibility again, this implies $H_4^{[r+1]}\cap S_H=\varnothing$ and so $D(h;S_H)=hv_{u_3}$ implies $H_2^{[r+1]}\subset S_H$.
 
@@
   By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
-  Thus by induction, we must have $H_{m-3}^{(k+1)}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{(k+1)}\subset\Omega^{-1}S_H$.
-  It follows from piecewise compatibility that $H_{m-1}^{(k+1)}\cap(\varphi^*)^{-1}S_V=\varnothing$.
-  But then by the definition of $\varphi^*$ we have $V_{m-2}^{(k+1)}\cap S_V=\varnothing$ and $S_V^{(k+1)}=V_m^{(k+1)}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
+  Thus by induction, we must have $H_{m-3}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{[r+1]}\subset\Omega^{-1}S_H$.
+  It follows from piecewise compatibility that $H_{m-1}^{[r+1]}\cap(\varphi^*)^{-1}S_V=\varnothing$.
+  But then by the definition of $\varphi^*$ we have $V_{m-2}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_m^{[r+1]}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
   Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
-  But this can only occur if $H_{m-2}^{(k+1)}\subset S_H$ since $H_m^{(k+1)}\cap S_H=\varnothing$ by piecewise compatibility.
+  But this can only occur if $H_{m-2}^{[r+1]}\subset S_H$ since $H_m^{[r+1]}\cap S_H=\varnothing$ by piecewise compatibility.
 \end{proof}
@@
 The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{llz} and the categorification of these variables using representations of $K(n)$ \cite{cc,ck}.
-\begin{theorem}\cite{llz}
+\begin{theorem}
+  \label{th:combinatorial euler}
+  \cite{llz}
   For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
@@
 
-Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~ ?%\ref{???}.
+Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{celldec}.
+We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_m^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
+\begin{theorem}
+  \label{th:compatible cells}
+  Compatible pairs label cells in $\Gr_\bfe(P_m^V)$.
+\end{theorem}
+\begin{proof}
+  The recursive construction of the 2-quivers $\cQ_m^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_m^{[r]}$.
+  This provides a bijection of these vertices with the edges of $D_m^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges).
+  Then Corollary~\ref{cor:piecewise not compatible} shows that under this bijection a subset $\beta\in(Q_m^{[r]})_0$ is strong successor closed in $\cQ_m^{[r]}$ if and only if the corresponding pair of subsets $\big(S_H(\beta),S_V(\beta)\big)$ is compatible.
+\end{proof}
 

### 2018-03-07 Grassmannian_cells.tex
Some polish in section 5.2

@@
 Then we may take the underlying quiver of $\cQ_{m+1}^{[r]}$ to be
-\[Q_{m+1}^{[r]}:=
+\begin{equation}
+  \label{eq:recursive 2-quivers}
+  Q_{m+1}^{[r]}:=
   \begin{cases}
@@
     Q_{m,1}^{[1]}\sqcup\coprod\limits_{i=2}^{n-r} Q_{m,i} & \text{if $m$ is odd.}
-  \end{cases}\]
+  \end{cases}
+\end{equation}
 For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
@@
   \cite{llz}
-  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
+  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have 
+  \[\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|.\]
 \end{theorem}
 
-Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{celldec}.
+Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\Gr_\bfe(P_m)$ found in Theorem~\ref{celldec}.
+In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_m^V)$ for truncated preprojectives $P_m^V$ are also naturally labeled by compatible pairs.
 We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_m^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
@@
   \label{th:compatible cells}
-  Compatible pairs label cells in $\Gr_\bfe(P_m^V)$.
+  \sayD{Fix abuse of notation $H_m$.}
+  For $m\ge1$ and $V\in\Gr(H_{m-1})$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_m^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_m^{[r]}$, where $r=\dim V$.
 \end{theorem}
@@
   The recursive construction of the 2-quivers $\cQ_m^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_m^{[r]}$.
-  This provides a bijection of these vertices with the edges of $D_m^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges).
-  Then Corollary~\ref{cor:piecewise not compatible} shows that under this bijection a subset $\beta\in(Q_m^{[r]})_0$ is strong successor closed in $\cQ_m^{[r]}$ if and only if the corresponding pair of subsets $\big(S_H(\beta),S_V(\beta)\big)$ is compatible.
+  Indeed, when considering the recursive construction of the 2-quiver $Q_m^{[r]}$ from \eqref{eq:recursive 2-quivers}, we order the component quivers $Q_{m-1,i}$ and $Q_{m-1,*}^{[1]}$ naturally according to their indices so that $Q_{m-1,*}^{[1]}$ comes last.
+  This provides a bijection of these vertices with the edges of $D_m^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges) of $D_m^{[r]}$.
+
+  Given a strong successor closed subset $\beta\subset(Q_m^{[r]})_0$, we define a pair of subsets $S_H(\beta)\subset H_m^{[r]}$ and $S_V(\beta)\subset V_m^{[r]}$ as follows: a vertical edge $v\in V_m^{[r]}$ is in $S_V(\beta)$ exactly when the corresponding vertex of $Q_m^{[r]}$ is in $\beta$ while a horizontal edge $h\in H_m^{[r]}$ is in $S_H(\beta)$ exactly when the corresponding vertex of $Q_m^{[r]}$ is \emph{not} in $\beta$.
+  Then Corollary~\ref{cor:piecewise not compatible} shows that under this bijection a subset $\beta\in(Q_m^{[r]})_0$ is strong successor closed in~$\cQ_m^{[r]}$ if and only if the corresponding pair of subsets $\big(S_H(\beta),S_V(\beta)\big)$ is compatible.
+  Applying Theorem~\ref{thm:2quivercells} completes the proof.
 \end{proof}

### 2018-03-11 Grassmannian_cells.tex
Committing to pull

@@
   On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
-  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a preprojective representation.
+  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
   As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
@@
 These filtration can be successively described by short exact sequences.
-The main advantage when passing to the universal covering is that the preprojective subrepresentations of the same dimension become orthogonal, a property which rigidifies the situation in a sense.
+The main advantage when passing to the universal covering is that the preprojective representations covering the same dimension vector below become orthogonal, a property which rigidifies the situation in a sense.
 In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
@@
 For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{llz}.
-The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
+The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians \cite{rupel}.
 A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.

### 2018-03-11 Grassmannian_cells.tex
Some intro edits

@@
 A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.
-\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
-
--something about compatible pairs and combinatorial construction of cluster variables\\
--statement of our results\\
--something about torus actions and the universal cover\\
--something about cell decompositions of quiver Grassmannians\\
--acknowledgements?\\
+
 The paper is organized as follows.
-In Section \ref{sec:covering}, we collect several results concerning quiver covering theory.
-In Section \ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which is needed to investigate the quiver Grassmannians attached to preprojective representations later.
-We first focus on preprojective and preinjective representations, written as $P_m$ and $I_m$, which enables us to investigate a special class of indecomposable representations in Section \ref{sec:truncated preprojectives} - we call them truncated preprojective representations.
-We proof that every preprojective representation admits a filtration by preprojectives of smaller dimensions such that all quotients appearing are actually truncated preprojective representations.
-In Section \ref{Lifting}, we use this together with the fact that every preprojective representation can be lifted to the universal covering in order to construct lifted filtrations.
+In Section~\ref{sec:covering}, we collect several results concerning quiver covering theory.
+In Section~\ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which are needed later to investigate the quiver Grassmannians attached to preprojective representations.
+We first focus on preprojective and preinjective representations, written as $P_m$ and $I_m$, which enables us to investigate a special class of indecomposable representations in Section~\ref{sec:truncated preprojectives} -- we call them truncated preprojective representations.
+We prove that every preprojective representation admits a filtration by preprojectives of smaller dimensions such that all quotients appearing are actually truncated preprojective representations.
+In Section~\ref{Lifting}, we use this together with the fact that every preprojective representation can be lifted to the universal covering in order to construct lifted filtrations.
 Throughout this section, we collect many results which will turn out to completely reveal the structure of quiver Grassmannians attached to (truncated) preprojective representations.
 
-The aim of Section \ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
-This is obtained by combining a torus action on quiver Grassmannians which is introduced in Section \ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations in Section \ref{sec:fibrations}.
-Our first main result is Theorem \ref{thm:torusfixedpoints} which may be formulated as follows.
+The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
+This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations.
+Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
 \begin{thm}
-  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q$.
-Then there exists a map $d:\supp(\hat X)\to\ZZ$ - with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ - which induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
+  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a torus action on $\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
 This torus action can be iterated in such a way that the remaining torus fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
-As far as generalized Kronecker quivers are concerned, we can show in Theorem \ref{thm:truncpp} that all quiver Grassmannians attached to truncated representations are smooth - actually, they only depend on dimension vectors.
-In view of results of Bia\l{}ynicki-Birula \cite{bb} - which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety - we can use this result to lift the investigation of the quiver Grassmannians to the universal covering quiver.
-This is insofar important as results as Corollary \ref{cor:perpendicular} are available which do not hold on the original quiver.
-Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems \ref{cellscover} and \ref{celldec}.
- \begin{thm} For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
+As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
+In view of results of Bia\l{}ynicki-Birula~\cite{bb} -- which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety -- we can use this result to lift the investigation of the geometry of quiver Grassmannians to the universal covering quiver.
+This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
+Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
+\begin{thm} 
+  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
 \end{thm}
-Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.
+\noindent Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.
 
 In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
-Theorem \ref{thm:2quivercells} can be formulated as follows.\begin{thm}
-With every truncated preprojective representation $P_{m+1}^V$ we can associated a $2$-quiver $\mathcal Q_{m+1}^{[\dim V]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[\dim V]})_0$.
+Theorem \ref{thm:2quivercells} can be formulated as follows.
+\begin{thm}
+  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
   In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
 \end{thm}
+\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
 \sayT{Insert something about Dyck path combinatorics and the correspondence here}
 \sayT{maybe we can erase some parts which show up twice in the introduction?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-03-11 Grassmannian_cells.tex
Some intro edits

@@
 \end{thm}
+
+The results of \cite{rupel} giving a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$ suggest the following.
+\begin{conjecture}
+  There exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the affine cell corresponding to a compatible pair $(S_H,S_V)$ has dimension...
+\end{conjecture}
 \sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}

### 2018-03-11 Grassmannian_cells.tex
Some polishing through section 3

@@
 \newtheorem{claim}[theorem]{Claim}
+\newtheorem{conjecture}[theorem]{Conjecture}
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \section{Introduction}
-\noindent A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension.
+\noindent A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension vector.
 In recent years, interest in quiver Grassmannians has grown considerably.
@@
 The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
-It turns out that these are precisely those representations which can be obtained from indecomposable representations of dimension $(d,1)$ when applying reflection functors.
+It turns out that these are precisely those representations which can be obtained from indecomposable representations with dimension vector $(d,1)$ when applying reflection functors.
 Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
@@
 
-Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
+Let $W_Q$ be the free (non-abelian) group generated by $Q_1$.  
 Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
@@
 Note that in our definition every covering quiver has infinitely many connected components, but each of its connected components is a covering in the sense of \cite{gab}.
-As indecomposable representations live on one of these components this distinction will be irrelevant.
+As indecomposable representations live on one of these components, this distinction will be irrelevant.
 Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\rep \widetilde Q\to\rep \hat Q$.
@@
 The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\rep\hat Q$ and on $\ZZ^{\hat Q_1}$.
-We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
+%We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
 The analogous observation can also be made for $\widetilde Q$.
@@
 Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
-For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.
 
@@
   in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
-  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.
+  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker(ev_V)=0$ for $m=1$ and thus $ev_V$ is injective in this case.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Truncated Preprojectives}
@@
 
+We collect below several basic homological results related to preprojective representations.
 \begin{lemma}
@@
 \begin{proof}
- As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain isomorphisms 
+ As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} gives isomorphisms 
   \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
@@
   \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
-  The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
-  The rigidity of $P_{m+1}$ gives the final claim.
+  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
 \end{proof}
@@
   But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
-  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
   In this case, there are isomorphisms
@@
 \end{proof}
-
 \begin{remark}
@@
 \end{remark}
+
 For the truncated preprojective representations $P_{m+1}^V$, we have  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
-They will play an important role when describing quiver Grassmannians of preprojective representations recursively.
-For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
+These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
+For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write 
+\[R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
+for the affine space of representations of $K(n)$ with dimension vector $d$. 
 \begin{proposition}
@@
   \begin{enumerate}
-    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
-    \item The indecomposable representations of dimension $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$ with $\dim V=r$. 
-    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
+    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
+    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$ with $\dim V=r$. 
+    \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   \end{enumerate}
@@
   By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives of dimension $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.
+  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives with dimension vector $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.
 
@@
 
+\begin{lemma}
+  \label{le:projective subrepresentations}
+  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+\end{lemma}
+\begin{proof}
+  We proceed by induction on $m$.
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.
+
+  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
+\end{proof}
+
 For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
@@
 Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
-\begin{lemma}
-  \label{le:projective subrepresentations}
-  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
-\end{lemma}
-\begin{proof}
-  We proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.
-
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-\end{proof}
 \begin{corollary}
@@
 \begin{proof}
-  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
+  This is clear for $m=1$ and follows in general by applying the recursion \eqref{eq:recursive covers}.
 \end{proof}
@@
   We make use of this fact below, stating only the support of the representation (also specifying those dimensions which are not one) and do not state the particular maps present in the lifts.
-  We call this the \emph{support quiver} of the representation and let $W_n$ act on these quivers by translating all vertices.
+  We call this the \emph{support quiver} of the representation and let $W_n$ act on these quivers by translating all vertices and arrows.
 
@@
     \label{dia:P2 quiver}
-    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n)}
+    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n).}
   \end{equation}
@@
     \label{dia:P3 quiver}
-    \xymatrix@R40pt@C10pt{&n-1&\\ \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[ru]&\cdots&\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lu]}
+    \xymatrix@R40pt@C10pt{&n-1&\\ \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[ru]&\cdots&\alpha_n^{-1}.\cA_n,\ar_{\alpha_n}[lu]}
   \end{equation}
@@
   Then $\tilde P_{2,j}\subset\tilde P_3$ has one-dimensional spaces at each vertex of the quiver
-  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_j^{-1})\ar_{\alpha_j}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{j-1}}[ld]\ar^(.65){\alpha_{j+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_j^{-1}\alpha_1)&\cdots&(1,\alpha_j^{-1}\alpha_{j-1})&&(1,\alpha_j^{-1}\alpha_{j+1})&\cdots&(1,\alpha_j^{-1}\alpha_n)}\]
+  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_j^{-1})\ar_{\alpha_j}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{j-1}}[ld]\ar^(.65){\alpha_{j+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_j^{-1}\alpha_1)&\cdots&(1,\alpha_j^{-1}\alpha_{j-1})&&(1,\alpha_j^{-1}\alpha_{j+1})&\cdots&(1,\alpha_j^{-1}\alpha_n).}\]
 
@@
     \label{dia:P4 quiver}
-    \xymatrix@R40pt@C10pt{&n-1\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1&\cdots&\alpha_n.\cB_n}
+    \xymatrix@R40pt@C10pt{&n-1\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1&\cdots&\alpha_n.\cB_n,}
   \end{equation}
@@
   \[\xymatrix@R40pt@C10pt{&&&2n-3&&&\\
-    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
+    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
   with top vertex $(1,e)$ having dimension $2n-3$.
@@
     &&&n-1&&&\\
-    \alpha_j\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_j\alpha_{j-1}^{-1}.\cA_{j-1}\ar^(.35){\alpha_{j-1}}[ru]&&\alpha_j\alpha_{j+1}^{-1}.\cA_{j+1}\ar_(.35){\alpha_{j+1}}[lu]&\cdots&\alpha_j\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
+    \alpha_j\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_j\alpha_{j-1}^{-1}.\cA_{j-1}\ar^(.35){\alpha_{j-1}}[ru]&&\alpha_j\alpha_{j+1}^{-1}.\cA_{j+1}\ar_(.35){\alpha_{j+1}}[lu]&\cdots&\alpha_j\alpha_n^{-1}.\cA_n,\ar_{\alpha_n}[lllu]}\]
   where the central vertex is $(1,\alpha_j)$.
@@
 It will be important to understand the possible subrepresentations of the truncated preprojective representations $\tilde P_{m+1}^I$.
-
 \begin{lemma}
@@
 
-In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
-
+In what follows, we will need to carefully understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
 \begin{lemma}
@@
   The support quiver of $\tilde P_4^I$ is given by the following analogue of the quiver \eqref{dia:P4 quiver} of $\tilde P_4$:
-  \[\xymatrix@R40pt@C10pt{&n-1-|I|\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1^I&\cdots&\alpha_n.\cB_n^I}\]
+  \[\xymatrix@R40pt@C10pt{&n-1-|I|\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1^I&\cdots&\alpha_n.\cB_n^I,}\]
   where the top vertex of dimension $n-1-|I|$ is again $(2,e)$ and $\cB_i^I$ is simply a space of dimension~$n-1-|I|$ if $i\in I$ and otherwise is the quiver
   \[\xymatrix@R40pt@C10pt{&&&2n-3-|I|&&&\\
-    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
+    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}.\cA_n.\ar_{\alpha_n}[lllu]}\]
 \end{example}
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
-Write $\Ind(K(n),d)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ of dimension $d$ for $d\in\NN^{K(n)_0}$.
+Write $\Ind(K(n),d)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$.
 As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind(K(n),d)$.
@@
 Fix a cell $B_i\subset\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$.
-As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fiber over $B_i\times C_0$ is empty or that the fiber is of constant dimension building a new cell $CB_i$.
+As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fiber over $B_i\times C_0$ is empty or that the fiber is of constant dimension, thus building a new cell $CB_i$.
 For all representations $U\in CB_i$ we have $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$ because $\pi_{m,\uj}^{\bf j}$ is surjective and $\pi_{m,\uj'}^{j_l}(U)=\tilde P_{m}^{\uj}$.
 
-In the second case, the fiber over $B_i\times C_k$ is non empty and of constant dimension building a new cell $CB_{i,k}$.
+In the second case, the fiber over $B_i\times C_k$ is non empty and of constant dimension, thus building a new cell $CB_{i,k}$.
 As we have $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$, it follows that $\pi^{\bf j'}_{m,\uj'}(U)=0$ for all representations $U\in (CB)_{i,k}$.
@@
 The second part of the Proposition says that the fibers are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma~\ref{vb}?}.
+In all other cases, the fiber dimensions only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma~\ref{vb}?}.
 Analogously to Lemma~\ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
@@
 \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
-\item Let $X\in\rep K(n)$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
+\item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
 Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
@@
 As already mentioned two different vertices of $\mathcal Q_m^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[r]})_0$ are defined by
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe(\beta)$ and  $\bfe(\beta)$ of a subset $\beta\subset(\mathcal Q_m^{[r]})_0$ are defined by
 \[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
-where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[r]})_0$.
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_m^{[r]})_0$.
 

### 2018-03-11 Grassmannian_cells.tex
Some polishing up through section 4.3

@@
   \cite[Section 4]{bb}
-  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is a vector bundle.
+  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine vector bundle.
   Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
@@
 If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
-Indeed, we can trivialize each vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
+Indeed, we can trivialize each affine vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
 
@@
 
-Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
+Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist indices $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
 \[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
@@
 Let $Q$ be an acyclic quiver.
-We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
-We can consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_i$.
+Choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
+We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
 Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
@@
 
-The next result provides conditions required of the map $d:\hat Q_0\to\ZZ$ needed to get an analogue of Lemma~\ref{le:usualGrass}
+The next result provides the conditions on the map $d:\hat Q_0\to\ZZ$ needed to get an analogue of Lemma~\ref{le:usualGrass}
 \begin{lemma}
   \label{le:degree condition} 
-  Let $\hat X$ be an indecomposable representation of $\hat Q$.
+  Let $\hat X\in\rep\hat Q$ be an indecomposable representation of $\hat Q$.
   There exists $d:\supp(\hat X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
   \begin{enumerate}
-    \item for $(i,\chi),\,(i,\chi')\in\supp(X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
-    \item for $(i,\chi),\,(j,\chi')\in\supp(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
+    \item for $(i,\chi),\,(i,\chi')\in\supp(\hat X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
+    \item for $(i,\chi),\,(j,\chi')\in\supp(\hat X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
   \end{enumerate}
@@
   For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_n\}$.
-  Since $X$ is finite-dimensional and indecomposable, the support quiver $\supp(X)$ is a connected and finite subquiver of $\hat Q$.
-  In order to prove the statement, we may assume that $(i',0)\in\supp(X)$ for some $i'\in Q_0$.
-  Let $K$ be the maximal length of a path in $\supp(X)$ starting or ending in $(i',0)$ such that the underlying graph of the path has no cycles.
-  This implies that, for $(i,\chi)\in\supp(X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.
+  Since $\hat X$ is finite-dimensional and indecomposable, the support quiver $\supp(\hat X)$ is a connected and finite subquiver of $\hat Q$.
+  In order to prove the statement, we may assume that $(i',0)\in\supp(\hat X)$ for some $i'\in Q_0$.
+  Let $K$ be the maximal length of a path in $\supp(\hat X)$ starting or ending in $(i',0)$ such that the underlying graph of the path has no cycles.
+  This implies that, for $(i,\chi)\in\supp(\hat X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.
 
@@
   for $l=2,\ldots,n$.  
-  Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(X)$.
+  Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(\hat X)$.
   %In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
@@
 
-  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ when $(j,\chi+e_\alpha)\in\supp(X)$.
+  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ when $(j,\chi+e_\alpha)\in\supp(\hat X)$.
   Now assuming $d(j,\chi')-d(i,\chi)=c_\alpha$, an analogous argument to the one above shows that $\chi'=\chi+e_\alpha$.
@@
 
-In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
+In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
 \begin{theorem}\label{thm:torusfixedpoints}
-  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
-  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
+  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
   \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
-  which is equivalent to $U$ being liftable to the universal abelian covering.
-\end{proof}
-The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
+  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
+\end{proof}
+The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
 Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
@@
 Define the $F$-polynomial of a representation $X$ by 
-$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$
-
-\begin{corollary}\label{fpoly}
+$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].$$
+
+\begin{corollary}
+  \label{fpoly}
   Let $X$ be a representation which can be lifted to the universal covering quiver.
   \begin{enumerate}
-\item 
-If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{ \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
-\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[x_i\mid i\in Q_0]$ given by $S(x_{(i,w)})=x_i$ for all $i\in Q_0$ and $w\in W_Q$.
+    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_\tbfe(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+    \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
   \end{enumerate} 
@@
 An important special case for this is the case of exceptional representations.
-In this case the quiver Grassmannians $\Gr_\tbfe(X)$ are smooth by \cite[Corollary 4]{cr}.
+In this case the quiver Grassmannians $\Gr_\bfe(X)$ are smooth by \cite[Corollary 4]{cr}.
 Moreover, every exceptional representation is a tree module by \cite{rin1} which means that it can be lifted to the universal covering.
@@
 %Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
-Write $\Ind(K(n),d)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$.
-As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind(K(n),d)$.
-\begin{proposition} \label{indecomposables}
-  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),d(m,r))$.
+Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$.
+As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
+\begin{proposition} 
+  \label{indecomposables}
+  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
+  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
 \end{proposition}
 \begin{proof}
-  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_{d(1,r)}(K(n))$.
-  As the reflection functors preserve indecomposability and isomorphism classes, by Lemma~\ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
-  \[\xymatrix{\Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),d(m+1,r))\ar[d]^g\\
-    \Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),d(m+1,r))}.\]
+  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
+  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
+  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
+    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
   As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
@@
 
-  Proposition~\ref{pro:indecomposables} and~\ref{indecomposables} imply that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
-  With other words we use that all indecomposables are truncated preprojectives.
+  Propositions~\ref{pro:indecomposables} and~\ref{indecomposables} imply that the quiver Grassmannians $\Gr_\bfe(M)$ for $M\in\Ind\big(K(n),\udim P_{m+1}^V\big)$ are all isomorphic for a fixed $\bfe\in\NN^{Q_0}$.
+  In other words, we use that all indecomposables with this dimension vector are truncated preprojectives.
 

### 2018-03-11 Grassmannian_cells.tex
Some final polishing in section 4

@@
 \begin{itemize}
-  \item We consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,e)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
-  \item We consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,e)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
+  \item We consider the lift $\tilde P_1$ satisfying $\udim(\tilde P_1)_{(1,e)}=1$ and $\udim(\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
+  \item We consider the lift $\tilde P_2$ satisfying $\udim(\tilde P_2)_{(2,e)}=\udim(\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\udim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
   \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
@@
   \label{indecomposables}
-  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
+  Let $m\geq 1$ and $d(m,r)=\udim P_{m+1}-r\udim P_m$ with $0\leq r\leq n-1$.
   The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
@@
 This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
-\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto (V\cap M,(V+M)/M).\]
+\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto \big(V\cap M,(V+M)/M\big).\]
 Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.
 
-Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
+Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$. Then we have
 $$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
@@
   \label{vb}
-  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it is an affine bundle over the image.
-  In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$, then it is an affine bundle over the image.
+  In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
 \end{theorem}
@@
   \label{eq:truncated CC2}
-  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
+  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
 \end{equation}
@@
     0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
-    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
-    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
+    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
+    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
     &0&0&0&}\]
-  By Corollary~\ref{cor:perpendicular}, we have $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)=0$ as well.
+  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
   This yields the isomorphisms
@@
   By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
-  \[\Ext(\tilde K_m,\tilde K_m)=0,\quad \Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
+  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
   For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
@@
   We work by induction on $m$.
-  When $m=1$, the claim is trivial since all quiver Grassmannians are points in this case.
+  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
   We establish the result for $m\ge2$ by proving the following more general statement:\\
@@
   Now suppose $|J|<n-1$.
-  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
+  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous and any cell decomposition will suffice.
   Thus we may assume $J\subsetneq I_0$.
@@
 
-\begin{theorem}\label{celldec}The following holds:
+\begin{theorem}
+  \label{celldec}
+  The following hold:
   \begin{enumerate}
     \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
-\item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$.
-Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
+    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
+      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
   \end{enumerate}
@@
 \begin{proof}
-The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover} taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation which can be proven using the same argument as in the proof of Lemma~\ref{le:lifts of transjectives}.
-The dual version for preinjective representations follows as $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$ respectively.
+  The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover}, taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation (c.f.\ Lemma~\ref{le:lifts of transjectives}).
+  The dual version for preinjective representations follows immediately since $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$.
 
@@
   As every exceptional representation of $K(n)$ is either preprojective or preinjective, we have
-$$X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i}$$
+  \[X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i},\]
   where we assume that $j_i\leq j_{i+1}$ and write
-$$P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}$$ 
+  \[P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}\]
   for $r'\leq r$ and $s'\leq s$.
 
-By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$. Consider the short exact sequence
+  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$.
+  Consider the short exact sequence
   \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
-By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition into affine spaces. Consider the Caldero-Chapoton map
-\[\Psi_\bfe:\Gr_\bfe(P(r'+1))\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r')).\]
-The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,V)=\AA^{\dim\Hom(V,P_{j_{r'+1}}/U)}$  for all $(U,V)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$, in particular the fibre is never empty.
-Now every subrepresentation $V$ of $P(r')$ is isomorphic to direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
+  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition into affine spaces.
+  Consider the Caldero-Chapoton map
+  \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
+  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)=\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
+  Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
   Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
-Together this yields $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
-$$\dim\Hom(V,P_{j_{r'+1}}/U)=\langle V, P_{j_{r'+1}}/U\rangle$$
-for all $(U,V)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
-By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}(P(r'))$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
-By duality, the same is true for $\Gr_{\bfe}(I(s))$.
+  Together these yield $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
+  \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
+  for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
+  By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
+  By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.
 
   Finally consider the short exact sequence
-$$\ses{I(s)}{X}{P(r)}.$$
-As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition into affine spaces
-\end{proof}
-
-As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{\udim P_m{(k)}}$.
+  \[\ses{I(s)}{X}{P(r)}.\]
+  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition into affine spaces.
+\end{proof}
+
+As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{d(m,r)}$.
 The description of the non-empty fibers in Proposition~\ref{fibers} together with Corollary~\ref{fpoly} and Theorem~\ref{celldec} yield the following:
 \begin{corollary}
-For $m\geq 2$ and $0\leq k\leq n-2$, we have 
-$$F_{\udim P_m^{(k)}}=F_{\udim P_m^{(k+1)}}F_{\udim P_{m-1}}-x^{\udim P_{m}^{(k)}}F_{\udim P_{m-2}^{(k)}}.$$
+  For $m\geq 1$ and $0\leq r\leq n-2$, we have 
+  \[F_{d(m,r)}=F_{d(m,r+1)}F_{\udim P_m}-x^{d(m,r)}F_{d(m-2,r)}.\]
 \end{corollary}

### 2018-03-11 Grassmannian_cells.tex
Some polishing in section 5.1

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Combinatorial description of non-empty cells}\label{sec:combinatorics}
+\section{Combinatorial description of non-empty cells}
+\label{sec:combinatorics}
 \noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
@@
 
-  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
+  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\implies\Gamma(2)$.
   A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
-  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
+  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.
 \end{definition}
@@
   \label{def:2equivalence}
-  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
+  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\implies\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
   \begin{enumerate}
@@
   \begin{enumerate}
-    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
-    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
+    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\implies\Gamma(2)$;
+    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\implies\{q\}$;
     \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
@@
   Let $\beta\subset Q_0$ be strong successor closed in $\cQ$.
-  To see that $\beta$ is strong successor closed in $\cQ_p$ it suffices to consider the 2-arrow $V_p:\{p\}\to\Gamma(2)$.
+  To see that $\beta$ is strong successor closed in $\cQ_p$ it suffices to consider the 2-arrow $V_p:\{p\}\implies\Gamma(2)$.
   Suppose $\{p\}\subset\beta$.
@@
   Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
-  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\to\{q\}$ for which the claim is obvious as above.
+  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\implies\{q\}$ for which the claim is obvious as above.
 \end{proof}
@@
   Below we will usually apply Lemma~\ref{lem:2equivalence} after performing each of the equivalences from Definition~\ref{def:2equivalence}.
-  That is, given a 2-arrow $V:\Gamma(1)\to\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
+  That is, given a 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
 \end{remark}
@@
   \label{coeff}
-    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r})}
+    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r}).}
 \end{align}
-In this way we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
+Thus we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
 In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
-In this way we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
+In this way, we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.
 
@@
 Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$.
-For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
+For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
 By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
@@
 \begin{tikzpicture}[scale=1.35]
-  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
+  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} +(0.1,-1.3) node {\footnotesize$\mathcal Q_3$};
   \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
@@
 \end{equation}
-For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
+For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
 \begin{remark}
@@
 
-\begin{flushleft}
+\[
 \begin{tikzpicture}[scale=0.97]
@@
   +(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,r}$}
+  +(0,-4.2) node {$\cQ_{m+1}^{[r-1]}$}
   +(1.65,0) node (B1) {\footnotesize$Q_{m-1,2}$}
@@
   +(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[r]}$}
-  +(11.2,0) node (B11b) {\footnotesize$\dots$}
-  +(12.8,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
-  +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
+  +(11.125,0) node (B11b) {\footnotesize$\dots$}
+  +(12.7,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
+  +(12.7,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
   +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$};
@@
 
-\draw (4.45,0) node (B) {$\mathcal Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
+\draw (4.45,0) node (B) {\footnotesize$Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {\footnotesize$Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0.25) node (D) {\footnotesize$Q_{m,n-1}$}  +(10,0.25) node (E) {\footnotesize$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.35) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$};
 \node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
@@
 \end{tikzpicture}
-\\
-\end{flushleft}
-\noindent 
-As already mentioned two different vertices of $\mathcal Q_m^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
-Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe(\beta)$ and  $\bfe(\beta)$ of a subset $\beta\subset(\mathcal Q_m^{[r]})_0$ are defined by
-\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
-where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_m^{[r]})_0$.
-
+\]
+As already mentioned two different vertices of $\mathcal Q_{m+1}^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
+Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe(\beta)$ and  $\bfe(\beta)$ of a subset $\beta\subset(\mathcal Q_{m+1}^{[r]})_0$ are defined by
+\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}}\qquad\text{and}\qquad\bfe(\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
+where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_{m+1}^{[r]})_0$.
 \begin{theorem}\mbox{}
@@
   \begin{enumerate}
-    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_m^{[r]}\big)$ (resp.
-$Gr_\bfe\big(P_m^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
+    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_{m+1}^{[r]}\big)$ (resp.
+$\Gr_\bfe\big(P_{m+1}^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\cQ_{m+1}^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
 $\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
     \item For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
-$\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[r]}))$ (resp.
-$\chi(\Gr_{\bfe }(P_m^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$ (resp.
-$\bfe$) of the $2$-quiver of $\mathcal Q_m^{[r]}$.
+$\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_\tbfe(\tilde P_{m+1}^{[r]}))$ (resp.
+$\chi(\Gr_{\bfe }(P_{m+1}^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$ (resp.
+$\bfe$) of the $2$-quiver of $\cQ_{m+1}^{[r]}$.
   \end{enumerate}
@@
   The case of the representation $\tilde P_1$ is trivial.
-We have $(\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[r]}$ .
-Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[r]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[r]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[r]}$ is strong successor closed.
-
-  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[r]}$ and consider the short exact sequence
-  \[
-    \ses{\tilde P_m}{\tilde P_{m+1}^{[r-1]}}{\tilde P_{m+1}^{[r]}}.
-  \]
-  We have $(\mathcal Q_{m+1}^{[r-1]})_0=(\mathcal Q_{m+1}^{[r]})_0\coprod{}(\mathcal Q_{m,r})_0$.
-	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[r-1]})_0\coprod{}(\mathcal Q_{m,r})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
- % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
-  By Proposition~\ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[r]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[r]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[r]}$ is considered as a $2$-quiver of $\mathcal Q_{m,r}$.
+  We have $(\udim\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to $\mathcal Q_2^{[r]}$.
+  Equivalently, we have $\Gr_\tbfe(\tilde P_2^{[r]})\in\{\varnothing,\{\pt\}\}$ so that $\Gr_{\tbfe}(\tilde P_2^{[r]})=\{\pt\}$ if and only if $\tbfe\subset\cQ_2^{[r]}$ is strong successor closed.
+
+  Thus assume that the claim is true for $\tilde P_m$ and $\tilde P_{m+1}^{[r]}$.
+  Consider the short exact sequence
+  \[\ses{\tilde P_m}{\tilde P_{m+1}^{[r-1]}}{\tilde P_{m+1}^{[r]}}.\]
+  We have $(\cQ_{m+1}^{[r-1]})_0=(\cQ_{m+1}^{[r]})_0\coprod{}(\cQ_{m,r})_0$.
+  Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[r-1]})_0\coprod{}(\mathcal Q_{m,r})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by the induction hypothesis.
+  By Proposition~\ref{quotient}, the fiber over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[r]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[r]})_0=\varnothing$, where $\mathcal Q_{m-1}^{[r]}$ is considered as a sub-$2$-quiver of $\mathcal Q_{m,r}$.
   But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[r]}$ is connected to $\mathcal Q_{m-1}^{[r]}$ by a $2$-arrow.
@@
 %\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
-\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2)--(J11) node[pos=.5,above] {´};
+\draw[-implies,double equal sign distance,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
+\draw[-implies,double equal sign distance,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
+\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {´};
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1]
-\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
+\draw (1.6,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
 \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
@@
 
-\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
+\draw (3.6,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
 \draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
@@
 %\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
-\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
+\draw (7.6,0) node (I3) {$\bullet$} +(-1,0) node (J31) {$\bullet$} +(-2,0) node (J33) {$\bullet$}; 
 \draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
@@
 %\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
-\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2)--(J11) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
+\draw[-implies,double equal sign distance,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
+\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {};
 
@@
 
-\draw[->,red] (Q0b)--(J33b) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q1b)--(J22b) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2b)--(J11b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q0b)--(J33b) node[pos=.5,above] {\scriptsize $b$};
+\draw[-implies,double equal sign distance,red] (Q1b)--(J22b) node[pos=.5,above] {\scriptsize $c$};
+\draw[-implies,double equal sign distance,red] (Q2b)--(J11b) node[pos=.5,above] {};
 
@@
 \node (Q3c)[draw=black,fit={(Q2c) (Q2b) (I1b)}]{};
-\draw[->,red] (Q0c)--(J33c) node[pos=.5,above] {\scriptsize $b$};
-\draw[->,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
-\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {};
-\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {};
+\draw[-implies,double equal sign distance,red] (Q0c)--(J33c) node[pos=.5,above] {\scriptsize $b$};
+\draw[-implies,double equal sign distance,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
+\draw[-implies,double equal sign distance,red] (Q2c)--(Q0b) node[pos=.5,above] {};
+\draw[-implies,double equal sign distance,red] (Q3c)--(Q1) node[pos=.6,above] {};
 

### 2018-03-12 Grassmannian_cells.tex
Some polishing in section 5.2

@@
 It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.  
-
 The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
@@
   \label{cor:short hooks}
-  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
+  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges, all other vertical egdes are immediately preceded by exactly $n$ horizontal edges.
 \end{corollary}
@@
 
-For $m\ge2$ and $1\le r\le n-1$, write $D_m^{[r]}$ for the maximal Dyck path obtained from $D_m$ by removing the first $r$ copies of $D_{m-1}$.
-Extending this notation we also set $D_m^{[0]}:=D_m$.
+For $m\ge1$ and $1\le r\le n-1$, write $D_{m+1}^{[r]}$ for the maximal Dyck path obtained from $D_{m+1}$ by removing the first $r$ copies of $D_m$.
+Extending this notation we also set $D_{m+1}^{[0]}:=D_{m+1}$.
+
+For $m\ge1$ and $1\le i\le n-1$, we write $D_{m,i}$ for the $i$-th copy of $D_m$ inside $D_{m+1}$.
+Note that for $1\le r\le n-1$, the maximal Dyck paths $D_{m,i}$, $r+1\le i\le n$, naturally identify with subpaths of $D_{m+1}^{[r]}$.
+Extending the notation above, for $m\ge2$ and $1\le r\le n-1$, we write $D_{m,i}^{[r]}$ for the Dyck path obtained by removing the first $r$ copies of $D_{m-1}$ from $D_{m,i}$.
 \begin{remark}
-  Note that by Theorem~\ref{th:dyck path recursion}, we have a natural identification of $D_m^{[n-1]}$, $m\ge3$, with $D_{m-1}^{[1]}$.
+  For notational convenience, we also set $D_{m,n}^{[1]}:=D_{m+1}^{[n-1]}$ even though there is no maximal Dyck path $D_{m,n}$ identifying with a copy of $D_m$ inside $D_{m+1}$, such notation is justified by Theorem~\ref{th:dyck path recursion}.
+  This allows to write $D_{m,n}^{[r]}$ for $1\le r\le n-1$ for the terminal subpaths of $D_{m+1}$.
+  This should be compared with Corollary~\ref{cor:truncated preprojective isomorphism} and Lemma~\ref{le:truncated quotients}.
 \end{remark}
-For fixed $m\ge2$ and $1\le i\le n-1$, we write $D_{m-1,i}$ for the $i$-th copy of $D_{m-1}$ inside $D_m$.
-For notational convenience we also set $D_{m-1,n}:=D_m^{[n-1]}$ even though this maximal Dyck path does not identify with a copy of $D_{m-1}$.
-For $m\ge2$ and $1\le r\le n-1$, the maximal Dyck paths $D_{m-1,i}$, $r+1\le i\le n$, naturally identify with subpaths of $D_m^{[r]}$.
-
-We identify the edges of $D_m$ with the ordered set $E_m=\{1,\ldots,u_m+u_{m-1}\}$, where edges of $D_m$ are taken in the natural order beginning from $(0,0)$.
-Let $E_m=H_m\sqcup V_m$, where $H_m=\{h_1,\ldots,h_{u_m}\}$ and $V_m=\{v_1,\ldots,v_{u_{m-1}}\}$ denote the horizontal and vertical edges of $D_m$ respectively.
-Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_m=\bigsqcup_{i=1}^n E_{m-1,i}$, where $E_{m-1,i}$ denotes the edges of $D_{m-1,i}$.
-The set $E_{m-1,i}$ is naturally partitioned into its subsets $H_{m-1,i}$ and $V_{m-1,i}$ of horizontal and vertical edges.
-
-Given edges $e,e'\in E_m$ with $e<e'$, write $ee'$ for the shortest subpath of $D_m$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
+
+For $m\ge1$, we identify the edges of $D_{m+1}$ with the ordered set $E_{m+1}=\{1,\ldots,u_{m+1}+u_m\}$, where edges of $D_{m+1}$ are taken in the natural order beginning from $(0,0)$.
+Let $E_{m+1}=H_{m+1}\sqcup V_{m+1}$, where $H_{m+1}=\{h_1,\ldots,h_{u_{m+1}}\}$ and $V_{m+1}=\{v_1,\ldots,v_{u_m}\}$ denote the horizontal and vertical edges of $D_{m+1}$ respectively.
+Following Theorem~\ref{th:dyck path recursion}, we partition the edges as $E_{m+1}=\bigsqcup_{i=1}^n E_{m,i}$, where $E_{m,i}$ denotes the edges of $D_{m,i}$.
+The set $E_{m,i}$ is naturally partitioned into its subsets $H_{m,i}$ and $V_{m,i}$ of horizontal and vertical edges.
+The edges of $D_{m+1}^{[r]}$ are similarly partitioned as $E_{m+1}^{[r]}=\bigsqcup_{i=r+1}^n E_{m,i}=H_{m+1}^{[r]}\sqcup V_{m+1}^{[r]}$.
+
+Given edges $e,e'\in E_{m+1}$ with $e<e'$, write $ee'$ for the shortest subpath of $D_{m+1}$ containing $e$ and $e'$, in particular $ee$ is the subpath containing the single edge $e$.
 \begin{definition}
   \label{def:compatibility}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{compatible} if: 
-  for each pair $(h,v)\in S_H\times S_V$ with $h<v$ there exists an edge $e\in hv$ so that at least one of the following holds
+  For $m\ge1$, a pair of subsets $S_H\subset H_{m+1}$ and $S_V\subset V_{m+1}$ is called \emph{compatible} if: 
+  for each pair $(h,v)\in S_H\times S_V$ with $h<v$, there exists an edge $e\in hv$ so that at least one of the following holds
   \begin{equation}
     \label{eq:hgc}
-    e\ne v\qquad\text{and}\qquad |he\cap V_m|=n|he\cap S_H|
+    e\ne v\qquad\text{and}\qquad |he\cap V_{m+1}|=n|he\cap S_H|
   \end{equation}
@@
     \label{eq:vgc}
-    e\ne h\qquad\text{and}\qquad |ev\cap H_m|=n|ev\cap S_V|.
+    e\ne h\qquad\text{and}\qquad |ev\cap H_{m+1}|=n|ev\cap S_V|.
   \end{equation}
-  Write $\cC_m$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
+  Write $\cC_{m+1}$ for the collection of all pairs $(S_H,S_V)$ which are compatible as above.
 \end{definition}
 \begin{remark}
-  This notion of compatibility extends naturally to the maximal Dyck paths $D_m^{[r]}$, $1\le r\le n-1$.  Write $\cC_m^{[r]}$ for the set of all compatible pairs in $D_m^{[r]}$.
+  This notion of compatibility extends naturally to the maximal Dyck paths $D_{m+1}^{[r]}$, $1\le r\le n-1$, and trivially to the Dyck path $D_1$.
+  Write $\cC_{m+1}^{[r]}$ for the set of all compatible pairs in $D_{m+1}^{[r]}$.
 \end{remark}
@@
   \label{def:piecewise compatibility}
-  A pair of subsets $S_H\subset H_m$ and $S_V\subset V_m$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m-1,i}$ and $v\in V_{m-1,i}$.
+  A pair of subsets $S_H\subset H_{m+1}$ and $S_V\subset V_{m+1}$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m,i}$ and $v\in V_{m,i}$.
 \end{definition}
 \begin{remark}
-  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_m^{[r]}$, $1\le r\le n-1$.
+  The notion of piecewise compatibility naturally extends to the maximal Dyck paths $D_{m+1}^{[r]}$, $1\le r\le n-1$.
+  Given a compatible pair $(S_H,S_V)$ in $D_{m+1}^{[r]}$, we write $S_H^{[r+1]}=S_H\cap H_{m+1}^{[r+1]}\subset H_{m+1}^{[r]}$ and $S_V^{[r+1]}=S_V\cap V_{m+1}^{[r+1]}\subset V_{m+1}^{[r]}$.
+  In particular, the pair $(S_H^{[r+1]},S_V^{[r+1]})$ is compatible in $D_{m+1}^{[r+1]}$.
+  We also write $S_{H,i}=S_H\cap H_{m,i}$ and $S_{V,i}=S_V\cap V_{m,i}$ for $r+1\le i\le n-1$.
 \end{remark}
@@
 To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
-For a horizontal edge $h\in H_m$ and a subset $S_H\subset H_m$, write $D(h;S_H)=he$ for the shortest subpath of $D_m$ for which $|he\cap V_m|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_{m-1}}$.
+For a horizontal edge $h\in H_{m+1}$ and a subset $S_H\subset H_{m+1}$, write $D(h;S_H)=he$ for the shortest subpath of $D_{m+1}$ for which $|he\cap V_{m+1}|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_m}$.
 The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
-Similarly, for a vertical edge $v\in V_m$ and a subset $S_V\subset V_m$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_m$ for which $|ev\cap H_m|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
+Similarly, for a vertical edge $v\in V_{m+1}$ and a subset $S_V\subset V_{m+1}$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_{m+1}$ for which $|ev\cap H_{m+1}|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
 \begin{definition}
   \cite[Definition 3.17]{rupel}
-  A horizontal edge $h_i\in H_m$, $m\ge3$, is called \emph{blocking} for a subset $S_H\subset H_m$ if $D(h_i;S_H)=h_iv_{u_{m-1}}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal with this property.
-
-  Suppose $S_H\subset H_m$ admits a blocking edge $h_i\in H_m$.
+  A horizontal edge $h_i\in H_{m+1}$, $m\ge2$, is called \emph{blocking} for a subset $S_H\subset H_{m+1}$ if $D(h_i;S_H)=h_iv_{u_m}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal.
+
+  Suppose $S_H\subset H_{m+1}$ admits a blocking edge $h_i\in H_{m+1}$.
   Then $S_H$ is \emph{left-justified at $h_i$} if there exists $k\ge i$ so that $S_H=\{h_i,h_{i+1},\ldots,h_k\}$.
-  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_{m-1}}\cap V_m|=n|h_iv_{u_{m-1}}\cap S_H|$.
-
-  A subset $S_V\subset V_m$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_{m-1}}$ so that $S_V\cap h_iv_{u_{m-1}}=\{v_s,v_{s-1},\ldots,v_{u_{m-1}}\}$.
-  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_{m-1}};S_V)=h_iv_{u_{m-1}}$ with $|h_iv_{u_{m-1}}\cap H_m|=n|h_iv_{u_{m-1}}\cap S_V|$.
+  The subset $S_H$ is \emph{strongly left-justified at $h_i$} if $S_H$ is left-justified at $h_i$ and $|h_iv_{u_m}\cap V_{m+1}|=n|h_iv_{u_m}\cap S_H|$.
+
+  A subset $S_V\subset V_{m+1}$ is \emph{right-justified with respect to $h_i$} if there exists a vertical edge $v_s\in h_iv_{u_m}$ so that $S_V\cap h_iv_{u_m}=\{v_s,v_{s-1},\ldots,v_{u_m}\}$.
+  The subset $S_V$ is \emph{strongly right-justified with respect to $h_i$} if $S_V$ is right-justified with respect to $h_i$ and $D(v_{u_m};S_V)=h_iv_{u_m}$ with $|h_iv_{u_m}\cap H_{m+1}|=n|h_iv_{u_m}\cap S_V|$.
 \end{definition}
@@
   \label{th:blocking edge conditions}
-  For $m\ge3$, suppose $S_H\subset H_m$ and $S_V\subset V_m$ are piecewise compatible. 
+  For $m\ge2$, suppose $S_H\subset H_{m+1}$ and $S_V\subset V_{m+1}$ are piecewise compatible. 
   Then the following hold:
   \begin{enumerate}
-    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_m$.
-    \item Suppose $S_H$ admits a blocking edge $h_i\in H_m$ and $(S_H,S_V)$ is not compatible.
+    \item If $S_H$ does not admit a blocking edge, then $(S_H,S_V)\in\cC_{m+1}$.
+    \item Suppose $S_H$ admits a blocking edge $h_i\in H_{m+1}$ and $(S_H,S_V)$ is not compatible.
       Then $S_H$ is left-justified at $h_i$ and $S_V$ is strongly right-justified with respect to $h_i$.
-      In addition the following hold:
+      In addition, the following hold:
       \begin{enumerate}
-        \item If $m=3$, then $S_H\cap h_iv_{u_{m-1}}=\{h_i\}$.
-        \item If $m\ge4$, then $S_H$ is strongly left-justified at $h_i$.
-        \item If $m\ge5$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_m$.
+        \item If $m=2$, then $S_H\cap h_iv_{u_m}=\{h_i\}$.
+        \item If $m\ge3$, then $S_H$ is strongly left-justified at $h_i$.
+        \item If $m\ge4$, then either $i=1$ or $h_i$ is immediately preceded by a vertical edge in $D_{m+1}$.
       \end{enumerate}
@@
   \label{cor:piecewise not compatible}
-  For $m\ge4$ and $0\le r\le n-1$, consider $S_H\subset H_m^{[r]}$ and $S_V\subset V_m^{[r]}$ so that $(S_H,S_V)$ is piecewise compatible.
-  Assume $\big(S_H^{[r+1]},S_V^{[r+1]}\big)\in\cC_m^{[r+1]}$.
-  Then $(S_H,S_V)$ is not compatible if and only if $H_{m-2}^{[r+1]}\subset S_{H,r+1}$ and $V_m^{[r+1]}\subset S_V$.
+  For $m\ge3$ and $0\le r\le n-1$, consider $S_H\subset H_{m+1}^{[r]}$ and $S_V\subset V_{m+1}^{[r]}$ so that $(S_H,S_V)$ is piecewise compatible.
+  Assume $\big(S_H^{[r+1]},S_V^{[r+1]}\big)\in\cC_{m+1}^{[r+1]}$.
+  Then $(S_H,S_V)$ is not compatible if and only if $H_{m,r+1,n}^{[r+1]}\subset S_{H,r+1}$ and $V_{m+1}^{[r+1]}\subset S_V$.
 \end{corollary}
@@
   We begin with the reverse implication.
-  First note that there are $(n-r)u_{m-1}-u_{m-2}$ horizontal edges and $(n-r)u_{m-2}-u_{m-3}$ vertical edges in $D_m^{[r]}$. 
-  It follows that $V_{m-2}^{[r+1]}\sqcup V_m^{[r+1]}$ contains $n(n-r)u_{m-3}-nu_{m-4}$ vertical edges and $H_{m-2}^{[r+1]}\sqcup H_m^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ horizontal edges.
-
-  Assuming $H_{m-2}^{[r+1]}\subset S_{H,r+1}$ and $S_V^{[r+1]}=V_m^{[r+1]}$, we have $S_V\cap V_{m-2}^{[r+1]}=\varnothing$ and $S_H\cap H_m^{[r+1]}=\varnothing$ by piecewise compatibility.
-  Let $h\in H_m^{[r]}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m-2}^{[r+1]}$.
-  Then, since there are $(n-r)u_{m-3}-u_{m-4}$ horizontal edges in $H_{m-2}^{[r+1]}$, the local shadow path $D(h;S_H)$ contains $n\big((n-r)u_{m-3}-u_{m-4}\big)$ vertical edges and is thus equal to $hv_{u_{m-1}}$.
-  Similarly, the local shadow path $D(v_{u_{m-1}};S_V)$ is also equal to $hv_{u_{m-1}}$.
-  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_{m-1}}$ and so $(S_H,S_V)$ is not compatible.
-
-  For the forward implication, we work by induction on $m\ge4$.
+  First note that there are $(n-r)u_m-u_{m-1}$ horizontal edges and $(n-r)u_{m-1}-u_{m-2}$ vertical edges in $D_{m+1}^{[r]}$. 
+  It follows that $H_{m,r+1,n}^{[r+1]}\sqcup H_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-1}-nu_{m-2}$ horizontal edges and $V_{m-1}^{[r+1]}\sqcup V_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ vertical edges (note that $H_{m,r+1,n}^{[r+1]}$ naturally identifies with the Dyck path $H_{m-1}^{[r+1]}$).
+
+  Assuming $H_{m,r+1,n}^{[r+1]}\subset S_{H,r+1}$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$, we have $S_V\cap V_{m,r+1,n}^{[r+1]}=\varnothing$ and $S_H\cap H_{m+1}^{[r+1]}=\varnothing$ by piecewise compatibility.
+  Let $h\in H_{m+1}^{[r]}$ be the horizontal edge corresponding to the first horizontal edge of $H_{m,r+1,n}^{[r+1]}$.
+  Then, since there are $(n-r)u_{m-2}-u_{m-3}$ horizontal edges in $H_{m,r+1,n}^{[r+1]}$, the local shadow path $D(h;S_H)$ contains $n\big((n-r)u_{m-2}-u_{m-3}\big)$ vertical edges and is thus equal to $hv_{u_m}$.
+  Similarly, the local shadow path $D(v_{u_m};S_V)$ is also equal to $hv_{u_m}$.
+  In particular, neither of the compatibility conditions of Definition~\ref{def:compatibility} are satisfied for the path $hv_{u_m}$ and so $(S_H,S_V)$ is not compatible.
+
+  For the forward implication, we work by induction on $m\ge3$.
   Consider a pair $(S_H,S_V)$ for $D_4^{[r]}$ as above which is not compatible.
@@
   Then the number of vertical edges in the local shadow path $D(h;S_H)=hv_{u_3}$ must be divisible by $n$. 
-  Since $\big(S_H^{[r+1]},S_V^{[r+1]}\big)$ is compatible, we must have $h\in H_{3,r}$.
-  But observe that $|V_m^{[r]}|=(n-r)n-1$ and so the divisibility condition above implies $h\in H_{3,r}^{[n-1]}$.
+  Since $\big(S_H^{[r+1]},S_V^{[r+1]}\big)$ is compatible, we must have $h\in H_{3,r+1}$.
+  But observe that $|V_4^{[r]}|=(n-r)n-1$ and so the divisibility condition above implies $h\in H_{3,r+1}^{[n-1]}$.
   But $S_V$ is strongly right-justified with respect to $h$ and thus the number of horizontal edges in $D(v_{u_3};S_V)=hv_{u_3}$ is divisible by $n$.
-  Identifying $H_{3,r}^{[n-1]}$ with $H_2^{[1]}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{[r+1]}\subset H_2^{[1]}$.
+  Identifying $H_{3,r+1}^{[n-1]}$ with $H_2^{[1]}$, this divisibility condition only occurs when $h$ is the first horizontal edge in $H_2^{[r+1]}\subset H_2^{[1]}$.
   Then by piecewise compatibility, the vertical edge of $H_2^{[1]}$ cannot be an element of $S_V$ and we must have $V_4^{[r+1]}\subset S_V$.
@@
 
-  To continue, let $(S_H,S_V)$ be a pair for $D_m$, $m\ge5$, which is not compatible.
-  Write $\varphi:H_{m-1}\to V_m$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_{m-1}$.
-  For any subset $T\subset H_{m-1}$, set $\varphi^*(T)=V_m\setminus\varphi(T)$.
-  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_{m-1}$ and subsets of $V_m$.
-  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_{m-1}$ is given, we refer the reder to \emph{loc. cit} for notation.
+  To continue, let $(S_H,S_V)$ be a pair for $D_{m+1}$, $m\ge4$, which is not compatible.
+  Write $\varphi:H_m\to V_{m+1}$ for the bijection given by $\varphi(h_i)=v_i$ for $1\le i\le u_m$.
+  For any subset $T\subset H_m$, set $\varphi^*(T)=V_{m+1}\setminus\varphi(T)$.
+  Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_m$ and subsets of $V_{m+1}$.
+  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_m$ is given, we refer the reader to \emph{loc. cit} for notation.
   By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
-  Thus by induction, we must have $H_{m-3}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_{m-1}^{[r+1]}\subset\Omega^{-1}S_H$.
-  It follows from piecewise compatibility that $H_{m-1}^{[r+1]}\cap(\varphi^*)^{-1}S_V=\varnothing$.
-  But then by the definition of $\varphi^*$ we have $V_{m-2}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_m^{[r+1]}$ so that $D(v_{u_{m-1}};S_V)=hv_{u_{m-1}}$ with $h$ as in the first case above.
-  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_{m-1}}$.
-  But this can only occur if $H_{m-2}^{[r+1]}\subset S_H$ since $H_m^{[r+1]}\cap S_H=\varnothing$ by piecewise compatibility.
+  Thus by induction, we must have $H_{m-2}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_m^{[r+1]}\subset\Omega^{-1}S_H$.
+  It follows from piecewise compatibility that $H_m^{[r+1]}\cap(\varphi^*)^{-1}S_V=\varnothing$.
+  But then by the definition of $\varphi^*$ we have $V_{m-1}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$ so that $D(v_{u_m};S_V)=hv_{u_m}$ with $h$ as in the first case above.
+  Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_m}$.
+  But this can only occur if $H_{m,r+1,n}^{[r+1]}\subset S_H$ since $H_{m+1}^{[r+1]}\cap S_H=\varnothing$ by piecewise compatibility.
 \end{proof}
@@
   For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have 
-  \[\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|.\]
+  \[\chi\big(\Gr_\bfe(P_m)\big)=\Big|\big\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\big\}\Big|.\]
 \end{theorem}
 
-Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\Gr_\bfe(P_m)$ found in Theorem~\ref{celldec}.
-In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_m^V)$ for truncated preprojectives $P_m^V$ are also naturally labeled by compatible pairs.
-We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_m^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
+Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\Gr_\bfe(P_{m+1})$ found in Theorem~\ref{celldec}.
+In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ for truncated preprojectives $P_{m+1}^V$ are also naturally labeled by compatible pairs.
+We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_{m+1}^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
 \begin{theorem}
@@
   \sayD{Fix abuse of notation $H_m$.}
-  For $m\ge1$ and $V\in\Gr(H_{m-1})$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_m^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_m^{[r]}$, where $r=\dim V$.
+  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
 \end{theorem}
 \begin{proof}
-  The recursive construction of the 2-quivers $\cQ_m^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_m^{[r]}$.
-  Indeed, when considering the recursive construction of the 2-quiver $Q_m^{[r]}$ from \eqref{eq:recursive 2-quivers}, we order the component quivers $Q_{m-1,i}$ and $Q_{m-1,*}^{[1]}$ naturally according to their indices so that $Q_{m-1,*}^{[1]}$ comes last.
-  This provides a bijection of these vertices with the edges of $D_m^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges) of $D_m^{[r]}$.
-
-  Given a strong successor closed subset $\beta\subset(Q_m^{[r]})_0$, we define a pair of subsets $S_H(\beta)\subset H_m^{[r]}$ and $S_V(\beta)\subset V_m^{[r]}$ as follows: a vertical edge $v\in V_m^{[r]}$ is in $S_V(\beta)$ exactly when the corresponding vertex of $Q_m^{[r]}$ is in $\beta$ while a horizontal edge $h\in H_m^{[r]}$ is in $S_H(\beta)$ exactly when the corresponding vertex of $Q_m^{[r]}$ is \emph{not} in $\beta$.
-  Then Corollary~\ref{cor:piecewise not compatible} shows that under this bijection a subset $\beta\in(Q_m^{[r]})_0$ is strong successor closed in~$\cQ_m^{[r]}$ if and only if the corresponding pair of subsets $\big(S_H(\beta),S_V(\beta)\big)$ is compatible.
+  The recursive construction of the 2-quivers $\cQ_{m+1}^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_{m+1}^{[r]}$.
+  Indeed, when considering the recursive construction of the 2-quiver $Q_{m+1}^{[r]}$ from \eqref{eq:recursive 2-quivers}, we order the component quivers $Q_{m,i}$ and $Q_{m,*}^{[1]}$ naturally according to their indices so that $Q_{m,*}^{[1]}$ comes last.
+  This provides a bijection of these vertices with the edges of $D_{m+1}^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges) of $D_{m+1}^{[r]}$.
+
+  Given a strong successor closed subset $\beta\subset(Q_{m+1}^{[r]})_0$, we define a pair of subsets $S_H(\beta)\subset H_{m+1}^{[r]}$ and $S_V(\beta)\subset V_{m+1}^{[r]}$ as follows: a vertical edge $v\in V_{m+1}^{[r]}$ is in $S_V(\beta)$ exactly when the corresponding vertex of $Q_{m+1}^{[r]}$ is in $\beta$ while a horizontal edge $h\in H_{m+1}^{[r]}$ is in $S_H(\beta)$ exactly when the corresponding vertex of $Q_{m+1}^{[r]}$ is \emph{not} in $\beta$.
+  Then Corollary~\ref{cor:piecewise not compatible} shows that under this bijection a subset $\beta\in(Q_{m+1}^{[r]})_0$ is strong successor closed in~$\cQ_{m+1}^{[r]}$ if and only if the corresponding pair of subsets $\big(S_H(\beta),S_V(\beta)\big)$ is compatible.
   Applying Theorem~\ref{thm:2quivercells} completes the proof.

### 2018-03-12 Grassmannian_cells.tex
Small section 5.2 edit
cleaned up references, added acknowledgements

@@
 \author{Thorsten Weist}
-\address[Thorsten Weist]{}
+\address[Thorsten Weist]{Bergische Universit\"at Wuppertal, Gau\ss str.\ 20, 42097 Wuppertal, Germany}
 \email{weist@uni-wuppertal.de}
@@
 \sayT{maybe we can erase some parts which show up twice in the introduction?}
-
+\subsection*{Acknowledgements}We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   For notational convenience, we also set $D_{m,n}^{[1]}:=D_{m+1}^{[n-1]}$ even though there is no maximal Dyck path $D_{m,n}$ identifying with a copy of $D_m$ inside $D_{m+1}$, such notation is justified by Theorem~\ref{th:dyck path recursion}.
+  This should be compared with Corollary~\ref{cor:truncated preprojective isomorphism} and Lemma~\ref{le:truncated quotients}.
+
   This allows to write $D_{m,n}^{[r]}$ for $1\le r\le n-1$ for the terminal subpaths of $D_{m+1}$.
-  This should be compared with Corollary~\ref{cor:truncated preprojective isomorphism} and Lemma~\ref{le:truncated quotients}.
+  We also iterate this notation below by identifying $D_{m,r+1}$ with $D_m$ and identifying $D_{m,r+1,n}^{[r+1]}$ with the subpath obtained by removing the first $r+1$ copies of $D_{m-2}$ from a copy of $D_{m-1}$.
 \end{remark}
@@
 
-\sayT{references to be unified}
+%\sayT{references to be unified}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibitem{brenner-butler} 
-  S.~Benner, M.~C.~R.~Butler, The equivalence of certain functors occuring in the representation theory of artin algebras and species, J. London Math. Soc., 14 (1976), 183-187.
+  S.~Benner, M.~C.~R.~Butler: The equivalence of certain functors occuring in the representation theory of artin algebras and species.
+Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).
 \bibitem{cc} 
@@
 \bibitem{ck} 
-  P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Ann. Sci. \'Ecole Norm. Sup. (4) \textbf{39} (2006), no. 6, pp.~983--1009.
+  P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Annales Scientifique de l'Ecole Normale Superi\'{e}ure (4) \textbf{39} (6), 983-1009 (2006).
 \bibitem{ce} 
-  G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory, 5(6), 777-801.
+  G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory \textbf{5}(6), 777-801 (2011).
 \bibitem{cefr} 
-  G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2017.
+  G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2018.
 \bibitem{cr} 
@@
   P.~Gabriel: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
-\bibitem{hr} 
-  D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
+%\bibitem{hr} 
+ % D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}(2), 399-443 (1982).
 \bibitem{llz} 
-  K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014) pp.~57--82.
+  K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Mathematica \textbf{20}(1), 57-82 (2014).
 \bibitem{lw} 
@@
 \bibitem{rin1} 
-  C.~M.~Ringel. Exceptional modules are tree modules. \textit{Linear algebra and its Applications}, 275/276:471-493, 1998.
-\bibitem{rin} 
-  C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
+  C.~M.~Ringel. Exceptional modules are tree modules. Linear algebra and its Applications \textbf{275/276}, 471-493 (1998).
+%\bibitem{rin} 
+ % C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}(3), 465-479 (1980).
 %\bibitem{mats} Matsumura, H.: Commutative ring theory. 
 \bibitem{rupel} 
-  D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity, arXiv.
+  D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity. Preprint 2017, arXiv:1707.02696.
 \bibitem{sch} 
@@
   T.~Weist: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
-\bibitem{wei2} 
-  T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
+%\bibitem{wei2} 
+ % T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
 %\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).

### 2018-03-12 Grassmannian_cells.tex
Added conjectural cell dimensions to section 5.2

--- 2018-03-12 Grassmannian_cells.tex
@@
 \end{proof}
+
+The results of \cite{rupel} provide a stronger statement than Theorem~\ref{th:combinatorial euler}.
+Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).
+We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explaination of this result.
+\begin{conjecture}
+  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, there exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the dimension of the cell labeled by a compatible pair $(S_H,S_V)$ in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$, is given by $\overline{\gamma}_{S_H,S_V}=\sum\limits_{e<e'\in E_{m+1}^{[r]}}\overline{\gamma}_\omega(e,e')$ for
+  \begin{equation*}
+    \overline{\gamma}_\omega(e,e')=\begin{cases}
+      -n & \text{if $e\in S_H$ and $e'\in S_V$;}\\ 
+      1 & \text{if $e\in S_H$ and $e'\in H_{m+1}^{[r]}\setminus S_H$;}\\ 
+      1 & \text{if $e\in V_{m+1}^{[r]}\setminus S_V$ and $e'\in S_V$;}\\ 
+      0 & \text{otherwise.}\\ 
+    \end{cases}
+  \end{equation*}
+\end{conjecture}
 

### 2018-03-12 Grassmannian_cells.tex
Better merge

--- 2018-03-12 Grassmannian_cells.tex
@@
 
-%\sayT{references to be unified}
+The results of \cite{rupel} provide a stronger statement than Theorem~\ref{th:combinatorial euler}.
+Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).
+We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explaination of this result.
+\begin{conjecture}
+  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, there exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the dimension of the cell labeled by a compatible pair $(S_H,S_V)$ in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$, is given by $\overline{\gamma}_{S_H,S_V}=\sum\limits_{e<e'\in E_{m+1}^{[r]}}\overline{\gamma}_\omega(e,e')$ for
+  \begin{equation*}
+    \overline{\gamma}_\omega(e,e')=\begin{cases}
+      -n & \text{if $e\in S_H$ and $e'\in S_V$;}\\ 
+      1 & \text{if $e\in S_H$ and $e'\in H_{m+1}^{[r]}\setminus S_H$;}\\ 
+      1 & \text{if $e\in V_{m+1}^{[r]}\setminus S_V$ and $e'\in S_V$;}\\ 
+      0 & \text{otherwise.}\\ 
+    \end{cases}
+  \end{equation*}
+\end{conjecture}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-03-12 Grassmannian_cells.tex
Testing \cH in Theorem 5.20

@@
 \newcommand{\cG}{\mathcal{G}}
+\newcommand{\cH}{\mathcal{H}}
 \newcommand{\cP}{\mathcal{P}}
@@
   \sayD{Fix abuse of notation $H_m$.}
-  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
+  For $m\ge1$ and $V\in\Gr(\cH_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
 \end{theorem}

### 2018-03-12 Grassmannian_cells.tex
Changed to \cH

@@
 
-Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
-Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
-Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
+Set $\cH_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
+Write $\Gr(\cH_m)$ for the \emph{total Grassmannian} of $\cH_m$ whose elements are nontrivial proper subspaces $V\subset \cH_m$.
+Some results below remain true if we allow $\cH_m$ or $0$ as elements of $\Gr(\cH_m)$, but not all, so for uniformity of exposition we omit these possibilities.
 
@@
   \label{eq:AR sequence}
-  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
+  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes \cH_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
 \end{equation}
@@
   \label{le:injective evaluation maps}
-  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
+  For any $V\in \Gr(\cH_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
 \end{lemma}
@@
   As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
-  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
+  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes \cH_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
   in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
@@
   In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
-  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
+  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes \cH_1/V$.
   Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
-  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
+  \[\xymatrix{0 \ar[r]  & P_1\otimes \cH_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes \cH_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
 
@@
   As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
-  But this already shows that $K$ is indecomposable as $\udim K=(\dim H_1/V,1)$.
-  Since $V$ is a proper subspace of $H_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
+  But this already shows that $K$ is indecomposable as $\udim K=(\dim \cH_1/V,1)$.
+  Since $V$ is a proper subspace of $\cH_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
 \end{proof}
@@
 \begin{definition}
-  For $V\in \Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
+  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
   \begin{equation}
@@
   \label{le:truncated homomorphisms}
-  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
+  For $V\in \Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong \cH_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
 \end{lemma}
@@
   \label{le:unique preprojective morphism}
-  For $V\in \Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
   Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
@@
   \label{le:unique morphisms}
-  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
+  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
   \begin{enumerate}
     \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
+    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
   \end{enumerate}
@@
   In this case, there are isomorphisms
-  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
+  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes \cH_m/V,\]
   where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
@@
 \begin{remark}
-  The total Grassmannian $\Gr(H_m)$ is naturally a poset under inclusion.
-  This structure gives rise to a $\CC$-linear category $\CC \Gr(H_m)$ with objects the elements of $\Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
-  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(H_m)$.
-  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(H_m)\cong\cP_{m+1}$.
+  The total Grassmannian $\Gr(\cH_m)$ is naturally a poset under inclusion.
+  This structure gives rise to a $\CC$-linear category $\CC \Gr(\cH_m)$ with objects the elements of $\Gr(\cH_m)$ and at most one morphism (up to scalars) between any two objects.
+  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(\cH_m)$.
+  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(\cH_m)\cong\cP_{m+1}$.
 \end{remark}
@@
     \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
-    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$ with $\dim V=r$. 
+    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
     \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
@@
   \label{le:basic homological properties}
-  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
+  For $V\in\Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
 \end{lemma}
@@
   \label{le:reflected truncated preprojectives}
-  For $V\in\Gr(H_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
+  For $V\in\Gr(\cH_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
 \end{lemma}
@@
   \label{le:projective subrepresentations}
-  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
+  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
 \end{lemma}
@@
   We proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
 
@@
 
-For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
+For $V\in \Gr(\cH_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
 \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
@@
   \label{cor:base fibers}
-  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
+  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$, with $W\subset V$.
   Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
@@
   \label{le:unique truncated extension}
-  For $V\in \Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
+  For $V\in \Gr(\cH_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
   \begin{equation}
     \label{eq:unique extension}
-    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
+    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(\cH_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
   \end{equation}
@@
     & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
-    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
+    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes \cH_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
     0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
     & & 0 & 0 & }\]
-  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
+  from which we immediately obtain the isomorphism $X\cong P_m\otimes(\cH_m/V)$.
 \end{proof}
@@
   \label{le:preprojective homomorphism duality}
-  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
+  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $\cH_m^*\cong \cH_{m-1}$.
 \end{lemma}
 \begin{proof}
-  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
-  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
-  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
+  Define a map $\cH_m^*\to \cH_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
+  Suppose $\varphi\in \cH_m^*$ is a nonzero functional on $\cH_m$ and let $V\subsetneq \cH_m$ denote the kernel of $\varphi$.
+  Then $\bar{\varphi}=0\in \cH_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes \cH_m$.
   But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
-  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
+  Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
 \end{proof}
 \begin{remark}
-  The set $\Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(H_m)^{op}\cong \Gr(H_m^*)$ with $\Gr(H_{m-1})$.
-  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
-  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
+  The set $\Gr(\cH_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(\cH_m)^{op}\cong \Gr(\cH_m^*)$ with $\Gr(\cH_{m-1})$.
+  We write $\bar{V}\subset \cH_{m-1}$ for the subspace corresponding to $V\subset \cH_m$ under this identification.
+  Under the isomorphism of $\cH_{m-1}$ with $\cH_m^*$, we have $\bar{V}=(\cH_m/V)^*$.
 \end{remark}
@@
   \label{cor:truncated preprojective isomorphism}
-  Suppose $V\in \Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
+  Suppose $V\in \Gr(\cH_m)$ has codimension-one in $\cH_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
 \end{corollary}
@@
   By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
-  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
-  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
+  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(\cH_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
+  But $\cH_m/V$ is a one-dimensional vector space and so $P_m\otimes(\cH_m/V)\cong P_m$.
   Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
@@
 Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
-In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
+In this section, we fix compatible bases for each $\cH_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
 This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
@@
 
-  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
+  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
   The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
@@
 \subsection{\texorpdfstring{$\mathbf{GL_n}$}{Gln}-Action on Arrows of \texorpdfstring{$\mathbf{K(n)}$}{K(n)}}
-The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
+The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq \cH_m$.
 We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
@@
 %  \label{le:transitivity}
-%  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $\Gr_d(H_m)$.
+%  The action of $GL_n(\CC)$ on $\cH_m$ induces a transitive action of $GL_n(\CC)$ on each component $\Gr_d(\cH_m)$.
 %\end{lemma} 
 %\begin{proof}
-%  The map $\theta\mapsto g.\theta$ for $\theta\in H_m$ induces a group homomorphism $GL_n(\CC)\to GL(H_m)$ which we denote by $g\mapsto\tilde g_m$.
+%  The map $\theta\mapsto g.\theta$ for $\theta\in \cH_m$ induces a group homomorphism $GL_n(\CC)\to GL(\cH_m)$ which we denote by $g\mapsto\tilde g_m$.
 %  We claim that this homomorphism is surjective which immediately implies the result.
@@
 %  We work by induction on $m$.
-%  Suppose $GL_n(\CC)\to GL(H_m)$ is surjective.
+%  Suppose $GL_n(\CC)\to GL(\cH_m)$ is surjective.
 %
@@
 
-%Similarly, for $V^g\in \Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
+%Similarly, for $V^g\in \Gr(\cH_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
 %\begin{lemma}
@@
   Fix a dimension vector $\bfe$.
-  The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr(H_m)$.
-  Moreover, for $V,W\in \Gr_d(H_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$.
+  The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr(\cH_m)$.
+  Moreover, for $V,W\in \Gr_d(\cH_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$.
 \end{theorem}
@@
   %For each dimension vector $\bfe$, there is a smooth variety
-  %\[X_{\bfe,m}=\{(\tilde E,V):V\in \Gr_d(H_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
-  %Under the natural projection $\pi:X_{\bfe,m}\to \Gr_d(H_m)$, the fiber $\pi^{-1}(V)$ identifies with $\Gr_\bfe(P_{m+1}^V)$.
-  %In particular, this implies $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr_d(H_m)$.
+  %\[X_{\bfe,m}=\{(\tilde E,V):V\in \Gr_d(\cH_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
+  %Under the natural projection $\pi:X_{\bfe,m}\to \Gr_d(\cH_m)$, the fiber $\pi^{-1}(V)$ identifies with $\Gr_\bfe(P_{m+1}^V)$.
+  %In particular, this implies $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr_d(\cH_m)$.
   %The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.
@@
   %\[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
-  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ and $\Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in \Gr_d(H_m)$.
+  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ and $\Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in \Gr_d(\cH_m)$.
 \end{proof}
@@
 In the following, we freely use the notation and conventions of Section~\ref{sec:RepK(n)}.
-For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(H_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
+For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(\cH_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
 In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.
@@
 By Theorem~\ref{celldec}, the cells of the quiver Grassmannians of $P_{m+1}^V$ are in one-to-one correspondence with those attached to any lift $\tilde P_{m+1}^{[r]}$ to $\widetilde{K(n)}$.
-Since the choice of $V\in\Gr(H_m)$ with $\dim V=r$ is immaterial for understanding the geometry of $\Gr_\bfe(P_{m+1}^V)$, we may fix a particular choice of $V$ and a particular lift to the universal cover.
+Since the choice of $V\in\Gr(\cH_m)$ with $\dim V=r$ is immaterial for understanding the geometry of $\Gr_\bfe(P_{m+1}^V)$, we may fix a particular choice of $V$ and a particular lift to the universal cover.
 Indeed, set
@@
 \end{align}
-Thus we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
+Thus we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(\cH_1)$ with $\dim V=r$.
 In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.

### 2018-03-12 Grassmannian_cells.tex
Intro edits

@@
 
-The results of \cite{rupel} giving a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$ suggest the following.
-\begin{conjecture}
-  There exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the affine cell corresponding to a compatible pair $(S_H,S_V)$ has dimension...
-\end{conjecture}
-\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
-\sayT{Insert something about Dyck path combinatorics and the correspondence here}
+The results of \cite{rupel} giving a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$ suggest that the dimensions of cells can be computed using this combinatorics (or the equivalent combinatorics of compatible pairs).
+This is made precise in Conjecture~\ref{conj:cell dimensions}.
 \sayT{maybe we can erase some parts which show up twice in the introduction?}
@@
   \label{th:compatible cells}
-  \sayD{Fix abuse of notation $H_m$.}
   For $m\ge1$ and $V\in\Gr(\cH_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
@@
 \begin{conjecture}
+  \label{conj:cell dimensions}
   For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, there exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the dimension of the cell labeled by a compatible pair $(S_H,S_V)$ in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$, is given by $\overline{\gamma}_{S_H,S_V}=\sum\limits_{e<e'\in E_{m+1}^{[r]}}\overline{\gamma}_\omega(e,e')$ for

### 2018-03-13 Grassmannian_cells.tex
added argument to proof of 4.18, minor changes

@@
 This is made precise in Conjecture~\ref{conj:cell dimensions}.
-\sayT{maybe we can erase some parts which show up twice in the introduction?}
-\subsection*{Acknowledgements}We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
+%\sayT{maybe we can erase some parts which show up twice in the introduction?}
+\subsubsection*{Acknowledgements}We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \begin{enumerate}
-    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_\tbfe(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\hat Q}_\tbfe(\hat X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
     \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
@@
 \end{theorem}
-\begin{proof}
-  The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover}, taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation (c.f.\ Lemma~\ref{le:lifts of transjectives}).
+\begin{proof}Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth.
+For the truncated preprojective representations of $K(n)$ this is Theorem~\ref{thm:truncpp}.
+For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively - when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) -  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth.
+Note that this is indeed clear for $m= 2$.
+
+  The first part now follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover}, taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation (c.f.\ Lemma~\ref{le:lifts of transjectives}).
   The dual version for preinjective representations follows immediately since $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$.
 
-  The second part follows in the same way, additionally, taking Theorem~\ref{thm:truncpp} into account.
+  The second part follows in the same way taking into account the initial remark.
 \end{proof}
@@
   Below we will usually apply Lemma~\ref{lem:2equivalence} after performing each of the equivalences from Definition~\ref{def:2equivalence}.
-  That is, given a 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
+  That is, given a 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $\alpha_V:p\to q$.
 \end{remark}

### 2018-03-13 Grassmannian_cells.tex
Fixed some typos in proof of Corollary 5.18

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Combinatorial description of non-empty cells}
+\section{Combinatorial Descriptions of Non-Empty Cells}
 \label{sec:combinatorics}
@@
   First note that there are $(n-r)u_m-u_{m-1}$ horizontal edges and $(n-r)u_{m-1}-u_{m-2}$ vertical edges in $D_{m+1}^{[r]}$. 
-  It follows that $H_{m,r+1,n}^{[r+1]}\sqcup H_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-1}-nu_{m-2}$ horizontal edges and $V_{m-1}^{[r+1]}\sqcup V_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ vertical edges (note that $H_{m,r+1,n}^{[r+1]}$ naturally identifies with the Dyck path $H_{m-1}^{[r+1]}$).
+  It follows that $H_{m,r+1,n}^{[r+1]}\sqcup H_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-1}-nu_{m-2}$ horizontal edges and $V_{m-1}^{[r+1]}\sqcup V_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ vertical edges (note that $D_{m,r+1,n}^{[r+1]}$ naturally identifies with the Dyck path $D_{m-1}^{[r+1]}$).
 
@@
   Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_m$ and subsets of $V_{m+1}$.
-  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_m$ is given, we refer the reader to \emph{loc. cit} for notation.
-  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
-  Thus by induction, we must have $H_{m-2}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_m^{[r+1]}\subset\Omega^{-1}S_H$.
+  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_m$ is given, we refer the reader to \emph{loc.\ cit} for notation.
+  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[Proposition 3.16]{rupel}.
+  Thus by induction, we must have $H_{m-1,r+1,n}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_m^{[r+1]}\subset\Omega^{-1}S_H$.
   It follows from piecewise compatibility that $H_m^{[r+1]}\cap(\varphi^*)^{-1}S_V=\varnothing$.
-  But then by the definition of $\varphi^*$ we have $V_{m-1}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$ so that $D(v_{u_m};S_V)=hv_{u_m}$ with $h$ as in the first case above.
+  But then by the definition of $\varphi^*$ we have $V_{m,r+1,n}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$ so that $D(v_{u_m};S_V)=hv_{u_m}$ with $h$ as in the first case above.
   Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_m}$.

### 2018-03-13 Grassmannian_cells.tex
Fixed some typos in proof of Corollary 5.18

@@
   On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
-  As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
+  As there is a natural bijection between these two labelings, this also gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
 \end{abstract}

### 2018-03-13 Grassmannian_cells.tex
Intro edits

@@
 Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
-%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
-it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
+it turns out that very interesting phenomena arise when restricting to certain quivers or to representations with certain properties.
 For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
@@
 It turns out that these are precisely those representations which can be obtained from indecomposable representations with dimension vector $(d,1)$ when applying reflection functors.
-Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
-
-As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to liftable representations of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
+Actually, we prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
+
+As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
 These are precisely those cases where the universal covering quiver differs from the original quiver.
@@
 In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
-These filtration can be successively described by short exact sequences.
+These filtrations can be successively described by short exact sequences.
 The main advantage when passing to the universal covering is that the preprojective representations covering the same dimension vector below become orthogonal, a property which rigidifies the situation in a sense.
@@
 The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
-This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations.
+This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the Caldero-Chapoton map for short exact sequences of representations.
 Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
@@
   Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
-  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
 
-In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
+In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions by introducing the notion of $2$-quivers which are a slight generalization of the usual notion of quivers.
 Theorem \ref{thm:2quivercells} can be formulated as follows.

### 2018-03-15 Grassmannian_cells.tex
Some small edits

@@
   \cite[Section 4]{bb}
-  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine vector bundle.
+  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
   Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
@@
 If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
-Indeed, we can trivialize each affine vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
+Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
 
@@
   \[\xymatrix{
-    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
-    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
-    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
-    &0&0&0&}\]
+    \Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
+    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
+    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
+    0&0&0&}\]
   By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
@@
   This in particular says the first map of the induced sequence
-  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
-  is zero.
+  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
+  is surjective.
   By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 

### 2018-03-15 Grassmannian_cells.tex
Brief intro to section 4

@@
 \label{QG}
+
+In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
+By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_0\subset X_1\subset \cdots \subset X_k=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i-1}$ is isomorphic to an affine space.
 

### 2018-03-15 Grassmannian_cells.tex
Section 4.2 edits

@@
 There are basically two possible ways to find cell decompositions of quiver Grassmannians if they exist.
-One is to find a non-trivial torus action on the quiver Grassmannian under consideration.
+One is to find a non-trivial $\CC^*$-action on the quiver Grassmannian under consideration.
 If the quiver Grassmannian is smooth, one can apply a result of Bia\l{}ynicki-Birula \cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
@@
 
-As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
+As a first step, we show that a $\CC^*$-action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
 These are precisely those cases where the universal covering quiver differs from the original quiver.
 This lifting property holds in particular for so-called tree modules, a class of representations which includes all exceptional representations.
-The fixed point set of this torus action consists precisely of those subrepresentations which can also be lifted to the universal (abelian) covering quiver.
-Actually, it turns out that each fixed point component is itself a quiver Grassmannian attached to the lifted representation.
-
-The next step is to investigate conditions under which the fixed point components admit a cell decomposition.
+The fixed point set of this $\CC^*$-action consists precisely of those subrepresentations which can also be lifted to the universal abelian covering quiver.
+Actually, it turns out that each fixed point component is itself a quiver Grassmannian attached to the lifted representation and thus, iterating this procedure, it suffices to understand the quiver Grassmannians for the universal covering quiver.
+
+The next step is to investigate conditions under which the iterated fixed point components admit a cell decomposition.
 Here the Caldero-Chapoton map comes into play.
@@
 In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
-As all the quiver Grassmannians of the (non-lifted) representation are smooth, this combines with the torus action to give a cell decomposition of these quiver Grassmannians.
+As all the quiver Grassmannians of the (non-lifted) representation are smooth, this combines with the iterated torus actions on fixed point components to give a cell decomposition of these quiver Grassmannians.
 
@@
 The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
-This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the Caldero-Chapoton map for short exact sequences of representations.
+This is obtained in Section~\ref{sec:fibrations} by combining iterated $\CC^*$-actions on quiver Grassmannians, which are introduced in Section~\ref{torusaction}, with the Caldero-Chapoton map for short exact sequences of representations.
 Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
@@
 \end{thm}
-This torus action can be iterated in such a way that the remaining torus fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
+This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$ fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
 As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
@@
 This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
-Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
+Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail, and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
 \begin{thm} 
@@
 \subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
-The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
+The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
 If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
@@
 \[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
-The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
+The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points.
 \begin{theorem}
@@
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
-We first consider a natural torus action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.
+We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
+Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$ fixed point sets can be calculated in an analogous manner.
 
@@
 for $q=1,\ldots,k$ and $r=1,\ldots,n$.
-Observe that each Schubert cell $X_\bfi$ is invariant under this torus action.
+Observe that each Schubert cell $X_\bfi$ is invariant under this $\CC^*$-action.
 
@@
 
-  For the reverse direction, assume $U\in X_{\bfi}$ is a torus fixed point represented by the matrix $M(U)$.
+  For the reverse direction, assume $U\in X_{\bfi}$ is a $\CC^*$ fixed point represented by the matrix $M(U)$.
   Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
@@
 Choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
-We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
+We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a $\CC^*$-action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
 Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
-In general, this does not induce a torus action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
+In general, this does not induce a $\CC^*$-action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
 Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
@@
   Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
-  Then the torus action on $X$ determined by $d$ induces a torus action on $\Gr_\bfe(X)$.
+  Then the $\CC^*$-action on $X$ determined by $d$ induces a $\CC^*$-action on $\Gr_\bfe(X)$.
 \end{lemma}
@@
   Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
-  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
+  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
 \begin{proof}
-  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
-  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
+  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$ fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
+  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
   By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
@@
 \end{proof}
-The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
+The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
 Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
-Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
-Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
-If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
+Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
+Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}_1}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
+If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
 \begin{corollary}
-Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
-  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
+  Let $X$ be a representation which can be lifted to $\tilde Q$.
+  Then there exists an iterated torus action such that
+  \[\Gr^Q_\bfe(X)^{(k+1)}\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)^{\CC^*}\cong \bigsqcup_{\hat\bfe^{(k+1)}} \Gr^{\hat Q^{(k+1)}}_{\hat\bfe^{(k+1)}}\big(\hat X^{(k+1)}\big)\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X),\]
+  where $\hat\bfe^{(k)},\,\hat\bfe^{(k+1)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
 \end{corollary}

### 2018-03-15 Grassmannian_cells.tex
typos + Thm 4.1

--- 2018-03-15 Grassmannian_cells.tex
@@
   On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
-  As there is a natural bijection between these two labelings, this also gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
+  As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
 \end{abstract}
@@
 Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
-it turns out that very interesting phenomena arise when restricting to certain quivers or to representations with certain properties.
+%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
+it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
 For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
@@
 It turns out that these are precisely those representations which can be obtained from indecomposable representations with dimension vector $(d,1)$ when applying reflection functors.
-Actually, we prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
-
-As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
+Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.
+
+As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to liftable representations of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
 These are precisely those cases where the universal covering quiver differs from the original quiver.
@@
 In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
-These filtrations can be successively described by short exact sequences.
+These filtration can be successively described by short exact sequences.
 The main advantage when passing to the universal covering is that the preprojective representations covering the same dimension vector below become orthogonal, a property which rigidifies the situation in a sense.
@@
 The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
-This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the Caldero-Chapoton map for short exact sequences of representations.
+This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations.
 Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
@@
   Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
-  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
+  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a torus action on $\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
 
-In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions by introducing the notion of $2$-quivers which are a slight generalization of the usual notion of quivers.
+In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
 Theorem \ref{thm:2quivercells} can be formulated as follows.
@@
 \[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
-Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
+Depending on context (in particular, the parity of $m+1$), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
 In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
@@
 \[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
-The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
+The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points. The following is proved in \cite[Section 4]{bb}, see also \cite[Section 4]{ca}.
 \begin{theorem}
   \label{thm:bb}
-  \cite[Section 4]{bb}
-  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
-  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
+Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.
+Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine vector bundle.
+  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$ where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
+
   In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
@@
 If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
-Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
+Indeed, we can trivialize each affine vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
 
@@
   For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
-  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
+  As reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
   \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
@@
   \[\xymatrix{
-    \Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
-    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
-    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
-    0&0&0&}\]
+    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
+    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
+    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
+    &0&0&0&}\]
   By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
@@
   This in particular says the first map of the induced sequence
-  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
-  is surjective.
+  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
+  is zero.
   By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
@@
   When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
-  We establish the result for $m\ge2$ by proving the following more general statement:\\
+  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Combinatorial Descriptions of Non-Empty Cells}
+\section{Combinatorial description of non-empty cells}
 \label{sec:combinatorics}
@@
 
-  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\cQ_V$.
+  Finally, let $\beta\subset(Q_V)_0$ be strong successor closed in $\cQ_V$.
   Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
@@
 By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
-Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
+Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \bigskip
 \[
@@
 
-As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\\
+As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\bigskip
 
@@
 \end{tikzpicture}
-\\
-
-The one of $\tilde P_4$ is given by:\\
+\bigskip
+
+The one of $\tilde P_4$ is given by:\bigskip
 
@@
 
-\end{tikzpicture}\\
-
+\end{tikzpicture}\bigskip
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \label{cor:short hooks}
-  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges, all other vertical egdes are immediately preceded by exactly $n$ horizontal edges.
+  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges, all other vertical edges are immediately preceded by exactly $n$ horizontal edges.
 \end{corollary}
@@
 The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
-Similarly, for a vertical edge $v\in V_{m+1}$ and a subset $S_V\subset V_{m+1}$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_{m+1}$ for which $|ev\cap H_{m+1}|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
+Similarly, for a vertical edge $v\in V_{m+1}$ and a subset $S_V\subset V_{m+1}$, the \emph{local shadow path} of $v$ with respect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_{m+1}$ for which $|ev\cap H_{m+1}|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
 \begin{definition}
@@
   First note that there are $(n-r)u_m-u_{m-1}$ horizontal edges and $(n-r)u_{m-1}-u_{m-2}$ vertical edges in $D_{m+1}^{[r]}$. 
-  It follows that $H_{m,r+1,n}^{[r+1]}\sqcup H_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-1}-nu_{m-2}$ horizontal edges and $V_{m-1}^{[r+1]}\sqcup V_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ vertical edges (note that $D_{m,r+1,n}^{[r+1]}$ naturally identifies with the Dyck path $D_{m-1}^{[r+1]}$).
+  It follows that $H_{m,r+1,n}^{[r+1]}\sqcup H_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-1}-nu_{m-2}$ horizontal edges and $V_{m-1}^{[r+1]}\sqcup V_{m+1}^{[r+1]}$ contains $n(n-r)u_{m-2}-nu_{m-3}$ vertical edges (note that $H_{m,r+1,n}^{[r+1]}$ naturally identifies with the Dyck path $H_{m-1}^{[r+1]}$).
 
@@
   Clearly, the map $\varphi^*$ gives a bijection between subsets of $H_m$ and subsets of $V_{m+1}$.
-  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_m$ is given, we refer the reader to \emph{loc.\ cit} for notation.
-  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[Proposition 3.16]{rupel}.
-  Thus by induction, we must have $H_{m-1,r+1,n}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_m^{[r+1]}\subset\Omega^{-1}S_H$.
+  In Section 3.2 of \cite{rupel}, a new pair of subsets $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ for $D_m$ is given, we refer the reader to \emph{loc. cit} for notation.
+  By \cite[Proposition 3.10]{rupel}, the pair $\big((\varphi^*)^{-1}S_V,\Omega^{-1}S_H\big)$ is not compatible, but is piecewise compatible by \cite[proposition 3.16]{rupel}.
+  Thus by induction, we must have $H_{m-2}^{[r+1]}\subset(\varphi^*)^{-1}S_V$ and $V_m^{[r+1]}\subset\Omega^{-1}S_H$.
   It follows from piecewise compatibility that $H_m^{[r+1]}\cap(\varphi^*)^{-1}S_V=\varnothing$.
-  But then by the definition of $\varphi^*$ we have $V_{m,r+1,n}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$ so that $D(v_{u_m};S_V)=hv_{u_m}$ with $h$ as in the first case above.
+  But then by the definition of $\varphi^*$ we have $V_{m-1}^{[r+1]}\cap S_V=\varnothing$ and $S_V^{[r+1]}=V_{m+1}^{[r+1]}$ so that $D(v_{u_m};S_V)=hv_{u_m}$ with $h$ as in the first case above.
   Since $(S_H,S_V)$ is not compatible, Theorem~\ref{th:blocking edge conditions} states that $h$ must be the blocking edge for $S_H$ and we must have $D(h;S_H)=hv_{u_m}$.
@@
 Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).
-We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explaination of this result.
+We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explanation of this result.
 \begin{conjecture}
@@
 \bibitem{brenner-butler} 
-  S.~Benner, M.~C.~R.~Butler: The equivalence of certain functors occuring in the representation theory of artin algebras and species.
+  S.~Brenner, M.~C.~R.~Butler: The equivalence of certain functors occuing in the representation theory of artin algebras and species.
 Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).
@@
   P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Annales Scientifique de l'Ecole Normale Superi\'{e}ure (4) \textbf{39} (6), 983-1009 (2006).
+\bibitem{ca}	J.B.~Carrell: Torus actions and cohomology.
+Algebraic quotients.
+Torus actions and cohomology.
+The adjoint representation and the adjoint action, 83-158.
+Encyclopaedia Mathematical Science \textbf{131}, Invariant Theory and Algebraic
+Transformation Groups, Springer, Berlin, 2002.
 \bibitem{ce} 

### 2018-03-15 Grassmannian_cells.tex

--- 2018-03-15 Grassmannian_cells.tex
@@
 \[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
-The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points.
+The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
 \begin{theorem}
   \label{thm:bb}
-  \cite[Section 4]{bb}
-  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
-  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
+  Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.
+  Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
+  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$, where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
   In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.

### 2018-03-15 Grassmannian_cells.tex
typo

@@
 \bibitem{brenner-butler} 
-  S.~Brenner, M.~C.~R.~Butler: The equivalence of certain functors occuing in the representation theory of artin algebras and species.
+  S.~Brenner, M.~C.~R.~Butler: The equivalence of certain functors occurring in the representation theory of artin algebras and species.
 Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).

### 2018-03-16 Grassmannian_cells.tex
small changes

@@
 
-If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
-Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.
+If each component $C_i$ admits a cell decomposition, Theorem~\ref{thm:bb} implies the same is true of $X$.
+Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ and then taking the natural ordering of the resulting affine spaces gives a cell decomposition of $X$.
 
@@
 Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
-Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}_1}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
+Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
 If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
@@
 
-Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$. Then we have
-$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
-The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
+For $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have $$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
+Then $\Psi_\tbfe$ restricts to a map
 \[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
@@
   \label{vb}
-  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$, then it is an affine bundle over the image.
+  If $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$, then $\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ is an affine bundle.
   In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.

### 2018-03-16 Grassmannian_cells.tex
Added corollary on openness and a say about cell decompositions

--- 2018-03-15 Grassmannian_cells.tex
@@
 
+\begin{corollary}
+  The image of $\Psi_{m+1,I,j}$ is open for all $\tbfe$, $\tbff$, and $\tbfg$.
+\end{corollary}
+
 Now we are able to state the following result concerning the fibers of $\Psi_{m+1,I,j}$:
@@
   \label{cellscover}
-  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
+  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition.
 \end{theorem}
@@
   \vs
+
+  \sayD{When $\Psi_{m+1,I,j}$ is surjective, $\cG_{\tbff,\tbfg}$ is a closed subset of the Grassmannian.
+  The map is not surjective exactly when $\tbfg=\udim \tilde P_{m+1}^I$ and so we get a cell decomposition by taking the affine cells from this $\cG_{\tbff,\tbfg}$ last.}
 

### 2018-03-17 Grassmannian_cells.tex
Notation changes

@@
 \newcommand{\bfJ}{\mathbf{J}}
+\newcommand{\bfs}{\mathbf{s}}
+\newcommand{\bft}{\mathbf{t}}
 
@@
 \newcommand{\tbfh}{{\tilde\bfh}}
+\newcommand{\tbfs}{{\tilde\bfs}}
+\newcommand{\tbft}{{\tilde\bft}}
 
@@
 Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
-This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
-\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto \big(V\cap M,(V+M)/M\big).\]
-Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.
-
-For $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have $$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
-Then $\Psi_\tbfe$ restricts to a map
-\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
-The following is proved in \cite[Section 3]{cefr}.
+For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
+\begin{align*}
+  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
+  E&\mapsto \big(E\cap M,(E+M)/M\big).
+\end{align*}
+Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.
+
+For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
+\begin{equation}
+  \label{eq:grassmannian decomposition}
+  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
+\end{equation}
+Then $\Psi$ restricts to a map
+\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+The following results are proven in \cite[Section 3]{cefr}.
+For completeness we include a proof of the first.
+\begin{lemma}
+  \label{le:good partition}
+  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
+  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\succeq\tbff}} \cG_{\tbff',\tbfg}\]
+  is closed in $\Gr_\tbfe(B)$.
+\end{lemma}
+\begin{proof}
+  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
+  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
+  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
+  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
+  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\geq\tbff}} \cG_{\tbff',\tbfg}\subset \Gr_\tbfe(B)\]
+  for any fixed $\tbff$.
+  Any refinement of this partial order to a total order will give the claim.
+\end{proof}
 \begin{theorem}
   \label{vb}
-  If $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$, then $\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ is an affine bundle.
-  In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+  If $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
+  In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
 \end{theorem}
@@
 Fix $m\ge1$.
-For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
+For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
 \begin{equation}
@@
 \end{equation}
-which induces a map between quiver Grassmannians as above:
+which induces a map between quiver Grassmannians as above for any fixed $\tbfe$:
 \begin{equation}
   \label{eq:truncated CC}
-  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
+  \Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
 \end{equation}
@@
 where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
-Then in the same way as above we obtain the map
+Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
 \begin{equation}
   \label{eq:truncated CC2}
-  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
+  \Phi:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
 \end{equation}
@@
   \begin{enumerate}
-    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
-    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
+    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
+    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
   \end{enumerate} 
@@
   \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
-  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
+  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
   \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
@@
 
-  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
+  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi^{-1}(V,W)$.
   This gives rise to the following commutative diagram:  
@@
 
-  If $W=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)=\varnothing$.
+  If $W=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)=\varnothing$.
 
@@
   But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
-  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
-\end{proof}
-
-\begin{corollary}
-  The image of $\Psi_{m+1,I,j}$ is open for all $\tbfe$, $\tbff$, and $\tbfg$.
-\end{corollary}
-
-Now we are able to state the following result concerning the fibers of $\Psi_{m+1,I,j}$:
+  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
+\end{proof}
+
+Now we are able to state the following result concerning the fibers of $\Psi$:
 \begin{proposition}
@@
   \begin{enumerate}
-    \item For $W\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
-    \item If $W=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,W)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
-      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
+    \item For $W\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi^{-1}(U,W)\cong\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
+    \item If $W=\tilde P_{m+1}^I$, the fiber $\Psi^{-1}(U,W)$ is not empty if and only if $\Phi(U)\neq(U,0)$.
+      In this case, we have $\Psi^{-1}(U,W)\cong\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
   \end{enumerate}
@@
 \begin{remark}
-  Part (1) of Proposition~\ref{fibers} holds equally well when considering the analogues of the Caldero-Chapoton maps $\Psi_{m+1,I,j}$ for $K(n)$.
+  Part (1) of Proposition~\ref{fibers} holds equally well when considering the analogues of the Caldero-Chapoton maps $\Psi$ for $K(n)$.
   This follows from Corollary~\ref{cor:base fibers} and Lemma~\ref{le:projective subrepresentations}.
@@
   The second statement follows directly from Proposition~\ref{quotient}.
+\end{proof}
+
+\begin{corollary}
+  For all $\tbff$ and $\tbfg$, the image of $\Psi_{\tbff,\tbfg}$ is open in $\Gr_\tbff(\tilde P_{m,j})\times\Gr_\tbfg(\tilde P_{m+1}^I)$.
+\end{corollary}
+\begin{proof}
+  By Proposition~\ref{fibers}, the map $\Psi_{\tbff,\tbfg}$ is surjective for $\tbfg\ne\udim\tilde P_{m+1}^I$ and there is nothing to show in this case.
+  Assume $\tbfg=\udim\tilde P_{m+1}^I$.
+  By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(U,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
+  But the map $U\mapsto\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
 \end{proof}
@@
   Choose any subset $I\subset I_0$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
-  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
+  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
   Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
@@
 
-  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi_{m+1,I,j}$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
+  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
   \begin{itemize}
@@
   \end{itemize}
-  When the fibers of $\Psi_{m+1,I,j}$ are not empty, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  When the fibers of $\Psi$ are not empty, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
   For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
   But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
-\begin{comment}
-\noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$.
-The quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition into affine spaces which is compatible with $\pi_{m,\uj}^{\bf j}$  in the following way:
- Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
-Then we have $\pi_{m,\uj}^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
-\vs
-
-We proceed by induction on $m$ and reverse (?) induction on $l$.
-Let $\uj'=(j_1,\ldots,j_{l-1})$.
-If $m=1$ or $m=2$, the statement is straightforward for arbitrary $l$ as all quiver Grassmannians are points.
-For general $m$, we consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ which induces a map between quiver Grassmannians
-$$\Psi_{m,\uj}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj}).$$
-It is important that we can choose $j_l$ arbitrarily with respect to the condition $j_l\neq j_1,\ldots, j_{l-1}$. Moreover, we consider the short exact sequence
-$$\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf i}_m}$$
-where
-$${\bf i}=((1,\ldots,j_l-1,\widehat{j_l},j_l+1,\ldots,n),(j_1,\ldots,j_{l-1}))$$
-and $\tau\tilde P_{m}^{\uj} =\tilde P^{\uj}_{m-2}=\tilde P_{m-2}^{\bf i}$ together with the induced map on quiver Grassmannians $\Phi_{m,\uj}$.
-
-By induction hypothesis the quiver Grassmannians $\Gr^{\tilde Q}_\tbff( \tilde P_{m-1,j_l})$ have cell decompositions which are compatible with $\pi^{\bf i}_m$ and, moreover, the quiver Grassmannians $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ have a cell decompositions which are compatible with $\pi^{\bf j}_{m,\uj}$.
-The second part of Proposition~\ref{fibers} says that the fibers are empty if and only if $\pi^{\bf i}_m=0$ and $\tbfg=\udim \tilde P_{m+1}^{(k)}$.
-This yields a collection of cells over which the fibers are empty.
-Note that $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is just a point in this case.
-
-If $\tbfg\neq \udim\tilde P_{m+1}^{(k)}$, by Proposition~\ref{fibers}, the fiber dimension only depends on the dimension vectors $\tbff, \tbfg$ which means that they are constant over the cells of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})\times \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$.
-In particular, they are constant over cells whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)\neq 0$, but also over those whose subrepresentations $U\in \Gr^{\tilde Q}_\tbff(P_{m-1,i_k})$ satisfy $\pi_m^{\bf i}(U)= 0$.
-By Theorem~\ref{vb}, it follows that $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ has a cell decomposition.
-
-Thus it remains to show that this cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj'})$ is compatible with $\pi_{m,\uj'}^{\bf j}$ where ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ with $\underline{j_1}=(\uj',j_{1,l},\ldots,j_{1,n-1})\in I_{n-1}$ and $j_{1,l}=j_l$.
-Recall that we have $\pi_{m,\uj'}^{\bf j}=\pi_{m,\uj}^{\bf j}\circ\pi_{m,\uj'}^{j_l}$ by Lemma~\ref{le:truncated quotients}.(2).
-
-Fix $\tbff$ and $\tbfg$ together with cell decompositions 
-\[\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})=\coprod_{i\in I} B_i,\quad \Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})=\coprod_{k\in K} C_k\]
-such that the cell decomposition of $\Gr^{\tilde Q}_\tbfg(\tilde P_{m}^{\uj})$ is compatible with $\pi^{\bf j}_{m,\uj}$.
-To finish the prove, it suffices to show that the cell decomposition of for $\Gr_{\tbff+\tbfg}(\tilde P_m^{\uj'})$ is compatible with $\pi^{\bf j}_{m,\uj'}$ because every projection onto a truncated preprojective is of this shape and we did not impose any restrictions on ${\bf j}$.
-
-We distinguish the following cases
-\begin{itemize}
-\item $\tbfg =\udim \tilde P_{m}^{\uj}$.
-\item $\tbfg \neq \udim \tilde P_{m}^{\uj}$ with cells $B_i$ and $C_k$ such that $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$.
- \item $\tbfg \neq \udim \tilde P_{m}^{\uj}$ with cells $B_i$ and $C_k$ such that $\pi^{\bf j}_{m,\uj}(V)\neq 0$ for all $V\in C_k$.
-
-\end{itemize}
-In the first case, we have $\Gr_\tbfg(\tilde P_{m}^{\uj})=\{\pt\}$ and thus there exists a single cell $C_0=\mathbb{A}^0$.
-Fix a cell $B_i\subset\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$.
-As the cell decomposition of $\Gr^{\tilde Q}_\tbff(P_{m-1,j_l})$ is compatible with $\pi_{m}^{\bf i}$, we either have that the fiber over $B_i\times C_0$ is empty or that the fiber is of constant dimension, thus building a new cell $CB_i$.
-For all representations $U\in CB_i$ we have $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$ because $\pi_{m,\uj}^{\bf j}$ is surjective and $\pi_{m,\uj'}^{j_l}(U)=\tilde P_{m}^{\uj}$.
-
-In the second case, the fiber over $B_i\times C_k$ is non empty and of constant dimension, thus building a new cell $CB_{i,k}$.
-As we have $\pi^{\bf j}_{m,\uj}(V)=0$ for all $V\in C_k$, it follows that $\pi^{\bf j'}_{m,\uj'}(U)=0$ for all representations $U\in (CB)_{i,k}$.
-
-In the third case, an analogous argument shows that $\pi^{\bf j'}_{m,\uj'}(U)\neq 0$ for all $U\in (CB)_{i,k}$.
-
-%Thus let $\pi_{m,\uj'}^{\bf j'}(U)= 0$ with $U\subset \tilde P_{m}^{\uj'}$.
-Then we either have $\pi_{m,\uj'}^{j_l}(U)=0$ which means that $U$ comes from a subrepresentation of $\tilde P_{m,j_l}$ and $\tbfg=0$.
-In this case, all representations in the cell of $U$ come from a subrepresentation of $\tilde P_{m,j_l}$.
-Thus assume that $\pi_{m,\uj'}^{j_l}(U)\neq 0$.
-We have $\pi_{m,\uj'}^{j_l}(U)\neq \tilde P_{m}^{\uj}$ because otherwise we had $\pi_{m,\uj'}^{\bf j'}(U)\neq 0$.
-Apply induction hypothesis now.
-
-We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
-\[\Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} \Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]
-
-By Lemma~\ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition.
-The second part of the Proposition says that the fibers are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$.
-In all other cases, the fiber dimensions only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $\Gr^{\tilde Q}_\tbff( P(m,k))\times \Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times \Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional), apply Lemma~\ref{vb}?}.
-Analogously to Lemma~\ref{directsums}, we can conclude that this induces trivial bundles over every affine cell.
-In total, this yields a cell decomposition of the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
-\end{comment}
 \end{proof}

### 2018-03-17 Grassmannian_cells.tex
Cell decomposition

@@
 \begin{abstract}
-  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
+  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
   In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
@@
 For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
-For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
+For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition, see \cite{ce,lw} and references therein.
 It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
@@
 If the short exact sequence has certain properties -- e.g.
-(almost) split sequences and certain generalizations -- then cell decompositions of quiver Grassmannians attached to the outer terms transfer to a decomposition of the quiver Grassmannians of the middle term.
-
-In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition into affine spaces.
+(almost) split sequences and certain generalizations -- then cell decompositions of quiver Grassmannians attached to the outer terms transfer to a cell decomposition of the quiver Grassmannians of the middle term.
+
+In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition.
 The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
@@
 
-The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
+The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they each admit a cell decomposition.
 This is obtained in Section~\ref{sec:fibrations} by combining iterated $\CC^*$-actions on quiver Grassmannians, which are introduced in Section~\ref{torusaction}, with the Caldero-Chapoton map for short exact sequences of representations.
@@
 \begin{thm} 
-  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
+  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition.
 \end{thm}
@@
 \begin{thm}
-  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
+  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the affine cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
   In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
@@
 By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_0\subset X_1\subset \cdots \subset X_k=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i-1}$ is isomorphic to an affine space.
+Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_1\sqcup\cdots\sqcup U_i$ is closed in $X$ with $X_k=X$.
+We call the subsets $U_i$ the \emph{affine cells} for this cell decomposition.
 
@@
   \begin{enumerate}
-    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\hat Q}_\tbfe(\hat X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\hat Q}_\tbfe(\hat X)$ has a cell decomposition, then $\Gr_\bfe(X)$ has a cell decomposition.
     \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
@@
   By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(U,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
-  But the map $U\mapsto\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
+  But the map $U\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
 \end{proof}
@@
   \noindent{\bf Claim.}
-  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
@@
   To begin, we assume $|J|=n-1$ and thus $J=I_0$.
-  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,i_0}^{J_0}$ and so by induction on $m$ the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)=\Gr^{\tilde Q}_\tbfe(\tilde P_{m,i_0}^{J_0})$ admits a decomposition into affine spaces so that the compatibility condition ($\dagger$) holds for the unique map $\pi_{m,i_0}^{J_0,\delta\bfI}:\tilde P_{m,i_0}^{J_0}\to\tilde P_{m,i_0}^{\delta\bfI}$.
+  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,i_0}^{J_0}$ and so by induction on $m$ the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)=\Gr^{\tilde Q}_\tbfe(\tilde P_{m,i_0}^{J_0})$ admits a cell decomposition so that the compatibility condition ($\dagger$) holds for the unique map $\pi_{m,i_0}^{J_0,\delta\bfI}:\tilde P_{m,i_0}^{J_0}\to\tilde P_{m,i_0}^{\delta\bfI}$.
   But $\tilde P_{m,i_0}^{\delta\bfI}=\tilde P_{m+1}^\bfI$ so that $\pi_{m,i_0}^{J_0,\delta\bfI}$ coincides with the map $\pi_{m+1}^{J,\bfI}$ and thus the condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
@@
   This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
-  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
+  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a cell decomposition which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
   \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{k=1}^r C_k.\]
@@
   When $m=2$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ is just a point.
-  For $m\ge3$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ admits a decomposition into affine spaces which is compatible with the map $\pi_{m,j}^\bfJ:\tilde P_{m,j}\to\tilde P_{m-1,(j,j)}^I$, where $\bfJ=(\{1,\ldots,\widehat j,\ldots,n\},I)$, say
+  For $m\ge3$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ admits a cell decomposition which is compatible with the map $\pi_{m,j}^\bfJ:\tilde P_{m,j}\to\tilde P_{m-1,(j,j)}^I$, where $\bfJ=(\{1,\ldots,\widehat j,\ldots,n\},I)$, say
   \[\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=\coprod_{\ell=1}^s B_\ell.\] 
@@
   \begin{enumerate}
-    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
+    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
     \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
-      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
+      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition.
   \end{enumerate}
@@
   Let $X\in\rep K(n)$ be a direct sum of exceptional representations.
-  Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
+  Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition.
   In particular, this is true for all rigid representations of $K(n)$.
@@
   \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
-  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition into affine spaces.
+  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition.
   Consider the Caldero-Chapoton map
@@
   for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
-  By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
+  By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
   By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.
@@
   \[\ses{I(s)}{X}{P(r)}.\]
-  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition into affine spaces.
+  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition.
 \end{proof}
@@
 \noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
-The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
+The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition from Section~\ref{sec:fibrations}.
 The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
@@
   \begin{enumerate}
-    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_{m+1}^{[r]}\big)$ (resp.
+    \item The affine cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_{m+1}^{[r]}\big)$ (resp.
 $\Gr_\bfe\big(P_{m+1}^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\cQ_{m+1}^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp.
@@
   \label{th:compatible cells}
-  For $m\ge1$ and $V\in\Gr(\cH_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
+  For $m\ge1$ and $V\in\Gr(\cH_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with affine cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
 \end{theorem}

### 2018-03-17 Grassmannian_cells.tex
The remark

@@
 \newcommand{\Hom}{\operatorname{Hom}}
-\newcommand{\im}{\operatorname{im}}
+\renewcommand{\Im}{\operatorname{Im}}
 \newcommand{\Ind}{\mathrm{Ind}}
@@
 In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
-By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_0\subset X_1\subset \cdots \subset X_k=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i-1}$ is isomorphic to an affine space.
-Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_1\sqcup\cdots\sqcup U_i$ is closed in $X$ with $X_k=X$.
-We call the subsets $U_i$ the \emph{affine cells} for this cell decomposition.
+By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
+Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
+We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
 
@@
   for any fixed $\tbff$.
-  Any refinement of this partial order to a total order will give the claim.
+  Any refinement of this partial order to a total order $\preceq$ will give the claim.
 \end{proof}
@@
   \label{vb}
-  If $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
-  In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
+  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
+  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
 \end{theorem}
-%\begin{proof}\footnote{sketch, double-check}
-%As $X$ and $Y$ are projective, they are compact.
-As the fibers are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$.
-This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
-%\end{proof}
-
-We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
+
+\begin{remark}
+  \label{rem:cell decompositions}
+  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
+  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
+
+  By Theorem~\ref{vb}, to establish cell decompositions for the $\cG_{\tbff,\tbfg}$ it suffices to find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ for which $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells.
+\end{remark}
+
+We will apply these results in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
 Fix $m\ge1$.

### 2018-03-17 Grassmannian_cells.tex
Better remark?

@@
   \label{rem:cell decompositions}
+  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.
+
   By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
   Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
-
-  By Theorem~\ref{vb}, to establish cell decompositions for the $\cG_{\tbff,\tbfg}$ it suffices to find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ for which $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells.
 \end{remark}

### 2018-03-17 Grassmannian_cells.tex
Thm 4.18

@@
  For $m=2$, we write $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=B_1$.
-
-  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
+In view of Remark \ref{rem:cell decompositions}, we need to show that the image of each $\Psi_{\tbff,\tbfg}$ is compatible with these cell decompositions in order to establish a cell decomposition of each $\mathcal G_{\tbff,\tbfg}$ which then gives a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
+
+ Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(U,V)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
   \begin{itemize}
@@
   \end{itemize}
-  When the fibers of $\Psi$ are not empty, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or non fibres over $B_l\times C_k$ are empty.
+This shows the compatibility with the image.
+If the fibre is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
+
   For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
   But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
+
 \end{proof}

### 2018-03-17 Grassmannian_cells.tex
Intro to section 4

@@
 This is made precise in Conjecture~\ref{conj:cell dimensions}.
-%\sayT{maybe we can erase some parts which show up twice in the introduction?}
 \subsubsection*{Acknowledgements}We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
@@
 The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\rep\hat Q$ and on $\ZZ^{\hat Q_1}$.
-%We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
 The analogous observation can also be made for $\widetilde Q$.
@@
 We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
+Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
+Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union of a subset of the affine cells for $X$.
+In this case, $U$ also has a cell decomposition given by taking exactly those affine cells which are contained in $U$.
 
@@
   Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(\hat X)$.
-  %In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
-  %\[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]
 
@@
 
-  \sayD{When $\Psi_{m+1,I,j}$ is surjective, $\cG_{\tbff,\tbfg}$ is a closed subset of the Grassmannian.
-  The map is not surjective exactly when $\tbfg=\udim \tilde P_{m+1}^I$ and so we get a cell decomposition by taking the affine cells from this $\cG_{\tbff,\tbfg}$ last.}
-
   In what follows, we will freely use the notation from Lemma~\ref{le:truncated quotients}.
@@
   This shows the compatibility with the image.
-If the fibre is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  If the fiber is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
   Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
@@
 This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
-
-\end{proof}
-
-%Note that we can also consider 
-%$\Psi_1:\Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times \Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows).
-But then one needs to adjust $\Psi_2$ because the factor of $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
+\end{proof}
 

### 2018-03-17 Grassmannian_cells.tex
small edits

--- 2018-03-17 Grassmannian_cells.tex
@@
     \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
-    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
+    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$.
   \end{itemize}
-By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or non fibres over $B_l\times C_k$ are empty.
+By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or none of the fibers over $B_l\times C_k$ are empty.
 This shows the compatibility with the image.
-If the fibre is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+If the fiber is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
 Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
@@
   for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
-  By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
+Following Remark \ref{rem:cell decompositions}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
   By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.

### 2018-03-17 Grassmannian_cells.tex

--- 2018-03-17 Grassmannian_cells.tex
@@
     \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
-    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
+    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$.
   \end{itemize}
-  By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or non fibres over $B_l\times C_k$ are empty.
+By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or none of the fibers over $B_l\times C_k$ are empty.
 This shows the compatibility with the image.

### 2018-03-17 Grassmannian_cells.tex
...

@@
 \label{QG}
-
+\noindent 
 In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.

### 2018-03-17 Grassmannian_cells.tex
Cor 4.22 edit

--- 2018-03-17 Grassmannian_cells.tex
@@
   But now the same proof as for exceptional roots applies in order to show that these quiver Grassmannians need to be smooth, see \cite[Corollary 4]{cr}.
- % \footnote{The proof using moduli spaces needs to be written}
-  %Both claims are proven via the same geometric construction.
-  %For each dimension vector $\bfe$, there is a smooth variety
-  %\[X_{\bfe,m}=\{(\tilde E,V):V\in \Gr_d(\cH_m),\ P_m\otimes V\subset\tilde E\subset P_{m+1}i,\ \udim\tilde E=\bfe+d\udim P_m\}.\]
-  %Under the natural projection $\pi:X_{\bfe,m}\to \Gr_d(\cH_m)$, the fiber $\pi^{-1}(V)$ identifies with $\Gr_\bfe(P_{m+1}^V)$.
-  %In particular, this implies $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr_d(\cH_m)$.
-  %The variety $X_{\bfe,m}$ supports an action of $GL_n(\CC)$ by setting $g.(\tilde E,V)=\big(\phi_{m+1,g}^{-1}(g.\tilde E),g.V\big)$.
-  %Indeed, by Lemma~\ref{le:g equalities} we have 
-  %\[P_m\otimes g.V=\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)=\phi_{m+1,g}^{-1}\big(g.(P_m\otimes V)\big)\subset\phi_{m+1,g}^{-1}(g.\tilde E).\]
-  %Observe that the projection map $\pi$ is $GL_n(\CC)$-equivariant and thus by Lemma~\ref{le:transitivity} the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ and $\Gr_\bfe(P_{m+1}^W)$ are isomorphic for any $V,W\in \Gr_d(\cH_m)$.
-\end{proof}
-
-%\begin{lemma}
-%  For any $m\ge1$, we have 
-%  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
-%  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
-%\end{lemma}
-%\begin{proof} 
-%  Note that we have an Auslander-Reiten sequence
-%  \begin{equation}
-%    \label{eq:AR sequence}
-%    0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
-%  \end{equation}
-%  with irreducible homomorphisms $f_i$ which are also linearly independent. 
-%  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
-%  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
-%  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
-%\end{proof}
-%\begin{remark}
-%  Fix a basis $\{f_{m,1},\ldots,f_{m,n}\}$ for $\Hom(P_m,P_{m+1})$, $m\ge2$.
-%  Define a basis $\{f_{\ell,1},\ldots,f_{\ell,n}\}$ for each $\Hom(P_\ell,P_{\ell+1})$, $1\le\ell\le m-1$, by downward induction as follows.  
-%  Write $\iota_\ell:P_\ell\to P_{\ell+1}^n$ for the left-hand morphism from the sequence \eqref{eq:AR sequence} computed using $f_k=f_{\ell+1,k}$, $1\le k\le n$. 
-%  Then the basis element $f_{\ell,k}$ is given by composing $\iota_\ell$ with the coordinate projection $\pi_k:P_{\ell+1}^n\to P_{\ell+1}$ onto the $k$-th factor.
-%  Indeed, applying $\Hom(-,P_{\ell+1})$ to this sequence \eqref{eq:AR sequence} gives an isomorphism $\Hom(P_{\ell+1}^n,P_{\ell+1})\cong\Hom(P_\ell,P_{\ell+1})$ whereby the natural basis of coordinate projections on the left is taken to the basis $\{f_{\ell,k}\}$ on the right.
-%\end{remark}
+\end{proof}
 
@@
   for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
-Following Remark \ref{rem:cell decompositions}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
+  Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
   By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.

### 2018-03-17 Grassmannian_cells.tex
Intro edits

@@
 \usetikzlibrary{arrows}
-%\usepackage{pgflibraryarrows}
-%\usepackage{pgflibrarysnakes}
 \usetikzlibrary{fit}
@@
 
-\usepackage[inline]{showlabels}
-
+%\usepackage[inline]{showlabels}
 %\usepackage[marginal]{showlabels}
-%
+
 \newtheorem{theorem}{Theorem}[section]
@@
 \begin{abstract}
-  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
+  We prove that all quiver Grassmannians for exceptional representations of a generalized Kronecker quiver admit a cell decomposition.  
   In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
@@
   We also provide two natural combinatorial labelings for these cells.
-  On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
-  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
-  As there is a natural bijection between these two labelings, this also gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
+  On the one hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
+  On the other hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
+  The natural bijection between these two labelings gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
 \end{abstract}
@@
 it turns out that very interesting phenomena arise when restricting to certain quivers or to representations with certain properties.
-For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
-For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition, see \cite{ce,lw} and references therein.
+For instance, quiver Grassmannians attached to exceptional representations are smooth~\cite{cr}.
+For Dynkin quivers and tame quivers of types~$\tilde A$ or~$\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition, see \cite{ce,lw} and references therein.
 It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
@@
 One is to find a non-trivial $\CC^*$-action on the quiver Grassmannian under consideration.
-If the quiver Grassmannian is smooth, one can apply a result of Bia\l{}ynicki-Birula \cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
+If the quiver Grassmannian is smooth, one can apply a result of Bia\l{}ynicki-Birula~\cite{bb} which shows that the quiver Grassmannian decomposes into affine bundles over the fixed point components.
 In particular, this shows that the quiver Grassmannian has a cell decomposition if the fixed point components have such a decomposition.
@@
 If the short exact sequence has certain properties -- e.g.
-(almost) split sequences and certain generalizations -- then cell decompositions of quiver Grassmannians attached to the outer terms transfer to a cell decomposition of the quiver Grassmannians of the middle term.
+(almost) split sequences and certain generalizations -- then cell decompositions of quiver Grassmannians attached to the outer terms transfer to cell decompositions for the quiver Grassmannians of the middle term.
 
@@
 
-The results of \cite{rupel} giving a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$ suggest that the dimensions of cells can be computed using this combinatorics (or the equivalent combinatorics of compatible pairs).
+The results of \cite{rupel} give a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$.
+This suggests that the dimensions of cells can be directly computed using this combinatorics (or the equivalent combinatorics of compatible pairs).
 This is made precise in Conjecture~\ref{conj:cell dimensions}.
-\subsubsection*{Acknowledgements}We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
+
+\subsubsection*{Acknowledgements}
+We would like to thank Giovanni Cerulli Irelli, Hans Franzen, Oliver Lorscheid and Markus Reineke for very fruitful discussions related to this project.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Representation Theory of Generalized Kronecker Quivers}
@@
 Set $\cH_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
-Write $\Gr(\cH_m)$ for the \emph{total Grassmannian} of $\cH_m$ whose elements are nontrivial proper subspaces $V\subset \cH_m$.
+Write $\Gr(\cH_m)$ for the \emph{total Grassmannian} of $\cH_m$ whose elements are non-trivial proper subspaces $V\subset \cH_m$.
 Some results below remain true if we allow $\cH_m$ or $0$ as elements of $\Gr(\cH_m)$, but not all, so for uniformity of exposition we omit these possibilities.
@@
 \label{sec:truncated preprojectives}
+
 Motivated by Lemma~\ref{le:injective evaluation maps}, we define the following.
@@
   However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
-  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
 \end{proof}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Lifting to \texorpdfstring{$\mathbf{\widetilde{K(n)}}$}{K(n)}}
@@
 For $k\ge1$, set
-\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
+\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]
 Depending on context (in particular, the parity of $m+1$), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quiver Grassmannians}
 \label{QG}
+
 \noindent 
@@
 
-\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}
+\label{sec:bb}
+
 The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Torus Actions on Quiver Grassmannians}
 \label{torusaction}
+
 Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
@@
 In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
-\begin{theorem}\label{thm:torusfixedpoints}
+\begin{theorem}
+  \label{thm:torusfixedpoints}
   Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
@@
 \end{corollary}
-%\begin{corollary}
-%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
-%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
-%\end{corollary}
+
 Define the $F$-polynomial of a representation $X$ by 
-$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].$$
-
+\[F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].\]
 \begin{corollary}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{\texorpdfstring{$\mathbf{GL_n}$}{Gln}-Action on Arrows of \texorpdfstring{$\mathbf{K(n)}$}{K(n)}}
+
 The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq \cH_m$.
@@
 \end{proof}
-
-%Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
-%Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
-%With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
-%Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.
 
@@
 
-%\begin{corollary}
-%  \label{cor:preprojective stability}
-%  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
-%\end{corollary}
-%\begin{proof}
-%  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
-%  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
-%\end{proof}
-%For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.
-
-%\begin{lemma}
-%  \label{le:transitivity}
-%  The action of $GL_n(\CC)$ on $\cH_m$ induces a transitive action of $GL_n(\CC)$ on each component $\Gr_d(\cH_m)$.
-%\end{lemma} 
-%\begin{proof}
-%  The map $\theta\mapsto g.\theta$ for $\theta\in \cH_m$ induces a group homomorphism $GL_n(\CC)\to GL(\cH_m)$ which we denote by $g\mapsto\tilde g_m$.
-%  We claim that this homomorphism is surjective which immediately implies the result.
-%
-%  We work by induction on $m$.
-%  Suppose $GL_n(\CC)\to GL(\cH_m)$ is surjective.
-%
-%\end{proof}
-
-%Similarly, for $V^g\in \Gr(\cH_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
-%\begin{lemma}
-%  \label{le:g equalities}
-%  For any $g\in GL_n(\CC)$, the subrepresentation $g.(P_m\otimes V)\subset g.P_{m+1}$ is equal to $g.P_m\otimes V^g\subset g.P_{m+1}$ and the subrepresentation $\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)\subset P_{m+1}$ is equal to $P_m\otimes g.V\subset P_{m+1}$.
-%\end{lemma}
-%\begin{proof}
-%  The first equality is immediate from the definitions.
-%  The second equality also follows from the definitions by observing that $\phi_{m+1,g}(P_m\otimes g.V)=g.P_m\otimes V^g$.
-%\end{proof}
-
-%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
 Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$.
@@
 
-\begin{theorem}\label{thm:truncpp}
+\begin{theorem}
+  \label{thm:truncpp}
   Fix a dimension vector $\bfe$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Fibrations of Quiver Grassmannians}
 \label{sec:fibrations}
+
 Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Combinatorial Descriptions of Non-Empty Cells}
 \label{sec:combinatorics}
-\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
+
+\noindent 
+In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
 The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition from Section~\ref{sec:fibrations}.
@@
 
-\subsection{2-Quivers}\label{sec:2quivers}
+%%%%%%%%%%%%%%%%%%%%%%
+\subsection{2-Quivers}
+\label{sec:2quivers}
 
@@
 
-%The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section~\ref{QG}.
-%These $2$-quivers are related to certain coefficient quivers of these representations.
-%The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$.
-%Hence the corresponding Euler characteristic can be computed when counting these subsets.
-%It will turn out that a feature of this description is that it does not take care of the coloring of the different arrows induced by the arrows of $K(n)$.
-
-%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
-%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
-%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.
-%\end{remark}
 In the following, we freely use the notation and conventions of Section~\ref{sec:RepK(n)}.
@@
   \draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
-  %\tikzstyle{every node}=[circle,fill=white!10]
   \node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
-  %\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
   \draw[-implies,double equal sign distance,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{};
@@
   \draw[-implies,double equal sign distance,red] (Q5)--(J11)  node[pos=.5,above,sloped] {};
-
 \end{tikzpicture}
@@
 where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_{m+1}^{[r]})_0$.
-\begin{theorem}\mbox{}
+\begin{theorem}
   \label{thm:2quivercells}
+  \mbox{}
   \begin{enumerate}
@@
 \draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
@@
 \draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
 \draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
-%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \node (Q0)[draw=black,fit={(I3) (J31) }]{};
@@
 
-%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
 \draw[-implies,double equal sign distance,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
@@
 
-The one of $\tilde P_4$ is given by:\bigskip
-
+The one of $\tilde P_4$ is given by:
+\bigskip
 \begin{tikzpicture}[scale=1]
@@
 \draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \draw (7.6,0) node (I3) {$\bullet$} +(-1,0) node (J31) {$\bullet$} +(-2,0) node (J33) {$\bullet$}; 
 \draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
-%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
-%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 \node (Q0)[draw=black,fit={(I3) (J31) }]{};
@@
 \draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
-%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
 
@@
 \draw[-implies,double equal sign distance,red] (Q3c)--(Q1) node[pos=.6,above] {};
-
-\end{tikzpicture}\bigskip
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{tikzpicture}
+\bigskip
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Compatible Pairs}
+
 For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
@@
 \begin{theorem}
+  \label{th:dyck path recursion}
   \cite[Corollary 2.4]{rupel}
-  \label{th:dyck path recursion}
   For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
@@
 \begin{definition}
+  \label{def:piecewise compatibility}
   \cite[Definition 3.11]{rupel}
-  \label{def:piecewise compatibility}
   A pair of subsets $S_H\subset H_{m+1}$ and $S_V\subset V_{m+1}$ is called \emph{piecewise compatible} if, for each $1\le r\le n$, one of the conditions \eqref{eq:hgc} or \eqref{eq:vgc} is satisfied for each pair $(h,v)\in S_H\times S_V$ with $h\in H_{m,i}$ and $v\in V_{m,i}$.
@@
 \begin{theorem}
+  \label{th:blocking edge conditions}
   \cite[Theorem 3.20 and Corollary 3.22]{rupel}
-  \label{th:blocking edge conditions}
   For $m\ge2$, suppose $S_H\subset H_{m+1}$ and $S_V\subset V_{m+1}$ are piecewise compatible. 
@@
   \begin{equation*}
-    \overline{\gamma}_\omega(e,e')=\begin{cases}
+    \overline{\gamma}_\omega(e,e')=
+    \begin{cases}
       -n & \text{if $e\in S_H$ and $e'\in S_V$;}\\ 
@@
   I.~Assem, D.~Simson, A.~Skowronski: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
+
 \bibitem{ars} 
   M.~Auslander, I.~Reiten, S.~O.~Smalo: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
+
 \bibitem{bb} 
   A.~Bia\l{}ynicki-Birula: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
+
 \bibitem{bgp} 
   I.~N.~Bernstein, I.~M.~Gelfand, V.~A.~Ponomarev: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
+
 \bibitem{brenner-butler} 
@@
 Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).
+
 \bibitem{cc} 
   P.~Caldero, F.~Chapoton: Cluster algebras as {H}all algebras of quiver representations. Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
+
 \bibitem{ck} 
   P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Annales Scientifique de l'Ecole Normale Superi\'{e}ure (4) \textbf{39} (6), 983-1009 (2006).
+
 \bibitem{ca}	J.B.~Carrell: Torus actions and cohomology.
@@
 The adjoint representation and the adjoint action, 83-158.
-Encyclopaedia Mathematical Science \textbf{131}, Invariant Theory and Algebraic
-Transformation Groups, Springer, Berlin, 2002.
+Encyclopaedia Mathematical Science \textbf{131}, Invariant Theory and Algebraic Transformation Groups, Springer, Berlin, 2002.
+
 \bibitem{ce} 
   G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory \textbf{5}(6), 777-801 (2011).
+
 \bibitem{cefr} 
   G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2018.
+
 \bibitem{cr} 
   P.~Caldero, M.~Reineke: On the quiver Grassmannian in the acyclic case. Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
-%\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
+
 \bibitem{gab} 
   P.~Gabriel: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
-%\bibitem{hr} 
- % D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}(2), 399-443 (1982).
+
 \bibitem{llz} 
   K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Mathematica \textbf{20}(1), 57-82 (2014).
+
 \bibitem{lw} 
   O.~Lorscheid, T.~Weist: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
+
 \bibitem{rin1} 
   C.~M.~Ringel. Exceptional modules are tree modules. Linear algebra and its Applications \textbf{275/276}, 471-493 (1998).
-%\bibitem{rin} 
- % C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}(3), 465-479 (1980).
-%\bibitem{mats} Matsumura, H.: Commutative ring theory. 
+
 \bibitem{rupel} 
   D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity. Preprint 2017, arXiv:1707.02696.
+
 \bibitem{sch} 
   A.~Schofield: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
+
 \bibitem{wei} 
   T.~Weist: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
-%\bibitem{wei2} 
- % T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
-%\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).
+
 \end{thebibliography}

### 2018-03-17 Grassmannian_cells.tex
small edit

--- 2018-03-17 Grassmannian_cells.tex
@@
 \end{thm}
-This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$ fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
+This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$-fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
 As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
@@
 \[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
-The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
+The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$-fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
 \begin{theorem}
@@
 We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
-Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$ fixed point sets can be calculated in an analogous manner.
+Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$-fixed point sets can be calculated in an analogous manner.
 
@@
 
-  For the reverse direction, assume $U\in X_{\bfi}$ is a $\CC^*$ fixed point represented by the matrix $M(U)$.
+  For the reverse direction, assume $U\in X_{\bfi}$ is a $\CC^*$-fixed point represented by the matrix $M(U)$.
   Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
@@
 \begin{proof}
-  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$ fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
+  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
   Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
@@
 \end{align*}
-Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.
+Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
 
@@
   There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
-  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\succeq\tbff}} \cG_{\tbff',\tbfg}\]
+  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
   is closed in $\Gr_\tbfe(B)$.
@@
   It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
-  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\geq\tbff}} \cG_{\tbff',\tbfg}\subset \Gr_\tbfe(B)\]
+  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
   for any fixed $\tbff$.
@@
   \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
-  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)=\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
+  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)\cong\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
   Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.

### 2018-03-17 Grassmannian_cells.tex
typo
Minor edits

@@
   \label{le:special subrepresentations}
-  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
+  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
   \begin{enumerate}
@@
   \label{cor:perpendicular}
-  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
+  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
   For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
@@
 By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
-Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
+Alternatively, a cell decomposition of $X$ is a collection of disjoint locally closed subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
 We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
 Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
-Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union of a subset of the affine cells for $X$.
-In this case, $U$ also has a cell decomposition given by taking exactly those affine cells which are contained in $U$.
+Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union over a subset of the affine cells for $X$.
+In this case, $U$ also has a cell decomposition given by taking exactly those affine cells for $X$ which are contained in $U$.
 
@@
 Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
-If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
+If we denote these iterated $\CC^*$-fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
 \begin{corollary}
@@
 \end{align*}
-Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
+Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
 
@@
   \label{quotient}
-  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
+  For $m\geq 2$ and a non-empty subset $I\subsetneq\{1,\ldots,n\}$.
   The following hold for any $j\in I$:
@@
   \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
-  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
+  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
   \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
@@
   But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
-  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
+  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is non-empty in this case.
 \end{proof}
@@
 In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ for truncated preprojectives $P_{m+1}^V$ are also naturally labeled by compatible pairs.
-We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_{m+1}^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
+We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_{m+1}^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the non-empty cells.
 \begin{theorem}

### 2019-05-07 Grassmannian_cells.tex
Update

@@
-\documentclass{amsart}
+\documentclass[smallextended,envcountsect,envcountsame]{svjour3}
 
 % Commands for marginal notes
-\usepackage[draft]{say}
-\newcommand{\sayD}[1]{\say[D]{#1}}
-\newcommand{\sayT}[1]{\say[T]{#1}}
 
 \usepackage{amsmath,amssymb,latexsym,color}
-\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
+\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=black]{hyperref}
 \usepackage{tikz}
@@
 \xyoption{all}
+\smartqed
 
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{question}[theorem]{Question}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{claim}[theorem]{Claim}
+%\newtheorem{conjecture}[theorem]{Conjecture}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{question}[theorem]{Question}%
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{remark}[theorem]{Remark}
+%\newtheorem{example}[theorem]{Example}
 \newtheorem{thm}{Theorem}
@@
 
-\author{Dylan Rupel}
-\address[Dylan Rupel]{University of Notre Dame, Department of Mathematics, Notre Dame, IN 46556, USA}
-\email{drupel@nd.edu}
-\author{Thorsten Weist}
-\address[Thorsten Weist]{Bergische Universit\"at Wuppertal, Gau\ss str.\ 20, 42097 Wuppertal, Germany}
-\email{weist@uni-wuppertal.de}
+\author{Dylan Rupel \and Thorsten Weist}
+\institute{Dylan Rupel \at University of Notre Dame, Department of Mathematics, Notre Dame, IN 46556, USA\\\email{drupel@nd.edu} \and Thorsten Weist \at Bergische Universit\"at Wuppertal, Gau\ss str.\ 20, 42097 Wuppertal, Germany\\\email{weist@uni-wuppertal.de}}
+
+%\email{drupel@nd.edu}
+%\author{Thorsten Weist}
+%\institute{Bergische Universit\"at Wuppertal, Gau\ss str.\ 20, 42097 Wuppertal, Germany}
+%\email{weist@uni-wuppertal.de}
 
 \begin{document}
+\setcounter{tocdepth}{2}
+
+\maketitle%\tableofcontents
+
 \begin{abstract}
@@
   The natural bijection between these two labelings gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
+	\subclass{16G20,14M15,13F60}
+	\keywords{Quiver Grassmannians, torus action, generalized Kronecker quiver, cell decompositions, combinatorial labeling of cells}
+
 \end{abstract}
 
-\setcounter{tocdepth}{2}
-
-\maketitle
-
-\tableofcontents
 %%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-\noindent A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parametrizes subrepresentations of a fixed dimension vector.
+\noindent A quiver Grassmannian is a projective variety attached to a fixed quiver representation which parame\-tri\-zes subrepresentations of a fixed dimension vector.
 In recent years, interest in quiver Grassmannians has grown considerably.
@@
   This gives both claims.
-\end{proof}
+\qed\end{proof}
 
@@
   \label{th:rigids}
-  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively satisfying $\Hom(P_m,P_r)=0$ (resp.
+  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively such that $\Hom(P_m,P_r)=0$ (resp.
 $\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0$ (resp.
@@
   Since $V$ is a proper subspace of $\cH_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
-\end{proof}
+\qed\end{proof}
 
@@
   The final claim follows from Theorem ~\ref{th:rigids} which implies $\Ext(P_m,P_{m+1})=0$.
-\end{proof}
+\qed\end{proof}
 
@@
   The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
-\end{proof}
+\qed\end{proof}
 
@@
   We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
-  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
+  \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
   But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
@@
   where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
-\end{proof}
+\qed\end{proof}
 \begin{remark}
@@
 
-For the truncated preprojective representations $P_{m+1}^V$, we have  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
+The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
 These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
@@
   This shows the last claim.
-\end{proof}
+\qed\end{proof}
 \begin{remark}
@@
   However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
-\end{proof}
+\qed\end{proof}
 
@@
   which gives the claim.
-\end{proof}
+\qed\end{proof}
 
@@
   Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-\end{proof}
+\qed\end{proof}
 
@@
   The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
-\end{proof}
+\qed\end{proof}
 
@@
 \begin{proof}
-  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
+ When applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
   Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
@@
   from which we immediately obtain the isomorphism $X\cong P_m\otimes(\cH_m/V)$.
-\end{proof}
+\qed\end{proof}
 
@@
   Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
-\end{proof}
+\qed\end{proof}
 \begin{remark}
@@
   Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
-\end{proof}
+\qed\end{proof}
 
@@
   This is clear for $m=1$ and follows in general by applying the recursion \eqref{eq:recursive covers}.
-\end{proof}
+\qed\end{proof}
 \begin{remark}
@@
   \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_j^{-1})\ar_{\alpha_j}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{j-1}}[ld]\ar^(.65){\alpha_{j+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_j^{-1}\alpha_1)&\cdots&(1,\alpha_j^{-1}\alpha_{j-1})&&(1,\alpha_j^{-1}\alpha_{j+1})&\cdots&(1,\alpha_j^{-1}\alpha_n).}\]
-
  The representation $\tilde P_4$ has support quiver
@@
   Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
-\end{proof}
+\qed\end{proof}
 
@@
   Since, following Lemma~\ref{le:lifts of transjectives}, any lift of a preprojective of $K(n)$ will be a preprojective representation of $\widetilde{K(n)}$, this gives the result.
-\end{proof}
+\qed\end{proof}
 
@@
   Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).
-\end{proof}
+\qed\end{proof}
 
@@
   The equality $\tilde P_{m+1}^I=\tau^{-1}\tilde P_{m-1}^I$ is obtained in the same way using the functor $\tilde\Sigma_1\tilde\Sigma_2=\tau^{-1}$.
-\end{proof}
+\qed\end{proof}
 
@@
   The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark~\ref{rem:reflection recursion}.(2).
-\end{proof}
+\qed\end{proof}
 
@@
   Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,i)}$ for $i\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$ and this implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,i)}\big)=0$ for $i\neq j$.
-\end{proof}
+\qed\end{proof}
 
@@
         \label{dia:truncated coherence}
-        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I'_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
+        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I'_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
         \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
@@
   The first claim of part (2) is then immediate by repeatedly applying part (1) while the final claim of part (2) is a consequence of the definition of $\delta$.
-\end{proof}
+\qed\end{proof}
 
@@
   That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
-\end{proof}
+\qed\end{proof}
 The next step is to generalize this to quiver Grassmannians.
@@
   Therefore $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and we obtain a $\CC^*$-action on $\Gr_\bfe(X)$.
-\end{proof}
+\qed\end{proof}
 
@@
   Now assuming $d(j,\chi')-d(i,\chi)=c_\alpha$, an analogous argument to the one above shows that $\chi'=\chi+e_\alpha$.
-\end{proof}
+\qed\end{proof}
 
@@
   which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
-\end{proof}
+\qed\end{proof}
 The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
@@
   so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
-\end{proof}
+\qed\end{proof}
 \begin{corollary}
@@
   But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
-\end{proof}
+\qed\end{proof}
 
@@
 \begin{lemma}\label{compatibleGSigma}
-  For $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
+  For each $g\in G$, the reflection functors $\Sigma_i:\rep K(n)\to\rep K(n)$ satisfy $g.\Sigma_i(M)=\Sigma_i(g^{-T}.M)$. 
 \end{lemma}
@@
   i.e. $g.\Sigma_2(M)=\Sigma_2(g^{-T}.M)$.
-\end{proof}
+\qed\end{proof}
 
@@
   For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
-  As reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
+  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
   \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
@@
   As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
-\end{proof}
+\qed\end{proof}
 
@@
 
-  Propositions~\ref{pro:indecomposables} and~\ref{indecomposables} imply that the quiver Grassmannians $\Gr_\bfe(M)$ for $M\in\Ind\big(K(n),\udim P_{m+1}^V\big)$ are all isomorphic for a fixed $\bfe\in\NN^{Q_0}$.
+  Propositions~\ref{pro:indecomposables} and~\ref{indecomposables} give that the quiver Grassmannians $\Gr_\bfe(M)$ for $M\in\Ind\big(K(n),\udim P_{m+1}^V\big)$ are all isomorphic for a fixed $\bfe\in\NN^{Q_0}$.
   In other words, we use that all indecomposables with this dimension vector are truncated preprojectives.
@@
   But now the same proof as for exceptional roots applies in order to show that these quiver Grassmannians need to be smooth, see \cite[Corollary 4]{cr}.
-\end{proof}
+\qed\end{proof}
 
@@
   Any refinement of this partial order to a total order $\preceq$ will give the claim.
-\end{proof}
+\qed\end{proof}
 \begin{theorem}
@@
   By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is non-empty in this case.
-\end{proof}
+\qed\end{proof}
 
@@
   The second statement follows directly from Proposition~\ref{quotient}.
-\end{proof}
+\qed\end{proof}
 
@@
   But the map $U\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
-\end{proof}
+\qed\end{proof}
 
@@
 This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
-\end{proof}
+\qed\end{proof}
 
@@
   The second part follows in the same way taking into account the initial remark.
-\end{proof}
+\qed\end{proof}
 
@@
   Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
-  Together these yield $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
+  Together these yield $\Ext(W,P_{j_{r'+1}}/U)=0$ and thus
   \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
@@
   As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition.
-\end{proof}
+\qed\end{proof}
 
@@
   To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\implies\{q\}$ for which the claim is obvious as above.
-\end{proof}
+\qed\end{proof}
 
@@
 
-The 2-quiver $\cQ_2^{[r]}$ associated to $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
-\[\begin{tikzpicture}
+The 2-quiver $\cQ_2^{[r]}$ associated to $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows as in the figure below:
+\[\begin{tikzpicture}[scale=0.98]
   \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
@@
 \[
-\begin{tikzpicture}[scale=1.35]
+\begin{tikzpicture}[scale=1.34]
   \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} +(0.1,-1.3) node {\footnotesize$\mathcal Q_3$};
@@
   \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[r]},P_m\big)}{\Ext\big(P_{m+1}^{[r+1]},P_m\big)}.\]
-  Thus a basis of $\Ext\big(P_{m+1}^{[r]},P_m\big)$ can be obtained by taking the last $r$ elements of a basis for $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
+  Thus we obtain a basis of $\Ext\big(P_{m+1}^{[r]},P_m\big)$ by taking the last $r$ elements of a basis for $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
   The choice of 2-arrows in $\cQ_{m+1}^{[r]}$ should be viewed as a combinatorial shadow of the isomorphisms above.
@@
 \[
-\begin{tikzpicture}[scale=0.97]
+\begin{tikzpicture}[scale=0.94]
 \draw (0,4) node (A1) {\footnotesize$Q_{m-1,1}$}
@@
 \node (PMK) [draw=black,fit={(Q2b) (B)}]{};
-\draw[-implies,double equal sign distance,red,thick] (PMK)--(P11b);
+\draw[-implies,double equal sign distance,red] (PMK)--(P11b);
 \end{tikzpicture}
@@
   The case of the representation $\tilde P_1$ is trivial.
-  We have $(\udim\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to $\mathcal Q_2^{[r]}$.
+  Now we have $(\udim\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to $\mathcal Q_2^{[r]}$.
   Equivalently, we have $\Gr_\tbfe(\tilde P_2^{[r]})\in\{\varnothing,\{\pt\}\}$ so that $\Gr_{\tbfe}(\tilde P_2^{[r]})=\{\pt\}$ if and only if $\tbfe\subset\cQ_2^{[r]}$ is strong successor closed.
@@
 This shows the first claim.
-\end{proof}
+\qed\end{proof}
 
@@
 
-The one of $\tilde P_4$ is given by:
-\bigskip
+The one of $\tilde P_4$ is given by:\bigskip
+
 \begin{tikzpicture}[scale=1]
@@
   For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
-\end{proof}
+\qed\end{proof}
 
@@
   But this can only occur if $H_{m,r+1,n}^{[r+1]}\subset S_H$ since $H_{m+1}^{[r+1]}\cap S_H=\varnothing$ by piecewise compatibility.
-\end{proof}
+\qed\end{proof}
 
@@
   Applying Theorem~\ref{thm:2quivercells} completes the proof.
-\end{proof}
+\qed\end{proof}
 

### 2019-05-07 Grassmannian_cells.tex
started updating section 4

@@
 \[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
+The following lemma generalizes \cite[Theorem 1]{cerulli}.
 \begin{lemma}
@@
 Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
-
+\begin{remark}
+We should always keep in mind that the middle term $B$ and the Caldero-Chapoton depend on the short exact sequence $\eta\in\Ext(N,M)$, i.e.
+to be more exact we should have named it $\Psi^{\eta}$.
+As a matter of readability we decided to omit this index.
+\end{remark}
 For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
@@
 
+\bibitem{cerulli} G.~Cerulli Irelli: Quiver Grassmannians associated with string modules. Journal of Algebraic Combinatorics \textbf{33}(2), 259-276 (2011).
+
 \bibitem{cefr} 

### 2019-05-08 Grassmannian_cells.tex
Committing to pull

--- 2018-03-17 Grassmannian_cells.tex
@@
 
-\title{Cell Decompositions for Rank Two Quiver Grassmannians}
+\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}
 
@@
 \draw[-implies,double equal sign distance,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
-\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {´};
+\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {'};
 \end{tikzpicture}

### 2019-05-08 response to reviewer.tex

\documentclass[titlepage,11pt,a4paper]{{scrartcl}}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[arrow,matrix,curve]{xy}
\usepackage[latin1]{inputenc}
\usepackage{theorem}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{a4paper,top=3cm, bottom=3cm} 
\newtheorem{satz}{Theorem}
\newtheorem{aufg}[satz]{Aufgabe}
\newtheorem{defi}[satz]{Definition}
\newtheorem{bem}[satz]{Remark}
\newtheorem{kor}[satz]{Corollary}
\newtheorem{lem}[satz]{Lemma}
\newtheorem{ver}[satz]{Conjecture}
\newtheorem{zit}[satz]{Zitat}
\newtheorem{beo}[satz]{Beobachtung}
\newtheorem{bei}[satz]{Example}
\newtheorem{pro}[satz]{Proposition}
\newcommand{\dju}{\bigcup\hspace{-2.23mm\dot}\hspace{2mm}}
\newcommand{\modu}{~\rm{mod}~}
\newcommand{\smdju}{\cup\hspace{-2.15mm\dot}\hspace{2mm}}
\newcommand\dis[1]{\bigcup_{#1}\hspace{-2.5mm\dot}\hspace{2mm}}
\newcommand{\qed}{\begin{flushright}$\square$\end{flushright}}
\newcommand\R{$\mathbb{R}$}
\newcommand\Q{$\mathbb{Q}$}
\newcommand\Z{$\mathbb{Z}$}
\newcommand\N{$\mathbb{N}$}
\newcommand\C{$\mathbb{C}$}
\newcommand\Rn{\mathbb{R}}
\newcommand\Qn{\mathbb{Q}}
\newcommand\Zn{\mathbb{Z}}
\newcommand\Nn{\mathbb{N}}
\newcommand\Cn{\mathbb{C}}
\newcommand\Sk{\langle\,\,,\,\rangle}
\newcommand{\Hom}{\mathrm{Hom}}

\newcommand{\filt}[6]{
\[
\begin{xy}
\xymatrix@R20pt@C20pt{
&\mathbb{C}^3&\\\langle #1,#2 \rangle\ar[ru]&\langle #3,#4\rangle\ar[u]&\langle #5,#6\rangle\ar[lu]\\\langle #1\rangle\ar[u]&\langle #3\rangle\ar[u]&\langle #5\rangle\ar[u]}
\end{xy}
\]
} 
\begin{document}
\pagestyle{empty}

\noindent{\bf Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}\\

\noindent In the following, we point out the changes we made.

Section 4:
\begin{enumerate}
\renewcommand{\labelenumi}{(\arabic{enumi})}
\item This should be a matter of definition and by reindexing appropriately we should get the version with $\ast$'s on the right.
\item We refer to Cerulli Irelli's paper now. But not that the assumptions in Theorem 1 are stronger than ours as we do not assume that every basis element is mapped on a scalar multiple of another basis element. Note also that the number of fixed points is finite in Cerulli Irelli's case which is not true in general.
\item Then I think that Haupt's result is also not as general as ours, but I need to check this.
\item We inserted a remark which addresses this issue.
\item Theorems 4.20, 4.21 are to be updated.
\item Corollary 4.23: shorten the proof in the middle, the argument stays the same.
\end{enumerate}

\end{document}

### 2019-05-08 response to reviewer.tex
added Remark 4.6

@@
 Note also that the number of fixed points is finite in Cerulli Irelli's case which is not true in general.
-\item Then I think that Haupt's result is also not as general as ours, but I need to check this.
+\item We inserted a remark concerning the result of Haupt.
+Our approach seems to simplify the language and generalize the techniques of Haupt.
+If we are not mistaken, the proof of Theorem 1.2(c) in Section 8 only deals with those representations of the universal (abelian) covering whose dimension vectors only consists of $0$'s and $1$'s.
+We actually consider arbitrary representations of $\hat Q$.
+Moreover, the explicit description of the fixed points of $\mathrm{Gr}_{\mathbf{e}}(M)$ of a liftable representation $M$ as subrepresentations of the lifted representations $\hat M$ seems to be missing.
+
 \item We inserted a remark which addresses this issue.

### 2019-05-08 Grassmannian_cells.tex
added Remark 4.6

--- 2019-05-07 Grassmannian_cells.tex
@@
 \qed\end{proof}
+\begin{remark} Note that similar techniques and results are obtained in \cite{haupt}, see e.g.
+\cite[Theorem 1.2(c)]{haupt}.
+Note that only representations $\hat X$ of $\hat Q$ are considered in the corresponding proof in \cite[Section 8]{haupt} which satisfy $\dim \hat X_{(i,\chi)}\in\{0,1\}$.
+Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result.
+\end{remark}
+
 The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
@@
 
+\bibitem{haupt} N.~Haupt: Euler Characteristics of Quiver Grassmannians and Ringel-Hall Algebras of String Algebras. Algebras and Representation Theory \text{15}, 755-793 (2012).
+
 \bibitem{llz} 

### 2019-05-10 Grassmannian_cells.tex
Theorem 4.22 (former 4.20) update
Added a remark after the claim

@@
   \label{cellscover}
-  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition.
+  For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
+In particular, every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
 \end{theorem}
 \begin{proof}
+
 	We work by induction on $m$.
@@
   \vs
+Note that having proved the claim, for $|J|\leq n-2$ the statement itself is obtained when setting $\bfI=(J\cup\{i\})$ for any $i\in\{1,\ldots,n\}\backslash\{J\}$.
+For $|J|=n-1$, we can apply Lemma~\ref{le:truncated quotients}, i.e.
+$P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ with $J^c=\{j\}$, together with the fact that $\tilde P_{m,j}^{\{j\}}$ is obtained when translating $\tilde P_{m}^{\{j\}}$ in the universal covering quiver.
+Clearly, translation does not affect quiver Grassmannians when also translating dimension vectors $\tbfe$, i.e.
+quiver Grassmannians of $\tilde P_{m,j}^{\{j\}}$ are just the same as those of $\tilde P_{m}^{\{j\}}$.
+
+Finally, recall that the preprojective representations $\tilde P_{m+1}$ and their quiver Grassmannians are obtained when setting $J=\varnothing$ and considering any short exact sequence
+		$$\ses{\tilde P_{m,j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\{j\}}}$$
+for $j\in\{1,\ldots,n\}$. Then we can use the fact that $\tilde P_{m,j}$ is the translation of $\tilde P_m$.
 

### 2019-05-11 response to reviewer.tex
further updates

@@
 \renewcommand{\labelenumi}{(\arabic{enumi})}
+\item Note that the proof and the examples before show how to compute the kernel of the right hand vertical map for $m=2$ and $m=3$.
+As it is indeed not obvious to prove surjectivity for general $m$ directly, we deduce it from the $m=2,3$-cases and apply $\tau^{-1}$-shifts which preserve exact sequences if no direct summand is injective.
+This is mentioned in Remark 3.2 to which we refer to in the proof of Lemma 3.30.
+\item We omit the notation $~\perp$ as it is only used in Corollary 3.32.
 \item This should be a matter of definition and by reindexing appropriately we should get the version with $\ast$'s on the right.
@@
 \item We inserted a remark which addresses this issue.
-\item Theorems 4.20, 4.21 are to be updated.
-\item Corollary 4.23: shorten the proof in the middle, the argument stays the same.
+\item We inserted a remark in Theorem 4.22 (former 4.20) which is meant to explain how the statement is obtained from the claim. Moreover, it should make the proof clearer.
+\item I find the strategy if 4.23 is very clear and I also think that the proof of 4.24 is very close to the suggestion of the referee. Any ideas what to change?
 \end{enumerate}

### 2019-05-11 Grassmannian_cells.tex
further updates

@@
   Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
-  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
+  For $m\geq 2$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_m(I,j))=\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$.
 \end{corollary}
@@
   \vs
+
+\begin{remark}
 Note that having proved the claim, for $|J|\leq n-2$ the statement itself is obtained when setting $\bfI=(J\cup\{i\})$ for any $i\in\{1,\ldots,n\}\backslash\{J\}$.
@@
 
-Finally, recall that the preprojective representations $\tilde P_{m+1}$ and their quiver Grassmannians are obtained when setting $J=\varnothing$ and considering any short exact sequence
+Furthermore, recall that the preprojective representations $\tilde P_{m+1}$ and their quiver Grassmannians are obtained when setting $J=\varnothing$ and considering any short exact sequence
 		$$\ses{\tilde P_{m,j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\{j\}}}$$
 for $j\in\{1,\ldots,n\}$. Then we can use the fact that $\tilde P_{m,j}$ is the translation of $\tilde P_m$.
+
+Finally, note that the claim together with Proposition \ref{label} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant.
+Thus Theorem \ref{vb} gives the statement of the Theorem.
+\end{remark}
 

### 2019-05-15 Grassmannian_cells.tex
Minor intro edits

@@
   Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established.
-  We also provide two natural combinatorial labelings for these cells.
-  On the one hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
+
+  We provide two combinatorial labelings for these cells.
+  On the one hand, they are naturally labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
   On the other hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
-  The natural bijection between these two labelings gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
+  The provided bijection between these two labelings gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
 	\subclass{16G20,14M15,13F60}
-	\keywords{Quiver Grassmannians, torus action, generalized Kronecker quiver, cell decompositions, combinatorial labeling of cells}
+        \keywords{Quiver Grassmannians, torus action, generalized Kronecker quiver, cell decompositions, combinatorial labeling of cells, Dyck path combinatorics}
 
@@
 Another method uses short exact sequences of quiver representations to induce maps between quiver Grassmannians.
-More precisely, the quiver Grassmannian of the middle term maps to the product of the quiver Grassmannians for the two outer terms via the ``Caldero-Chapoton map'' which first appeared in \cite{cc}. 
+More precisely, the quiver Grassmannian of the middle term maps to a disjoint union of products of the quiver Grassmannians for the two outer terms via the ``Caldero-Chapoton map'' which first appeared in \cite{cc}.
 If the short exact sequence has certain properties -- e.g.
@@
 
-As a first step, we show that a $\CC^*$-action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
+As a first step, we show that a $\CC^*$-action with proper fixed point subset can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
 These are precisely those cases where the universal covering quiver differs from the original quiver.
@@
 \begin{thm}
-  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the affine cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
+  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, there is an associated $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the affine cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
   In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.

### 2019-05-16 Grassmannian_cells.tex
Minor Section 2 edits

@@
 
-\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}
+%\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}
 
@@
 \begin{document}
-\setcounter{tocdepth}{2}
-
-\maketitle%\tableofcontents
+%\setcounter{tocdepth}{2}
+
+%\maketitle%\tableofcontents
 
@@
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
-We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$ and we assume in the following that all representations are finite-dimensional.
+We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$, and we assume in the following that all representations are finite-dimensional.
 

### 2019-05-23 Grassmannian_cells.tex
Section 3 edits

@@
 In Section~\ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which are needed later to investigate the quiver Grassmannians attached to preprojective representations.
-We first focus on preprojective and preinjective representations, written as $P_m$ and $I_m$, which enables us to investigate a special class of indecomposable representations in Section~\ref{sec:truncated preprojectives} -- we call them truncated preprojective representations.
+Our primary focus is on a special class of indecomposable representations which we call truncated preprojective representations.
 We prove that every preprojective representation admits a filtration by preprojectives of smaller dimensions such that all quotients appearing are actually truncated preprojective representations.
@@
 A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
+The dimension vector of $X$ is $\udim X:=(\dim X_i)_{i\in Q_0}\in\NN^{Q_0}$.
 Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
@@
 We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
-Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep_{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
-In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep_{\langle i\rangle} K(n)\to\rep_{\langle i\rangle} K(n)^{op}$.
+Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep^{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
+In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep^{\langle i\rangle} K(n)\to\rep^{\langle i\rangle} K(n)^{op}$.
 Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.
@@
 Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
+Observe by an easy induction that $u_{k+1}-u_k>0$ for $k\ge0$ since $n\ge3$.
+
 The following is well-known.
@@
   \label{th:rigids}
-  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively such that $\Hom(P_m,P_r)=0$ (resp.
-$\Hom(I_r,I_m)=0$) and $\Ext(P_r,P_m)=0$ (resp.
-$\Ext(I_m,I_r)=0$) for $1\leq r\leq m$.
+  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
+  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim I_m=(u_{m-1},u_m).\]
+  These satisfy 
+  \[\Hom(P_m,P_r)=0, \qquad \Hom(I_r,I_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(I_m,I_r)=0\]
+  for $1\leq r\leq m$.
   Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
-
 \end{theorem}
+
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
@@
   Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
+  Using this, we have the following:
   \begin{enumerate}
@@
       In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
-    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
+    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
   \end{enumerate}
@@
 \begin{proof}
-  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
-  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes \cH_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
-  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
-  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker(ev_V)=0$ for $m=1$ and thus $ev_V$ is injective in this case.
-
-  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
-  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes \cH_1/V$.
-  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
-  \[\xymatrix{0 \ar[r]  & P_1\otimes \cH_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes \cH_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
-
-  We need to show that $K$ has no preinjective direct summand.
-  As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
-  But this already shows that $K$ is indecomposable as $\udim K=(\dim \cH_1/V,1)$.
-  Since $V$ is a proper subspace of $\cH_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
-\qed\end{proof}
-
-In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Truncated Preprojectives}
-\label{sec:truncated preprojectives}
-
-Motivated by Lemma~\ref{le:injective evaluation maps}, we define the following.
+  The map $ev_V$ is irreducible and is thus either injective or surjective.
+  But as observed above, we have $r\cdot\udim P_m<\udim P_{m+1}$ for $1\le r<n$ and so $ev_V$ cannot be surjective.
+\qed\end{proof}
+
+% As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
+% \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes \cH_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
+% in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
+% Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker(ev_V)=0$ for $m=1$ and thus $ev_V$ is injective in this case.
+% 
+% In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
+% Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes \cH_1/V$.
+% Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
+% \[\xymatrix{0 \ar[r]  & P_1\otimes \cH_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes \cH_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]
+
+% We need to show that $K$ has no preinjective direct summand.
+% As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
+% But this already shows that $K$ is indecomposable as $\udim K=(\dim \cH_1/V,1)$.
+% Since $V$ is a proper subspace of $\cH_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
+%\qed\end{proof}
+
 \begin{definition}
@@
 \begin{proof}
-  As $P_m$ is exceptional, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
+  As $P_m$ is rigid, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
   \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
@@
   \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
-  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
-  The final claim follows from Theorem ~\ref{th:rigids} which implies $\Ext(P_m,P_{m+1})=0$.
+  There is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ giving the first claim.
+  The second claim follows from the vanishing of $\Ext(P_m,P_{m+1})$ (c.f.~Theorem~\ref{th:rigids}).
 \qed\end{proof}
@@
 \begin{proof}
-  We proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
-
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-\qed\end{proof}
+  Since $ev_V$ is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows.
+\qed\end{proof}
+% We proceed by induction on $m$.
+% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
+% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
+
+% For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+% Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
+%\qed\end{proof}
 

### 2019-05-25 Grassmannian_cells.tex
Section 3 edits

@@
 
+\subsection{Truncated Preprojectives}
+
 \begin{definition}
@@
   \begin{enumerate}
-    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
-    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
+    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$ and this morphism is unique (up to scalars) when it exists.
+    \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
   \end{enumerate}
@@
   \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
-  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$.
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (and hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
+  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subseteq V$.
   In this case, there are isomorphisms
@@
 \begin{proof}
-  Since $ev_V$ is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows.
+  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows.
 \qed\end{proof}
@@
   We write $\bar{V}\subset \cH_{m-1}$ for the subspace corresponding to $V\subset \cH_m$ under this identification.
-  Under the isomorphism of $\cH_{m-1}$ with $\cH_m^*$, we have $\bar{V}=(\cH_m/V)^*$.
+  Under the isomorphism of $\cH_m^*$ with $\cH_{m-1}$, we have $\bar{V}=(\cH_m/V)^*$.
 \end{remark}

### 2019-05-27 Grassmannian_cells.tex
Section 3 edits

@@
 
+\newcommand{\bfd}{\mathbf{d}}
 \newcommand{\bfe}{\mathbf{e}}
@@
 The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
+The following homological organization is well-known.
+\begin{lemma}
+  \label{le:preprojective subs}
+  If $\Hom(X,P_m)\ne0$ (resp.
+$\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp.
+$1\le r\le m-2$).
+\end{lemma}
 \begin{remark}
@@
 \begin{remark}
-  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
+  It will be convenient to also set $P_{m+1}^0=P_{m+1}$ as this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
 \end{remark}
 
-We collect below several basic homological results related to preprojective representations.
+We collect below several basic homological results related to truncated preprojective representations.
 \begin{lemma}
@@
   \begin{enumerate}
-    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$ and this morphism is unique (up to scalars) when it exists.
+    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$, and this morphism is unique (up to scalars) when it exists.
     \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
+      Otherwise, $\Ext(P_{m+1}^W,P_{m+1}^V)$ is naturally isomorphic to the quotient of $W^*\otimes (\cH_m/V)$ by the line corresponding to the standard counit $\CC\to W^*\otimes W$, this line degenerates to a point in the case $W\subseteq V$.
   \end{enumerate}
@@
   \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
-  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (and hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
-  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subseteq V$.
-  In this case, there are isomorphisms
+  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, therefore $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
+  A routine chase using the following pullback diagram confirms the latter holds if and only if $W\subseteq V$.
+  \[\xymatrix{
+      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] \\
+      0 \ar[r] & K \ar[r] \ar[d] \ar@{}[dr]|(.7){\lrcorner} & P_m\otimes W \ar[d]^{ev_W} \ar[r] & C \ar[r] \ar[d] & 0\\
+    0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_V} & P_{m+1}^V \ar[r] & 0}\]
+
+  In case $W\subseteq V$, there are isomorphisms
   \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes \cH_m/V,\]
   where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
+  Otherwise, we must quotient $\Hom(P_m\otimes W,P_{m+1}^V)$ by the image of $-\circ ev_W$.
+  This line can be described as above since that gives $ev_W$ under the isomorphism $W^*\otimes\cH_m\cong\Hom(P_m\otimes W,P_{m+1})$.
 \qed\end{proof}
@@
 
-The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
+The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
 These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
-For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write 
-\[R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
-for the affine space of representations of $K(n)$ with dimension vector $d$. 
+For a dimension vector $\bfd=(d_1,d_2)\in\NN^{K(n)_0}$, write 
+\[R_\bfd(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
+for the affine space of representations of $K(n)$ with dimension vector $\bfd$. 
 \begin{proposition}
@@
   \begin{enumerate}
-    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
-    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
-    \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
+    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
+    \item The indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
+    \item The set of indecomposable representations with dimension vector $\bfd(m,r)$ is given by a non-empty open subset of $R_{\bfd(m,r)}(K(n))$. 
   \end{enumerate}
@@
 \begin{proof}
-  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
-  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
-  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
-  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
-  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.
-
-  This shows that the indecomposable representations in $R_{(l,1)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
-  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$l$ spanned by the row vectors of the corresponding matrix $M_X$.
-  Now it is straightforward to check that the $\GL_{d(m,r)}=\GL_l(\CC)\times\CC^\ast$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\GL_l(\CC)$ on the set of these subspaces.
+  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(\bfd(m,r))^\sigma=\bfd(m+1,r)$, it suffices to prove the first statement for $m=1$.
+  Then we have $\bfd(m,r)=(\ell,1)$ for $\ell:=n-r$.
+  This means that $X\in R_{\bfd(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{\ell\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
+  Now $X$ is indecomposable if and only if $\rk(M_X)=\ell$.
+  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=\ell-k$.
+
+  This shows that the indecomposable representations in $R_{(\ell,1)}(K(n))$ are in one-to-one correspondence with $\ell\times n$ matrices of maximal rank.
+  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$\ell$ spanned by the row vectors of the corresponding matrix $M_X$.
+  Now it is straightforward to check that the $\GL_{\bfd(m,r)}=\GL_\ell(\CC)\times\CC^\ast$-action on $R_{\bfd(m,r)}(K(n))$ corresponds to the base change action of $\GL_\ell(\CC)$ on the set of these subspaces.
   This shows the first statement.
@@
   By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
-  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives with dimension vector $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.
-
-  As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
-  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
+  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives with dimension vector $\bfd(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.
+
+  As there exist representations with trivial endomorphism ring, the dimension vectors $\bfd(m,r)$ are Schur roots.
+  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{\bfd(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
   This shows the last claim.
@@
   There is a more elegant way to prove the first part of Proposition~\ref{pro:indecomposables} using the notion of stability and moduli spaces.
-  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
+  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(\bfd)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_\ell(\CC^n)$.
   We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
@@
 \begin{proof}
-  Recall that $\Hom(X,P_\ell)\ne0$ (resp.
-$\Ext(P_\ell,X)\ne0$) for some indecomposable representation $X$ and some $\ell\ge1$ implies that $X$ is preprojective of the form $P_r$ with $1\le r\le\ell$ (resp.
-$1\le r\le\ell-2$).
-  However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+   The representation $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
+   The claim then follows from Lemma~\ref{le:preprojective subs}.
 \qed\end{proof}
@@
 \begin{proof}
-  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows.
+  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
 \qed\end{proof}
@@
   must split.
-  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
+  The claim for an arbitrary subrepresentation $Z\subseteq P_m\otimes(V/W)$ is an immediate consequence of this splitting.
 \qed\end{proof}
@@
   But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
-  Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
+  Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$, must be injective and hence an isomorphism.
 \qed\end{proof}
@@
 
-Fix a natural number $n\geq 3$.
 Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.

### 2019-05-28 Grassmannian_cells.tex
Cleamed up Lemma 3.31 (formerly 3.30) following referees comments

@@
 
-It will be rather important that our chosen lifts of $P_{2l}$ for $l\ge1$ and our chosen lifts of $P_{2l-1}$ for $l\ge1$ live on two different components of the universal covering quiver.
+It will be rather important that our chosen lifts of $P_{2\ell}$ for $\ell\ge1$ and our chosen lifts of $P_{2\ell-1}$ for $\ell\ge1$ live on two different components of the universal covering quiver.
 Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
-To simplify the notation, we abbreviate $\tilde P_{2l-1,j}:=\tilde P_{2l-1,\alpha_j}$ and $\tilde P_{2l,j}:=\tilde P_{2l,\alpha_j^{-1}}$.
+To simplify the notation, we abbreviate $\tilde P_{2\ell-1,j}:=\tilde P_{2\ell-1,\alpha_j}$ and $\tilde P_{2\ell,j}:=\tilde P_{2\ell,\alpha_j^{-1}}$.
 \begin{lemma}
@@
 
-The next result establishes some basic homological properties of the translated preprojective representations.
+The next result establishes some basic homological properties of these translated preprojective representations.
 \begin{lemma}
@@
         \label{ses1}
-        \sesm{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}{\pi_{m+1}^I}.
+        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
       \end{equation}
@@
       Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
-      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
+      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\] 
+      is generated by the non-split sequence
+      \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
     \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subset I$, in which case
@@
 \[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]
-Depending on context (in particular, the parity of $m+1$), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
+Depending on context (in particular, the parity of $m$), we will either identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ when $m$ is even or with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$ when $m$ is odd.
+
 In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
-More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
+More precisely, we obtain from Lemma~\ref{le:shifted subreps} a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
 \[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
-Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.
+Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(\ell)}$ for $1\le \ell<k$, these will not be naturally equipped with a canonical inclusion into $\tilde P_{m+1}$.
 
@@
         \begin{cases}
-          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
-          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
+          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{m-1,(j,k)}\oplus \bigoplus_{i\in I\setminus\{j\}j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
+          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{1,(j,k)} & \text{ if $m=2$.}
         \end{cases}\]
@@
   \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]
-  We establish the final claim of part (1) directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
+
+  We establish the final claim of part (1) directly for $m=2$.
   Using the description in Example~\ref{ex:truncated lifts}, it is not hard to see that $\tau\tilde P_3^I$ is indecomposable with one-dimensional spaces at only the vertices $(1,e)$ and $(2,\alpha_i^{-1})$ for $i\in I$.
@@
 
-  For the $m=3$ case, we note that $\tau\tilde P_4^I=\tilde P_2^I$ by Lemma~\ref{le:truncated tau}.
-  Then the claimed structure $\tilde P_3(I,j)$ of the kernel and the surjectivity of the map $\tilde P_{3,j}\to\tau\tilde P_4^I$ are immediate from the explicit descriptions of $\tilde P_{3,j}$ and $\tilde P_2^I$ in Example~\ref{ex:lifted preprojectives} and Example~\ref{ex:truncated lifts} respectively.
-  The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark~\ref{rem:reflection recursion}.(2).
+  For the $m\ge3$ case, we apply Lemma~\ref{le:properties} to get the lower sequence in the following commutative diagram
+  \[
+    \xymatrix{
+    0 \ar[r] & \tilde P_{m-2,j} \ar@{=}[d] \ar[r] & \bigoplus_{k=1}^n \tilde P_{m-1,(j,k)} \ar[d]^\eta \ar[r] & \tilde P_{m,j} \ar[d] \ar[r] & 0\\
+    0 \ar[r] & \tilde P_{m-2,j} \ar[r] & \tilde P_{m-1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m-1}^I \ar[r] & 0}
+  \]
+  which exists because the upper sequence is almost split.
+
+  Since the evaluation map $ev_I$ in equation~\eqref{ses1} is irreducible, any nontrivial map to $\tilde P_{m-1}^{I\setminus\{j\}}$ must factor through $\tilde P_{m-1}$.
+  It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\in I\setminus\{j\}$.
+  Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} P_{m-2,(j,j,i)}$, and so $\ker\eta=P_m(I,j)$.
+  Since $\eta$ and the right hand vertical morphism have the same kernel, this completes the proof of (1).
+
+  This also shows that the vertical map $\eta$ is surjective, and thus the map $\tilde P_{m,j}\to \tilde P_{m-1}^I\cong \tilde P_{m+1}^I$ is surjective.
+  This establishes part (2).
+% Then the claimed structure $\tilde P_3(I,j)$ of the kernel and the surjectivity of the map $\tilde P_{3,j}\to\tau\tilde P_4^I$ are immediate from the explicit descriptions of $\tilde P_{3,j}$ and $\tilde P_2^I$ in Example~\ref{ex:lifted preprojectives} and Example~\ref{ex:truncated lifts} respectively.
+% The general cases for parts (1) and (2) both then follow using the reflection recursions \eqref{eq:recursive covers} taking into account Remark~\ref{rem:reflection recursion}.(2).
 \qed\end{proof}

### 2019-06-05 Grassmannian_cells.tex
Section 3 edits and reorganization

@@
   For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
-  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim I_m=(u_{m-1},u_m).\]
+  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim Q_m=(u_{m-1},u_m).\]
   These satisfy 
-  \[\Hom(P_m,P_r)=0, \qquad \Hom(I_r,I_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(I_m,I_r)=0\]
+  \[\Hom(P_m,P_r)=0, \qquad \Hom(Q_r,Q_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(Q_m,Q_r)=0\]
   for $1\leq r\leq m$.
-  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
+  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $Q_m^{a_1}\oplus Q_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
 \end{theorem}
 
-The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
+The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $Q_m$ are called \emph{preinjective}.
 The following homological organization is well-known.
@@
     \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
-      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
+      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 I_{m-1}\]
       for $m\ge2$.
-      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
+      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $Q_{m+1}=\tau Q_{m-1}$ for $m\ge2$.
     \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
@@
 Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
-One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
+Another main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
 
@@
 Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
-The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
+The preprojective lifts we use are defined by the following analogue of the recursion of Remark~\ref{rem:reflection recursion}.
 \begin{itemize}
@@
 It will be rather important that our chosen lifts of $P_{2\ell}$ for $\ell\ge1$ and our chosen lifts of $P_{2\ell-1}$ for $\ell\ge1$ live on two different components of the universal covering quiver.
-Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
+Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via left translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
 Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
-To simplify the notation, we abbreviate $\tilde P_{2\ell-1,j}:=\tilde P_{2\ell-1,\alpha_j}$ and $\tilde P_{2\ell,j}:=\tilde P_{2\ell,\alpha_j^{-1}}$.
+\begin{remark}
+  \label{rem:abbreviations}
+  To simplify the notation, we abbreviate $\tilde P_{2\ell-1,i}:=\tilde P_{2\ell-1,\alpha_i}$ and $\tilde P_{2\ell,i}:=\tilde P_{2\ell,\alpha_i^{-1}}$ for $\ell\ge1$ and $i\in\{1,\ldots,n\}$.
+\end{remark}
 \begin{lemma}
@@
   Then $\tilde P_{1,j}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_j)$.
-  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink.
+  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink $(1,\alpha_i)$.
 
@@
 
-The next result establishes some basic homological properties of these translated preprojective representations.
+The next result establishes some basic homological properties of these translates of preprojective representations.
 \begin{lemma}
@@
 
-  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
+  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
   The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
@@
       \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
-    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subset I$, in which case
+    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subseteq I$, in which case
       \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
       In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
+    \item For each proper subset $J\subsetneq I$, there is an exact sequence 
+      \begin{equation*}
+        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{J,I}} & \tilde P_{m+1}^I \ar[r] & 0}.
+      \end{equation*}
+      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
   \end{enumerate}
@@
   \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
-  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
-  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.(3).
+  where the final zero follows from Lemma~\ref{le:homdecomposition}.2.
+  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.3.
   Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).
@@
   For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
-  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
-  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
-  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
+  Then taking into account Lemma~\ref{le:homdecomposition}.3, we get the isomorphism
+  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}),\] 
+  and Lemma~\ref{le:homdecomposition}.2 gives the final claim of part (3).
 
   Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).
+
+  The exactness in the first half of (5) follows from a routine chase through the following commutative diagram:
+  \begin{equation*}
+    \xymatrix{ 
+      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] & \\
+      0 \ar[r] & \bigoplus_{i\in J} \tilde P_{m,i} \ar@{=}[r] \ar[d] & \bigoplus_{i\in J} \tilde P_{m,i} \ar[r] \ar[d] & 0 \ar[r] \ar[d] & 0\\
+      0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r] \ar[d] & \tilde P_{m+1} \ar[r] \ar[d] & \tilde P_{m+1}^I \ar[r] \ar@{=}[d] & 0\\
+      0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] \ar[d] & \tilde P^J_{m+1} \ar[r] \ar[d] & \tilde P_{m+1}^I \ar[r] \ar[d] & 0 \\
+      & 0 & 0 & 0 &
+    }
+  \end{equation*}
+  This and a similar diagram give the equalities at the end of (5).
 \qed\end{proof}
@@
   Building on Example~\ref{ex:lifted preprojectives}, we describe here the truncated preprojectives $\tilde P_m^I$ for $m=2,3,4$.
-  Following Lemma~\ref{le:properties}.(4), we can do this by simply specifying their dimension vectors as we did above.
+  Following Lemma~\ref{le:properties}.4, we can do this by simply specifying their dimension vectors as we did above.
 
@@
 
-We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
-Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
-For $k\ge1$, set
-\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]
-Depending on context (in particular, the parity of $m$), we will either identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ when $m$ is even or with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$ when $m$ is odd.
-
-In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
+We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations $\tilde P_{m+1}$.
+To each word $\ui=(i_1,\ldots,i_k)$, with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
 More precisely, we obtain from Lemma~\ref{le:shifted subreps} a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
 \[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
-Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(\ell)}$ for $1\le \ell<k$, these will not be naturally equipped with a canonical inclusion into $\tilde P_{m+1}$.
-
-To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
+\begin{remark}
+  Following Remark~\ref{rem:abbreviations}, we will either identify a word~$\ui=(i_1,\ldots,i_k)$ with the element 
+  \[\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n\]
+  when $m$ is even or with the element 
+  \[\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n\]
+  when $m$ is odd.
+  In this way, a subscript $\ui$ on a representation or morphism will denote the corresponding shift inside $\rep\widetilde{K(n)}$.
+\end{remark}
+
+Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui$, these in general will not be naturally equipped with a canonical inclusion into $\tilde P_{m+1}$.
+To emphasize this point, consider a word $\ui$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
 Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
-Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
+%Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
+
+To avoid such ambiguities, we introduce the set
+\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
+and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
+The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
+For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
+\begin{lemma}
+  \label{le:truncated quotients}
+  For $m\ge3$, the following hold:
+  \begin{enumerate}
+    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
+      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
+    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$, there is a commutative diagram
+      \begin{equation}
+        \label{dia:truncated coherence}
+        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.35){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.35){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
+        \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
+      \end{equation}
+    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,I}:\tilde P_{m+1}\to \tilde P_{m+1-k,\ui}^I$ satisfying:
+      \[\tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
+      \qquad\text{and}\qquad
+    \tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
+      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
+  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
+    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
+    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
+    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
+  & & 0& 0&}\]
+  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.
+
+  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from the definitions of these maps.
+
+  These diagrams stitch together to give the composition 
+  \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
+  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
+\qed\end{proof}
+
+The next technical results illustrate the need to lift to the universal covering quiver $\widetilde K(n)$.
 \begin{lemma}
@@
         \begin{cases}
-          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{m-1,(j,k)}\oplus \bigoplus_{i\in I\setminus\{j\}j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
+          \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{m-1,(j,k)}\oplus \bigoplus_{i\in I\setminus\{j\}}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
           \bigoplus_{\substack{1\leq k\leq n\\k\neq j}}\tilde P_{1,(j,k)} & \text{ if $m=2$.}
@@
 \begin{proof}
-  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
+  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.3.
   Indeed, this gives
@@
 
-  For the $m\ge3$ case, we apply Lemma~\ref{le:properties} to get the lower sequence in the following commutative diagram
+  For the $m\ge3$ case, we apply Lemma~\ref{le:properties} to get the lower sequence in the following commutative diagram, which exists because the upper sequence is almost split:
   \[
@@
   \]
-  which exists because the upper sequence is almost split.
 
   Since the evaluation map $ev_I$ in equation~\eqref{ses1} is irreducible, any nontrivial map to $\tilde P_{m-1}^{I\setminus\{j\}}$ must factor through $\tilde P_{m-1}$.
-  It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\in I\setminus\{j\}$.
+  It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\ne j$.
   Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} P_{m-2,(j,j,i)}$, and so $\ker\eta=P_m(I,j)$.
@@
 
-  This also shows that the vertical map $\eta$ is surjective, and thus the map $\tilde P_{m,j}\to \tilde P_{m-1}^I\cong \tilde P_{m+1}^I$ is surjective.
+  This also shows that the vertical map $\eta$ is surjective, and thus the map $\tilde P_{m,j}\to \tilde P_{m-1}^I\cong \tau\tilde P_{m+1}^I$ is surjective.
   This establishes part (2).
@@
 The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
+Given $\tilde M\in\rep \tilde K(n)$, write
+\[\tilde M^\perp := \{\tilde N\in\rep \tilde K(n):\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
 \begin{corollary}
@@
   Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
-  For $m\geq 2$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_m(I,j))=\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$.
+  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
 \end{corollary}
 \begin{proof}
+  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of the simple projective representations $\tilde P_{1,(j,k)}$ for $k\ne j$.
+  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,k)}$ for $k\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$, which implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,k)}\big)=0$ for $k\neq j$ and thus $\Ext\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$.
+
   If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
   \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
-  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
-  From Lemma~\ref{le:properties}.(3) again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
-  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.(4), we get
+  Following Lemma~\ref{le:properties}.3, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
+  From Lemma~\ref{le:properties}.3 again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
+  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.4, we get
   \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
   It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
-  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.(4) again imply 
+  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.4 again imply 
   \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
   Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
-
-  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of simple projective representations.
-  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,i)}$ for $i\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$ and this implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,i)}\big)=0$ for $i\neq j$.
-\qed\end{proof}
-
-The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
-\begin{definition}
-  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
-  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge0$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
-  \begin{enumerate}
-    \item if $k\ge1$, then $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
-    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=I_{l+1}\cup (I'_l)^c$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
-  \end{enumerate}
-  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $(I'_k)^c$.
-  Given an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k\ge1$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$.
-\end{definition}
-
-In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-That is, taking $\varepsilon=(-1)^{m+1}$ we have an exact sequence
-\[\ses{\bigoplus_{i\in I} \tilde P_{m,w\alpha_i^\varepsilon}}{\tilde P_{m+1,w}}{\tilde P_{m+1,w}^I}.\]
-These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
-We adopt similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
-
-By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
-\begin{equation}
-  \label{eq:truncted sequence}
-  \sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.
-\end{equation}
-For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
-For $w\in W_n$, we write $\pi_{m+1,w}^{I,J}:\tilde P_{m+1,w}^I\to\tilde P_{m+1,w}^J$ for the translated morphism with similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
-\begin{lemma}
-  \label{le:truncated quotients}
-  For $m\ge3$, the following hold:
-  \begin{enumerate}
-    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
-      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
-    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $0<k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
-      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
-      \begin{equation}
-        \label{dia:truncated coherence}
-        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I'_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
-        \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
-      \end{equation}
-      where the composed map $\pi_{m+1}^\bfI:\tilde P_{m+1}\to\tilde P_{m+1-k,\ui}^{I'_k}$ is unique up to scaling and therefore we write
-      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_k}.\]
-      These truncated preprojective representations satisfy 
-      \[\tilde P_{m+1}^\bfI=\tilde P_{m,i_0}^{\delta\bfI}=\cdots=\tilde P_{m+1-k,\ui}^{\delta^k\bfI}.\]
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
-  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
-    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
-    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
-    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
-  & & 0& 0&}\]
-  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.
-
-  The first claim of part (2) is then immediate by repeatedly applying part (1) while the final claim of part (2) is a consequence of the definition of $\delta$.
 \qed\end{proof}
@@
 Fix $m\ge1$.
-For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
+For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.1 provides a short exact sequence 
 \begin{equation}
@@
     0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
-  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
+  in which the bottom row is not split by Lemma~\ref{le:properties}.4.
   This implies that the map 
@@
   is surjective.
-  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
+  By Lemma~\ref{le:properties}.4 and the Auslander-Reiten formulas, we have 
   \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]

### 2019-06-08 response to reviewer.tex
Section 3 edits
Section 3 edits and reorganization
Small epduate to referee response
Section 3 and 4 edits, cleanup of rebuttal

--- 2019-05-08 response to reviewer.tex
@@
 
-\noindent In the following, we point out the changes we made.
+\noindent In the following, we point out the changes made and give responses to the referee's comments..
+
+\renewcommand{\labelenumi}{(\arabic{enumi})}
+\begin{enumerate}
+  \item[Section 3.1] The referee's suggestions were incorporated into shortened proofs of Lemmas 3.4 and 3.15, and motivated a rewriting of the proof of Lemma 3.9.
+  \item[Lemma 3.30] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.
+  \item[Corollary 3.32] The notation of perpendicular categories has been incorporated into the statement of the result.
+  \item[Definition 3.33] We had overlooked this simple viewpoint on admissible sequences and thank the referee for these extremely helpful remarks.
+    The entire section has been somewhat reorganized to better capture the nature of the construction.
+  \item[After Definition 3.33] After the reorganization, this notation is no longer being used.
+  \item[Before Lemma 3.34] This typo has been corrected.
+  \item[Lemma 3.34] Lemma 3.34 (now 3.33) has been rewritten to clarify the inductive structure of truncated preprojectives following the change of focus onto admissible sequences.
+  \item[Section 4.2] This is a matter of convention.
+    In general, the placement of the $*$'s for an attracting set is equivalent to the choice of the map $d:\{1,\ldots,n\}\to\ZZ$, cells of our chosen form impose the condition $d(1)>\cdots>d(n)$.
+  \item[Lemma 4.3] We have added references to Cerulli Irelli and Haupt at the beginning of Section 4.2.
+    However, Haupt's statement is stronger than his proof since it assumes a thin lift to an abelian cover, a trait our representations rarely possess.
+    Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result.
+  \item[Section 4.4] The dependence of various Caldero-Chapoton maps on their defining sequences has been clarified.
+  \item[Theorem 4.20] 
+\end{enumerate}
 
@@
 \renewcommand{\labelenumi}{(\arabic{enumi})}
-\item This should be a matter of definition and by reindexing appropriately we should get the version with $\ast$'s on the right.
-\item We refer to Cerulli Irelli's paper now.
-But not that the assumptions in Theorem 1 are stronger than ours as we do not assume that every basis element is mapped on a scalar multiple of another basis element.
-Note also that the number of fixed points is finite in Cerulli Irelli's case which is not true in general.
 \item We inserted a remark concerning the result of Haupt.
@@
 
-\item We inserted a remark which addresses this issue.
-\item Theorems 4.20, 4.21 are to be updated.
-\item Corollary 4.23: shorten the proof in the middle, the argument stays the same.
+\item We inserted a remark in Theorem 4.22 (former 4.20) which is meant to explain how the statement is obtained from the claim. Moreover, it should make the proof clearer.
+\item I find the strategy if 4.23 is very clear and I also think that the proof of 4.24 is very close to the suggestion of the referee. Any ideas what to change?
 \end{enumerate}

### 2019-06-08 Grassmannian_cells.tex
Section 3 and 4 edits, cleanup of rebuttal

@@
 Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
-Observe by an easy induction that $u_{k+1}-u_k>0$ for $k\ge0$ since $n\ge3$.
+Since $n\ge3$, we may observe by an easy induction that $u_{k+1}-u_k>0$ for $k\ge0$ and thus $u_{k+1}>(n-1)u_k$ for $k\ge0$.
 
@@
         \label{dia:truncated coherence}
-        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.35){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.35){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
+        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
         \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
@@
 
-  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from the definitions of these maps.
-
-  These diagrams stitch together to give the composition 
+  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from Lemma~\ref{le:properties}.5.
+
+  These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
   \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
@@
 The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
-Given $\tilde M\in\rep \tilde K(n)$, write
-\[\tilde M^\perp := \{\tilde N\in\rep \tilde K(n):\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
+As usual, given $\tilde M\in\rep \widetilde{K(n)}$, we write
+\[\tilde M^\perp := \{\tilde N\in\rep \widetilde{K(n)}:\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
 \begin{corollary}
@@
 Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$-fixed point sets can be calculated in an analogous manner.
+This greatly extends the results \cite[Theorem 1]{cerulli} and \cite[Theorem 1.2]{haupt} which utilize similar constructions.
 
@@
 \[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
-The following lemma generalizes \cite[Theorem 1]{cerulli}.
 \begin{lemma}
@@
 \qed\end{proof}
-\begin{remark} Note that similar techniques and results are obtained in \cite{haupt}, see e.g.
-\cite[Theorem 1.2(c)]{haupt}.
-Note that only representations $\hat X$ of $\hat Q$ are considered in the corresponding proof in \cite[Section 8]{haupt} which satisfy $\dim \hat X_{(i,\chi)}\in\{0,1\}$.
-Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result.
-\end{remark}
 
@@
 
-Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
-For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
+Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
+For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
 \begin{align*}
-  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
+  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
   E&\mapsto \big(E\cap M,(E+M)/M\big).
@@
 Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
-\begin{remark}
-We should always keep in mind that the middle term $B$ and the Caldero-Chapoton depend on the short exact sequence $\eta\in\Ext(N,M)$, i.e.
-to be more exact we should have named it $\Psi^{\eta}$.
-As a matter of readability we decided to omit this index.
-\end{remark}
 For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
@@
   \label{eq:truncated ses}
-  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
+  \eta_m:\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
 \end{equation}
@@
   \label{eq:truncated CC}
-  \Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
+  \Psi=\Psi^{\eta_m}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
 \end{equation}
@@
   \label{eq:tau sequence}
-  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
+  \xi_m:\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
 \end{equation}
@@
   \label{eq:truncated CC2}
-  \Phi:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
+  \Phi=\Phi^{\xi_m}:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
 \end{equation}
@@
 
-Finally, note that the claim together with Proposition \ref{label} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant.
+Finally, note that the claim together with Proposition \ref{fibers} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant.
 Thus Theorem \ref{vb} gives the statement of the Theorem.
@@
 
+\bibitem{cerulli} G.~Cerulli Irelli: Quiver Grassmannians associated with string modules. Journal of Algebraic Combinatorics \textbf{33}(2), 259-276 (2011).
+
 \bibitem{ce} 
@@
 
-\bibitem{cerulli} G.~Cerulli Irelli: Quiver Grassmannians associated with string modules. Journal of Algebraic Combinatorics \textbf{33}(2), 259-276 (2011).
-
 \bibitem{cefr} 

### 2019-06-08 Grassmannian_cells.tex
Minor edits

@@
 By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
-Alternatively, a cell decomposition of $X$ is a collection of disjoint locally closed subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
+Alternatively, a cell decomposition of $X$ is a disjoint collection of locally closed subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
 We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
@@
 The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
-If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
+If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, this action can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
 More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
 For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
-\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
+\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\},\]
+where $\lim_{t\to 0}t.y$ denotes the unique completion of the map $\CC^*\to X$, $t\mapsto t.y$, to a map $\CC\to X$.
 The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$-fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
@@
 If each component $C_i$ admits a cell decomposition, Theorem~\ref{thm:bb} implies the same is true of $X$.
-Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ and then taking the natural ordering of the resulting affine spaces gives a cell decomposition of $X$.
+Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ and then taking the natural ordering on the resulting affine spaces gives a cell decomposition of $X$.
 
@@
 For this recall that we can represent each subspace~$U\in\Gr_k(X)$ uniquely by a $k\times n$ matrix $M(U)$ whose rows provide a basis for $U$ when expanded as coefficient vectors in the basis $\mathcal B$.
-The uniqueness of $M(U)$ comes from requiring that it be in row-echelon form, i.e.\ there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
+The uniqueness of $M(U)$ comes from requiring that it be in a row-echelon form, e.g.\ we will assume there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
 \[M(U):=
@@
   \begin{enumerate}
-    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\hat Q}_\tbfe(\hat X)$ has a cell decomposition, then $\Gr_\bfe(X)$ has a cell decomposition.
+    \item If $\Gr_\bfe(X)$ is smooth and each $\Gr^{\tilde Q}_\tbfe(\tilde X)$ has a cell decomposition, then $\Gr_\bfe(X)$ has a cell decomposition.
     \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
@@
 Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$.
-As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
+As the $\GL_n(\CC)$-action above commutes with the natural base change action on representations, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
 \begin{proposition} 

### 2019-06-09 Grassmannian_cells.tex
Notation changes in section 4

@@
       \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
-    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$, there is a commutative diagram
+    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
       \begin{equation}
         \label{dia:truncated coherence}
-        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
-        \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
+        \xymatrix@R40pt@C60pt{& \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[dl] \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
+        \tilde P_{m+1}^J \ar^{\tilde\pi_{m+1}^{J,\{i\}^c}}[r] & \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
       \end{equation}
-    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,I}:\tilde P_{m+1}\to \tilde P_{m+1-k,\ui}^I$ satisfying:
-      \[\tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
+    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
+      \[\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
       \qquad\text{and}\qquad
-    \tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
+    \tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
       for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
@@
 \end{lemma}
+\begin{remark}
+  Note that we may take $J=\varnothing$ in Lemma~\ref{le:truncated quotients}.3 but the conditions impose $I\ne\varnothing$.
+\end{remark}
 \begin{proof}
@@
 
-  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from Lemma~\ref{le:properties}.5.
+  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangles is immediate from Lemma~\ref{le:properties}.5.
 
   These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
-  \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
+  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}\]
   which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
@@
 \end{align*}
-Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
+Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(F,G)\cong\mathbb{A}^{\dim\Hom(G,M/F)}$.
 For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
@@
   In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
-  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
-  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
+  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\prec\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
+  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
   for any fixed $\tbff$.
@@
 Fix $m\ge1$.
-For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.1 provides a short exact sequence 
+For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.3 provides a short exact sequence 
 \begin{equation}
@@
   \begin{enumerate}
-    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
-    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
+    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
+    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(F)=(F,0)$, i.e.\ $F$ is already a subrepresentation of $\tilde P_m(I,j)$.
   \end{enumerate} 
@@
 \begin{proof}
-  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
-  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
-  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
-  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
+  Any subrepresentation $F\subset\tilde P_{m,j}$ produces an exact sequence
+  \[\xymatrix{\Ext(\tilde P_{m+1}^I,F)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r] & 0}.\]
+  But note that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
+  \[\xymatrix{0\ar[r]& F\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & F'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
     0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
@@
   This implies that the map 
-  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
-  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
+  \[\Ext(\tilde P_{m+1}^I,F)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
+  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
   This argument can be reversed and thus (1) holds.
 
-  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi^{-1}(V,W)$.
+  Now consider $F\subset\tilde P_{m,j}$ with 
+  \[\Phi(F)=(S,T)\in\Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).\]
   This gives rise to the following commutative diagram:  
   \[\xymatrix{
-    \Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
+    \Ext(\tilde P_{m+1}^I,S)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,T)\ar[r]\ar[d] & 0\\
     \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
-    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
+    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\ar[r]\ar[d] & 0 \\
     0&0&0&}\]
-  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
+  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)=0$ as well.
   This yields the isomorphisms
-  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]
-
-  If $W=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)=\varnothing$.
-
-  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
-  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
+  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T).\]
+
+  If $T=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)=\varnothing$.
+
+  If $T\neq 0$, $\tilde K_m/T$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/T)=0$.
+  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/T$ factors through the middle term $Z$ of the AR-sequence 
   \begin{equation}
@@
   This in particular says the first map of the induced sequence
-  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
+  \[\Hom(Z,\tilde K_m/T)\to\Hom(\tilde K_m,\tilde K_m/T)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\to\Ext(Z,\tilde K_m/T)\]
   is surjective.
@@
   Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
-  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
-  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is non-empty in this case.
-\qed\end{proof}
-
-Now we are able to state the following result concerning the fibers of $\Psi$:
+  But then $\Ext(Z,\tilde K_m/T)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T)$ must be zero as well.
+  By part (1) we see that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is non-empty in this case.
+\qed\end{proof}
+
+Now we are able to state the following crucial result concerning the fibers of $\Psi$:
 \begin{proposition}
@@
   \begin{enumerate}
-    \item For $W\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi^{-1}(U,W)\cong\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
-    \item If $W=\tilde P_{m+1}^I$, the fiber $\Psi^{-1}(U,W)$ is not empty if and only if $\Phi(U)\neq(U,0)$.
-      In this case, we have $\Psi^{-1}(U,W)\cong\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
+    \item For $G\subsetneq\tilde P_{m+1}^I$ and $F\subseteq\tilde P_{m,j}$, we have $\Psi^{-1}(F,G)\cong\AA^{\langle G,\tilde P_{m,j}/F\rangle}$.
+    \item If $G=\tilde P_{m+1}^I$, the fiber $\Psi^{-1}(F,G)$ is not empty if and only if $\Phi(F)\neq(F,0)$.
+      In this case, we have $\Psi^{-1}(F,G)\cong\AA^{\langle G,\tilde P_{m,j}/F\rangle}$.
   \end{enumerate}
@@
 \begin{proof}
-  By Lemma~\ref{le:subrep}, any subrepresentation $W\subsetneq\tilde P_{m+1}^I$ is preprojective.
-  But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
-  Thus we have $\Ext(W,\tilde P_{m,j}/U)=0$. 
-  If $U=0$, we have $\Ext(W,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $W$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_m)=0$ for $l\leq m+1$.
+  By Lemma~\ref{le:subrep}, any subrepresentation $G\subsetneq\tilde P_{m+1}^I$ is preprojective.
+  But the representation $\tilde P_{m,j}/F$ is not preprojective as it is a proper quotient of a preprojective representation unless $F=0$.
+  Thus we have $\Ext(G,\tilde P_{m,j}/F)=0$. 
+  If $F=0$, we have $\Ext(G,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $G$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_m)=0$ for $l\leq m+1$.
 
@@
   Assume $\tbfg=\udim\tilde P_{m+1}^I$.
-  By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(U,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
-  But the map $U\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
+  By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(F,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
+  But the map $F\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
 \qed\end{proof}
@@
   \begin{itemize}
-    \item[($\dagger$)] For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
+    \item[($\dagger$)] For any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(E)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
   \end{itemize}
@@
 
-Finally, note that the claim together with Proposition \ref{fibers} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant.
+Finally, note that the claim together with Proposition \ref{fibers} ensures that the fiber dimension along the points of the affine cell $C_E$ is constant.
 Thus Theorem \ref{vb} gives the statement of the Theorem.
@@
 
-  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(U,V)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
+  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(F,G)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
   \begin{itemize}
     \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
-    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$.
+    \item $m\ge3$, with $\pi_{m,j}^\bfJ(F)=0$.
   \end{itemize}
@@
 
-  For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
-  But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+  For $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(E)\in C_k$.
+  But then $\pi_{m+1}^{J,\bfI}(E)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(G)\ne0$ for all $G\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(E')\ne0$ for all $E'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
 This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
@@
   \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
-  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)\cong\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
-  Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
-  Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
-  Together these yield $\Ext(W,P_{j_{r'+1}}/U)=0$ and thus
-  \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
-  for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
+  The results of \cite[Section 3]{cc} show that $\Psi_{\bfe}^{-1}(F,G)\cong\AA^{\dim\Hom(G,P_{j_{r'+1}}/F)}$ for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
+  Now every subrepresentation $G$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
+  Moreover, the quotient $P_{j_{r'+1}}/F$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
+  Together these yield $\Ext(G,P_{j_{r'+1}}/F)=0$ and thus
+  \[\dim\Hom(G,P_{j_{r'+1}}/F)=\langle G, P_{j_{r'+1}}/F\rangle\]
+  for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
   Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.

### 2019-06-09 Grassmannian_cells.tex
Notation changes in section 4

@@
 We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a $\CC^*$-action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
-Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
-In general, this does not induce a $\CC^*$-action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
-Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
+Associated to each subspace $E_i$, there is a corresponding subspace $t.E_i$ for each $t\in\CC^*$.
+In general, this does not induce a $\CC^*$-action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.E=(t.E_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $E\in\Gr_\bfe(X)$.
+Indeed, for this such an action must satisfy $X_\alpha(t.E_i)\subset t.E_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
 \begin{lemma}
@@
 \begin{proof} 
-  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
-  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.
+  Fix $E\in\Gr_\bfe(X)$ and consider $e_i\in E_i$.
+  Since $E$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(e_i)=e_j$ for some $e_j\in E_j$.
 
   As $X$ can be lifted to $\hat Q$, for any arrow $\alpha\in Q_1$ we can write $X_\alpha:X_i\to X_j$ as a block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$ for $\chi\in A_Q$.
-  Then writing $u_i=\sum_{\chi\in A_Q} u_{(i,\chi)}$ for some vectors $u_{(i,\chi)}\in X_{(i,\chi)}$, we have $X_\alpha(u_{(i,\chi)})=X_{(\alpha,\chi)}(u_{(i,\chi)})\in X_{(j,\chi+e_\alpha)}$, say $X_{(\alpha,\chi)}(u_{(i,\chi)})=u_{(j,\chi+e_\alpha)}$.
-  It follows that $u_j=\sum_{\chi\in A_Q} u_{(j,\chi+e_\alpha)}$ and so
+  Then writing $e_i=\sum_{\chi\in A_Q} e_{(i,\chi)}$ for some vectors $e_{(i,\chi)}\in X_{(i,\chi)}$, we have $X_\alpha(e_{(i,\chi)})=X_{(\alpha,\chi)}(e_{(i,\chi)})\in X_{(j,\chi+e_\alpha)}$, say $X_{(\alpha,\chi)}(e_{(i,\chi)})=e_{(j,\chi+e_\alpha)}$.
+  It follows that $e_j=\sum_{\chi\in A_Q} e_{(j,\chi+e_\alpha)}$ and so
   \begin{align*}
-    X_\alpha(t.u_i)
-    &=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}X_{(\alpha,\chi)}(u_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}\sum\limits_{\chi\in A_Q} t.u_{(j,\chi+e_\alpha)}=t^{-c_\alpha} t.u_j.
+    X_\alpha(t.e_i)
+    &=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}X_{(\alpha,\chi)}(e_{(i,\chi)})=\sum\limits_{\chi\in A_Q} t^{d(i,\chi)}e_{(j,\chi+e_\alpha)}=t^{-c_\alpha}\sum\limits_{\chi\in A_Q} t.e_{(j,\chi+e_\alpha)}=t^{-c_\alpha} t.e_j.
   \end{align*}
-  Therefore $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and we obtain a $\CC^*$-action on $\Gr_\bfe(X)$.
+  Therefore $X_\alpha(t.E_i)\subset t.E_j$ for every arrow $\alpha:i\to j$ of $Q$ and we obtain a $\CC^*$-action on $\Gr_\bfe(X)$.
 \qed\end{proof}
@@
 \begin{proof}
-  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
-  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
+  A representation $E\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.E=E$ for all $t\in\C^\ast$, i.e.\ $t.E_i=E_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
+  Thus, apart from being a subrepresentation of $X$, each component $E_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
   By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
-  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
-  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
+  \[E_i=\bigoplus_{\chi\in A_Q} E_i\cap X_{(i,\chi)}\]
+  which is equivalent to $E$ being liftable to the universal abelian covering $\hat Q$.
 \qed\end{proof}
@@
   Then $g.P_{m+1}^V$ is given by the matrices $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
-  Let $(U_1,U_2)\in\Gr_\bfe(g.P_{m+1}^V)$.
+  Let $(E_1,E_2)\in\Gr_\bfe(g.P_{m+1}^V)$.
   Then we have  
-  \[M_{\alpha_i}(U_2)\subset U_1 \text{ for all } i=1,\ldots,n\Leftrightarrow \left(\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}\right)(U_2)\subset U_1 \text{ for all } i=1,\ldots,n.\]
+  \[M_{\alpha_i}(E_2)\subset E_1 \text{ for all } i=1,\ldots,n\Leftrightarrow \left(\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}\right)(E_2)\subset E_1 \text{ for all } i=1,\ldots,n.\]
   Note that we have $g^{-1}.(g.P_{m+1}^V)=P_{m+1}^V$ which shows the non-obvious direction.
@@
   \noindent{\bf Claim.}
-  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  For any admissible sequence $\bfi=(i_1,\ldots,i_k)$ with $k<m$ and any subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
-    \item[($\dagger$)] For any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(E)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
+    \item[($\dagger$)] For any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,J,I}(E)\neq 0$, we have $\tilde\pi_{m+1}^{\ui,J,I}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
   \end{itemize}

### 2019-06-09 Grassmannian_cells.tex
Notation changes in section 4

@@
   For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
-In particular, every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
 \end{theorem}
-\begin{proof}
+\begin{corollary}
+  Every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
+\end{corollary}
+\begin{proof}
+  This is the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
+\end{proof}
+\begin[Proof of Theorem~\ref{cellscover}]{proof}
 

### 2019-06-10 Grassmannian_cells.tex
Section 3 edits

@@
 and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
+
 The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
@@
   \label{le:truncated quotients}
-  For $m\ge3$, the following hold:
+  For $m\ge2$, the following hold:
   \begin{enumerate}
@@
       \end{equation}
-    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
-      \[\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
-      \qquad\text{and}\qquad
-    \tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
-      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
+    \item For an admissible sequence $\ui\in A_1^{(k)}$, $k<m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if and only if $i_1\notin J$.
+    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
+      \begin{itemize}
+        \item $\tilde\pi_{m+1}^{\ui,J,I}\circ\tilde\pi_{m+1}^{K,J}=\tilde\pi_{m+1}^{\ui,K,I}$ for $K\subsetneq J$;
+        \item $\tilde\pi_{m+1-k,\ui}^{I,H}\circ\tilde\pi_{m+1}^{\ui,J,I}=\tilde\pi_{m+1}^{\ui,J,H}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
+        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I$;
+        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,\varnothing,I}$ for $\ell<k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
+      \end{itemize}
   \end{enumerate}
 \end{lemma}
-\begin{remark}
-  Note that we may take $J=\varnothing$ in Lemma~\ref{le:truncated quotients}.3 but the conditions impose $I\ne\varnothing$.
-\end{remark}
 \begin{proof}
@@
 
-  These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
-  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}\]
-  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
+  For (3), if $i_1\in J$, then $\tilde P_{m,i_1}\subset\ker\tilde\pi_{m+1}^J$ and so the same is true of $\tilde P_{m+1-k,\ui}$.
+  By Lemma~\ref{le:properties} and the admissibility of $\ui$, the representation $\tilde P_{m-1,(i_1,i_2)}$ embeds into $\tilde P_{m,i_1}^{\{i_1\}}$ and hence the same is true of $\tilde P_{m+1-k,\ui}$.
+  For $i_1\notin J$, part (2) shows that such embeddings factor through $\tilde P_{m+1}^J$ which gives (3).
+
+  The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
+  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}.\]
+  These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
 \qed\end{proof}
@@
   \label{cellscover}
-  For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
+  For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
+  These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  \begin{itemize}
+    \item[($\dagger$)] for any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,J,I}(E)\neq 0$ for some admissible sequence $\bfi=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,J,I}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
+  \end{itemize}
 \end{theorem}
@@
 \end{proof}
-\begin[Proof of Theorem~\ref{cellscover}]{proof}
-
+\subsubsection*{Proof of Theorem~\ref{cellscover}}
   We work by induction on $m$.
@@
 This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
-\qed\end{proof}
+\qed
 

### 2019-06-11 Grassmannian_cells.tex
Section 3 edits
Proof of Theorem 4.20

@@
     \label{eq:truncated preprojectives}
-    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
+    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_{m+1}^V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
   \end{equation}
@@
   \label{le:unique preprojective morphism}
-  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_{m+1}^V:P_{m+1}\to P_{m+1}^V$.
   Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
@@
   \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
-  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
+  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_{m+1}^V:P_{m+1}\to P_{m+1}^V$.
   The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
@@
       0 \ar[r] & K \ar[r] \ar[d] \ar@{}[dr]|(.7){\lrcorner} & P_m\otimes W \ar[d]^{ev_W} \ar[r] & C \ar[r] \ar[d] & 0\\
-    0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_V} & P_{m+1}^V \ar[r] & 0}\]
+      0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_{m+1}^V} & P_{m+1}^V \ar[r] & 0}\]
 
@@
         \label{ses1}
-        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
+        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\tilde\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
       \end{equation}
@@
       \begin{equation*}
-        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{J,I}} & \tilde P_{m+1}^I \ar[r] & 0}.
+        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{I,J}} & \tilde P_{m+1}^I \ar[r] & 0}.
       \end{equation*}
-      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
+      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{I,K}=\pi_{m+1}^{I,J}\circ\pi_{m+1}^{J,K}$ and $\pi_{m+1}^I=\pi_{m+1}^{I,J}\circ\pi_{m+1}^J$.
   \end{enumerate}
@@
 and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
+Here we allow $k=0$ and take $A_1^{(0)}$ to consist of only the empty word $\ui=()$.
 
@@
   \begin{enumerate}
-    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
-      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
+    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
+      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
     \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
@@
         \label{dia:truncated coherence}
-        \xymatrix@R40pt@C60pt{& \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[dl] \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
-        \tilde P_{m+1}^J \ar^{\tilde\pi_{m+1}^{J,\{i\}^c}}[r] & \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
+        \xymatrix@R40pt@C60pt{
+           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
+          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
+          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
+          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
+          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
+          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
       \end{equation}
-    \item For an admissible sequence $\ui\in A_1^{(k)}$, $k<m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if and only if $i_1\notin J$.
-    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
+    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
+    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
+      These satisfy the following relations:
       \begin{itemize}
-        \item $\tilde\pi_{m+1}^{\ui,J,I}\circ\tilde\pi_{m+1}^{K,J}=\tilde\pi_{m+1}^{\ui,K,I}$ for $K\subsetneq J$;
-        \item $\tilde\pi_{m+1-k,\ui}^{I,H}\circ\tilde\pi_{m+1}^{\ui,J,I}=\tilde\pi_{m+1}^{\ui,J,H}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
-        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I$;
-        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,\varnothing,I}$ for $\ell<k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
+        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
+          \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
+        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
+        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $0\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
       \end{itemize}
@@
   The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
-  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}.\]
+  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
   These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
@@
   But then $\Ext(Z,\tilde K_m/T)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T)$ must be zero as well.
-  By part (1) we see that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is non-empty in this case.
+  From part (1), we see that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is non-empty in this case.
 \qed\end{proof}
@@
   For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
-  These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
-    \item[($\dagger$)] for any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,J,I}(E)\neq 0$ for some admissible sequence $\bfi=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,J,I}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
+    \item[($\dagger$)] for any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,I,J}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
   \end{itemize}
@@
 \begin{proof}
-  This is the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
-\end{proof}
+  For the standard lifts $\tilde P_m$, this is just the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
+  The claim for any translate $\tilde P_{m,w}$ for $w\in W_n$ is an immediate consequence of this.
+\qed\end{proof}
 \subsubsection*{Proof of Theorem~\ref{cellscover}}
@@
   When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
-  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip
-
-  \noindent{\bf Claim.}
-  For any admissible sequence $\bfi=(i_1,\ldots,i_k)$ with $k<m$ and any subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
-  \begin{itemize}
-    \item[($\dagger$)] For any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,J,I}(E)\neq 0$, we have $\tilde\pi_{m+1}^{\ui,J,I}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
-  \end{itemize}
-  \vs
-
-\begin{remark}
-Note that having proved the claim, for $|J|\leq n-2$ the statement itself is obtained when setting $\bfI=(J\cup\{i\})$ for any $i\in\{1,\ldots,n\}\backslash\{J\}$.
-For $|J|=n-1$, we can apply Lemma~\ref{le:truncated quotients}, i.e.
-$P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ with $J^c=\{j\}$, together with the fact that $\tilde P_{m,j}^{\{j\}}$ is obtained when translating $\tilde P_{m}^{\{j\}}$ in the universal covering quiver.
-Clearly, translation does not affect quiver Grassmannians when also translating dimension vectors $\tbfe$, i.e.
-quiver Grassmannians of $\tilde P_{m,j}^{\{j\}}$ are just the same as those of $\tilde P_{m}^{\{j\}}$.
-
-Furthermore, recall that the preprojective representations $\tilde P_{m+1}$ and their quiver Grassmannians are obtained when setting $J=\varnothing$ and considering any short exact sequence
-		$$\ses{\tilde P_{m,j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\{j\}}}$$
-for $j\in\{1,\ldots,n\}$. Then we can use the fact that $\tilde P_{m,j}$ is the translation of $\tilde P_m$.
-
-Finally, note that the claim together with Proposition \ref{fibers} ensures that the fiber dimension along the points of the affine cell $C_E$ is constant.
-Thus Theorem \ref{vb} gives the statement of the Theorem.
-\end{remark}
-
-  In what follows, we will freely use the notation from Lemma~\ref{le:truncated quotients}.
-  We proceed by simultaneous induction on $m$ and reverse induction on $|J|$.
-  Fix an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$.
-
-  To begin, we assume $|J|=n-1$ and thus $J=I_0$.
-  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,i_0}^{J_0}$ and so by induction on $m$ the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)=\Gr^{\tilde Q}_\tbfe(\tilde P_{m,i_0}^{J_0})$ admits a cell decomposition so that the compatibility condition ($\dagger$) holds for the unique map $\pi_{m,i_0}^{J_0,\delta\bfI}:\tilde P_{m,i_0}^{J_0}\to\tilde P_{m,i_0}^{\delta\bfI}$.
-  But $\tilde P_{m,i_0}^{\delta\bfI}=\tilde P_{m+1}^\bfI$ so that $\pi_{m,i_0}^{J_0,\delta\bfI}$ coincides with the map $\pi_{m+1}^{J,\bfI}$ and thus the condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
-
-  Now suppose $|J|<n-1$.
-  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous and any cell decomposition will suffice.
-  Thus we may assume $J\subsetneq I_0$.
-
-  Choose any subset $I\subset I_0$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
+
+  For $m\ge2$, we work by reverse induction on $|J|$ with the base case $|J|=n-1$, say $J^c=\{j\}$.
+  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui,I,\{j\}}$ coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
+  By the induction on $m$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for each of the maps $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$, where $\ui'_1=(i_2,\ldots,i_k)$ with $i_2\ne j$.
+  But~$\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr^{\tilde Q}_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection maps $\tilde\pi_{m,j}^{\ui,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
+  Then using the equivalence $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\cong\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+
+  Consider $J\subsetneq I\subsetneq \{1,\ldots,n\}$ with $I\setminus J=\{j\}$.
   This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
-  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a cell decomposition which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
-  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{k=1}^r C_k.\]
-
-  When $m=2$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ is just a point.
-  For $m\ge3$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})$ admits a cell decomposition which is compatible with the map $\pi_{m,j}^\bfJ:\tilde P_{m,j}\to\tilde P_{m-1,(j,j)}^I$, where $\bfJ=(\{1,\ldots,\widehat j,\ldots,n\},I)$, say
-  \[\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=\coprod_{\ell=1}^s B_\ell.\] 
- For $m=2$, we write $\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=B_1$.
-In view of Remark \ref{rem:cell decompositions}, we need to show that the image of each $\Psi_{\tbff,\tbfg}$ is compatible with these cell decompositions in order to establish a cell decomposition of each $\mathcal G_{\tbff,\tbfg}$ which then gives a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
-
-  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(F,G)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
+  By way of induction, we assume all quiver Grassmannians $Gr_\tbff(\tilde P_{m,j})$ and $Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$), say
+  \begin{equation}
+    \label{eq:cellB}
+    \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=\coprod_{k=1}^r B_{\tbff,k}
+  \end{equation}
+  and
+  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
+  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(F,G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
   \begin{itemize}
     \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
-    \item $m\ge3$, with $\pi_{m,j}^\bfJ(F)=0$.
+    \item $m\ge3$ with $\tilde\pi_{m,j}^{j,I,\varnothing}(F)=0$.
   \end{itemize}
-By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or none of the fibers over $B_l\times C_k$ are empty.
-This shows the compatibility with the image.
-If the fiber is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
-Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
-
-  For $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(E)\in C_k$.
-  But then $\pi_{m+1}^{J,\bfI}(E)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(G)\ne0$ for all $G\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(E')\ne0$ for all $E'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
-This shows ($\dagger$) for $\pi_{m+1}^{J,\bfI}$.
+  By the compatibility with $\tilde\pi_{m,j}^{j,I,\varnothing}$ for the cell decomposition \eqref{eq:cellB}, we see that either all or none of the fibers over $B_{\tbff,k}\times C_{\tbfg,\ell}$ are empty.
+  It follows that there is an induced cell decomposition on the image of $\Psi_{\tbff,\tbfg}$ given by those products of cells $B_{\tbff,k}\times C_{\tbfg,\ell}$ over which the fiber is not empty.
+  Theorem \ref{vb} then provides a cell decomposition for $\cG_{\tbff,\tbfg}$, where cells take the form $B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  By Lemma~\ref{le:good partition}, we may order the affine cells in the $\cG_{\tbff,\tbfg}$ appropriately to obtain a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$ (c.f.
+Remark~\ref{rem:cell decompositions}).
+
+  Now consider $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $E\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and some subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
+  There are two cases to consider:
+  \begin{itemize}
+    \item If $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
+      By construction, we have $\tilde\pi_{m+1}^{I,J}(E')\in C_{\tbfg,\ell}$ for all~$E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+      But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(G)\ne0$ for all~$G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(E')\big)\neq 0$ for all $E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+    \item If $i_1=j$, the restricted map $\tilde\pi_{m+1}^{\ui,I',J}\Big|_{\tilde P_{m,j}}$ coincides with $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}$ by Lemma~\ref{le:truncated quotients}.4.
+      By construction, we have $E'\cap P_{m,j}\in B_{\tbff,k}$ for all ~$E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+      But $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(E\cap\tilde P_{m,j})=\tilde\pi_{m+1}^{\ui,I',J}(E)\ne0$ implies $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(F)\ne0$ for all~$F\in B_{\tbff,k}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(E')=\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(E'\cap \tilde P_{m,j})\neq 0$ for all $E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+  \end{itemize}
+  Thus the compatibility condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
 \qed

### 2019-06-13 Grassmannian_cells.tex
Committing to checkout old version

@@
     \item For each proper subset $J\subsetneq I$, there is an exact sequence 
-      \begin{equation*}
+      \begin{equation}
+        \label{eq:truncted sequence}
         \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{I,J}} & \tilde P_{m+1}^I \ar[r] & 0}.
-      \end{equation*}
+      \end{equation}
       For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{I,K}=\pi_{m+1}^{I,J}\circ\pi_{m+1}^{J,K}$ and $\pi_{m+1}^I=\pi_{m+1}^{I,J}\circ\pi_{m+1}^J$.
@@
 The results of \cite{rupel} provide a stronger statement than Theorem~\ref{th:combinatorial euler}.
-Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).
+Indeed, the compatible pairs are shown to compute the counting polynomials of the quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).
 We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explanation of this result.

### 2019-06-13 response to reviewer.tex
Restored the old proof of Lemma 3.15

@@
 \begin{enumerate}
-  \item[Section 3.1] The referee's suggestions were incorporated into shortened proofs of Lemmas 3.4 and 3.15, and motivated a rewriting of the proof of Lemma 3.9.
+  \item[Section 3.1] The referee's suggestions were incorporated into a shortened proof of Lemmas 3.4 and motivated a rewriting of the proof of Lemma 3.9.
+    We could not see how to use irreducibility to prove Lemma 3.15, it is not clear why a subrepresentation $U \subset \tilde P_{m+1}^V$ lifts to a map $U \to \tilde P_{m+1}$ rather than giving rise to a map $\tilde P_{m+1} \to U$.
   \item[Lemma 3.30] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.

### 2019-06-13 Grassmannian_cells.tex
Restored the old proof of Lemma 3.15

@@
 \begin{proof}
-  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
+  We proceed by induction on $m$.
+  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
+  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
+
+  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
 \qed\end{proof}

### 2019-06-17 Grassmannian_cells.tex
Added independence of construction of cells to Theorem 4.20

@@
         %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
-        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $0\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
+        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
       \end{itemize}
@@
   The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
-  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
+  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_1}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
   These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
@@
       Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
-      \[\tilde P_m(I,j):=
+      \[\tilde P_m(j,I):=
         \begin{cases}
@@
   It then follows from Lemma~\ref{le:homdecomposition} that $\tilde P_{m-1,(j,k)}$ is in the kernel of the vertical morphism $\eta$ for $k\ne j$.
-  Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} P_{m-2,(j,j,i)}$, and so $\ker\eta=P_m(I,j)$.
+  Therefore $\ker\eta$ is the direct sum of these with the kernel of the induced map $\tilde P_{m-1}\to\tilde P_{m-1}^{I\setminus\{j\}}$, that is with $\bigoplus_{i\in I\setminus\{j\}} \tilde P_{m-2,i}=\bigoplus_{i\in I\setminus\{j\}} \tilde P_{m-2,(j,j,i)}$, and so $\ker\eta=\tilde P_m(j,I)$.
   Since $\eta$ and the right hand vertical morphism have the same kernel, this completes the proof of (1).
@@
   Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
-  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
+  For $m\geq 2$, we have $\tilde P_m(j,I)\in (\tilde P_{m+1}^I)^\perp$.
 \end{corollary}
@@
   If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
-  \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
-  Following Lemma~\ref{le:properties}.3, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
+  \[\ses{\tilde P_m(j,I)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
+  Following Lemma~\ref{le:properties}.3, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)=0$.
   From Lemma~\ref{le:properties}.3 again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
@@
   \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
-  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
+  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)=0$.
 \qed\end{proof}
@@
 
-Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
+Let $\eta:\ses{\tilde M}{\tilde B}{\tilde N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
 For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
 \begin{align*}
-  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
-  E&\mapsto \big(E\cap M,(E+M)/M\big).
+  \Psi=\Psi^\eta:\Gr_\tbfe(\tilde B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N)\\
+  E&\mapsto \big(\tilde E\cap \tilde M,(\tilde E+\tilde M)/\tilde M\big).
 \end{align*}
-Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(F,G)\cong\mathbb{A}^{\dim\Hom(G,M/F)}$.
-For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
+Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(\tilde F,\tilde G)\cong\mathbb{A}^{\dim\Hom(\tilde G,\tilde M/\tilde F)}$.
+For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N)\big)$, we have 
 \begin{equation}
   \label{eq:grassmannian decomposition}
-  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
+  \Gr_\tbfe(\tilde B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
 \end{equation}
 Then $\Psi$ restricts to a map
-\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
+\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(\tilde M)\times \Gr_\tbfg(\tilde N).\]
 The following results are proven in \cite[Section 3]{cefr}.
@@
   \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
-  is closed in $\Gr_\tbfe(B)$.
-\end{lemma}
-\begin{proof}
-  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
-  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
-  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
+  is closed in $\Gr_\tbfe(\tilde B)$.
+\end{lemma}
+\begin{proof}
+  Recall that $\Gr_\tbfe(\tilde B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(\tilde B_i)$.
+  For each $i$, the inclusion $\tilde M_i\subset \tilde B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(\tilde E_i)=\dim(\tilde E_i\cap \tilde M_i)$.
+  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(\tilde B_i)$.
   It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\prec\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
-  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
+  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(\tilde B)\]
   for any fixed $\tbff$.
@@
   \label{rem:cell decompositions}
-  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.
-
-  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
-  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
+  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(\tilde M)\times\Gr_\tbfg(\tilde N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.
+
+  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(\tilde B)$.
+  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(\tilde B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
 \end{remark}
@@
   \label{eq:truncated CC}
-  \Psi=\Psi^{\eta_m}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
+  \Psi=\Psi^{\eta_m}:\Gr_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(\tilde P_{m,j})\times\Gr_\tbfg(\tilde P_{m+1}^I).
 \end{equation}
@@
   \label{eq:tau sequence}
-  \xi_m:\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
+  \xi_m:\ses{\tilde P_m(j,I)}{\tilde P_{m,j}}{\tilde C_m},
 \end{equation}
-where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
+where $\tilde C_m=\tilde C_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde C_2=\tilde C_2(j,I)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
 Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
@@
   \label{eq:truncated CC2}
-  \Phi=\Phi^{\xi_m}:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
+  \Phi=\Phi^{\xi_m}:\Gr_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr_\tbfs\big(\tilde P_m(j,I)\big)\times\Gr_\tbft(\tilde C_m).
 \end{equation}
@@
   \begin{enumerate}
-    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
-    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(F)=(F,0)$, i.e.\ $F$ is already a subrepresentation of $\tilde P_m(I,j)$.
+    \item The fiber $\Psi^{-1}(\tilde F,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)=0$.
+    \item The fiber $\Psi^{-1}(\tilde F,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(\tilde F)=(\tilde F,0)$, i.e.\ $\tilde F$ is already a subrepresentation of $\tilde P_m(j,I)$.
   \end{enumerate} 
@@
 \begin{proof}
-  Any subrepresentation $F\subset\tilde P_{m,j}$ produces an exact sequence
-  \[\xymatrix{\Ext(\tilde P_{m+1}^I,F)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r] & 0}.\]
-  But note that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
-  \[\xymatrix{0\ar[r]& F\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & F'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
+  Any subrepresentation $\tilde F\subset\tilde P_{m,j}$ produces an exact sequence
+  \[\xymatrix{\Ext(\tilde P_{m+1}^I,\tilde F)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)\ar[r] & 0}.\]
+  But note that the fiber $\Psi^{-1}(\tilde F,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
+  \[\xymatrix{0\ar[r]& \tilde F\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & \tilde F'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
     0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
@@
   This implies that the map 
-  \[\Ext(\tilde P_{m+1}^I,F)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
-  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
+  \[\Ext(\tilde P_{m+1}^I,\tilde F)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
+  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)=0$.
   This argument can be reversed and thus (1) holds.
 
-  Now consider $F\subset\tilde P_{m,j}$ with 
-  \[\Phi(F)=(S,T)\in\Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).\]
+  Now consider $\tilde F\subset\tilde P_{m,j}$ with 
+  \[\Phi(\tilde F)=(\tilde S,\tilde T)\in\Gr_\tbfs\big(\tilde P_m(j,I)\big)\times\Gr_\tbft(\tilde C_m).\]
   This gives rise to the following commutative diagram:  
   \[\xymatrix{
-    \Ext(\tilde P_{m+1}^I,S)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,T)\ar[r]\ar[d] & 0\\
-    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
-    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\ar[r]\ar[d] & 0 \\
+    \Ext(\tilde P_{m+1}^I,\tilde S)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde T)\ar[r]\ar[d] & 0\\
+    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde C_m)\ar[r]\ar[d] & 0\\
+    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(j,I)/\tilde S\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde C_m/\tilde T)\ar[r]\ar[d] & 0 \\
     0&0&0&}\]
-  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)=0$ as well.
+    By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(j,I)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(j,I)/\tilde S\big)=0$ as well.
   This yields the isomorphisms
-  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T).\]
-
-  If $T=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)=\varnothing$.
-
-  If $T\neq 0$, $\tilde K_m/T$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/T)=0$.
-  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/T$ factors through the middle term $Z$ of the AR-sequence 
+  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde C_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)\cong\Ext(\tilde P_{m+1}^I,\tilde C_m/\tilde T).\]
+
+  If $\tilde T=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(\tilde F,\tilde P_{m+1}^I)=\varnothing$.
+
+  If $\tilde T\neq 0$, $\tilde C_m/\tilde T$ is a proper factor of $\tilde C_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde C_m/\tilde T)=0$.
+  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde C_m\to\tilde C_m/\tilde T$ factors through the middle term $\tilde Z$ of the AR-sequence 
   \begin{equation}
     \label{eq:ar2}
-    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
+    \ses{\tilde C_m}{\tilde Z}{\tilde P_{m+1}^I}.
   \end{equation}
   This in particular says the first map of the induced sequence
-  \[\Hom(Z,\tilde K_m/T)\to\Hom(\tilde K_m,\tilde K_m/T)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\to\Ext(Z,\tilde K_m/T)\]
+  \[\Hom(\tilde Z,\tilde C_m/\tilde T)\to\Hom(\tilde C_m,\tilde C_m/\tilde T)\to\Ext(\tilde P_{m+1}^I,\tilde C_m/\tilde T)\to\Ext(\tilde Z,\tilde C_m/\tilde T)\]
   is surjective.
   By Lemma~\ref{le:properties}.4 and the Auslander-Reiten formulas, we have 
-  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
+  \[\Ext(\tilde C_m,\tilde C_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde C_m)=\CC.\]
   For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
-  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
-  But then $\Ext(Z,\tilde K_m/T)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T)$ must be zero as well.
-  From part (1), we see that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is non-empty in this case.
+  Thus the injective map $\CC=\Hom(\tilde C_m,\tilde C_m)\to\Ext(\tilde P_{m+1}^I,\tilde C_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde C_m)$ to this sequence yields $\Ext(\tilde Z,\tilde C_m)=0$.
+  But then $\Ext(\tilde Z,\tilde C_m/\tilde T)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)\cong\Ext(\tilde P_{m+1}^I,\tilde C_m/\tilde T)$ must be zero as well.
+  From part (1), we see that the fiber $\Psi^{-1}(\tilde F,\tilde P_{m+1}^I)$ is non-empty in this case.
 \qed\end{proof}
@@
   \begin{enumerate}
-    \item For $G\subsetneq\tilde P_{m+1}^I$ and $F\subseteq\tilde P_{m,j}$, we have $\Psi^{-1}(F,G)\cong\AA^{\langle G,\tilde P_{m,j}/F\rangle}$.
-    \item If $G=\tilde P_{m+1}^I$, the fiber $\Psi^{-1}(F,G)$ is not empty if and only if $\Phi(F)\neq(F,0)$.
-      In this case, we have $\Psi^{-1}(F,G)\cong\AA^{\langle G,\tilde P_{m,j}/F\rangle}$.
+    \item For $\tilde G\subsetneq\tilde P_{m+1}^I$ and $\tilde F\subseteq\tilde P_{m,j}$, we have $\Psi^{-1}(\tilde F,\tilde G)\cong\AA^{\langle \tilde G,\tilde P_{m,j}/\tilde F\rangle}$.
+    \item If $\tilde G=\tilde P_{m+1}^I$, the fiber $\Psi^{-1}(\tilde F,\tilde G)$ is not empty if and only if $\Phi(\tilde F)\neq(\tilde F,0)$.
+      In this case, we have $\Psi^{-1}(\tilde F,\tilde G)\cong\AA^{\langle \tilde G,\tilde P_{m,j}/\tilde F\rangle}$.
   \end{enumerate}
@@
 \begin{proof}
-  By Lemma~\ref{le:subrep}, any subrepresentation $G\subsetneq\tilde P_{m+1}^I$ is preprojective.
-  But the representation $\tilde P_{m,j}/F$ is not preprojective as it is a proper quotient of a preprojective representation unless $F=0$.
-  Thus we have $\Ext(G,\tilde P_{m,j}/F)=0$. 
-  If $F=0$, we have $\Ext(G,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $G$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_m)=0$ for $l\leq m+1$.
+  By Lemma~\ref{le:subrep}, any subrepresentation $\tilde G\subsetneq\tilde P_{m+1}^I$ is preprojective.
+  But the representation $\tilde P_{m,j}/\tilde F$ is not preprojective as it is a proper quotient of a preprojective representation unless $\tilde F=0$.
+  Thus we have $\Ext(\tilde G,\tilde P_{m,j}/\tilde F)=0$. 
+  If $\tilde F=0$, we have $\Ext(\tilde G,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $\tilde G$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_m)=0$ for $l\leq m+1$.
 
@@
   Assume $\tbfg=\udim\tilde P_{m+1}^I$.
-  By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(F,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
-  But the map $F\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
+  By Proposition~\ref{quotient}, the image of $\Psi_{\tbff,\tbfg}$ consist precisely of those pairs $(\tilde F,\tilde P_{m+1}^I)$ for which $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)=0$.
+  But the map $\tilde F\mapsto\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/\tilde F)$ is upper semicontinuous so that its minimal value on $\Gr_\tbff(\tilde P_{m,j})$ is its generic value, i.e.\ the image of $\Psi_{\tbff,\tbfg}$ is open.
 \qed\end{proof}
@@
   \label{cellscover}
-  For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
+  For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
   These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
-    \item[($\dagger$)] for any $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,I,J}(E')\neq 0$ for all $E'\in C_E$, where $C_E$ is the affine cell which contains $E$.
+    \item[($\dagger$)] for any $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E')\neq 0$ for all $\tilde E'\in C_{\tilde E}$, where $C_{\tilde E}$ is the affine cell which contains $\tilde E$.
   \end{itemize}
+  Moreover, the cell decompositions are independent of the choices made during their inductive construction.
 \end{theorem}
+We record the following immediate consequence before giving the proof.
 \begin{corollary}
@@
   For $m\ge2$, we work by reverse induction on $|J|$ with the base case $|J|=n-1$, say $J^c=\{j\}$.
-  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui,I,\{j\}}$ coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
-  By the induction on $m$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for each of the maps $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$, where $\ui'_1=(i_2,\ldots,i_k)$ with $i_2\ne j$.
-  But~$\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr^{\tilde Q}_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection maps $\tilde\pi_{m,j}^{\ui,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
-  Then using the equivalence $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\cong\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
-
-  Consider $J\subsetneq I\subsetneq \{1,\ldots,n\}$ with $I\setminus J=\{j\}$.
+  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}$, where $\ui'_1=(i_2,\ldots,i_k)$, coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
+  By the induction on $m$, the quiver Grassmannian $\Gr_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for each of the maps $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$.
+  But~$\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection maps $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
+  Then using the equivalence $\Gr_\tbfe(\tilde P_{m+1}^J)\cong\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ which is compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$.
+
+  Now consider $J\subsetneq I\subsetneq \{1,\ldots,n\}$ with $I\setminus J=\{j\}$.
   This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
-  By way of induction, we assume all quiver Grassmannians $Gr_\tbff(\tilde P_{m,j})$ and $Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$), say
+  By way of induction, we assume all quiver Grassmannians $\Gr_\tbff(\tilde P_{m,j})$ and $\Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$), say
   \begin{equation}
     \label{eq:cellB}
-    \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})=\coprod_{k=1}^r B_{\tbff,k}
+    \Gr_\tbff(\tilde P_{m,j})=\coprod_{k=1}^r B_{\tbff,k}
   \end{equation}
   and
-  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
-  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(F,G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
+  \[\Gr_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
+  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(\tilde F,\tilde G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
   \begin{itemize}
     \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
-    \item $m\ge3$ with $\tilde\pi_{m,j}^{j,I,\varnothing}(F)=0$.
+    \item $m\ge3$ with $\tilde\pi_{m,j}^{j,I,\varnothing}(\tilde F)=0$.
   \end{itemize}
@@
   It follows that there is an induced cell decomposition on the image of $\Psi_{\tbff,\tbfg}$ given by those products of cells $B_{\tbff,k}\times C_{\tbfg,\ell}$ over which the fiber is not empty.
-  Theorem \ref{vb} then provides a cell decomposition for $\cG_{\tbff,\tbfg}$, where cells take the form $B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
-  By Lemma~\ref{le:good partition}, we may order the affine cells in the $\cG_{\tbff,\tbfg}$ appropriately to obtain a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$ (c.f.
+  Theorem \ref{vb} then provides a cell decomposition for $\cG_{\tbff,\tbfg}$, where cells take the form $\AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
+  By Lemma~\ref{le:good partition}, we may order the affine cells in the $\cG_{\tbff,\tbfg}$ appropriately to obtain a cell decomposition of $\Gr_{\tbfe}(\tilde P_{m+1}^J)$ (c.f.
 Remark~\ref{rem:cell decompositions}).
 
-  Now consider $E\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $E\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and some subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
+  Now consider $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $\tilde E\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and some subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
   There are two cases to consider:
@@
     \item If $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
-      By construction, we have $\tilde\pi_{m+1}^{I,J}(E')\in C_{\tbfg,\ell}$ for all~$E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
-      But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(G)\ne0$ for all~$G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(E')\big)\neq 0$ for all $E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+      By construction, we have $\tilde\pi_{m+1}^{I,J}(\tilde E')\in C_{\tbfg,\ell}$ for all~$\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
+      But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(\tilde G)\ne0$ for all~$\tilde G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E')\big)\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
     \item If $i_1=j$, the restricted map $\tilde\pi_{m+1}^{\ui,I',J}\Big|_{\tilde P_{m,j}}$ coincides with $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}$ by Lemma~\ref{le:truncated quotients}.4.
-      By construction, we have $E'\cap P_{m,j}\in B_{\tbff,k}$ for all ~$E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
-      But $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(E\cap\tilde P_{m,j})=\tilde\pi_{m+1}^{\ui,I',J}(E)\ne0$ implies $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(F)\ne0$ for all~$F\in B_{\tbff,k}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(E')=\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(E'\cap \tilde P_{m,j})\neq 0$ for all $E'\in B_{\tbff,k}\times C_{\tbfg,\ell}\times\AA^d$.
+      By construction, we have $\tilde E'\cap \tilde P_{m,j}\in B_{\tbff,k}$ for all ~$\tilde E'\in \AA^d\times B_{\tbff,k} \times C_{\tbfg,\ell}$.
+      But $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E\cap\tilde P_{m,j})=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde F)\ne0$ for all~$\tilde F\in B_{\tbff,k}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E'\cap \tilde P_{m,j})\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
   \end{itemize}
-  Thus the compatibility condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
+  Thus the compatibility condition ($\dagger$) holds for the cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.
+
+  To see the final claim, there are three cases to consider.
+  The case $|J|=n-1$ is immediate from the construction above.
+  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ with $J\subsetneq I,I'$, $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
+  This gives rise to the following commutative diagram:
+  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
+    & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
+    0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
+    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
+  & & 0& 0&}\]
+  Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
+  Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
+  Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
+  In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
+  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde\pi_{m+1}^{I',J}(\tilde G')\in D$ and $\tilde G'\cap \tilde P_{m,j}\in B$.
+  Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
+  The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
+  For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
+  \begin{itemize}
+    \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
+    \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
+  \end{itemize}
+  It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.
+
+  Now suppose $|J|=n-2$, say $\{1,\ldots,n\}\setminus J=\{j,j'\}$.
+  This gives rise to the following commutative diagram:
+  \[\xymatrix{& 0 \ar[d] & 0 \ar[d] & & \\
+      0 \ar[r] & \tilde P_{m-1} \ar[r] \ar[d] \ar@{}[dr]|(.3){\ulcorner} & \tilde P_{m,j'} \ar[d]\ar[r] & \tilde P_{m,j'}^{\{j'\}} \ar[d]^{\sim}\ar[r] & 0 \\
+    0 \ar[r] & \tilde P_{m,j} \ar[r]\ar[d] & \tilde P_{m+1}^J\ar[d]\ar[r] & \tilde P_{m+1}^{\{j'\}^c} \ar[r]& 0\\
+    &\tilde P_{m,j}^{\{j\}}\ar[r]^{\sim}\ar[d] & \tilde P_{m+1}^{\{j\}^c}\ar[d] & & \\
+  & 0 & 0& &}\]
+  where $\tilde P_{m-1}$ is labeled as $\tilde P_{m-1,(j,j)}$ in the left vertical sequence and as $\tilde P_{m-1,(j',j')}$ in the upper horizontal sequence.
+  By a chase through this diagram dual to the previous case, we see that the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is the same regardless of whether we use the middle horizontal or the middle vertical sequence for its construction.
 \qed
@@
   \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
-  The results of \cite[Section 3]{cc} show that $\Psi_{\bfe}^{-1}(F,G)\cong\AA^{\dim\Hom(G,P_{j_{r'+1}}/F)}$ for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
+  The results of \cite[Section 3]{cc} show that $\Psi_{\bfe}^{-1}(\tilde F,\tilde G)\cong\AA^{\dim\Hom(\tilde G,P_{j_{r'+1}}/\tilde F)}$ for all $(\tilde F,\tilde G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
   Now every subrepresentation $G$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
   Moreover, the quotient $P_{j_{r'+1}}/F$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
-  Together these yield $\Ext(G,P_{j_{r'+1}}/F)=0$ and thus
-  \[\dim\Hom(G,P_{j_{r'+1}}/F)=\langle G, P_{j_{r'+1}}/F\rangle\]
-  for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
+  Together these yield $\Ext(\tilde G,P_{j_{r'+1}}/\tilde F)=0$ and thus
+  \[\dim\Hom(\tilde G,P_{j_{r'+1}}/\tilde F)=\langle \tilde G, P_{j_{r'+1}}/\tilde F\rangle\]
+  for all $(\tilde F,\tilde G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
   Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
@@
 
-As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{d(m,r)}$.
+While the cell decompositions above appear to depend on the data built into their recursive construction, the compatibility condition ($\dagger$) implies these cell decompositions exhibit a remarkable amount of recursive symmetry.
+\begin{corollary}
+  Fix an admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, and subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_1\notin J$ and $i_k\in I$.
+  Let $\tilde K_m=\tilde K_m(\ui,I,J)$ denote the kernel of the projection $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
+  For any dimension vectors $\tbfe,\tbff,\tbfg$ with $\tbfe=\tbff+\tbfg$, and any affine cell $A_\tbfe$ of $Gr_\tbfe(\tilde P_{m+1}^J)$ which intersects the preimage under the Caldero-Chapoton map of a product of affine cells $B_\tbff\times C_\tbfg$ from $Gr_\tbff(\tilde K_m)\times Gr_\tbfg(\tilde P_{m+1-k,\ui}^I)$, we have $\Psi(\tilde E)\in B_\tbff\times C_\tbfg$ for all $\tilde E\in A_\tbfe$.
+  Moreover, the induced map $A_\tbfe\to B_\tbff\times C_\tbfg$ is surjective with affine fibers.
+\end{corollary}
+\begin{proof}
+  \begin{itemize}
+    \item Implicit in the construction of the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is a choice of complete filtration for $\tilde P_{m+1}^J$ by subrepresentations of the form $\tilde K_m(\ui',I',J)$.
+      In Section~\ref{sec:2quivers}, we fix a standard convention.
+
+    \item By the compatibility of the cell $A_\tbfe$ with the map $\tilde\pi_{m+1}^{\ui,I,J}$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\ne 0$ for all $\tilde E\in A_\tbfe$.
+  \end{itemize}
+
+  Suppose the cell $A_\tbfe$ was constructed inductively using $J\subsetneq I'\subsetneq \{1,\ldots,n\}$ with $I'\setminus J=\{j\}$.
+\end{proof}
+
+As the $F$-polynomials of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{d(m,r)}$.
 The description of the non-empty fibers in Proposition~\ref{fibers} together with Corollary~\ref{fpoly} and Theorem~\ref{celldec} yield the following:
@@
   \end{align}
-  The image of a nonzero map $\tilde P_{m,i}\to\tau\tilde P_{m+1}^{[r]}$ is the representation $\tilde K_m$ from the appropriate sequence \eqref{eq:tau sequence}.
+  The image of a nonzero map $\tilde P_{m,i}\to\tau\tilde P_{m+1}^{[r]}$ is the representation $\tilde C_m$ from the appropriate sequence \eqref{eq:tau sequence}.
   Such a map is surjective if $m\ge3$ and for $m=2$ has image with support quiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,e)$.
   In view of Corollary~\ref{cor:perpendicular}, the sequence \eqref{eq:tau sequence} gives rise to an isomorphism 
-  \[\Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)\cong\Ext\big(\tilde P_{m+1}^{[r]},\tilde K_m\big).\]
+  \[\Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)\cong\Ext\big(\tilde P_{m+1}^{[r]},\tilde C_m\big).\]
 

### 2019-06-17 Grassmannian_cells.tex
Typo fixes

@@
   The case $|J|=n-1$ is immediate from the construction above.
-  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ with $J\subsetneq I,I'$, $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
+  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ containing $J$ so that $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
   This gives rise to the following commutative diagram:
@@
   In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
-  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde\pi_{m+1}^{I',J}(\tilde G')\in D$ and $\tilde G'\cap \tilde P_{m,j}\in B$.
+  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde G'\cap \tilde P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I\cup I',I'}(\tilde G')\in D$.
   Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.

### 2019-06-21 Grassmannian_cells.tex
Lemma 3.15

@@
 \begin{proof}
-  We proceed by induction on $m$.
-  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
-  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
-
-  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-\qed\end{proof}
-% We proceed by induction on $m$.
-% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
-% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
-
-% For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies that any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
-% Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
-%\qed\end{proof}
+  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
+  %We proceed by induction on $m$.
+  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
+  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
+
+  %For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
+  %Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
+\qed\end{proof}
 

### 2019-06-22 Grassmannian_cells.tex
Eliminated false claims in Theorem 4.20

@@
   \end{itemize}
-  Moreover, the cell decompositions are independent of the choices made during their inductive construction.
+% Moreover, the cell decompositions are independent of the choices made during their inductive construction.
 \end{theorem}
@@
 
-  To see the final claim, there are three cases to consider.
-  The case $|J|=n-1$ is immediate from the construction above.
-  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ containing $J$ so that $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
-  This gives rise to the following commutative diagram:
-  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
-    & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
-    0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
-    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
-  & & 0& 0&}\]
-  Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
-  Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
-  Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
-  In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
-  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde G'\cap \tilde P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I\cup I',I'}(\tilde G')\in D$.
-  Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
-  The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
-  For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
-  \begin{itemize}
-    \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
-    \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
-  \end{itemize}
-  It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.
-
-  Now suppose $|J|=n-2$, say $\{1,\ldots,n\}\setminus J=\{j,j'\}$.
-  This gives rise to the following commutative diagram:
-  \[\xymatrix{& 0 \ar[d] & 0 \ar[d] & & \\
-      0 \ar[r] & \tilde P_{m-1} \ar[r] \ar[d] \ar@{}[dr]|(.3){\ulcorner} & \tilde P_{m,j'} \ar[d]\ar[r] & \tilde P_{m,j'}^{\{j'\}} \ar[d]^{\sim}\ar[r] & 0 \\
-    0 \ar[r] & \tilde P_{m,j} \ar[r]\ar[d] & \tilde P_{m+1}^J\ar[d]\ar[r] & \tilde P_{m+1}^{\{j'\}^c} \ar[r]& 0\\
-    &\tilde P_{m,j}^{\{j\}}\ar[r]^{\sim}\ar[d] & \tilde P_{m+1}^{\{j\}^c}\ar[d] & & \\
-  & 0 & 0& &}\]
-  where $\tilde P_{m-1}$ is labeled as $\tilde P_{m-1,(j,j)}$ in the left vertical sequence and as $\tilde P_{m-1,(j',j')}$ in the upper horizontal sequence.
-  By a chase through this diagram dual to the previous case, we see that the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is the same regardless of whether we use the middle horizontal or the middle vertical sequence for its construction.
+% To see the final claim, there are three cases to consider.
+% The case $|J|=n-1$ is immediate from the construction above.
+% When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ containing $J$ so that $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
+% This gives rise to the following commutative diagram:
+% \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
+%   & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
+%   0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
+%   0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
+% & & 0& 0&}\]
+% Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
+% Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
+% Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
+% In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
+% Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde G'\cap \tilde P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I\cup I',I'}(\tilde G')\in D$.
+% Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
+% The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
+% For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
+% \begin{itemize}
+%   \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
+%   \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
+% \end{itemize}
+% It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.
+
+% Now suppose $|J|=n-2$, say $\{1,\ldots,n\}\setminus J=\{j,j'\}$.
+% This gives rise to the following commutative diagram:
+% \[\xymatrix{& 0 \ar[d] & 0 \ar[d] & & \\
+%     0 \ar[r] & \tilde P_{m-1} \ar[r] \ar[d] \ar@{}[dr]|(.3){\ulcorner} & \tilde P_{m,j'} \ar[d]\ar[r] & \tilde P_{m,j'}^{\{j'\}} \ar[d]^{\sim}\ar[r] & 0 \\
+%   0 \ar[r] & \tilde P_{m,j} \ar[r]\ar[d] & \tilde P_{m+1}^J\ar[d]\ar[r] & \tilde P_{m+1}^{\{j'\}^c} \ar[r]& 0\\
+%   &\tilde P_{m,j}^{\{j\}}\ar[r]^{\sim}\ar[d] & \tilde P_{m+1}^{\{j\}^c}\ar[d] & & \\
+% & 0 & 0& &}\]
+% where $\tilde P_{m-1}$ is labeled as $\tilde P_{m-1,(j,j)}$ in the left vertical sequence and as $\tilde P_{m-1,(j',j')}$ in the upper horizontal sequence.
+% By a chase through this diagram dual to the previous case, we see that the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is the same regardless of whether we use the middle horizontal or the middle vertical sequence for its construction.
 \qed

### 2019-06-24 Grassmannian_cells.tex
Lemma 3.15

@@
 \end{lemma}
-\begin{proof}
-  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
+\begin{proof}We use some of the ideas of the proof of \cite[Lemma IV.1.7]{ass}.
+For every proper subrepresentation $X$ of $P_{m+1}^V$ together with the natural embedding $\iota$, we get a pullback diagram
+\[\xymatrix{0 \ar[r] & P_m\otimes V \ar@{=}[d]\ar^f[r] & E\ar^g[r]\ar^h[d] & X \ar^{\iota}[d]\ar[r] & 0 \\
+    0 \ar[r] & P_m\otimes V \ar^{ev_V}[r] & P_{m+1} \ar^{\pi_{m+1}^V}[r] & P_{m+1}^V \ar[r] & 0}\]
+
+  Since the map $ev_V$ is irreducible, $f$ is either a section or $h$ a retraction.
+As $h$ is injective by the Snake lemma, it cannot be a retraction.
+It follows that $f$ is a section and thus $g$ a retraction.
+Thus we find a morphism $g':X\to E$ such that $g\circ g'=\mathrm{id}_X$.
+We obtain
+	$$\iota=\iota\circ\mathrm{id}_X=\iota\circ g\circ g'=\pi_{m+1}^V \circ h\circ g',$$i.e. $\iota$ factors through $P_{m+1}$,	and the claim follows from Lemma~\ref{le:preprojective subs}.
   %We proceed by induction on $m$.

### 2019-06-28 Grassmannian_cells.tex
Theorem 4.20 cleanup

@@
         %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
-        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
+        %\item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
       \end{itemize}
@@
   For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
-  These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
+  These cell decompositions can be chosen compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
   \begin{itemize}
-    \item[($\dagger$)] for any $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E')\neq 0$ for all $\tilde E'\in C_{\tilde E}$, where $C_{\tilde E}$ is the affine cell which contains $\tilde E$.
+    \item[($\dagger$)] for any $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exists a cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ so that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E')\neq 0$ for all $\tilde E'\in C_{\tilde E}$, where $C_{\tilde E}$ is the affine cell which contains $\tilde E$.
   \end{itemize}
-% Moreover, the cell decompositions are independent of the choices made during their inductive construction.
 \end{theorem}
@@
   This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}$, where $\ui'_1=(i_2,\ldots,i_k)$, coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
-  By the induction on $m$, the quiver Grassmannian $\Gr_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for each of the maps $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$.
-  But~$\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection maps $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
-  Then using the equivalence $\Gr_\tbfe(\tilde P_{m+1}^J)\cong\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ which is compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$.
-
-  Now consider $J\subsetneq I\subsetneq \{1,\ldots,n\}$ with $I\setminus J=\{j\}$.
+  By the induction on $m$, the quiver Grassmannian $\Gr_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for the map $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$.
+  But~$\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection map $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
+  Then using the equivalence $\Gr_\tbfe(\tilde P_{m+1}^J)\cong\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ which is compatible with the projection map $\tilde\pi_{m+1}^{\ui,I,J}$.
+
+  Now suppose $|J|\le n-2$ and consider an admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and a subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
+  Taking $j\notin J$ with $j\ne i_1$, we write $I=J\cup\{j\}$.
   This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
-  By way of induction, we assume all quiver Grassmannians $\Gr_\tbff(\tilde P_{m,j})$ and $\Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$), say
+  By way of induction, we assume all quiver Grassmannians $\Gr_\tbff(\tilde P_{m,j})$ and $\Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$) for the maps $\tilde\pi_{m,j}^{j,I',\varnothing}$ and $\tilde\pi_{m+1}^{\ui,I',I}$ respectively, say
   \begin{equation}
@@
   \[\Gr_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
-  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(\tilde F,\tilde G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
+  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(\tilde F,\tilde G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied:
   \begin{itemize}
@@
 
-  Now consider $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $\tilde E\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and some subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
-  There are two cases to consider:
-  \begin{itemize}
-    \item If $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
+  Now consider $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $\tilde E\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\neq 0$.
+  Since $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
   By construction, we have $\tilde\pi_{m+1}^{I,J}(\tilde E')\in C_{\tbfg,\ell}$ for all~$\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
   But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(\tilde G)\ne0$ for all~$\tilde G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E')\big)\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
-    \item If $i_1=j$, the restricted map $\tilde\pi_{m+1}^{\ui,I',J}\Big|_{\tilde P_{m,j}}$ coincides with $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}$ by Lemma~\ref{le:truncated quotients}.4.
-      By construction, we have $\tilde E'\cap \tilde P_{m,j}\in B_{\tbff,k}$ for all ~$\tilde E'\in \AA^d\times B_{\tbff,k} \times C_{\tbfg,\ell}$.
-      But $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E\cap\tilde P_{m,j})=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde F)\ne0$ for all~$\tilde F\in B_{\tbff,k}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E'\cap \tilde P_{m,j})\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
-  \end{itemize}
-  Thus the compatibility condition ($\dagger$) holds for the cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.
+  Thus the compatibility condition ($\dagger$) with $\tilde\pi_{m+1}^{\ui,I',J}$ holds for this cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.
 

### 2019-06-28 Grassmannian_cells.tex
Clean up

@@
 \end{theorem}
-\begin{proof}Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth.
-For the truncated preprojective representations of $K(n)$ this is Theorem~\ref{thm:truncpp}.
-For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively - when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) -  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth.
+\begin{proof}
+  Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth.
+  For the truncated preprojective representations of $K(n)$, this is Theorem~\ref{thm:truncpp}.
+  For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively -- when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) --  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth.
   Note that this is indeed clear for $m= 2$.
@@
 \qed\end{proof}
-
-While the cell decompositions above appear to depend on the data built into their recursive construction, the compatibility condition ($\dagger$) implies these cell decompositions exhibit a remarkable amount of recursive symmetry.
-\begin{corollary}
-  Fix an admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, and subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_1\notin J$ and $i_k\in I$.
-  Let $\tilde K_m=\tilde K_m(\ui,I,J)$ denote the kernel of the projection $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
-  For any dimension vectors $\tbfe,\tbff,\tbfg$ with $\tbfe=\tbff+\tbfg$, and any affine cell $A_\tbfe$ of $Gr_\tbfe(\tilde P_{m+1}^J)$ which intersects the preimage under the Caldero-Chapoton map of a product of affine cells $B_\tbff\times C_\tbfg$ from $Gr_\tbff(\tilde K_m)\times Gr_\tbfg(\tilde P_{m+1-k,\ui}^I)$, we have $\Psi(\tilde E)\in B_\tbff\times C_\tbfg$ for all $\tilde E\in A_\tbfe$.
-  Moreover, the induced map $A_\tbfe\to B_\tbff\times C_\tbfg$ is surjective with affine fibers.
-\end{corollary}
-\begin{proof}
-  \begin{itemize}
-    \item Implicit in the construction of the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is a choice of complete filtration for $\tilde P_{m+1}^J$ by subrepresentations of the form $\tilde K_m(\ui',I',J)$.
-      In Section~\ref{sec:2quivers}, we fix a standard convention.
-
-    \item By the compatibility of the cell $A_\tbfe$ with the map $\tilde\pi_{m+1}^{\ui,I,J}$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\ne 0$ for all $\tilde E\in A_\tbfe$.
-  \end{itemize}
-
-  Suppose the cell $A_\tbfe$ was constructed inductively using $J\subsetneq I'\subsetneq \{1,\ldots,n\}$ with $I'\setminus J=\{j\}$.
-\end{proof}
 

### 2019-06-30 response to reviewer.tex
Theorem 4.23 and other random edits

--- 2019-05-11 response to reviewer.tex
@@
-\documentclass[titlepage,11pt,a4paper]{{scrartcl}}
+\documentclass[11pt,a4paper]{{scrartcl}}
 \usepackage{amstext}
@@
 }
+
+\title{Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}
+\date{}
+
 \begin{document}
@@
 
-\noindent{\bf Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}\\
+\maketitle
 
-\noindent In the following, we point out the changes we made.
+\noindent In the following, we point out the changes made and give responses to the referee's comments.
 
-Section 4:
+\renewcommand{\labelenumi}{(\arabic{enumi})}
 \begin{enumerate}
-\renewcommand{\labelenumi}{(\arabic{enumi})}
-\item Note that the proof and the examples before show how to compute the kernel of the right hand vertical map for $m=2$ and $m=3$.
-As it is indeed not obvious to prove surjectivity for general $m$ directly, we deduce it from the $m=2,3$-cases and apply $\tau^{-1}$-shifts which preserve exact sequences if no direct summand is injective.
-This is mentioned in Remark 3.2 to which we refer to in the proof of Lemma 3.30.
-\item We omit the notation $~\perp$ as it is only used in Corollary 3.32.
-\item This should be a matter of definition and by reindexing appropriately we should get the version with $\ast$'s on the right.
-\item We refer to Cerulli Irelli's paper now.
-But not that the assumptions in Theorem 1 are stronger than ours as we do not assume that every basis element is mapped on a scalar multiple of another basis element.
-Note also that the number of fixed points is finite in Cerulli Irelli's case which is not true in general.
-\item We inserted a remark concerning the result of Haupt.
-Our approach seems to simplify the language and generalize the techniques of Haupt.
-If we are not mistaken, the proof of Theorem 1.2(c) in Section 8 only deals with those representations of the universal (abelian) covering whose dimension vectors only consists of $0$'s and $1$'s.
-We actually consider arbitrary representations of $\hat Q$.
-Moreover, the explicit description of the fixed points of $\mathrm{Gr}_{\mathbf{e}}(M)$ of a liftable representation $M$ as subrepresentations of the lifted representations $\hat M$ seems to be missing.
-
-\item We inserted a remark which addresses this issue.
-\item We inserted a remark in Theorem 4.22 (former 4.20) which is meant to explain how the statement is obtained from the claim. Moreover, it should make the proof clearer.
-\item I find the strategy if 4.23 is very clear and I also think that the proof of 4.24 is very close to the suggestion of the referee. Any ideas what to change?
+  \item[Section 3.1:] The referee's suggestions were incorporated into shortened proofs of Lemmas 3.4, 3.15 and motivated a rewriting of the proof of Lemma 3.9.
+  \item[Lemma 3.30:] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.
+  \item[Corollary 3.32:] The notation of perpendicular categories has been incorporated into the statement of the result.
+  \item[Definition 3.33:] We had overlooked this simple viewpoint on admissible sequences and thank the referee for these extremely helpful remarks.
+    The entire section has been somewhat reorganized to better capture the nature of the construction.
+  \item[After Definition 3.33:] After the reorganization, this notation is no longer being used.
+  \item[Before Lemma 3.34:] This typo has been corrected.
+  \item[Lemma 3.34:] Lemma 3.34 (now 3.33) has been rewritten to clarify the inductive structure of truncated preprojectives following the change of focus onto admissible sequences.
+  \item[Section 4.2:] This is a matter of convention.
+    In general, the placement of the $*$'s for an attracting set is equivalent to the choice of the map $d:\{1,\ldots,n\}\to\Zn$, cells of our chosen form impose the condition $d(1)>\cdots>d(n)$.
+  \item[Lemma 4.3:] We have added references to Cerulli Irelli and Haupt at the beginning of Section 4.2.
+    However, Haupt's statement is stronger than his proof since it assumes a thin lift to an abelian cover, a trait our representations rarely possess.
+    Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's construction when this applies.
+  \item[Section 4.4:] The dependence of various Caldero-Chapoton maps on their defining sequences has been clarified.
+  \item[Theorem 4.20:] The proof has been reorganized and rewritten to accommodate the changes of notation surrounding admissible sequences, we hope to have clarified the proof in the process.
+  \item[Theorem 4.21:] The proof has been rewritten to clarify the logic of the inductive construction by iterated torus actions.
+  \item[Corollary 4.22:] We believe the proof will not be shortened much by the notational changes suggested by the referee.
+    Moreover, the explicit nature of the recursion given allows one to easily construct a 2-quiver whose strong successor-closed subsets label the affine cells, Remark 4.25 has been added to alert the reader to this observation.
 \end{enumerate}

### 2019-06-30 Grassmannian_cells.tex
Theorem 4.23 and other random edits

@@
 \newcommand{\cC}{\mathcal{C}}
+\newcommand{\cF}{\mathcal{F}}
 \newcommand{\cG}{\mathcal{G}}
@@
   \label{th:rigids}
-  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
+  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $Q_m$ of $K(n)$ with dimension vectors 
   \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim Q_m=(u_{m-1},u_m).\]
@@
     \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
-      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 I_{m-1}\]
+      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 Q_{m-1}\]
       for $m\ge2$.
@@
 
-The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
+The truncated preprojective representation $P_{m+1}^V$ has dimension vector
+\[\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m.\]
 These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
@@
       \end{equation}
-      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
+      Moreover, $G(\tilde P_{m+1}^I)=:P_{m+1}^{\langle I\rangle}$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
   \end{enumerate}
@@
 
-  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
-  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
-  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
+  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $\langle I\rangle\subset \cH_m$ spanned by the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
+  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_{\langle I\rangle}:P_m\otimes \langle I\rangle\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
+  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^{\langle I\rangle}$ is truncated preprojective as well.
 \qed\end{proof}
@@
 
+For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
+\begin{corollary}
+  \label{cor:truncated lift}
+  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, the lift $\widetilde P_{m+1}^I$ of the truncated preprojective $P_{m+1}^{\langle I\rangle}$ is preprojective.
+\end{corollary}
+\begin{proof}
+  We see explicitly that $\widetilde P_2^I=\Big(\prod\limits_{j\in I^c}\tilde\Sigma_{(1,\alpha_j)}\Big)(\tilde S_{(2,e)})$ is preprojective.
+  The case $m\ge2$ then follows immediately from Lemma~\ref{le:truncated tau}.
+\qed\end{proof}
+
 We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations $\tilde P_{m+1}$.
@@
 The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
-For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
 \begin{lemma}
@@
 
+The following result of Caldero and Reineke lays a foundation for our approach.
+\begin{theorem}
+  \cite{cr}
+  \label{thm:smooth rigid}
+  Every quiver Grassmannian of a rigid representations of an acyclic quiver is smooth.
+\end{theorem}
+This allows the application of the torus method of Bia\l{}ynicki-Birula described in the following section.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
+  In particular, the existence of a cell decomposition of $C$ implies a cell decomposition of $\Att(C)$.
   Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$, where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
-  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
+  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$ and, when each $C_i$ admits a cell decomposition, we obtain a cell decomposition of $X$.
 \end{theorem}
@@
 \begin{corollary}
+  \label{cor:iterated fixed points}
   Let $X$ be a representation which can be lifted to $\tilde Q$.
@@
 
-Define the $F$-polynomial of a representation $X$ by 
-\[F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].\]
+Define the $\cF$-polynomial of a representation $X$ by 
+\[\cF_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].\]
 \begin{corollary}
@@
     \item If $\Gr_\bfe(X)$ is smooth and each $\Gr^{\tilde Q}_\tbfe(\tilde X)$ has a cell decomposition, then $\Gr_\bfe(X)$ has a cell decomposition.
-    \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
+    \item We have $\cF_X=S\cF_{\tilde X}$ where $S\cF_{\tilde X}$ is obtained from $\cF_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
   \end{enumerate} 
@@
   The quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ is smooth for each $V\in \Gr(\cH_m)$.
-  Moreover, for $V,W\in \Gr_d(\cH_m)$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$.
+  Moreover, for $V,W\in \Gr_r(\cH_m)$, $1\le r\le n-1$, we have $\Gr_\bfe(P_{m+1}^V)\cong \Gr_\bfe(P_{m+1}^W)$.
 \end{theorem}
@@
 \begin{corollary}
-  Every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
+  Every quiver Grassmannian of any lift of a (truncated) preprojective representation admits a cell decomposition.
 \end{corollary}
 \begin{proof}
-  For the standard lifts $\tilde P_m$, this is just the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
-  The claim for any translate $\tilde P_{m,w}$ for $w\in W_n$ is an immediate consequence of this.
+  For the standard lifts $\tilde P_{m+1}^J$, this is Theorem~\ref{cellscover}.
+  The claim for any translate $\tilde P_{m+1,w}^J$ for $w\in W_n$ is an immediate consequence of this.
 \qed\end{proof}
@@
   Thus the compatibility condition ($\dagger$) with $\tilde\pi_{m+1}^{\ui,I',J}$ holds for this cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.
-
-% To see the final claim, there are three cases to consider.
-% The case $|J|=n-1$ is immediate from the construction above.
-% When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ containing $J$ so that $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
-% This gives rise to the following commutative diagram:
-% \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
-%   & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
-%   0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
-%   0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
-% & & 0& 0&}\]
-% Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
-% Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
-% Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
-% In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
-% Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde G'\cap \tilde P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I\cup I',I'}(\tilde G')\in D$.
-% Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
-% The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
-% For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
-% \begin{itemize}
-%   \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
-%   \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
-% \end{itemize}
-% It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.
-
-% Now suppose $|J|=n-2$, say $\{1,\ldots,n\}\setminus J=\{j,j'\}$.
-% This gives rise to the following commutative diagram:
-% \[\xymatrix{& 0 \ar[d] & 0 \ar[d] & & \\
-%     0 \ar[r] & \tilde P_{m-1} \ar[r] \ar[d] \ar@{}[dr]|(.3){\ulcorner} & \tilde P_{m,j'} \ar[d]\ar[r] & \tilde P_{m,j'}^{\{j'\}} \ar[d]^{\sim}\ar[r] & 0 \\
-%   0 \ar[r] & \tilde P_{m,j} \ar[r]\ar[d] & \tilde P_{m+1}^J\ar[d]\ar[r] & \tilde P_{m+1}^{\{j'\}^c} \ar[r]& 0\\
-%   &\tilde P_{m,j}^{\{j\}}\ar[r]^{\sim}\ar[d] & \tilde P_{m+1}^{\{j\}^c}\ar[d] & & \\
-% & 0 & 0& &}\]
-% where $\tilde P_{m-1}$ is labeled as $\tilde P_{m-1,(j,j)}$ in the left vertical sequence and as $\tilde P_{m-1,(j',j')}$ in the upper horizontal sequence.
-% By a chase through this diagram dual to the previous case, we see that the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is the same regardless of whether we use the middle horizontal or the middle vertical sequence for its construction.
 \qed
-
+\bigskip
+Now we come to the main result of this work.
 \begin{theorem}
@@
   \begin{enumerate}
-    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
-    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
+    \item Every quiver Grassmannian of an indecomposable preprojective or preinjective representation of~$K(n)$ has a cell decomposition.
+    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $1\leq r\leq n-1$.
       Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition.
@@
 \begin{proof}
-  Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth.
-  For the truncated preprojective representations of $K(n)$, this is Theorem~\ref{thm:truncpp}.
-  For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively -- when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) --  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth.
-  Note that this is indeed clear for $m= 2$.
-
-  The first part now follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover}, taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation (c.f.\ Lemma~\ref{le:lifts of transjectives}).
-  The dual version for preinjective representations follows immediately since $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$.
-
-  The second part follows in the same way taking into account the initial remark.
+  We consider a representation $X$ of $K(n)$ which is either an indecomposable preprojective or truncated preprojective (c.f.
+Proposition~\ref{pro:indecomposables}.2), the results for preinjectives or the duals of truncated preprojectives follow via the isomorphisms
+  \[\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(Q_m) \qquad \text{and} \qquad \Gr_{\bfe}(P_{m+1}^V)\cong \Gr_{\udim P_{m+1}^V-\bfe}\big((P_{m+1}^V)^*\big),\]
+  where $(-)^*=\Hom_\CC(-,\CC)$ is the $\CC$-linear duality.
+
+  By Theorem~\ref{thm:smooth rigid}, each quiver Grassmannian $\Gr_\bfe(P_m)$ is smooth.
+  Theorem~\ref{thm:truncpp} shows each $\Gr_{\bfe}(P_{m+1}^V)$ is smooth and that, after an isomorphism, we may assume $V$ is a coordinate subspace under the decomposition in Lemma~\ref{le:basic homological properties}.
+  In particular, we can assume $P_{m+1}^V$ admits a lift to the universal covering quiver $\widetilde{K(n)}$.
+  This is true in the preprojective case by Lemma~\ref{le:lifts of transjectives}.
+
+  It follows that $X$ lifts to each iterated abelian cover $\widehat{K(n)}^{(k)}$.
+  As in Corollary~\ref{cor:truncated lift}, we see that each such lift is preprojective and thus the lifted representations all have smooth quiver Grassmannians.
+
+  Using Corollary~\ref{cor:iterated fixed points} and the associated iteration of Theorem~\ref{thm:bb}, we reduce the problem of constructing cell decompositions for the quiver Grassmannians of $X$ to constructing cells decompositions for the quiver Grassmannians of the lift to $\widetilde{K(n)}$.
+  The claim then follows from Theorem~\ref{cellscover}.
 \qed\end{proof}
@@
   As every exceptional representation of $K(n)$ is either preprojective or preinjective, we have
-  \[X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i},\]
+  \[X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sQ_{k_i},\]
   where we assume that $j_i\leq j_{i+1}$ and write
-  \[P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}\]
+  \[P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}Q_{k_i}\]
   for $r'\leq r$ and $s'\leq s$.
 
-  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$.
+  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $Q_{k_i}$.
   Consider the short exact sequence
@@
   \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
-  The results of \cite[Section 3]{cc} show that $\Psi_{\bfe}^{-1}(\tilde F,\tilde G)\cong\AA^{\dim\Hom(\tilde G,P_{j_{r'+1}}/\tilde F)}$ for all $(\tilde F,\tilde G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
+  The results of \cite[Section 3]{cc} show that $\Psi_{\bfe}^{-1}(F,G)\cong\AA^{\dim\Hom(G,P_{j_{r'+1}}/F)}$ for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
   Now every subrepresentation $G$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
   Moreover, the quotient $P_{j_{r'+1}}/F$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
-  Together these yield $\Ext(\tilde G,P_{j_{r'+1}}/\tilde F)=0$ and thus
-  \[\dim\Hom(\tilde G,P_{j_{r'+1}}/\tilde F)=\langle \tilde G, P_{j_{r'+1}}/\tilde F\rangle\]
-  for all $(\tilde F,\tilde G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
+  Together these yield $\Ext(G,P_{j_{r'+1}}/F)=0$ and thus
+  \[\dim\Hom(G,P_{j_{r'+1}}/F)=\langle G, P_{j_{r'+1}}/F\rangle\]
+  for all $(F,G)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
   Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
@@
   \[\ses{I(s)}{X}{P(r)}.\]
-  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition.
-\qed\end{proof}
-
-As the $F$-polynomials of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{d(m,r)}$.
+  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument as above shows that every quiver Grassmannian attached to $X$ has a cell decomposition.
+\qed\end{proof}
+\begin{remark}
+  The interested reader may utilize the iterative construction of the cell decomposition above to describe the cells using strong successor closed subsets of an appropriate 2-quiver as we do for the truncated preprojectives in the next section.
+\end{remark}
+
+As the $\cF$-polynomials of truncated preprojective representations only depend on the dimension vector, we may denote them by $\cF_{d(m,r)}$.
 The description of the non-empty fibers in Proposition~\ref{fibers} together with Corollary~\ref{fpoly} and Theorem~\ref{celldec} yield the following:
@@
   For $m\geq 1$ and $0\leq r\leq n-2$, we have 
-  \[F_{d(m,r)}=F_{d(m,r+1)}F_{\udim P_m}-x^{d(m,r)}F_{d(m-2,r)}.\]
+  \[\cF_{d(m,r)}=\cF_{d(m,r+1)}\cF_{\udim P_m}-x^{d(m,r)}\cF_{d(m-2,r)}.\]
 \end{corollary}

### 2019-06-30 Grassmannian_cells.tex
Intro edits

@@
 
-Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
+Although it follows from the results of Hille, Huisgen-Zimmermann, Reineke, and Ringel that every projective variety can be realized as a quiver Grassmannian, 
 it turns out that very interesting phenomena arise when restricting to certain quivers or to representations with certain properties.
@@
 The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians \cite{rupel}.
-A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.
+A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets of the associated 2-quiver and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.
 
@@
 In Section~\ref{sec:covering}, we collect several results concerning quiver covering theory.
-In Section~\ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which are needed later to investigate the quiver Grassmannians attached to preprojective representations.
+In Section~\ref{sec:RepK(n)}, we recall basic facts concerning the representation theory of generalized Kronecker quivers $K(n)$ which are needed later to investigate the quiver Grassmannians attached to preprojective representations (the preinjective case follows by duality and we do not address it directly).
 Our primary focus is on a special class of indecomposable representations which we call truncated preprojective representations.
@@
   Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
-  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
+  Then there exists a map $d:\supp(\hat X)\to\ZZ$ --- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ --- which induces a $\CC^*$-action on~$\Gr_\bfe^Q(X)$ such that
   \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
@@
 \end{thm}
-This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$-fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
+
+When $X$ lifts all the way to the universal covering quiver, this $\CC^*$-action can be iterated in such a way that the ultimate $\CC^*$-fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
 As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.

### 2019-07-01 Grassmannian_cells.tex
Small edit
revised version submitted to Math.Zeit.

@@
 
-%\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}
+\title{Cell Decompositions for Rank Two Quiver Grassmannians}
 
@@
 \begin{document}
-%\setcounter{tocdepth}{2}
-
-%\maketitle%\tableofcontents
+\setcounter{tocdepth}{2}
+
+\maketitle%\tableofcontents
 
@@
 \noindent
-We refer to \cite{gab} for an introduction to covering theory.
+We refer to \cite{gab} for an introduction to quiver covering theory.
 Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
@@
   Since the map $ev_V$ is irreducible, $f$ is either a section or $h$ a retraction.
-As $h$ is injective by the Snake lemma, it cannot be a retraction.
+As $h$ is injective by the Snake Lemma, it cannot be a retraction.
 It follows that $f$ is a section and thus $g$ a retraction.
